### 2021-05-15 paper/paper.tex
change layout

%\documentclass[a4paper,superscriptaddress,11pt]{quantumarticle}
%\documentclass[aps,twocolumn,longbibliography,english,superscriptaddress]{revtex4-1}
\documentclass{article}
\usepackage{iclr2021_conference}
%\documentclass[a4paper,superscriptaddress,11pt]{article}
\pdfoutput=1
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{tabularx}
\usepackage{quoting}
\usepackage{upquote}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage{wrapfig}
%\usepackage{caption}
%\usepackage[plain]{algorithm}
\usepackage[ruled, vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{rotating}
%\usepackage{cite}
\usepackage{booktabs}
%\usepackage{unicode-math}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
%\usepackage{algpseudocode}% http://ctan.org/pkg/algpseudocode
\usepackage{xcolor}% http://ctan.org/pkg/xcolor
\makeatletter
\newsavebox{\@brx}
\newcommand{\llangle}[1][]{\savebox{\@brx}{\(\m@th{#1\langle}\)}%
  \mathopen{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
\newcommand{\rrangle}[1][]{\savebox{\@brx}{\(\m@th{#1\rangle}\)}%
  \mathclose{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
\makeatother
\usepackage{bbm}
\usepackage{jlcode}
\usepackage{graphicx}
\usepackage{amsmath,color,amsthm}
\usepackage{mathrsfs}
\usepackage{float}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{indentfirst}
\usepackage{txfonts}
\usepackage[epsilon, tsrm, altpo]{backnaur}

\newcommand{\listingcaption}[1]%
{%
\refstepcounter{lstlisting}\hfill%
Listing \thelstlisting: #1\hfill%\hfill%
}%
\newcolumntype{b}{X}
\newcolumntype{s}{>{\hsize=.7\hsize}X}
\usepackage{listings}
\lstset{
    language=Julia,
    basicstyle=\ttfamily\scriptsize,
    numberstyle=\scriptsize,
    % numbers=left,
    backgroundcolor=\color{gray!7},
    %backgroundcolor=\color{white},
    %frame=single,
    xleftmargin=2em,
    tabsize=2,
    rulecolor=\color{black!15},
    %title=\lstname,
    escapeinside={(*}{*)},
    breaklines=true,
    %breakatwhitespace=true,
    %framextopmargin=2pt,
    %framexbottommargin=2pt,
    frame=bt,
    extendedchars=true,
    inputencoding=utf8,
    columns=fullflexible,
    %escapeinside={(*@}{@*)},
}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=1000
\hbadness=1000

\makeatletter

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.

%Journal reference.  Comma sets off: name, vol, page, year
\def\journal #1, #2, #3, 1#4#5#6{{\sl #1~}{\bf #2}, #3 (1#4#5#6) }
\def\pr{\journal Phys. Rev., }
\def\prb{\journal Phys. Rev. B, }
\def\prl{\journal Phys. Rev. Lett., }
\def\pl{\journal Phys. Lett., }
%\def\np{\journal Nucl. Phys., }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage{CJK}
%\usepackage[colorlinks, citecolor=blue]{hyperref}
\DeclareMathOperator*{\argmax}{arg\,max}

%%%%%% Shortcut related
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\out}{{\vx^L}}
\newcommand{\inp}{{\vx^0}}
\newcommand{\cquad}{{{ }_{\quad}}}
\newcommand{\pluseq}{\mathrel{+}=}
\newcommand{\minuseq}{\mathrel{-}=}
\newcommand{\vx}{{\mathbf{x}}}
\newcommand{\vg}{{\mathbf{g}}}
\newcommand{\vp}{{\mathbf{p}}}
\newcommand{\vy}{{\mathbf{y}}}
\newcommand{\Var}{{\mathrm{Var}}}
\newcommand{\Mean}{{\mathrm{E}}}
\newcommand{\vvalue}{{\texttt{value}}}
\newcommand{\grad}{{\texttt{grad}}}
\newcommand{\parameter}{{\texttt{parameter}}}
%%%%%% Convention related
\newcommand{\SWAP}{{\rm SWAP}}
\newcommand{\CNOT}{{\rm CNOT}}
\newcommand{\bigO}{{\mathcal{O}}}
\newcommand{\X}{{\rm X}}
\renewcommand{\H}{{\rm H}}
\newcommand{\Rx}{{\rm Rx}}
\renewcommand{\v}[1]{{\bf #1}}
\newcommand{\dataset}{{\mathcal{D}}}
\newcommand{\wfunc}{{\psi}}
\newcommand{\SU}{{\rm SU}}
\newcommand{\UU}{{\rm U}}
\newcommand{\thetav}{{\boldsymbol{\theta}}}
\newcommand{\gammav}{{\boldsymbol{\gamma}}}
\newcommand{\thetai}{{\theta^\alpha_l}}
\newcommand{\Expect}{{\mathbb{E}}}
\newcommand{\Tr}{{\rm Tr}}
\renewcommand{\cite}[1]{{\citep{#1}}}
\newcommand{\etc}{{\it etc~}}
\newcommand{\etal}{{\it etal~}}
\newcommand{\xset}{\mathbf{X}}
\newcommand{\fl}{\texttt{fl}}
\newcommand{\pdata}{\mathbf{\pi}}
\newcommand{\q}{\mathbf{q}}
\newcommand{\epdata}{\mathbf{\hat{\pi}}}
\newcommand{\gammaset}{\boldsymbol{\Gamma}}
\newcommand{\ei}{{\mathbf{e}_l^\alpha}}
\newcommand{\vtheta}{{\boldsymbol{\theta}}}
\newcommand{\sigmag}{{\nu}}
\newcommand{\sigmai}[2]{{\sigma^{#2}_{#1}}}
\newcommand{\qi}[1]{{q^{\alpha_{#1}}_{#1}}}
\newcommand{\BAS}{Bars-and-Stripes}
\newcommand{\circled}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
\newcommand{\qexpect}[1]{{\left\langle #1\right\rangle}}
\newcommand{\expect}[2]{{\mathop{\mathbb{E}}\limits_{\substack{#2}}\left[#1\right]}}
\newcommand{\var}[2]{{\mathop{\mathrm{Var}}\limits_{\substack{#2}}\left(#1\right)}}
\newcommand{\pshift}[1]{{p_{\thetav+#1}}}
\newcommand{\upcite}[1]{\textsuperscript{\cite{#1}}}
\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
\newcommand{\Fig}[1]{Fig.~\ref{#1}}
\newcommand{\Lst}[1]{Listing.~\ref{#1}}
\newcommand{\Tbl}[1]{Table~\ref{#1}}
\newcommand{\Sec}[1]{Sec.~\ref{#1}}
\newcommand{\App}[1]{Appendix~\ref{#1}}
\newcommand{\bra}[1]{\mbox{$\left\langle #1 \right|$}}
\newcommand{\ket}[1]{\mbox{$\left| #1 \right\rangle$}}
\newcommand{\braket}[2]{\mbox{$\left\langle #1 | #2 \right\rangle$}}
\newcommand{\tr}[1]{\mathrm{tr}\mbox{$\left[ #1\right]$}}

\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}

%%%%%% Comment related
\newcommand{\red}[1]{[{\bf  \color{red}{LW: #1}}]}
\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{LW: #1}}}]}
\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
\newcommand{\violet}[1]{[{\bf  \color{violet}{MLS: #1}}]}
\newcommand{\green}[1]{[{\bf  \color{green}{TZ: #1}}]}
\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{TZ: #1}}}]}
\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
\newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
\newcommand{\orange}[1]{\iffalse[{\bf  \color{orange}{Jo: #1}}]\fi}

\newtheorem{theorem}{\textit{Theorem}}
\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}

\makeatother

\iclrfinalcopy
\begin{document}
\title{Solving the maximum independant set problem with Tropical tensor networks}

\author{Jin-Guo Liu\\
Harvard University\\
\texttt{jinguoliu@harvard.edu}\\
%\AND
%Sheng-Tao Wang\\
%QuEra computing Inc.
}
\maketitle

\begin{abstract}
	Solving the maximum independent set size problem: the maximum independent set size, the degeneracy, the optimal configuration and the equivalence between different graphs.
\end{abstract}

\section{Tools}
\begin{description}
	\item[OMEinsum] a package for einsum \\ \href{https://github.com/under-Peter/OMEinsum.jl}{https://github.com/under-Peter/OMEinsum.jl}
	\item[TropicalGEMM] a package for efficient tropical matrix multiplication (compatible with OMEinsum) \\ \href{https://github.com/TensorBFS/TropicalGEMM.jl}{https://github.com/TensorBFS/TropicalGEMM.jl}
	\item[TropicalNumbers] a package providing tropical number types and tropical algebra, one o the dependency of TropicalGEMM \\ \href{https://github.com/TensorBFS/TropicalNumbers.jl}{https://github.com/TensorBFS/TropicalNumbers.jl}
\end{description}

\section{Computing degeneracy}
\section{The contraction of a widget}

\section{}

\bibliographystyle{iclr2021_conference}
\bibliography{refs}

\appendix

\end{document}

### 2021-05-15 src/tropicalwidget.jl

@@ -1,0 +1,436 @@
+### A Pluto.jl notebook ###
+# v0.12.21
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
+        el
+    end
+end
+
+# ╔═╡ 53ce616e-8055-11eb-0caf-e968c041ff4f
+using Revise, Viznet, Compose, TropicalNumbers, OMEinsum
+
+# ╔═╡ fadb61d5-0aac-496e-83e5-da89be0589ba
+using ForwardDiff
+
+# ╔═╡ a4faf523-31f2-4446-82d2-059e39793e62
+using PlutoUI
+
+# ╔═╡ 448c3e6a-8203-11eb-2c9e-fd7d2a3db9d2
+using Profile
+
+# ╔═╡ 69180ced-3729-4cf7-9fb4-db89de76469e
+function b(::Type{T}) where T
+	res = ones(T, 2, 2)
+	res[2, 2] = zero(T)
+	return res
+end
+
+# ╔═╡ 5df8b62e-8357-11eb-2322-f54c02f1dc6c
+b(TropicalF64)
+
+# ╔═╡ f005035b-b982-47f8-b292-28aac5b5c00d
+function v(::Type{T}, n::Int, val) where T
+	res = zeros(T, fill(2, n)...)
+	res[1] = one(T)
+	res[end] = T(val)
+	return res
+end
+
+# ╔═╡ 6c50f6de-8357-11eb-1a29-4f742afaeaa2
+v(TropicalF64, 3, 1.0)
+
+# ╔═╡ bb36b716-8357-11eb-1007-536e94c427c9
+zero(TropicalF64)
+
+# ╔═╡ bfda24e2-8357-11eb-1fb9-7390cc2b0988
+one(TropicalF64)
+
+# ╔═╡ c18e8111-16a8-42a8-8fa8-67ac76f4a13e
+begin
[…]

### 2021-05-18 paper/paper.tex
update note

@@
 \section{Computing degeneracy}
-\section{The contraction of a widget}
+\section{Utilizing the sparsity}
+Tensor network compression is an important tool to utilize sparsity.
+\subsection{The equivalence between branching and compression}
+We contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
+The maximum independant set size in this region with boundary configuration $\sigma \in \{0,1\}\otimes |C|$ is $A_{\sigma}$.
+We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
+\begin{align}
+(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
+\end{align}
+where $\land$ is a bitwise and operations.
+The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
+While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
+The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
+When Eq.
+\ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
+\section{Vertifying a widget}
 

### 2021-05-18 src/NoteOnTropicalMIS.jl

@@ -4,6 +4,7 @@ using TropicalGEMM, TropicalNumbers
 using OMEinsum
 
 include("tensors.jl")
+include("graphs.jl")
 include("viz.jl")
 
 end

### 2021-05-18 src/tropicalwidget.jl

@@ -1,116 +1,14 @@
-using Revise, Viznet, Compose, TropicalNumbers, OMEinsum
-using ForwardDiff
-
-# ╔═╡ 4053c327-43d2-4203-aa60-48b02a8c4dac
-nodes = let
-	a = 0.12
-	ymid = xmid = 0.5
-	X = 0.45
-	Y = 0.33
-	D = 0.15
-	y = [ymid-Y, ymid-Y+D, ymid-a/2, ymid+a/2, ymid+Y-D, ymid+Y]
-	x = [xmid-X, xmid-X+D, xmid-1.5a, xmid-a/2, xmid+a/2, xmid+1.5a, xmid+X-D, xmid+X]
-	xmin, xmax, ymin, ymax = x[1], x[end], y[1], y[end]
-	["a"=>(xmid, y[1]), "b"=>(xmin, ymid), "c"=>(xmid, ymax), "d"=>(xmax, ymid),
-		"e"=>(xmid, y[2]), "f"=>(x[2], ymid), "g"=>(xmid, y[end-1]),
-		"h"=>(x[end-1], ymid), "i"=>(x[3], y[3]), "j"=>(x[4], y[3]),
-		"k"=>(x[5], y[3]), "l"=>(x[6], y[3]), "m"=>(x[3], y[4]),
-		"n"=>(x[4], y[4]), "o"=>(x[5], y[4]), "p"=>(x[6], y[4])]
-end
-
-# ╔═╡ 6c9ed9a9-4579-4260-adba-6af2df243ec1
-function find_edges(nodes, distance)
-	edges = Tuple{Int,Int}[]
-	for (i, p) in enumerate(nodes)
-		for (j,p2) in enumerate(nodes)
-			if i<j && sqrt(sum(abs2, p2 .- p)) < distance
-				push!(edges, (i,j))
-			end
-		end
-	end
-	edges
-end
-
-# ╔═╡ ef28826a-24a5-48c7-b819-e42be90d05ab
-edges = find_edges(getindex.(nodes, 2), sqrt(0.05))
-
-# ╔═╡ e35ec714-70be-47bf-982f-1ef20d7ed470
-@assert length(edges) == 32
-
-# ╔═╡ 30b768c5-0ce0-4f4a-9981-a23f169b4a96
-function vizconfig(nodes, edges, config=zeros(Int, length(nodes)))
-	Compose.set_default_graphic_size(12cm, 12cm)
[…]

### 2021-05-18 src/viz.jl

@@ -1,31 +1,57 @@
 using Viznet
-using AbstractTrees
-using OMEinsum: NestedEinsum
+export viztnet, vizconfig
+using Compose
 
-function AbstractTrees.children(ne::NestedEinsum)
-    d = Dict()
-    for (k,item) in enumerate(ne.args)
-        d[k] = item isa Integer ? join(OMEinsum.getixs(ne.eins)[k]) : item
-    end
-    d
+vizconfig(ud::UnitdiskWidget, config=zeros(Int, length(ud.nodes))) = vizconfig(ud.nodes, edges(ud), config)
+viztnet(ud::UnitdiskWidget, config=zeros(Int, length(ud.nodes))) = viztnet(ud.nodes, edges(ud), config)
+
+function vizconfig(nodes, edges, config=zeros(Int, length(nodes)), unit=1.0, graphsize=12cm)
+	tb = textstyle(:default, fill("white"))
+	nb = nodestyle(:circle, fill("black"), r=0.02*unit)
+	nb2 = nodestyle(:circle, fill("red"),r=0.02*unit)
+	eb = bondstyle(:default)
+	img = canvas() do
+		for (i, (t, p)) in enumerate(nodes)
+			(config[i]==1 ? nb2 : nb) >> p
+			tb >> (p, t)
+		end
+		for (i,j) in edges
+			eb >> (nodes[i].second, nodes[j].second)
+		end
+	end
+    XMIN = minimum(x->x.second[1], nodes)
+    YMIN = minimum(x->x.second[2], nodes)
+    XMAX = maximum(x->x.second[1], nodes)
+    YMAX = maximum(x->x.second[2], nodes)
+    zoom_into(img, XMIN, XMAX, YMIN, YMAX; graphsize=graphsize)
 end
 
-function AbstractTrees.printnode(io::IO, x::String)
-    print(io, x)
-end
-function AbstractTrees.printnode(io::IO, x::NestedEinsum)
-    print(io, x.eins)
+function zoom_into(img, XMIN, XMAX, YMIN, YMAX; graphsize)
+    sx = 0.8/(XMAX-XMIN)
+    sy = 0.8/(YMAX-YMIN)
+	Compose.set_default_graphic_size(graphsize*sy/sx, graphsize)
+    Compose.compose(context(-((XMIN+XMAX)/2*sx-0.5), -((YMIN+YMAX)/2*sy-0.5), sx, sy), img)
 end
 
[…]

### 2021-05-18 test/tensors.jl

@@ -5,3 +5,9 @@ using TropicalNumbers
     @test misb(TropicalF64) == [TropicalF64(0) TropicalF64(0); TropicalF64(0) TropicalF64(-Inf)]
     @test misv(TropicalF64, 1, 2.0) == [TropicalF64(0), TropicalF64(2.0)]
 end
+
+edges = find_edges(getindex.(nodes, 2), sqrt(0.05))
+@test length(edges) == 32
+vizconfig(nodes, edges)
+res2 = contract_a(TropicalF64, ones(16))
+

### 2021-05-18 test/viz.jl

@@ -1,0 +1,2 @@
+using NoteOnTropicalMIS: widget12, widget16
+nodes = widget12()

### 2021-05-18 paper/paper.tex
update

@@
 
-\newtheorem{theorem}{\textit{Theorem}}
+\newtheorem{theorem}{\textit{Rule}}
 \theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
@@
 Tensor network compression is an important tool to utilize sparsity.
-\subsection{The equivalence between branching and compression}
+
 We contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
@@
 \ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
-\section{Vertifying a widget}
 
-\section{}
+\subsection{The equivalence between branching and compression}
+We are going the verify the Lemmas used in branching algorithm in book~\cite{Fomin2013}.
+\begin{theorem} % basic
+  If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
+On the other hand, if $I$ is a maximum (and thus maximal) independent set,
+and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
+\end{theorem}
+\begin{theorem} % 2.6
+Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
+\begin{equation}
+\alpha(G)=\alpha(G\backslash w).
+\end{equation}
+\end{theorem}
+
+\begin{theorem} % 2.7
+  Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
+independent set of $G$ contains $v$ then every maximum independent set of $G$ contains
+at least two vertices of $N(v)$.
+\end{theorem}
+
+\begin{theorem} % 2.8
+Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
+\begin{equation}
+\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
+\end{equation}
+\end{theorem}
+
+\begin{theorem} % 2.9
+Let $G = (V, E)$ be a graph and $v$ be a vertex of $G$ such that $N[v]$ is a
+clique. Then
+\begin{equation}
+\alpha(G) = 1 + \alpha(G \backslash N[v]).
+\end{equation}
+\end{theorem}
+
+\begin{theorem}  %2.10
+Let $G$ be a graph, let $S$ be a separator of $G$ and let $I(S)$ be the set of
+all subsets of $S$ being an independent set of $G$. Then
+\begin{equation}
+\alpha(G) = \max_{A\in I(S)} |A| + \alpha(G \backslash (S \cup N[A])).
+\end{equation}
+\end{theorem}
+
+\begin{theorem}  %2.11
+Let $G = (V, E)$ be a disconnected graph and $C \subseteq V$ a connected com-
+ponent of $G$. Then
+\begin{equation}
+\alpha(G) = \alpha(G[C]) + \alpha(G \backslash C)).
+\end{equation}
+\end{theorem}
+
+\begin{align}
+if |V| = 0 then
+return 0
+if \exists v \in V with d(v) \leq 1 then
+return 1 + mis2(G \backslash N[v])
+if \exists v \in V with d(v) = 2 then
+(let u 1 and u 2 be the neighbors of v)
+if {u 1 , u 2 } \in E then
+return 1 + mis2(G \backslash N[v])
+if {u 1 , u 2 } \in
+/ E then
+if |N 2 (v)| = 1 then
+(let N 2 (v) = {w})
+return max(2 + mis2(G \backslash (N 2 [v] \cup N[w])), 2 + mis2(G \backslash N 2 [v]))
+if |N 2 (v)| > 1 then
+return max(mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
+if \exists v \in V with d(v) = 3 then
+(let u 1 u 2 and u 3 be the neighbors of v)
+if G[N(v)] has no edge then
+if v has a mirror then
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup {v}))
+if v has no mirror then
+return max(1 + mis2(G \backslash N[v]), 2 + mis2(G \backslash N[{u 1 , u 2 }]), 2 + mis2(G \backslash
+(N[{u_1 , u_3 }] \cup \{u_2\})), 2 + mis2(G \backslash (N[{u_2 , u_3 }] \cup \{1\})))
+if G[N(v)] has one or two edges then
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
+if G[N(v)] has three edges then
+return 1 + mis2(G \backslash N[v])
+if \Delta (G) \geq 6 then
+choose a vertex v of maximum degree in G
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash v))
+if G is disconnected then
+(let C \subseteq V be a component of G)
+return mis2(G[C]) + mis2(G \backslash C)
+if G is 4 or 5-regular then
+choose any vertex v of G
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup \{v\}))
+if \Delta (G) = 5 and \delta (G) = 4 then
+choose adjacent vertices v and w with d(v) = 5 and d(w) = 4 in G
+return
+\max(1 + mis2(G \backslash N[v]), 1 + mis2(G \backslash (\{v\} \cup M(v) \cup N[w])), mis2(G \backslash (M(v) \cup \{v, w\})))
+\end{align}
 

### 2021-05-18 src/demos.jl

@@ -1,0 +1,1 @@
+ein"v,va,vb,vc"()

### 2021-05-25 paper/paper.tex
update paper

@@
 \section{Computing degeneracy}
+Consider the following 5 node graph.
+
+\begin{figure}[H]
+    \centerline{\includegraphics[width=0.4\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig1.pdf}}
+\end{figure}
+
+If put a vector of size $2$ at each vertex
+\begin{equation}
+    \left(\begin{matrix}
+        1 \\
+        x
+    \end{matrix}\right),
+\end{equation}
+
+and a matrix of size $2 \times 2$ at each edge
+\begin{equation}
+    \left(\begin{matrix}
+        1  & 1\\
+        1 & 0
+    \end{matrix}\right).
+\end{equation}
+
+\begin{figure}[H]
+    \centerline{\includegraphics[width=0.4\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig2.pdf}}
+\end{figure}
+
+Here $x$ is a variable. Then we contract this graph with einsum \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+The result is a scalar function of $x$, it corresponds to the independance polynomial~\cite{}.
+\begin{equation}
+I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the the degeneracy for independant set size $k$.
+
+\subsection{Symbolic computing}
+The most straight forward approach is the symbolic computing, where we store a polynomial of $x$ as a vector of factors.
+We define the algebra between these vectors of factors and insert them to the original tensor network contraction algorithm.
+However, this method suffers from a space overhead that propotional to the maximum independant set size.
+
+\subsection{Polynomial fitting}
+Let $m$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
+We compute the einsum contraction for each $x \in X$ and obtain the following relations
+\begin{align}
+a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
+a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
+\ldots&\\
+a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
+\end{align}
+The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
+
+\subsection{Fourier transformation}
+\begin{align}
+\left(\begin{matrix}
+1 & x_1 & x_1^2 & \ldots & x_1^m \\
+1 & x_2 & x_2^2 & \ldots & x_2^m \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_m & x_m^2 & \ldots & x_m^m
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right)
+\end{align}
+
+\begin{align}
+\left(\begin{matrix}
+1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
+1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right)
+\end{align}
+
+When $r=1$, the left side is a DFT matrix. We can obtain the factors using the relation $\vec a = {\rm FFT^{-1}}(\omega) \cdot \vec y$.
+In the special case that $\omega = e^{-2\pi i/(m+1)}$, it is directly solvable with inverse fast fourier transformation algorithm in package \texttt{FFTW}.
+
+\begin{equation}
+{\rm FFT}(\omega) \cdot \vec a_r = \vec y
+\end{equation}
+where $(\vec a_r)_k = a_k r ^k$, by choosing diferent $r$, we can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
+
+\subsection{Finite field algebra}
+
 \section{Utilizing the sparsity}
@@
 
-\subsection{The equivalence between branching and compression}
+\subsection{The tensor network compression detects branching rules automatically}
+
+\textit{max-size rule} The resulting tensor of Tropical tensor contraction stores only the local independant set size that maximizes the internal degrees on freedom.
+Where the internal degree of freedom are edges that does not connect to tensors not contracted.
+
+\textit{max-interior rule} The resulting tensor of Tropical tensor contraction stores only the local independant set size that maximizes the internal degrees on freedom.
+
 We are going the verify the Lemmas used in branching algorithm in book~\cite{Fomin2013}.
-\begin{theorem} % basic
+\begin{theorem}\label{rule:one} % basic
   If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
@@
 \end{theorem}
-\begin{theorem} % 2.6
+
+Contract $N[v]$, each entry of the resulting tensor of rank $|N(v)|$ corresponds to a locally maximized independant set size with fixed boundary configuration.
+If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independant set size.
+
+\begin{theorem} % 2.5
 Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
@@
 
-\begin{theorem} % 2.7
+Contract $N[w]$, both $\{v, w\}$ disapear from the tensor indices because they are inner degrees of freedom.
+If $w$ is one, then $N[v]$ are all zeros, the resulting tensor element can not be larger than setting $v=1$ and $w=0$.
+By the maximization rule, the local tensor does not change if we remove $w$.
+
+\begin{theorem} % 2.6
   Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
@@
 
-\begin{theorem} % 2.8
+\begin{theorem} % 2.7
 Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
@@
 \end{theorem}
+
+Here, $M(v)$ is the set of mirrors of $v$ in $G$.
+A vertex $w \in N^2(v)$ is called a mirror of $v$ if $N(v) \backslash N(w)$ is a clique.
+This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
+otherwise, there must be one of $N(v)$ in the MIS (maximization rule).
+If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (maximization rule),
+since clique has at most one node in the MIS, the tensor compression will eliminate this solution by moving the occuppied node to the interior.
+Hence, the tensor compression rule do captures the mirror rule.
 

### 2021-05-25 notebooks/proofs.jl

@@ -14,16 +14,22 @@ macro bind(def, element)
 end
 
 # ╔═╡ c8c14900-b7f5-11eb-3dbe-4390dd0fcc0a
-using Revise, OMEinsum, TropicalNumbers, NoteOnTropicalMIS, Compose, Viznet
+begin
+	using Revise, OMEinsum, OMEinsumContractionOrders, TropicalNumbers, NoteOnTropicalMIS, Compose, Viznet
+	using OMEinsumContractionOrders: uniformsize
+	function savetodisk(obj, filename)
+		obj |> SVG(filename*".svg")
+	end
+end;
+
+# ╔═╡ e56f2ba7-6a50-4400-b761-9f587076778f
+using Polynomials
 
 # ╔═╡ d1a8f940-c8b8-4ce6-af68-dee3a286e632
 using LightGraphs
 
 # ╔═╡ 8e2263d2-ffbf-4aa5-bf7e-29f16b2dbade
 using PlutoUI
-
-# ╔═╡ e56f2ba7-6a50-4400-b761-9f587076778f
-using Polynomials
 
 # ╔═╡ f2c1633a-0e2b-4ecc-81bf-f54fa0efcb44
 using FFTW
@@ -50,6 +56,26 @@ using Test
 # ╔═╡ a97d1c41-fb19-42ce-a412-68491f02a3fa
 using Primes
 
+# ╔═╡ d13e65e9-0cbb-42f7-b7e9-72237e353528
+using ProfileSVG
+
+# ╔═╡ 2a37780e-53b6-4a40-9738-5daba20c1001
+begin
+	node_black = nodestyle(:circle, r=0.03)
+	node_white = nodestyle(:circle, fill("white"), r=0.08)
+	edge_black = bondstyle(:default)
+	text_black = textstyle(:default)
+	text_white = textstyle(:default, fill("white"))
+	
+	function save_pdf(img, fname, save)
+		if save
+			img |> SVG("$fname.svg")
+		end
+		run(`rsvg-convert -f pdf -o $fname.pdf $fname.svg`)
+		return img
+	end
+end;
+
 # ╔═╡ b91528fe-6aa1-4c58-968e-a8997e895af3
 md"## Rule 0"
 
@@ -64,6 +90,9 @@ mis_solve(code1)
 
[…]

### 2021-05-25 src/polynomial.jl

@@ -1,0 +1,26 @@
+export mis_polysolve
+
+_auto_mispolytensor(x::T, ix::NTuple{2}) where T = T[1 1; 1 0]
+_auto_mispolytensor(x::T, ix::NTuple{1}) where T = T[1, x]
+function generate_polyxs!(x::T, code::OMEinsum.NestedEinsum, xs=Vector{Any}(undef, ninput(code))) where {T}
+    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
+		if arg isa Integer
+			xs[arg] = _auto_mispolytensor(x, ix)
+		else
+        	generate_polyxs!(x, arg, xs)
+		end
+    end
+	return xs
+end
+
+function generate_polyxs!(x::T, code::EinCode, xs=Vector{Any}(undef, ninput(code))) where {T}
+    for (i,ix) in enumerate(OMEinsum.getixs(code))
+		xs[i] = _auto_mispolytensor(x, ix)
+    end
+	return xs
+end
+
+function mis_polysolve(code, x::T) where {T}
+	xs = generate_polyxs!(x, code, Vector{Any}(undef, NoteOnTropicalMIS.ninput(code)))
+	code(xs...)
+end

### 2021-05-25 paper/paper.tex
update paper

@@
 \begin{document}
-\title{Solving the maximum independant set problem with Tropical tensor networks}
+\title{Solving the maximum independant set problem with tensor networks}
 
@@
 Harvard University\\
-\texttt{jinguoliu@harvard.edu}\\
+\texttt{jinguoliu@g.harvard.edu}\\
+\AND
+Xun Gao\\
+Harvard University\\
+\texttt{xungao@g.harvard.edu}\\
 %\AND
@@
 \begin{abstract}
-	Solving the maximum independent set size problem: the maximum independent set size, the degeneracy, the optimal configuration and the equivalence between different graphs.
+	Solving the maximum independent set size problem: the maximum independent set size, the independance polynomial and the optimal configuration.
 \end{abstract}
 
-\section{Tools}
+\section{Technical guide}
 \begin{description}
-	\item[OMEinsum] a package for einsum \\ \href{https://github.com/under-Peter/OMEinsum.jl}{https://github.com/under-Peter/OMEinsum.jl}
-	\item[TropicalGEMM] a package for efficient tropical matrix multiplication (compatible with OMEinsum) \\ \href{https://github.com/TensorBFS/TropicalGEMM.jl}{https://github.com/TensorBFS/TropicalGEMM.jl}
-	\item[TropicalNumbers] a package providing tropical number types and tropical algebra, one o the dependency of TropicalGEMM \\ \href{https://github.com/TensorBFS/TropicalNumbers.jl}{https://github.com/TensorBFS/TropicalNumbers.jl}
+	\item[OMEinsum] a package for einsum,
+	\item[OMEinsumContractionOrders] a package for finding the optimal contraction order for einsum \\ \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl},
+	\item[TropicalGEMM] a package for efficient tropical matrix multiplication (compatible with OMEinsum),
+	\item[TropicalNumbers] a package providing tropical number types and tropical algebra, one o the dependency of TropicalGEMM,
+	\item[LightGraphs] a package providing graph utilities, like random regular graph generator,
+	\item[Polynomials] a package providing polynomial algebra and polynomial fitting,
+	\item[Mods and Primes] packages providing finite field algebra and prime number generators.
 \end{description}
+
+One can install these packages by opening a julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
+\begin{lstlisting}
+pkg> add OMEinsum
+\end{lstlisting}
+
+An example of computing the maximum independant set size
+\begin{lstlisting}
+julia> using OMEinsum, LightGraphs, TropicalNumbers
+
+julia> n, k = 6, 3
+(6, 3)
+
+julia> g = LightGraphs.random_regular_graph(n, k)
+{6, 9} undirected simple Int64 graph
+
+julia> ixs = [minmax(e.src,e.dst) for e in LightGraphs.edges(g)]
+9-element Vector{Tuple{Int64, Int64}}:
+ (1, 2)
+ (1, 4)
+ (1, 5)
+ (2, 3)
+ (2, 6)
+ (3, 5)
+ (3, 6)
+ (4, 5)
+ (4, 6)
+
+julia> code = EinCode((ixs..., [(i,) for i in LightGraphs.vertices(g)]...), ())
+1∘2, 1∘4, 1∘5, 2∘3, 2∘6, 3∘5, 3∘6, 4∘5, 4∘6, 1, 2, 3, 4, 5, 6 ->
+
+julia> optimized_code = optimize_greedy(code, Dict([i=>2 for i=1:6]))
+4∘6, 4∘6 -> 
+├─ 4∘6, 6 -> 4∘6
+│  ├─ 6
+│  └─ 4∘6
+└─ 2∘5∘4, 5∘2∘6 -> 4∘6
+   ├─ 2∘5∘6, 6∘2 -> 5∘2∘6
+   │  ├─ 2∘6, 2 -> 6∘2
+   │  │  ├─ 2
+   │  │  └─ 2∘6
+   │  └─ 2∘3, 5∘6∘3 -> 2∘5∘6
+   │     ├─ 3∘5, 6∘3 -> 5∘6∘3
+   │     │  ├─ 3∘6, 3 -> 6∘3
+   │     │  │  ⋮
+   │     │  │  
+   │     │  └─ 3∘5, 5 -> 3∘5
+   │     │     ⋮
+   │     │     
+   │     └─ 2∘3
+   └─ 2∘4∘1, 1∘4∘5 -> 2∘5∘4
+      ├─ 1∘5, 5∘4 -> 1∘4∘5
+      │  ├─ 4∘5, 4 -> 5∘4
+      │  │  ├─ 4
+      │  │  └─ 4∘5
+      │  └─ 1∘5
+      └─ 2∘1, 1∘4 -> 2∘4∘1
+         ├─ 1∘4
+         └─ 1∘2, 1 -> 2∘1
+            ├─ 1
+            └─ 1∘2
+
+julia> function mis_contract(code::OMEinsum.NestedEinsum, x::T) where T
+           tensors = map(OMEinsum.getixs(Iterators.flatten(code))) do ix
+               @assert length(ix) == 1 || length(ix) == 2
+                           length(ix) == 1 ? [one(T), x] : [one(T) one(T); one(T) zero(T)]
+           end
+                 code(tensors...)
+       end
+mis_contract (generic function with 1 method)
+
+julia> result = mis_contract(optimized_code, Tropical(1.0))
+0-dimensional Array{TropicalF64, 0}:
+2.0ₜ
+\end{lstlisting}
+
+For larger graph, we hight recommend using two additional packages,
+\texttt{TropicalGEMM} for BLAS speed tropical matrix multiplication and
+\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar approach) ~\cite{Gray2021,Pan2021}.
 
@@
 \end{equation}
-
-and a matrix of size $2 \times 2$ at each edge
+were $x$ is a variable, and a matrix of size $2 \times 2$ at each edge
 \begin{equation}
@@
 
-Here $x$ is a variable. Then we contract this graph with einsum \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+Then we contract this graph with einsum \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 The result is a scalar function of $x$, it corresponds to the independance polynomial~\cite{}.

### 2021-05-25 notebooks/proofs.jl

@@ -56,9 +56,6 @@ using Test
 # ╔═╡ a97d1c41-fb19-42ce-a412-68491f02a3fa
 using Primes
 
-# ╔═╡ d13e65e9-0cbb-42f7-b7e9-72237e353528
-using ProfileSVG
-
 # ╔═╡ 2a37780e-53b6-4a40-9738-5daba20c1001
 begin
 	node_black = nodestyle(:circle, r=0.03)
@@ -547,7 +544,7 @@ end
 md"## Symbolic"
 
 # ╔═╡ ec4ef314-d42b-4a52-ae75-d109dab02426
-OMEinsum.asarray(x::Polynomial, y::AbstractArray{<:Polynomial}) = fill(x)
+OMEinsum.asarray(x::Polynomial, y::AbstractArray) = fill(x)
 
 # ╔═╡ 2f20b087-e990-44d5-abaf-c6605d1515ed
 mis_polysolve(optcode, Polynomial([0, 1]))
@@ -592,7 +589,7 @@ YS = let
 	
 	YS = []
 	for P in bigest_prime_table(Int, 5)
-		ys = [mis_polysolve(optcode, Mod{P,Int}(x))[] for x in xs]
+		ys = [mis_polysolve(optcode, Mod{P}(x))[] for x in xs]
 		push!(YS, ys)
 	end
 	YS
@@ -640,7 +637,7 @@ Base.isless(x::Mod{N}, y::Mod{N}) where N = mod(x.val, N) < mod(y.val, N)
 let
 	xs = 0:mis_result
 	N = prevprime(typemax(Int))
-	T = Mod{N,Int}
+	T = Mod{N}
 	ys = [mis_polysolve(optcode, T(x))[] for x in xs]
 	A = zeros(T, mis_result+1, mis_result+1)
 	for j=1:mis_result+1, i=1:mis_result+1
@@ -666,6 +663,9 @@ Mod{997}(1) == Mod{997}(998)
 
 # ╔═╡ 0ec2b495-07f3-40c8-833a-01223514521f
 Mod{997}(40) / Mod{997}(2341234)
+
+# ╔═╡ 13cb14b6-50e6-4f48-8243-b8793bdd4cbf
+inv(Mod{997}(37))
 
[…]

### 2021-05-26 paper/paper.tex
finite field method

@@
 %\usepackage[plain]{algorithm}
-\usepackage[ruled, vlined]{algorithm2e}
+\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
 \usepackage{algpseudocode}
@@
 \begin{abstract}
-	Solving the maximum independent set size problem: the maximum independent set size, the independance polynomial and the optimal configuration.
+	Solving the maximum independent set size problem: the maximum independent set size, the independence polynomial and the optimal configuration.
 \end{abstract}
@@
 \texttt{TropicalGEMM} for BLAS speed tropical matrix multiplication and
-\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar approach) ~\cite{Gray2021,Pan2021}.
+\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar~\cite{Schlag2020} approach) ~\cite{Gray2021,Pan2021}.
 
@@
 Then we contract this graph with einsum \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
-The result is a scalar function of $x$, it corresponds to the independance polynomial~\cite{}.
+The result is a scalar function of $x$, it corresponds to the independence polynomial~\cite{Ferrin2014}.
 \begin{equation}
@@
 \subsection{Finite field algebra}
+It is possible to compute the independence polynomials exactly using basic integer types only,
+even when the degeneracy is bigger than that can be represented by 64 bit integers.
+What we need is computing with the finite field algebra. In a finite field algebra $GF(p)$, we have the following observations
+\begin{enumerate}
+    \item One can still use Gaussian elimination~\cite{Golub2013} to solve the linear equations in a finite field, since the multiplicative inverse is properly defined in a finite field,
+    \item Let remainders of an integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$ being $\{x \pmod {p_1}, x\pmod {p_2}, \ldots, x \pmod {p_n}\}$,
+    then $\{x \pmod {p_1 \times p_2 \times \ldots \times p_n}\}$ can be obtained using the chinese remainder theorem.
+\end{enumerate}
+With these observations, we use Algorithm~\ref{alg:finitefield} to compute degeneracies.
+In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width.
+
+\begin{algorithm}[!ht]
+    \small
+    \SetAlgoNoLine
+    \LinesNumbered
+    Let $P = 1$, $X = {0,1,2,\ldots,m}$ and $\hat X_{ij} = X_i^j$, where $i,j = \{0, 1, \ldots m\}$\;
+    \While{true}{
+        compute the largest prime 64 bit integer $p$ that $\gcd(p, P) = 1$\;
+        compute the tensor network contraction on $GF(p)$ and obtain $Y\pmod p = \{y_0 \pmod p, y_1 \pmod p, \ldots , y_m \pmod p\} $\;
+        $A \pmod p = \{a_0 \pmod p, a_1 \pmod p, \ldots, a_m \pmod p\} = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+        $A \pmod {P\times p} = {\rm chinese\_remainder}(A \pmod P, A \pmod p)$\;
+        \If{$A \pmod P = A \pmod {P \times p}$}{
+            \Return $A \pmod P$\;
+        }
+        $P = P \times p$\;
+    }\caption{Compute independence polynomial exactly without integer overflow}\label{alg:finitefield}
+\end{algorithm}
 

### 2021-05-27 paper/paper.tex
update note

@@
 
+\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
 \newcommand{\listingcaption}[1]%
@@
 
-\newtheorem{theorem}{\textit{Rule}}
+\newtheorem{theorem}{\textit{Branching Rule}}
 \theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
@@
 \begin{document}
-\title{Solving the maximum independant set problem with tensor networks}
+\title{Solving the maximum independant set problem with einsum networks}
 
@@
 \end{abstract}
+
+\section{Computing independence polynomial}
+The independence polynomial~\cite{Ferrin2014, Harvey2017} of a graph $G$ is defined as
+\begin{equation}
+I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of order $k$ in $G$, and $\alpha(G)$ is the maximum independent set size of graph $G$.
+
+If we map a graph into an einsum network, as shown in \Fig{fig:einsummapping}, by putting a vertex tensor of size $2$ at each vertex
+\begin{equation}
+    W(x) = \left(\begin{matrix}
+        1 \\
+        x
+    \end{matrix}\right),
+\end{equation}
+were $x$ is a variable, and a matrix of size $2 \times 2$ at each edge
+\begin{equation}
+    B = \left(\begin{matrix}
+        1  & 1\\
+        1 & 0
+    \end{matrix}\right).
+\end{equation}
+
+The contractionof this einsum network is exactly the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+\begin{equation}
+    I(G, x) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i, s_j}.
+\end{equation}
+Here, the einsum enumerates all possible configurations and accumulates the product of tensor elements to the output.
+The product over edge tensors will provide a factor $0$ if the configuration is not an independent set, otherwise $1$.
+While the product over edges provide a factor $x^k$, where $k$ depends on how many times a vertex takes value $1$.
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}[t]{0.4\textwidth}
+        \centering
+        \centerline{\includegraphics[width=0.8\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig1.pdf}}
+        \caption{}
+    \end{subfigure}%
+    ~
+    \begin{subfigure}[t]{0.4\textwidth}
+        \centering
+    \centerline{\includegraphics[width=0.8\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig2.pdf}}
+        \caption{}
+    \end{subfigure}
+    \caption{Mapping a graph to an einsum network.}\label{fig:einsummapping}
+\end{figure*}
+The benefit of mapping the problem to einsum is, some existing algorithms can be used to decrease the complexity of the problem.
+Especially those techiniques developed in recent quantum circuit simulations for finding the optimal exactly contraction order of a tensor network ~\cite{Gray2021,Pan2021}.
+With these algorithms, one can easily find a good contraction order that reduces the complexity to a quantity related to the minimum treewidth of the graph.~\cite{Markov2008}
+Such mapping makes it possible to utilize fater linear algebra functions.
+
+\subsection{Symbolic computing}
+To evaluate this polynomial, one can use the symbolic computing directly.
+One can store a polynomial of $x$ as a vector of factors.
+We define the algebra between the polynomial expansions of order $k$ as
+\begin{align}
+    \begin{split}
+    a \oplus b &= \{a_0 + b_0, a_1 + b_1, \ldots, a_k + b_k\},\\
+    a \odot b &= \{a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_k + b_k\},\\
+    \mymathbb{0} &= \{\},\\
+    \mymathbb{1} &= \{1\},
+    \end{split}
+\end{align}
+and insert them to the original tensor network contraction algorithm.
+However, this method suffers from a space overhead that propotional to the maximum independant set size.
+
+\subsection{Polynomial fitting}
+Let $m$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
+We compute the einsum contraction for each $x \in X$ and obtain the following relations
+\begin{align}
+    \begin{split}
+a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
+a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
+\ldots&\\
+a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
+    \end{split}
+\end{align}
+The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
+
+\subsection{Fourier transformation}
+\begin{align}
+\left(\begin{matrix}
+1 & x_1 & x_1^2 & \ldots & x_1^m \\
+1 & x_2 & x_2^2 & \ldots & x_2^m \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_m & x_m^2 & \ldots & x_m^m
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right)
+\end{align}
+
+\begin{align}
+\left(\begin{matrix}
+1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
+1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right)
+\end{align}
+
+When $r=1$, the left side is a DFT matrix. We can obtain the factors using the relation $\vec a = {\rm FFT^{-1}}(\omega) \cdot \vec y$.
+In the special case that $\omega = e^{-2\pi i/(m+1)}$, it is directly solvable with inverse fast fourier transformation algorithm in package \texttt{FFTW}.
+
+\begin{equation}
+{\rm FFT}(\omega) \cdot \vec a_r = \vec y
+\end{equation}
+where $(\vec a_r)_k = a_k r ^k$, by choosing diferent $r$, we can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
+
+\subsection{Finite field algebra}
+It is possible to compute the independence polynomials exactly using basic integer types only,
+even when the degeneracy is bigger than that can be represented by 64 bit integers.
+What we need is computing with the finite field algebra $GF(p)$
+
+\begin{align}
+\begin{split}
+    x\pmod p ~\oplus~ y\pmod p &= x+y\pmod p\\
+    x\pmod p ~\odot~ y\pmod p &= xy\pmod p\\
+    \mymathbb{0} &= 0\\
+    \mymathbb{1} &= 1
+\end{split}
+\end{align}
+
+It a field because the multiplicative inverse can defined on non-zero values, which can be computed with the extended Euclidean algorithm.
+In a finite field algebra, we have the following observations
+\begin{enumerate}
+    \item One can still use Gaussian elimination~\cite{Golub2013} to solve the linear equations in a finite field, since the multiplicative inverse is properly defined in a finite field,
+    \item Let remainders of an integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$ being $\{x \pmod {p_1}, x\pmod {p_2}, \ldots, x \pmod {p_n}\}$,
+    then $\{x \pmod {p_1 \times p_2 \times \ldots \times p_n}\}$ can be obtained using the chinese remainder theorem.
+\end{enumerate}
+With these observations, we use Algorithm~\ref{alg:finitefield} to compute degeneracies.
+In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width.
+
+\begin{algorithm}[!ht]
+    \small
+    \SetAlgoNoLine
+    \LinesNumbered
+    Let $P = 1$, $X = {0,1,2,\ldots,m}$ and $\hat X_{ij} = X_i^j$, where $i,j = \{0, 1, \ldots m\}$\;
+    \While{true}{
+        compute the largest prime 64 bit integer $p$ that $\gcd(p, P) = 1$\;
+        compute the tensor network contraction on $GF(p)$ and obtain $Y\pmod p = \{y_0 \pmod p, y_1 \pmod p, \ldots , y_m \pmod p\} $\;
+        $A \pmod p = \{a_0 \pmod p, a_1 \pmod p, \ldots, a_m \pmod p\} = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+        $A \pmod {P\times p} = {\rm chinese\_remainder}(A \pmod P, A \pmod p)$\;
+        \If{$A \pmod P = A \pmod {P \times p}$}{
+            \Return $A \pmod P$\;
+        }
+        $P = P \times p$\;
+    }\caption{Compute independence polynomial exactly without integer overflow}\label{alg:finitefield}
+\end{algorithm}
+
+\section{Computing maximum independent set size and its degeneracy}
+Obtaining the maximum independent set size and its degeneracy is much easier. Let $x=\infty$, then the independence polynomial becomes
+\begin{equation}
+I(G, \infty) = a_k \infty^{\alpha(G)},
+\end{equation}
+where the lower orders terms disappear automatically. We can define a new algebra as
+\begin{align}
+\begin{split}
+    a_x\infty^x + a_y\infty^y &= \begin{cases}
+        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
+        a_y\infty^{\max(x,y)}, & x < y\\
+        a_x\infty^{\max(x,y)}, & x > y
+    \end{cases}\\
+    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
+    \mymathbb{0} &= -\infty\\
+    \mymathbb{1} &= 0
+\end{split}
+\end{align}
+In the program, we only store the power $x$ and the corresponding factor $a_x$. This is exactly the tropical tensor network~\cite{Liu2021} used in solving spin glass ground states.
+Here if we are only interested in obtaining $\alpha(G)$, we can only consider the powers, which corresponds to the tropical algebra~\cite{Maclagan2015}.
+
+\subsection{Utilizing sparsity}
+So far, we have used the language of einsum networks for contraction.
+When using sparse tropical tensor networks to find the maximum independent set, we can introduce a new rule to compress the tensor by removing elements that are not helpful.
+As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
+Each tensor entry $A_{\sigma}$ defines a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
+We call this properly the \textit{local maximum rule}.
+
+In addition, suppose we have two entries with the same local maximum independent set size corresponding to local configurations shown in (a) and (b), it is safe to claim configuration (a) being better than configuration (b) and remove the entry $A_{\sigma_b}$.
+This is because the boundary of (a) is less restrictive to the rest of the graph while having the equally good local maximum independent set size, 
+i.e. any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
+Hence an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ can be defined as
+\begin{align}
+(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
+\end{align}
+where $\land$ is a bitwise and operations.
+The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
+While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
+The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
+When Eq.
+\ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
+With this observation, it is safe to set $A_{\sigma_b}$ to tropical zero.
+We call this property the \textit{least restrictive rule}, that is,
+among boundary configurations with equal local maximum independent sizes,
+we only retain those least restrictive (less ones at the boundary) to exterial configurations.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
+    \caption{Two configurations with same local independent size $v_a = v_b = 3$ and different boundary configurations (a) ${001}$ and (b) ${101}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compressrule}
+\end{figure}
+
+\subsection{The tensor network compression detects branching rules automatically}
+In the following, we are going to show \textit{local maximum rule} and \textit{least restrictive rule} can automatically discover branching rules and use it for compressing tensor elements,
+i.e. sparse tropical tensor network can not be worse than branching in truncating the search space.
+
+We are going the verify the Lemmas used for branching in book~\cite{Fomin2013}.
+\begin{theorem}\label{rule:one} % basic
+  If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
+On the other hand, if $I$ is a maximum (and thus maximal) independent set,
+and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
+\end{theorem}
+
+Contract $N[v]$ and the resulting tensor $A$ has a rank $|N(v)|$.
+Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independant set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
+If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independant set size.
+
+\begin{theorem} % 2.5
+Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
+\begin{equation}
+\alpha(G)=\alpha(G\backslash w).
+\end{equation}
+\end{theorem}
+
+Contract $N[w]$, both $\{v, w\}$ disapear from the tensor indices because they are inner degrees of freedom.
+If $w$ is one, then $N[v]$ are all zeros, the resulting tensor element can not be larger than setting $v=1$ and $w=0$.
+By the maximization rule, the local tensor does not change if we remove $w$.
+
+\begin{theorem} % 2.6
+  Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
+independent set of $G$ contains $v$ then every maximum independent set of $G$ contains
+at least two vertices of $N(v)$.
+\end{theorem}
+Contract $N[v]$, the minimum tensor element is $2$, otherwise letting $v$ be in the independent set is one of the solutions. This is again captured by the \textit{local maximum rule}.
+
+\begin{theorem} % 2.7
+Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
+\begin{equation}
+\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
+\end{equation}
+\end{theorem}
+
+Here, $M(v)$ is the set of mirrors of $v$ in $G$.
+A vertex $w \in N^2(v)$ is called a mirror of $v$ if $N(v) \backslash N(w)$ is a clique.
+This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
+otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
+If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
+since clique has at most one node in the MIS, the tensor compression will eliminate this solution by moving the occuppied node to the interior.
+Hence, the \textit{least restrictive rule} captures the mirror rule.
+
+\begin{theorem} % 2.9
+Let $G = (V, E)$ be a graph and $v$ be a vertex of $G$ such that $N[v]$ is a
+clique. Then
+\begin{equation}
+\alpha(G) = 1 + \alpha(G \backslash N[v]).
+\end{equation}
+\end{theorem}
+
+Contract $N[v]$, and this rule can be captured by the \textit{local maximum rule}.
+
+\begin{theorem}  %2.10
+Let $G$ be a graph, let $S$ be a separator of $G$ and let $I(S)$ be the set of
+all subsets of $S$ being an independent set of $G$. Then
+\begin{equation}
+\alpha(G) = \max_{A\in I(S)} |A| + \alpha(G \backslash (S \cup N[A])).
+\end{equation}
+\end{theorem}
+This rule corresponds to first contract tensors in subgraph $S$, then $N[S]$, and then contract the rest parts.
+These branching rule can be captured by the \textit{local maximum rule}.
+
+\begin{theorem}  %2.11
+Let $G = (V, E)$ be a disconnected graph and $C \subseteq V$ a connected component of $G$. Then
+\begin{equation}
+\alpha(G) = \alpha(G[C]) + \alpha(G \backslash C)).
+\end{equation}
+\end{theorem}
+Contract by the disconnected parts, and this rule can be captured by the \textit{local maximum rule}.
+
+\iffalse
+\begin{align}
+if |V| = 0 then
+return 0
+if \exists v \in V with d(v) \leq 1 then
+return 1 + mis2(G \backslash N[v])
+if \exists v \in V with d(v) = 2 then
+(let u 1 and u 2 be the neighbors of v)
+if {u 1 , u 2 } \in E then
+return 1 + mis2(G \backslash N[v])
+if {u 1 , u 2 } \in
+/ E then
+if |N 2 (v)| = 1 then
+(let N 2 (v) = {w})
+return max(2 + mis2(G \backslash (N 2 [v] \cup N[w])), 2 + mis2(G \backslash N 2 [v]))
+if |N 2 (v)| > 1 then
+return max(mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
+if \exists v \in V with d(v) = 3 then
+(let u 1 u 2 and u 3 be the neighbors of v)
+if G[N(v)] has no edge then
+if v has a mirror then
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup {v}))
+if v has no mirror then
+return max(1 + mis2(G \backslash N[v]), 2 + mis2(G \backslash N[{u 1 , u 2 }]), 2 + mis2(G \backslash
+(N[{u_1 , u_3 }] \cup \{u_2\})), 2 + mis2(G \backslash (N[{u_2 , u_3 }] \cup \{1\})))
+if G[N(v)] has one or two edges then
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
+if G[N(v)] has three edges then
+return 1 + mis2(G \backslash N[v])
+if \Delta (G) \geq 6 then
+choose a vertex v of maximum degree in G
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash v))
+if G is disconnected then
+(let C \subseteq V be a component of G)
+return mis2(G[C]) + mis2(G \backslash C)
+if G is 4 or 5-regular then
+choose any vertex v of G
+return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup \{v\}))
+if \Delta (G) = 5 and \delta (G) = 4 then
+choose adjacent vertices v and w with d(v) = 5 and d(w) = 4 in G
+return
+\max(1 + mis2(G \backslash N[v]), 1 + mis2(G \backslash (\{v\} \cup M(v) \cup N[w])), mis2(G \backslash (M(v) \cup \{v, w\})))
+\end{align}
+\fi
+
+\bibliographystyle{iclr2021_conference}
+\bibliography{refs}
+
+\appendix
 
@@
 
-\section{Computing degeneracy}
-Consider the following 5 node graph.
-
-\begin{figure}[H]
-    \centerline{\includegraphics[width=0.4\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig1.pdf}}
-\end{figure}
-
-If put a vector of size $2$ at each vertex
-\begin{equation}
-    \left(\begin{matrix}
-        1 \\
-        x
-    \end{matrix}\right),
-\end{equation}
-were $x$ is a variable, and a matrix of size $2 \times 2$ at each edge
-\begin{equation}
-    \left(\begin{matrix}
-        1  & 1\\
-        1 & 0
-    \end{matrix}\right).
-\end{equation}
-
-\begin{figure}[H]
-    \centerline{\includegraphics[width=0.4\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig2.pdf}}
-\end{figure}
-
-Then we contract this graph with einsum \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
-The result is a scalar function of $x$, it corresponds to the independence polynomial~\cite{Ferrin2014}.
-\begin{equation}
-I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the the degeneracy for independant set size $k$.
-
-\subsection{Symbolic computing}
-The most straight forward approach is the symbolic computing, where we store a polynomial of $x$ as a vector of factors.
-We define the algebra between these vectors of factors and insert them to the original tensor network contraction algorithm.
-However, this method suffers from a space overhead that propotional to the maximum independant set size.
-
-\subsection{Polynomial fitting}
-Let $m$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
-We compute the einsum contraction for each $x \in X$ and obtain the following relations
-\begin{align}
-a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
-a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
-\ldots&\\
-a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
-\end{align}
-The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
-
-\subsection{Fourier transformation}
-\begin{align}
-\left(\begin{matrix}
-1 & x_1 & x_1^2 & \ldots & x_1^m \\
-1 & x_2 & x_2^2 & \ldots & x_2^m \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_m & x_m^2 & \ldots & x_m^m
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right)
-\end{align}
-
-\begin{align}
-\left(\begin{matrix}
-1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
-1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right)
-\end{align}
-
-When $r=1$, the left side is a DFT matrix. We can obtain the factors using the relation $\vec a = {\rm FFT^{-1}}(\omega) \cdot \vec y$.
-In the special case that $\omega = e^{-2\pi i/(m+1)}$, it is directly solvable with inverse fast fourier transformation algorithm in package \texttt{FFTW}.
-
-\begin{equation}
-{\rm FFT}(\omega) \cdot \vec a_r = \vec y
-\end{equation}
-where $(\vec a_r)_k = a_k r ^k$, by choosing diferent $r$, we can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
-
-\subsection{Finite field algebra}
-It is possible to compute the independence polynomials exactly using basic integer types only,
-even when the degeneracy is bigger than that can be represented by 64 bit integers.
-What we need is computing with the finite field algebra. In a finite field algebra $GF(p)$, we have the following observations
-\begin{enumerate}
-    \item One can still use Gaussian elimination~\cite{Golub2013} to solve the linear equations in a finite field, since the multiplicative inverse is properly defined in a finite field,
-    \item Let remainders of an integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$ being $\{x \pmod {p_1}, x\pmod {p_2}, \ldots, x \pmod {p_n}\}$,
-    then $\{x \pmod {p_1 \times p_2 \times \ldots \times p_n}\}$ can be obtained using the chinese remainder theorem.
-\end{enumerate}
-With these observations, we use Algorithm~\ref{alg:finitefield} to compute degeneracies.
-In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width.
-
-\begin{algorithm}[!ht]
-    \small
-    \SetAlgoNoLine
-    \LinesNumbered
-    Let $P = 1$, $X = {0,1,2,\ldots,m}$ and $\hat X_{ij} = X_i^j$, where $i,j = \{0, 1, \ldots m\}$\;
-    \While{true}{
-        compute the largest prime 64 bit integer $p$ that $\gcd(p, P) = 1$\;
-        compute the tensor network contraction on $GF(p)$ and obtain $Y\pmod p = \{y_0 \pmod p, y_1 \pmod p, \ldots , y_m \pmod p\} $\;
-        $A \pmod p = \{a_0 \pmod p, a_1 \pmod p, \ldots, a_m \pmod p\} = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
-        $A \pmod {P\times p} = {\rm chinese\_remainder}(A \pmod P, A \pmod p)$\;
-        \If{$A \pmod P = A \pmod {P \times p}$}{
-            \Return $A \pmod P$\;
-        }
-        $P = P \times p$\;
-    }\caption{Compute independence polynomial exactly without integer overflow}\label{alg:finitefield}
-\end{algorithm}
-
-\section{Utilizing the sparsity}
-Tensor network compression is an important tool to utilize sparsity.
-
-We contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
-The maximum independant set size in this region with boundary configuration $\sigma \in \{0,1\}\otimes |C|$ is $A_{\sigma}$.
-We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
-\begin{align}
-(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
-\end{align}
-where $\land$ is a bitwise and operations.
-The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
-While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
-The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
-When Eq.
-\ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
-
-\subsection{The tensor network compression detects branching rules automatically}
-
-\textit{max-size rule} The resulting tensor of Tropical tensor contraction stores only the local independant set size that maximizes the internal degrees on freedom.
-Where the internal degree of freedom are edges that does not connect to tensors not contracted.
-
-\textit{max-interior rule} The resulting tensor of Tropical tensor contraction stores only the local independant set size that maximizes the internal degrees on freedom.
-
-We are going the verify the Lemmas used in branching algorithm in book~\cite{Fomin2013}.
-\begin{theorem}\label{rule:one} % basic
-  If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
-On the other hand, if $I$ is a maximum (and thus maximal) independent set,
-and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
-\end{theorem}
-
-Contract $N[v]$, each entry of the resulting tensor of rank $|N(v)|$ corresponds to a locally maximized independant set size with fixed boundary configuration.
-If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independant set size.
-
-\begin{theorem} % 2.5
-Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
-\begin{equation}
-\alpha(G)=\alpha(G\backslash w).
-\end{equation}
-\end{theorem}
-
-Contract $N[w]$, both $\{v, w\}$ disapear from the tensor indices because they are inner degrees of freedom.
-If $w$ is one, then $N[v]$ are all zeros, the resulting tensor element can not be larger than setting $v=1$ and $w=0$.
-By the maximization rule, the local tensor does not change if we remove $w$.
-
-\begin{theorem} % 2.6
-  Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
-independent set of $G$ contains $v$ then every maximum independent set of $G$ contains
-at least two vertices of $N(v)$.
-\end{theorem}
-
-\begin{theorem} % 2.7
-Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
-\begin{equation}
-\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
-\end{equation}
-\end{theorem}
-
-Here, $M(v)$ is the set of mirrors of $v$ in $G$.
-A vertex $w \in N^2(v)$ is called a mirror of $v$ if $N(v) \backslash N(w)$ is a clique.
-This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
-otherwise, there must be one of $N(v)$ in the MIS (maximization rule).
-If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (maximization rule),
-since clique has at most one node in the MIS, the tensor compression will eliminate this solution by moving the occuppied node to the interior.
-Hence, the tensor compression rule do captures the mirror rule.
-
-\begin{theorem} % 2.9
-Let $G = (V, E)$ be a graph and $v$ be a vertex of $G$ such that $N[v]$ is a
-clique. Then
-\begin{equation}
-\alpha(G) = 1 + \alpha(G \backslash N[v]).
-\end{equation}
-\end{theorem}
-
-\begin{theorem}  %2.10
-Let $G$ be a graph, let $S$ be a separator of $G$ and let $I(S)$ be the set of
-all subsets of $S$ being an independent set of $G$. Then
-\begin{equation}
-\alpha(G) = \max_{A\in I(S)} |A| + \alpha(G \backslash (S \cup N[A])).
-\end{equation}
-\end{theorem}
-
-\begin{theorem}  %2.11
-Let $G = (V, E)$ be a disconnected graph and $C \subseteq V$ a connected com-
-ponent of $G$. Then
-\begin{equation}
-\alpha(G) = \alpha(G[C]) + \alpha(G \backslash C)).
-\end{equation}
-\end{theorem}
-
-\begin{align}
-if |V| = 0 then
-return 0
-if \exists v \in V with d(v) \leq 1 then
-return 1 + mis2(G \backslash N[v])
-if \exists v \in V with d(v) = 2 then
-(let u 1 and u 2 be the neighbors of v)
-if {u 1 , u 2 } \in E then
-return 1 + mis2(G \backslash N[v])
-if {u 1 , u 2 } \in
-/ E then
-if |N 2 (v)| = 1 then
-(let N 2 (v) = {w})
-return max(2 + mis2(G \backslash (N 2 [v] \cup N[w])), 2 + mis2(G \backslash N 2 [v]))
-if |N 2 (v)| > 1 then
-return max(mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
-if \exists v \in V with d(v) = 3 then
-(let u 1 u 2 and u 3 be the neighbors of v)
-if G[N(v)] has no edge then
-if v has a mirror then
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup {v}))
-if v has no mirror then
-return max(1 + mis2(G \backslash N[v]), 2 + mis2(G \backslash N[{u 1 , u 2 }]), 2 + mis2(G \backslash
-(N[{u_1 , u_3 }] \cup \{u_2\})), 2 + mis2(G \backslash (N[{u_2 , u_3 }] \cup \{1\})))
-if G[N(v)] has one or two edges then
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
-if G[N(v)] has three edges then
-return 1 + mis2(G \backslash N[v])
-if \Delta (G) \geq 6 then
-choose a vertex v of maximum degree in G
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash v))
-if G is disconnected then
-(let C \subseteq V be a component of G)
-return mis2(G[C]) + mis2(G \backslash C)
-if G is 4 or 5-regular then
-choose any vertex v of G
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup \{v\}))
-if \Delta (G) = 5 and \delta (G) = 4 then
-choose adjacent vertices v and w with d(v) = 5 and d(w) = 4 in G
-return
-\max(1 + mis2(G \backslash N[v]), 1 + mis2(G \backslash (\{v\} \cup M(v) \cup N[w])), mis2(G \backslash (M(v) \cup \{v, w\})))
-\end{align}
-
-\bibliographystyle{iclr2021_conference}
-\bibliography{refs}
-
-\appendix
-
 \end{document}

### 2021-05-27 notebooks/proofs.jl

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.14.5
+# v0.14.6
 
 using Markdown
 using InteractiveUtils
@@ -56,9 +56,13 @@ using Test
 # ╔═╡ a97d1c41-fb19-42ce-a412-68491f02a3fa
 using Primes
 
+# ╔═╡ d13e65e9-0cbb-42f7-b7e9-72237e353528
+using ProfileSVG
+
 # ╔═╡ 2a37780e-53b6-4a40-9738-5daba20c1001
 begin
 	node_black = nodestyle(:circle, r=0.03)
+	node_red = nodestyle(:circle, fill("red"), r=0.03)
 	node_white = nodestyle(:circle, fill("white"), r=0.08)
 	edge_black = bondstyle(:default)
 	text_black = textstyle(:default)
@@ -72,6 +76,105 @@ begin
 		return img
 	end
 end;
+
+# ╔═╡ a8ac2b58-86c7-4964-ac10-46c842cbe731
+canvas() do
+	Compose.set_default_graphic_size(8cm, 8cm)
+	xs = [(0.1, 0.5), (0.1, 0.7), (0.3, 0.5), (0.4, 0.8), (0.5, 0.6), (0.3, 0.3), (0.5, 0.2), (0.6, 0.7), (0.7, 0.4), (0.9, 0.5)]
+	for (i, loc) in enumerate(xs)
+		(i ∈ (3,4,5,6,7) ? node_red : node_black) >> loc
+		text_white >> (loc, string('a'+i-1))
+	end
+	for (i,j) in [(1, 2), (2,3), (1,3), (3, 4), (4, 5), (5, 6), (6,7), (7,8), (8, 9), (9, 10), (3, 5), (3, 6), (7,9), (6,9), (10,8), (3,9)]
+		edge_black >> (xs[i], xs[j])
+	end
+end
+
+# ╔═╡ e57abcc2-7b48-4e38-a90a-fe6a6bc1eeb7
+let
+	img1 = canvas() do
+		xs = [(0.1, 0.5), (0.1, 0.7), (0.3, 0.5), (0.4, 0.8), (0.5, 0.6), (0.3, 0.3), (0.5, 0.2), (0.6, 0.7), (0.7, 0.4), (0.9, 0.5)]
+		for (i, loc) in enumerate(xs)
[…]

### 2021-05-28 src/NoteOnTropicalMIS.jl
independence polynomial

@@ -5,7 +5,8 @@ using OMEinsum
 
 include("tensors.jl")
 include("graphs.jl")
-include("polynomial.jl")
+include("independence_polynomial.jl")
+include("random_regular_graph.jl")
 include("viz.jl")
 
 end

### 2021-05-28 src/graphs.jl

@@ -5,7 +5,7 @@ struct UnitdiskWidget{LT}
     radius::Float64
 end
 
-function edges(ud::UnitdiskWidget)
+function get_edges(ud::UnitdiskWidget)
 	edges = Tuple{Int,Int}[]
 	for (i, p) in enumerate(ud.nodes)
 		for (j,p2) in enumerate(ud.nodes)

### 2021-05-28 src/random_regular_graph.jl

@@ -1,0 +1,18 @@
+using LightGraphs
+export random_regular_eincode
+
+function random_regular_eincode(n, k)
+	g = LightGraphs.random_regular_graph(n, k)
+	ixs = [minmax(e.src,e.dst) for e in LightGraphs.edges(g)]
+	return EinCode((ixs..., [(i,) for i in LightGraphs.vertices(g)]...), ())
+end
+
+function solve_regular_graph(n::Int, k::Int; sc_target=20)
+    code = random_regular_eincode(n, k)
+    optcode = optimize_kahypar(code, uniformsize(code, 2); sc_target=sc_target, max_group_size=40)
+    mis_size = mis_solve(optcode)[].n |> Int
+
+	xs = (0:mis_size)
+	ys = [mis_polysolve(optcode, x)[] for x in xs]
+	fit(xs, ys, mis_size)
+end

### 2021-05-28 test/runtests.jl

@@ -1,6 +1,10 @@
 using NoteOnTropicalMIS
 using Test
 
-@testset "tensors.jl" begin
+@testset "tensors" begin
     include("tensors.jl")
+end
+
+@testset "independence polynomial" begin
+    include("independence_polynomial.jl")
 end

### 2021-06-01 paper/paper.tex
independence polynomial
update computing configurations

@@
-%\documentclass[a4paper,superscriptaddress,11pt]{quantumarticle}
 %\documentclass[aps,twocolumn,longbibliography,english,superscriptaddress]{revtex4-1}
@@
 \begin{abstract}
-	Solving the maximum independent set size problem: the maximum independent set size, the independence polynomial and the optimal configuration.
+	Solving the maximum independent set size problem by mapping the problem to an einsum network. 
+    We obtain the maximum independent set size,
+    the independence polynomial and the optimal configuration by using different tensor elements to a commutative semiring.
 \end{abstract}
@@
 where $a_k$ is the number of independent sets of order $k$ in $G$, and $\alpha(G)$ is the maximum independent set size of graph $G$.
-
 If we map a graph into an einsum network, as shown in \Fig{fig:einsummapping}, by putting a vertex tensor of size $2$ at each vertex
@@
 \end{equation}
-were $x$ is a variable, and a matrix of size $2 \times 2$ at each edge
+and a matrix of size $2 \times 2$ at each edge
 \begin{equation}
@@
 
-The contractionof this einsum network is exactly the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+Here $0$ and $1$ are the additive identity and multiplicative identity of a commutative semiring respectively.
+$x$ is a variable.
+The contraction of this einsum network is the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
@@
 \begin{split}
-    a_x\infty^x + a_y\infty^y &= \begin{cases}
+    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
         (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
@@
 \end{align}
-In the program, we only store the power $x$ and the corresponding factor $a_x$. This is exactly the tropical tensor network~\cite{Liu2021} used in solving spin glass ground states.
+In the program, we only store the power $x$ and the corresponding factor $a_x$ that initialized to $1$.
+This is exactly the tropical tensor network~\cite{Liu2021} used in solving spin glass ground states.
 Here if we are only interested in obtaining $\alpha(G)$, we can only consider the powers, which corresponds to the tropical algebra~\cite{Maclagan2015}.
+
+One may want to obtain all ground state configurations,
+it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$ initialized to a vertex dependent value $s_i = \{\delta_{ij=1,\ldots,n}$\}.
+The bit strings has a redefined algebra
+\begin{align}
+\begin{split}
+    s_x \oplus s_y &= s_x \cup s_y\\
+    s_x \odot s_y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}
+\end{split}
+\end{align}
+The $\vee$ is the bit-wise \texttt{or}.
 

### 2021-06-01 src/configurations.jl

@@ -1,0 +1,50 @@
+export mis_enumerate, ConfigEnumerator
+
+struct ConfigEnumerator{N}
+    data::Vector{BitVector}
+end
+
+Base.length(x::ConfigEnumerator{N}) where N = length(x.data)
+Base.:(==)(x::ConfigEnumerator, y::ConfigEnumerator) = x.data == y.data
+
+function Base.:+(x::ConfigEnumerator{N}, y::ConfigEnumerator{N}) where N
+    res = ConfigEnumerator{N}(vcat(x.data, y.data))
+    @show length(x), length(y), length(res)
+    @assert length(res) == length(x) + length(y)
+    return res
+end
+
+function Base.:*(x::ConfigEnumerator{L}, y::ConfigEnumerator{L}) where L
+    M, N = length(x), length(y)
+    z = Vector{BitVector}(undef, M*N)
+    for j=1:N, i=1:M
+        z[(j-1)*M+i] = x.data[i] .| y.data[j]
+    end
+    #@show M, N, length(z)
+    @assert length(z) == length(x) * length(y)
+    return ConfigEnumerator{L}(z)
+end
+
+Base.zero(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}(BitVector[])
+Base.one(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}([falses(N)])
+
+function onehot(::Type{ConfigEnumerator{N}}, i::Int) where N
+    res = one(ConfigEnumerator{N})
+    res.data[1][i] |= true
+    return res
+end
+
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
+    [one(T) one(T); one(T) zero(T)]
+end
+function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
+    [one(T), CountingTropical(one(T1), onehot(ConfigEnumerator{N}, vertex_index[ix[1]]))]
+end
+
+symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(ixs))
+symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne))
+function mis_enumerate(code)
+    vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(code))])
[…]

### 2021-06-01 src/tensors.jl

@@ -36,20 +36,20 @@ end
 
 _auto_mistensor(::Type{T}, ix::NTuple{2}) where T = misb(T)
 _auto_mistensor(::Type{T}, ix::NTuple{1}) where T = misv(T, 1, 1.0)
-function generate_xs!(::Type{T}, code::NestedEinsum, xs) where {T}
+function generate_xs!(f, ::Type{T}, code::NestedEinsum, xs) where {T}
     for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
 		if arg isa Integer
-			xs[arg] = _auto_mistensor(T, ix)
+			xs[arg] = f(T, ix)
 		else
-        	generate_xs!(T, arg, xs)
+        	generate_xs!(f, T, arg, xs)
 		end
     end
 	return xs
 end
 
-function generate_xs!(::Type{T}, code::EinCode, xs) where {T}
+function generate_xs!(f, ::Type{T}, code::EinCode, xs) where {T}
     for (i,ix) in enumerate(OMEinsum.getixs(code))
-		xs[i] = _auto_mistensor(T, ix)
+		xs[i] = f(T, ix)
     end
 	return xs
 end
@@ -62,11 +62,11 @@ end
 
 export mis_solve, mis_count
 function mis_contract(::Type{T}, code) where {T}
-	xs = generate_xs!(T, code, Vector{Any}(undef, ninput(code)))
+	xs = generate_xs!(_auto_mistensor, T, code, Vector{Any}(undef, ninput(code)))
 	code(xs...)
 end
 mis_solve(code) = mis_contract(TropicalF64, code)
-mis_count(code) = mis_contract(CountingTropical{Float64}, code)
+mis_count(code) = mis_contract(CountingTropical{Float64,Float64}, code)
 
 function is_diff_by_const(t1::AbstractArray{T}, t2::AbstractArray{T}) where T
 	x = NaN

### 2021-06-01 paper/paper.tex
update commutative semiring checking

@@
 \texttt{xungao@g.harvard.edu}\\
-%\AND
-%Sheng-Tao Wang\\
-%QuEra computing Inc.
+\AND
+Sheng-Tao Wang\\
+QuEra computing Inc.
 }
@@
 
-Here $0$ and $1$ are the additive identity and multiplicative identity of a commutative semiring respectively.
-$x$ is a variable.
+where $x$ is a variable.
 The contraction of this einsum network is the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
-    I(G, x) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i, s_j}.
+    I(G, x) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
 \end{equation}
 Here, the einsum enumerates all possible configurations and accumulates the product of tensor elements to the output.
-The product over edge tensors will provide a factor $0$ if the configuration is not an independent set, otherwise $1$.
-While the product over edges provide a factor $x^k$, where $k$ depends on how many times a vertex takes value $1$.
+The product over vertices tensors provides a factor $x^k$, where $k=\sum_k s_k$ is the set size.
+While the product over edge tensors provides a factor $0$ if the configuration is not an independent set, otherwise $1$.
 \begin{figure*}[t!]
@@
 With these algorithms, one can easily find a good contraction order that reduces the complexity to a quantity related to the minimum treewidth of the graph.~\cite{Markov2008}
-Such mapping makes it possible to utilize fater linear algebra functions.
+Such mapping also makes it possible to utilize faster BLAS functions.
+
+Before contracting the tensor network and evaluating this polynomial numerically, let us give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
+Instead, we treat them as the additive identity and multiplicative identity of a commutative semiring.
+A commutative semiring can be defined as: a ring without additive inverse is called a semiring, and commutative semiring is a semiring that multiplication commutative.
 
@@
 and insert them to the original tensor network contraction algorithm.
-However, this method suffers from a space overhead that propotional to the maximum independant set size.
+In the program, the multiplication can be evaluated efficiently with the convolution theorem.
+However, this method still suffers from a space overhead that propotional to the maximum independant set size.
 
@@
 \texttt{TropicalGEMM} for BLAS speed tropical matrix multiplication and
-\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar~\cite{Schlag2020} approach) ~\cite{Gray2021,Pan2021}.
+\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar~\cite{Schlag2020} approach) ~\cite{Kourtis2019,Gray2021,Pan2021}.
 

### 2021-06-01 src/NoteOnTropicalMIS.jl

@@ -3,6 +3,7 @@ module NoteOnTropicalMIS
 using TropicalGEMM, TropicalNumbers
 using OMEinsum
 
+include("arithematics.jl")
 include("tensors.jl")
 include("graphs.jl")
 include("independence_polynomial.jl")

### 2021-06-01 src/arithematics.jl

@@ -1,0 +1,16 @@
+export is_commutative_semiring
+
+function is_commutative_semiring(a::T, b::T, c::T) where T
+    # +
+    (a + b) + c == a + (b + c) &&
+    a + zero(T) == zero(T) + a == a &&
+    a + b == b + a &&
+    # *
+    (a * b) * c == a * (b * c) &&
+    a * one(T) == one(T) * a == a &&
+    a * b == b * a &&
+    # more
+    a * (b+c) == a*b + a*c &&
+    (a+b) * c == a*c + b*c &&
+    a * zero(T) == zero(T) * a == zero(T)
+end

### 2021-06-02 paper/paper.tex
update paper

@@
 \end{equation}
-where $a_k$ is the number of independent sets of order $k$ in $G$, and $\alpha(G)$ is the maximum independent set size of graph $G$.
-If we map a graph into an einsum network, as shown in \Fig{fig:einsummapping}, by putting a vertex tensor of size $2$ at each vertex
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
+\blue{here, I preassumed a user knows tensor network, add more details later.}
+If we map a graph into an einsum network, as shown in \Fig{fig:einsummapping}, by placing a rank one tensor of size $2$ at each vertex
 \begin{equation}
-    W(x) = \left(\begin{matrix}
+    W(x)_{s_i} = \left(\begin{matrix}
         1 \\
         x
-    \end{matrix}\right),
+    \end{matrix}\right)_{s_i},
 \end{equation}
-and a matrix of size $2 \times 2$ at each edge
+and a rank two tensor of size $2 \times 2$ at each edge
 \begin{equation}
-    B = \left(\begin{matrix}
+    B_{s_i s_j} = \left(\begin{matrix}
         1  & 1\\
         1 & 0
-    \end{matrix}\right).
+    \end{matrix}\right)_{s_is_j},
 \end{equation}
-
-where $x$ is a variable.
-The contraction of this einsum network is the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+the contraction of this einsum network is the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
@@
 Here, the einsum enumerates all possible configurations and accumulates the product of tensor elements to the output.
-The product over vertices tensors provides a factor $x^k$, where $k=\sum_k s_k$ is the set size.
+The product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the set size.
 While the product over edge tensors provides a factor $0$ if the configuration is not an independent set, otherwise $1$.
@@
 \end{figure*}
-The benefit of mapping the problem to einsum is, some existing algorithms can be used to decrease the complexity of the problem.
+By mapping the problem to einsum, one can use some existing algorithms to decrease the complexity of the problem.
 Especially those techiniques developed in recent quantum circuit simulations for finding the optimal exactly contraction order of a tensor network ~\cite{Gray2021,Pan2021}.
@@
 Such mapping also makes it possible to utilize faster BLAS functions.
-
-Before contracting the tensor network and evaluating this polynomial numerically, let us give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
+Before contracting the tensor network and evaluating this polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
 Instead, we treat them as the additive identity and multiplicative identity of a commutative semiring.
-A commutative semiring can be defined as: a ring without additive inverse is called a semiring, and commutative semiring is a semiring that multiplication commutative.
+A ring without additive inverse is called a semiring, and commutative semiring is a semiring that multiplication commutative.
+To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relation must hold for arbituary three elements $a, b, c \in R$.
+\begin{align*}
+(a \oplus b) \oplus c = a \oplus (b \oplus c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\oplus$ with identity $\mymathbb{0}$}\\
+a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
+a \oplus b = b \oplus a &\\
+&\\
+(a \odot b) \odot c = a \odot (b \odot c)  &   \hspace{5em}\text{$\triangleright$ commutative monoid $\odot$ with identity $\mymathbb{1}$}\\
+a \odot  \mymathbb{1} =  \mymathbb{1} \odot a = a &\\
+a \odot b = b \odot a &\\
+&\\
+a \odot (b\oplus c) = a\odot b + a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
+(a\oplus b) \odot c = a\odot c \oplus b\odot c &\\
+&\\
+a \odot \mymathbb{0} = \mymathbb{0} * a = \mymathbb{0}
+\end{align*}
 
@@
 One can store a polynomial of $x$ as a vector of factors.
-We define the algebra between the polynomial expansions of order $k$ as
+We define the algebra between the polynomial expansions $a$ of order $k_a$ and $b$ of order $k_b$ as
 \begin{align}
     \begin{split}
-    a \oplus b &= \{a_0 + b_0, a_1 + b_1, \ldots, a_k + b_k\},\\
-    a \odot b &= \{a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_k + b_k\},\\
+    a \oplus b &= \{a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}\},\\
+    a \odot b &= \{a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_{k_a} b_{k_b}\},\\
     \mymathbb{0} &= \{\},\\
@@
 
-\subsection{Polynomial fitting}
-Let $m$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
+\subsection{Polynomial fitting and Fourier transformation}
+Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
 We compute the einsum contraction for each $x \in X$ and obtain the following relations
@@
 The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
-
-\subsection{Fourier transformation}
+The polynomial fitting is esentially about solving the following linear equation
 \begin{align}
@@
 y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right)
+\end{matrix}\right).
 \end{align}
 
+However, the result is very unreliable in practise due to the non-negligible round off error of floating point numbers.
+Instead of choosing $X$ as a set of random real numbers, we let $x_i = r\omega^i$ and the above linear equation becomes
 \begin{align}
@@
 y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right)
+\end{matrix}\right).
 \end{align}
@@
 
-\section{Computing maximum independent set size and its degeneracy}
+\section{Computing maximum independent set size and its corresponding degeneracy and configurations}
 Obtaining the maximum independent set size and its degeneracy is much easier. Let $x=\infty$, then the independence polynomial becomes
@@
 One may want to obtain all ground state configurations,
-it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$ initialized to a vertex dependent value $s_i = \{\delta_{ij=1,\ldots,n}$\}.
+it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$ initialized to a vertex index $i$ dependent onehot vector $s_i = \{\boldsymbol{\delta}_{ij=1,\ldots,n}\}$.
 The bit strings has a redefined algebra
@@
     s_x \oplus s_y &= s_x \cup s_y\\
-    s_x \odot s_y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}
+    s_x \odot s_y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\\
+    \mymathbb{0} &= \{\}\\
+    \mymathbb{1} &= \{\boldsymbol 0\}
 \end{split}
 \end{align}
-The $\vee$ is the bit-wise \texttt{or}.
+The $\vee$ is the bit-wise \texttt{or}. One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
 
-\subsection{Utilizing sparsity}
+\section{Utilizing sparsity}
 So far, we have used the language of einsum networks for contraction.

### 2021-06-02 paper/paper.tex
get single configuration

@@
 \texttt{xungao@g.harvard.edu}\\
-\AND
-Sheng-Tao Wang\\
-QuEra computing Inc.
 }
@@
     a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-    \mymathbb{0} &= -\infty\\
-    \mymathbb{1} &= 0
+    \mymathbb{0} &= 0\infty^{-\infty}\\
+    \mymathbb{1} &= 1\infty^{0}
 \end{split}
@@
 it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$ initialized to a vertex index $i$ dependent onehot vector $s_i = \{\boldsymbol{\delta}_{ij=1,\ldots,n}\}$.
-The bit strings has a redefined algebra
+\iffalse
 \begin{align}
@@
 \end{align}
+\fi
+\begin{align}
+\begin{split}
+    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
+        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
+        s_y\infty^{\max(x,y)}, & x < y\\
+        s_x\infty^{\max(x,y)}, & x > y
+    \end{cases}\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y}\\
+    \mymathbb{0} &= \{\}\infty^{-\infty}\\
+    \mymathbb{1} &= \{\boldsymbol 0\}\infty^{0}
+\end{split}
+\end{align}
 The $\vee$ is the bit-wise \texttt{or}. One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
+By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save computational effort.
+We leave this as an exercise for readers.
 
@@
 
+\section{Indenpendence polynomials}
+\subsection{Common}
+\begin{lstlisting}
+using Polynomials
+
+_auto_mispolytensor(x::T, ix::NTuple{2}) where T = T[1 1; 1 0]
+_auto_mispolytensor(x::T, ix::NTuple{1}) where T = T[1, x]
+function generate_polyxs!(x::T, code::OMEinsum.NestedEinsum, xs=Vector{Any}(undef, ninput(code))) where {T}
+    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
+		if arg isa Integer
+			xs[arg] = _auto_mispolytensor(x, ix)
+		else
+        	generate_polyxs!(x, arg, xs)
+		end
+    end
+	return xs
+end
+
+function generate_polyxs!(x::T, code::EinCode, xs=Vector{Any}(undef, ninput(code))) where {T}
+    for (i,ix) in enumerate(OMEinsum.getixs(code))
+		xs[i] = _auto_mispolytensor(x, ix)
+    end
+	return xs
+end
+
+function mis_polysolve(code, x::T) where {T}
+	xs = generate_polyxs!(x, code, Vector{Any}(undef, NoteOnTropicalMIS.ninput(code)))
+	code(xs...)
+end
+\end{lstlisting}
+
+\subsection{Symbolic}
+\begin{lstlisting}
+function independence_polynomial(::Val{:polynomial}, code)
+    mis_polysolve(code, Polynomial([0, 1.0]))[]
+end
+\end{lstlisting}
+
+\subsection{Fitting and FFT}
+\begin{lstlisting}
+using FFTW
+function independence_polynomial(::Val{:fft}, code; mis_size=Int(mis_solve(code)[].n), r=1.0)
+	ω = exp(-2im*π/(mis_size+1))
+	xs = r .* collect(ω .^ (0:mis_size))
+	ys = [mis_polysolve(code, x)[] for x in xs]
+	Polynomial(real.(ifft(ys) ./ (r .^ (0:mis_size))))
+end
+
+function independence_polynomial(::Val{:fitting}, code; mis_size=Int(mis_solve(code)[].n))
+	xs = (0:mis_size)
+	ys = [mis_polysolve(code, x)[] for x in xs]
+	fit(xs, ys, mis_size)
+end
+\end{lstlisting}
+
+\subsection{Finite field algebra}
+\begin{lstlisting}
+using Mods, Primes
+
+# pirate
+Base.abs(x::Mod) = x
+Base.isless(x::Mod{N}, y::Mod{N}) where N = mod(x.val, N) < mod(y.val, N)
+
+function _independance_polynomial(::Type{T}, code, mis_size::Int) where T
+	xs = 0:mis_size
+	ys = [mis_polysolve(code, T(x))[] for x in xs]
+	A = zeros(T, mis_size+1, mis_size+1)
+	for j=1:mis_size+1, i=1:mis_size+1
+		A[j,i] = T(xs[j])^(i-1)
+	end
+	A \ T.(ys)
+end
+
+function independence_polynomial(::Val{:finitefield}, code; mis_size=Int(mis_solve(code)[].n), max_order=100)
+    N = typemax(Int)
+    YS = []
+    local res
+    for k = 1:max_order
+	    N = prevprime(N-1)
+        T = Mods.Mod{N,Int}
+        rk = _independance_polynomial(T, code, mis_size)
+        push!(YS, rk)
+        if max_order==1
+            return Polynomial(Mods.value.(YS[1]))
+        elseif k != 1
+            ra = improved_counting(YS[1:end-1])
+            res = improved_counting(YS)
+            ra == res && return Polynomial(res)
+        end
+    end
+    @warn "result is potentially inconsistent."
+    return Polynomial(res)
+end
+
+function improved_counting(sequences)
+    map(yi->Mods.CRT(yi...), zip(sequences...))
+end
+\end{lstlisting}
+
+\section{Enumerating configurations}
+\begin{lstlisting}
+using OMEinsum, TropicalNumbers
+
+struct ConfigEnumerator{N}
+    data::Vector{BitVector}
+end
+
+Base.length(x::ConfigEnumerator{N}) where N = length(x.data)
+Base.:(==)(x::ConfigEnumerator, y::ConfigEnumerator) = x.data == y.data
+
+function Base.:+(x::ConfigEnumerator{N}, y::ConfigEnumerator{N}) where N
+    res = ConfigEnumerator{N}(vcat(x.data, y.data))
+    @show length(x), length(y), length(res)
+    @assert length(res) == length(x) + length(y)
+    return res
+end
+
+function Base.:*(x::ConfigEnumerator{L}, y::ConfigEnumerator{L}) where L
+    M, N = length(x), length(y)
+    z = Vector{BitVector}(undef, M*N)
+    for j=1:N, i=1:M
+        z[(j-1)*M+i] = x.data[i] .| y.data[j]
+    end
+    #@show M, N, length(z)
+    @assert length(z) == length(x) * length(y)
+    return ConfigEnumerator{L}(z)
+end
+
+Base.zero(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}(BitVector[])
+Base.one(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}([falses(N)])
+
+function onehot(::Type{ConfigEnumerator{N}}, i::Int) where N
+    res = one(ConfigEnumerator{N})
+    res.data[1][i] |= true
+    return res
+end
+
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
+    [one(T) one(T); one(T) zero(T)]
+end
+function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
+    [one(T), CountingTropical(one(T1), onehot(ConfigEnumerator{N}, vertex_index[ix[1]]))]
+end
+
+symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(ixs))
+symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne))
+function mis_enumerate(code)
+    vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(code))])
+	xs = generate_xs!((T, ix)->enumerator_t(T, ix, vertex_index), CountingTropical{Float64,ConfigEnumerator{length(vertex_index)}}, code, Vector{Any}(undef, ninput(code)))
+	code(xs...)
+end
+\end{lstlisting}
 \end{document}

### 2021-06-02 src/configtropical.jl

@@ -1,0 +1,22 @@
+struct ConfigTropical{T,N}
+    n::T
+    config::BitVector
+end
+
+Base.:(==)(x::ConfigTropical{T,N}, y::ConfigTropical{T,N}) where {T,N} = x.n == y.n && x.config == y.config
+
+function Base.:+(x::ConfigTropical{T,N}, y::ConfigTropical{T,N}) where {T,N}
+    return x.n > y.n ? x : y
+end
+
+function Base.:*(x::ConfigTropical{T,L}, y::ConfigTropical{T,L}) where {T,L}
+    return ConfigTropical{T,L}(x.n+y.n, x.config .| y.config)
+end
+
+Base.zero(::Type{ConfigTropical{T, N}}) where {T,N} = ConfigTropical{T,N}(zero(Tropical{T}).n, trues(N))
+Base.one(::Type{ConfigTropical{T, N}}) where {T,N} = ConfigTropical{T,N}(one(Tropical{T}).n, falses(N))
+function onehot(::Type{ConfigTropical{T,N}}, i::Int) where {T,N}
+    c = falses(N)
+    c[i] |= true
+    return ConfigTropical{T,N}(one(T), c)
+end

### 2021-06-02 src/configurations.jl

@@ -1,4 +1,4 @@
-export mis_enumerate, ConfigEnumerator
+export mis_config, ConfigEnumerator, ConfigTropical
 
 struct ConfigEnumerator{N}
     data::Vector{BitVector}
@@ -9,8 +9,6 @@ Base.:(==)(x::ConfigEnumerator, y::ConfigEnumerator) = x.data == y.data
 
 function Base.:+(x::ConfigEnumerator{N}, y::ConfigEnumerator{N}) where N
     res = ConfigEnumerator{N}(vcat(x.data, y.data))
-    @show length(x), length(y), length(res)
-    @assert length(res) == length(x) + length(y)
     return res
 end
 
@@ -20,8 +18,6 @@ function Base.:*(x::ConfigEnumerator{L}, y::ConfigEnumerator{L}) where L
     for j=1:N, i=1:M
         z[(j-1)*M+i] = x.data[i] .| y.data[j]
     end
-    #@show M, N, length(z)
-    @assert length(z) == length(x) * length(y)
     return ConfigEnumerator{L}(z)
 end
 
@@ -34,17 +30,26 @@ function onehot(::Type{ConfigEnumerator{N}}, i::Int) where N
     return res
 end
 
-function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
+include("configtropical.jl")
+
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, T2, T<:CountingTropical{T1, T2}}
     [one(T) one(T); one(T) zero(T)]
 end
-function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
-    [one(T), CountingTropical(one(T1), onehot(ConfigEnumerator{N}, vertex_index[ix[1]]))]
+function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, T2, T<:CountingTropical{T1, T2}}
+    [one(T), CountingTropical(one(T1), onehot(T2, vertex_index[ix[1]]))]
+end
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, T2, T<:ConfigTropical{T1, T2}}
+    [one(T) one(T); one(T) zero(T)]
+end
[…]

### 2021-06-02 src/independence_polynomial.jl

@@ -1,47 +1,22 @@
 using Polynomials
-export mis_polysolve, independence_polynomial
-
-_auto_mispolytensor(x::T, ix::NTuple{2}) where T = T[1 1; 1 0]
-_auto_mispolytensor(x::T, ix::NTuple{1}) where T = T[1, x]
-function generate_polyxs!(x::T, code::OMEinsum.NestedEinsum, xs=Vector{Any}(undef, ninput(code))) where {T}
-    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
-		if arg isa Integer
-			xs[arg] = _auto_mispolytensor(x, ix)
-		else
-        	generate_polyxs!(x, arg, xs)
-		end
-    end
-	return xs
-end
-
-function generate_polyxs!(x::T, code::EinCode, xs=Vector{Any}(undef, ninput(code))) where {T}
-    for (i,ix) in enumerate(OMEinsum.getixs(code))
-		xs[i] = _auto_mispolytensor(x, ix)
-    end
-	return xs
-end
-
-function mis_polysolve(code, x::T) where {T}
-	xs = generate_polyxs!(x, code, Vector{Any}(undef, NoteOnTropicalMIS.ninput(code)))
-	code(xs...)
-end
+export independence_polynomial
 
 using FFTW
 function independence_polynomial(::Val{:fft}, code; mis_size=Int(mis_solve(code)[].n), r=1.0)
 	ω = exp(-2im*π/(mis_size+1))
 	xs = r .* collect(ω .^ (0:mis_size))
-	ys = [mis_polysolve(code, x)[] for x in xs]
+	ys = [mis_contract(x, code)[] for x in xs]
 	Polynomial(real.(ifft(ys) ./ (r .^ (0:mis_size))))
 end
 
 function independence_polynomial(::Val{:fitting}, code; mis_size=Int(mis_solve(code)[].n))
 	xs = (0:mis_size)
-	ys = [mis_polysolve(code, x)[] for x in xs]
+	ys = [mis_contract(x, code)[] for x in xs]
 	fit(xs, ys, mis_size)
 end
 
 function independence_polynomial(::Val{:polynomial}, code)
-    mis_polysolve(code, Polynomial([0, 1.0]))[]
+    mis_contract(Polynomial([0, 1.0]), code)[]
 end
 
 using Mods, Primes
[…]

### 2021-06-02 src/tensors.jl

@@ -10,7 +10,7 @@ end
 function misv(::Type{T}, n::Int, val) where T
 	res = zeros(T, fill(2, n)...)
 	res[1] = one(T)
-	res[end] = T(val)
+	res[end] = convert(T, val)
 	return res
 end
 
@@ -34,22 +34,22 @@ function cross(::Type{T}) where T
 	ein"((((a,c),b),d),bd,ac)->abcd"([misv(T, 1, 1.0) for i=1:4]..., misb(T), misb(T))
 end
 
-_auto_mistensor(::Type{T}, ix::NTuple{2}) where T = misb(T)
-_auto_mistensor(::Type{T}, ix::NTuple{1}) where T = misv(T, 1, 1.0)
-function generate_xs!(f, ::Type{T}, code::NestedEinsum, xs) where {T}
+_auto_mistensor(x::T, ix::NTuple{2}) where T = misb(T)
+_auto_mistensor(x::T, ix::NTuple{1}) where T = misv(T, 1, x)
+function generate_xs!(f, x::T, code::NestedEinsum, xs) where {T}
     for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
 		if arg isa Integer
-			xs[arg] = f(T, ix)
+			xs[arg] = f(x, ix)
 		else
-        	generate_xs!(f, T, arg, xs)
+        	generate_xs!(f, x, arg, xs)
 		end
     end
 	return xs
 end
 
-function generate_xs!(f, ::Type{T}, code::EinCode, xs) where {T}
+function generate_xs!(f, x::T, code::EinCode, xs) where {T}
     for (i,ix) in enumerate(OMEinsum.getixs(code))
-		xs[i] = f(T, ix)
+		xs[i] = f(x, ix)
     end
 	return xs
 end
@@ -61,12 +61,12 @@ function ninput(ne::NestedEinsum)
 end
 
 export mis_solve, mis_count
-function mis_contract(::Type{T}, code) where {T}
-	xs = generate_xs!(_auto_mistensor, T, code, Vector{Any}(undef, ninput(code)))
+function mis_contract(x::T, code) where {T}
+	xs = generate_xs!(_auto_mistensor, x, code, Vector{Any}(undef, ninput(code)))
 	code(xs...)
 end
-mis_solve(code) = mis_contract(TropicalF64, code)
-mis_count(code) = mis_contract(CountingTropical{Float64,Float64}, code)
[…]

### 2021-06-02 test/configurations.jl

@@ -1,10 +1,21 @@
 using NoteOnTropicalMIS, Test, LightGraphs
 
+@testset "ConfigTropical" begin
+    x = one(ConfigTropical{Float64, 5})
+    @test x.n == 0
+    @test x.config == falses(5)
+    x = zero(ConfigTropical{Float64, 5})
+    @test x.n == -Inf
+    @test x.config == trues(5)
+end
+
 @testset "enumerating" begin
     @test NoteOnTropicalMIS.onehot(ConfigEnumerator{10}, 3) == ConfigEnumerator{10}(BitVector[[0, 0, 1, 0, 0, 0, 0, 0, 0, 0]])
     code = random_regular_eincode(10, 3)
     res1 = mis_count(code)[]
-    res2 = mis_enumerate(code)[]
-    @test res1.n == res2.n
+    res2 = mis_config(code; all=true)[]
+    res3 = mis_config(code; all=false)[]
+    @test res1.n == res2.n == res3.n
     @test res1.c == length(res2.c)
+    @test res3.config ∈ res2.c.data
 end

### 2021-06-02 paper/paper.tex
update config getter

@@
 \end{equation}
-the contraction of this einsum network is the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+the contraction of this einsum network generates the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
@@
 
-\section{Enumerating configurations}
+\section{Maximum independent set}
+\subsection{Tropical numbers}
+\begin{lstlisting}
+function independence_polynomial(::Val{:polynomial}, code)
+    mis_polysolve(code, Polynomial([0, 1.0]))[]
+end
+\end{lstlisting}
+
+\subsection{Enumerating configurations}
 \begin{lstlisting}

### 2021-06-02 test/independence_polynomial.jl

@@ -14,11 +14,14 @@ using Mods, Polynomials, TropicalNumbers
 end
 
 @testset "arithematics" begin
-    for (a, b, c) in [(Mod{17}(2), Mod{17}(8), Mod{17}(9)),
+    for (a, b, c) in [
+                    (TropicalF64(2), TropicalF64(8), TropicalF64(9)),
+                    (CountingTropicalF64(2, 8), CountingTropicalF64(8, 9), CountingTropicalF64(9, 2)),
+                    (Mod{17}(2), Mod{17}(8), Mod{17}(9)),
                     (Polynomial([0,1,2,3.0]), Polynomial([3,2.0]), Polynomial([1,7.0])),
                     (TropicalF64(5), TropicalF64(3), TropicalF64(-9)),
                     (CountingTropicalF64(5, 3), CountingTropicalF64(3, 9), CountingTropicalF64(-3, 2)),
-                    (ConfigTropical{Float64,10}(5.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10}(3.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10}(-3.0, BitVector(rand(Bool, 10)))),
+                    (ConfigTropical{Float64,10,1}(5.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10,1}(3.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10,1}(-3.0, BitVector(rand(Bool, 10)))),
                     (CountingTropical(5.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:3])), CountingTropical(3.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:4])), CountingTropical(-3.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:5]))),
                     ]
         @test is_commutative_semiring(a, b, c)

### 2021-06-02 paper/paper.tex
update code

@@
 
-\section{Computing independence polynomial}
+\section{Three approaches to computing independence polynomial}
 The independence polynomial~\cite{Ferrin2014, Harvey2017} of a graph $G$ is defined as
@@
 \subsection{Symbolic computing}
-To evaluate this polynomial, one can use the symbolic computing directly.
-One can store a polynomial of $x$ as a vector of factors.
-We define the algebra between the polynomial expansions $a$ of order $k_a$ and $b$ of order $k_b$ as
+To evaluate this polynomial, one can use the symbolic computing directly, that is, storing a polynomial of $x$ as a vector of factors.
+We define the algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ as
 \begin{align}
@@
     \mymathbb{0} &= \{\},\\
-    \mymathbb{1} &= \{1\},
+    \mymathbb{1} &= \{1\}.
     \end{split}
 \end{align}
-and insert them to the original tensor network contraction algorithm.
+The variable $x$ now is represented as a vector $\{0, 1\}$.
+Then we insert them to the original tensor network contraction algorithm, the final result is the exact representation of the independence polynomial.
 In the program, the multiplication can be evaluated efficiently with the convolution theorem.
-However, this method still suffers from a space overhead that propotional to the maximum independant set size.
+However, this method suffers from a space overhead that propotional to the maximum independant set size because each polynomial requires a vector of such size to store.
 
@@
 \section{Computing maximum independent set size and its corresponding degeneracy and configurations}
-Obtaining the maximum independent set size and its degeneracy is much easier. Let $x=\infty$, then the independence polynomial becomes
+Obtaining the maximum independent set size and its degeneracy is computational more efficient. Let $x=\infty$, then the independence polynomial becomes
 \begin{equation}
@@
 In the program, we only store the power $x$ and the corresponding factor $a_x$ that initialized to $1$.
-This is exactly the tropical tensor network~\cite{Liu2021} used in solving spin glass ground states.
-Here if we are only interested in obtaining $\alpha(G)$, we can only consider the powers, which corresponds to the tropical algebra~\cite{Maclagan2015}.
+This algebra is consistent with the one we derived in ~\cite{Liu2021} that uses the tropical tensor network solving spin glass ground states.
+Here if we are only interested in obtaining $\alpha(G)$ and omit the factors, the algebra of $x$ corresponds to the tropical algebra~\cite{Maclagan2015,Moore2011}.
 

### 2021-06-02 paper/paper.tex
update example

@@
 \subsection{Enumerating configurations}
+
+The following is a complete example.
+
 \begin{lstlisting}
 using OMEinsum, TropicalNumbers
+using OMEinsum: NestedEinsum
 
-struct ConfigEnumerator{N}
-    data::Vector{BitVector}
+struct ConfigEnumerator{N,C}
+    data::Vector{StaticBitVector{N,C}}
 end
@@
 Base.length(x::ConfigEnumerator{N}) where N = length(x.data)
-Base.:(==)(x::ConfigEnumerator, y::ConfigEnumerator) = x.data == y.data
+Base.:(==)(x::ConfigEnumerator{N,C}, y::ConfigEnumerator{N,C}) where {N,C} = x.data == y.data
 
-function Base.:+(x::ConfigEnumerator{N}, y::ConfigEnumerator{N}) where N
-    res = ConfigEnumerator{N}(vcat(x.data, y.data))
-    @show length(x), length(y), length(res)
-    @assert length(res) == length(x) + length(y)
+function Base.:+(x::ConfigEnumerator{N,C}, y::ConfigEnumerator{N,C}) where {N,C}
+    res = ConfigEnumerator{N,C}(vcat(x.data, y.data))
     return res
@@
 
-function Base.:*(x::ConfigEnumerator{L}, y::ConfigEnumerator{L}) where L
+function Base.:*(x::ConfigEnumerator{L,C}, y::ConfigEnumerator{L,C}) where {L,C}
     M, N = length(x), length(y)
-    z = Vector{BitVector}(undef, M*N)
+    z = Vector{StaticBitVector{L,C}}(undef, M*N)
     for j=1:N, i=1:M
@@
     end
-    #@show M, N, length(z)
-    @assert length(z) == length(x) * length(y)
-    return ConfigEnumerator{L}(z)
+    return ConfigEnumerator{L,C}(z)
 end
 
-Base.zero(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}(BitVector[])
-Base.one(::Type{ConfigEnumerator{N}}) where N = ConfigEnumerator{N}([falses(N)])
+Base.zero(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}(StaticBitVector{N,C}[])
+Base.one(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}([TropicalNumbers.staticfalses(StaticBitVector{N,C})])
 
-function onehot(::Type{ConfigEnumerator{N}}, i::Int) where N
-    res = one(ConfigEnumerator{N})
-    res.data[1][i] |= true
-    return res
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, C, T<:CountingTropical{T1,ConfigEnumerator{N,C}}}
+    [one(T) one(T); one(T) zero(T)]
+end
+function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, C, T<:CountingTropical{T1,ConfigEnumerator{N,C}}}
+    [one(T), CountingTropical(one(T1), ConfigEnumerator([TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]])]))]
+end
+function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1,N,C, T<:ConfigTropical{T1,N,C}}
+    [one(T) one(T); one(T) zero(T)]
+end
+function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1,N,C, T<:ConfigTropical{T1,N,C}}
+    [one(T), T(one(T1), TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]]))]
 end
 
-function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
-    [one(T) one(T); one(T) zero(T)]
+function generate_xs!(f, x::T, code::NestedEinsum, xs) where {T}
+    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
+		if arg isa Integer
+			xs[arg] = f(x, ix)
+		else
+        	generate_xs!(f, x, arg, xs)
 		end
-function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, T<:CountingTropical{T1, ConfigEnumerator{N}}}
-    [one(T), CountingTropical(one(T1), onehot(ConfigEnumerator{N}, vertex_index[ix[1]]))]
+    end
+	return xs
+end
+
+function generate_xs!(f, x::T, code::EinCode, xs) where {T}
+    for (i,ix) in enumerate(OMEinsum.getixs(code))
+		xs[i] = f(x, ix)
+    end
+	return xs
 end
@@
 symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne))
-function mis_enumerate(code)
+ninput(::EinCode{ixs}) where ixs = length(ixs)
+ninput(ne::NestedEinsum) = ninput(Iterators.flatten(ne))
+function mis_config(code; all=false)
     vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(code))])
-	xs = generate_xs!((T, ix)->enumerator_t(T, ix, vertex_index), CountingTropical{Float64,ConfigEnumerator{length(vertex_index)}}, code, Vector{Any}(undef, ninput(code)))
+    N = length(vertex_index)
+    C = TropicalNumbers._nints(N)
+    T = all ? CountingTropical{Float64, ConfigEnumerator{N,C}} : ConfigTropical{Float64, N, C}
+	xs = generate_xs!((T, ix)->enumerator_t(T, ix, vertex_index), T, code, Vector{Any}(undef, ninput(code)))
 	code(xs...)
 end
+
+mis_config(optimize_greedy(ein"i,j,k,l,ij,jk,kl,li->", Dict('i'=>2, 'j'=>2, 'k'=>2, 'l'=>2)); all=true)  # square
 \end{lstlisting}
+
+You will see the following output
+
+\begin{lstlisting}
+0-dimensional Array{CountingTropical{Float64, ConfigEnumerator{4, 1}}, 0}:
+(2.0, ConfigEnumerator{4, 1}(StaticBitVector{4, 1}[1010, 0101]))ₜ
+\end{lstlisting}
+
 \end{document}

### 2021-06-02 src/configurations.jl

@@ -38,7 +38,9 @@ function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1,N,C, T<:
 end
 
 symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(ixs))
-symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne))
+symbols(ne::OMEinsum.NestedEinsum) = symbols(Iterators.flatten(ne))
+ninput(::EinCode{ixs}) where ixs = length(ixs)
+ninput(ne::OMEinsum.NestedEinsum) = ninput(Iterators.flatten(ne))
 function mis_config(code; all=false)
     vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(code))])
     N = length(vertex_index)

### 2021-06-02 src/tensors.jl

@@ -54,12 +54,6 @@ function generate_xs!(f, x::T, code::EinCode, xs) where {T}
 	return xs
 end
 
-ninput(::EinCode{ixs}) where ixs = length(ixs)
-ninput(ne::Int) = 1
-function ninput(ne::NestedEinsum)
-    mapreduce(ninput, +, ne.args, init=0)
-end
-
 export mis_solve, mis_count
 function mis_contract(x::T, code) where {T}
 	xs = generate_xs!(_auto_mistensor, x, code, Vector{Any}(undef, ninput(code)))

### 2021-06-03 notebooks/regular-generic.jl
fix all configurations

@@ -1,0 +1,135 @@
+### A Pluto.jl notebook ###
+# v0.14.7
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
+        el
+    end
+end
+
+# ╔═╡ 4e4610ca-99e9-43e5-906b-c4f86e17ecd4
+begin
+	using Revise
+	using NoteOnTropicalMIS
+	using NoteOnTropicalMIS.OMEinsum, NoteOnTropicalMIS.TropicalNumbers, NoteOnTropicalMIS.Polynomials
+	using OMEinsumContractionOrders, PlutoUI
+end
+
+# ╔═╡ 18124cde-bdf0-11eb-382a-a727d1fbe17a
+md"# Tensor network playground
+-- Random Regular graphs"
+
+# ╔═╡ 7be402c5-bc70-49d9-aeb2-2cc4783660cd
+md"## Generate a random-regular graph"
+
+# ╔═╡ d704acbf-12c0-4468-b122-3f25406e2e5a
+n = 80;
+
+# ╔═╡ 5527cdcb-dc41-4237-aeb0-f38b1e218729
+k = 3;
+
+# ╔═╡ aa4fec11-2e61-4dd1-9484-3aca470f07bf
+code = random_regular_eincode(n, k);
+
+# ╔═╡ c7e48886-3cc4-44cf-a9dd-0fa54f05c860
+md"""
+contraction order optimizer $(@bind order_optimizer Select(["Greedy", "KaHyPar"]))
+"""
+
+# ╔═╡ 4480b2b7-4676-4980-a0a9-13831e223e27
+let
+	if order_optimizer == "Greedy"
+		@doc optimize_greedy
+	else
+		md"""
+$(@doc optimize_kahypar)
+target space complexity = $(@bind sc_target NumberField(2:32; default=20))
+"""
+	end
+end
+
+# ╔═╡ db4fdd62-7fc9-4427-b072-2b992f59e3fd
+optimized_code = if order_optimizer == "Greedy"
+	optimize_greedy(code, Dict([i=>2 for i=1:n]))
[…]

### 2021-06-03 notebooks/tutorial-basic.jl

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.14.6
+# v0.14.7
 
 using Markdown
 using InteractiveUtils
@@ -9,9 +9,6 @@ using OMEinsum, LightGraphs, TropicalNumbers
 
 # ╔═╡ f67a7abb-d96c-4167-962f-b9afa23300cd
 using Polynomials
-
-# ╔═╡ 20fbd4af-50a3-45b1-b519-e9e7c4b5740f
-using SymEngine
 
 # ╔═╡ 0fd7b695-fd29-4570-b33f-a9261565b06b
 using ForwardDiff
@@ -84,19 +81,19 @@ md"Here, the size of each bond is 2."
 md"## Generate tensors and do the contraction"
 
 # ╔═╡ 092cb056-2c0e-40af-ba1b-8879460c6dd1
-function mis_contract(code::OMEinsum.NestedEinsum, x::T) where T
+function mis_contract(f, ::Type{T}, code::OMEinsum.NestedEinsum) where T
    	tensors = map(OMEinsum.getixs(Iterators.flatten(code))) do ix
 	   	@assert length(ix) == 1 || length(ix) == 2
-		length(ix) == 1 ? [one(T), x] : [one(T) one(T); one(T) zero(T)]
+		length(ix) == 1 ? [one(T), convert(T, f(ix[1]))] : [one(T) one(T); one(T) zero(T)]
    	end
    	code(tensors...)
 end
 
 # ╔═╡ 42628cd3-5a34-46c6-a1a2-325463fafe45
-mis_size = mis_contract(optimized_code, Tropical(1.0))
+mis_size = mis_contract(ix->TropicalF64(1.0), TropicalF64, optimized_code)
 
 # ╔═╡ 4fe151d5-cc5a-4447-9ae6-bb6a1fbbddf8
-mis_size_with_degeneracy = mis_contract(optimized_code, CountingTropical(1.0))
+mis_size_with_degeneracy = mis_contract(ix->CountingTropicalF64(1.0), CountingTropicalF64, optimized_code)
 
 # ╔═╡ 112f8104-88b2-4968-8c7a-2d96ef6a52b8
 md"For independence polynomial"
[…]

### 2021-06-03 notebooks/unit-disk-tropical.jl

@@ -1,0 +1,138 @@
+### A Pluto.jl notebook ###
+# v0.14.7
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
+        el
+    end
+end
+
+# ╔═╡ 4e4610ca-99e9-43e5-906b-c4f86e17ecd4
+using OMEinsum, Viznet, TropicalNumbers, OMEinsumContractionOrders, Compose, PlutoUI
+
+# ╔═╡ 18124cde-bdf0-11eb-382a-a727d1fbe17a
+md"# Tensor network playground"
+
+# ╔═╡ 7be402c5-bc70-49d9-aeb2-2cc4783660cd
+md"## Generate a unit-disk graph"
+
+# ╔═╡ d704acbf-12c0-4468-b122-3f25406e2e5a
+n = 20;
+
+# ╔═╡ 5527cdcb-dc41-4237-aeb0-f38b1e218729
+unit_distance = 0.4;
+
+# ╔═╡ 883443b5-8e7f-49e9-8234-6854f0609c8b
+locations = [(rand(), rand()) for _ = 1:n];
+
+# ╔═╡ 6d22f9be-a17d-47f5-8dc8-9a3b75368ed9
+let
+	xlocs = getindex.(locations, 1)
+	ylocs = getindex.(locations, 2)
+	xmin, ymin = minimum(xlocs), minimum(ylocs)
+	Δx = maximum(xlocs) - xmin
+	Δy = maximum(ylocs) - ymin
+	Δ = max(Δx, Δy) / 0.8
+	xlocs .-= xmin
+	ylocs .-= ymin
+	xlocs .= xlocs ./ Δ .+ 0.1
+	ylocs .= ylocs ./ Δ .+ 0.1
+	u = 0.2/Δ
+	lattice = UnitDisk([zip(xlocs, ylocs)...], unit_distance/Δ)
+	Compose.set_default_graphic_size(8cm, 8cm)
+	viz(lattice; line_style=bondstyle(:default, stroke("black"), linewidth(2*u*mm)),
[…]

### 2021-06-06 paper/paper.tex
fix all configurations
new masked configure finder

@@
     We obtain the maximum independent set size,
-    the independence polynomial and the optimal configuration by using different tensor elements to a commutative semiring.
+    the independence polynomial and the optimal configuration by generic programming tensor networks.
 \end{abstract}
 
-\section{Three approaches to computing independence polynomial}
+\section{Three approaches to compute independence polynomial}
 The independence polynomial~\cite{Ferrin2014, Harvey2017} of a graph $G$ is defined as
@@
 \end{equation}
-the contraction of this einsum network generates the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+the contraction of this einsum network gives the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
@@
 
-However, the result is very unreliable in practise due to the non-negligible round off error of floating point numbers.
+However, the result is very unreliable in practise due to the non-negligible round off error of floating point operations.
 Instead of choosing $X$ as a set of random real numbers, we let $x_i = r\omega^i$ and the above linear equation becomes
@@
 This algebra is consistent with the one we derived in ~\cite{Liu2021} that uses the tropical tensor network solving spin glass ground states.
-Here if we are only interested in obtaining $\alpha(G)$ and omit the factors, the algebra of $x$ corresponds to the tropical algebra~\cite{Maclagan2015,Moore2011}.
+Here if we are only interested in obtaining $\alpha(G)$ and omit the factors, the algebra of $x$ corresponds to the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
 
@@
 We leave this as an exercise for readers.
+
+\subsection{bounding the enumeration space}
+If one tries to implement the above algebra for enumerating configurations, he will find the space overhead is not propotional to the degeneracy of the optimal configuration.
+It stores more than nessesary intermedite configurations. To speed up calculation, we use the result of much faster tropical number for bounding.
+We first compute the optimal maximum independent set size $\alpha(G)$ with tropical numbers and cache all intermediate tensors in the contraction route.
+Then we use boolean masks to mark relevent items for each cached tensor, i.e. using a boolean true to mark a tensor element with nonzero gradients and boolean false otherwise.
+Finally, we perform masked matrix multiplication using the new element type with the above algebra for obtaining all configurations.
+To compute the masks, we ``back propagate'' the masks through contraction route.
+Consider a tropical matrix multiplication $C = A B$, we have the following inequality
+\begin{align}
+    A_{ij} \odot B_{jk} &\leq C_{ik}
+\end{align}
+
+Using the tropical algebra, we have
+\begin{align}
+    A_{ij} &\leq (\max_{k} (C_{ik}^{-1} \odot B_{jk}))^{-1}
+\end{align}
+where the tropical multiplicative inverse is defined as the additive inverse of the regular algebra. The equality holds if and only if $A_{ij}$ can contribute to $C$ (i.e. has nonzero gradient).
+Let the mask for $C$ being $\overline C$, the backward rule for the mask reads
+\begin{align}
+\overline{A}_{ij} = \delta(A_{ij}, ((C^{\circ-1} \circ \overline C )B^T)_{ij}^{\circ -1}),
+\end{align}
+where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard multiplication, boolean false is treated as tropical zero and boolean true is treated as tropical one.
+This backward rule utilizes the properties that tropical algebra has multiplicative inverse for a nonzero element, while the ordering is well defined too.
+This rule defined on matrix multiplication can be easily generalized to the einsum by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum.
 

### 2021-06-06 project/randomregular.jl

@@ -1,0 +1,33 @@
+using DelimitedFiles, NoteOnTropicalMIS
+using NoteOnTropicalMIS.OMEinsumContractionOrders
+using NoteOnTropicalMIS.OMEinsum
+
+function mis_configurations(n, seed; writefile=false)
+    folder = joinpath("project", "data")
+    mask = Matrix{Bool}(readdlm(fname))
+    rawcode = diagonal_coupled_eincode(mask)
+    code = optimize_kahypar(rawcode, uniformsize(rawcode, 2); sc_target=17, max_group_size=40)
+    if task == :counting
+        nc = mis_count(code)[]
+        println("n = $n, MIS size = $(nc.n), degeneracy = $(nc.c)")
+    elseif task == :config
+    elseif task == :allconfigs
+        res = mis_config(code; all=true)[]
+        @assert res.n == nc.n
+        config = res.c
+        @assert length(config) == nc.c
+
+        ofname = joinpath(folder, "configurations_$(n)x$(n)_5.3x5.3_$seed.dat")
+        writefile && write(ofname, Matrix(config))
+        return nc.n, config
+    end
+end
+
+if true
+    #for n in [7, 10], seed in 1:6
+    #    mis_configurations(n, seed; writefile=true)
+    #end
+    for n in [13, 15], seed in [1, 2, 3, "Easy_1", "Medium_1", "Hard_1"]
+        mis_configurations(n, seed, writefile=true)
+    end
+end

### 2021-06-06 src/ad.jl

@@ -3,11 +3,29 @@ using TupleTools
 export bounding_contract
 
 Base.isnan(x::Tropical) = isnan(x.n)
-function backward_tropical(@nospecialize(ixs), @nospecialize(xs), @nospecialize(iy), @nospecialize(y), @nospecialize(ymask), i, size_dict)
+function backward_tropical(mode, @nospecialize(ixs), @nospecialize(xs), @nospecialize(iy), @nospecialize(y), @nospecialize(ymask), i, size_dict)
     nixs = TupleTools.insertat(ixs, i, (iy,))
     nxs  = TupleTools.insertat( xs, i, (OMEinsum.asarray(inv.(y) .* ymask),))
     niy = ixs[i]
-    return inv.(einsum(EinCode(nixs, niy), nxs, size_dict)) .== xs[i]
+    A = inv.(einsum(EinCode(nixs, niy), nxs, size_dict))
+    if mode == :all
+        return A .== xs[i]
+    elseif mode == :single  # wrong, need `B` matching `A`.
+        mask = falses(size(A)...)
+        found = false
+        for j=1:length(A)
+            if xs[i][j] == A[j] && !found
+                #@show j, A, xs[i]
+                mask[j] = true
+                found = true
+            else
+                xs[i][j] = zero(eltype(xs[i]))
+            end
+        end
+        return mask
+    else
+        error("unkown mode: $mod")
+    end
 end
 
 struct CacheTree{T}
@@ -24,14 +42,14 @@ function cached_einsum(code::NestedEinsum, @nospecialize(xs), size_dict)
     CacheTree(y, caches)
 end
 
-function generate_masktree(code::Int, cache, mask, size_dict)
+function generate_masktree(code::Int, cache, mask, size_dict, mode=:all)
     CacheTree(mask, CacheTree{Bool}[])
 end
-function generate_masktree(code::NestedEinsum, cache, mask, size_dict)
+function generate_masktree(code::NestedEinsum, cache, mask, size_dict, mode=:all)
     submasks = map(1:length(code.args)) do i
-        backward_tropical(OMEinsum.getixs(code.eins), (getfield.(cache.siblings, :content)...,), OMEinsum.getiy(code.eins), cache.content, mask, i, size_dict)
+        backward_tropical(mode, OMEinsum.getixs(code.eins), (getfield.(cache.siblings, :content)...,), OMEinsum.getiy(code.eins), cache.content, mask, i, size_dict)
     end
[…]

### 2021-06-06 src/tensors.jl

@@ -37,14 +37,7 @@ end
 _auto_mistensor(x::T, ix::NTuple{2}) where T = misb(T)
 _auto_mistensor(x::T, ix::NTuple{1}) where T = misv(T, 1, x)
 function generate_xs!(f, x::T, code::NestedEinsum, xs) where {T}
-    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
-		if arg isa Integer
-			xs[arg] = f(x, ix)
-		else
-        	generate_xs!(f, x, arg, xs)
-		end
-    end
-	return xs
+    generate_xs!(f, x, Iterators.flatten(code), xs)
 end
 
 function generate_xs!(f, x::T, code::EinCode, xs) where {T}

### 2021-06-06 test/configurations.jl

@@ -15,10 +15,15 @@ end
     optcode = OMEinsum.optimize_greedy(rawcode, uniformsize(rawcode, 2))
     for code in [rawcode, optcode]
         res1 = mis_count(code)[]
-        res2 = mis_config(code; all=true)[]
-        res3 = mis_config(code; all=false)[]
-        @test res1.n == res2.n == res3.n
-        @test res1.c == length(res2.c)
+        res2 = mis_config(code; all=true, usemask=true)[]
+        res3 = mis_config(code; all=false, usemask=false)[]
+        res4 = mis_config(code; all=true, usemask=false)[]
+        @test res1.n == res2.n == res3.n == res4.n
+        @test res1.c == length(res2.c) == length(res4.c)
         @test res3.config ∈ res2.c.data
+        @test res3.config ∈ res4.c.data
+        res5 = mis_config(code; all=false, usemask=true)[]
+        @test res5.n == res1.n
+        @test res5.config ∈ res2.c.data
     end
 end

### 2021-06-11 paper/paper.tex
update

--- 2021-06-02 paper/paper.tex
@@
 \begin{document}
-\title{Solving the maximum independant set problem with einsum networks}
+\title{Solving the maximum independant set problem by generic programming einsum networks}
 
@@
 \begin{abstract}
-	Solving the maximum independent set size problem by mapping the problem to an einsum network. 
-    We obtain the maximum independent set size,
-    the independence polynomial and the optimal configuration by using different tensor elements to a commutative semiring.
+	Solving the maximum independent set size problem by mapping the graph to an einsum network. 
+    By contracting the einsum network with generic element types, we show how to obtain the maximum independent set size,
+    the independence polynomial and optimal configurations.
 \end{abstract}
 
-\section{Three approaches to computing independence polynomial}
+\section{Independence polynomial}
 The independence polynomial~\cite{Ferrin2014, Harvey2017} of a graph $G$ is defined as
@@
 \blue{here, I preassumed a user knows tensor network, add more details later.}
-If we map a graph into an einsum network, as shown in \Fig{fig:einsummapping}, by placing a rank one tensor of size $2$ at each vertex
+Let us map the graph $G$ into an einsum network, as shown in \Fig{fig:einsummapping}, by placing a rank one tensor of size $2$ on vertex $i$
 \begin{equation}
@@
 \end{equation}
-and a rank two tensor of size $2 \times 2$ at each edge
+and a rank two tensor of size $2 \times 2$ on edge $(i,j)$
 \begin{equation}
@@
 \end{equation}
-the contraction of this einsum network generates the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise.
+The contraction of this einsum network gives the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
 \begin{equation}
@@
 \end{equation}
-Here, the einsum enumerates all possible configurations and accumulates the product of tensor elements to the output.
-The product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the set size.
-While the product over edge tensors provides a factor $0$ if the configuration is not an independent set, otherwise $1$.
+Here, the einsum runs over all possible vertex configurations and accumulates the product of tensor elements to the output.
+The product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
+while the product over edge tensors provides a factor $0$ for configurations not being an independent set.
 \begin{figure*}[t!]
@@
 \end{figure*}
-By mapping the problem to einsum, one can use some existing algorithms to decrease the complexity of the problem.
-Especially those techiniques developed in recent quantum circuit simulations for finding the optimal exactly contraction order of a tensor network ~\cite{Gray2021,Pan2021}.
-With these algorithms, one can easily find a good contraction order that reduces the complexity to a quantity related to the minimum treewidth of the graph.~\cite{Markov2008}
-Such mapping also makes it possible to utilize faster BLAS functions.
-Before contracting the tensor network and evaluating this polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
+With this einsum network representation, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
+A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of $G$.~\cite{Markov2008}
+The pairwise tensor contraction also makes it possible to utilize fast basic linear algebra subprograms (BLAS) functions for certain tensor element types.
+
+Before contracting the einsum network and evaluating the independence polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
 Instead, we treat them as the additive identity and multiplicative identity of a commutative semiring.
-A ring without additive inverse is called a semiring, and commutative semiring is a semiring that multiplication commutative.
+A semiring is a ring without additive inverse, while a commutative semiring is a semiring that multiplication commutative.
 To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relation must hold for arbituary three elements $a, b, c \in R$.
@@
 
-\subsection{Symbolic computing}
-To evaluate this polynomial, one can use the symbolic computing directly, that is, storing a polynomial of $x$ as a vector of factors.
+In the rest of this paper, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
+i.e. making the einsum network programming generic~\cite{Stepanov2014}.
+
+\subsection{The polynomial approach}
+A straight forward approach to evaluate the independence polynomial is treating the tensor elements as polynomials, and evaluate the polynomial directly.
+Let us create a polynomial type, and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a vector $(a_0, a_1, \ldots, a_k) \in R^k$, e.g. $x$ is represented as $(0, 1)$.
 We define the algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ as
@@
     \begin{split}
-    a \oplus b &= \{a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}\},\\
-    a \odot b &= \{a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_{k_a} b_{k_b}\},\\
-    \mymathbb{0} &= \{\},\\
-    \mymathbb{1} &= \{1\}.
+    a \oplus b &= (a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
+    a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_{k_a} b_{k_b}),\\
+    \mymathbb{0} &= (),\\
+    \mymathbb{1} &= (1).
     \end{split}
 \end{align}
-The variable $x$ now is represented as a vector $\{0, 1\}$.
-Then we insert them to the original tensor network contraction algorithm, the final result is the exact representation of the independence polynomial.
+By contracting the einsum network with polynomial type, the final result is the exact representation of the independence polynomial.
 In the program, the multiplication can be evaluated efficiently with the convolution theorem.
-However, this method suffers from a space overhead that propotional to the maximum independant set size because each polynomial requires a vector of such size to store.
+The only problem of this method is it suffers from a space overhead that propotional to the maximum independant set size because each polynomial requires a vector of such size to store the factors.
+In the following subsections, we managed to solve this problem.
 
-\subsection{Polynomial fitting and Fourier transformation}
+\subsection{The fitting and Fourier transformation approaches}
 Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
-We compute the einsum contraction for each $x \in X$ and obtain the following relations
+We compute the einsum contraction for each $x_i \in X$ and obtain the following relations
 \begin{align}
@@
 
-However, the result is very unreliable in practise due to the non-negligible round off error of floating point numbers.
-Instead of choosing $X$ as a set of random real numbers, we let $x_i = r\omega^i$ and the above linear equation becomes
+In practise, the fitting can suffer from the non-negligible round off errors of floating point operations and produce unreliable results.
+This is because the factors of independence polynomial can be different in magnitude by many orders.
+Instead of choosing $X$ as a set of random real numbers, we make it form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/(m+1)}$.
+The above linear equation becomes
 \begin{align}
@@
 
-When $r=1$, the left side is a DFT matrix. We can obtain the factors using the relation $\vec a = {\rm FFT^{-1}}(\omega) \cdot \vec y$.
-In the special case that $\omega = e^{-2\pi i/(m+1)}$, it is directly solvable with inverse fast fourier transformation algorithm in package \texttt{FFTW}.
+Let us rearange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a descrete fourier transformation (DFT) matrix.
+Then we can obtain the factors using the inverse fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
+By choosing diferent $r$, one can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
 
-\begin{equation}
-{\rm FFT}(\omega) \cdot \vec a_r = \vec y
-\end{equation}
-where $(\vec a_r)_k = a_k r ^k$, by choosing diferent $r$, we can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
-
-\subsection{Finite field algebra}
-It is possible to compute the independence polynomials exactly using basic integer types only,
-even when the degeneracy is bigger than that can be represented by 64 bit integers.
-What we need is computing with the finite field algebra $GF(p)$
+\subsection{The finite field algebra approach}
+It is possible to compute the independence polynomials exactly using 64 bit integers types only,
+even when the factors are larger than that can be represented by 64 bit integers.
+We achieve this by designing a finite field algebra $GF(p)$
 
@@
 \begin{split}
-    x\pmod p ~\oplus~ y\pmod p &= x+y\pmod p\\
-    x\pmod p ~\odot~ y\pmod p &= xy\pmod p\\
-    \mymathbb{0} &= 0\\
-    \mymathbb{1} &= 1
+    x ~\oplus~ y &= x+y\pmod p,\\
+    x ~\odot~ y &= xy\pmod p,\\
+    \mymathbb{0} &= 0,\\
+    \mymathbb{1} &= 1.
 \end{split}
@@
 
-It a field because the multiplicative inverse can defined on non-zero values, which can be computed with the extended Euclidean algorithm.
 In a finite field algebra, we have the following observations
 \begin{enumerate}
-    \item One can still use Gaussian elimination~\cite{Golub2013} to solve the linear equations in a finite field, since the multiplicative inverse is properly defined in a finite field,
-    \item Let remainders of an integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$ being $\{x \pmod {p_1}, x\pmod {p_2}, \ldots, x \pmod {p_n}\}$,
-    then $\{x \pmod {p_1 \times p_2 \times \ldots \times p_n}\}$ can be obtained using the chinese remainder theorem.
+    \item One can still use Gaussian elimination~\cite{Golub2013} to solve a linear equation.
+    This is because a field has the property that the multiplicative inverse exists for any non-zero value.
+    The multiplicative inverse here can be computed with the extended Euclidean algorithm.
+    \item Given the remainders of a larger integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$,
+    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the chinese remainder theorem.
+    With this, one can infer big integers even though its bit width is larger than the register size.
 \end{enumerate}
-With these observations, we use Algorithm~\ref{alg:finitefield} to compute degeneracies.
-In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width.
+With these observations, we developed Algorithm~\ref{alg:finitefield} to compute independent polynomial exactly without introducing space overheads.
+In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width $W$.
 
@@
     \LinesNumbered
-    Let $P = 1$, $X = {0,1,2,\ldots,m}$ and $\hat X_{ij} = X_i^j$, where $i,j = \{0, 1, \ldots m\}$\;
+    Let $P = 1$, vector $X = (0,1,2,\ldots,m)$, matrix $\hat X_{ij} = X_i^j$, where $i,j = 0, 1, \ldots m$\;
     \While{true}{
-        compute the largest prime 64 bit integer $p$ that $\gcd(p, P) = 1$\;
-        compute the tensor network contraction on $GF(p)$ and obtain $Y\pmod p = \{y_0 \pmod p, y_1 \pmod p, \ldots , y_m \pmod p\} $\;
-        $A \pmod p = \{a_0 \pmod p, a_1 \pmod p, \ldots, a_m \pmod p\} = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
-        $A \pmod {P\times p} = {\rm chinese\_remainder}(A \pmod P, A \pmod p)$\;
-        \If{$A \pmod P = A \pmod {P \times p}$}{
-            \Return $A \pmod P$\;
+        compute the largest prime $p$ that $\gcd(p, P) = 1 \land p \leq 2^W$\;
+        compute the tensor network contraction on $GF(p)$ and obtain $Y = (y_0, y_1, \ldots , y_m) \pmod p $\;
+        $A_p = (a_0, a_1, \ldots, a_m) \pmod p = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
+        \If{$A_P = A_{P \times p}$}{
+            \Return $A_P$ \tcp*[l]{converged}
         }
@@
 \section{Computing maximum independent set size and its corresponding degeneracy and configurations}
-Obtaining the maximum independent set size and its degeneracy is computational more efficient. Let $x=\infty$, then the independence polynomial becomes
+Obtaining the maximum independent set size and its degeneracy can be computational more efficient. Let $x=\infty$, then the independence polynomial becomes
 \begin{equation}
@@
 In the program, we only store the power $x$ and the corresponding factor $a_x$ that initialized to $1$.
-This algebra is consistent with the one we derived in ~\cite{Liu2021} that uses the tropical tensor network solving spin glass ground states.
-Here if we are only interested in obtaining $\alpha(G)$ and omit the factors, the algebra of $x$ corresponds to the tropical algebra~\cite{Maclagan2015,Moore2011}.
+This algebra is consistent with the one we derived in ~\cite{Liu2021} that uses the tropical tensor network for solving spin glass ground states.
+If one is only interested in obtaining $\alpha(G)$, he can drop the factor parts, then the algebra of $x$ becomes the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
 
-One may want to obtain all ground state configurations,
-it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$ initialized to a vertex index $i$ dependent onehot vector $s_i = \{\boldsymbol{\delta}_{ij=1,\ldots,n}\}$.
+One may also want to obtain all ground state configurations, it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$.
+We design a new element type that having algebra
 \iffalse
@@
         s_x\infty^{\max(x,y)}, & x > y
-    \end{cases}\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y}\\
-    \mymathbb{0} &= \{\}\infty^{-\infty}\\
-    \mymathbb{1} &= \{\boldsymbol 0\}\infty^{0}
+    \end{cases},\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+    \mymathbb{0} &= \{\}\infty^{-\infty},\\
+    \mymathbb{1} &= \{\boldsymbol 0\}\infty^{0},
 \end{split}
 \end{align}
-The $\vee$ is the bit-wise \texttt{or}. One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
+where $\vee$ is the bit-wise \texttt{or}. One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
+We first initialize the bit strings of the variable $x$ in the vertex tensor to a vertex index $i$ dependent onehot vector $x_i = \boldsymbol{e}_{i}$,
+then we contract the tensor network. The resulting object will give us the set of all optimal configurations.
 By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save computational effort.
 We leave this as an exercise for readers.
+
+\subsection{bounding the enumeration space}
+When we try to implement the above algebra for enumerating configurations, we find the space overhead is larger than than we have expected.
+It stores more than nessesary intermedite configurations. To speed up the computation, we use $\alpha(G)$ that much easier to compute for bounding.
+We first compute the value of $\alpha(G)$ with tropical numbers and cache all intermediate tensors.
+Then we compute a boolean masks for each cached tensor, where we use a boolean true to represent a tensor element having contribution to the maximum independent set (i.e.
+with a nonzero gradient) and boolean false otherwise.
+Finally, we perform masked matrix multiplication using the new element type with the above algebra for obtaining all configurations.
+To compute the masks, we ``back propagate'' the masks step by step through contraction process using the cached intermediate tensors.
+Consider a tropical matrix multiplication $C = A B$, we have the following inequality
+\begin{align}
+    A_{ij} \odot B_{jk} &\leq C_{ik}.
+\end{align}
+
+Moving $B_{ik}$ to the right hand side, we have
+\begin{align}
+    A_{ij} &\leq (\oplus_{k} (C_{ik}^{-1} \odot B_{jk}))^{-1}
+\end{align}
+where the tropical multiplicative inverse is defined as the additive inverse of the regular algebra.
+The equality holds if and only if element $A_{ij}$ contributions to $C$ (i.e.
+has nonzero gradient).
+Let the mask for $C$ being $\overline C$, the backward rule for gradient masks reads
+\begin{align}
+\overline{A}_{ij} = \delta(A_{ij}, ((C^{\circ-1} \circ \overline C )B^T)_{ij}^{\circ -1}),
+\end{align}
+where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard multiplication, boolean false is treated as tropical zero and boolean true is treated as tropical one.
+This rule defined on matrix multiplication can be easily generalized to the einsum of two tensors by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum.
 

### 2021-06-11 project/configurations.jl

@@ -33,10 +33,10 @@ if false
     mis_configurations(13, 1, 'A')
     mis_configurations(13, 3, 'A')
 else
-    #for n in [7, 10], seed in 1:6
-    #    mis_configurations(n, seed, 'B'; writefile=true)
-    #end
-    for n in [13, 15], seed in [1, 2, 3, "Easy_1", "Medium_1", "Hard_1"]
-        mis_configurations(n, seed, 'B', writefile=true)
+    for n in [7, 10], seed in 1:6
+        mis_configurations(n, seed, 'B'; writefile=true)
     end
+    #for n in [13, 15], seed in [1, 2, 3, "Easy_1", "Medium_1", "Hard_1"]
+    #    mis_configurations(n, seed, 'B', writefile=true)
+    #end
 end

### 2021-06-11 src/ad.jl

@@ -3,29 +3,43 @@ using TupleTools
 export bounding_contract
 
 Base.isnan(x::Tropical) = isnan(x.n)
-function backward_tropical(mode, @nospecialize(ixs), @nospecialize(xs), @nospecialize(iy), @nospecialize(y), @nospecialize(ymask), i, size_dict)
-    nixs = TupleTools.insertat(ixs, i, (iy,))
-    nxs  = TupleTools.insertat( xs, i, (OMEinsum.asarray(inv.(y) .* ymask),))
-    niy = ixs[i]
-    A = inv.(einsum(EinCode(nixs, niy), nxs, size_dict))
-    if mode == :all
-        return A .== xs[i]
-    elseif mode == :single  # wrong, need `B` matching `A`.
-        mask = falses(size(A)...)
-        found = false
-        for j=1:length(A)
-            if xs[i][j] == A[j] && !found
-                #@show j, A, xs[i]
-                mask[j] = true
-                found = true
-            else
-                xs[i][j] = zero(eltype(xs[i]))
-            end
-        end
-        return mask
-    else
-        error("unkown mode: $mod")
+function backward_tropical(mode, @nospecialize(ixs), @nospecialize(xs), @nospecialize(iy), @nospecialize(y), @nospecialize(ymask), size_dict)
+    @inbounds for i=1:length(y)
+        y[i] = inv(y[i]) * ymask[i]
     end
+    masks = []
+    for i=1:length(ixs)
+        nixs = TupleTools.insertat(ixs, i, (iy,))
+        nxs  = TupleTools.insertat( xs, i, (y,))
+        niy = ixs[i]
+        if mode == :all
+            mask = zeros(Bool, size(xs[i]))
+            mask .= inv.(einsum(EinCode(nixs, niy), nxs, size_dict)) .== xs[i]
+            push!(masks, mask)
+        elseif mode == :single  # wrong, need `B` matching `A`.
+            A = zeros(eltype(xs[i]), size(xs[i]))
+            A = einsum(EinCode(nixs, niy), nxs, size_dict)
+            push!(masks, hotmask(A, xs[i]))
+        else
+            error("unkown mode: $mod")
+        end
+    end
+    return masks
+end
+
+function hotmask(A, X::AbstractArray{T}) where T
+    @assert length(A) == length(X)
+    mask = falses(size(A)...)
+    found = false
+    @inbounds for j=1:length(A)
+        if X[j] == inv(A[j]) && !found
+            mask[j] = true
[…]

### 2021-06-12 paper/paper.tex
update code

@@
 &\\
-a \odot \mymathbb{0} = \mymathbb{0} * a = \mymathbb{0}
+a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
 \end{align*}
@@
 
+\section{discussion}
+We introduced in the main text how to compute the indenpendence polynomial, maximum independent set and optimal configurations.
+It is interesting that although these properties are global,
+they can be solved by designing different element types that having two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
+One thing in common is that they all defines a commutative semiring.
+Here, we want the $\oplus$ and $\odot$ operations being commutative because we do not want the contraction result of an einsum network to be sensitive to the contraction order.
+We show most of the implementation in Appendix \ref{sec:technical}. It is supprisingly short.
+The style that we program is called generic programming,
+it is about writing a single copy of code, feeding different types into it, and the program computing the result with a proper performance.
+It is language dependent feature. If someone want to implement this algorithm in python,
+one has to rewrite the matrix multiplication for different element types in C and then export the interface to python.
+In C++, users can use templates for such a purpose.
+In our work, we chose Julia because its just in time compiling is very powerful that it can generate fast code dynamically for users.
+Elements of fixed size, such as the finite field algebra, tropical number, tropical number with counting/configuration field used in the main text can be inlined in an array.
+Furthermore, these inlined arrays can be upload to GPU devices for faster generic matrix multiplication implemented in CUDA.jl.
+
 \iffalse
@@
 
-\section{Technical guide}
+\section{Technical guide}\label{sec:technical}
 \begin{description}
@@
 \begin{lstlisting}
-pkg> add OMEinsum
+pkg> add OMEinsum LightGraphs Mods Primes FFTW Polynomials TropicalNumbers
 \end{lstlisting}
 
-An example of computing the maximum independant set size
-\begin{lstlisting}
-julia> using OMEinsum, LightGraphs, TropicalNumbers
+It may supprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding and sparsity related parts,
+all are contained in this appendix. After installing required packages, one can open a Julia REPL and copy the following code into it.
 
-julia> n, k = 6, 3
-(6, 3)
+\lstinputlisting[breaklines]{../democode/demo.jl}
 
-julia> g = LightGraphs.random_regular_graph(n, k)
-{6, 9} undirected simple Int64 graph
-
-julia> ixs = [minmax(e.src,e.dst) for e in LightGraphs.edges(g)]
-9-element Vector{Tuple{Int64, Int64}}:
- (1, 2)
- (1, 4)
- (1, 5)
- (2, 3)
- (2, 6)
- (3, 5)
- (3, 6)
- (4, 5)
- (4, 6)
-
-julia> code = EinCode((ixs..., [(i,) for i in LightGraphs.vertices(g)]...), ())
-1∘2, 1∘4, 1∘5, 2∘3, 2∘6, 3∘5, 3∘6, 4∘5, 4∘6, 1, 2, 3, 4, 5, 6 ->
-
-julia> optimized_code = optimize_greedy(code, Dict([i=>2 for i=1:6]))
-4∘6, 4∘6 -> 
-├─ 4∘6, 6 -> 4∘6
-│  ├─ 6
-│  └─ 4∘6
-└─ 2∘5∘4, 5∘2∘6 -> 4∘6
-   ├─ 2∘5∘6, 6∘2 -> 5∘2∘6
-   │  ├─ 2∘6, 2 -> 6∘2
-   │  │  ├─ 2
-   │  │  └─ 2∘6
-   │  └─ 2∘3, 5∘6∘3 -> 2∘5∘6
-   │     ├─ 3∘5, 6∘3 -> 5∘6∘3
-   │     │  ├─ 3∘6, 3 -> 6∘3
-   │     │  │  ⋮
-   │     │  │  
-   │     │  └─ 3∘5, 5 -> 3∘5
-   │     │     ⋮
-   │     │     
-   │     └─ 2∘3
-   └─ 2∘4∘1, 1∘4∘5 -> 2∘5∘4
-      ├─ 1∘5, 5∘4 -> 1∘4∘5
-      │  ├─ 4∘5, 4 -> 5∘4
-      │  │  ├─ 4
-      │  │  └─ 4∘5
-      │  └─ 1∘5
-      └─ 2∘1, 1∘4 -> 2∘4∘1
-         ├─ 1∘4
-         └─ 1∘2, 1 -> 2∘1
-            ├─ 1
-            └─ 1∘2
-
-julia> function mis_contract(code::OMEinsum.NestedEinsum, x::T) where T
-           tensors = map(OMEinsum.getixs(Iterators.flatten(code))) do ix
-               @assert length(ix) == 1 || length(ix) == 2
-                           length(ix) == 1 ? [one(T), x] : [one(T) one(T); one(T) zero(T)]
-           end
-           code(tensors...)
-       end
-mis_contract (generic function with 1 method)
-
-julia> result = mis_contract(optimized_code, Tropical(1.0))
-0-dimensional Array{TropicalF64, 0}:
-2.0ₜ
-\end{lstlisting}
-
-For larger graph, we hight recommend using two additional packages,
-\texttt{TropicalGEMM} for BLAS speed tropical matrix multiplication and
-\texttt{OMEinsumContractionOrders} for hyper optimized contraction order (the KaHyPar~\cite{Schlag2020} approach) ~\cite{Kourtis2019,Gray2021,Pan2021}.
-
-\section{Indenpendence polynomials}
-\subsection{Common}
-\begin{lstlisting}
-using Polynomials
-
-_auto_mispolytensor(x::T, ix::NTuple{2}) where T = T[1 1; 1 0]
-_auto_mispolytensor(x::T, ix::NTuple{1}) where T = T[1, x]
-function generate_polyxs!(x::T, code::OMEinsum.NestedEinsum, xs=Vector{Any}(undef, ninput(code))) where {T}
-    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
-		if arg isa Integer
-			xs[arg] = _auto_mispolytensor(x, ix)
-		else
-        	generate_polyxs!(x, arg, xs)
-		end
-    end
-	return xs
-end
-
-function generate_polyxs!(x::T, code::EinCode, xs=Vector{Any}(undef, ninput(code))) where {T}
-    for (i,ix) in enumerate(OMEinsum.getixs(code))
-		xs[i] = _auto_mispolytensor(x, ix)
-    end
-	return xs
-end
-
-function mis_polysolve(code, x::T) where {T}
-	xs = generate_polyxs!(x, code, Vector{Any}(undef, NoteOnTropicalMIS.ninput(code)))
-	code(xs...)
-end
-\end{lstlisting}
-
-\subsection{Symbolic}
-\begin{lstlisting}
-function independence_polynomial(::Val{:polynomial}, code)
-    mis_polysolve(code, Polynomial([0, 1.0]))[]
-end
-\end{lstlisting}
-
-\subsection{Fitting and FFT}
-\begin{lstlisting}
-using FFTW
-function independence_polynomial(::Val{:fft}, code; mis_size=Int(mis_solve(code)[].n), r=1.0)
-	ω = exp(-2im*π/(mis_size+1))
-	xs = r .* collect(ω .^ (0:mis_size))
-	ys = [mis_polysolve(code, x)[] for x in xs]
-	Polynomial(real.(ifft(ys) ./ (r .^ (0:mis_size))))
-end
-
-function independence_polynomial(::Val{:fitting}, code; mis_size=Int(mis_solve(code)[].n))
-	xs = (0:mis_size)
-	ys = [mis_polysolve(code, x)[] for x in xs]
-	fit(xs, ys, mis_size)
-end
-\end{lstlisting}
-
-\subsection{Finite field algebra}
-\begin{lstlisting}
-using Mods, Primes
-
-# pirate
-Base.abs(x::Mod) = x
-Base.isless(x::Mod{N}, y::Mod{N}) where N = mod(x.val, N) < mod(y.val, N)
-
-function _independance_polynomial(::Type{T}, code, mis_size::Int) where T
-	xs = 0:mis_size
-	ys = [mis_polysolve(code, T(x))[] for x in xs]
-	A = zeros(T, mis_size+1, mis_size+1)
-	for j=1:mis_size+1, i=1:mis_size+1
-		A[j,i] = T(xs[j])^(i-1)
-	end
-	A \ T.(ys)
-end
-
-function independence_polynomial(::Val{:finitefield}, code; mis_size=Int(mis_solve(code)[].n), max_order=100)
-    N = typemax(Int)
-    YS = []
-    local res
-    for k = 1:max_order
-	    N = prevprime(N-1)
-        T = Mods.Mod{N,Int}
-        rk = _independance_polynomial(T, code, mis_size)
-        push!(YS, rk)
-        if max_order==1
-            return Polynomial(Mods.value.(YS[1]))
-        elseif k != 1
-            ra = improved_counting(YS[1:end-1])
-            res = improved_counting(YS)
-            ra == res && return Polynomial(res)
-        end
-    end
-    @warn "result is potentially inconsistent."
-    return Polynomial(res)
-end
-
-function improved_counting(sequences)
-    map(yi->Mods.CRT(yi...), zip(sequences...))
-end
-\end{lstlisting}
-
-\section{Maximum independent set}
-\subsection{Tropical numbers}
-\begin{lstlisting}
-function independence_polynomial(::Val{:polynomial}, code)
-    mis_polysolve(code, Polynomial([0, 1.0]))[]
-end
-\end{lstlisting}
-
-\subsection{Enumerating configurations}
-
-The following is a complete example.
-
-\begin{lstlisting}
-using OMEinsum, TropicalNumbers
-using OMEinsum: NestedEinsum
-
-struct ConfigEnumerator{N,C}
-    data::Vector{StaticBitVector{N,C}}
-end
-
-Base.length(x::ConfigEnumerator{N}) where N = length(x.data)
-Base.:(==)(x::ConfigEnumerator{N,C}, y::ConfigEnumerator{N,C}) where {N,C} = x.data == y.data
-
-function Base.:+(x::ConfigEnumerator{N,C}, y::ConfigEnumerator{N,C}) where {N,C}
-    res = ConfigEnumerator{N,C}(vcat(x.data, y.data))
-    return res
-end
-
-function Base.:*(x::ConfigEnumerator{L,C}, y::ConfigEnumerator{L,C}) where {L,C}
-    M, N = length(x), length(y)
-    z = Vector{StaticBitVector{L,C}}(undef, M*N)
-    for j=1:N, i=1:M
-        z[(j-1)*M+i] = x.data[i] .| y.data[j]
-    end
-    return ConfigEnumerator{L,C}(z)
-end
-
-Base.zero(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}(StaticBitVector{N,C}[])
-Base.one(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}([TropicalNumbers.staticfalses(StaticBitVector{N,C})])
-
-function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1, N, C, T<:CountingTropical{T1,ConfigEnumerator{N,C}}}
-    [one(T) one(T); one(T) zero(T)]
-end
-function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1, N, C, T<:CountingTropical{T1,ConfigEnumerator{N,C}}}
-    [one(T), CountingTropical(one(T1), ConfigEnumerator([TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]])]))]
-end
-function enumerator_t(::Type{T}, ix::NTuple{2}, vertex_index) where {T1,N,C, T<:ConfigTropical{T1,N,C}}
-    [one(T) one(T); one(T) zero(T)]
-end
-function enumerator_t(::Type{T}, ix::NTuple{1}, vertex_index) where {T1,N,C, T<:ConfigTropical{T1,N,C}}
-    [one(T), T(one(T1), TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]]))]
-end
-
-function generate_xs!(f, x::T, code::NestedEinsum, xs) where {T}
-    for (ix, arg) in zip(OMEinsum.getixs(code.eins), code.args)
-		if arg isa Integer
-			xs[arg] = f(x, ix)
-		else
-        	generate_xs!(f, x, arg, xs)
-		end
-    end
-	return xs
-end
-
-function generate_xs!(f, x::T, code::EinCode, xs) where {T}
-    for (i,ix) in enumerate(OMEinsum.getixs(code))
-		xs[i] = f(x, ix)
-    end
-	return xs
-end
-
-symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(ixs))
-symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne))
-ninput(::EinCode{ixs}) where ixs = length(ixs)
-ninput(ne::NestedEinsum) = ninput(Iterators.flatten(ne))
-function mis_config(code; all=false)
-    vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(code))])
-    N = length(vertex_index)
-    C = TropicalNumbers._nints(N)
-    T = all ? CountingTropical{Float64, ConfigEnumerator{N,C}} : ConfigTropical{Float64, N, C}
-	xs = generate_xs!((T, ix)->enumerator_t(T, ix, vertex_index), T, code, Vector{Any}(undef, ninput(code)))
-	code(xs...)
-end
-
-mis_config(optimize_greedy(ein"i,j,k,l,ij,jk,kl,li->", Dict('i'=>2, 'j'=>2, 'k'=>2, 'l'=>2)); all=true)  # square
-\end{lstlisting}
-
-You will see the following output
-
-\begin{lstlisting}
-0-dimensional Array{CountingTropical{Float64, ConfigEnumerator{4, 1}}, 0}:
-(2.0, ConfigEnumerator{4, 1}(StaticBitVector{4, 1}[1010, 0101]))ₜ
-\end{lstlisting}
-
+In the above examples, the configuration enumeration is very slow, one should use the optimal MIS size for bounding as decribed in the main text.
+We will not show any example about implementing the backward rule here because it has approximately 100 lines of code.
+Please checkout our Github repository \href{https://github.com/Happy-Diode/NoteOnTropicalMIS}{https://github.com/Happy-Diode/NoteOnTropicalMIS}.
 \end{document}

### 2021-06-12 democode/demo.jl

@@ -1,0 +1,151 @@
+using OMEinsumContractionOrders: OMEinsum
+using OMEinsum, OMEinsumContractionOrders
+using OMEinsum: NestedEinsum
+using LightGraphs
+using Random
+
+# generate a random regular graph of size 100, degree 3
+graph = (Random.seed!(2); LightGraphs.random_regular_graph(100, 3))
+
+# generate einsum code, i.e. the labels of tensors
+code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # labels for edge tensors
+                [(i,) for i in LightGraphs.vertices(graph)]...), ())        # labels for vertex tensors
+
+# an einsum contraction without contraction order specified is called `EinCode`,
+# an einsum contraction has contraction order (specified as a tree structure) is called `NestedEinsum`.
+# assign each label a dimension-2, it will be used in contraction order optimization
+# `symbols` function extracts tensor labels into a vector.
+symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(ixs)) # `ixs` is input tensor labels
+symbols(ne::NestedEinsum) = symbols(Iterators.flatten(ne)) # `Iterators.flatten` converts a `NestedEinsum` to an `EinCode`
+size_dict = Dict([s=>2 for s in symbols(code)])
+# optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+optimized_code = optimize_kahypar(code, size_dict; sc_target=17, max_group_size=40)
+println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
+
+# a function for computing independence polynomial
+function independence_polynomial(x::T, code) where {T}
+	xs = map(OMEinsum.getixs(Iterators.flatten(code))) do ix
+        # if the tensor rank is 1, create a vertex tensor.
+        # otherwise the tensor rank must be 2, create a bond tensor.
+        length(ix)==1 ? [one(T), x] : [one(T) one(T); one(T) zero(T)]
+    end
+    # both `EinCode` and `NestedEinsum` are callable, inputs are tensors.
+	code(xs...)
+end
+
+########## COMPUTING MAXIMUM INDEPENDENT SET SIZE AND ITS DEGENERACY ###########
+
+# using Tropical numbers to compute the MIS size and MIS degeneracy.
+using TropicalNumbers
[…]

### 2021-06-12 src/ad.jl

@@ -80,10 +80,10 @@ end
 function bounding_contract(code::NestedEinsum, @nospecialize(xsa), ymask, @nospecialize(xsb); size_info=nothing)
     size_dict = OMEinsum.get_size_dict(OMEinsum.getixs(Iterators.flatten(code)), xsa, size_info)
     # compute intermediate tensors
-    println("caching einsum...")
+    @debug "caching einsum..."
     c = cached_einsum(code, xsa, size_dict)
     # compute masks from cached tensors
-    println("generating masked tree...")
+    @debug "generating masked tree..."
     mt = generate_masktree(code, c, ymask, size_dict, :all)
     # compute results with masks
     masked_einsum(code, xsb, mt, size_dict)
@@ -96,11 +96,11 @@ end
 function mis_config_ad(code::NestedEinsum, @nospecialize(xsa), ymask; size_info=nothing)
     size_dict = OMEinsum.get_size_dict(OMEinsum.getixs(Iterators.flatten(code)), xsa, size_info)
     # compute intermediate tensors
-    println("caching einsum...")
+    @debug "caching einsum..."
     c = cached_einsum(code, xsa, size_dict)
     n = c.content[]
     # compute masks from cached tensors
-    println("generating masked tree...")
+    @debug "generating masked tree..."
     mt = generate_masktree(code, c, ymask, size_dict, :single)
     n, read_config!(code, mt, Dict())
 end

### 2021-06-12 test/ad.jl

@@ -24,7 +24,7 @@ end
     end
     rawcode = random_regular_eincode(10, 3)
     optcode = OMEinsum.optimize_greedy(rawcode, uniformsize(rawcode, 2))
-    xs = NoteOnTropicalMIS.generate_xs!(NoteOnTropicalMIS._auto_mistensor, TropicalF64(1.0), rawcode, Vector{Any}(undef, NoteOnTropicalMIS.ninput(rawcode)))
+    xs = NoteOnTropicalMIS.generate_vertextensors(ix->length(ix)==1 ? misv(TropicalF64,1,TropicalF64(1.0)) : misb(TropicalF64), rawcode)
     y1 = rawcode(xs...)
     y2 = bounding_contract(rawcode, xs, BitArray(fill(true)), xs)
     @test y1 ≈ y2

### 2021-06-12 test/independence_polynomial.jl

@@ -22,7 +22,7 @@ end
                     (TropicalF64(5), TropicalF64(3), TropicalF64(-9)),
                     (CountingTropicalF64(5, 3), CountingTropicalF64(3, 9), CountingTropicalF64(-3, 2)),
                     (ConfigTropical{Float64,10,1}(5.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10,1}(3.0, BitVector(rand(Bool, 10))), ConfigTropical{Float64,10,1}(-3.0, BitVector(rand(Bool, 10)))),
-                    (CountingTropical(5.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:3])), CountingTropical(3.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:4])), CountingTropical(-3.0, ConfigEnumerator{10}([BitVector(rand(Bool, 10)) for j=1:5]))),
+                    (CountingTropical(5.0, ConfigEnumerator([StaticBitVector(rand(Bool, 10)) for j=1:3])), CountingTropical(3.0, ConfigEnumerator([StaticBitVector(rand(Bool, 10)) for j=1:4])), CountingTropical(-3.0, ConfigEnumerator([StaticBitVector(rand(Bool, 10)) for j=1:5]))),
                     ]
         @test is_commutative_semiring(a, b, c)
     end

### 2021-06-12 paper/paper.tex
update
demos

@@
 \end{abstract}
+
+\section{Introduction}
+Exact algorithms that solves the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
 
@@
 
-\section{Utilizing sparsity}
+\section{Automated branching}
+% check http://www.tcs.rwth-aachen.de/independentset/ for more rules
 So far, we have used the language of einsum networks for contraction.
@@
 
+\begin{table}[h!]\centering
+\begin{minipage}{0.9\columnwidth}
+\ra{1.3}
+    \scalebox{1.0}{
+        \begin{tabularx}{\textwidth}{bb}\toprule
+            \hline
+            \textbf{element type}     & \textbf{purpose} \\
+            {regular number}     & {counting all indenepent sets} \\
+            {tropical number}     & {finding the maximum independent set size} \\
+            {tropical number with counting}     & {finding both the maximum independent set size and its degeneracy} \\
+            {tropical number with configuration}     & {finding the maximum independent set size and one of the optimal configurations} \\
+            {tropical number with multiple configurations}     & {finding the maximum independent set size and all optimal configurations} \\
+            {polynomial}     & {computing the indenpendence polynomials exactly} \\
+            {complex number}     & {fitting the indenpendence polynomials with fast fourier transformation} \\
+            {finite field algebra}     & {fitting the indenpendence polynomials exactly using number theory} \\
+            \bottomrule
+        \end{tabularx}
+    }
+    \caption{Tensor element types used in the main text and their purposes.}\label{tbl:generictypes}
+\end{minipage}
+\end{table}
+
 \iffalse

### 2021-06-12 democode/demo.jl

@@ -18,7 +18,7 @@ code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # la
 symbols(::EinCode{ixs}) where ixs = unique(flatten(filter(x->length(x)==1,ixs)))
 symbols(ne::OMEinsum.NestedEinsum) = symbols(flatten(ne))
 size_dict = Dict([s=>2 for s in symbols(code)])
-# optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+# optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^17
 optimized_code = optimize_kahypar(code, size_dict; sc_target=17, max_group_size=40)
 println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
 

### 2021-06-12 project/configurations.jl

@@ -22,9 +22,18 @@ function mis_configurations(n, seed, round; writefile=false)
         @assert length(config) == nc.c
 
         ofname = joinpath(folder, "configurations_$(n)x$(n)_5.3x5.3_$seed.dat")
-        writefile && write(ofname, Matrix(config))
+
+        writefile && write(ofname, toMatrix(config))
         return nc.n, config
     end
+end
+
+function toMatrix(x::ConfigEnumerator{N,C}) where {N,C}
+    m = zeros(UInt64, C, length(x))
+    for i=1:length(x)
+        m[:,i] .= x.data[i].data
+    end
+    return m
 end
 
 if false

### 2021-06-12 src/configurations.jl

@@ -29,7 +29,7 @@ Base.one(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}([Tro
 
 symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(filter(x->length(x)==1,ixs)))
 
-function mis_config(code; all=false, usemask=true)
+function mis_config(code; all=false, bounding=true)
     flatten_code = flatten(code)
     vertex_index = Dict([s=>i for (i, s) in enumerate(symbols(flatten_code))])
     N = length(vertex_index)
@@ -37,17 +37,17 @@ function mis_config(code; all=false, usemask=true)
     xs = map(getixs(flatten_code)) do ix
         T = all ? CountingTropical{Float64, ConfigEnumerator{N,C}} : ConfigTropical{Float64, N, C}
         if length(ix) == 2
-            return [one(T) one(T); one(T) zero(T)]
+            return misb(T)
         else
             s = TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]])
             if all
-                [one(T), T(1.0, ConfigEnumerator([s]))]
+                misv(T, T(1.0, ConfigEnumerator([s])))
             else
-                [one(T), T(1.0, s)]
+                misv(T, T(1.0, s))
             end
         end
     end
-    if usemask
+    if bounding
         ymask = trues(fill(2, length(getiy(flatten_code)))...)
         xst = map(getixs(flatten_code)) do ix
             length(ix) == 1 ? misv(TropicalF64,Tropical(1.0)) : misb(TropicalF64)
@@ -57,16 +57,9 @@ function mis_config(code; all=false, usemask=true)
         else
             @assert ndims(ymask) == 0
             t, res = mis_config_ad(code, xst, ymask)
-            return fill(ConfigTropical(t[].n, StaticBitVector(map(l->res[l], 1:N))))
+            return fill(ConfigTropical(asscalar(t).n, StaticBitVector(map(l->res[l], 1:N))))
         end
     else
 	    return code(xs...)
     end
-end
-function Base.Matrix(x::ConfigEnumerator{N,C}) where {N,C}
-    m = zeros(UInt64, C, length(x))
-    for i=1:length(x)
-        m[:,i] .= x.data[i].data
-    end
-    return m
 end

### 2021-06-12 src/demos.jl

@@ -1,1 +1,54 @@
-ein"v,va,vb,vc"()
+export case_r3, run_task
+
+using Random
+
+function case_r3(n, k=3; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    graph = (Random.seed!(seed); LightGraphs.random_regular_graph(n, k))
+    # generate einsum code, i.e. the labels of tensors
+    code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # labels for edge tensors
+                    [(i,) for i in LightGraphs.vertices(graph)]...), ())        # labels for vertex tensors
+    size_dict = Dict([s=>2 for s in symbols(code)])
+    # optimize the contraction order using KaHyPar + Greedy
+    optimized_code = optimize_kahypar(code, size_dict; sc_target=sc_target, max_group_size=40)
+    println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
+    return optimized_code
+end
+
+function case_dc(L::Int, ρ; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    Random.seed!(seed)
+    graph = diagonal_coupled_graph(rand(L, L) .< ρ)
+    # generate einsum code, i.e. the labels of tensors
+    code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # labels for edge tensors
+                    [(i,) for i in LightGraphs.vertices(graph)]...), ())        # labels for vertex tensors
+    size_dict = Dict([s=>2 for s in symbols(code)])
+    # optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+    optimized_code = optimize_kahypar(code, size_dict; sc_target=sc_target, max_group_size=40)
+    println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
+    return optimized_code
+end
+
+function run_task(code, task)
+    if task == :totalsize
+        return mis_contract(1.0, code)
+    elseif task == :maxsize
+        return mis_size(code)
+    elseif task == :counting
+        return mis_count(code)
+    elseif task == :idp_polynomial
+        return independence_polynomial(Val(:polynomial), code)
+    elseif task == :idp_fft
+        return independence_polynomial(Val(:fft), code)
+    elseif task == :idp_finitefield
+        return independence_polynomial(Val(:finitefield), code)
+    elseif task == :config_single
[…]

### 2021-06-12 src/independence_polynomial.jl

@@ -57,12 +57,13 @@ function _independance_polynomial(::Type{T}, code, mis_size::Int) where T
 end
 
 function independence_polynomial(::Val{:finitefield}, code; mis_size=mis_size(code), max_order=100)
-    N = typemax(Int)
+    TI = Int32  # Int 32 is faster
+    N = typemax(TI)
     YS = []
     local res
     for k = 1:max_order
-	    N = prevprime(N-1)
-        T = Mods.Mod{N,Int}
+	    N = prevprime(N-TI(1))
+        T = Mods.Mod{N,TI}
         rk = _independance_polynomial(T, code, mis_size)
         push!(YS, rk)
         if max_order==1

### 2021-06-15 paper/paper.tex
new proof

@@
 
-\newtheorem{theorem}{\textit{Branching Rule}}
+\newtheorem{theorem}{\textit{Theorem}}
+\newtheorem{corollary}{\textit Branching Rule}
 \theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
@@
 When using sparse tropical tensor networks to find the maximum independent set, we can introduce a new rule to compress the tensor by removing elements that are not helpful.
-As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of vertice tensors at the cut.
+As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of boundary vertices defined as $C := \{c | c\in R \land c \in G\backslash R\}$.
+
+We denote the effective branching number of contracting the local degrees of freedoms as $|T_S|_{\neq -\infty}/2^{|S|}$, where $|\cdot|_{\neq -\infty}$ is the number of nonzero elements in a tropical tensor.
+
 Each tensor entry $A_{\sigma}$ defines a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
@@
 
+\begin{theorem}
+    A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be further reduces.
+\end{theorem}
+
+\begin{proof}
+    Let us prove it by showing any nonzero entry in a MIS-compact tropical tensor can be the only solution of maximum independent set under a certan exterior graph configuration.
+    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma} = k$, where $\sigma$ is the bounary configuration.
+    Construct a graph $G$ such that for a $v \in C$, if $\sigma_v=1$, $\alpha(N[v] \cap (G \backslash R)) = 0$, otherwise, $\alpha(N[v] \cap (G\backslash R)) = \infty$.
+    The simplest construction is connecting vertices that $\sigma_v=0$ with infinite many mutually disconnected vertices as illustrated in the following graph.
+
+    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 6cm 0cm}, clip]{proofoptimal.pdf}}
+
+    Then we have $\alpha(G) = \infty (|C|-|\sigma|) + k$. If there exists another configuration $\tau$ that generating the same good result, then $\tau \prec \sigma$,
+    otherwise it will suffer from infinite punishment from $G\backslash R$.
+    Since this tropical tensor is MIS-compact, it is not possible to find a such $\tau$ that $A_\tau \geq k$, otherwise $\sigma$ will be remove by the \textit{least restrictive rule}.
+\end{proof}
+
 \subsection{The tensor network compression detects branching rules automatically}
@@
 
-We are going the verify the Lemmas used for branching in book~\cite{Fomin2013}.
-\begin{theorem}\label{rule:one} % basic
+\begin{corollary}\label{rule:one} % basic
   If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
@@
 and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
-\end{theorem}
+\end{corollary}
 
@@
 
-\begin{theorem} % 2.5
-Let $G=(V,E)$ be a graph, let $v$ and $w$ be adjacent vertices of $G$ such that $N[v] \subseteq N[w]$. Then
-\begin{equation}
-\alpha(G)=\alpha(G\backslash w).
-\end{equation}
-\end{theorem}
+\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/basic.pdf}}
 
-Contract $N[w]$, both $\{v, w\}$ disapear from the tensor indices because they are inner degrees of freedom.
-If $w$ is one, then $N[v]$ are all zeros, the resulting tensor element can not be larger than setting $v=1$ and $w=0$.
-By the maximization rule, the local tensor does not change if we remove $w$.
+After contracting $N[v]$, $v$ becomes an internal degree of freedom.
+Applying tensor compression rule \Eq{eq:compress}, the resulting rank 4 tropical tensor is
 
-\begin{theorem} % 2.6
-  Let $G = (V, E)$ be a graph and let $v$ be a vertex of $G$. If no maximum
-independent set of $G$ contains $v$ then every maximum independent set of $G$ contains
-at least two vertices of $N(v)$.
-\end{theorem}
-Contract $N[v]$, the minimum tensor element is $2$, otherwise letting $v$ be in the independent set is one of the solutions. This is again captured by the \textit{local maximum rule}.
+\begin{align}
+    T_{juwk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        ~~~~1 & -\infty \\
+        -\infty & ~~~~2
+        \end{matrix}\right)_{ju}&
+        \left(\begin{matrix}
+        -\infty & ~~~~2 \\
+        ~~~~2 & ~~~~3
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        -\infty & ~~~~2 \\
+        ~~~~2 & ~~~~3
+        \end{matrix}\right)_{ju} &
+        \left(\begin{matrix}
+        ~~~~2 & ~~~~3 \\
+        ~~~~3 & ~~~~4
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{wk}.
+\end{align}
 
-\begin{theorem} % 2.7
+The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
+It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
+
+\begin{corollary}[mirror rule] % 2.7
+For some $v \in V$, a node $u \in N^2(v)$ is called mirror of $v$, if $N(v) \backslash N(u)$ is a clique. We denote the set of of a node $v$ mirrors~\cite{Fomin2013} by $M(v)$.
 Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
@@
 \end{equation}
-\end{theorem}
+\end{corollary}
 
-Here, $M(v)$ is the set of mirrors of $v$ in $G$.
-A vertex $w \in N^2(v)$ is called a mirror of $v$ if $N(v) \backslash N(w)$ is a clique.
 This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
@@
 
-\begin{theorem} % 2.9
-Let $G = (V, E)$ be a graph and $v$ be a vertex of $G$ such that $N[v]$ is a
-clique. Then
+In the following example, since $u\in N^2(v)$ and $N(v) \backslash N(u)$ is a clique, $u$ is a mirror of $v$.
+
+\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/mirror.pdf}}
+
+After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
+Applying tensor compression rule \Eq{eq:compress}, the resulting rank 4 tropical tensor is
+
+\begin{align}
+    T_{juwk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        ~~~~1 & ~~~~2 \\
+        -\infty & -\infty
+        \end{matrix}\right)_{ju}&
+        \left(\begin{matrix}
+        -\infty & -\infty \\
+        ~~~~2 & -\infty
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        -\infty & -\infty \\
+        -\infty & -\infty
+        \end{matrix}\right)_{ju} &
+        \left(\begin{matrix}
+        -\infty & -\infty \\
+        -\infty & -\infty
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{wk}.
+\end{align}
+
+In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
+which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
+
+\begin{corollary}[satellite rule] % satellite rule
+Let $G$ be agraph $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
+The set of satellites of a node $v$ is denotedby $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
 \begin{equation}
-\alpha(G) = 1 + \alpha(G \backslash N[v]).
+\alpha(G) = \max\{\alpha(G \backslash \{v\}), \alpha(G \backslash N[S[v]]) + |S(v)| + 1\}.
 \end{equation}
-\end{theorem}
+\end{corollary}
 
-Contract $N[v]$, and this rule can be captured by the \textit{local maximum rule}.
+This rule can be capture by contracting $N[v] \cup S(v)$.
+In the following example, since $u \in N^2(v)$ and $w \in N(v)$ satisfies $N[w] \backslash N[v] = \{u\}$, $u$ is a satellite of $v$.
 
-\begin{theorem}  %2.10
-Let $G$ be a graph, let $S$ be a separator of $G$ and let $I(S)$ be the set of
-all subsets of $S$ being an independent set of $G$. Then
-\begin{equation}
-\alpha(G) = \max_{A\in I(S)} |A| + \alpha(G \backslash (S \cup N[A])).
-\end{equation}
-\end{theorem}
-This rule corresponds to first contract tensors in subgraph $S$, then $N[S]$, and then contract the rest parts.
-These branching rule can be captured by the \textit{local maximum rule}.
+\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/satellite.pdf}}
 
-\begin{theorem}  %2.11
-Let $G = (V, E)$ be a disconnected graph and $C \subseteq V$ a connected component of $G$. Then
-\begin{equation}
-\alpha(G) = \alpha(G[C]) + \alpha(G \backslash C)).
-\end{equation}
-\end{theorem}
-Contract by the disconnected parts, and this rule can be captured by the \textit{local maximum rule}.
+After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
+Applying tensor compression rule \Eq{eq:compress}, the resulting rank 3 tropical tensor is
+\begin{align}
+    T_{juk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        ~~~~1 & ~~~~2 \\
+        ~~~~2 & -\infty
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        -\infty & -\infty \\
+        -\infty & -\infty
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{k}.
+\end{align}
+
+There are 3 nonzero entries. The internal configurations of entry $T(j=1, u=0, k=0) = 2$ is $(v=0, w =1)$,
+that of entry $T(j=0, u=1, k=0)=2$ is $(v=1, w=0)$, and that of entry $T(j=0, u=0, k=0)=1$ is $(v=1, w=0)$ or $(v=0, w=1)$.
+For entry $T(j=0, u=0, k=0)=1$, we post-select the internal degree of freedom as $(v=0, w=1)$.
+Then we can see the satellite rule either ${v, u} \in I$ or $v \notin I$ is satisfied.
+In this case, the effective branching number is $3^{1/5}\approx 1.2457$.
 

### 2021-06-15 benchmarks/independence_polynomial.jl

@@ -31,7 +31,7 @@ function run_benchmarks(cases; output_file)
     writedlm(output_file, times)
 end
 
-function run(;
+function runcase(;
         case_set=:r3,
         task = :maxsize,
         usecuda = false,
@@ -63,4 +63,4 @@ const truncatedict = Dict(
         (:idp_polynomial, 0), (:idp_fft, 0), (:idp_finitefield, 0),
         (:config_single, 0), (:config_all, 5), (:config_single_bounded, 0), (:config_all_bounded, 0)
     ]]))
-run(case_set=Symbol(GRAPH), task=Symbol(TASK), usecuda=DEVICE>=0, ntruncate=truncatedict[GRAPH][TASK])
+runcase(case_set=Symbol(GRAPH), task=Symbol(TASK), usecuda=DEVICE>=0, ntruncate=truncatedict[GRAPH][TASK])

### 2021-06-15 project/proofs.jl

@@ -1,0 +1,4 @@
+using TropicalNumbers, OMEinsum, NoteOnTropicalMIS
+
+code = ein"u,v,w,j,k,vw,vj,vk,ku,wu,wk->juk"
+mis_contract(Tropical(1.0), code)

### 2021-06-15 paper/paper.tex
finish proof

@@
 % check http://www.tcs.rwth-aachen.de/independentset/ for more rules
-So far, we have used the language of einsum networks for contraction.
-When using sparse tropical tensor networks to find the maximum independent set, we can introduce a new rule to compress the tensor by removing elements that are not helpful.
-As show in \Fig{fig:compressrule}, after we contract the tensors in a subregion $R \subseteq G$ of a graph $G$, and obtain a resulting tensor $A$ of rank $|C|$, where $C$ is the set of boundary vertices defined as $C := \{c | c\in R \land c \in G\backslash R\}$.
-
-We denote the effective branching number of contracting the local degrees of freedoms as $|T_S|_{\neq -\infty}/2^{|S|}$, where $|\cdot|_{\neq -\infty}$ is the number of nonzero elements in a tropical tensor.
-
-Each tensor entry $A_{\sigma}$ defines a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
-We call this properly the \textit{local maximum rule}.
-
-In addition, suppose we have two entries with the same local maximum independent set size corresponding to local configurations shown in (a) and (b), it is safe to claim configuration (a) being better than configuration (b) and remove the entry $A_{\sigma_b}$.
-This is because the boundary of (a) is less restrictive to the rest of the graph while having the equally good local maximum independent set size, 
-i.e. any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
-Hence an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ can be defined as
+Branching rules can be automatically discovered by contracting the tropical einsum network for a subgraph $R \subseteq G$.
+Let us denote the resulting tropical tensor of rank $|C|$ as $A$, where $C$ is the set of boundary vertices defined as $C := \{c | c\in R \land c \in G\backslash R\}$ and $|C|$ the size of $C$.
+Each tensor entry $A_{\sigma}$ is a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
+If we are only interested in finding a single maximum independent set rather than enumerating all possible solutions,
+this tensor can be further ``compresed'' by setting some entries to tropical zero.
+Let us define a relation of \textit{less restrictive} as
 \begin{align}
-(\sigma_a \land \sigma_b = \sigma_a) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}
+(\sigma_a \prec \sigma_b) := (\sigma_a \neq \sigma_b) \land (\sigma_a \leq^\circ \sigma_b)
 \end{align}
-where $\land$ is a bitwise and operations.
-The first term means that whenever a bit in $\sigma_a$ has boolean value $1$, the corresponding bit in $\sigma_b$ is also $1$.
-While the second term means the maximum independant set size with boundary configuration fixed to $\sigma_a$ is not less than that fixed to $\sigma_b$.
-The word ``better'' means the best solution with boundary configuration $\sigma_a$ is never worse than that with $\sigma_b$.
-When Eq.
-\ref{eq:compress} holds, It is easy to see that if $\sigma_b \cup \overline{\sigma_b}$ is one of the solutions for maximum independant sets in $G$, $\sigma_a \cup \overline{\sigma_b}$ is also a solution.
-With this observation, it is safe to set $A_{\sigma_b}$ to tropical zero.
-We call this property the \textit{least restrictive rule}, that is,
+where $\leq^\circ$ is the Hadamard less or equal operations.
+We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
+\begin{align}
+(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}.
+\end{align}
+If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranted to give the same maximum independant set size.
+It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compressrule} (a) and (b).
+If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independant sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
+Hence, we can set $A_{\sigma_b}$ to tropical zero safely.
+We name this entry elimination principle as the \textit{least restrictive principle}, that is,
 among boundary configurations with equal local maximum independent sizes,
@@
     \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
-    \caption{Two configurations with same local independent size $v_a = v_b = 3$ and different boundary configurations (a) ${001}$ and (b) ${101}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compressrule}
+    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compressrule}
 \end{figure}
@@
 \begin{theorem}
-    A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be further reduces.
+    We denote a tensors $A$ as MIS-compact if are no two nonzero entries of it that one is ``better'' than another.
+    A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be removed without accessing global information.
 \end{theorem}
@@
 \begin{proof}
-    Let us prove it by showing any nonzero entry in a MIS-compact tropical tensor can be the only solution of maximum independent set under a certan exterior graph configuration.
-    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma} = k$, where $\sigma$ is the bounary configuration.
-    Construct a graph $G$ such that for a $v \in C$, if $\sigma_v=1$, $\alpha(N[v] \cap (G \backslash R)) = 0$, otherwise, $\alpha(N[v] \cap (G\backslash R)) = \infty$.
+    %Given $A_\{\sigma_a}$ is better than $A_\{\sigma_b\}$, any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
+    Let use prove it by showing $\forall \sigma$ in a MIS-compact tropical tensor for a subgraph $R$, there exists a graph $G$ that $R\subseteq G$ and $\sigma$ is the only boundary configuration that produces the maximum independent set.
+    i.e. no tensor entry can be removed without knowledge about $G\backslash R$.
+    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the bounary configuration.
+    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, $\alpha(N[v] \cap (G \backslash R)) = 0$, otherwise, $\alpha(N[v] \cap (G\backslash R)) = \infty$, meanwhile, for any $v, w \in C$, $N[v]\cap N[w] = \emptyset$.
     The simplest construction is connecting vertices that $\sigma_v=0$ with infinite many mutually disconnected vertices as illustrated in the following graph.
@@
 
-    Then we have $\alpha(G) = \infty (|C|-|\sigma|) + k$. If there exists another configuration $\tau$ that generating the same good result, then $\tau \prec \sigma$,
-    otherwise it will suffer from infinite punishment from $G\backslash R$.
-    Since this tropical tensor is MIS-compact, it is not possible to find a such $\tau$ that $A_\tau \geq k$, otherwise $\sigma$ will be remove by the \textit{least restrictive rule}.
+    Then we have the maximum independent set size with boundary configuration $\sigma$ being $\alpha(G,\sigma) = \infty (|C|-|\sigma|) + A_{\sigma}$,
+    where $|\sigma|$ is defined as the number of $1$s in $\sigma$.
+    Let us assume there exists another configuration $\tau$ that generating the same or even better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
+    Then we have $\tau \prec \sigma$, otherwise it will suffer from infinite punishment from $G\backslash R$.
+    For such a $\tau$, we have $A_\tau < A_\sigma$, otherwise $A_\sigma \prec A_\tau$ contradicts with $A$ being MIS-compact.
+    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} < \alpha(G,\sigma)$, which contradicts with our preassumtion.
+Such $\tau$ does not exist and $\sigma$ is the only boundary configuration that $\alpha(G) = \alpha(G, \sigma)$.
 \end{proof}
@@
 \subsection{The tensor network compression detects branching rules automatically}
-In the following, we are going to show \textit{local maximum rule} and \textit{least restrictive rule} can automatically discover branching rules and use it for compressing tensor elements,
-i.e. sparse tropical tensor network can not be worse than branching in truncating the search space.
+In the following, we are going to show tropical tensor networks with least restrictive principle can automatically discover branching rules.
+We denote the effective branching number of contracting the local degrees of freedoms as $|T_S|_{\neq -\infty}/2^{|S|}$, where $|\cdot|_{\neq -\infty}$ is the number of nonzero elements in a tropical tensor.
 
@@
 since clique has at most one node in the MIS, the tensor compression will eliminate this solution by moving the occuppied node to the interior.
-Hence, the \textit{least restrictive rule} captures the mirror rule.
+Hence, the \textit{least restrictive principle} captures the mirror rule.
 

### 2021-06-15 paper/paper.tex
new data and new introduction

@@
 Exact algorithms that solves the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
+Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $2^{tw(G)}$.
+
+\section{A short introduction to einsum networks}
+
+The word ``einsum'' is a shorthand for Einstein's summation, but it is actually invented by a group of programmers.
+Einstein's notation is originally proposed as a generalization to of multiplication between two matrices to the contraction between multiple tensors.
+Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$,
+or $C_i^k = A_i^j B_j^k$ in the Einstein's original notation, where the paired subscript and superscript $j$ is a dummy index summed over.
+An example of tensor networks is $C_i^l = A_{ij}^k B^l_k V^j$.
+One can map a tensor network to a muti-graph with open edges by viewing a tensor in the expression on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining labels as open edges.
+This is because a label in a tensor network representation always appear exactly twice.
+
+\centerline{\begin{tikzpicture}
+    \def\dx{0};
+    \def\r{0.25}
+    \def\ax{0}
+    \def\ay{0}
+    \def\bx{1}
+    \def\by{1}
+    \def\cx{1}
+    \def\cy{-1}
+    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
+    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
+    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
+    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
+    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
+    \draw [black,thick] (\ax+\dx,\ay) -- (\cx+\dx,\cy);
+    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.6,\ay);
+    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.6,\by);
+    \node[color=white] at (\ax+\dx,\ax) {A};
+    \node[color=white] at (\bx+\dx,\by) {B};
+    \node[color=white] at (\cx+\dx,\cy) {V};
+\end{tikzpicture}}
+
+Numpy programmers make a generalization to this notation by not restricting the number of times a label is used by tensors.
+For example, $C_{ijk} = A_{jkm} B_{mia} V_{jm}$ is a elgal einsum representation, all indices not appearing in the output are summed over, i.e.
+it represents $C_{ijki} = \sum_{ma}A_{jkm} B_{mia} V_{jm}$.
+Whether the index appear as a superscript or a subscript makes no sense now.
+The graphical representation of an einsum is called a hypergraph, where an edge can be shared by any number of nodes.
+
+\centerline{\begin{tikzpicture}
+    \def\dx{0};
+    \def\r{0.25}
+    \def\ax{0}
+    \def\ay{0}
+    \def\bx{1}
+    \def\by{1}
+    \def\cx{1}
+    \def\cy{-1}
+    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
+    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
+    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
+    \draw[color=blue,thick] (\bx+\dx,\by) circle [radius=\r+0.1];
+    \node[color=blue] at (\bx+\dx-0.6,\bx) {i};
+    \draw[color=cyan,dashed,thick] (\bx+\dx,\by) circle [radius=\r+0.25];
+    \node[color=cyan] at (\bx+\dx+0.5,\bx-0.5) {a};
+    \draw[color=violet,thick,dashed] (\ax+\dx,\ay) circle [radius=\r+0.1];
+    \node[color=violet] at (\ax+\dx+0.4,-0.4) {k};
+    \draw[color=black,thick] (0.5+\dx,0) circle [radius=1.7];
+    \node[color=black] at (0.5+\dx-1.9,0) {m};
+    \draw[color=red,thick,rotate=135,dashed] (-0.6,0) ellipse (1.2 and 0.5);
+    \node[color=red] at (\ax+\dx,-1.0) {j};
+    \node[color=white] at (\ax+\dx,\ax) {A};
+    \node[color=white] at (\bx+\dx,\by) {B};
+    \node[color=white] at (\cx+\dx,\cy) {V};
+\end{tikzpicture}}
+
+In the main text, we stick to the einsum notation, although to most physicists, they are more familiar with tensor networks,
+and an einsum network can be translated to an equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
+We do not use the language of tensor network because it can sometime increase the contraction complexity of a graph. We will show an example in the appendix.
 
@@
 Hence, we can set $A_{\sigma_b}$ to tropical zero safely.
-We name this entry elimination principle as the \textit{least restrictive principle}, that is,
-among boundary configurations with equal local maximum independent sizes,
-we only retain those least restrictive (less ones at the boundary) to exterial configurations.
+%among boundary configurations with equal local maximum independent sizes,
+%we only retain those least restrictive (less ones at the boundary) to exterial configurations.
 
@@
 If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
-since clique has at most one node in the MIS, the tensor compression will eliminate this solution by moving the occuppied node to the interior.
-Hence, the \textit{least restrictive principle} captures the mirror rule.
+since clique has at most one node in the MIS, by moving the occuppied node to the interior, we obtain a ``better'' solution.
+%Hence, the \textit{least restrictive principle} captures the mirror rule.
 

### 2021-06-16 paper/paper.tex
new data

@@
     \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
-    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
-    \draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
+    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
+    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
+    \draw [black,thick] (\ax+\dx,\ay) -- (\bx+\dx,\by);
     \draw [black,thick] (\ax+\dx,\ay) -- (\cx+\dx,\cy);
-    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.6,\ay);
-    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.6,\by);
+    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.8,\ay);
+    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.8,\by);
     \node[color=white] at (\ax+\dx,\ax) {A};
     \node[color=white] at (\bx+\dx,\by) {B};
+    \node[color=black] at (0.5*\ax+0.5*\bx-0.2+\dx,0.5*\ay+0.5\by+0.2) {k};
+    \node[color=black] at (0.5*\ax+0.5*\cx+\dx+0.2,0.5*\ay+0.5\cy+0.2) {j};
+    \node[color=black] at (\ax+\dx-0.5,\ay-0.2) {i};
+    \node[color=black] at (\bx+\dx+0.5,\by-0.2) {l};
     \node[color=white] at (\cx+\dx,\cy) {V};
@@
 In the following, we are going to show tropical tensor networks with least restrictive principle can automatically discover branching rules.
-We denote the effective branching number of contracting the local degrees of freedoms as $|T_S|_{\neq -\infty}/2^{|S|}$, where $|\cdot|_{\neq -\infty}$ is the number of nonzero elements in a tropical tensor.
+We denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
+It is the effective degree of freedoms per vertex in $R$.
 

### 2021-06-16 benchmarks/independence_polynomial.jl

@@ -26,7 +26,7 @@ function run_benchmarks(cases; output_file)
         times[k] = minimum(res[case].times)
     end
 
-    println("Writing benchmark results to file: $output_file.")
+    println("Writing benchmark results to file: $output_file")
     mkpath(dirname(output_file))
     writedlm(output_file, times)
 end

### 2021-06-16 paper/paper.tex
update

@@
 \usepackage[framemethod=TikZ]{mdframed}
+\usetikzlibrary{shapes}
 \usepackage{wrapfig}
@@
 \section{Introduction}
-Exact algorithms that solves the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
+Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
 Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $2^{tw(G)}$.
@@
 
-The word ``einsum'' is a shorthand for Einstein's summation, but it is actually invented by a group of programmers.
+The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
 Einstein's notation is originally proposed as a generalization to of multiplication between two matrices to the contraction between multiple tensors.
-Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$,
-or $C_i^k = A_i^j B_j^k$ in the Einstein's original notation, where the paired subscript and superscript $j$ is a dummy index summed over.
+Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
+It is denoted as $C_i^k = A_i^j B_j^k$ in the Einstein's original notation, where the paired subscript and superscript $j$ is a dummy index summed over.
 An example of tensor networks is $C_i^l = A_{ij}^k B^l_k V^j$.
 One can map a tensor network to a muti-graph with open edges by viewing a tensor in the expression on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining labels as open edges.
-This is because a label in a tensor network representation always appear exactly twice.
+We get the graphical notation as the following.
 
@@
 
+One can easily check a label in a tensor network representation appears precisely twice.
 Numpy programmers make a generalization to this notation by not restricting the number of times a label is used by tensors.
-For example, $C_{ijk} = A_{jkm} B_{mia} V_{jm}$ is a elgal einsum representation, all indices not appearing in the output are summed over, i.e.
-it represents $C_{ijki} = \sum_{ma}A_{jkm} B_{mia} V_{jm}$.
+For example, $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum but not a tensor network.
+Here, all indices not appearing in the output are summed over, i.e.
+it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
 Whether the index appear as a superscript or a subscript makes no sense now.
-The graphical representation of an einsum is called a hypergraph, where an edge can be shared by any number of nodes.
+The graphical representation of an einsum is a hypergraph, where an edge can be shared by a arbituary number of nodes.
 
@@
     \draw[color=cyan,dashed,thick] (\bx+\dx,\by) circle [radius=\r+0.25];
-    \node[color=cyan] at (\bx+\dx+0.5,\bx-0.5) {a};
+    \node[color=cyan] at (\bx+\dx+0.5,\bx-0.5) {l};
     \draw[color=violet,thick,dashed] (\ax+\dx,\ay) circle [radius=\r+0.1];
@@
 
-In the main text, we stick to the einsum notation, although to most physicists, they are more familiar with tensor networks,
-and an einsum network can be translated to an equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
+In the main text, we stick to the einsum notation rather than the tensor network notation,
+although one can easily translate an einsum network to the equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
 We do not use the language of tensor network because it can sometime increase the contraction complexity of a graph. We will show an example in the appendix.
@@
 \section{Independence polynomial}
-The independence polynomial~\cite{Ferrin2014, Harvey2017} of a graph $G$ is defined as
-\begin{equation}
-I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-\blue{here, I preassumed a user knows tensor network, add more details later.}
+\begin{figure*}[h!]
+    \centerline{\begin{tikzpicture}
+        \def\dx{0};
+        \def\r{0.25}
+        \filldraw[fill=black] (\dx,0) circle [radius=\r];
+        \filldraw[fill=black] (\dx,1.5) circle [radius=\r];
+        \filldraw[fill=black] (1.5+\dx,0) circle [radius=\r];
+        \filldraw[fill=black] (1.5+\dx,1.5) circle [radius=\r];
+        \filldraw[fill=black] (2.5+\dx,2.5) circle [radius=\r];
+        \draw [black,thick] (\dx,0) -- (\dx,1.5);
+        \draw [black,thick] (\dx,0) -- (1.5+\dx,0);
+        \draw [black,thick] (\dx,1.5) -- (1.5+\dx,1.5);
+        \draw [black,thick] (1.5+\dx,0) -- (1.5+\dx,1.5);
+        \draw [black,thick] (1.5+\dx,0) -- (\dx,1.5);
+        \draw [black,thick] (2.5+\dx,2.5) -- (1.5+\dx,1.5);
+        \node[color=white] at (\dx,0) {a};
+        \node[color=white] at (\dx,1.5) {b};
+        \node[color=white] at (1.5+\dx,0) {c};
+        \node[color=white] at (1.5+\dx,1.5) {d};
+        \node[color=white] at (2.5+\dx,2.5) {e};
+        \def\dx{5};
+        \def\r{0.25}
+        \draw [black,thick] (\dx,0) -- (\dx,1.5);
+        \draw [black,thick] (\dx,0) -- (1.5+\dx,0);
+        \draw [black,thick] (\dx,1.5) -- (1.5+\dx,1.5);
+        \draw [black,thick] (1.5+\dx,0) -- (1.5+\dx,1.5);
+        \draw [black,thick] (1.5+\dx,0) -- (\dx,1.5);
+        \draw [black,thick] (2.5+\dx,2.5) -- (1.5+\dx,1.5);
+        \node[color=black,fill=white] at (0.75+\dx,0) {\scriptsize $B$};
+        \node[color=black,fill=white] at (\dx,0.75) {\scriptsize $B$};
+        \node[color=black,fill=white] at (1.5+\dx,0.75) {\scriptsize $B$};
+        \node[color=black,fill=white] at (0.75+\dx,1.5) {\scriptsize $B$};
+        \node[color=black,fill=white] at (0.75+\dx,0.75) {\scriptsize $B$};
+        \node[color=black,fill=white] at (2+\dx,2) {\scriptsize $B$};
+        \node[color=black,fill=white] at (\dx,0) {\scriptsize $W(x_a)$};
+        \node[color=black,fill=white] at (\dx,1.5) {\scriptsize $W(x_b)$};
+        \node[color=black,fill=white] at (1.5+\dx,0) {\scriptsize $W(x_c)$};
+        \node[color=black,fill=white] at (1.5+\dx,1.5) {\scriptsize $W(x_d)$};
+        \node[color=black,fill=white] at (2.5+\dx,2.5) {\scriptsize $W(x_e)$};
+    \end{tikzpicture}}
+    \caption{Mapping a graph to an einsum network.}\label{fig:einsummapping}
+\end{figure*}
+
 Let us map the graph $G$ into an einsum network, as shown in \Fig{fig:einsummapping}, by placing a rank one tensor of size $2$ on vertex $i$
 \begin{equation}
-    W(x)_{s_i} = \left(\begin{matrix}
+    W(x_i)_{s_i} = \left(\begin{matrix}
         1 \\
-        x
+        x_i
     \end{matrix}\right)_{s_i},
@@
 \end{equation}
-where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise.
-The contraction of this einsum network gives the independence polynomial %, we denote this contraction as \texttt{a,b,c,d,ab,ad,bc,bd,cd,ce->}.
+where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise, $x_i$ is a variable.
+We denote the contraction result of this einsum network as
 \begin{equation}
-    I(G, x) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
+    A(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
 \end{equation}
 Here, the einsum runs over all possible vertex configurations and accumulates the product of tensor elements to the output.
-The product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
-while the product over edge tensors provides a factor $0$ for configurations not being an independent set.
-\begin{figure*}[t!]
-    \centering
-    \begin{subfigure}[t]{0.4\textwidth}
-        \centering
-        \centerline{\includegraphics[width=0.8\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig1.pdf}}
-        \caption{}
-    \end{subfigure}%
-    ~
-    \begin{subfigure}[t]{0.4\textwidth}
-        \centering
-    \centerline{\includegraphics[width=0.8\columnwidth,trim={0 0cm 0 0},clip]{../notebooks/fig2.pdf}}
-        \caption{}
-    \end{subfigure}
-    \caption{Mapping a graph to an einsum network.}\label{fig:einsummapping}
-\end{figure*}
-With this einsum network representation, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+Let $x_i = x$ be the same variable, then the product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
+and the product over edge tensors provides a factor $0$ for configurations not being an independent set.
+The contraction of this einsum network gives the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$
+\begin{equation}
+I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
+By mapping the independence polynomial solving problem to the einsum network contraction, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
 where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
@@
 Please checkout our Github repository \href{https://github.com/Happy-Diode/NoteOnTropicalMIS}{https://github.com/Happy-Diode/NoteOnTropicalMIS}.
+
+\section{When tensor network is worse than einsum network}\label{app:tensorbad}
+
+Given a graph
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.2}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+\end{tikzpicture}}
+
+Its tensor network representation is
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.1}
+    \def\a{0.1}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
+            \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
+            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+\end{tikzpicture}}
+
+Its einsum network representation is
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.1}
+    \def\a{0.1}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+        \node[fill, regular polygon, 
+            regular polygon sides=3, scale=0.5] at (\x, \y) {};
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
+            \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
+            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+\end{tikzpicture}}
+
 \end{document}

### 2021-06-16 paper/paper.tex
save

@@
     \end{cases},\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma + \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
     \mymathbb{0} &= \{\}\infty^{-\infty},\\
@@
 \end{align}
-where $\vee$ is the bit-wise \texttt{or}. One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
+One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
 We first initialize the bit strings of the variable $x$ in the vertex tensor to a vertex index $i$ dependent onehot vector $x_i = \boldsymbol{e}_{i}$,
@@
 \end{align}
-where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard multiplication, boolean false is treated as tropical zero and boolean true is treated as tropical one.
+where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard product, boolean false is treated as tropical zero and boolean true is treated as tropical one.
 This rule defined on matrix multiplication can be easily generalized to the einsum of two tensors by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum.
@@
 
-\iffalse
-\begin{align}
-if |V| = 0 then
-return 0
-if \exists v \in V with d(v) \leq 1 then
-return 1 + mis2(G \backslash N[v])
-if \exists v \in V with d(v) = 2 then
-(let u 1 and u 2 be the neighbors of v)
-if {u 1 , u 2 } \in E then
-return 1 + mis2(G \backslash N[v])
-if {u 1 , u 2 } \in
-/ E then
-if |N 2 (v)| = 1 then
-(let N 2 (v) = {w})
-return max(2 + mis2(G \backslash (N 2 [v] \cup N[w])), 2 + mis2(G \backslash N 2 [v]))
-if |N 2 (v)| > 1 then
-return max(mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
-if \exists v \in V with d(v) = 3 then
-(let u 1 u 2 and u 3 be the neighbors of v)
-if G[N(v)] has no edge then
-if v has a mirror then
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup {v}))
-if v has no mirror then
-return max(1 + mis2(G \backslash N[v]), 2 + mis2(G \backslash N[{u 1 , u 2 }]), 2 + mis2(G \backslash
-(N[{u_1 , u_3 }] \cup \{u_2\})), 2 + mis2(G \backslash (N[{u_2 , u_3 }] \cup \{1\})))
-if G[N(v)] has one or two edges then
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup cup))
-if G[N(v)] has three edges then
-return 1 + mis2(G \backslash N[v])
-if \Delta (G) \geq 6 then
-choose a vertex v of maximum degree in G
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash v))
-if G is disconnected then
-(let C \subseteq V be a component of G)
-return mis2(G[C]) + mis2(G \backslash C)
-if G is 4 or 5-regular then
-choose any vertex v of G
-return max(1 + mis2(G \backslash N[v]), mis2(G \backslash (M(v) \cup \{v\}))
-if \Delta (G) = 5 and \delta (G) = 4 then
-choose adjacent vertices v and w with d(v) = 5 and d(w) = 4 in G
-return
-\max(1 + mis2(G \backslash N[v]), 1 + mis2(G \backslash (\{v\} \cup M(v) \cup N[w])), mis2(G \backslash (M(v) \cup \{v, w\})))
-\end{align}
-\fi
-
 \bibliographystyle{iclr2021_conference}
@@
     \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}
+        \foreach \y in {1,...,5}{
         \node[fill, regular polygon, 
-            regular polygon sides=3, scale=0.5] at (\x, \y) {};
+            regular polygon sides=3, scale=0.3, rotate=90] at (\x+0.1, \y+0.2) {};
+        \draw [black,thick] (\x,\y) -- (\x+0.1,\y+0.2);
+        }
     \foreach \x in {1,...,5}

### 2021-06-16 paper/paper.tex
update

@@
     \def\r{0.1}
-    \def\a{0.1}
+    \def\a{0.07}
+    \def\L{0.6}
+    \def\l{0.1}
     \foreach \x in {1,...,5}
@@
         \node[fill, regular polygon, 
-            regular polygon sides=3, scale=0.3, rotate=90] at (\x+0.1, \y+0.2) {};
-        \draw [black,thick] (\x,\y) -- (\x+0.1,\y+0.2);
+            regular polygon sides=3, scale=0.3] at (\x, \y) {};
         }
     \foreach \x in {1,...,5}
-        \foreach \y in {1,...,4}{
+        \foreach \y in {1,...,5}{
+            \ifnum \y < 5
                 \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
                 \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
-            \draw [black,thick] (\x,\y) -- (\x,\y+1);
-            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+            \fi
+            \filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l,\y+\l) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
         }
@@
             \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
-            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
-            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
         }

### 2021-07-25 paper/paper.tex
update paper
clique counting

@@
 \documentclass{article}
-\usepackage{iclr2021_conference}
+%\usepackage{iclr2021_conference}
+\usepackage{natbib}
 %\documentclass[a4paper,superscriptaddress,11pt]{article}
@@
 
+\makeatletter
+\def\parsept#1#2#3{%
+    \def\nospace##1{\zap@space##1 \@empty}%
+    \def\rawparsept(##1,##2){%
+        \edef#1{\nospace{##1}}%
+        \edef#2{\nospace{##2}}%
+    }%
+    \expandafter\rawparsept#3%
+}
+\makeatother
 \DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
@@
 
-\iclrfinalcopy
+%\iclrfinalcopy
 \begin{document}
@@
 
-\author{Jin-Guo Liu\\
-Harvard University\\
-\texttt{jinguoliu@g.harvard.edu}\\
-\AND
-Xun Gao\\
-Harvard University\\
-\texttt{xungao@g.harvard.edu}\\
-}
+%\author{Jin-Guo Liu\\
+%Harvard University\\
+%\texttt{jinguoliu@g.harvard.edu}\\
+%\AND
+%Xun Gao\\
+%Harvard University\\
+%\texttt{xungao@g.harvard.edu}\\
+%}
 \maketitle
@@
 \section{Introduction}
+MIS problem is hard~\cite{Hastad1996}.
 Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
 Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $2^{tw(G)}$.
+A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
+A set is independent if and only if its complement is a vertex cover.[4] Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
 
@@
 We leave this as an exercise for readers.
+This algorithm is parallelizable.
 
@@
 where $\leq^\circ$ is the Hadamard less or equal operations.
-We say an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
+
+\begin{definition}
+A tensors $A$ is \textit{MIS-compact} if are no two nonzero entries of it that one is ``better'' than another,
+where an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
 \begin{align}
-(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b}),\label{eq:compress}.
+(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compress}.
 \end{align}
+\end{definition}
+
 If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranted to give the same maximum independant set size.
@@
 \begin{theorem}
-    We denote a tensors $A$ as MIS-compact if are no two nonzero entries of it that one is ``better'' than another.
     A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be removed without accessing global information.
@@
 
+\subsection{gadget design}
+
+Suppose we have a local structure as the following.
+
+\centerline{\begin{tikzpicture}[scale=1.0]
+    \def\r{0.2}
+    \foreach \x/\y [count=\i] in {0.17/0.5,0.83/0.5,0.5/0.67,0.5/0.33}
+        \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+    \draw (1) -- (2);
+    \draw (3) -- (4);
+\end{tikzpicture}}
+
+Contract this local structure gives the tropical tensor
+
+\begin{align}
+    \left(\begin{matrix}
+        \left(\begin{matrix}
+            ~~~~0 & ~~~~1\\
+            ~~~~1 & ~~~~2
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~1 & -\infty\\
+            ~~~~2 & -\infty
+        \end{matrix}\right) \\
+        \left(\begin{matrix}
+            ~~~~1 & ~~~~2\\
+            -\infty & -\infty
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~2 & -\infty\\
+            -\infty & -\infty
+        \end{matrix}\right)
+    \end{matrix}\right).
+\end{align}
+
+The following gadget is equivalent to the above diagram up to a constant $2$.
+
+\centerline{\begin{tikzpicture}
+    \def\nodes{(0.5, 0.33), (0.17, 0.5), (0.5, 0.67), (0.83, 0.5), (0.32, 0.44), (0.44, 0.44), (0.56, 0.44), (0.68, 0.44), (0.32, 0.56), (0.44, 0.56), (0.56, 0.56), (0.68, 0.56)}
+    \def\edges{(1, 5), (1, 6), (1, 7), (1, 8), (2, 5), (2, 9), (3, 9), (3, 10), (3, 11), (3, 12), (4, 8), (4, 12), (5, 6), (5, 9), (5, 10), (6, 7), (6, 9), (6, 10), (6, 11), (7, 8), (7, 10), (7, 11), (7, 12), (8, 11), (8, 12), (9, 10), (10, 11), (11, 12)}
+    \def\r{0.2}
+    \foreach \p [count=\i] in \nodes{
+        \parsept{\x}{\y}{\p}
+        \pgfmathparse{((\x<0.2 || \x>0.8 || \y<0.35 || \y>0.65) ? 1 : 0)}
+        \ifnum\pgfmathresult>0
+            \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+        \else
+            \node[fill,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+        \fi
+    }
+    \foreach \e [count=\i] in \edges{
+        \parsept{\x}{\y}{\e}
+        \draw (\x) -- (\y);
+    }
+\end{tikzpicture}}
+
+\begin{align}
+    \left(\begin{matrix}
+        \left(\begin{matrix}
+            ~~~~2 & ~~~~3\\
+            ~~~~3 & ~~~~4
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~3 & ~~~~3\\
+            ~~~~4 & ~~~~4
+        \end{matrix}\right) \\
+        \left(\begin{matrix}
+            ~~~~3 & ~~~~4\\
+            ~~~~2 & ~~~~3
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~4 & ~~~~4\\
+            ~~~~3 & ~~~~4
+        \end{matrix}\right)
+    \end{matrix}\right)
+    \xrightarrow[\text{compress, -2}]{}
+    \left(\begin{matrix}
+        \left(\begin{matrix}
+            ~~~~0 & ~~~~1\\
+            ~~~~1 & ~~~~2
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~1 & -\infty\\
+            ~~~~2 & -\infty
+        \end{matrix}\right) \\
+        \left(\begin{matrix}
+            ~~~~1 & ~~~~2\\
+            -\infty & -\infty
+        \end{matrix}\right) &
+        \left(\begin{matrix}
+            ~~~~2 & -\infty\\
+            -\infty & -\infty
+        \end{matrix}\right)
+    \end{matrix}\right)
+\end{align}
+
+We can
+
+\section{benchmarks}
+We run a sequetial program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results bellow.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.8\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{benchmark.pdf}
+    \caption{Benchmark results for computing different properties with different element types.
+    }\label{fig:benchmark}
+\end{figure}
+
 \section{discussion}
@@
 
+Once we represent a $\delta$ tensor as a general tensor, the complexity of this contraction is $\approx 2^{2L}$.
 Its einsum network representation is
@@
     \def\l{0.1}
+    \def\sql{0.24}
     \foreach \x in {1,...,5}

### 2021-07-25 project/maximal.jl

@@ -1,0 +1,6 @@
+using NoteOnTropicalMIS, Polynomials, Random, OMEinsum, FFTW
+
+Random.seed!(2)
+g = diagonal_coupled_graph(rand(13,13) .<= 0.8)
+@time maximal_polynomial(Val(:fft), g; sc_target=24, imbalances=0.0:0.00151:1.0, max_group_size=50)
+@time maximal_polynomial(Val(:polynomial), g; sc_target=19, imbalances=0.0:0.00151:1.0, max_group_size=50)

### 2021-07-25 src/configurations.jl

@@ -27,7 +27,17 @@ end
 Base.zero(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}(StaticBitVector{N,C}[])
 Base.one(::Type{ConfigEnumerator{N,C}}) where {N,C} = ConfigEnumerator{N,C}([TropicalNumbers.staticfalses(StaticBitVector{N,C})])
 
-symbols(::EinCode{ixs}) where ixs = unique(Iterators.flatten(filter(x->length(x)==1,ixs)))
+function symbols(::EinCode{ixs}) where ixs
+    res = []
+    for ix in ixs
+        for l in ix
+            if l ∉ res
+                push!(res, l)
+            end
+        end
+    end
+    return res
+end
 
 function mis_config(code; all=false, bounding=true, usecuda=false)
     if all && usecuda

### 2021-07-25 src/demos.jl

@@ -1,32 +1,22 @@
-export case_r3, case_dc, run_task
+export case_r3, case_dc, run_task, suboptimal_counting
 
 using Random
 
 function case_r3(n, k=3; sc_target, seed=2)
     # generate a random regular graph of size 100, degree 3
     graph = (Random.seed!(seed); LightGraphs.random_regular_graph(n, k))
-    # generate einsum code, i.e. the labels of tensors
-    code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # labels for edge tensors
-                    [(i,) for i in LightGraphs.vertices(graph)]...), ())        # labels for vertex tensors
-    size_dict = Dict([s=>2 for s in symbols(code)])
     # optimize the contraction order using KaHyPar + Greedy
-    optimized_code = optimize_kahypar(code, size_dict; sc_target=sc_target, max_group_size=40)
-    println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
-    return optimized_code
+    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40)
+    return optcode
 end
 
 function case_dc(L::Int, ρ; sc_target, seed=2)
     # generate a random regular graph of size 100, degree 3
     Random.seed!(seed)
     graph = diagonal_coupled_graph(rand(L, L) .< ρ)
-    # generate einsum code, i.e. the labels of tensors
-    code = EinCode(([minmax(e.src,e.dst) for e in LightGraphs.edges(graph)]..., # labels for edge tensors
-                    [(i,) for i in LightGraphs.vertices(graph)]...), ())        # labels for vertex tensors
-    size_dict = Dict([s=>2 for s in symbols(code)])
     # optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
-    optimized_code = optimize_kahypar(code, size_dict; sc_target=sc_target, max_group_size=40)
-    println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
-    return optimized_code
+    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40)
+    return optcode
 end
 
 
@@ -46,7 +36,7 @@ end
     * `:config_all`, all MIS configurations,
     * `:config_all_bounded`, all MIS configurations, the bounded approach (much faster),
 """
[…]

### 2021-07-26 paper/paper.tex
computing maximal

@@
 
+\section{Counting maximal independent sets}
+Let us denote the neighbor of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent sets that there is no such vertex $v$ that $N[v] \cap I_m = \emptyset$.
+Let us modify the einsum network for computing independence polynomial to count maximal independent sets.
+We define a tensor on $N[v]$ to capture this property
+\begin{align}
+    T(x)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+        s_vx & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
+        1-s_v& otherwise.\\
+    \end{cases}
+\end{align}
+As an example, for a vertex of degree 2, the resulting rank 3 tensor is
+\begin{align}
+    T(x)=\left(\begin{matrix}
+    \left(\begin{matrix}
+        0 &1 \\
+        1 &1
+    \end{matrix}\right)\\
+    \left(\begin{matrix}
+        x &0 \\
+        0 &0
+    \end{matrix}\right)
+    \end{matrix}\right).
+\end{align}
+
+We do the same computation as independence polynoimal, the coefficients of resulting polynomial gives the counting of maximal independent sets.
+In many sparse graphs, this tensor network contraction approach is much faster than computing the maximal cliques of its complement and use Bron Kerbosch algorithms for finding maximum cliques.
+However, the treewidth of this new tensor network is larger than the one for independence polynomial because it can not utilize some structures of the original graph,
+while the original tensor network can be trivially reduced to this one.
+We will use an example in the appendix to show why this tensor network is harder to contract.
+
 \section{Automated branching}

### 2021-07-26 src/demos.jl

@@ -19,6 +19,14 @@ function case_dc(L::Int, ρ; sc_target, seed=2)
     return optcode
 end
 
+function case_sq(L::Int, ρ; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    Random.seed!(seed)
+    graph = square_lattice_graph(rand(L, L) .< ρ)
+    # optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40)
+    return optcode
+end
 
 """
     run_task(code, task; usecuda=false)

### 2021-07-26 src/graphs.jl

@@ -1,6 +1,7 @@
 using LightGraphs, OMEinsumContractionOrders
 export random_regular_graph, diagonal_coupled_graph, isindependentset
 export random_regular_eincode, random_diagonal_coupled_eincode, diagonal_coupled_eincode
+export square_lattice_graph
 
 isindependentset(g, v) = !any(e->v[e.src] == 1 && v[e.dst] == 1, edges(g))
 
@@ -11,6 +12,11 @@ end
 function OMEinsum.EinCode(g::SimpleGraph; outputs=())
 	ixs = [minmax(e.src,e.dst) for e in LightGraphs.edges(g)]
 	return EinCode((ixs..., [(i,) for i in LightGraphs.vertices(g)]...), outputs)
+end
+
+function square_lattice_graph(mask::AbstractMatrix{Bool})
+    locs = [(i, j) for i=1:size(mask, 1), j=1:size(mask, 2) if mask[i,j]]
+    unitdisk_graph(locs, 1.1)
 end
 
 function random_diagonal_coupled_graph(m::Int, n::Int, ρ::Real)

### 2021-07-29 paper/paper.tex
switch to SIAM

@@
-%\documentclass[aps,twocolumn,longbibliography,english,superscriptaddress]{revtex4-1}
-\documentclass{article}
-%\usepackage{iclr2021_conference}
-\usepackage{natbib}
-%\documentclass[a4paper,superscriptaddress,11pt]{article}
+\documentclass[review,onefignum,onetabnum]{siamart190516}
+%\usepackage{natbib}
 \pdfoutput=1
-\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage[english]{babel}
@@
 %\usepackage{caption}
-%\usepackage[plain]{algorithm}
-\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
+%\usepackage[plain]{algorithmic}
+\usepackage[linesnumbered, ruled, vlined, algo2e]{algorithm2e}
 \usepackage{algpseudocode}
@@
 \usepackage{graphicx}
-\usepackage{amsmath,color,amsthm}
+\usepackage{amsmath,color}
 \usepackage{mathrsfs}
@@
 \newcommand{\Tr}{{\rm Tr}}
-\renewcommand{\cite}[1]{{\citep{#1}}}
 \newcommand{\etc}{{\it etc~}}
@@
 
-\newtheorem{theorem}{\textit{Theorem}}
-\newtheorem{corollary}{\textit Branching Rule}
-\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
+%\newtheorem{theorem}{\textit{Theorem}}
+%\newtheorem{corollary}{\textit Branching Rule}
+%\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
+%\newtheorem{defin}[thm]{Definition}
 
@@
 
-%\iclrfinalcopy
+%\externaldocument{ex_supplement}
+
+\title{Solving the maximum independant set problem by generic programming einsum networks
+\thanks{\funding{...}}
+}
+
+\author{XXX\thanks{XXX 
+  (\email{email}, \url{website}).}
+\and YYY\thanks{yyyyy 
+  (\email{yyyy}, \email{email}).}
+}
+
 \begin{document}
-\title{Solving the maximum independant set problem by generic programming einsum networks}
-
-%\author{Jin-Guo Liu\\
-%Harvard University\\
-%\texttt{jinguoliu@g.harvard.edu}\\
-%\AND
-%Xun Gao\\
-%Harvard University\\
-%\texttt{xungao@g.harvard.edu}\\
-%}
+
 \maketitle
@@
 	Solving the maximum independent set size problem by mapping the graph to an einsum network. 
-    By contracting the einsum network with generic element types, we show how to obtain the maximum independent set size,
-    the independence polynomial and optimal configurations.
+    We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
 \end{abstract}
@@
 A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
-A set is independent if and only if its complement is a vertex cover.[4] Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
-
-\section{A short introduction to einsum networks}
-
+A set is independent if and only if its complement is a vertex cover.
+Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
+It is related to hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
+
+In this work, we attack this problem by mapping it to an ``einsum'' network.
 The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
@@
     Let $P = 1$, vector $X = (0,1,2,\ldots,m)$, matrix $\hat X_{ij} = X_i^j$, where $i,j = 0, 1, \ldots m$\;
+
     \While{true}{
         compute the largest prime $p$ that $\gcd(p, P) = 1 \land p \leq 2^W$\;
+
         compute the tensor network contraction on $GF(p)$ and obtain $Y = (y_0, y_1, \ldots , y_m) \pmod p $\;
+
         $A_p = (a_0, a_1, \ldots, a_m) \pmod p = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+
         $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
+
         \If{$A_P = A_{P \times p}$}{
@@
 
-\begin{theorem}
+\begin{theorem}[]
     A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be removed without accessing global information.
@@
 
-\bibliographystyle{iclr2021_conference}
+\bibliographystyle{siamplain}
 \bibliography{refs}

### 2021-07-29 paper/siamart_190516/docsiamart.tex
switch to SIAM

\documentclass[final,onefignum,onetabnum]{siamart190516}

%% ------------------------------------------------------------------
%% Code used in examples, needed to reproduce 
%% ------------------------------------------------------------------
%% Used for \set, used in an example below
\usepackage{braket,amsfonts}

%% Used in table example below
\usepackage{array}

%% Used in table and figure examples below
\usepackage[caption=false]{subfig}
%% Used for papers with subtables created with the subfig package
\captionsetup[subtable]{position=bottom}
\captionsetup[table]{position=bottom}

%% Used for PgfPlots example, shown in the "Figures" section below.
\usepackage{pgfplots}

%% Used for creating new theorem and remark environments
\newsiamthm{claim}{Claim}
\newsiamremark{remark}{Remark}
\newsiamremark{hypothesis}{Hypothesis}
\crefname{hypothesis}{Hypothesis}{Hypotheses}

%% Algorithm style, could alternatively use algpseudocode
\usepackage{algorithmic}

%% For figures
\usepackage{graphicx,epstopdf}

%% For referencing line numbers
\Crefname{ALC@unique}{Line}{Lines}

%% For creating math operators
\usepackage{amsopn}
\DeclareMathOperator{\Range}{Range}

%% ------------------------------------------------------------------
%% Macros for in-document examples. These are not meant to reused for
%% SIAM journal papers.
%% ------------------------------------------------------------------
\usepackage{xspace}
\usepackage{bold-extra}
\usepackage[most]{tcolorbox}
\newcommand{\BibTeX}{{\scshape Bib}\TeX\xspace}
\newcounter{example}
\colorlet{texcscolor}{blue!50!black}
\colorlet{texemcolor}{red!70!black}
\colorlet{texpreamble}{red!70!black}
\colorlet{codebackground}{black!25!white!25}

\newcommand\bs{\symbol{'134}} % print backslash in typewriter OT1/T1
\newcommand{\preamble}[2][\small]{\textcolor{texpreamble}{#1\texttt{#2 \emph{\% <- Preamble}}}}

\lstdefinestyle{siamlatex}{%
  style=tcblatex,
  texcsstyle=*\color{texcscolor},
  texcsstyle=[2]\color{texemcolor},
  keywordstyle=[2]\color{texemcolor},
  moretexcs={cref,Cref,maketitle,mathcal,text,headers,email,url},
}

\tcbset{%
  colframe=black!75!white!75,
  coltitle=white,
  colback=codebackground, % bottom/left side
  colbacklower=white, % top/right side
  fonttitle=\bfseries,
  arc=0pt,outer arc=0pt,
  top=1pt,bottom=1pt,left=1mm,right=1mm,middle=1mm,boxsep=1mm,
  leftrule=0.3mm,rightrule=0.3mm,toprule=0.3mm,bottomrule=0.3mm,
  listing options={style=siamlatex}
}

\newtcblisting[use counter=example]{example}[2][]{%
  title={Example~\thetcbcounter: #2},#1}

\newtcbinputlisting[use counter=example]{\examplefile}[3][]{%
  title={Example~\thetcbcounter: #2},listing file={#3},#1}

\DeclareTotalTCBox{\code}{ v O{} }
{ %fontupper=\ttfamily\color{texemcolor},
  fontupper=\ttfamily\color{black},
  nobeforeafter,
  tcbox raise base,
  colback=codebackground,colframe=white,
  top=0pt,bottom=0pt,left=0mm,right=0mm,
  leftrule=0pt,rightrule=0pt,toprule=0mm,bottomrule=0mm,
  boxsep=0.5mm,
  #2}{#1}

% Stretch the pages
\patchcmd\newpage{\vfil}{}{}{}
\flushbottom

%% ------------------------------------------------------------------
%% End of macros for in-document examples. 
%% ------------------------------------------------------------------

%% ------------------------------------------------------------------
%% HEADING INFORMATION
%% ------------------------------------------------------------------
\begin{tcbverbatimwrite}{tmp_\jobname_header.tex}
\title{Guide to Using SIAM's \LaTeX\ Style\thanks{Submitted to the editors DATE.
\funding{Funding information goes here.}}}

\author{Dianne Doe\thanks{Imagination Corp., Chicago, IL (\email{ddoe@imag.com}).}
\and Paul T. Frank\thanks{Department of Applied Math, Fictional University, Boise, ID (\email{ptfrank@fictional.edu}, \email{jesmith@fictional.edu}).}
\and Jane E. Smith\footnotemark[3]}

% Custom SIAM macro to insert headers
\headers{Guide to Using  SIAM'S \LaTeX\ Style}{Dianne Doe, Paul T. Frank, and Jane E. Smith}
\end{tcbverbatimwrite}
\input{tmp_\jobname_header.tex}

% Optional: Set up PDF title and authors
\ifpdf
\hypersetup{ pdftitle={Guide to Using  SIAM'S \LaTeX\ Style} }
\fi

%% ------------------------------------------------------------------
%% END HEADING INFORMATION
%% ------------------------------------------------------------------

%% ------------------------------------------------------------------
%% MAIN Document
%% ------------------------------------------------------------------
\begin{document}
\maketitle

%% ------------------------------------------------------------------
%% ABSTRACT
%% ------------------------------------------------------------------
\begin{tcbverbatimwrite}{tmp_\jobname_abstract.tex}
\begin{abstract}
  Documentation is given for use of the SIAM standard \LaTeX\ and \BibTeX\
  macros.  Instructions and suggestions for compliance with SIAM style
  standards are also included. Familiarity with standard \LaTeX\ commands is assumed.
\end{abstract}

\begin{keywords}
  \LaTeX, \BibTeX, SIAM Journals, Documentation 
\end{keywords}

\begin{AMS}
  00A20 
\end{AMS}
\end{tcbverbatimwrite}
\input{tmp_\jobname_abstract.tex}
%% ------------------------------------------------------------------
%% END HEADER
%% ------------------------------------------------------------------

\section{Introduction}
\label{sec:intro}

This file is documentation for the SIAM \LaTeX\ style, including how
to typeset the main document, the \BibTeX\ file, and any supplementary
material. More information
about SIAM's editorial style can be found in the style manual, available
at \url{https://www.siam.org/journals/pdf/stylemanual.pdf}.
%
The major changes in the SIAM standard class are summarized in \cref{sec:changes}.
%
The SIAM \LaTeX\@ files can be found at
\url{https://www.siam.org/journals/auth-info.php}. The files that
are distributed for the standard macros are given below. 
\begin{itemize}
\item \texttt{siamart190516.cls} (required): Main SIAM standard \LaTeX\ class file.
\item \texttt{siamplain.bst} (required): Bibliographic style file for
  \BibTeX.
\item \texttt{docsiamart.tex}: Produces this documentation.
\item \texttt{references.bib}: \BibTeX\ database for this
  documentation and examples.
\item \texttt{ex\_article.tex}: Template for article.
\item \texttt{ex\_supplement.tex}: Template for supplement.
\item \texttt{ex\_shared.tex}: Template for shared information for
  article and supplement.
\end{itemize}
To use these files, put \texttt{siamart190516.cls} and
\texttt{siamplain.bst} in the directory with your
paper or, alternatively, into your \LaTeX\@ and \BibTeX\@ paths,
respectively. 
%
The outline of a SIAM \LaTeX\ article is shown in
\cref{ex:outline}. Templates are provided and discussed in more detail
in \cref{sec:template}.

\begin{example}[label={ex:outline},listing only,%
  listing options={style=siamlatex,{morekeywords=[1]{maketitle},
      morekeywords=[2]{siamart190516}},}]%
  {Document outline}
\documentclass{siamart190516}
% Preamble consisting of:
% Packages and macro definitions go here.
% Define title, authors, headers here.
\begin{document}
\maketitle
% Other front matter goes here: abstract, keywords, AMS subjects.
% Main body goes here.
% Appendices goes here (optional).
% Acknowledgements go here (optional).
% Bibliography goes here.
\end{document}
\end{example}

\section{Class options}
\label{sec:class-options}

Class options can be included in the bracketed argument of the
command, separated by commas. The possible class options are:
\begin{itemize}
\item \code{review} --- Recommended for submitting your manuscript to
  a SIAM journal.  Adds line numbers as well as the statement ``This
  manuscript is for review purposes only'' to the bottom of each page.
\item \code{final} --- Turns off the black boxes that help authors
  identify lines that are too long. The final published version will
  have this option on.
\item \code{supplement} --- Specifies that the file is a supplement
  and not the main document, causing changes in the appearance of the
  title and numbering; see \cref{sec:supplement} for details.
\item \code{hidelinks} --- Turns off colors on hyperlinks; see
  \cref{sec:cr+hyp}. The hyperlinks still exist, but there is no color
  to differentiate them.
  The final published version will have this option on.
\end{itemize}

\section{Front matter}
\label{sec:front}
The title and author parts are formatted using the standard
\code{\title}, \code{\author}, and \code{\maketitle} commands as
described in Lamport \cite{La86}. The title and author should be
declared in the preamble. The title and author names are automatically
converted to uppercase in the document.
%
If there is more than one author, each additional author should be preceded by
the \code{\and} command.  
%
The addresses and support acknowledgments are added via
\code{\thanks}. Each author's thanks should specify their address.
The support acknowledgment should be put in the title thanks,
unless specific support needs to be specified for individual authors,
in which case it should follow the author address.  
%
The header for this file was produced by the code in \cref{ex:header}, including an
example of a shared footnote. Each thanks produces a footnote, so the
footnote of the second author is \#3.
%
The command
\code{\headers{title}{authors}} command, with
the title (possibly shortened to fit) and the authors' names, creates
the page headers, automatically converted to uppercase.

\examplefile[label={ex:header},listing only,%
listing options={style=siamlatex,%
deletetexcs={and,thanks,title,author},%
{moretexcs=[2]{and,thanks,title,author,maketitle,headers,email}}}
]{Title and authors in preamble}{tmp_\jobname_header.tex}

\newpage
Following the author and title is the abstract, key words listing, and AMS subject
classifications, designated using the \code{abstract}, \code{keywords}, and \code{AMS}
environments. 
Authors are responsible for providing AMS numbers which can be found
on the AMS web site \cite{AMSMSC2010}. The abstract, keywords, and AMS subject classifications
for this document are specified in \cref{ex:abstract}.

\examplefile[label={ex:abstract},%
before upper={\preamble{\bs newcommand\{\bs BibTeX\}\{\{\bs scshape Bib\}\bs TeX\bs xspace\}}},
listing only,%
listing options={style=siamlatex,%
{morekeywords=[2]{abstract,keywords,AMS}}}
]{Abstract, keywords, and AMS classifications}{tmp_\jobname_abstract.tex}

A more complete example, including a PDF supplement, that uses the
included files \texttt{ex\_article.tex}, \texttt{ex\_supplement.tex},
and \texttt{ex\_shared.tex} is discussed in
\cref{sec:template}. The example files can be used as a starting point
for producing a document.

\section{Cross references and hyperlinks}
\label{sec:cr+hyp}

SIAM now supports cross references and hyperlinks via the
\texttt{cleveref} and \texttt{hyperef} packages, which are loaded by
the class file.

\subsection{Cleveref}
\label{sec:cleveref}

SIAM strongly recommends using the commands provided by 
the \texttt{cleveref} package for cross referencing.
The package is automatically loaded and already customized
to adhere to SIAM's style guidelines. 
%
To create a cross reference, use the command \code{\cref} (inside
sentence) or \code{\Cref} (beginning of a sentence) in place of the
object name and \code{\ref}. 
%
The \texttt{cleveref}
package enhances \LaTeX's cross-referencing features, allowing
the format of cross references to be determined automatically
according to the ``type" of cross reference (equation, section, etc.)
and the context in which the cross reference is used.
%
So, the package
\emph{automatically} inserts the object name as well as the
appropriate hyperlink; see \cref{ex:cref}.
It may require two \LaTeX\@ compilations for the references to show up
correctly.
Additional examples are shown in the sections below
for equations, tables, figures, sections, etc.

\begin{example}[label=ex:cref,bicolor,listing options={style=siamlatex,%
{morekeywords=[2]{cref,ref}}}]{Advantage of using cleveref}
The normal way to get a cross reference with a hyperlink requires a
lot of typing: \hyperref[thm:mvt]{Theorem~\ref*{thm:mvt}}.
The \texttt{cleveref} package gets both the name and hyperlink
automatically using a single macro: \cref{thm:mvt}.
It also handles multiple references with the same macro, such as
\cref{thm:mvt,fig:pgfplots,fig:testfig}.
\end{example}

%

%\newpage
\subsection{Hyperef}
\label{sec:hyperef}

Hyperlinks are created with the \code{\href} and \code{\url} commands,
as shown in \cref{ex:href}.
SIAM has also defined the \code{\email} command, as shown in
\cref{ex:header}.
You can hide links (i.e., turn off link colors) with the \code{hidelinks} option.

\begin{example}[label={ex:href},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{href,url}}}]{Creating hyperlinks}
The \href{https://www.siam.org}{SIAM homepage} has general information.
Note that the colored text will \emph{not} appear in the print version
nor will the hyperlink be active, so the writer may want to specify
the location explicitly instead by using \url{https://www.siam.org}.
\end{example}

Note that homepage links via \code{\url} in the \code{\thanks} environment require
special formatting for the tilde (\string~) character. The formatting
is used in the template and shown in \cref{ex:shared}.

\section{Math and equations}
\label{sec:math}
Here we show some example equations, with numbering, and examples of
referencing the equations. SIAM now includes the package 
\texttt{amsmath} by default, and we include some of its features as
well, although the reader should consult the package user manual for
further guidance \cite{amsmath,shortmath}.
 Several of the example are adapted 
from Mittlebach and Goossen's guide to \LaTeX~\cite{MiGo04}.

\Cref{ex:textmath} is a straightforward example of inline mathematics
equations that does not use any special packages or features.

\begin{example}[label={ex:textmath},bicolor]{Inline math}
The following shows an example of math in text: 
Let $S=[s_{ij}]$ ($1\leq i,j\leq n$) be a $(0,1,-1)$-matrix of order $n$.
\end{example}

In \cref{ex:bbm}, we show the recommended method for getting
blackboard fonts using the \texttt{amsfonts} package. This is not
loaded by default and must be included in the preamble.

\begin{example}[label={ex:bbm},bicolor,before upper={\preamble{\bs
      usepackage\{amsfonts\}}},%
listing options={style=siamlatex,%
{morekeywords=[2]{mathbb}}}]{Blackboard math}
Blackboard bold characters, such as $\mathbb{C}$ and $\mathbb{R}$,
should be created with the \texttt{amsfonts} package, although this
is not included by default.
\end{example}

%\newpage
\Cref{ex:smallmatrix} shows the \code{smallmatrix} environment for an
inline matrix from the \texttt{amsmath} package, which is included by
default.

\begin{example}[label={ex:smallmatrix},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{smallmatrix}}}]{Inline matrix}
Matrices of no more than two rows appearing in text can be created
as shown in the next example:
$B = \bigl[ \begin{smallmatrix} B_{11} & B_{12} \\ 
  B_{21} & B_{22} \end{smallmatrix} \bigr]$.
\end{example}

Bigger matrices can be rendered with environments from
the \texttt{amsmath} package, such as \code{bmatrix} and
\code{pmatrix} used in
\cref{ex:matrices}.

\begin{example}[label={ex:matrices},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{bmatrix,pmatrix}}}]{Creating matrices}
Display matrices can be rendered using environments from \texttt{amsmath}:
\begin{equation}\label{eq:matrices}
  S=\begin{bmatrix}1&0\\0&0\end{bmatrix}
  \quad\text{and}\quad
  C=\begin{pmatrix}1&1&0\\1&1&0\\0&0&0\end{pmatrix}.
\end{equation}
\Cref{eq:matrices} shows some example matrices.
\end{example}

\newpage
\Cref{ex:dmo} shows how to use the \code{\DeclareMathOperator} command
from the \texttt{amsopn} package to declare the \code{\Range} macro. 
(This example also uses the \texttt{braket} package for the
\code{\set} macro, but this is not necessarily recommended by SIAM.)
%
\begin{example}[label={ex:dmo},%
before upper={\preamble{\bs usepackage\{braket,amsfonts,amsopn\}}\\
\noindent\preamble{\bs DeclareMathOperator\{\bs Range\}\{Range\}}},%
bicolor,%
listing options={style=siamlatex,%
{moretexcs=[2]{Range}}}
]{Declaring math operators}
An example of a math operator:
\begin{equation}\label{eq:range}
  \Range(A) = \set{ y \in \mathbb{R}^n | y = Ax }.
\end{equation}
\end{example}

%\newpage
\Cref{ex:foo} shows how to use the \code{align} environment from
\texttt{amsmath} to easily align multiple equations.

\begin{example}[label={ex:foo},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{align}}}]{Aligned equations}
\Cref{eq:a,eq:b,eq:c} show three aligned equations.
\begin{align} 
  f &= g, \label{eq:a} \\
  f' &= g', \quad\text{and} \label{eq:b} \\
  \mathcal{L}f &= \mathcal{L}g \label{eq:c}.
\end{align}
\end{example}

Another way to number a set of equations is the
\code{subequations} environment from \texttt{amsmath}, as shown in \cref{ex:aligned}.

\begin{example}[label={ex:aligned},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{subequations}}}]{Subequations}
We calculate the Fr\'{e}chet derivative of $F$ as follows:
\begin{subequations}
\begin{align}
  F'(U,V)(H,K) 
  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T} -
  P(H\Sigma V^{T} + U\Sigma K^{T})\rangle \label{eq:aa} \\
  &= \langle R(U,V),H\Sigma V^{T} + U\Sigma K^{T}\rangle 
  \nonumber \\
  &= \langle R(U,V)V\Sigma^{T},H\rangle + 
  \langle \Sigma^{T}U^{T}R(U,V),K^{T}\rangle. \label{eq:bb}
\end{align}
\end{subequations}
\Cref{eq:aa} is the first line, and \cref{eq:bb} is the last line.
\end{example}

%\newpage
~

For an equation split over multiple lines, \cref{ex:ml} shows the
usage of the \code{multline} environment provided by \texttt{amsmath}.

~

\begin{example}[label={ex:ml},bicolor,%
listing options={style=siamlatex,%
{morekeywords=[2]{multline}}}]{Equation split across lines}
We claim that the projection $g(U,V)$ is given by the pair of matrices:
\begin{multline} \label{eq:ml}
  g(U,V) = \biggl( \frac{R(U,V)V\Sigma^{T}U^{T} 
    - U\Sigma V^{T}R(U,V)^{T}}{2}U,\\
  \frac{R(U,V)^{T}U\Sigma V^{T}-V \Sigma^{T}U^{T}R(U,V)}{2}V \biggr).
\end{multline}
\end{example}

\section{Theorem-like environments}
\label{sec:thm}
SIAM loads \texttt{ntheorem} package and uses it to define the following
theorem-like environments:
\code{theorem}, 
\code{lemma}, 
\code{corollary},
\code{definition}, and
\code{proposition}.
SIAM also defines a \code{proof} environment that automatically
inserts the symbol ``$\,\proofbox\,$'' at the end of any proof, even if it ends in an
equation environment. \emph{Note that the document may need to be
  compiled twice for the mark to appear.}
Some of the calculus examples were adapted from \cite{CalcI}. 
%
% An example theorem and lemma declaration is shown in \cref{ex:theorem}.  These
% are all numbered in the same sequence and produce labels in small caps
% with an italic body. Use the command \code{\textup} to produce Roman
% type for numbers and parentheses.
%
\Cref{ex:theorem} shows usage of the \code{theorem} environment. 
An optional argument can be used to name the theorem.
\Cref{ex:cor} illustrates a corollary, without a name, and the
proof environment.

~

\begin{example}[label=ex:theorem,bicolor,parbox=false,%
listing options={style=siamlatex,%
{morekeywords=[2]{theorem}}}]{Theorem}
\begin{theorem}[Mean Value Theorem]\label{thm:mvt}
  Suppose $f$ is a function that is continuous on the closed interval
  $[a,b]$.  and differentiable on the open interval $(a,b)$.
  Then there exists a number $c$ such that $a < c < b$ and
  \begin{displaymath}
    f'(c) = \frac{f(b)-f(a)}{b-a}.
  \end{displaymath}
  In other words, $f(b)-f(a) = f'(c)(b-a)$.
\end{theorem}
\end{example}

\begin{example}[label=ex:cor,bicolor,parbox=false,%
listing options={style=siamlatex,%
{morekeywords=[2]{corollary,proof}}}]%
{Corollary and proof}
\begin{corollary}
  Let $f(x)$ be continuous and differentiable everywhere. If $f(x)$
  has at least two roots, then $f'(x)$ must have at least one root.
\end{corollary}
\begin{proof}
  Let $a$ and $b$ be two distinct roots of $f$.
  By \cref{thm:mvt}, there exists a number $c$ such that
  \begin{displaymath}
    f'(c) = \frac{f(b)-f(a)}{b-a} = \frac{0-0}{b-a} = 0.
  \end{displaymath}
\end{proof}
\end{example}

SIAM also defines commands to create your own theorem- and
remark-like environments:
\begin{itemize}
\item \code{newsiamthm} --- Small caps header, italized body. 
\item \code{newsiamremark} --- Italics header, roman body.
\end{itemize}
Each command takes two arguments. The first is the environment name,
and the second is the name to show in the document. These commands should
be used instead of \code{\newtheorem}.
\Cref{ex:claim,ex:ref} shows how to use the commands above, including how to
specify the plural version for \texttt{cleveref} if it is unusual.

\begin{example}[label=ex:claim,bicolor,%
before upper={\preamble{\bs newsiamthm\{claim\}\{Claim\}}\\
\noindent\preamble{\bs newsiamremark\{hypothesis\}\{Hypothesis\}}\\
\noindent\preamble{\bs crefname\{hypothesis\}\{Hypothesis\}\{Hypotheses\}}},%
parbox=false,%
listing options={style=siamlatex,%
{morekeywords=[2]{claim,proof,hypothesis}}}]{New theorem-like environment}
\begin{claim}\label{cl:constant}
  If $f'(x) = 0$ for all $x \in (a,b)$ then $f(x)$ is constant on $(a,b)$.
\end{claim}
\begin{hypothesis}\label{hyp1}
The function $f$ is continuously differentiable.
\end{hypothesis}
\begin{hypothesis}\label{hyp2}
The random variable is normally distributed.
\end{hypothesis}
\end{example}

% \begin{example}[label=ex:remark,bicolor,%
% before upper={\preamble{\bs newsiamremark\{expl\}\{Example\}}},%
% parbox=false,%
% listing options={style=siamlatex,%
% {morekeywords=[2]{expl}}}]{New remark-like environment}
% \begin{expl}[Trivial note]\label{ex:a}
%   Let $f(x) = 2$. Since $f'(x) = 0$ for all $x$, $f$ is constant
%   everywhere.
% \end{expl}
% \end{example}

\begin{example}[label=ex:ref,bicolor,listing options={style=siamlatex,%
{morekeywords=[2]{cref}}}]{References}
We can reference multiple types of objects with a single reference:
\cref{cl:constant,thm:mvt,hyp1,hyp2}.
\end{example}

\section{Tables}
\label{sec:tab}
Table captions should go above the tables.
\Cref{ex:simpletable} shows the code to generate a
\cref{tab:simpletable}.
A more complicated example is shown in 
\cref{ex:table}, which generates \cref{tab:KoMa14}. This
example uses subfloats via the \texttt{subfig} package, as well as
special column options from the \texttt{array} package.

\begin{tcbverbatimwrite}{tmp_\jobname_simpletable.tex}
\begin{table}[tbhp]
{\footnotesize
  \caption{Example table}\label{tab:simpletable}
\begin{center}
  \begin{tabular}{|c|c|c|} \hline
   Species & \bf Mean & \bf Std.~Dev. \\ \hline
    1 & 3.4 & 1.2 \\
    2 & 5.4 & 0.6 \\ \hline
  \end{tabular}
\end{center}
}
\end{table}
\end{tcbverbatimwrite}

\examplefile[label={ex:simpletable},%
listing only, listing options={style=siamlatex}]%
{Example table.}{tmp_\jobname_simpletable.tex}

\input{tmp_\jobname_simpletable.tex}

\begin{tcbverbatimwrite}{tmp_\jobname_table.tex}
\newcolumntype{R}{>{$}r<{$}}  %
\newcolumntype{V}[1]{>{[\;}*{#1}{R@{\;\;}}R<{\;]}} %
\begin{table}[tbhp]
{\footnotesize
 \captionsetup{position=top} %<- Needed for using subtables created with the subfig package 
  \caption{Example table adapted from Kolda and Mayo \rm{\cite{KoMa14}}.}\label{tab:KoMa14}
\begin{center}
  \subfloat[$\beta=1$]{
    \begin{tabular}{|r|R|V{3}|c|r@{\,$\pm$\,}l|} \hline
occ. & \multicolumn{1}{c|}{$\lambda$} & \multicolumn{4}{c|}{$\mathbf{x}$} & 
fevals &  \multicolumn{2}{c|}{time (sec.)}\\ \hline
 718 & 11.3476 &  0.5544 &  0.3155 &  1.2018 &  0.0977 &   45 & 0.17 & 0.06 \\ \hline 
 134 &  3.7394 &  0.2642 & -1.1056 &  0.2657 & -0.3160 &   31 & 0.12 & 0.05 \\ \hline 
   4 & \multicolumn{6}{c|}{\emph{--- Failed to converge ---}} & 0.21 & 0.10 \\ \hline 
 \end{tabular}}

  \subfloat[$\beta=-1$]{
    \begin{tabular}{|r|R|V{3}|c|r@{\,$\pm$\,}l|} \hline
occ. & \multicolumn{1}{c|}{$\lambda$} & \multicolumn{4}{c|}{$\mathbf{x}$} & 
fevals &  \multicolumn{2}{c|}{time (sec.)}\\ \hline
  72 & -1.1507 &  0.2291 &  0.6444 &  0.3540 & -0.8990 &   34 & 0.14 & 0.06 \\ \hline 
 624 & -6.3985 &  0.1003 &  0.1840 &  0.5305 &  1.2438 &   48 & 0.19 & 0.08 \\ \hline 
   2 & \multicolumn{6}{c|}{\emph{--- Failed to converge ---}} & 0.23 & 0.02 \\ \hline 
 \end{tabular}}
\end{center}
}
\end{table}
\end{tcbverbatimwrite}

\examplefile[label={ex:table},%
before upper={\preamble[\scriptsize]{\bs usepackage\{array\}}\\[-0.4em]
\noindent\preamble[\scriptsize]{\bs usepackage[caption=false]\{subfig\}}},%
listing only, listing options={%
  style=siamlatex,basicstyle=\ttfamily\scriptsize}]%
{Example table with subtables.}{tmp_\jobname_table.tex}

\input{tmp_\jobname_table.tex}

\section{Figures}
\label{sec:fig}

It is recommended that all figures be generated in high resolution.
In the past, SIAM has required encapsulated
postscript (EPS) format for final production. This is still an
acceptable format, but SIAM also now allows high-resolution 
PDF, JPEG, and PNG figures. 
%
If working with EPS images and using \texttt{pdflatex}, we
recommend the package \texttt{epstopdf} to automatically convert EPS
images to PDF for inclusion in PDF documents created by
\texttt{pdflatex}.
%
\Cref{ex:fig} shows the code to generate \cref{fig:testfig}.  This
example uses the \texttt{graphicx} package for the
\code{\includegraphics} command.

\begin{tcbverbatimwrite}{tmp_\jobname_fig.tex}
\begin{figure}[tbhp]
  \centering
  \subfloat[$\epsilon_{\max}=5$]{\label{fig:a}\includegraphics{lexample_fig1}}
  \subfloat[$\epsilon_{\max}=0.5$]{\label{fig:b}\includegraphics{lexample_fig2}}
  \caption{Example figure using external image files.}
  \label{fig:testfig}
\end{figure}
\end{tcbverbatimwrite}

\examplefile[label={ex:fig},%
before upper={\preamble[\scriptsize]{\bs usepackage\{graphicx,epstopdf\}}\\[-0.4em]
\noindent\preamble[\scriptsize]{\bs usepackage[caption=false]\{subfig\}}},%
listing only, listing options={%
  style=siamlatex,basicstyle=\ttfamily\scriptsize}]%
{Example figure with subfigures and external files}{tmp_\jobname_fig.tex}

\input{tmp_\jobname_fig.tex}

%\newpage
Another option for figures is a graphics-generator that is platform- and
format-independent.
PGF is a TeX macro package for generating  such graphics and works together with the most important TeX backend drivers, including pdftex and dvips. 
The user-friedly syntax layer called TikZ.
Here we show an example using \texttt{PGFPLOTS}, useful for drawing high-quality 
plots directly in \LaTeX.
\Cref{ex:data} and \cref{ex:pgfplots} shows the data and code, respectively, to generate \cref{fig:pgfplots}, adapted from \cite{pgfplots}.

\examplefile[label={ex:data},listing only,
listing options={style=siamlatex,basicstyle=\ttfamily\scriptsize}]%
{Example data file (data.dat)}{data.dat}

\begin{tcbverbatimwrite}{tmp_\jobname_tikz.tex}
\begin{figure}[tbhp]
  \centering
  \begin{tikzpicture}
    \begin{loglogaxis}[height=2.75in, grid=major,
      xlabel={Degrees of Freedom}, ylabel={$L_2$ Error},
      legend entries={$d=2$,$d=3$}]
      \addplot table [x=d2_dof,y=d2_l2_err] {data.dat};
      \addplot table [x=d3_dof,y=d3_l2_err] {data.dat};
    \end{loglogaxis}
  \end{tikzpicture}
  \caption{Example \texttt{PGFPLOTS} figure.}
  \label{fig:pgfplots}
\end{figure}
\end{tcbverbatimwrite}

\examplefile[label={ex:pgfplots},%
before upper={\preamble[\scriptsize]{\bs usepackage\{pgfplots\}}},%
listing only, listing options={%
  style=siamlatex}]%
{Example TikZ/PGF for platform-independent graphics.}{tmp_\jobname_tikz.tex}

\input{tmp_\jobname_tikz.tex}

%\newpage  
\section{Algorithms}
\label{sec:algs}

SIAM automatically includes the \texttt{algorithm} package in the
class definition. This provides the float environment.
Users have the choice of \texttt{algpseudocode},
\texttt{algorithmic}, and other packages for actually formatting the algorithm.
For example, \cref{alg:buildtree} is produced by the code in \cref{ex:alg}.
In order to reference lines within the algorithm, we need to tell the
\texttt{cleveref} package how to do the referencing, which is the
second line of \cref{ex:alg}. Then we can use the code
\code{\cref{line3}} to produce \cref{line3}.

\begin{tcbverbatimwrite}{tmp_\jobname_alg.tex}
\begin{algorithm}
\caption{Build tree}
\label{alg:buildtree}
\begin{algorithmic}[1]
\STATE{Define $P:=T:=\{ \{1\},\ldots,\{d\}$\}}
\WHILE{$\#P > 1$}
\STATE\label{line3}{Choose $C^\prime\in\mathcal{C}_p(P)$ with $C^\prime := \operatorname{argmin}_{C\in\mathcal{C}_p(P)} \varrho(C)$}
\STATE{Find an optimal partition tree $T_{C^\prime}$ }
\STATE{Update $P := (P{\setminus} C^\prime) \cup \{ \bigcup_{t\in C^\prime} t \}$}
\STATE{Update $T := T \cup \{ \bigcup_{t\in\tau} t : \tau\in T_{C^\prime}{\setminus} \mathcal{L}(T_{C^\prime})\}$}
\ENDWHILE
\RETURN $T$
\end{algorithmic}
\end{algorithm}
\end{tcbverbatimwrite}

\examplefile[float=htpb,label={ex:alg},%
before upper={\preamble[\scriptsize]{\bs usepackage\{algorithmic\}}\\[-0.4em]
\preamble[\scriptsize]{\bs Crefname\{ALC@unique\}\{Line\}\{Lines\}}},%
listing only, listing options={%
  style=siamlatex,basicstyle=\ttfamily\scriptsize}]%
{Example algorithm}{tmp_\jobname_alg.tex}

\input{tmp_\jobname_alg.tex}

\section{Sections}
\label{sec:sec}
Sections are denoted using standard \LaTeX\ section commands, i.e.,
\code{\section}, \code{\subsection}, etc. 
%
If you wish to end the section title with something other that a period (the default), you have to add the command \code{\nopunct} at the end of the title.

Appendices are created with the normal sectioning commands, following
the command \code{\appendix}. 
%
Titles of appendices created with
\code{\section} are preceded by the word ``Appendix,'' but not the
subsections or appendices created with \code{\section*}.
%
Unlike normal sections, appendix sections may be sensitive to blank lines
following the declaration, causing a new paragraph rather than the
text immediately following the appendix title. This can be corrected
by removing and blank lines.
%
Any numbered, labeled sections can be referenced using \code{\cref},
including those without a title.
%
Section titles are automatically inserted into the table of contents
and converted to bookmarks; see \cref{sec:spec-instr-pdf} for handling
special characters.

The acknowledgments section comes
immediately before the references and after any appendices. It should
be declared by \code{\section*{Acknowledgments}}.

%
% \Cref{ex:secref} shows how to reference sections.

% \begin{example}[label={ex:secref},lefthand ratio=0.4,bicolor,sidebyside,%
% listing options={style=siamlatex,basicstyle=\ttfamily\scriptsize,%
% deletetexcs={cref,Cref},{moretexcs=[2]{cref,Cref}}}]
% {Right and wrong ways to reference a section}
% Inside a sentence\dots\\
% Single: \cref{sec:intro}\\
% Range: \cref{sec:intro,sec:front,%
% sec:sec}\\
% Multiple: \cref{sec:intro,sec:sec,%
% sec:tab,sec:math,sec:thm}\\
% Appendix: \cref{sec:changes}\\

% Beginning of a sentence\dots\\
% Single: \Cref{sec:intro}\\
% Range: \Cref{sec:intro,sec:front,%
% sec:sec}\\
% Multiple: \Cref{sec:intro,sec:sec,%
% sec:tab,sec:math,sec:thm}\\
% Appendix: \Cref{sec:changes}\\

% Just don't do it this way\dots\\
% Section~\ref{sec:intro}  
% \end{example}

\section{Supplemental material}
\label{sec:supplement}

For several SIAM journals, authors are encouraged to submit
Supplementary Materials to complement their articles. This might
include additional figures or examples, animations, data sets used in
the paper, computer code used to generate figures or tables, or other
materials that are necessary to fully document the research contained
in the paper or to facilitate the readers' ability to understand and
extend the work.

\newpage
The class option \code{supplement} should be used in the
supplemental \LaTeX\ file provided for creating PDF supplemental material.
The supplement should have the same title and authors as the main
document.  The title is modified automatically by the SIAM
class file so that it is preceded by the text ``Supplementary
Materials'', followed by a colon.  
%
The numbering is modified so that
all sections, equations, figures, tables, algorithms, %
and so on to start with ``SM''. 
%
A supplement does have sections but does not have an
abstract, keywords, AMS classifications, or appendices.  The main
document and supplement can cross reference sections, equations,
theorem-like declarations, figures, tables, algorithms, etc.  However,
there is no sharing of references. The references are optional for a
supplement.
A template is provide, as discussed in \cref{sec:template}.

\section{Template}
\label{sec:template}

The files \texttt{ex\_article.tex}, \texttt{ex\_shared.tex},
and \texttt{ex\_supplement} \texttt{.tex} provide a template that can be used
for creating a \LaTeX\ document with an optional supplement.
%
\Cref{ex:artoutline,ex:suppoutline} give the outline of an article and
the supplement. In this case we
assume that the title and authors are defined in the
\texttt{ex\_shared.tex} file, shown in \cref{ex:shared}.
%
Cross referencing between the main document and the supplement is
enabled using the \texttt{xr-hyperref} package (included by the
SIAM class file). Use \code{\externaldocument}
to specify the external document to search for external
references.
%

\begin{example}[label={ex:artoutline},listing only,%
  listing options={style=siamlatex,%
    {morekeywords=[2]{externaldocument}}}]%
  {Document outline with supplement}
\documentclass{siamart190516}
\input{ex_shared}
\externaldocument{ex_supplement}
\begin{document}
\maketitle
% Other front matter: abstract, keywords, subject classifications.
% Main body goes here.
% Appendices and/or acknowledgments.
% Bibliography
\end{document}
\end{example}

\begin{example}[label={ex:suppoutline},listing only,%
  listing options={style=siamlatex,%
    {morekeywords=[2]{supplement,siampretitle,externaldocument}}}]%
  {Supplement document outline}
\documentclass[supplement]{siamart190516}
\input{ex_shared}
\externaldocument{ex_article}
\begin{document}
\maketitle
% No abstract, keywords, subject classifications.
% Main body goes here.
% No appendices or acknowledgments.
% Optional bibliography goes here.
\end{document}
\end{example}

%\newpage
\Cref{ex:shared} (from \texttt{ex\_shared.tex}) shows how the
``shared'' title and authors may be defined across the main document
and a supplement. 
%
Note the use of the \code{\string} command in the URL for the tilde;
this is only necessary inside the \code{\thanks} command.
%

\examplefile[label=ex:shared,listing only,%
listing options={style=siamlatex,firstline=19,lastline=40,%
{morekeywords=[2]{siampretitle,MakeUppercase,string}}}
]{Example of shared title and author macros}{ex_shared.tex}

\section{Bibliography}
\label{sec:bib}

The SIAM \BibTeX style file, now called \texttt{siamplain.bst}, has been updated to include the new keys listed below:
\begin{itemize}
\item \code{doi}: Digital object identifier, a unique alphanumeric string
\item \code{url}: Web address, usually impermanent
\item \code{urldate}: Date that the web address was last accessed
\item \code{eprint}: Archive identifier, a unique alphanumeric string
\item \code{eprintclass}: Archive class
\item \code{archive}: Archive URL, defaults to \nolinkurl{https://arXiv.org/abs}
\item \code{archivepreprint}: Archive name, defaults to ``arXiv''.
\item \code{eid}: Article ID, if there are no page numbers
\item \code{pagetotal}: Total number of pages, for use with article ID
\end{itemize}
Every entry type has been modified to include an optional link to a
DOI, a URL, and/or an archive preprint reference.
%
Additionally, the \code{article} entry now supports an Article ID,
\code{eid}, and number of pages, \code{pagetotal}.
%
To use this, include the following code in your \LaTeX\ source code:
\code{\bibliographystyle{siamplain}}.

\subsection{DOI}

A digital object identifier (DOI) is a unique alphanumeric string that provides a persistent link to its location on the Internet. The publisher assigns a DOI when your article is published and made available electronically. Using the \code{doi} field in \BibTeX to specify it, as shown for \cite{KoMa14} in \cref{ex:article}; observe the new \code{doi} field which produces a hyperlink in the citation.
Do not include the full URL, i.e., \nolinkurl{https://doi.org/} preceding the DOI.
Authors are highly advised to provide DOIs; if they are not provided, they
will be requested during the copyediting process.

\examplefile[label=ex:article,listing only,%
listing options={style=siamlatex,firstline=1,lastline=12,{morekeywords=[2]{doi}}}
]{Example article in \BibTeX}{references.bib}

\subsection{URL}
There is also now support for the  \code{url} field. Generally, the DOI is preferred to the URL, since the DOIs should be permanent references. For that reason, it is good practice to specify the last date that the URL was accessed, which is specified by the optional \code{urldate} field. Reference \cite{Hi14} produced by \cref{ex:url} shows an example of using these fields.

\examplefile[label=ex:url,listing only,%
listing options={style=siamlatex,firstline=20,lastline=28,%
{morekeywords=[2]{url,urldate}}}
]{Example with the URL field in \BibTeX}{references.bib}

\subsection{Preprint servers such as arXiv}

More and more manuscripts are available on preprint servers. In fact,
SIAM's publication policy explicitly allows the final accepted version
of any article to be posted on a preprint server such as arXiv.

For an arXiv paper,
the \code{eprint} field is used to specify the identifier. The optional \code{eprintclass} field specifies the class. \Cref{ex:arxiv} shows the \BibTeX for \cite{PeKoPi14}.

\examplefile[label=ex:arxiv,listing only,%
listing options={style=siamlatex,firstline=30,lastline=38,%
{morekeywords=[2]{eprint,eprintclass}}}
]{Example arXiv reference in \BibTeX}{references.bib}

\newpage
Other preprint servers are supported as well, but these require
specification of the fields \code{archive} and \code{archiveprefix}. In this case, the target URL is formed by concatenating the \code{archive}, a forward slash (\texttt{/}), and the \code{eprint}; and the text for the hyperlink is formed by concatenating the \code{archiveprevix}, a colon (:), and the \code{eprint}.
%
\Cref{ex:pubmed} shows the code to generate \cite{WoZhMeSh05}, including the preprint from PubMed.
Note that this example has both the journal citation as well as the link for the preprint.

\examplefile[label=ex:pubmed,listing only,%
listing options={style=siamlatex,firstline=40,lastline=55,%
{morekeywords=[2]{eprint,eprintclass,archive,archiveprefix}}}
]{Example PubMed reference in \BibTeX}{references.bib}

\subsection{Article ID}
Some journals use an article ID rather than page numbers. 
The field \texttt{eid} specifies the article ID. The optional field \texttt{pagetotal} can say the number
of pages in the document. An example of an article using these fields is shown in \cref{ex:eid} for citation \cite{Ne03}.

\examplefile[label=ex:eid,listing only,%
listing options={style=siamlatex,firstline=57,lastline=67,%
{morekeywords=[2]{eid,pagetotal}}}
]{Example article ID reference in \BibTeX}{references.bib}

\subsection{Software citations}

SIAM encourages software citations, both related technical publications as well as the software itself. A citation to a software package may look something like what is shown in \cref{ex:clawpack} for citation \cite{clawpack}. Notice the double braces around the \texttt{author} key; else, it would appear as ``C. D. Team''.

\examplefile[label=ex:clawpack,listing only,%
listing options={style=siamlatex,firstline=69,lastline=76,%
{morekeywords=[2]{key}}}
]{Example software reference in \BibTeX}{references.bib}

\appendix
\section{Summary of major changes}
\label{sec:changes}

Here we summarize the major changes in the latest version of
the SIAM standard \LaTeX\@ and \BibTeX\ classes:
\begin{itemize}
\item Change in file names: \texttt{siamart171218.cls} is replaced by
  \texttt{siamart190516.cls}, and the \texttt{siam.bst} bibliography style
  file is replaced by \texttt{siamplain.bst}; see \cref{sec:intro}.
\item Hyperlinking in cross references via the
  \texttt{cleveref} package, including customizations to adhere to
  SIAM conventions. Automatic PDF bookmarks enabled for sections,
  appendices, and references.
  See \cref{sec:cleveref}.
\item Colored hyperlinks (red for external, green for internal). Can
  be disabled with class options \code{hidelinks}; see \cref{sec:hyperef}.
\item New fields for \BibTeX, as listed in \cref{sec:bib}.
\item  Support for supplemental PDF files, including
  cross references between the supplement and the main document; see
  \cref{sec:supplement}. 
\item New command for setting headers: \code{\headings}; see
  \cref{sec:front}. 
\item Updated theorem-like and proof environments using
  \texttt{ntheorem} package; see \cref{sec:thm}.
\item Fixed handling of appendices to adhere to SIAM style guidelines;
  see \cref{sec:sec}.
\item Added \code{review} class option; see \cref{sec:class-options}.
\item Includes the following packages by default:
  \texttt{algorithm},
  \texttt{amsmath}, 
  \texttt{breakurl}, 
  \texttt{cleveref}, 
  \texttt{hypcap}, 
  \texttt{hyperef},
  \texttt{ifpdf},
  \texttt{ntheorem}, 
  \texttt{xcolor}, and
  \texttt{xr-hyperef}.
  Adds the \texttt{lineno}
  package if the \code{review} class option is enabled.
\end{itemize}

\section{Special modifications}

\subsection{Special macros}
In past versions, 
the SIAM standard \LaTeX\ class defined the following macros:
\code{\const},
\code{\diag},
\code{\grad},
\code{\Range},
\code{\rank}, and
\code{\supp}.
These are no longer declared; however, they can be redefined using the
\code{\DeclareMathOperator} command from the \texttt{amsopn}
package as demonstrated in \cref{ex:dmo}.

\subsection{Labeling objects sequentially}
SIAM recommends numbering objects by section number. 
However, if you prefer to number objects sequentially (e.g., Figure 5
would indicate the fifth figure appearing in the paper regardless of which section it is in), add the code from
\cref{ex:numbering} as documentclass options (e.g., \code{\documentclass[review,onefignum,onetabnum]{siamart190516}}).

\begin{example}[label=ex:numbering,listing only,%
listing options={style=siamlatex,{morekeywords=[2]{makeatletter,makeatother}},}]%
{Labeling objects sequentially}
oneeqnum % equations
onetabnum % tables
onefignum % figures
onealgnum % algorithms
onethmnum % theorem environments
\end{example}

\subsection{Appendices with no title}
The SIAM style manual \cite{siam} allows for an appendix that is
numbered (by a letter) but has no title. We have a special command to
create such an appendix: \code{\appendixnotitle}. This is equivalent
to a \code{\section} command in the appendix except that it has no
arguments.

\subsection{Changing the font of algorithm titles}
\label{sec:chang-font-algor}

Currently, the algorithm title font matches the figure and table title
fonts. To make the algorithm title font appear as small caps, insert
the code in \cref{ex:algfont} into the preamble.

\begin{example}[label=ex:algfont,listing only,%
listing options={style=siamlatex}]{Changing algorithm title font}
\makeatletter
\renewcommand{\ALG@name}{\sc Algorithm}
\makeatother
\end{example}

\subsection{Changing title of proof}
To change the title of a proof to, say, ``Proof of main theorem,''
simply use an optional argument as shown in
\cref{ex:newproof}.

\begin{example}[label=ex:newproof,listing only,%
listing options={style=siamlatex}]{Altered proof environment}
\begin{proof}[Proof of main theorem]
We now show ...
\end{proof}
\end{example}

\subsection{Special instructions for PDF bookmarks}
\label{sec:spec-instr-pdf}

Section titles are automatically inserted into the table of contents
and therefore used as PDF bookmarks. Some special symbols may not
correctly render. In that case, you can define alternate text as shown
in \cref{ex:specialtitle}, using the \code{\texorpdfstring} command
provided by the \texttt{hypertex} package. In this example, the
default bookmark would be ``Discussion of Z = X Y''; instead, it is
replaced by ``Discussion of Z = X union Y.''

\begin{example}[label=ex:specialtitle,listing only,%
listing options={style=siamlatex}]{PDF bookmarks for symbols in section titles}
\section{Discussion of \texorpdfstring{{\boldmath$Z=X \cup Y$}}{Z = X union Y}}
\end{example}

\bibliographystyle{siamplain}
\bibliography{references}

\end{document}

### 2021-07-29 paper/siamart_190516/ex_shared.tex
switch to SIAM

% SIAM Shared Information Template
% This is information that is shared between the main document and any
% supplement. If no supplement is required, then this information can
% be included directly in the main document.

% Packages and macros go here
\usepackage{lipsum}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{algorithmic}
\ifpdf
  \DeclareGraphicsExtensions{.eps,.pdf,.png,.jpg}
\else
  \DeclareGraphicsExtensions{.eps}
\fi

% Add a serial/Oxford comma by default.
\newcommand{\creflastconjunction}{, and~}

% Used for creating new theorem and remark environments
\newsiamremark{remark}{Remark}
\newsiamremark{hypothesis}{Hypothesis}
\crefname{hypothesis}{Hypothesis}{Hypotheses}
\newsiamthm{claim}{Claim}

% Sets running headers as well as PDF title and authors
\headers{An Example Article}{D. Doe, P. T. Frank, and J. E. Smith}

% Title. If the supplement option is on, then "Supplementary Material"
% is automatically inserted before the title.
\title{An Example Article\thanks{Submitted to the editors DATE.
\funding{This work was funded by the Fog Research Institute under contract no.~FRI-454.}}}

% Authors: full names plus addresses.
\author{Dianne Doe\thanks{Imagination Corp., Chicago, IL 
  (\email{ddoe@imag.com}, \url{http://www.imag.com/\string~ddoe/}).}
\and Paul T. Frank\thanks{Department of Applied Mathematics, Fictional University, Boise, ID 
  (\email{ptfrank@fictional.edu}, \email{jesmith@fictional.edu}).}
\and Jane E. Smith\footnotemark[3]}

\usepackage{amsopn}
\DeclareMathOperator{\diag}{diag}

%%% Local Variables: 
%%% mode:latex
%%% TeX-master: "ex_article"
%%% End:

### 2021-07-30 paper/paper.tex

@@
 
+% REQUIRED
+\begin{keywords}
+  maximum independent set, einsum network
+\end{keywords}
+
+% REQUIRED
+% 14N07  	Secant varieties, tensor rank, varieties of sums of powers
+\begin{AMS}
+  05C31, 14N07
+\end{AMS}
+
 \section{Introduction}
@@
 Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
-Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $2^{tw(G)}$.
+Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $O(2^{tw(G)}tw(G)n)$.
 A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
@@
 
+\section{matching polynomial}
+One can generalize the generic einsum network for solving another \#P-complete problem, the matching polynomials.
+A match polynomial of a graph $G$ is defined as
+\begin{align}
+    M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
+\end{align}
+where $k$ is the number of matches, and coefficients $c_k$ are countings.
+
+We define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
+\begin{align}
+    W_{v\rightarrow n_1, v\rightarrow n_2, \ldots, v\rightarrow n_{d(v)}} = \begin{cases}
+        1, & \sum_{i=1}^{d(v)} v\rightarrow n_i \leq 1,\\
+        0, & otherwise,
+    \end{cases}
+\end{align}
+and a tensor of rank $1$ on the bond
+\begin{align}
+    B_{v\rightarrow w} = \begin{cases}
+    1, & v \rightarrow w = 0 \\
+    x, & v \rightarrow w = 1.
+\end{cases}
+\end{align}
+
+Here, we use bond index $v \rightarrow w$ to label tensors.
+
 \end{document}

### 2021-07-31 project/configurations2.jl
update

@@ -14,12 +14,13 @@ function mis_configurations(n, seed; writefile, sc_target=12)
     if c > 1000000
         @warn "degeneracy too high, got: $c"
     end
-    s2, config = (res = mis_config(code; all=true)[]; (res.n, res.c))
+    s2, config1, config0 = (res = mis_max2_config(code)[]; (res.maxorder, res.a, res.b))
     @assert s == s2
-    @assert length(config) == c
-    ofname = joinpath(folder, "configurations_$(n)x$(n)_$seed.dat")
-    writefile && write(ofname, toMatrix(config))
-    return s, config
+    @assert length(config0) == c
+    #ofname = joinpath(folder, "configurations_$(n)x$(n)_$seed.dat")
+    ofname1 = joinpath(folder, "configurations_suboptimal_$(n)x$(n)_$seed.dat")
+    writefile && write(ofname1, toMatrix(config1))
+    return s, config0, config1
 end
 
 function toMatrix(x::ConfigEnumerator{N,C}) where {N,C}
@@ -30,10 +31,15 @@ function toMatrix(x::ConfigEnumerator{N,C}) where {N,C}
     return m
 end
 
-for seed in [0, 2, 4, 9, 50]
-    @time mis_configurations(10, seed; writefile=true)
-end
-
-for seed in  [4, 6, 7, 17] #[26, 40, 339, 339, 8, 13, 25, 89, 108, 138]
-    @time mis_configurations(15, seed; writefile=true, sc_target=16)
+for (n, seeds) in [
+    #(5, [410, 407, 396]),
+    #(6, [667, 557, 78]),
+    #(7, [189, 623, 354]),
+    #(10, [983, 828, 61]),
+    #(11, [571, 808, 438]),
+    (15, [612, 907, 758])
+    ]
+    for seed in seeds
+        @time mis_configurations(n, seed; writefile=true, sc_target=14)
+    end
 end

### 2021-07-31 src/configurations.jl

@@ -46,7 +46,6 @@ function mis_config(code; all=false, bounding=true, usecuda=false)
     flatten_code = flatten(code)
     syms = unique(Iterators.flatten(filter(x->length(x)==1,OMEinsum.getixs(flatten_code))))
     vertex_index = Dict([s=>i for (i, s) in enumerate(syms)])
-    @show syms
     N = length(vertex_index)
     C = TropicalNumbers._nints(N)
     xs = map(getixs(flatten_code)) do ix
@@ -82,6 +81,25 @@ function mis_config(code; all=false, bounding=true, usecuda=false)
         if usecuda
             xs = CuArray.(xs)
         end
-	    return code(xs...)
+	    return dynamic_einsum(code, xs)
     end
+end
+
+export mis_max2_config
+function mis_max2_config(code)
+    flatten_code = flatten(code)
+    syms = unique(Iterators.flatten(filter(x->length(x)==1,OMEinsum.getixs(flatten_code))))
+    vertex_index = Dict([s=>i for (i, s) in enumerate(syms)])
+    N = length(vertex_index)
+    C = TropicalNumbers._nints(N)
+    xs = map(getixs(flatten_code)) do ix
+        T = Max2Poly{ConfigEnumerator{N,C}}
+        if length(ix) == 2
+            return misb(T)
+        else
+            s = TropicalNumbers.onehot(StaticBitVector{N,C}, vertex_index[ix[1]])
+            misv(T, Max2Poly(zero(ConfigEnumerator{N,C}), ConfigEnumerator([s]), 1.0))
+        end
+    end
+    return dynamic_einsum(code, xs)
 end

### 2021-08-06 paper/paper.tex
update

@@
 %\usepackage{natbib}
+%\usepackage[sort]{cite}
 \pdfoutput=1
@@
 \usetikzlibrary{shapes}
+\usetikzlibrary{snakes}
 \usepackage{wrapfig}
@@
 
+\newcounter{example}
+\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
+   \noindent \textbf{Example~\theexample. #1} \rmfamily}{\medskip}
+
 %\newtheorem{theorem}{\textit{Theorem}}
@@
 \section{Introduction}
-MIS problem is hard~\cite{Hastad1996}.
-Branching algorithms can solve the MIS problem in $1.1893^n n ^{O(1)}$ time ~\cite{Xiao2017}.
-Previous dynamic programming approach~\cite{Fomin2013} can reduce the complexity of computing to $O(2^{tw(G)}tw(G)n)$.
-A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
-A set is independent if and only if its complement is a vertex cover.
+In this work, we introduce a new method to solve the classic graph problem, finding independent sets.
+Given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
+Finding the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$ belongs to the complexity class NP-complete~\cite{Hastad1996}, which is unlikely to be decided in polynomial time.
+It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbituary small possitive $\epsilon$.
+The naive algorithm of enumerating all configuration space gives a $2^{|V|}$ time solution.
+More efficient algorithms to compute the MIS size exactly includes the branching algorithm and dynamic programming.
+Without changing the fact of exponential scaling in computing time, the branching algorithm gives a smaller base.
+For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm gives a time complexity $1.1893^n n ^{O(1)}$.
+The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for graphs with small tree width $tw(G)$, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
+People are interested in solving this problem better not only because it is a NP-complete problem that directly related to other NP-complete prolems like maximal cliques and vertex cover~\cite{Moore2011},
+but also for its close relation with physical applications like hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
+In these applications, knowing the MIS size and one of the optimal solution is not the only goal.
+%A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
+%A set is independent if and only if its complement is a vertex cover.
 Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
-It is related to hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
-
-In this work, we attack this problem by mapping it to an ``einsum'' network.
+People often ask different questions about independent sets in order to understand the landscape of their models better.
+These questions includes but not limited to, counting all independent sets, obtaining all indenepent sets of size $\alpha(G)$ and $\alpha(G)-1$,
+counting the number of (maximal) independent sets of different sizes.
+In this work, we attack this problem by mapping it to an generic ``einsum'' network.
+It does not give a better time complexity comparing to dynamic programming, but is versatile enough to answer the above questions by engineering the tensor elements.
+
+\section{Einsum network}
 The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
@@
 It is denoted as $C_i^k = A_i^j B_j^k$ in the Einstein's original notation, where the paired subscript and superscript $j$ is a dummy index summed over.
-An example of tensor networks is $C_i^l = A_{ij}^k B^l_k V^j$.
 One can map a tensor network to a muti-graph with open edges by viewing a tensor in the expression on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining labels as open edges.
-We get the graphical notation as the following.
+
+\begin{example}
+    A tensor networks $C_i^l = A_{ij}^k B^l_k V^j$, where its graphical notation as the following.
+One can easily check a label in a tensor network representation appears precisely twice.
 
@@
 
-One can easily check a label in a tensor network representation appears precisely twice.
-Numpy programmers make a generalization to this notation by not restricting the number of times a label is used by tensors.
-For example, $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum but not a tensor network.
-Here, all indices not appearing in the output are summed over, i.e.
-it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
-Whether the index appear as a superscript or a subscript makes no sense now.
-The graphical representation of an einsum is a hypergraph, where an edge can be shared by a arbituary number of nodes.
-
-\centerline{\begin{tikzpicture}
+\end{example}
+
+Numpy programmers make a generalization of this notation by not restricting the number of times a label is used by tensors,
+hence whether an index appears as a superscript or a subscript makes no sense now.
+It has different names in different context, like sum-product network and factor graph~\cite{Bishop2006}.
+The graphical representation of an einsum is a hypergraph, where an edge (degree of freedom) can be shared by a arbituary number of nodes (tensors).
+
+\begin{example}
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum but not a tensor network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
+Its hypergraph representation is as the following, where we use different color to annotate different hyperedges.
+
+\centerline{\begin{tikzpicture}[
+    dot/.style = {circle, fill, minimum size=#1,
+                inner sep=0pt, outer sep=0pt},
+    dot/.default = 6pt  % size of the circle diameter 
+                    ]  
     \def\dx{0};
-    \def\r{0.25}
+    \def\r{0.5cm}
     \def\ax{0}
@@
     \def\cy{-1}
-    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
-    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
-    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
-    \draw[color=blue,thick] (\bx+\dx,\by) circle [radius=\r+0.1];
-    \node[color=blue] at (\bx+\dx-0.6,\bx) {i};
-    \draw[color=cyan,dashed,thick] (\bx+\dx,\by) circle [radius=\r+0.25];
-    \node[color=cyan] at (\bx+\dx+0.5,\bx-0.5) {l};
-    \draw[color=violet,thick,dashed] (\ax+\dx,\ay) circle [radius=\r+0.1];
-    \node[color=violet] at (\ax+\dx+0.4,-0.4) {k};
-    \draw[color=black,thick] (0.5+\dx,0) circle [radius=1.7];
-    \node[color=black] at (0.5+\dx-1.9,0) {m};
-    \draw[color=red,thick,rotate=135,dashed] (-0.6,0) ellipse (1.2 and 0.5);
-    \node[color=red] at (\ax+\dx,-1.0) {j};
-    \node[color=white] at (\ax+\dx,\ax) {A};
-    \node[color=white] at (\bx+\dx,\by) {B};
-    \node[color=white] at (\cx+\dx,\cy) {V};
+    \node[color=white,fill=black,dot=\r] at (\ax+\dx,\ax) (a) {A};
+    \node[color=white,fill=black,dot=\r] at (\bx+\dx,\by) (b) {B};
+    \node[color=white,fill=black,dot=\r] at (\cx+\dx,\cy) (v) {V};
+    \node at (\ax-0.8,\ay) (k) {k};
+    \node at (\bx+0.4,\ay) (m) {m};
+    \node at (\ax,\cy) (j) {j};
+    \node at (\bx+1,\by) (l) {l};
+    \node at (\bx-1,\by) (i) {i};
+    \draw[color=blue] (i) -- (b);
+    \draw[color=blue] (i) -- (\ax-1,\by);
+    \draw[color=cyan,thick] (l) -- (b);
+    \draw[color=violet,thick] (k) -- (a);
+    \draw[color=violet,thick] (k) -- (\ax-1.5,\ay);
+    \draw[color=black,thick] (b) -- (m);
+    \draw[color=black,thick] (m) -- (a);
+    \draw[color=black,thick] (m) -- (v);
+    \draw[color=red,thick] (a) -- (j);
+    \draw[color=red,thick] (v) -- (j);
+    \draw[color=red,thick] (\ax-1,\cy) -- (j);
 \end{tikzpicture}}
-
-In the main text, we stick to the einsum notation rather than the tensor network notation,
+\end{example}
+
+In the main text, we stick to the einsum notation rather than the tensor network notation.
+As a note to those who are more familiar with tensor network representation,
 although one can easily translate an einsum network to the equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
-We do not use the language of tensor network because it can sometime increase the contraction complexity of a graph. We will show an example in the appendix.
+It can sometime increase the contraction complexity of a graph. We have an example demonstrating this in \App{app:tensorbad}.
 
 \section{Independence polynomial}
-\begin{figure*}[h!]
-    \centerline{\begin{tikzpicture}
+One can encode the independent set problem on graph $G$ to an einsum network by placing a rank one tensor of size $2$ on vertex $i$
+\begin{equation}
+    W(x_i)_{s_i} = \left(\begin{matrix}
+        1 \\
+        x_i
+    \end{matrix}\right)_{s_i},\label{eq:wtensor}
+\end{equation}
+and a rank two tensor of size $2 \times 2$ on edge $(i,j)$
+\begin{equation}
+    B_{s_i s_j} = \left(\begin{matrix}
+        1  & 1\\
+        1 & 0
+    \end{matrix}\right)_{s_is_j},\label{eq:btensor}
+\end{equation}
+where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise.
+It corresponds to a hyperedge in the hypergraph.
+$x_i$ is a variable.
+The contraction of such an einsum network gives
+\begin{equation}
+    A(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
+\end{equation}
+Here, the einsum runs over all vertex configurations $\{s_1,\ldots,s_n\}$ and accumulates the product of tensor elements to the scalar output.
+Let $x_i = x$, then the product over vertex tensors gives a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
+and the product over edge tensors gives a factor $0$ for configurations not being an independent set.
+The contraction of this einsum network gives the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$
+\begin{equation}
+I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
+By mapping the independence polynomial solving problem to the einsum network contraction, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
+A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of the line graph of a tensor network, here it corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
+The pairwise tensor contraction also makes it possible to utilize fast basic linear algebra subprograms (BLAS) functions for certain tensor element types.
+
+\begin{example}
+    Mapping a graph (left) to an einsum network, the resulting einsum network is shown in the right panel.
+    A vertex is mapped to a hyperedge in the einsum's graphical notation.
+    An edge is mapped to an edge tensor.
+
+    \centerline{\begin{tikzpicture}[
+    dot/.style = {circle, fill, minimum size=#1,
+                inner sep=0pt, outer sep=0pt},
+    dot/.default = 6pt  % size of the circle diameter 
+                    ]
+
         \def\dx{0};
-        \def\r{0.25}
+        \def\r{0.25cm}
         \filldraw[fill=black] (\dx,0) circle [radius=\r];
@@
         \def\dx{5};
-        \def\r{0.25}
-        \draw [black,thick] (\dx,0) -- (\dx,1.5);
-        \draw [black,thick] (\dx,0) -- (1.5+\dx,0);
-        \draw [black,thick] (\dx,1.5) -- (1.5+\dx,1.5);
-        \draw [black,thick] (1.5+\dx,0) -- (1.5+\dx,1.5);
-        \draw [black,thick] (1.5+\dx,0) -- (\dx,1.5);
-        \draw [black,thick] (2.5+\dx,2.5) -- (1.5+\dx,1.5);
-        \node[color=black,fill=white] at (0.75+\dx,0) {\scriptsize $B$};
-        \node[color=black,fill=white] at (\dx,0.75) {\scriptsize $B$};
-        \node[color=black,fill=white] at (1.5+\dx,0.75) {\scriptsize $B$};
-        \node[color=black,fill=white] at (0.75+\dx,1.5) {\scriptsize $B$};
-        \node[color=black,fill=white] at (0.75+\dx,0.75) {\scriptsize $B$};
-        \node[color=black,fill=white] at (2+\dx,2) {\scriptsize $B$};
-        \node[color=black,fill=white] at (\dx,0) {\scriptsize $W(x_a)$};
-        \node[color=black,fill=white] at (\dx,1.5) {\scriptsize $W(x_b)$};
-        \node[color=black,fill=white] at (1.5+\dx,0) {\scriptsize $W(x_c)$};
-        \node[color=black,fill=white] at (1.5+\dx,1.5) {\scriptsize $W(x_d)$};
-        \node[color=black,fill=white] at (2.5+\dx,2.5) {\scriptsize $W(x_e)$};
+        \def\r{0.25cm}
+        \foreach \x/\y/\e in {0.75/0/ac, 0/0.75/ab, 1.5/0.75/cd, 0.75/1.5/bd, 0.75/0.75/bc, 2/2/de}
+            \node[color=white,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize B};
+        \foreach \x/\y/\v in {0/0/a, 0/1.5/b, 1.5/0/c, 1.5/1.5/d, 2.5/2.5/e}
+            \node[color=black] at (\x+\dx,\y) (\v) {$s_\v$};
+        \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
+            \node[color=white,fill=black,dot=\r] at (\x+\dx,\y) (\v\v) {};
+        \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
+            \node[color=black] at (\x+\dx+0.5,\y) {\scriptsize $W(x_\v)$};
+        \draw [cyan,thick] (a) -- (aa);
+        \draw [cyan,thick] (a) -- (ab);
+        \draw [cyan,thick] (a) -- (ac);
+        \draw [blue,thick] (b) -- (bb);
+        \draw [blue,thick] (b) -- (ab);
+        \draw [blue,thick] (b) -- (bc);
+        \draw [blue,thick] (b) -- (bd);
+        \draw [red,thick] (c) -- (cc);
+        \draw [red,thick] (c) -- (ac);
+        \draw [red,thick] (c) -- (bc);
+        \draw [red,thick] (c) -- (cd);
+        \draw [green,thick] (d) -- (dd);
+        \draw [green,thick] (d) -- (bd);
+        \draw [green,thick] (d) -- (de);
+        \draw [green,thick] (d) -- (cd);
+        \draw [orange,thick] (e) -- (ee);
+        \draw [orange,thick] (e) -- (de);
     \end{tikzpicture}}
-    \caption{Mapping a graph to an einsum network.}\label{fig:einsummapping}
-\end{figure*}
-
-Let us map the graph $G$ into an einsum network, as shown in \Fig{fig:einsummapping}, by placing a rank one tensor of size $2$ on vertex $i$
-\begin{equation}
-    W(x_i)_{s_i} = \left(\begin{matrix}
-        1 \\
-        x_i
-    \end{matrix}\right)_{s_i},
-\end{equation}
-and a rank two tensor of size $2 \times 2$ on edge $(i,j)$
-\begin{equation}
-    B_{s_i s_j} = \left(\begin{matrix}
-        1  & 1\\
-        1 & 0
-    \end{matrix}\right)_{s_is_j},
-\end{equation}
-where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise, $x_i$ is a variable.
-We denote the contraction result of this einsum network as
-\begin{equation}
-    A(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
-\end{equation}
-Here, the einsum runs over all possible vertex configurations and accumulates the product of tensor elements to the output.
-Let $x_i = x$ be the same variable, then the product over vertex tensors provides a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
-and the product over edge tensors provides a factor $0$ for configurations not being an independent set.
-The contraction of this einsum network gives the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$
-\begin{equation}
-I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-By mapping the independence polynomial solving problem to the einsum network contraction, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
-where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
-A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of $G$.~\cite{Markov2008}
-The pairwise tensor contraction also makes it possible to utilize fast basic linear algebra subprograms (BLAS) functions for certain tensor element types.
+    \begin{align*}
+        \sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}.
+    \end{align*}
+\end{example}
 
@@
 In the rest of this paper, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
-i.e. making the einsum network programming generic~\cite{Stepanov2014}.
+i.e. making the einsum network generic~\cite{Stepanov2014}.
 
@@
     \mymathbb{0} &= (),\\
-    \mymathbb{1} &= (1).
+    \mymathbb{1} &= (1).\label{eq:polynomial}
     \end{split}
@@
 y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right).
+\end{matrix}\right).\label{eq:lineareq}
 \end{align}
@@
 \subsection{The finite field algebra approach}
-It is possible to compute the independence polynomials exactly using 64 bit integers types only,
-even when the factors are larger than that can be represented by 64 bit integers.
-We achieve this by designing a finite field algebra $GF(p)$
+It sounds a bit over ambitious to compute the independence polynomial regorously using integer number types only,
+because the fixed width integer types are often too small to store the countings,
+while big integer with arbituary precision can be very slow and imcompatible with graphic processing units (GPU) devices.
+The solution we found is to computation on a finite field algebra $GF(p)$
 
@@
 \begin{enumerate}
-    \item One can still use Gaussian elimination~\cite{Golub2013} to solve a linear equation.
+    \item One can still use Gaussian elimination~\cite{Golub2013} to solve a linear equation \Eq{eq:lineareq}.
     This is because a field has the property that the multiplicative inverse exists for any non-zero value.
@@
 \end{enumerate}
-With these observations, we developed Algorithm~\ref{alg:finitefield} to compute independent polynomial exactly without introducing space overheads.
-In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers with fixed width $W$.
+With these observations, we developed Algorithm~\ref{alg:finitefield} to compute independence polynomial exactly without introducing space overheads.
+In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers of fixed width $W$.
 
@@
     \end{cases},\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma + \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
     \mymathbb{0} &= \{\}\infty^{-\infty},\\
-    \mymathbb{1} &= \{\boldsymbol 0\}\infty^{0},
+    \mymathbb{1} &= \{0^{\otimes n}\}\infty^{0},
 \end{split}
 \end{align}
+
 One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
@@
 By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save computational effort.
-We leave this as an exercise for readers.
-This algorithm is parallelizable.
+%We leave this as an exercise for readers.
+
+\begin{align}
+\begin{split}
+    \sigma_x\infty^x \oplus \sigma_y\infty^y &= \begin{cases}
+        {\rm select}(\sigma_x, \sigma_y)\infty^{\max(x,y)}, & x = y\\
+        \sigma_y\infty^{\max(x,y)}, & x < y\\
+        \sigma_x\infty^{\max(x,y)}, & x > y
+    \end{cases},\\
+    \sigma_x\infty^x \odot \sigma_y\infty^y &= (\sigma_x \lor^\circ \sigma_y)\infty^{x+y},\\
+    \mymathbb{0} &= 1^{\otimes n}\infty^{-\infty},\\
+    \mymathbb{1} &= 0^{\otimes n}\infty^{0},
+\end{split}
+\end{align}
+where the \texttt{select} function picks one of $\sigma_x$ and $\sigma_y$.
+One can decide an order by some criteria to make the algebra commutative and associative.
+In most cases, it does not matter if one pick randomly from them, the program just output one of optimal configuration randomly.
+
+\subsection{counting sub-optimal solutions}
+Some times people are interested in finding sub-optimal solutions efficiently.
+We modify the polynomial algebra a bit by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
+\begin{align}
+    \begin{split}
+    a \oplus b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
+    a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
+    \mymathbb{0} &= (),\\
+    \mymathbb{1} &= (1).\label{eq:polynomial}
+    \end{split}
+\end{align}
+By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
 
@@
 
-We do the same computation as independence polynoimal, the coefficients of resulting polynomial gives the counting of maximal independent sets.
+We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets.
 In many sparse graphs, this tensor network contraction approach is much faster than computing the maximal cliques of its complement and use Bron Kerbosch algorithms for finding maximum cliques.
@@
 
-We can
+We can see these two subgraphs produce exactly the same tensors.
 
@@
 \end{figure}
+Einsum network contraction is parallelizable. When the element type is immutable, one can just upload the data to GPU to enjoy the speed up.
 
@@
 \centerline{\begin{tikzpicture}
-    \def\r{0.1}
+    \def\r{0.08}
     \def\a{0.1}
@@
         \foreach \y in {1,...,5}
-            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+            \filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
     \foreach \x in {1,...,5}
         \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
-            \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
+            \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
             \draw [black,thick] (\x,\y) -- (\x,\y+1);
@@
         \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
-            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
+            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
             \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
@@
         }
+    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
+                    post length=0mm,pre length=0mm}}
+    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
 \end{tikzpicture}}
@@
 \centerline{\begin{tikzpicture}
-    \def\r{0.1}
+    \def\r{0.08}
     \def\a{0.07}
@@
     \def\sql{0.24}
+    \foreach[evaluate={\cr=0.1+0.5*Mod(\x,2)}] \x in {1,...,5}
+        \foreach[evaluate={\cg=0.1+0.3*Mod(\y,2); \cy=0.5-0.5*Mod(\y,2)}] \y in {1,...,5}{
+            %\filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l*2.5,\y+\l) (\x-\L*0.75,\y+\L*0.6) (\x-\L*0.6,\y+\L*0.75) (\x-\l,\y+\l*2.5) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l*2.5) (\x+\L*0.6,\y+\L*0.75) (\x+\L*0.75,\y+\L*0.6) (\x+\l*2.5,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
+            \ifnum \x < 5
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.5,\y);
+                \ifnum \y < 5
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y+0.3);
+                \fi
+                \ifnum \y > 1
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y-0.3);
+                \fi
+            \fi
+            \ifnum \x > 1
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.5,\y);
+                \ifnum \y < 5
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y+0.7);
+                \fi
+                \ifnum \y > 1
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y-0.7);
+                \fi
+            \fi
+            \ifnum \y < 5
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y+0.5);
+            \fi
+            \ifnum \y > 1
+                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y-0.5);
+            \fi
+        }
     \foreach \x in {1,...,5}
         \foreach \y in {1,...,5}{
-        \node[fill, regular polygon, 
-            regular polygon sides=3, scale=0.3] at (\x, \y) {};
+            \filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
         }
@@
             \ifnum \y < 5
-                \filldraw[fill=black] (\x-\a,\y+0.5-\a) rectangle (\x+\a, \y+0.5+\a);
-                \filldraw[fill=black] (\y+0.5-\a,\x-\a) rectangle (\y+0.5+\a, \x+\a);
+                \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
+                \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
             \fi
-            \filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l,\y+\l) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
         }
@@
         \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x+0.3-\a,\y+0.3-\a) rectangle (\x+0.3+\a, \y+0.3+\a);
-            \filldraw[fill=black] (\y+0.3-\a,\x+0.7-\a) rectangle (\y+0.3+\a, \x+0.7+\a);
-        }
+            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
+        }
+    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
+                    post length=0mm,pre length=0mm}}
+    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
 \end{tikzpicture}}
 
-\section{matching polynomial}
-One can generalize the generic einsum network for solving another \#P-complete problem, the matching polynomials.
+\section{Generalizing to other graph problems}
+Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded treewidth $k$ can be solved in linear time with respect to the graph size.
+Dynamic programming is a traditional approach to attack a $MSO$ problem, it can solve the MIS problem in $O(2^k)n$.
+An einsum network is closely related to dynamic programming.
+To be specific, the contraction of a einsum network is a special type of dynamic programming that its update rule can be characterized by a linear operation.
+An einsum network is strictly less expressive than $MSO$, the einsum network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
+\begin{align}
+    \begin{split}
+    \exists_X\forall_{u} (\forall_{v} {\rm adj}(u, v) \land (
+        &(u \not\in X \land v \not\in X \land B_{00}) \lor\\
+        &(u \not\in X \land v \in X \land B_{01}) \lor\\
+        &(u \in X \land v \not\in X \land B_{10}) \lor\\
+        &(u \in X \land v \in X \land B_{11})
+    ))\land\\
+    (
+        &(u \not\in X \land W_{0}) \lor\\
+        &(u \in X \land W_{1})
+    ),
+    \end{split}
+\end{align}
+while not all monadic second order logic can be represented as an einsum network contraction,
+for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
+At the cost of lossing expressiveness, we can encode the properties of the graph into the tensor elements.
+
+In the following, we introduce several other problems that can be solved in the framework of generic einsum network in $O(2^k n)$.
+The first one is the matching polynomials.
 A match polynomial of a graph $G$ is defined as

### 2021-08-06 src/demos.jl

@@ -5,8 +5,9 @@ using Random
 function case_r3(n, k=3; sc_target, seed=2)
     # generate a random regular graph of size 100, degree 3
     graph = (Random.seed!(seed); LightGraphs.random_regular_graph(n, k))
+    @assert length(connected_components(graph)) == 1  # connected graph
     # optimize the contraction order using KaHyPar + Greedy
-    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40)
+    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40, imbalances=0:0.001:1)
     return optcode
 end
 

### 2021-08-09 paper/paper.tex
upate

@@
 \usepackage{multicol}
+\usepackage{cancel}
 \usepackage[framemethod=TikZ]{mdframed}
@@
     We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
+    We also show how to analyse the local properties of a graph by contracting an open einsum network.
 \end{abstract}
@@
 \section{Introduction}
-In this work, we introduce a new method to solve the classic graph problem, finding independent sets.
+In this work, we introduce a tensor based framework to study the famous graph problem of finding independent sets.
 Given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
 Finding the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$ belongs to the complexity class NP-complete~\cite{Hastad1996}, which is unlikely to be decided in polynomial time.
-It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbituary small possitive $\epsilon$.
+It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbituarily small possitive $\epsilon$.
 The naive algorithm of enumerating all configuration space gives a $2^{|V|}$ time solution.
@@
 The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for graphs with small tree width $tw(G)$, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
-People are interested in solving this problem better not only because it is a NP-complete problem that directly related to other NP-complete prolems like maximal cliques and vertex cover~\cite{Moore2011},
+People are interested in solving the independent set problem better not only because it is a NP-complete problem that directly related to other NP-complete prolems like maximal cliques and vertex cover~\cite{Moore2011},
 but also for its close relation with physical applications like hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
-In these applications, knowing the MIS size and one of the optimal solution is not the only goal.
+However, in these applications, knowing the MIS size and one of the optimal solution is not the only goal.
 %A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
@@
 These questions includes but not limited to, counting all independent sets, obtaining all indenepent sets of size $\alpha(G)$ and $\alpha(G)-1$,
-counting the number of (maximal) independent sets of different sizes.
+counting the number of (maximal) independent sets of different sizes, and understanding the effect of a local gadget.
 In this work, we attack this problem by mapping it to an generic ``einsum'' network.
-It does not give a better time complexity comparing to dynamic programming, but is versatile enough to answer the above questions by engineering the tensor elements.
+It does not give a better time complexity comparing to dynamic programming, but is versatile enough to answer the above questions by engineering the tensor elements with minimum effort.
 
 \section{Einsum network}
-The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
-Einstein's notation is originally proposed as a generalization to of multiplication between two matrices to the contraction between multiple tensors.
+%The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
+Einstein's notation is originally proposed as a generalization to of binary matrix multiplication to n-ary tensor contraction.
 Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
-It is denoted as $C_i^k = A_i^j B_j^k$ in the Einstein's original notation, where the paired subscript and superscript $j$ is a dummy index summed over.
-One can map a tensor network to a muti-graph with open edges by viewing a tensor in the expression on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining labels as open edges.
+In Einstein's notation, it is denoted as $C_i^k = A_i^j B_j^k$, where the paired subscript and superscript $j$ is a dummy index summed over, hence each index appears precisely twice.
+When we have multiple tensors doing the above sum-product operation, we get a tensor network~\cite{Orus2014}.
+A tensor network has a nice a muti-graph with open edges.
+We view a tensor on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
 
 \begin{example}
-    A tensor networks $C_i^l = A_{ij}^k B^l_k V^j$, where its graphical notation as the following.
-One can easily check a label in a tensor network representation appears precisely twice.
+    A tensor networks $C_i^l = A_{ij}^k B^l_k V^j$ has the following graphical representation.
 
@@
 
-Numpy programmers make a generalization of this notation by not restricting the number of times a label is used by tensors,
-hence whether an index appears as a superscript or a subscript makes no sense now.
-It has different names in different context, like sum-product network and factor graph~\cite{Bishop2006}.
-The graphical representation of an einsum is a hypergraph, where an edge (degree of freedom) can be shared by a arbituary number of nodes (tensors).
+Einsum network is a generalization of tensor network by not restricting the number of times a label appears,
+hence whether an index is a superscript or a subscript makes no sense now.
+It is also called sum-product network or factor graph~\cite{Bishop2006} in some contexts.
+The graphical representation of an einsum is a hypergraph, where an edge (label) can be shared by an arbituary number of vertices (tensors).
 
 \begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum but not a tensor network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
 Its hypergraph representation is as the following, where we use different color to annotate different hyperedges.
@@
 where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-By mapping the independence polynomial solving problem to the einsum network contraction, one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+The benefit of mapping the independent set problem to the einsum network is one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
 where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
-A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of the line graph of a tensor network, here it corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
+A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of the line graph of a tensor network, 
+here it corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
 The pairwise tensor contraction also makes it possible to utilize fast basic linear algebra subprograms (BLAS) functions for certain tensor element types.
@@
     \end{tikzpicture}}
+    The contraction of this network can be done in a pairwise order.
     \begin{align*}
-        \sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}.
+        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}.\\
+        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e)_{s_e}\right) W(x_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c)_{s_c}\right)\right)\right.\\
+        &\phantom{XXX}\left.\left(B_{s_bs_c}\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a)_{s_a}\right)\right)\right)\\
+        =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e
     \end{align*}
@@
 A semiring is a ring without additive inverse, while a commutative semiring is a semiring that multiplication commutative.
-To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relation must hold for arbituary three elements $a, b, c \in R$.
+To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relations must hold for arbituary three elements $a, b, c \in R$.
 \begin{align*}
@@
 
-In the rest of this paper, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
+In the following, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
 i.e. making the einsum network generic~\cite{Stepanov2014}.
@@
 \subsection{The fitting and Fourier transformation approaches}
-Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of $m+1$ random real numbers, e.g. $\{0, 1, 2, \ldots, m\}$.
+Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of real numbers of cardinality $m+1$.
 We compute the einsum contraction for each $x_i \in X$ and obtain the following relations
@@
 because the fixed width integer types are often too small to store the countings,
-while big integer with arbituary precision can be very slow and imcompatible with graphic processing units (GPU) devices.
-The solution we found is to computation on a finite field algebra $GF(p)$
+while big integer with varying width can be very slow and imcompatible with graphic processing units (GPU) devices.
+This problem will be solved if we computate on a finite field algebra $GF(p)$
 
@@
     \mymathbb{1} &= 1.
-\end{split}
+\end{split}\label{eq:finitefield}
 \end{align}
@@
 
-\section{Computing maximum independent set size and its corresponding degeneracy and configurations}
-Obtaining the maximum independent set size and its degeneracy can be computational more efficient. Let $x=\infty$, then the independence polynomial becomes
+\subsection{Maximal independence polynomial}
+Let us denote the neighbor of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent sets that there does not exist a vertex $v$ that $N[v] \cap I_m = \emptyset$.
+Let us modify the einsum network for computing independence polynomial to count maximal independent sets.
+We define a tensor on $N[v]$ to capture this property
+\begin{align}
+    T(x)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+        s_vx & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
+        1-s_v& otherwise.\\
+    \end{cases}
+\end{align}
+As an example, for a vertex of degree 2, the resulting rank 3 tensor is
+\begin{align}
+    T(x)=\left(\begin{matrix}
+    \left(\begin{matrix}
+        0 &1 \\
+        1 &1
+    \end{matrix}\right)\\
+    \left(\begin{matrix}
+        x &0 \\
+        0 &0
+    \end{matrix}\right)
+    \end{matrix}\right).
+\end{align}
+
+We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets, or the maximal independence polynoimal.
+The treewidth of this new tensor network is often larger than the one for computing independence polynomial.
+However, in many sparse graphs, this tensor network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron Kerbosch algorithm.
+
+\section{Maximum independent sets and its counting problem}
+In the previous section, we mentioned how to compute independence polynomial for a given maximum independent set size $\alpha(G)$, but we didn't mention how to compute this number.
+The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
 \begin{equation}
@@
     \mymathbb{0} &= 0\infty^{-\infty}\\
-    \mymathbb{1} &= 1\infty^{0}
+    \mymathbb{1} &= 1\infty^{0}\label{eq:countingtropical}
 \end{split}
@@
 In the program, we only store the power $x$ and the corresponding factor $a_x$ that initialized to $1$.
-This algebra is consistent with the one we derived in ~\cite{Liu2021} that uses the tropical tensor network for solving spin glass ground states.
+This algebra is the same as the one in ~\cite{Liu2021} for counting spin glass ground states.
 If one is only interested in obtaining $\alpha(G)$, he can drop the factor parts, then the algebra of $x$ becomes the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
 
-One may also want to obtain all ground state configurations, it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$.
+\subsection{Sub-optimal solutions}
+Some times people are interested in finding sub-optimal solutions efficiently.
+We modify the polynomial algebra a bit by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
+\begin{align}
+    \begin{split}
+    a \oplus b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
+    a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
+    \mymathbb{0} &= (),\\
+    \mymathbb{1} &= (1).\label{eq:max2poly}
+    \end{split}
+\end{align}
+By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
+
+\section{Enumerating configurations}
+One may also want to obtain all solutions, it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$,
 We design a new element type that having algebra
+\begin{align}
+\begin{split}
+    s \oplus t &= s \cup t\\
+    s \odot t &= \{\sigma \lor^\circ \tau | \sigma \in s, \tau \in t\}\\
+    \mymathbb{0} &= \{\}\\
+    \mymathbb{1} &= \{0^{\otimes n}\}
+\end{split}\label{eq:set}
+\end{align}
 \iffalse
-\begin{align}
-\begin{split}
-    s_x \oplus s_y &= s_x \cup s_y\\
-    s_x \odot s_y &= \{\sigma \lor \tau | \sigma \in s_x, \tau \in s_y\}\\
-    \mymathbb{0} &= \{\}\\
-    \mymathbb{1} &= \{\boldsymbol 0\}
-\end{split}
-\end{align}
-\fi
 \begin{align}
@@
 \end{align}
-
-One can easily check that this replacement does not change the fact that the algebra is a commutative semiring.
-We first initialize the bit strings of the variable $x$ in the vertex tensor to a vertex index $i$ dependent onehot vector $x_i = \boldsymbol{e}_{i}$,
-then we contract the tensor network. The resulting object will give us the set of all optimal configurations.
-By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save computational effort.
+\fi
+where $\lor^\circ$ is the Hadamard logic or operation over two bit strings, which means joining of two local configurations.
+The variable $x$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$,
+where $e_i$ is a one hot vector of size $|G|$.
+One can easily check this algebra is a commutative semiring.
+When we use the above algebra as factors in \Eq{eq:countingtropical}, the resulting algebra is also a commutative semiring.
+With this new element type, the einsum network contraction will give all solutions rather than just a number for counting.
+By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save the computational effort.
 %We leave this as an exercise for readers.
 
+\iffalse
 \begin{align}
@@
 \end{align}
-where the \texttt{select} function picks one of $\sigma_x$ and $\sigma_y$.
-One can decide an order by some criteria to make the algebra commutative and associative.
-In most cases, it does not matter if one pick randomly from them, the program just output one of optimal configuration randomly.
-
-\subsection{counting sub-optimal solutions}
-Some times people are interested in finding sub-optimal solutions efficiently.
-We modify the polynomial algebra a bit by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
+\fi
 \begin{align}
 \begin{split}
-    a \oplus b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
-    a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (),\\
-    \mymathbb{1} &= (1).\label{eq:polynomial}
-    \end{split}
-\end{align}
-By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
-
-\subsection{bounding the enumeration space}
-When we try to implement the above algebra for enumerating configurations, we find the space overhead is larger than than we have expected.
-It stores more than nessesary intermedite configurations. To speed up the computation, we use $\alpha(G)$ that much easier to compute for bounding.
+    \sigma \oplus \tau &= {\rm select}(\sigma, \tau)\\
+    \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
+    \mymathbb{0} &= 1^{\otimes n},\\
+    \mymathbb{1} &= 0^{\otimes n},
+\end{split}\label{eq:singleconfig}
+\end{align}
+where the \texttt{select} function picks one of $\sigma_x$ and $\sigma_y$ by some criteria to make the algebra commutative and associative, e.g. by their integer values.
+In practise, one can just pick randomly from them, then the program will output one of the optimal configurations randomly.
+
+\subsection{Bounding the enumeration space}
+If one implements the above algebra for enumerating configurations naively, he will find the program stores more than nessesary intermedite configurations and cause significant overheads in space.
+To speed up the computation, we use $\alpha(G)$ to bound the search space.
 We first compute the value of $\alpha(G)$ with tropical numbers and cache all intermediate tensors.
@@
 Finally, we perform masked matrix multiplication using the new element type with the above algebra for obtaining all configurations.
-To compute the masks, we ``back propagate'' the masks step by step through contraction process using the cached intermediate tensors.
-Consider a tropical matrix multiplication $C = A B$, we have the following inequality
+Notice that these masks are in fact tensor elements with nonzero gradients with respect to MIS size, we compute these masks by back propagating gradients.
+To derive the backward rule, we consider a tropical matrix multiplication $C = A B$, we have the following inequality
 \begin{align}
@@
 has nonzero gradient).
-Let the mask for $C$ being $\overline C$, the backward rule for gradient masks reads
+Let the mask for $C$ being $\overline C$, the backward rule for ``gradient'' masks reads
 \begin{align}
@@
 
-\section{Counting maximal independent sets}
-Let us denote the neighbor of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent sets that there is no such vertex $v$ that $N[v] \cap I_m = \emptyset$.
-Let us modify the einsum network for computing independence polynomial to count maximal independent sets.
-We define a tensor on $N[v]$ to capture this property
-\begin{align}
-    T(x)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
-        1-s_v& otherwise.\\
-    \end{cases}
-\end{align}
-As an example, for a vertex of degree 2, the resulting rank 3 tensor is
-\begin{align}
-    T(x)=\left(\begin{matrix}
-    \left(\begin{matrix}
-        0 &1 \\
-        1 &1
-    \end{matrix}\right)\\
-    \left(\begin{matrix}
-        x &0 \\
-        0 &0
-    \end{matrix}\right)
-    \end{matrix}\right).
-\end{align}
-
-We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets.
-In many sparse graphs, this tensor network contraction approach is much faster than computing the maximal cliques of its complement and use Bron Kerbosch algorithms for finding maximum cliques.
-However, the treewidth of this new tensor network is larger than the one for independence polynomial because it can not utilize some structures of the original graph,
-while the original tensor network can be trivially reduced to this one.
-We will use an example in the appendix to show why this tensor network is harder to contract.
-
-\section{Automated branching}
+\section{Tropical tensors for automated branching}
 % check http://www.tcs.rwth-aachen.de/independentset/ for more rules
@@
 \end{align}
-where $\leq^\circ$ is the Hadamard less or equal operations.
+where $\leq^\circ$ is the Hadamard less or equal to operation.
 
@@
 \begin{align}
-(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compress}.
+(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
 \end{align}
@@
 If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranted to give the same maximum independant set size.
-It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compressrule} (a) and (b).
+It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compactifying} (a) and (b).
 If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independant sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
@@
     \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
-    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compressrule}
+    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compactifying}
 \end{figure}
 
-\begin{theorem}[]
-    A MIS-compact tropical tensor is optimal, i.e. none of its none zero entries can be removed without accessing global information.
+\begin{theorem}
+    A MIS-compact tropical tensor is optimal, i.e. any of its nonzero entries can produce the only global optimal solution given a proper environment.
 \end{theorem}
@@
 
-\subsection{The tensor network compression detects branching rules automatically}
-In the following, we are going to show tropical tensor networks with least restrictive principle can automatically discover branching rules.
-We denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
-It is the effective degree of freedoms per vertex in $R$.
+\subsection{The tensor network compactifying detects branching rules automatically}
+Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
+by including its neighborhoods,
+and keep only the configurations that has the potential to produce the only maximum independent sets.
+Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for $N^3[v]$, one can discover the optimal branching vector automatically.
 
@@
 After contracting $N[v]$, $v$ becomes an internal degree of freedom.
-Applying tensor compression rule \Eq{eq:compress}, the resulting rank 4 tropical tensor is
+Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
 
@@
 
-The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
-It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
+If we use sets for counting, one can check all configurations too.
+By studying the correlation between vertex variables, one can easily see $x_v$ does not co-exist with other vertex variables.
+These anti-correlation determines possible branching vectors in the maximum independent set problem.
+
+\begin{align}
+    S_{juwk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        1+x_v & - \\
+        - & ~~~~x_jx_u
+        \end{matrix}\right)_{ju}&
+        \left(\begin{matrix}
+        - & ~~~~x_ux_k \\
+        ~~~~x_jx_k & ~~~~x_ux_jx_k
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        - & ~~~~x_wx_u \\
+        ~~~~x_wx_j & ~~~~x_wx_jx_u
+        \end{matrix}\right)_{ju} &
+        \left(\begin{matrix}
+        ~~~~x_wx_k & ~~~~x_wx_kx_u \\
+        ~~~~x_wx_kx_j & ~~~~x_jx_ux_wx_k
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{wk},
+\end{align}
+where we use ``-'' to denote an entry is forbiden.
+
+%If we denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
+%The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
+%It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
 
@@
 otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
+Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighborhood of $v$.
 If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
@@
 %Hence, the \textit{least restrictive principle} captures the mirror rule.
-
 In the following example, since $u\in N^2(v)$ and $N(v) \backslash N(u)$ is a clique, $u$ is a mirror of $v$.
@@
 After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
-Applying tensor compression rule \Eq{eq:compress}, the resulting rank 4 tropical tensor is
+Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
 
@@
         ~~~~1 & ~~~~2 \\
-        -\infty & -\infty
+        ~~~~\cancel{1} & ~~~~\cancel{2}
         \end{matrix}\right)_{ju}&
         \left(\begin{matrix}
-        -\infty & -\infty \\
+        ~~~~\cancel{1} & -\infty \\
         ~~~~2 & -\infty
@@
         \left(\begin{matrix}
-        -\infty & -\infty \\
+        ~~~~\cancel{1} & ~~~~\cancel{2} \\
         -\infty & -\infty
@@
         \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk}.
-\end{align}
-
-In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
-which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
+    \end{matrix}\right)_{wk},
+\end{align}
+where entries striked through are removed by compactifying.
+
+%In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
+%which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
 
 \begin{corollary}[satellite rule] % satellite rule
-Let $G$ be agraph $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
+Let $G$ be a graph, $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
 The set of satellites of a node $v$ is denotedby $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
@@
 After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
-Applying tensor compression rule \Eq{eq:compress}, the resulting rank 3 tropical tensor is
+Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 3 tropical tensor is
 \begin{align}
@@
         ~~~~1 & ~~~~2 \\
-        ~~~~2 & -\infty
+        ~~~~2 & ~~~~\cancel{2}
         \end{matrix}\right)_{ju}\\
         \left(\begin{matrix}
-        -\infty & -\infty \\
-        -\infty & -\infty
+        ~~~~\cancel{1} & -\infty \\
+        ~~~~\cancel{2} & -\infty
         \end{matrix}\right)_{ju}
@@
     \end{matrix}\right)
-    \xrightarrow[\text{compress, -2}]{}
+    \xrightarrow[\text{compactify, -2}]{}
     \left(\begin{matrix}
@@
         \left(\begin{matrix}
-            ~~~~1 & -\infty\\
-            ~~~~2 & -\infty
+            ~~~~1 & ~~~~\cancel{1}\\
+            ~~~~2 & ~~~~\cancel{2}
         \end{matrix}\right) \\
@@
             ~~~~1 & ~~~~2\\
-            -\infty & -\infty
+            ~~~~\cancel{0} & \cancel{1}
         \end{matrix}\right) &
         \left(\begin{matrix}
-            ~~~~2 & -\infty\\
-            -\infty & -\infty
+            ~~~~2 & ~~~~\cancel{2}\\
+            ~~~~\cancel{1} & ~~~~\cancel{2}
         \end{matrix}\right)
@@
 
-We can see these two subgraphs produce exactly the same tensors.
+We can see these two subgraphs produce exactly the same compact tensor.
+When we replace the original tensor with this gadget, the solution.
 
@@
     \caption{Benchmark results for computing different properties with different element types.
+The right axis is only for the dashed line.
     }\label{fig:benchmark}
@@
             {regular number}     & {counting all indenepent sets} \\
-            {tropical number}     & {finding the maximum independent set size} \\
-            {tropical number with counting}     & {finding both the maximum independent set size and its degeneracy} \\
-            {tropical number with configuration}     & {finding the maximum independent set size and one of the optimal configurations} \\
-            {tropical number with multiple configurations}     & {finding the maximum independent set size and all optimal configurations} \\
-            {polynomial}     & {computing the indenpendence polynomials exactly} \\
+            {tropical number} (\Eq{eq:countingtropical})    & {finding the maximum independent set size} \\
+            {tropical number with counting} (\Eq{eq:countingtropical})     & {finding both the maximum independent set size and its degeneracy} \\
+            {tropical number with configurations} (\Eq{eq:singleconfig})     & {finding the maximum independent set size and one of the optimal configurations} \\
+            {tropical number with sets} (\Eq{eq:set})    & {finding the maximum independent set size and all optimal configurations} \\
+            {polynomial} (\Eq{eq:polynomial})     & {computing the indenpendence polynomials exactly} \\
+            {truncated polynomial} (\Eq{eq:max2poly})     & {counting the suboptimal independent sets} \\
             {complex number}     & {fitting the indenpendence polynomials with fast fourier transformation} \\
-            {finite field algebra}     & {fitting the indenpendence polynomials exactly using number theory} \\
+            {finite field algebra} \Eq{eq:finitefield}    & {fitting the indenpendence polynomials exactly using number theory} \\
             \bottomrule
@@
 
-\section{When tensor network is worse than einsum network}\label{app:tensorbad}
+\section{When a tensor network is worse than an einsum network}\label{app:tensorbad}
 
@@
 \end{tikzpicture}}
-
-Once we represent a $\delta$ tensor as a general tensor, the complexity of this contraction is $\approx 2^{2L}$.
-Its einsum network representation is
+where a small circle on an edge is a diagonal tensor.
+Its rank is $8$ in the bulk.
+If we contract this tensor network in a naive columwise order, the maximum intermediate tensor is approximately $3L$, giving a space complexity $\approx 2^{3L}$.
+If we treat it as the following einsum network
 
@@
     \def\sql{0.24}
+    \pgfmathsetseed{2}
     \foreach[evaluate={\cr=0.1+0.5*Mod(\x,2)}] \x in {1,...,5}
         \foreach[evaluate={\cg=0.1+0.3*Mod(\y,2); \cy=0.5-0.5*Mod(\y,2)}] \y in {1,...,5}{
+            \edef\R{\pdfuniformdeviate 255}
+            \edef\G{\pdfuniformdeviate 255}
+            \edef\B{\pdfuniformdeviate 255}
+            \xdefinecolor{MyColor}{RGB}{\R,\G,\B}
             %\filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l*2.5,\y+\l) (\x-\L*0.75,\y+\L*0.6) (\x-\L*0.6,\y+\L*0.75) (\x-\l,\y+\l*2.5) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l*2.5) (\x+\L*0.6,\y+\L*0.75) (\x+\L*0.75,\y+\L*0.6) (\x+\l*2.5,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
             \ifnum \x < 5
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.5,\y);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.5,\y);
                 \ifnum \y < 5
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y+0.3);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y+0.3);
                 \fi
                 \ifnum \y > 1
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y-0.3);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y-0.3);
                 \fi
@@
             \ifnum \x > 1
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.5,\y);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.5,\y);
                 \ifnum \y < 5
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y+0.7);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y+0.7);
                 \fi
                 \ifnum \y > 1
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y-0.7);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y-0.7);
                 \fi
@@
             \ifnum \y < 5
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y+0.5);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y+0.5);
             \fi
             \ifnum \y > 1
-                \draw [thick, color={rgb:red,\cr;green,\cg;yellow,\cy}, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y-0.5);
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y-0.5);
             \fi
@@
 \end{tikzpicture}}
+where we use different colors to distinguish different hyperedges.
+Now, the vertex tensor is always rank $1$.
+With the same naive contraction order, we can see the maximum intermediate tensor is approximately of size $2^L$ by counting the colors.
 
 \section{Generalizing to other graph problems}
+There are some other graph problems that can be encoded in an einsum network.
+To understand its representation power, it is a good starting point to connect it with dynamic programming because
+an einsum network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
 Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded treewidth $k$ can be solved in linear time with respect to the graph size.
-Dynamic programming is a traditional approach to attack a $MSO$ problem, it can solve the MIS problem in $O(2^k)n$.
-An einsum network is closely related to dynamic programming.
-To be specific, the contraction of a einsum network is a special type of dynamic programming that its update rule can be characterized by a linear operation.
-An einsum network is strictly less expressive than $MSO$, the einsum network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
+Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the einsum network approach.
+We mentioned in the main text that einsum network has nice mathematic property make it easier for generic programming.
+The cost is, the einsum network is less expressive than dynamic programming,
+\iffalse
+The cost is, it is less expressive than MSO because the einsum network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
 \begin{align}
     \begin{split}
-    \exists_X\forall_{u} (\forall_{v} {\rm adj}(u, v) \land (
-        &(u \not\in X \land v \not\in X \land B_{00}) \lor\\
-        &(u \not\in X \land v \in X \land B_{01}) \lor\\
-        &(u \in X \land v \not\in X \land B_{10}) \lor\\
-        &(u \in X \land v \in X \land B_{11})
-    ))\land\\
-    (
-        &(u \not\in X \land W_{0}) \lor\\
-        &(u \in X \land W_{1})
-    ),
+    \exists_X\forall_{u}&(\\
+    &\quad\forall_{v} 
+    \neg {\rm adj}(u, v) \lor
+    ({\rm adj}(u, v) \land ( \hspace{5em}\text{$\triangleright$ restrictions on edges}\\
+    &\quad\quad(u \not\in X \land v \not\in X \land B_{00}) \lor\\
+    &\quad\quad(u \not\in X \land v \in X \land B_{01}) \lor\\
+    &\quad\quad(u \in X \land v \not\in X \land B_{10}) \lor\\
+    &\quad\quad(u \in X \land v \in X \land B_{11})\\
+    &\quad)\\
+    &))\land\\
+    &(\hspace{16.5em}\text{$\triangleright$ restrictions on vertices}\\
+    &\quad(u \not\in X \land W_{0}) \lor\\
+    &\quad(u \in X \land W_{1})\\
+    &),
     \end{split}
@@
 At the cost of lossing expressiveness, we can encode the properties of the graph into the tensor elements.
-
-In the following, we introduce several other problems that can be solved in the framework of generic einsum network in $O(2^k n)$.
-The first one is the matching polynomials.
-A match polynomial of a graph $G$ is defined as
+\fi
+However, that are still some other problems that can be expressed in the framework of generic einsum network.
+\subsection{Matching problem}
+A matching polynomial of a graph $G$ is defined as
 \begin{align}
@@
 \end{align}
-
 Here, we use bond index $v \rightarrow w$ to label tensors.
 
+\subsection{k-Coloring}
+Let us use 3-coloring on the vertex as an example. We can define a vertex tensor as
+\begin{align}
+    W = \left(\begin{matrix}
+        r_v\\
+        g_v\\
+        b_v
+    \end{matrix}\right),
+\end{align}
+and an edge tensor as
+\begin{align}
+    B = \left(\begin{matrix}
+        0 & 1 & 1\\
+        1 & 0 & 1\\
+        1 & 1 & 0
+    \end{matrix}\right).
+\end{align}
+The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+By designing generic types as tensor elements, one should be able to get all possible colorings.
+It is straight forward to define the k-coloring problem on edges hence we will not discuss the detailed construction here.
+
 \end{document}

### 2021-08-11 paper/paper.tex
update

@@
 %%%%%% Comment related
-\newcommand{\red}[1]{[{\bf  \color{red}{LW: #1}}]}
-\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{LW: #1}}}]}
+\newcommand{\red}[1]{[{\bf  \color{red}{ST: #1}}]}
+\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{ST: #1}}}]}
+\newcommand{\green}[1]{[{\bf  \color{green}{XG: #1}}]}
+\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
 \newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
-\newcommand{\violet}[1]{[{\bf  \color{violet}{MLS: #1}}]}
-\newcommand{\green}[1]{[{\bf  \color{green}{TZ: #1}}]}
-\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{TZ: #1}}}]}
 \newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
 \newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
-\newcommand{\orange}[1]{\iffalse[{\bf  \color{orange}{Jo: #1}}]\fi}
 
@@
 
-\title{Solving the maximum independant set problem by generic programming einsum networks
+\title{Solving the independent set problem by generic programming einsum networks
 \thanks{\funding{...}}
@@
 \begin{abstract}
-	Solving the maximum independent set size problem by mapping the graph to an einsum network. 
+	This paper is about solving the independent set problem by eincoding this problem to an einsum network. 
     We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
@@
 Given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
-Finding the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$ belongs to the complexity class NP-complete~\cite{Hastad1996}, which is unlikely to be decided in polynomial time.
-It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbituarily small possitive $\epsilon$.
-The naive algorithm of enumerating all configuration space gives a $2^{|V|}$ time solution.
+The problem of finding the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$ belongs to the complexity class NP-complete~\cite{Hastad1996}, which is unlikely to be decided in polynomial time.
+It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
+The exhaustive search for a solution costs time $2^{|V|}$.
 More efficient algorithms to compute the MIS size exactly includes the branching algorithm and dynamic programming.
 Without changing the fact of exponential scaling in computing time, the branching algorithm gives a smaller base.
-For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm gives a time complexity $1.1893^n n ^{O(1)}$.
+For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm has a time complexity $1.1893^n n ^{O(1)}$.
 The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for graphs with small tree width $tw(G)$, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
-People are interested in solving the independent set problem better not only because it is a NP-complete problem that directly related to other NP-complete prolems like maximal cliques and vertex cover~\cite{Moore2011},
+People are interested in solving the independent set problem better not only because it is an NP-complete problem that directly related to other NP-complete problems like maximal cliques and vertex cover~\cite{Moore2011},
 but also for its close relation with physical applications like hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
-However, in these applications, knowing the MIS size and one of the optimal solution is not the only goal.
+However, in these applications, knowing the MIS size and one of the optimum solutions is not the only goal.
 %A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
@@
 People often ask different questions about independent sets in order to understand the landscape of their models better.
-These questions includes but not limited to, counting all independent sets, obtaining all indenepent sets of size $\alpha(G)$ and $\alpha(G)-1$,
+These questions includes but not limited to, counting all independent sets, obtaining all independent sets of size $\alpha(G)$ and $\alpha(G)-1$,
 counting the number of (maximal) independent sets of different sizes, and understanding the effect of a local gadget.
@@
 
-\section{Einsum network}
+\section{Einsum networks}
 %The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
@@
 When we have multiple tensors doing the above sum-product operation, we get a tensor network~\cite{Orus2014}.
-A tensor network has a nice a muti-graph with open edges.
-We view a tensor on the right hand side as a vertex in a graph, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
+A tensor network can be represented as a mutigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
 
 \begin{example}
-    A tensor networks $C_i^l = A_{ij}^k B^l_k V^j$ has the following graphical representation.
-
-\centerline{\begin{tikzpicture}
+    A tensor networks $C_i^l = A_{ij}^{km} B^l_{km} V^j$ has the following multigraph representation.
+
+\centerline{\begin{tikzpicture}[
+    dot/.style = {circle, fill, minimum size=#1,
+                inner sep=0pt, outer sep=0pt},
+    dot/.default = 6pt  % size of the circle diameter 
+                    ]  
     \def\dx{0};
-    \def\r{0.25}
+    \def\r{0.25cm}
     \def\ax{0}
@@
     \def\cy{-1}
-    \filldraw[fill=black] (\ax+\dx,\ax) circle [radius=\r];
-    \filldraw[fill=black] (\bx+\dx,\by) circle [radius=\r];
-    \filldraw[fill=black] (\cx+\dx,\cy) circle [radius=\r];
+    \node[color=white, fill=black, dot=2*\r] at (\ax+\dx,\ax) (a) {A};
+    \node[color=white, fill=black, dot=2*\r] at (\bx+\dx,\by) (b) {B};
+    \node[color=white, fill=black, dot=2*\r] at (\cx+\dx,\cy) (c) {V};
     %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
     %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
-    \draw [black,thick] (\ax+\dx,\ay) -- (\bx+\dx,\by);
-    \draw [black,thick] (\ax+\dx,\ay) -- (\cx+\dx,\cy);
-    \draw [black,thick] (\ax+\dx,\ay) -- (\ax+\dx-0.8,\ay);
-    \draw [black,thick] (\bx+\dx,\by) -- (\bx+\dx+0.8,\by);
-    \node[color=white] at (\ax+\dx,\ax) {A};
-    \node[color=white] at (\bx+\dx,\by) {B};
-    \node[color=black] at (0.5*\ax+0.5*\bx-0.2+\dx,0.5*\ay+0.5\by+0.2) {k};
+    \draw [black,thick] (a) .. controls (0.4, 0.6) .. (b);
+    \draw [black,thick] (a) .. controls (0.6, 0.4) .. (b);
+    \draw [black,thick] (a) -- (c);
+    \draw [black,thick] (a) -- (\ax+\dx-0.8,\ay);
+    \draw [black,thick] (b) -- (\bx+\dx+0.8,\by);
+    \node[color=black] at (0.5*\ax+0.5*\bx-0.3+\dx,0.5*\ay+0.5\by+0.3) {k};
+    \node[color=black] at (0.5*\ax+0.5*\bx+0.3+\dx,0.5*\ay+0.5\by-0.3) {m};
     \node[color=black] at (0.5*\ax+0.5*\cx+\dx+0.2,0.5*\ay+0.5\cy+0.2) {j};
@@
     \node[color=black] at (\bx+\dx+0.5,\by-0.2) {l};
-    \node[color=white] at (\cx+\dx,\cy) {V};
 \end{tikzpicture}}
@@
 
-Einsum network is a generalization of tensor network by not restricting the number of times a label appears,
+Einsum network is a generalization of tensor network by not restricting the number of times a label appears in the notation,
 hence whether an index is a superscript or a subscript makes no sense now.
 It is also called sum-product network or factor graph~\cite{Bishop2006} in some contexts.
-The graphical representation of an einsum is a hypergraph, where an edge (label) can be shared by an arbituary number of vertices (tensors).
+The graphical representation of an einsum is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
 
@@
 although one can easily translate an einsum network to the equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
-It can sometime increase the contraction complexity of a graph. We have an example demonstrating this in \App{app:tensorbad}.
+It can sometime increase the contraction complexity of a graph. We have an example demonstrating this point in \App{app:tensorbad}.
 
 \section{Independence polynomial}
-One can encode the independent set problem on graph $G$ to an einsum network by placing a rank one tensor of size $2$ on vertex $i$
+One can encode the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$ to an einsum network.
+Independence polynomial is an important graph polynomial that contains the counting information of an independent set problem. It is defined as
+\begin{equation}
+I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
+We encode this polynomial to an einsum network by placing a rank one tensor of size $2$ parametrized by $x_i$ on a vertex $i$
 \begin{equation}
@@
 \end{equation}
-and a rank two tensor of size $2 \times 2$ on edge $(i,j)$
+and a rank two tensor of size $2 \times 2$ on an edge $(i,j)$
 \begin{equation}
@@
 \end{equation}
-where a tensor index $s_i$ is a boolean variable that being 1 if vertex $i$ is in the independent set, 0 otherwise.
+where a tensor index $s_i$ is a boolean variable that having the meaning of being 1 if vertex $i$ is in the independent set, 0 otherwise.
 It corresponds to a hyperedge in the hypergraph.
-$x_i$ is a variable.
 The contraction of such an einsum network gives
 \begin{equation}
-    A(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j}.
+    P(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
 \end{equation}
-Here, the einsum runs over all vertex configurations $\{s_1,\ldots,s_n\}$ and accumulates the product of tensor elements to the scalar output.
-Let $x_i = x$, then the product over vertex tensors gives a factor $x^k$, where $k=\sum_i s_i$ is the vertex set size, 
-and the product over edge tensors gives a factor $0$ for configurations not being an independent set.
-The contraction of this einsum network gives the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$
-\begin{equation}
-I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-The benefit of mapping the independent set problem to the einsum network is one can take the advantage of recently developed techiniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
-where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
-A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$, where $tw(G)$ is the treewidth of the line graph of a tensor network, 
-here it corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
-The pairwise tensor contraction also makes it possible to utilize fast basic linear algebra subprograms (BLAS) functions for certain tensor element types.
+where the summation runs over all vertex configurations $\{s_1,\ldots,s_n\}$ and accumulates the product of tensor elements to the scalar output $P$.
+We can see an edge tensor represents the restriction on an edge that if both vertices connected by it are included in the set, then such configuration has no contribution to the output.
+When we set $x_i = x$, the contraction result corresponds to the independence polynomial.
+One can see the connection from the fact that the product over vertex tensor elements gives a factor $x^k$, where $k=\sum_i s_i$ counts the set size, 
+and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set, $0$ otherwise.
+One directly benefit of mapping the independent set problem to an einsum network is one can take the advantage of recently developed techniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+where people evaluate an einsum network by pairwise contracting tensors in a heuristic order.
+A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$.
+Here $tw(G)$ is the tree width of the line graph of an einsum hypergraph, while the line graph of an einsum hypergraph corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
+The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up our computation for certain tensor element types.
 
@@
     Mapping a graph (left) to an einsum network, the resulting einsum network is shown in the right panel.
-    A vertex is mapped to a hyperedge in the einsum's graphical notation.
-    An edge is mapped to an edge tensor.
+    In the einsum's graphical representation, a vertex is mapped to a hyperedge,
+    and an edge is mapped to an edge tensor.
 
@@
         =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e)_{s_e}\right) W(x_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c)_{s_c}\right)\right)\right.\\
-        &\phantom{XXX}\left.\left(B_{s_bs_c}\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a)_{s_a}\right)\right)\right)\\
-        =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e
+        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a)_{s_a}\right)\right)\right)\right)\\
+        =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e\\
+        =&1+5x+4x^2
     \end{align*}
@@
 A semiring is a ring without additive inverse, while a commutative semiring is a semiring that multiplication commutative.
-To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relations must hold for arbituary three elements $a, b, c \in R$.
+To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
 \begin{align*}
@@
 By contracting the einsum network with polynomial type, the final result is the exact representation of the independence polynomial.
-In the program, the multiplication can be evaluated efficiently with the convolution theorem.
-The only problem of this method is it suffers from a space overhead that propotional to the maximum independant set size because each polynomial requires a vector of such size to store the factors.
+In the program, the multiplication can be evaluated efficiently with the convolution theorem~\cite{Schonhage1971}.
+The only problem of this method is it suffers from a space overhead that proportional to the maximum independent set size because each polynomial requires a vector of such size to store the factors.
 In the following subsections, we managed to solve this problem.
@@
 The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
-The polynomial fitting is esentially about solving the following linear equation
+The polynomial fitting is essentially about solving the following linear equation
 \begin{align}
@@
 
-Let us rearange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a descrete fourier transformation (DFT) matrix.
-Then we can obtain the factors using the inverse fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing diferent $r$, one can obtain better precision in low independant set size region  ($\omega<1$) and high independant set size region ($\omega>1$).
+Let us rearrange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a discrete Fourier transformation (DFT) matrix.
+Then we can obtain the factors using the inverse Fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
+By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) and high independent set size region ($\omega>1$).
 
 \subsection{The finite field algebra approach}
-It sounds a bit over ambitious to compute the independence polynomial regorously using integer number types only,
-because the fixed width integer types are often too small to store the countings,
-while big integer with varying width can be very slow and imcompatible with graphic processing units (GPU) devices.
-This problem will be solved if we computate on a finite field algebra $GF(p)$
+It is possible but not trivial to compute the independence polynomial rigorously using integer number types only.
+The hardness originates from the practical consideration of computing speed and precision.
+Fixed width integer types are often too small to store the counting,
+while big integer with varying width can be very slow and incompatible with graphic processing units (GPU) devices.
+This problem can be solved by introducing finite field algebra $GF(p)$
 
@@
 \begin{enumerate}
-    \item One can still use Gaussian elimination~\cite{Golub2013} to solve a linear equation \Eq{eq:lineareq}.
-    This is because a field has the property that the multiplicative inverse exists for any non-zero value.
-    The multiplicative inverse here can be computed with the extended Euclidean algorithm.
-    \item Given the remainders of a larger integer $x$ over a set of coprime integers $\{p_1, p_2, \ldots, p_n\}$,
-    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the chinese remainder theorem.
-    With this, one can infer big integers even though its bit width is larger than the register size.
+    \item One can use Gaussian elimination~\cite{Golub2013} to solve a linear equation \Eq{eq:lineareq}
+    because it is a generic function that works for any elements with field algebra.
+    The multiplicative inverse of a finite field algebra can be computed with the extended Euclidean algorithm.
+    \item Given the remainders of a larger unkown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
+    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem.
+    With this, one can infer big integers from small integers.
 \end{enumerate}
 With these observations, we developed Algorithm~\ref{alg:finitefield} to compute independence polynomial exactly without introducing space overheads.
-In the algorithm, except the computation of chinese remainder theorem, all computations are done with integers of fixed width $W$.
+In the algorithm, except the computation of Chinese remainder theorem, all computations are done with integers of fixed width $W$.
 
@@
     \While{true}{
-        compute the largest prime $p$ that $\gcd(p, P) = 1 \land p \leq 2^W$\;
-
-        compute the tensor network contraction on $GF(p)$ and obtain $Y = (y_0, y_1, \ldots , y_m) \pmod p $\;
+        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p \leq 2^W$\;
+
+        compute the tensor contraction on $GF(p)$ and obtain $Y = (y_0, y_1, \ldots , y_m) \pmod p $\;
 
@@
 \subsection{Maximal independence polynomial}
-Let us denote the neighbor of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
+Some times people are interested in knowing maximal solutions to understand why their program is trapped in a local minimal.
+Then they might want to compute the maximal independence polynomial.
+Let us denote the neighbour of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
 A maximal independent set $I_m$ is an independent sets that there does not exist a vertex $v$ that $N[v] \cap I_m = \emptyset$.
-Let us modify the einsum network for computing independence polynomial to count maximal independent sets.
-We define a tensor on $N[v]$ to capture this property
-\begin{align}
-    T(x)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
+Let us modify the einsum network for computing independence polynomial by adding this restriction.
+Instead of defining the restriction on vertices and edges, we define it on $N[v]$
+\begin{align}
+    T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+        s_vx_v & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
         1-s_v& otherwise.\\
@@
 \begin{align}
-    T(x)=\left(\begin{matrix}
+    T(x_v)=\left(\begin{matrix}
     \left(\begin{matrix}
@@
     \left(\begin{matrix}
-        x &0 \\
+        x_v &0 \\
         0 &0
@@
 
-We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets, or the maximal independence polynoimal.
-The treewidth of this new tensor network is often larger than the one for computing independence polynomial.
-However, in many sparse graphs, this tensor network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron Kerbosch algorithm.
+We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets, or the maximal independence polynomial.
+The computational complexity of this new einsum network is often larger than the one for computing independence polynomial.
+However, in many sparse graphs, this einsum network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron-Kerbosch algorithm.
 
 \section{Maximum independent sets and its counting problem}
-In the previous section, we mentioned how to compute independence polynomial for a given maximum independent set size $\alpha(G)$, but we didn't mention how to compute this number.
+In the previous section, we focused on computing independence polynomial for a given maximum independent set size $\alpha(G)$, but we didn't mention how to compute this number.
 The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
@@
 This algebra is the same as the one in ~\cite{Liu2021} for counting spin glass ground states.
-If one is only interested in obtaining $\alpha(G)$, he can drop the factor parts, then the algebra of $x$ becomes the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
+If one is only interested in obtaining $\alpha(G)$, he can drop the factor parts, then the new algebra becomes the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
 
@@
 Some times people are interested in finding sub-optimal solutions efficiently.
-We modify the polynomial algebra a bit by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
+We define a truncated polynomial algebra by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
 \begin{align}
@@
 \end{align}
-By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
+%By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
+In the program, we need a data structure that contains three fields, the largest order $k$ and factors for two largest orders $a_k$ and $a_{k-1}$.
 
@@
 One may also want to obtain all solutions, it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$,
-We design a new element type that having algebra
+We design a new element type having the following algebra
 \begin{align}
@@
 The variable $x$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$,
-where $e_i$ is a one hot vector of size $|G|$.
+where $\boldsymbol{e}_i$ is a one hot vector of size $|G|$.
 One can easily check this algebra is a commutative semiring.
-When we use the above algebra as factors in \Eq{eq:countingtropical}, the resulting algebra is also a commutative semiring.
+When we use the above algebra as factors of independence polynomials, the resulting algebra is also a commutative semiring.
 With this new element type, the einsum network contraction will give all solutions rather than just a number for counting.
@@
 where the \texttt{select} function picks one of $\sigma_x$ and $\sigma_y$ by some criteria to make the algebra commutative and associative, e.g. by their integer values.
-In practise, one can just pick randomly from them, then the program will output one of the optimal configurations randomly.
+In practise, one can just pick randomly from them, then the program will output one of the configurations randomly.
 
 \subsection{Bounding the enumeration space}
-If one implements the above algebra for enumerating configurations naively, he will find the program stores more than nessesary intermedite configurations and cause significant overheads in space.
-To speed up the computation, we use $\alpha(G)$ to bound the search space.
+When one uses the set algebra in \Eq{eq:set} to represent the factors in \Eq{eq:countingtropical} for enumerating all optimum configurations, he will find the program stores more than necessary intermediate configurations and cause significant overheads in space.
+To speed up the computation, we use $\alpha(G)$ to bound the searching space.
 We first compute the value of $\alpha(G)$ with tropical numbers and cache all intermediate tensors.
 Then we compute a boolean masks for each cached tensor, where we use a boolean true to represent a tensor element having contribution to the maximum independent set (i.e.
-with a nonzero gradient) and boolean false otherwise.
+with a non-zero gradient) and boolean false otherwise.
 Finally, we perform masked matrix multiplication using the new element type with the above algebra for obtaining all configurations.
-Notice that these masks are in fact tensor elements with nonzero gradients with respect to MIS size, we compute these masks by back propagating gradients.
+Notice that these masks are in fact tensor elements with non-zero gradients with respect to MIS size, we compute these masks by back propagating gradients.
 To derive the backward rule, we consider a tropical matrix multiplication $C = A B$, we have the following inequality
@@
 \end{align}
-
 Moving $B_{ik}$ to the right hand side, we have
@@
 The equality holds if and only if element $A_{ij}$ contributions to $C$ (i.e.
-has nonzero gradient).
+has non-zero gradient).
 Let the mask for $C$ being $\overline C$, the backward rule for ``gradient'' masks reads
@@
 where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard product, boolean false is treated as tropical zero and boolean true is treated as tropical one.
-This rule defined on matrix multiplication can be easily generalized to the einsum of two tensors by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum.
-
-\section{Tropical tensors for automated branching}
+This rule defined on matrix multiplication can be easily generalized to einsum by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum operation.~\cite{} \blue{maybe add an appendix?}  % my blog
+
+\section{Tropical tensors for automated branching}\blue{$?$}
 % check http://www.tcs.rwth-aachen.de/independentset/ for more rules
-Branching rules can be automatically discovered by contracting the tropical einsum network for a subgraph $R \subseteq G$.
-Let us denote the resulting tropical tensor of rank $|C|$ as $A$, where $C$ is the set of boundary vertices defined as $C := \{c | c\in R \land c \in G\backslash R\}$ and $|C|$ the size of $C$.
-Each tensor entry $A_{\sigma}$ is a local maximum independant set size with a fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$ by marginalizing the inner degrees of freedom.
-If we are only interested in finding a single maximum independent set rather than enumerating all possible solutions,
-this tensor can be further ``compresed'' by setting some entries to tropical zero.
-Let us define a relation of \textit{less restrictive} as
+Branching rules can be automatically discovered by contracting the einsum network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
+Let $C$ be the set of boundary vertices defined as $C := \{u | u\in R \land (\exists v \in (G\backslash R) \land {\rm adj}(u, v))\}$, then the rank of the resulting tensor $A$ is $|C|$.
+Here, we use ${\rm adj}(u, v)$ to denote two vertices $u$ and $v$ are adjacent to each other.
+Each tensor entry $A_{\sigma}$ is a local maximum independent set size for the fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$.
+Suppose our goal is to find the maximum independent set size,
+then this tensor can be further ``compactified'' by removing some entries.
+To determine which entry can be removed, let us define a relation of \textit{less restrictive} as
 \begin{align}
@@
 \begin{definition}
-A tensors $A$ is \textit{MIS-compact} if are no two nonzero entries of it that one is ``better'' than another,
-where an entry $A_{\sigma_a}$ is ``better'' than $A_{\sigma_b}$ if
-\begin{align}
-(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
+A tensors $A$ is \textit{MIS-compact} if
+\begin{align}
+\forall{\sigma_b}\neg \exists{\sigma_a}(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
 \end{align}
@@
 
-If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranted to give the same maximum independant set size.
+If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranteed to give the same maximum independent set size.
 It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compactifying} (a) and (b).
-If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independant sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
-Hence, we can set $A_{\sigma_b}$ to tropical zero safely.
+If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independent sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
+Hence, we can remove entry $A_{\sigma_b}$ safely.
 %among boundary configurations with equal local maximum independent sizes,
@@
 \begin{theorem}
-    A MIS-compact tropical tensor is optimal, i.e. any of its nonzero entries can produce the only global optimal solution given a proper environment.
+    A MIS-compact tropical tensor can not be further reduce without gloal information, i.e. any of its non-zero entries can produce the only global optimal solution given a proper environment.
 \end{theorem}
@@
     %Given $A_\{\sigma_a}$ is better than $A_\{\sigma_b\}$, any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
-    Let use prove it by showing $\forall \sigma$ in a MIS-compact tropical tensor for a subgraph $R$, there exists a graph $G$ that $R\subseteq G$ and $\sigma$ is the only boundary configuration that produces the maximum independent set.
-    i.e. no tensor entry can be removed without knowledge about $G\backslash R$.
-    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the bounary configuration.
-    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, $\alpha(N[v] \cap (G \backslash R)) = 0$, otherwise, $\alpha(N[v] \cap (G\backslash R)) = \infty$, meanwhile, for any $v, w \in C$, $N[v]\cap N[w] = \emptyset$.
-    The simplest construction is connecting vertices that $\sigma_v=0$ with infinite many mutually disconnected vertices as illustrated in the following graph.
-
-    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 6cm 0cm}, clip]{proofoptimal.pdf}}
-
-    Then we have the maximum independent set size with boundary configuration $\sigma$ being $\alpha(G,\sigma) = \infty (|C|-|\sigma|) + A_{\sigma}$,
-    where $|\sigma|$ is defined as the number of $1$s in $\sigma$.
-    Let us assume there exists another configuration $\tau$ that generating the same or even better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
-    Then we have $\tau \prec \sigma$, otherwise it will suffer from infinite punishment from $G\backslash R$.
+    Let us prove it by showing for any $\sigma$ in a MIS-compact tropical tensor of a subgraph $R$, there exists a parent graph $G$ that $R\subseteq G$ and $\sigma$ is the boundary configuration that gives the only maximum independent set.
+    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the boundary configuration.
+    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, we connect it with two vertices $u, w \in G \backslash R$ that ${\rm adj}(v, u) \land {\rm adj}(u, w) \land \neg{\rm adj}(v, w)$.
+Otherwise, we attach infinite many disconnected neighbors to $v$.
+
+    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 5cm 0cm}, clip]{proofoptimal.pdf}}
+    Then we have the maximum independent set size $\alpha(G,\sigma) = A_{\sigma} + \infty (|C|-\sum_{v=1}^{|C|}\sigma_v) + \sum_{v=1}^{|C|} 1-\sigma_v$.
+    Let us assume there exists another configuration $\tau$ that generating the same or better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
+    Then we have $\tau \prec \sigma$, otherwise it will loss infinite contribution from the environment.
     For such a $\tau$, we have $A_\tau < A_\sigma$, otherwise $A_\sigma \prec A_\tau$ contradicts with $A$ being MIS-compact.
-    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} < \alpha(G,\sigma)$, which contradicts with our preassumtion.
-Such $\tau$ does not exist and $\sigma$ is the only boundary configuration that $\alpha(G) = \alpha(G, \sigma)$.
+    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} + \sum_{v=1}^{|C|} 1-\sigma_v < \alpha(G,\sigma)$, hence $\sigma$ is the only boundary configuration that gives the maximum independent set for this graph.
 \end{proof}
 
-\subsection{The tensor network compactifying detects branching rules automatically}
+\subsection{The einsum network compactification detects branching rules automatically}
 Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
-by including its neighborhoods,
-and keep only the configurations that has the potential to produce the only maximum independent sets.
-Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for $N^3[v]$, one can discover the optimal branching vector automatically.
+by including its neighbourhoods,
+and keep only the configurations that has the potential to produce the only maximum independent set.
+Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for the $k$-th neighbourhood $N^k[v]$, one can discover the optimal branching vector automatically.
+In the following, we are going to introduce several important rules for branching in the literature and show how it is connected to our tensor formulation.
 
 \begin{corollary}\label{rule:one} % basic
-  If a vertex $v$ is in an independent set $I$, then none of its neighbors can be in $I$.
+  If a vertex $v$ is in an independent set $I$, then none of its Neighbors can be in $I$.
 On the other hand, if $I$ is a maximum (and thus maximal) independent set,
-and thus if $v$ is not in $I$ then at least one of its neighbors is in $I$.
+and thus if $v$ is not in $I$ then at least one of its Neighbors is in $I$.
 \end{corollary}
@@
 Contract $N[v]$ and the resulting tensor $A$ has a rank $|N(v)|$.
-Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independant set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
-If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independant set size.
+Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independent set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
+If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independent set size.
 
@@
 After contracting $N[v]$, $v$ becomes an internal degree of freedom.
-Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
+Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
 
@@
         \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{wk},
+\end{align}
+where we use ``-'' to denote an entry is forbidden.
+If we use sets for counting, one can check all configurations too. The resulting polynomial tensor is
+\begin{align}
+    P_{juwk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        1+x_v & - \\
+        - & ~~x_jx_u
+        \end{matrix}\right)_{ju}&
+        \left(\begin{matrix}
+        - & x_ux_k \\
+        ~~~~x_jx_k & ~~~~x_ux_jx_k
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        - & x_wx_u \\
+        x_wx_j & x_wx_jx_u
+        \end{matrix}\right)_{ju} &
+        \left(\begin{matrix}
+        x_wx_k & x_wx_kx_u \\
+        x_wx_kx_j & x_jx_ux_wx_k
+        \end{matrix}\right)_{ju}
     \end{matrix}\right)_{wk}.
@@
 
-If we use sets for counting, one can check all configurations too.
 By studying the correlation between vertex variables, one can easily see $x_v$ does not co-exist with other vertex variables.
 These anti-correlation determines possible branching vectors in the maximum independent set problem.
-
-\begin{align}
-    S_{juwk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        1+x_v & - \\
-        - & ~~~~x_jx_u
-        \end{matrix}\right)_{ju}&
-        \left(\begin{matrix}
-        - & ~~~~x_ux_k \\
-        ~~~~x_jx_k & ~~~~x_ux_jx_k
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        - & ~~~~x_wx_u \\
-        ~~~~x_wx_j & ~~~~x_wx_jx_u
-        \end{matrix}\right)_{ju} &
-        \left(\begin{matrix}
-        ~~~~x_wx_k & ~~~~x_wx_kx_u \\
-        ~~~~x_wx_kx_j & ~~~~x_jx_ux_wx_k
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk},
-\end{align}
-where we use ``-'' to denote an entry is forbiden.
-
+It is easier to see if we list the set of optimal solutions as
+\begin{align}
+    \begin{split}
+    S_{juwkv} = \{&00001, 10001, 01010, 10010, 11010, 10100,\\&01100, 11100, 00110, 01110, 10110, 11110\}.
+    \end{split}
+\end{align}
 %If we denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
@@
 %It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
+The corresponding branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
 
@@
 otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
-Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighborhood of $v$.
+Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighbourhood of $v$.
 If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
-since clique has at most one node in the MIS, by moving the occuppied node to the interior, we obtain a ``better'' solution.
+since clique has at most one node in the MIS, by moving the occupied node to the interior, we obtain a ``better'' solution.
 %Hence, the \textit{least restrictive principle} captures the mirror rule.
@@
 After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
-Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
+Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
 
@@
 \end{align}
-where entries striked through are removed by compactifying.
+where entries stroked through are removed by compactification. The corresponding polynomial tensor is
+
+\begin{align}
+    P_{juwk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        1+x_v & x_u+x_ux_v \\
+        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{}\\
+        \end{matrix}\right)_{ju}&
+        \left(\begin{matrix}
+        ~~~~\cancel{} & - \\
+        x_jx_k & -
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{} \\
+        ~~~~~~~- & ~~~~~~~~~~~~~-
+        \end{matrix}\right)_{ju} &
+        \left(\begin{matrix}
+        ~~~~- & - \\
+        ~~~~- & -
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{wk}.
+\end{align}
+One can see $w$, as a mirror of $v$ does not appear in the maximum independent set after compactification.
 
@@
 %which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
+\begin{align}
+    \begin{split}
+    S_{juwkv} = \{&00001, 01001, 10010\}.
+    \end{split}
+\end{align}
 
@@
 Let $G$ be a graph, $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
-The set of satellites of a node $v$ is denotedby $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
+The set of satellites of a node $v$ is denoted by $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
 \begin{equation}
@@
 After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
-Applying tensor compactifying rule \Eq{eq:compactifying}, the resulting rank 3 tropical tensor is
+Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 3 polynomial tensor is
+\iffalse
 \begin{align}
@@
 \end{align}
-
-There are 3 nonzero entries. The internal configurations of entry $T(j=1, u=0, k=0) = 2$ is $(v=0, w =1)$,
-that of entry $T(j=0, u=1, k=0)=2$ is $(v=1, w=0)$, and that of entry $T(j=0, u=0, k=0)=1$ is $(v=1, w=0)$ or $(v=0, w=1)$.
-For entry $T(j=0, u=0, k=0)=1$, we post-select the internal degree of freedom as $(v=0, w=1)$.
-Then we can see the satellite rule either ${v, u} \in I$ or $v \notin I$ is satisfied.
-In this case, the effective branching number is $3^{1/5}\approx 1.2457$.
-
-\subsection{gadget design}
+\fi
+
+\begin{align}
+    P_{juk} = \left(\begin{matrix}
+        \left(\begin{matrix}
+        1+x_w+x_v & x_u + x_ux_v \\
+        x_j+x_wx_j & ~~~~~~~~~~~~\cancel{}
+        \end{matrix}\right)_{ju}\\
+        \left(\begin{matrix}
+        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~- \\
+        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~-
+        \end{matrix}\right)_{ju}
+    \end{matrix}\right)_{k}.
+\end{align}
+
+By choosing one of the optimal configurations in each entry,
+we can see the satellite rule of either ${v, u} \in I$ or $v \notin I$ is satisfied.
+
+\begin{align}
+    \begin{split}
+    S_{juwkv} = \{&\{00100,00001\}, 10100, 01001\}.
+    \end{split}
+\end{align}
+%In this case, the effective branching number is $3^{1/5}\approx 1.2457$.
+
+%We can use the conditional entropy to discover branching rules automatically. 
+%Let us take one best configuration a time from each entry of the compact polynomial matrix,
+%and denote the resulting configuration set as $S$.
+%The conditional entropy matrix here can be defined as
+%\begin{align}
+%    C_{uv} = H(s_u|s_v)
+%\end{align}
+%when two variables are strongly correlated to each other, the corresponding entry should be zero.
+
+\subsection{gadget design}\blue{$\times$}
 
@@
 
-\section{benchmarks}
+\section{Benchmarks and case study}
 We run a sequetial program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results bellow.
@@
 
-\section{discussion}
-We introduced in the main text how to compute the indenpendence polynomial, maximum independent set and optimal configurations.
-It is interesting that although these properties are global,
-they can be solved by designing different element types that having two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
-One thing in common is that they all defines a commutative semiring.
-Here, we want the $\oplus$ and $\odot$ operations being commutative because we do not want the contraction result of an einsum network to be sensitive to the contraction order.
-We show most of the implementation in Appendix \ref{sec:technical}. It is supprisingly short.
+\section{Discussion}
+We introduced in the main text how to compute the independence polynomial, maximum independent set and optimal configurations,
+derived the backward rule for tropical einsum to bound the search of solution space.
+%And, we also discussed how to use tensor network to study the local properties of a graph.
+Although many of these properties are global,
+we can encode it to different tensor element types as commutative semirings.
+The power of Einsum network's is not limited to the indenepent set problem, in \App{app:otherproblems} we show how to map matching problem and k-coloring to an einsum network.
+Here, we want to discuss more from the programming perspective.
+We show some of the Julia language~\cite{Bezanson2012} implementations in Appendix \ref{sec:technical}, you will find it being surprisingly short.
+What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
 The style that we program is called generic programming,
-it is about writing a single copy of code, feeding different types into it, and the program computing the result with a proper performance.
-It is language dependent feature. If someone want to implement this algorithm in python,
-one has to rewrite the matrix multiplication for different element types in C and then export the interface to python.
+meaning one can feed different data types into a same program, and the program will compute the result with a proper performance.
 In C++, users can use templates for such a purpose.
-In our work, we chose Julia because its just in time compiling is very powerful that it can generate fast code dynamically for users.
-Elements of fixed size, such as the finite field algebra, tropical number, tropical number with counting/configuration field used in the main text can be inlined in an array.
-Furthermore, these inlined arrays can be upload to GPU devices for faster generic matrix multiplication implemented in CUDA.jl.
+We chose Julia because its just in time compiling is very powerful that it can generate fast code dynamically for users.
+Elements of fixed size, such as the finite field algebra, truncated polynomial, tropical number and tropical number with counting or configuration field used in the main text can be inlined in an array.
+Furthermore, these inlined arrays can be upload to GPU devices for faster generic matrix multiplication implemented in CUDA.jl~\cite{Besard2018}.
 
@@
 
-One can install these packages by opening a julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
+One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
 \begin{lstlisting}
@@
 
-It may supprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding and sparsity related parts,
+It may surprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding and sparsity related parts,
 all are contained in this appendix. After installing required packages, one can open a Julia REPL and copy the following code into it.
@@
 We will not show any example about implementing the backward rule here because it has approximately 100 lines of code.
-Please checkout our Github repository \href{https://github.com/Happy-Diode/NoteOnTropicalMIS}{https://github.com/Happy-Diode/NoteOnTropicalMIS}.
+Please checkout our GitHub repository \href{https://github.com/Happy-Diode/NoteOnTropicalMIS}{https://github.com/Happy-Diode/NoteOnTropicalMIS}.
 
@@
 Its rank is $8$ in the bulk.
-If we contract this tensor network in a naive columwise order, the maximum intermediate tensor is approximately $3L$, giving a space complexity $\approx 2^{3L}$.
+If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor is approximately $3L$, giving a space complexity $\approx 2^{3L}$.
 If we treat it as the following einsum network
@@
 
-\section{Generalizing to other graph problems}
+\section{Generalizing to other graph problems}\label{app:otherproblems}
 There are some other graph problems that can be encoded in an einsum network.
@@
 an einsum network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded treewidth $k$ can be solved in linear time with respect to the graph size.
+Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded tree width $k$ can be solved in linear time with respect to the graph size.
 Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the einsum network approach.
-We mentioned in the main text that einsum network has nice mathematic property make it easier for generic programming.
+We mentioned in the main text that einsum network has nice analytic property make it easier for generic programming.
 The cost is, the einsum network is less expressive than dynamic programming,
@@
 while not all monadic second order logic can be represented as an einsum network contraction,
-for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
-At the cost of lossing expressiveness, we can encode the properties of the graph into the tensor elements.
+for example, it is hard to construct a einsum network to decide whether a graph is connected or not.
+At the cost of losing expressiveness, we can encode the properties of the graph into the tensor elements.
 \fi
@@
 
-\subsection{k-Coloring}
-Let us use 3-coloring on the vertex as an example. We can define a vertex tensor as
+\subsection{k-Colouring}
+Let us use 3-colouring on the vertex as an example. We can define a vertex tensor as
 \begin{align}
@@
 \end{align}
-The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
-By designing generic types as tensor elements, one should be able to get all possible colorings.
-It is straight forward to define the k-coloring problem on edges hence we will not discuss the detailed construction here.
+The number of possible colouring can be obtained by contracting this einsum network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+By designing generic types as tensor elements, one should be able to get all possible colourings.
+It is straight forward to define the k-colouring problem on edges hence we will not discuss the detailed construction here.
 

### 2021-08-12 paper/paper.tex
update

@@
 
-\title{Solving the independent set problem by generic programming einsum networks
+\title{Solving the independent set problem by generic programming tensor networks
 \thanks{\funding{...}}
@@
 \begin{abstract}
-	This paper is about solving the independent set problem by eincoding this problem to an einsum network. 
+	This paper is about solving the independent set problem by eincoding this problem to a tensor network. 
     We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
-    We also show how to analyse the local properties of a graph by contracting an open einsum network.
+    We also show how to analyse the local properties of a graph by contracting an open tensor network.
 \end{abstract}
@@
 \begin{keywords}
-  maximum independent set, einsum network
+  maximum independent set, tensor network
 \end{keywords}
@@
 counting the number of (maximal) independent sets of different sizes, and understanding the effect of a local gadget.
-In this work, we attack this problem by mapping it to an generic ``einsum'' network.
+In this work, we attack this problem by mapping it to an generic tensor network.
 It does not give a better time complexity comparing to dynamic programming, but is versatile enough to answer the above questions by engineering the tensor elements with minimum effort.
 
-\section{Einsum networks}
+\section{Tensor networks}
 %The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
-Einstein's notation is originally proposed as a generalization to of binary matrix multiplication to n-ary tensor contraction.
+A tensor network can be viewed as a generalization to of binary matrix multiplication to n-ary tensor contraction.
 Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
-In Einstein's notation, it is denoted as $C_i^k = A_i^j B_j^k$, where the paired subscript and superscript $j$ is a dummy index summed over, hence each index appears precisely twice.
-When we have multiple tensors doing the above sum-product operation, we get a tensor network~\cite{Orus2014}.
-A tensor network can be represented as a mutigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
+A traditional tensor network refers to the Einstein's notation.
+In this notation, the matrix multiplication is denoted as $C_i^k = A_i^j B_j^k$, where the paired subscript and superscript $j$ is a dummy index summed over, hence each index appears precisely twice.
+When we have multiple tensors doing the above sum-product operation, we get a traditional tensor network~\cite{Orus2014}.
+A traditional tensor network can be represented as a mutigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
 
 \begin{example}
-    A tensor networks $C_i^l = A_{ij}^{km} B^l_{km} V^j$ has the following multigraph representation.
+   A traditional tensor network $C_i^l = A_{ij}^{km} B^l_{km} V^j$ has the following multigraph representation.
 
@@
 
-Einsum network is a generalization of tensor network by not restricting the number of times a label appears in the notation,
+Here, we want to use a generalized tensor network notation by not restricting the number of times a label appears in the notation,
 hence whether an index is a superscript or a subscript makes no sense now.
-It is also called sum-product network or factor graph~\cite{Bishop2006} in some contexts.
-The graphical representation of an einsum is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
+It is also called einsum, sum-product network or factor graph~\cite{Bishop2006} in some contexts.
+The graphical representation of a tensor network in this paper is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
 
 \begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is an einsum network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
 Its hypergraph representation is as the following, where we use different color to annotate different hyperedges.
@@
 
-In the main text, we stick to the einsum notation rather than the tensor network notation.
-As a note to those who are more familiar with tensor network representation,
-although one can easily translate an einsum network to the equivalent tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
+In the main text, we stick to the our generalized tensor network notation rather than the traditional notation.
+As a note to those who are more familiar with the traditional tensor network representation,
+although one can easily translate a generalized tensor network to the equivalent traditional tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
 It can sometime increase the contraction complexity of a graph. We have an example demonstrating this point in \App{app:tensorbad}.
@@
 \section{Independence polynomial}
-One can encode the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$ to an einsum network.
+One can encode the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$ to a tensor network.
 Independence polynomial is an important graph polynomial that contains the counting information of an independent set problem. It is defined as
@@
 where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-We encode this polynomial to an einsum network by placing a rank one tensor of size $2$ parametrized by $x_i$ on a vertex $i$
+The problem of computing independence polynomial belongs to the complexity class \#P-hard.
+A traditional approach to compute independence polynomial rigorusly requires a computing time $O(1.442^n)$~\cite{Ferrin2014}\blue{I am not sure about this complexity, this is baed on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
+%with which computing the independence polynomial for a square lattice of size $30\times 30$ would be impossible.
+There are some interests in approximating this polynomial efficiently~\cite{Harvey2018}, but here, we focus on the rigorous approaches.
+We encode this polynomial to a tensor network by placing a rank one tensor of size $2$ parametrized by $x_i$ on a vertex $i$
 \begin{equation}
@@
 It corresponds to a hyperedge in the hypergraph.
-The contraction of such an einsum network gives
+The contraction of such a tensor network gives
 \begin{equation}
@@
 and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set, $0$ otherwise.
-One directly benefit of mapping the independent set problem to an einsum network is one can take the advantage of recently developed techniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
-where people evaluate an einsum network by pairwise contracting tensors in a heuristic order.
+One directly benefit of mapping the independent set problem to a tensor network is one can take the advantage of recently developed techniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
+where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
 A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$.
-Here $tw(G)$ is the tree width of the line graph of an einsum hypergraph, while the line graph of an einsum hypergraph corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
+Here $tw(G)$ is the tree width of the line graph of a tensor network hypergraph, while the line graph of a tensor network hypergraph corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up our computation for certain tensor element types.
@@
 \begin{example}
-    Mapping a graph (left) to an einsum network, the resulting einsum network is shown in the right panel.
-    In the einsum's graphical representation, a vertex is mapped to a hyperedge,
+    Mapping a graph (left) to a tensor network, the resulting tensor network is shown in the right panel.
+    In the generalize tensor network's graphical representation, a vertex is mapped to a hyperedge,
     and an edge is mapped to an edge tensor.
@@
 
-Before contracting the einsum network and evaluating the independence polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
+Before contracting the tensor network and evaluating the independence polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
 Instead, we treat them as the additive identity and multiplicative identity of a commutative semiring.
@@
 In the following, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
-i.e. making the einsum network generic~\cite{Stepanov2014}.
+i.e. making the tensor network generic~\cite{Stepanov2014}.
 
@@
 \end{align}
-By contracting the einsum network with polynomial type, the final result is the exact representation of the independence polynomial.
+By contracting the tensor network with polynomial type, the final result is the exact representation of the independence polynomial.
 In the program, the multiplication can be evaluated efficiently with the convolution theorem~\cite{Schonhage1971}.
@@
 Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of real numbers of cardinality $m+1$.
-We compute the einsum contraction for each $x_i \in X$ and obtain the following relations
+We compute the tensor network contraction for each $x_i \in X$ and obtain the following relations
 \begin{align}
@@
 A maximal independent set $I_m$ is an independent sets that there does not exist a vertex $v$ that $N[v] \cap I_m = \emptyset$.
-Let us modify the einsum network for computing independence polynomial by adding this restriction.
+Let us modify the tensor network for computing independence polynomial by adding this restriction.
 Instead of defining the restriction on vertices and edges, we define it on $N[v]$
@@
 We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets, or the maximal independence polynomial.
-The computational complexity of this new einsum network is often larger than the one for computing independence polynomial.
-However, in many sparse graphs, this einsum network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron-Kerbosch algorithm.
+The computational complexity of this new tensor network is often larger than the one for computing independence polynomial.
+However, in many sparse graphs, this tensor network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron-Kerbosch algorithm.
 
@@
 When we use the above algebra as factors of independence polynomials, the resulting algebra is also a commutative semiring.
-With this new element type, the einsum network contraction will give all solutions rather than just a number for counting.
+With this new element type, the tensor network contraction will give all solutions rather than just a number for counting.
 By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save the computational effort.
@@
 where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard product, boolean false is treated as tropical zero and boolean true is treated as tropical one.
-This rule defined on matrix multiplication can be easily generalized to einsum by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by an einsum operation.~\cite{} \blue{maybe add an appendix?}  % my blog
+This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by a tensor contraction.~\cite{} \blue{maybe add an appendix?}  % my blog
 
@@
 % check http://www.tcs.rwth-aachen.de/independentset/ for more rules
-Branching rules can be automatically discovered by contracting the einsum network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
+Branching rules can be automatically discovered by contracting the tensor network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
 Let $C$ be the set of boundary vertices defined as $C := \{u | u\in R \land (\exists v \in (G\backslash R) \land {\rm adj}(u, v))\}$, then the rank of the resulting tensor $A$ is $|C|$.
@@
 
-\subsection{The einsum network compactification detects branching rules automatically}
+\subsection{The tensor network compactification detects branching rules automatically}
 Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
@@
 %It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
-The corresponding branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
+The branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
 
@@
 \end{figure}
-Einsum network contraction is parallelizable. When the element type is immutable, one can just upload the data to GPU to enjoy the speed up.
+Tensor network contraction is parallelizable. When the element type is immutable, one can just upload the data to GPU to enjoy the speed up.
 
@@
 We introduced in the main text how to compute the independence polynomial, maximum independent set and optimal configurations,
-derived the backward rule for tropical einsum to bound the search of solution space.
-%And, we also discussed how to use tensor network to study the local properties of a graph.
+derived the backward rule for tropical tensor network to bound the search of solution space.
+%And, we also discussed how to use @tensor network to study the local properties of a graph.
 Although many of these properties are global,
 we can encode it to different tensor element types as commutative semirings.
-The power of Einsum network's is not limited to the indenepent set problem, in \App{app:otherproblems} we show how to map matching problem and k-coloring to an einsum network.
+The power of tensor network's is not limited to the indenepent set problem, in \App{app:otherproblems} we show how to map matching problem and k-coloring to a tensor network.
 Here, we want to discuss more from the programming perspective.
@@
 \begin{description}
-	\item[OMEinsum] a package for einsum,
-	\item[OMEinsumContractionOrders] a package for finding the optimal contraction order for einsum \\ \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl},
+	\item[OMEinsum] a package for the \texttt{einsum} function,
+	\item[OMEinsumContractionOrders] a package for finding the optimal contraction order for the \texttt{einsum} function \\ \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl},
 	\item[TropicalGEMM] a package for efficient tropical matrix multiplication (compatible with OMEinsum),
@@
 
-\section{When a tensor network is worse than an einsum network}\label{app:tensorbad}
+\section{Why not introducing $\delta$ tensors}\label{app:tensorbad}
 
@@
 
-Its tensor network representation is
+Its traditional tensor network representation with $\delta$ tensors is
 
@@
 If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor is approximately $3L$, giving a space complexity $\approx 2^{3L}$.
-If we treat it as the following einsum network
+If we treat it as the following generalized tensor network
 
@@
 \section{Generalizing to other graph problems}\label{app:otherproblems}
-There are some other graph problems that can be encoded in an einsum network.
+There are some other graph problems that can be encoded in a tensor network.
 To understand its representation power, it is a good starting point to connect it with dynamic programming because
-an einsum network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
+a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
 Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded tree width $k$ can be solved in linear time with respect to the graph size.
-Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the einsum network approach.
-We mentioned in the main text that einsum network has nice analytic property make it easier for generic programming.
-The cost is, the einsum network is less expressive than dynamic programming,
+Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
+We mentioned in the main text that tensor network has nice analytic property make it easier for generic programming.
+The cost is, the tensor network is less expressive than dynamic programming,
 \iffalse
-The cost is, it is less expressive than MSO because the einsum network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
+The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
 \begin{align}
@@
 \end{align}
-while not all monadic second order logic can be represented as an einsum network contraction,
-for example, it is hard to construct a einsum network to decide whether a graph is connected or not.
+while not all monadic second order logic can be represented as a tensor network contraction,
+for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
 At the cost of losing expressiveness, we can encode the properties of the graph into the tensor elements.
 \fi
-However, that are still some other problems that can be expressed in the framework of generic einsum network.
+However, that are still some other problems that can be expressed in the framework of generic tensor network.
 \subsection{Matching problem}
@@
 \end{align}
-The number of possible colouring can be obtained by contracting this einsum network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+The number of possible colouring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
 By designing generic types as tensor elements, one should be able to get all possible colourings.

### 2021-08-15 paper/paper.tex
update

@@
 \section{Introduction}
+\blue{efficient counting maximal independent sets~\cite{Manne2013}}
 In this work, we introduce a tensor based framework to study the famous graph problem of finding independent sets.
@@
 \end{align*}
-
+The property of being commutative is required here because we want the contraction result independent of the contraction order.
 In the following, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
 i.e. making the tensor network generic~\cite{Stepanov2014}.
-
-\subsection{The polynomial approach}
 A straight forward approach to evaluate the independence polynomial is treating the tensor elements as polynomials, and evaluate the polynomial directly.
@@
 In the program, the multiplication can be evaluated efficiently with the convolution theorem~\cite{Schonhage1971}.
-The only problem of this method is it suffers from a space overhead that proportional to the maximum independent set size because each polynomial requires a vector of such size to store the factors.
-In the following subsections, we managed to solve this problem.
-
-\subsection{The fitting and Fourier transformation approaches}
-Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of real numbers of cardinality $m+1$.
-We compute the tensor network contraction for each $x_i \in X$ and obtain the following relations
-\begin{align}
-    \begin{split}
-a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
-a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
-\ldots&\\
-a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
-    \end{split}
-\end{align}
-The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
-The polynomial fitting is essentially about solving the following linear equation
-\begin{align}
-\left(\begin{matrix}
-1 & x_1 & x_1^2 & \ldots & x_1^m \\
-1 & x_2 & x_2^2 & \ldots & x_2^m \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_m & x_m^2 & \ldots & x_m^m
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right).\label{eq:lineareq}
-\end{align}
-
-In practise, the fitting can suffer from the non-negligible round off errors of floating point operations and produce unreliable results.
-This is because the factors of independence polynomial can be different in magnitude by many orders.
-Instead of choosing $X$ as a set of random real numbers, we make it form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/(m+1)}$.
-The above linear equation becomes
-\begin{align}
-\left(\begin{matrix}
-1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
-1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right).
-\end{align}
-
-Let us rearrange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a discrete Fourier transformation (DFT) matrix.
-Then we can obtain the factors using the inverse Fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) and high independent set size region ($\omega>1$).
-
-\subsection{The finite field algebra approach}
-It is possible but not trivial to compute the independence polynomial rigorously using integer number types only.
-The hardness originates from the practical consideration of computing speed and precision.
-Fixed width integer types are often too small to store the counting,
-while big integer with varying width can be very slow and incompatible with graphic processing units (GPU) devices.
+However, this approach suffers from a space overhead that proportional to the maximum independent set size because each polynomial requires a vector of such size to store the factors.
+In \App{app:fft}, we provide a fitting based approach to compute the independence polynomial.
+One just set $x$ to $\alpha(G)+1$ random values, compute the result and use the polynomial fitting to get the factors.
+In this way, we do not have linear overheads in space, however, 
+due to fact that countings of different MIS sizes can be different in many orders, 
+the round off error dominates the high MIS size region that we are most interested about if we use floating point numbers in computation, 
+meanwhile the number easily overflows if we use fixed width integer types.
+The big integer type is not an option because big integers with varying width can be very slow and incompatible with graphic processing units (GPU) devices.
+Then we want to resort to integer numbers, however, fixed width integer types are often too small to store the counting,
 This problem can be solved by introducing finite field algebra $GF(p)$
-
 \begin{align}
@@
 \end{align}
-
 In a finite field algebra, we have the following observations
@@
 \subsection{Maximal independence polynomial}
-Some times people are interested in knowing maximal solutions to understand why their program is trapped in a local minimal.
+Some times people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
 Then they might want to compute the maximal independence polynomial.
@@
 \section{Enumerating configurations}
-One may also want to obtain all solutions, it can be achieved replacing the factors $a_x$ with a set of bit strings $s_x$,
+One may also want to obtain all solutions, it can be achieved replacing the factors with a set of solutions,
 We design a new element type having the following algebra
@@
 \end{align}
-\iffalse
+where $\lor^\circ$ is the Hadamard logic or operation over two bit strings, which means joining of two local configurations.
+The variable $x$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$,
+where $\boldsymbol{e}_i$ is a one hot vector of size $|G|$.
+As an example, if we want to enumerate all maximum independent sets, we can use the above set as the factors in \Eq{eq:countingtropical}.
+We get the following new algebra.
 \begin{align}
@@
 \end{align}
-\fi
-where $\lor^\circ$ is the Hadamard logic or operation over two bit strings, which means joining of two local configurations.
-The variable $x$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$,
-where $\boldsymbol{e}_i$ is a one hot vector of size $|G|$.
-One can easily check this algebra is a commutative semiring.
-When we use the above algebra as factors of independence polynomials, the resulting algebra is also a commutative semiring.
-With this new element type, the tensor network contraction will give all solutions rather than just a number for counting.
-By slightly modifying the above algebra, it can also be used to obtain just a single configuration to save the computational effort.
+One can easily check if the factor algebra is a commutative semiring,
+when we use the above algebra as factors of independence polynomials, the resulting algebra is also a commutative semiring.
+If one is only interested in obtaining a single configuration, one can also just keep a single configuration to save the computational effort.
+We arrive at a new algebra defined on bit strings.
 %We leave this as an exercise for readers.
@@
 Notice that these masks are in fact tensor elements with non-zero gradients with respect to MIS size, we compute these masks by back propagating gradients.
-To derive the backward rule, we consider a tropical matrix multiplication $C = A B$, we have the following inequality
+To derive the backward rule for tensor contraction,
+we first reduce the problem to finding the backward rule of a tropical matrix multiplication $C = A B$,
+where we have the following inequality
 \begin{align}
@@
 \end{align}
-Moving $B_{ik}$ to the right hand side, we have
-\begin{align}
-    A_{ij} &\leq (\oplus_{k} (C_{ik}^{-1} \odot B_{jk}))^{-1}
+Here is $\leq$ on tropical numbers are same as regular algebra.
+The tropical multiplication $\odot$ is the same as the regular $+$, then
+one can move $B_{ik}$ to the right hand side and get
+\begin{align}
+    A_{ij} &\leq C_{ik} \odot B_{jk}^{\circ -1}
 \end{align}
 where the tropical multiplicative inverse is defined as the additive inverse of the regular algebra.
-The equality holds if and only if element $A_{ij}$ contributions to $C$ (i.e.
-has non-zero gradient).
-Let the mask for $C$ being $\overline C$, the backward rule for ``gradient'' masks reads
+The inequality still holds if we take the minimum over $k$
+\begin{align}
+    \begin{split}
+    A_{ij} &\leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = (\oplus_{k} (C_{ik}^{-1} \odot B_{jk}))^{\circ -1}.
+    \end{split}
+\end{align}
+On the right hand side, we transformed the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines.
+The equality holds if and only if element $A_{ij}$ has contribution to $C$ (i.e. has non-zero gradient).
+Let the gradient mask for $C$ being $\overline C$, the backward rule for gradient masks reads
 \begin{align}
@@
 
+\section{The fitting and Fourier transformation approaches to computing independence polynomial}\label{app:fft}
+Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of real numbers of cardinality $m+1$.
+We compute the tensor network contraction for each $x_i \in X$ and obtain the following relations
+\begin{align}
+    \begin{split}
+a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
+a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
+\ldots&\\
+a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
+    \end{split}
+\end{align}
+The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
+The polynomial fitting is essentially about solving the following linear equation
+\begin{align}
+\left(\begin{matrix}
+1 & x_1 & x_1^2 & \ldots & x_1^m \\
+1 & x_2 & x_2^2 & \ldots & x_2^m \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_m & x_m^2 & \ldots & x_m^m
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right).\label{eq:lineareq}
+\end{align}
+
+In practise, the fitting can suffer from the non-negligible round off errors of floating point operations and produce unreliable results.
+This is because the factors of independence polynomial can be different in magnitude by many orders.
+Instead of choosing $X$ as a set of random real numbers, we make it form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/(m+1)}$.
+The above linear equation becomes
+\begin{align}
+\left(\begin{matrix}
+1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
+1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_m
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_m
+\end{matrix}\right).
+\end{align}
+
+Let us rearrange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a discrete Fourier transformation (DFT) matrix.
+Then we can obtain the factors using the inverse Fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
+By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) and high independent set size region ($\omega>1$).
+
 \end{document}

### 2021-08-25 paper/paper.tex
save

@@
 \section{Introduction}
-\blue{efficient counting maximal independent sets~\cite{Manne2013}}
+\blue{efficient counting maximal independent sets~\cite{Manne2013}, overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}}
 In this work, we introduce a tensor based framework to study the famous graph problem of finding independent sets.
@@
 
+\section*{Acknowledgments}
+We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
+their questions are the driving force of this project.
+Thank Chris Elord for helping us writting the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
+\blue{funding information}
+
 \bibliographystyle{siamplain}

### 2021-09-04 paper/paper.tex
update

@@
     We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
-    We also show how to analyse the local properties of a graph by contracting an open tensor network.
 \end{abstract}
@@
 \section{Introduction}
-\blue{efficient counting maximal independent sets~\cite{Manne2013}, overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}}
+\blue{some literature does not distinguish maximal and maximum, efficient counting maximal independent sets~\cite{Manne2013}, overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}, treewidth of 3-regular graphs ~\cite{Fomin2006}}
 In this work, we introduce a tensor based framework to study the famous graph problem of finding independent sets.
@@
 The exhaustive search for a solution costs time $2^{|V|}$.
-More efficient algorithms to compute the MIS size exactly includes the branching algorithm and dynamic programming.
+More efficient algorithms to compute the MIS size exactly includes the branching algorithm~\cite{Tarjan1977,Robson1986} and dynamic programming.
 Without changing the fact of exponential scaling in computing time, the branching algorithm gives a smaller base.
-For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm has a time complexity $1.1893^n n ^{O(1)}$.
-The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for graphs with small tree width $tw(G)$, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
+For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm has a time complexity $1.1996^n n ^{O(1)}$.
+The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for sparse graphs with small tree width $tw(G)$~\cite{Fomin2006}, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
 People are interested in solving the independent set problem better not only because it is an NP-complete problem that directly related to other NP-complete problems like maximal cliques and vertex cover~\cite{Moore2011},
@@
 These questions includes but not limited to, counting all independent sets, obtaining all independent sets of size $\alpha(G)$ and $\alpha(G)-1$,
-counting the number of (maximal) independent sets of different sizes, and understanding the effect of a local gadget.
+counting independent sets of different sizes, and understanding the effect of a local gadget.
 In this work, we attack this problem by mapping it to an generic tensor network.
@@
 \section{Independence polynomial}
-One can encode the independence polynomial~\cite{Ferrin2014, Harvey2017} of $G$ to a tensor network.
+One can encode the independence polynomial~\cite{Levit2005, Ferrin2014, Harvey2017} of $G$ to a tensor network.
 Independence polynomial is an important graph polynomial that contains the counting information of an independent set problem. It is defined as
@@
 \subsection{Maximal independence polynomial}
-Some times people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
-Then they might want to compute the maximal independence polynomial.
+Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
+In this paper, the word ``maximal'' is different with the ``maximum'' discussed the previous discussion in such a way that it is not necessarily refer to the gloal optimum.
 Let us denote the neighbour of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
@@
 This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by a tensor contraction.~\cite{} \blue{maybe add an appendix?}  % my blog
-
-\section{Tropical tensors for automated branching}\blue{$?$}
-% check http://www.tcs.rwth-aachen.de/independentset/ for more rules
-Branching rules can be automatically discovered by contracting the tensor network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
-Let $C$ be the set of boundary vertices defined as $C := \{u | u\in R \land (\exists v \in (G\backslash R) \land {\rm adj}(u, v))\}$, then the rank of the resulting tensor $A$ is $|C|$.
-Here, we use ${\rm adj}(u, v)$ to denote two vertices $u$ and $v$ are adjacent to each other.
-Each tensor entry $A_{\sigma}$ is a local maximum independent set size for the fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$.
-Suppose our goal is to find the maximum independent set size,
-then this tensor can be further ``compactified'' by removing some entries.
-To determine which entry can be removed, let us define a relation of \textit{less restrictive} as
-\begin{align}
-(\sigma_a \prec \sigma_b) := (\sigma_a \neq \sigma_b) \land (\sigma_a \leq^\circ \sigma_b)
-\end{align}
-where $\leq^\circ$ is the Hadamard less or equal to operation.
-
-\begin{definition}
-A tensors $A$ is \textit{MIS-compact} if
-\begin{align}
-\forall{\sigma_b}\neg \exists{\sigma_a}(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
-\end{align}
-\end{definition}
-
-If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranteed to give the same maximum independent set size.
-It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compactifying} (a) and (b).
-If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independent sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
-Hence, we can remove entry $A_{\sigma_b}$ safely.
-%among boundary configurations with equal local maximum independent sizes,
-%we only retain those least restrictive (less ones at the boundary) to exterial configurations.
-
-\begin{figure}
-    \centering
-    \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
-    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compactifying}
-\end{figure}
-
-\begin{theorem}
-    A MIS-compact tropical tensor can not be further reduce without gloal information, i.e. any of its non-zero entries can produce the only global optimal solution given a proper environment.
-\end{theorem}
-
-\begin{proof}
-    %Given $A_\{\sigma_a}$ is better than $A_\{\sigma_b\}$, any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
-    Let us prove it by showing for any $\sigma$ in a MIS-compact tropical tensor of a subgraph $R$, there exists a parent graph $G$ that $R\subseteq G$ and $\sigma$ is the boundary configuration that gives the only maximum independent set.
-    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the boundary configuration.
-    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, we connect it with two vertices $u, w \in G \backslash R$ that ${\rm adj}(v, u) \land {\rm adj}(u, w) \land \neg{\rm adj}(v, w)$.
-Otherwise, we attach infinite many disconnected neighbors to $v$.
-
-    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 5cm 0cm}, clip]{proofoptimal.pdf}}
-    Then we have the maximum independent set size $\alpha(G,\sigma) = A_{\sigma} + \infty (|C|-\sum_{v=1}^{|C|}\sigma_v) + \sum_{v=1}^{|C|} 1-\sigma_v$.
-    Let us assume there exists another configuration $\tau$ that generating the same or better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
-    Then we have $\tau \prec \sigma$, otherwise it will loss infinite contribution from the environment.
-    For such a $\tau$, we have $A_\tau < A_\sigma$, otherwise $A_\sigma \prec A_\tau$ contradicts with $A$ being MIS-compact.
-    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} + \sum_{v=1}^{|C|} 1-\sigma_v < \alpha(G,\sigma)$, hence $\sigma$ is the only boundary configuration that gives the maximum independent set for this graph.
-\end{proof}
-
-\subsection{The tensor network compactification detects branching rules automatically}
-Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
-by including its neighbourhoods,
-and keep only the configurations that has the potential to produce the only maximum independent set.
-Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for the $k$-th neighbourhood $N^k[v]$, one can discover the optimal branching vector automatically.
-In the following, we are going to introduce several important rules for branching in the literature and show how it is connected to our tensor formulation.
-
-\begin{corollary}\label{rule:one} % basic
-  If a vertex $v$ is in an independent set $I$, then none of its Neighbors can be in $I$.
-On the other hand, if $I$ is a maximum (and thus maximal) independent set,
-and thus if $v$ is not in $I$ then at least one of its Neighbors is in $I$.
-\end{corollary}
-
-Contract $N[v]$ and the resulting tensor $A$ has a rank $|N(v)|$.
-Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independent set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
-If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independent set size.
-
-\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/basic.pdf}}
-
-After contracting $N[v]$, $v$ becomes an internal degree of freedom.
-Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
-
-\begin{align}
-    T_{juwk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        ~~~~1 & -\infty \\
-        -\infty & ~~~~2
-        \end{matrix}\right)_{ju}&
-        \left(\begin{matrix}
-        -\infty & ~~~~2 \\
-        ~~~~2 & ~~~~3
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        -\infty & ~~~~2 \\
-        ~~~~2 & ~~~~3
-        \end{matrix}\right)_{ju} &
-        \left(\begin{matrix}
-        ~~~~2 & ~~~~3 \\
-        ~~~~3 & ~~~~4
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk},
-\end{align}
-where we use ``-'' to denote an entry is forbidden.
-If we use sets for counting, one can check all configurations too. The resulting polynomial tensor is
-\begin{align}
-    P_{juwk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        1+x_v & - \\
-        - & ~~x_jx_u
-        \end{matrix}\right)_{ju}&
-        \left(\begin{matrix}
-        - & x_ux_k \\
-        ~~~~x_jx_k & ~~~~x_ux_jx_k
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        - & x_wx_u \\
-        x_wx_j & x_wx_jx_u
-        \end{matrix}\right)_{ju} &
-        \left(\begin{matrix}
-        x_wx_k & x_wx_kx_u \\
-        x_wx_kx_j & x_jx_ux_wx_k
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk}.
-\end{align}
-
-By studying the correlation between vertex variables, one can easily see $x_v$ does not co-exist with other vertex variables.
-These anti-correlation determines possible branching vectors in the maximum independent set problem.
-It is easier to see if we list the set of optimal solutions as
-\begin{align}
-    \begin{split}
-    S_{juwkv} = \{&00001, 10001, 01010, 10010, 11010, 10100,\\&01100, 11100, 00110, 01110, 10110, 11110\}.
-    \end{split}
-\end{align}
-%If we denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
-%The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
-%It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
-The branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
-
-\begin{corollary}[mirror rule] % 2.7
-For some $v \in V$, a node $u \in N^2(v)$ is called mirror of $v$, if $N(v) \backslash N(u)$ is a clique. We denote the set of of a node $v$ mirrors~\cite{Fomin2013} by $M(v)$.
-Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
-\begin{equation}
-\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
-\end{equation}
-\end{corollary}
-
-This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
-otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
-Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighbourhood of $v$.
-If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
-since clique has at most one node in the MIS, by moving the occupied node to the interior, we obtain a ``better'' solution.
-%Hence, the \textit{least restrictive principle} captures the mirror rule.
-In the following example, since $u\in N^2(v)$ and $N(v) \backslash N(u)$ is a clique, $u$ is a mirror of $v$.
-
-\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/mirror.pdf}}
-
-After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
-Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
-
-\begin{align}
-    T_{juwk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        ~~~~1 & ~~~~2 \\
-        ~~~~\cancel{1} & ~~~~\cancel{2}
-        \end{matrix}\right)_{ju}&
-        \left(\begin{matrix}
-        ~~~~\cancel{1} & -\infty \\
-        ~~~~2 & -\infty
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        ~~~~\cancel{1} & ~~~~\cancel{2} \\
-        -\infty & -\infty
-        \end{matrix}\right)_{ju} &
-        \left(\begin{matrix}
-        -\infty & -\infty \\
-        -\infty & -\infty
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk},
-\end{align}
-where entries stroked through are removed by compactification. The corresponding polynomial tensor is
-
-\begin{align}
-    P_{juwk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        1+x_v & x_u+x_ux_v \\
-        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{}\\
-        \end{matrix}\right)_{ju}&
-        \left(\begin{matrix}
-        ~~~~\cancel{} & - \\
-        x_jx_k & -
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{} \\
-        ~~~~~~~- & ~~~~~~~~~~~~~-
-        \end{matrix}\right)_{ju} &
-        \left(\begin{matrix}
-        ~~~~- & - \\
-        ~~~~- & -
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{wk}.
-\end{align}
-One can see $w$, as a mirror of $v$ does not appear in the maximum independent set after compactification.
-
-%In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
-%which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
-\begin{align}
-    \begin{split}
-    S_{juwkv} = \{&00001, 01001, 10010\}.
-    \end{split}
-\end{align}
-
-\begin{corollary}[satellite rule] % satellite rule
-Let $G$ be a graph, $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
-The set of satellites of a node $v$ is denoted by $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
-\begin{equation}
-\alpha(G) = \max\{\alpha(G \backslash \{v\}), \alpha(G \backslash N[S[v]]) + |S(v)| + 1\}.
-\end{equation}
-\end{corollary}
-
-This rule can be capture by contracting $N[v] \cup S(v)$.
-In the following example, since $u \in N^2(v)$ and $w \in N(v)$ satisfies $N[w] \backslash N[v] = \{u\}$, $u$ is a satellite of $v$.
-
-\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/satellite.pdf}}
-
-After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
-Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 3 polynomial tensor is
-\iffalse
-\begin{align}
-    T_{juk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        ~~~~1 & ~~~~2 \\
-        ~~~~2 & ~~~~\cancel{2}
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        ~~~~\cancel{1} & -\infty \\
-        ~~~~\cancel{2} & -\infty
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{k}.
-\end{align}
-\fi
-
-\begin{align}
-    P_{juk} = \left(\begin{matrix}
-        \left(\begin{matrix}
-        1+x_w+x_v & x_u + x_ux_v \\
-        x_j+x_wx_j & ~~~~~~~~~~~~\cancel{}
-        \end{matrix}\right)_{ju}\\
-        \left(\begin{matrix}
-        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~- \\
-        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~-
-        \end{matrix}\right)_{ju}
-    \end{matrix}\right)_{k}.
-\end{align}
-
-By choosing one of the optimal configurations in each entry,
-we can see the satellite rule of either ${v, u} \in I$ or $v \notin I$ is satisfied.
-
-\begin{align}
-    \begin{split}
-    S_{juwkv} = \{&\{00100,00001\}, 10100, 01001\}.
-    \end{split}
-\end{align}
-%In this case, the effective branching number is $3^{1/5}\approx 1.2457$.
-
-%We can use the conditional entropy to discover branching rules automatically. 
-%Let us take one best configuration a time from each entry of the compact polynomial matrix,
-%and denote the resulting configuration set as $S$.
-%The conditional entropy matrix here can be defined as
-%\begin{align}
-%    C_{uv} = H(s_u|s_v)
-%\end{align}
-%when two variables are strongly correlated to each other, the corresponding entry should be zero.
-
-\subsection{gadget design}\blue{$\times$}
-
-Suppose we have a local structure as the following.
-
-\centerline{\begin{tikzpicture}[scale=1.0]
-    \def\r{0.2}
-    \foreach \x/\y [count=\i] in {0.17/0.5,0.83/0.5,0.5/0.67,0.5/0.33}
-        \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-    \draw (1) -- (2);
-    \draw (3) -- (4);
-\end{tikzpicture}}
-
-Contract this local structure gives the tropical tensor
-
-\begin{align}
-    \left(\begin{matrix}
-        \left(\begin{matrix}
-            ~~~~0 & ~~~~1\\
-            ~~~~1 & ~~~~2
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~1 & -\infty\\
-            ~~~~2 & -\infty
-        \end{matrix}\right) \\
-        \left(\begin{matrix}
-            ~~~~1 & ~~~~2\\
-            -\infty & -\infty
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~2 & -\infty\\
-            -\infty & -\infty
-        \end{matrix}\right)
-    \end{matrix}\right).
-\end{align}
-
-The following gadget is equivalent to the above diagram up to a constant $2$.
-
-\centerline{\begin{tikzpicture}
-    \def\nodes{(0.5, 0.33), (0.17, 0.5), (0.5, 0.67), (0.83, 0.5), (0.32, 0.44), (0.44, 0.44), (0.56, 0.44), (0.68, 0.44), (0.32, 0.56), (0.44, 0.56), (0.56, 0.56), (0.68, 0.56)}
-    \def\edges{(1, 5), (1, 6), (1, 7), (1, 8), (2, 5), (2, 9), (3, 9), (3, 10), (3, 11), (3, 12), (4, 8), (4, 12), (5, 6), (5, 9), (5, 10), (6, 7), (6, 9), (6, 10), (6, 11), (7, 8), (7, 10), (7, 11), (7, 12), (8, 11), (8, 12), (9, 10), (10, 11), (11, 12)}
-    \def\r{0.2}
-    \foreach \p [count=\i] in \nodes{
-        \parsept{\x}{\y}{\p}
-        \pgfmathparse{((\x<0.2 || \x>0.8 || \y<0.35 || \y>0.65) ? 1 : 0)}
-        \ifnum\pgfmathresult>0
-            \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-        \else
-            \node[fill,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-        \fi
-    }
-    \foreach \e [count=\i] in \edges{
-        \parsept{\x}{\y}{\e}
-        \draw (\x) -- (\y);
-    }
-\end{tikzpicture}}
-
-\begin{align}
-    \left(\begin{matrix}
-        \left(\begin{matrix}
-            ~~~~2 & ~~~~3\\
-            ~~~~3 & ~~~~4
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~3 & ~~~~3\\
-            ~~~~4 & ~~~~4
-        \end{matrix}\right) \\
-        \left(\begin{matrix}
-            ~~~~3 & ~~~~4\\
-            ~~~~2 & ~~~~3
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~4 & ~~~~4\\
-            ~~~~3 & ~~~~4
-        \end{matrix}\right)
-    \end{matrix}\right)
-    \xrightarrow[\text{compactify, -2}]{}
-    \left(\begin{matrix}
-        \left(\begin{matrix}
-            ~~~~0 & ~~~~1\\
-            ~~~~1 & ~~~~2
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~1 & ~~~~\cancel{1}\\
-            ~~~~2 & ~~~~\cancel{2}
-        \end{matrix}\right) \\
-        \left(\begin{matrix}
-            ~~~~1 & ~~~~2\\
-            ~~~~\cancel{0} & \cancel{1}
-        \end{matrix}\right) &
-        \left(\begin{matrix}
-            ~~~~2 & ~~~~\cancel{2}\\
-            ~~~~\cancel{1} & ~~~~\cancel{2}
-        \end{matrix}\right)
-    \end{matrix}\right)
-\end{align}
-
-We can see these two subgraphs produce exactly the same compact tensor.
-When we replace the original tensor with this gadget, the solution.
 

### 2021-09-04 project/configurations2.jl

@@ -50,7 +50,8 @@ for (n, seeds) in [
        #849, 854, 57, 64, 953, 43, 210])
     #(8, [100, 72, 316, 747, 216, 168, 852, 7, 743, 32, 573, 991, 957, 555, 936, 342, 950]),
     #(9, [805, 144, 560, 651, 234, 442, 408, 866, 263, 873, 91, 99, 566, 849, 854, 57, 64, 953, 43, 210])
-    (7, [189,623,354,40,323,173,661,345,813,35,162,965,336,667,870,1,156,901,576,346])
+    #(7, [189,623,354,40,323,173,661,345,813,35,162,965,336,667,870,1,156,901,576,346])
+    (7, [40, 323, 173, 661, 345, 813, 35, 162, 965, 336, 667, 870, 1, 156, 901, 576, 346])
     ]
     for seed in seeds
         @time mis_configurations(n, seed; writefile=true, sc_target=14)

### 2021-09-04 project/grover.jl

@@ -1,0 +1,14 @@
+using Yao, LightGraphs
+using Yao.ConstGate: P1
+
+# U*nᵢnⱼ + Ω*X + Δ*Z
+function rydberg_hamiltonian(g::SimpleGraph, U, Ω, Δ)
+    n = nv(g)
+    res = AbstractBlock{n}[]
+    U != 0 && push!(res, U * +([put(n, (e.src, e.dst)=>kron(P1, P1)) for e in edges(g)]...))
+    Ω != 0 && push!(res, Ω * +([put(n, v=>X) for v in vertices(g)]...))
+    Δ != 0 && push!(res, Δ * +([put(n, v=>(-P1)) for v in vertices(g)]...))
+    return Add(res)
+end
+
+rydberg_hamiltonian(random_regular_graph(10, 3), 100.0, 0.0, 1.0)

### 2021-09-04 project/trapped.jl

@@ -1,0 +1,92 @@
+using NoteOnTropicalMIS, LightGraphs
+using StatsBase, TropicalNumbers
+
+function random_graph(n::Int, m::Int)
+    g = SimpleGraph(n)
+    for i=1:m
+        (a,b) = sample(1:n, 2; replace=true)
+        add_edge!(g, a, b)
+    end
+    return g
+end
+
+function Base.count_ones(x::StaticBitVector)
+    sum(v->count_ones(v),x.data)
+end
+
+function phase_space_reachable(g)
+    code = NoteOnTropicalMIS.idp_code(g; method=:greedy)
+    s, c = (res = mis_contract(CountingTropical{Int,Int}(1,1), code)[]; (res.n, res.c))
+    println("Graph size = $(nv(g)), MIS size = $s, degeneracy = $c")
+    s2, config1, config0 = (res = mis_max2_config(code)[]; (res.maxorder, res.a, res.b))
+    @assert s == s2
+    @assert length(config0) == c
+    configs = config0.data ∪ config1.data
+    @show config0, config1
+    G = SimpleGraph(length(configs))
+    for (ic,c) in enumerate(configs)
+        for (id,d) in enumerate(configs)
+            diffpos = c ⊻ d
+            ndiff = count_ones(diffpos)
+            if ndiff == 1
+                add_edge!(G, ic, id)
+            elseif ndiff == 2
+                a = 0
+                b = 0
+                for (ip,p) in enumerate(diffpos)
+                    if p == 1
+                        if a == 0
+                            a = ip
+                        else
+                            b = ip
+                        end
+                    end
+                end
+                if has_edge(g, a, b)
+                    add_edge!(G, ic, id)
+                end
+            end
+        end
+    end
+    @show connected_components(G)
+    all(sg->any(v->v<=length(config0.data), sg), connected_components(G))
+end
+
+#=
+for s in [
+        (:diamond        , 4, 5, false),
+        (:bull           , 5, 5, false),
+        (:chvatal        , 12, 24, false),
+        (:cubical        , 8, 12, false),
+        (:desargues      , 20, 30, false),
+        (:dodecahedral   , 20, 30, false),
+        (:frucht         , 12, 18, false),
+        (:heawood        , 14, 21, false),
+        (:house          , 5,6, false),
+        (:housex         , 5, 8, false),
+        (:icosahedral    , 12, 30, false),
[…]

### 2021-09-04 project/xungao.jl

@@ -1,0 +1,162 @@
+using OMEinsumContractionOrders, OMEinsum
+using Random; Random.seed!(2)
+
+dims = Tuple{Int,Int,Bool}[(1, 4, false), (2, 4, false), (3, 4, false), (4, 4, false), (5, 4, false), (6, 4, false), (7, 4, false),
+    (8, 4, false), (9, 4, false), (10, 4, false), (11, 4, false), (12, 4, false), (13, 4, false), (14, 4, false),
+    (15, 4, false), (16, 4, false), (17, 4, false), (18, 4, false), (19, 4, false), (20, 4, false), (21, 4, false),
+    (22, 4, false), (23, 4, false), (24, 4, false), (25, 4, false), (26, 4, false), (27, 4, false), (28, 4, false),
+    (29, 4, false), (30, 4, false), (31, 4, false), (32, 4, false), (33, 4, false), (34, 4, false), (35, 4, false),
+    (36, 4, false), (37, 4, false), (38, 4, false), (39, 4, false), (40, 4, false), (41, 4, false), (42, 4, false), 
+    (43, 4, false), (44, 4, false), (45, 4, false), (46, 4, false), (47, 4, false), (48, 4, false), (49, 4, false), 
+    (50, 4, false), (51, 4, false), (52, 4, false), (53, 4, false), (54, 4, false), (55, 4, false), (56, 4, false), 
+    (57, 4, false), (58, 4, false), (59, 4, false), (60, 4, false), (61, 4, false), (62, 4, false), (63, 4, false),
+    (64, 4, false), (65, 4, false), (66, 4, false), (67, 4, false), (68, 4, false), (69, 4, false), (70, 4, false),
+    (71, 4, false), (72, 4, false), (73, 4, false), (74, 4, false), (75, 4, false), (76, 4, false), (77, 4, false),
+    (78, 4, false), (79, 4, false), (80, 4, false), (81, 4, false), (82, 4, false), (83, 4, false), (84, 4, false),
+    (85, 4, false), (86, 4, false), (87, 4, false), (88, 4, false), (89, 4, false), (90, 4, false), (91, 4, false),
+    (92, 4, false), (93, 4, false), (94, 4, false), (95, 4, false), (96, 4, false), (97, 4, false), (98, 4, false),
+    (99, 4, false), (100, 4, false), (101, 4, false), (102, 4, false), (103, 4, false), (104, 4, false), (105, 4, false),
[…]

### 2021-09-07 paper/paper.tex
first major revision

@@
-\documentclass[review,onefignum,onetabnum]{siamart190516}
+\documentclass[onefignum, onetabnum]{siamart190516}
 %\usepackage{natbib}
@@
 \usepackage{txfonts}
-\usepackage[epsilon, tsrm, altpo]{backnaur}
+%\usepackage[epsilon, tsrm, altpo]{backnaur}
 
@@
 
-\title{Solving the independent set problem by generic programming tensor networks
+\title{Computing properties of independent sets by generic programming tensor networks
 \thanks{\funding{...}}
@@
 \begin{abstract}
-	This paper is about solving the independent set problem by eincoding this problem to a tensor network. 
-    We show how to obtain the maximum independent set size, the independence polynomial and optimal configurations of a graph by engineering the tensor element algebra.
+We introduce a new approach to compute various properties of independent sets by encoding the problems into tensor networks with different tensor element algebra.
+The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of the maximum independence set configurations.
+Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods; on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
 \end{abstract}
@@
 \begin{keywords}
-  maximum independent set, tensor network
+independent set, tensor network, maximum independent set, independence polynomial
 \end{keywords}
@@
 \section{Introduction}
-\blue{some literature does not distinguish maximal and maximum, efficient counting maximal independent sets~\cite{Manne2013}, overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}, treewidth of 3-regular graphs ~\cite{Fomin2006}}
-In this work, we introduce a tensor based framework to study the famous graph problem of finding independent sets.
-Given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
-The problem of finding the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$ belongs to the complexity class NP-complete~\cite{Hastad1996}, which is unlikely to be decided in polynomial time.
-It is hard to even approximate this size in polynomial time within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-The exhaustive search for a solution costs time $2^{|V|}$.
-More efficient algorithms to compute the MIS size exactly includes the branching algorithm~\cite{Tarjan1977,Robson1986} and dynamic programming.
-Without changing the fact of exponential scaling in computing time, the branching algorithm gives a smaller base.
-For example, in ~\cite{Xiao2017}, a sophisticated branching algorithm has a time complexity $1.1996^n n ^{O(1)}$.
-The dynamic programming approach~\cite{Courcelle1990,Fomin2013} works better for sparse graphs with small tree width $tw(G)$~\cite{Fomin2006}, it gives an algorithms of complexity $O(2^{tw(G)}tw(G)n)$.
-People are interested in solving the independent set problem better not only because it is an NP-complete problem that directly related to other NP-complete problems like maximal cliques and vertex cover~\cite{Moore2011},
-but also for its close relation with physical applications like hard spheres lattice gas model~\cite{Dyre2016}, and Rydberg hamiltonian~\cite{Pichler2018}.
-However, in these applications, knowing the MIS size and one of the optimum solutions is not the only goal.
-%A set is independent if and only if it is a clique in the graph's complement, so the two concepts are complementary.
-%A set is independent if and only if its complement is a vertex cover.
-Therefore, the sum of the size of the largest independent set $\alpha (G)$ and the size of a minimum vertex cover $\beta (G)$ is equal to the number of vertices in the graph.
-People often ask different questions about independent sets in order to understand the landscape of their models better.
-These questions includes but not limited to, counting all independent sets, obtaining all independent sets of size $\alpha(G)$ and $\alpha(G)-1$,
-counting independent sets of different sizes, and understanding the effect of a local gadget.
-In this work, we attack this problem by mapping it to an generic tensor network.
-It does not give a better time complexity comparing to dynamic programming, but is versatile enough to answer the above questions by engineering the tensor elements with minimum effort.
-
-\section{Tensor networks}
-%The word ``einsum'' is a shorthand for Einstein's summation, however, modern einsum notation in program is actually invented by a group of programmers.
-A tensor network can be viewed as a generalization to of binary matrix multiplication to n-ary tensor contraction.
-Let $A, B$ be two matrices, the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
-A traditional tensor network refers to the Einstein's notation.
-In this notation, the matrix multiplication is denoted as $C_i^k = A_i^j B_j^k$, where the paired subscript and superscript $j$ is a dummy index summed over, hence each index appears precisely twice.
-When we have multiple tensors doing the above sum-product operation, we get a traditional tensor network~\cite{Orus2014}.
-A traditional tensor network can be represented as a mutigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
+\blue{efficient counting maximal independent sets~\cite{Manne2013}}
+In graph theory and combinatorics, there are many interesting but hard computational problems concerning properties of independent sets.
+An independent set is a set of vertices in a graph where no two vertices are adjacent to each other.
+More formally, given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
+The problem of finding an independent set of the largest possible size, the maximum independent set (MIS), is a paradigmatic NP-complete problem~\cite{Hastad1996}.
+The size of the MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$.
+
+Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
+Naive exhaustive search for the MIS requires time $O(2^{|V|})$.
+More efficient exact algorithms include the branching algorithms and dynamic programming.
+Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1893^n n ^{O(1)}$~\cite{Xiao2017} \red{reading the abstract, I think the algorithm is $1.1996^{|V|} {|V|}^{O(1)}$.
+The $1.1893^{|V|} {|V|}^{O(1)}$ scaling is for graphs with maximum degree 6}.
+Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$; these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
+
+The independent set problem is closely related to the clique problem and the vertex cover problem~\cite{Moore2011}; more concretely, an MIS of a graph $G$ corresponds to a maximum clique in the complement graph of $G$, and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
+Together, these problems find a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication, map labelling, computer vision, etc.~\cite{Butenko2003Maximum, Wu2015review}.
+Besides the standard MIS problem, there are many other interesting problems pertaining to independent sets, such as the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of optimal and sub-optimal configurations.
+Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007Monte} in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready}; they can, for example, be used to understand phase transitions and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
+
+In this work, we introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
+We map different problems into generic tensor network contraction with various tensor element algebra.
+Our approach does not necessarily provide a better time complexity compared to dynamic programming, but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts.
+We benchmark our algorithms, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
+Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
+
+\section{Tensor networks}\red{I removed the superscript and subscript, since I think it's not necessary to introduce those.}
+A tensor network~\cite{Cirac2020Matrix, Orus2014} can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
+Let $A, B$ be two matrices; the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
+Using the Einstein notation, we can write $C_{ik} = A_{ij}B_{jk}$, where $j$ is implicitly summed over.
+In the standard notation, each index can appear at most twice.
+A tensor network consists of multiple tensors performing the sum-product operation, i.e., contraction, and the tensor network can be represented as a multigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
 
 \begin{example}
-   A traditional tensor network $C_i^l = A_{ij}^{km} B^l_{km} V^j$ has the following multigraph representation.
+   A tensor network $C_{il} = A_{ijkm} B_{kml} V_{j}$ has the following multigraph representation.
 
@@
 \end{tikzpicture}}
-
 \end{example}
 
-Here, we want to use a generalized tensor network notation by not restricting the number of times a label appears in the notation,
-hence whether an index is a superscript or a subscript makes no sense now.
-It is also called einsum, sum-product network or factor graph~\cite{Bishop2006} in some contexts.
-The graphical representation of a tensor network in this paper is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
+One can generalize the tensor network notation by removing the restriction that each index can appear at most twice.
+The notation can be considered as a generalized Einstein notation, which is sometimes called einsum, sum-product network or factor graph~\cite{Bishop2006} in different contexts.
+The graphical representation of a tensor network we use in this paper is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
 
 \begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network, it represents $C_{ijk} = \sum_{ml}A_{jkm} B_{mia} V_{jm}$.
-Its hypergraph representation is as the following, where we use different color to annotate different hyperedges.
+$C_{ijkl} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijkl} = \sum_{m}A_{jkm} B_{mil} V_{jm}$  \red{I've changed this.
+please check.
+The original was $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ and $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$}.
+Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
 
@@
 
-In the main text, we stick to the our generalized tensor network notation rather than the traditional notation.
-As a note to those who are more familiar with the traditional tensor network representation,
-although one can easily translate a generalized tensor network to the equivalent traditional tensor network by adding $\delta$ tensors (a generalization of identity matrix to higher order).
-It can sometime increase the contraction complexity of a graph. We have an example demonstrating this point in \App{app:tensorbad}.
-
-\section{Independence polynomial}
-One can encode the independence polynomial~\cite{Levit2005, Ferrin2014, Harvey2017} of $G$ to a tensor network.
-Independence polynomial is an important graph polynomial that contains the counting information of an independent set problem. It is defined as
-\begin{equation}
-I(G, x) = \sum_{k=1}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the maximum independent set size.
-The problem of computing independence polynomial belongs to the complexity class \#P-hard.
-A traditional approach to compute independence polynomial rigorusly requires a computing time $O(1.442^n)$~\cite{Ferrin2014}\blue{I am not sure about this complexity, this is baed on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
-%with which computing the independence polynomial for a square lattice of size $30\times 30$ would be impossible.
-There are some interests in approximating this polynomial efficiently~\cite{Harvey2018}, but here, we focus on the rigorous approaches.
-We encode this polynomial to a tensor network by placing a rank one tensor of size $2$ parametrized by $x_i$ on a vertex $i$
+In the main text, we use the generalized tensor network notation.
+The generalized tensor network can be easily translated to the standard notation by adding identity tensors denoted as $\delta$ tensors.
+The example above can be written as $C_{ijkl} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}$ in the standard notion.
+However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
+
+\section{Generic programming}\label{sec:generic}
+\red{I suggest we have a section on generic programming, putting both the semiring stuff and the summary table to this section, since generic programming is one of the highlights of this paper as well.
+I think it doesn't need to be long.
+Jinguo, could you write one or two paragraphs introducing generic programming?}
+
+\red{Generic programming is ...}
+\red{dispatch to different types etc. ...}
+
+In the spirit of generic programming, the elements of the tensors in the tensor network do not always need to be floating point numbers or integers.
+In fact, for the tensor network contraction to make sense, one only needs the tensor elements to form a commutative semiring.
+A semiring is a ring without additive inverse, while a commutative semiring is a semiring where the multiplication operation is commutative.
+To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
+\begin{align*}
+(a \oplus b) \oplus c = a \oplus (b \oplus c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\oplus$ with identity $\mymathbb{0}$}\\
+a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
+a \oplus b = b \oplus a &\\
+&\\
+(a \odot b) \odot c = a \odot (b \odot c)  &   \hspace{5em}\text{$\triangleright$ commutative monoid $\odot$ with identity $\mymathbb{1}$}\\
+a \odot  \mymathbb{1} =  \mymathbb{1} \odot a = a &\\
+a \odot b = b \odot a &\\
+&\\
+a \odot (b\oplus c) = a\odot b \oplus a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
+(a\oplus b) \odot c = a\odot c \oplus b\odot c &\\
+&\\
+a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
+\end{align*}
+The requirement of being commutative is for the tensor contraction result to be independent of the contraction order, which could be relaxed in certain cases.
+In the following sections, we show how to compute the independence polynomial, the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.
+
+\begin{table}[t!]\centering
+\begin{minipage}{0.9\columnwidth}
+\ra{1.3}
+    \scalebox{1.0}{
+        \begin{tabularx}{\textwidth}{bb}\toprule
+            \hline
+            \textbf{element type}     & \textbf{purpose} \\
+            {real number}     & {counting all independent sets} \\
+            {tropical number} (\Eq{eq:countingtropical})    & {finding the independence number} \\
+            {tropical number with counting} (\Eq{eq:countingtropical})     & {finding the independence number and the number of MISs} \\
+            {tropical number with configurations} (\Eq{eq:singleconfig})     & {finding the independence number and one MIS} \\
+            {tropical number with sets} (\Eq{eq:set})    & {finding the independence number and enumeration of all MISs} \\
+            {polynomial} (\Eq{eq:polynomial})     & {computing the independence polynomial exactly} \\
+            {truncated polynomial} (\Eq{eq:max2poly})     & {counting MISs and independent sets of size $\alpha(G)-1$} \\
+            {complex number}     & {fitting the independence polynomial with fast Fourier transform} \\
+            {finite-field algebra (\Eq{eq:finitefield})} & {fitting the independence polynomial exactly using number theory} \\
+            \bottomrule
+        \end{tabularx}
+    }
+    \caption{Tensor element types and their purposes in calculating various independent set properties.}\label{tbl:generictypes}
+\end{minipage}
+\end{table}
+
+\section{Independence polynomial and maximal independence polynomial}
+\subsection{Independence polynomial}\label{sec:indpoly}
+The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
+\begin{equation}
+I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the independence number.
+The total number of independent sets is thus equal to $I(G, 1)$.
+The problem of computing the independence polynomial belongs to the complexity class \#P-hard.
+One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
+There are some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact methods to compute the independence polynomial.
+
+The independence polynomial is closely related to the matching polynomial, the clique polynomial, and the vertex cover polynomial.
+In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{levit2005Independence}.
+Thus, our algorithm to compute the independence polynomial can also be used to compute the above graph polynomials.
+Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{levit2005Independence}.
+We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
+
+To compute the independence polynomial of a graph $G$, we encode it to a tensor network.
+On the vertex $i$ of the graph $G$, we place a rank-one vertex tensor, $W(x_i)$, of size $2$ parametrized by $x_{i}$ and a rank-two edge tensor, $B$, of size $2 \times 2$ on an edge $(i,j)$
+\red{I removed the indices $s_{i}$ etc, on the right of the equations, since that looks confusing to me. If I understand correctly, $s_{i}, s_{j}$ just denotes the index of the vector/matrix.}
 \begin{equation}
@@
         x_i
-    \end{matrix}\right)_{s_i},\label{eq:wtensor}
-\end{equation}
-and a rank two tensor of size $2 \times 2$ on an edge $(i,j)$
-\begin{equation}
+    \end{matrix}\right),
+    \qquad \quad 
        B_{s_i s_j} = \left(\begin{matrix}
@@
         1 & 0
-    \end{matrix}\right)_{s_is_j},\label{eq:btensor}
-\end{equation}
-where a tensor index $s_i$ is a boolean variable that having the meaning of being 1 if vertex $i$ is in the independent set, 0 otherwise.
-It corresponds to a hyperedge in the hypergraph.
-The contraction of such a tensor network gives
-\begin{equation}
-    P(G, \{x_1,\ldots,x_n\}) = \sum\limits_{s_1, s_2, \ldots, s_n = 0}^{1} \prod\limits_{i=1}^n W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
-\end{equation}
-where the summation runs over all vertex configurations $\{s_1,\ldots,s_n\}$ and accumulates the product of tensor elements to the scalar output $P$.
-We can see an edge tensor represents the restriction on an edge that if both vertices connected by it are included in the set, then such configuration has no contribution to the output.
-When we set $x_i = x$, the contraction result corresponds to the independence polynomial.
-One can see the connection from the fact that the product over vertex tensor elements gives a factor $x^k$, where $k=\sum_i s_i$ counts the set size, 
-and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set, $0$ otherwise.
-One directly benefit of mapping the independent set problem to a tensor network is one can take the advantage of recently developed techniques in tensor network based quantum circuit simulations ~\cite{Gray2021,Pan2021},
-where people evaluate a tensor network by pairwise contracting tensors in a heuristic order.
-A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{tw(G)})$.
-Here $tw(G)$ is the tree width of the line graph of a tensor network hypergraph, while the line graph of a tensor network hypergraph corresponds to the original graph $G$ that we mapped from.~\cite{Markov2008}
-The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up our computation for certain tensor element types.
-
-\begin{example}
-    Mapping a graph (left) to a tensor network, the resulting tensor network is shown in the right panel.
-    In the generalize tensor network's graphical representation, a vertex is mapped to a hyperedge,
-    and an edge is mapped to an edge tensor.
+    \end{matrix}\right), \label{eq:tensor}
+\end{equation}
+where the tensor index $s_i$ is a boolean variable; $s_{i} = 1$ corresponds that the vertex $i$ is in the independent set, and $s_{i} = 0$ means otherwise.
+Let us assume the tensor elements are real numbers for now.
+The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
+The contraction of the tensor network representing $G$ gives
+\begin{equation}
+    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
+\end{equation}
+where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the scalar output $P$ (see Example \ref{eg:tensorcontraction} for a concrete example).
+In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
+The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size, and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise.
+In the implementation of the algorithm, we benefit from recent advances in tensor network contraction, where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a good heuristic order~\cite{Gray2021, Pan2021}.
+A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
+The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
+
+\begin{example}\label{eg:tensorcontraction}
+Mapping a graph (left) to a tensor network (right) that encodes the independence polynomial.
+In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge, and an edge is mapped to an edge tensor.
+\red{a vertex is mapped to a hyperedge?}
 
@@
                     ]  
-
         \def\dx{0};
@@
     \end{tikzpicture}}
-    The contraction of this network can be done in a pairwise order.
+
+    The contraction of this tensor network can be done in a pairwise order:
     \begin{align*}
-        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}.\\
+        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
         =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e)_{s_e}\right) W(x_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c)_{s_c}\right)\right)\right.\\
@@
         =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e\\
-        =&1+5x+4x^2
+        =&1+5x+4x^2 \qquad \quad (x_{i} = x)
     \end{align*}
@@
 
-Before contracting the tensor network and evaluating the independence polynomial numerically, let us first give up thinking $0$s and $1$s in tensors $W(x)$ and $B$ as regular computer numbers such as integers and floating point numbers.
-Instead, we treat them as the additive identity and multiplicative identity of a commutative semiring.
-A semiring is a ring without additive inverse, while a commutative semiring is a semiring that multiplication commutative.
-To define a commutative semiring with addition algebra $\oplus$ and multiplication algebra $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
-\begin{align*}
-(a \oplus b) \oplus c = a \oplus (b \oplus c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\oplus$ with identity $\mymathbb{0}$}\\
-a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
-a \oplus b = b \oplus a &\\
-&\\
-(a \odot b) \odot c = a \odot (b \odot c)  &   \hspace{5em}\text{$\triangleright$ commutative monoid $\odot$ with identity $\mymathbb{1}$}\\
-a \odot  \mymathbb{1} =  \mymathbb{1} \odot a = a &\\
-a \odot b = b \odot a &\\
-&\\
-a \odot (b\oplus c) = a\odot b + a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
-(a\oplus b) \odot c = a\odot c \oplus b\odot c &\\
-&\\
-a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
-\end{align*}
-The property of being commutative is required here because we want the contraction result independent of the contraction order.
-In the following, we show how to obtain the independence polynomial, the maximum independent set size and optimal configurations of a general graph $G$ by designing tensor element types as commutative semirings,
-i.e. making the tensor network generic~\cite{Stepanov2014}.
-A straight forward approach to evaluate the independence polynomial is treating the tensor elements as polynomials, and evaluate the polynomial directly.
-Let us create a polynomial type, and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a vector $(a_0, a_1, \ldots, a_k) \in R^k$, e.g. $x$ is represented as $(0, 1)$.
+Before contracting the tensor network and evaluating the independence polynomial numerically, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from integers and floating point numbers to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+The most natural approach is to treat the tensor elements as polynomials and evaluate the polynomial directly.
+Let us create a polynomial type, and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $(a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
 We define the algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ as
-\begin{align}
+\begin{equation}
     \begin{split}
     a \oplus b &= (a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
-    a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, \ldots, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (),\\
+    a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, a_{2}b_{0} + a_{1}b_{1} + a_{0}b_{2},  \ldots, a_{k_a} b_{k_b}),\\
+    \mymathbb{0} &= (), \text{\red{should this be (0)?}} \\
     \mymathbb{1} &= (1).\label{eq:polynomial}
     \end{split}
-\end{align}
-By contracting the tensor network with polynomial type, the final result is the exact representation of the independence polynomial.
-In the program, the multiplication can be evaluated efficiently with the convolution theorem~\cite{Schonhage1971}.
-However, this approach suffers from a space overhead that proportional to the maximum independent set size because each polynomial requires a vector of such size to store the factors.
-In \App{app:fft}, we provide a fitting based approach to compute the independence polynomial.
-One just set $x$ to $\alpha(G)+1$ random values, compute the result and use the polynomial fitting to get the factors.
-In this way, we do not have linear overheads in space, however, 
-due to fact that countings of different MIS sizes can be different in many orders, 
-the round off error dominates the high MIS size region that we are most interested about if we use floating point numbers in computation, 
-meanwhile the number easily overflows if we use fixed width integer types.
-The big integer type is not an option because big integers with varying width can be very slow and incompatible with graphic processing units (GPU) devices.
-Then we want to resort to integer numbers, however, fixed width integer types are often too small to store the counting,
-This problem can be solved by introducing finite field algebra $GF(p)$
-\begin{align}
+\end{equation}
+We can see these operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
+\begin{equation}
+    W_{s_i}^{\rm poly} = \left(\begin{matrix}
+        \mymathbb{1} \\
+        (0,1)
+    \end{matrix}\right),   
+    \qquad \qquad
+        B_{s_i s_j}^{\rm poly} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
+\end{equation}
+By contracting the tensor network with the polynomial type, the final result is the exact representation of the independence polynomial.
+One way to efficiently evaluate the multiplication operation is to use the convolution theorem~\cite{Schonhage1971}, but this approach suffers from a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients.
+
+Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random values of $x_{i}$ and $y_{i} = I(G,x_{i})$.
+One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
+\begin{equation}
+\left(\begin{matrix}
+1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
+1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
+\end{matrix}\right).\label{eq:lineareq}
+\end{equation}
+With this approach, we do not incur the linear overhead in space.
+However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large independent set sizes.
+In addition, the number could easily overflow if we use fixed-width integer types.
+The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with graphics processing unit (GPU) devices.
+These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
+\begin{equation}
 \begin{split}
@@
 \end{split}\label{eq:finitefield}
-\end{align}
-In a finite field algebra, we have the following observations
+\end{equation}
+With a finite-field algebra, we have the following observations:
 \begin{enumerate}
-    \item One can use Gaussian elimination~\cite{Golub2013} to solve a linear equation \Eq{eq:lineareq}
-    because it is a generic function that works for any elements with field algebra.
-    The multiplicative inverse of a finite field algebra can be computed with the extended Euclidean algorithm.
-    \item Given the remainders of a larger unkown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
-    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem.
-    With this, one can infer big integers from small integers.
+    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
+The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
+    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
+    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
 \end{enumerate}
-With these observations, we developed Algorithm~\ref{alg:finitefield} to compute independence polynomial exactly without introducing space overheads.
-In the algorithm, except the computation of Chinese remainder theorem, all computations are done with integers of fixed width $W$.
+With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
+In the algorithm, except the computation using the Chinese remainder theorem, all computations are done with integers of fixed width $W$.
+In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transform.
 
@@
     \LinesNumbered
-    Let $P = 1$, vector $X = (0,1,2,\ldots,m)$, matrix $\hat X_{ij} = X_i^j$, where $i,j = 0, 1, \ldots m$\;
+    Let $P = 1$, $W$ be the integer width, vector $X = (0,1,2, \ldots, \alpha(G))$, matrix $\hat X_{ij} = X_i^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
 
@@
 
-        compute the tensor contraction on $GF(p)$ and obtain $Y = (y_0, y_1, \ldots , y_m) \pmod p $\;
-
-        $A_p = (a_0, a_1, \ldots, a_m) \pmod p = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+        compute the tensor contraction on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\; \red{tensor network contraction for each $i$}
+
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
 
@@
         $P = P \times p$\;
-    }\caption{Compute independence polynomial exactly without integer overflow}\label{alg:finitefield}
+    }\caption{Exactly compute the independence polynomial of a graph $G$ without integer overflow}\label{alg:finitefield} \red{discuss this algorithm table, $X_{ij}$, etc.}
 \end{algorithm}
 
-\subsection{Maximal independence polynomial}
-Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
-In this paper, the word ``maximal'' is different with the ``maximum'' discussed the previous discussion in such a way that it is not necessarily refer to the gloal optimum.
-Let us denote the neighbour of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent sets that there does not exist a vertex $v$ that $N[v] \cap I_m = \emptyset$.
-Let us modify the tensor network for computing independence polynomial by adding this restriction.
-Instead of defining the restriction on vertices and edges, we define it on $N[v]$
-\begin{align}
+\subsection{Maximal independence polynomial} \red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} Instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017On}.
+Concretely, it is defined as
+\begin{equation}
+I_{\rm max}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
+\end{equation}
+where $b_k$ is the number of maximal independent sets of size $k$ in $G$.
+Obviously, $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
+$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012On, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012On}.
+For the problem of finding the MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
+The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017On}.
+
+Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent set where there exists no vertex $v$ such that $I_m \cap N[v]  = \emptyset$.
+We can modify the tensor network for computing the independence polynomial to include this restriction.
+Instead of defining the restriction on vertices and edges, it is more natural to define it on $N[v]$:
+\begin{equation}\label{eq:maximal}
     T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
@@
     \end{cases}
-\end{align}
-As an example, for a vertex of degree 2, the resulting rank 3 tensor is
-\begin{align}
+\end{equation}
+Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$, and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t.
+$s_{i} = 1$, then $v$ cannot be in $I_{m}$.
+As an example, for a vertex of degree 2, the resulting rank-3 tensor is
+\begin{equation}
     T(x_v)=\left(\begin{matrix}
@@
     \end{matrix}\right).
-\end{align}
-
-We do the same computation as independence polynomial, the coefficients of resulting polynomial gives the counting of maximal independent sets, or the maximal independence polynomial.
-The computational complexity of this new tensor network is often larger than the one for computing independence polynomial.
-However, in many sparse graphs, this tensor network contraction approach is still much faster than computing the maximal cliques on its complement by applying the Bron-Kerbosch algorithm.
+\end{equation}
+
+With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
+The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
+However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973Algorithm}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
 
 \section{Maximum independent sets and its counting problem}
-In the previous section, we focused on computing independence polynomial for a given maximum independent set size $\alpha(G)$, but we didn't mention how to compute this number.
-The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
-\begin{equation}
-I(G, \infty) = a_k \infty^{\alpha(G)},
-\end{equation}
-where the lower orders terms disappear automatically. We can define a new algebra as
-\begin{align}
+\subsection{Tropical algebra for finding the independence number and counting MISs}
+In the previous section, we focused on computing the independence polynomial for a graph $G$ of given independence number $\alpha(G)$, but we did not show how to compute this number.
+The method we use to compute this quantity is based on the following observations.
+Let $x=\infty$, the independence polynomial becomes
+\begin{equation}
+I(G, \infty) = a_{\alpha(G)} \infty^{\alpha(G)},
+\end{equation}
+where the lower-order terms vanish.
+We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with $a(k) = (a_{k}, k)$, where the second element stores the largest exponent $k$ and the first element stores the corresponding coefficient $a_{k}$.
+From this, we can define a new algebra as \red{I've changed this, but I don't have strong feelings about this.
+We can certainly consider changing back.
+I thought this would be more consistent with the earlier notations and show how it's stored in the program as well.}
+\begin{equation}
 \begin{split}
-    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
-        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
-        a_y\infty^{\max(x,y)}, & x < y\\
-        a_x\infty^{\max(x,y)}, & x > y
-    \end{cases}\\
-    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-    \mymathbb{0} &= 0\infty^{-\infty}\\
-    \mymathbb{1} &= 1\infty^{0}\label{eq:countingtropical}
+    a(k) \oplus a(j) &= \begin{cases}
+        \left(a_k + a_j, \max(k,j) \right), & k = j \\
+        \left(a_j, \max(k,j) \right), & k < j \\
+        \left(a_k, \max(k,j) \right), & k > j
+    \end{cases}, \\
+    a(k) \odot a(j) &= (a_k a_j, k+j) \\
+    \mymathbb{0} &= (0, -\infty)\\
+    \mymathbb{1} &= (1, 0). \label{eq:countingtropical}
 \end{split}
-\end{align}
-In the program, we only store the power $x$ and the corresponding factor $a_x$ that initialized to $1$.
-This algebra is the same as the one in ~\cite{Liu2021} for counting spin glass ground states.
-If one is only interested in obtaining $\alpha(G)$, he can drop the factor parts, then the new algebra becomes the max-plus tropical algebra~\cite{Maclagan2015,Moore2011}.
-
-\subsection{Sub-optimal solutions}
-Some times people are interested in finding sub-optimal solutions efficiently.
-We define a truncated polynomial algebra by keeping only largest two factors in the polynomial in \Eq{eq:polynomial}.
-\begin{align}
+\end{equation}
+%\begin{equation}
+%\begin{split}
+%    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
+%        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
+%        a_y\infty^{\max(x,y)}, & x < y\\
+%        a_x\infty^{\max(x,y)}, & x > y
+%    \end{cases}, \\
+%    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
+%    \mymathbb{0} &= 0\infty^{-\infty}\\
+%    \mymathbb{1} &= 1\infty^{0}. \label{eq:countingtropical}
+%\end{split}
+%\end{equation}
+% In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
+The algebra of the exponents becomes the max-plus tropical algebra: $k \oplus j = \max(k,j)$ and $k \odot j = k + j$~\cite{Maclagan2015, Moore2011}.
+This algebra is the same as the one used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
+For independent set calculations here, the vertex tensor and edge tensor becomes:
+\begin{equation}
+    W_{s_i}^{\rm tropical} = \left(\begin{matrix}
+        \mymathbb{1} \\
+        (1,1)
+    \end{matrix}\right),   
+    \qquad \qquad
+        B_{s_i s_j}^{\rm tropical} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
+\end{equation}
+
+\subsection{Truncated polynomial algebra for counting independent sets of large size}
+Instead of counting just the MISs, one may be interested in counting the independent sets of large sizes close to the MIS size.
+For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial}:
+\begin{equation}
     \begin{split}
@@
     a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (),\\
+    \mymathbb{0} &= (), \text{\red{should this be (0)?}}  \\
     \mymathbb{1} &= (1).\label{eq:max2poly}
     \end{split}
-\end{align}
-%By changing the factors to sets, and plus and multiplication operations on factors to set union and product, one can get all suboptimal solutions too.
-In the program, we need a data structure that contains three fields, the largest order $k$ and factors for two largest orders $a_k$ and $a_{k-1}$.
-
-\section{Enumerating configurations}
-One may also want to obtain all solutions, it can be achieved replacing the factors with a set of solutions,
-We design a new element type having the following algebra
-\begin{align}
+\end{equation}
+In the program, we thus need a data structure that contains three fields, the largest order $k$, and the coefficients for the two largest orders $a_k$ and $a_{k-1}$.
+This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
+\red{can be used to enumerate suboptimal solution as well?}
+
+\section{Enumeration of configurations and enumeration bounds}
+\subsection{Enumeration of MIS configurations}
+The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973Algorithm, Eppstein2010Listing, Johnson1988On}, including, for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
+The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973Algorithm}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
+Here, we adapt the tensor element types for different enumeration problems.
+For example, our tensor-network based algorithm to enumerate all MISs is expectedly much faster and more space-efficient than the Bron-Kerbosch algorithm, which lists all maximal independent sets.
+
+To enumerate all independent sets, we input a set of configurations into the tensor elements. More concretely, we design a new element type having the following algebra
+\begin{equation}
 \begin{split}
     s \oplus t &= s \cup t\\
-    s \odot t &= \{\sigma \lor^\circ \tau | \sigma \in s, \tau \in t\}\\
+    s \odot t &= \{\sigma \lor^\circ \tau \, | \, \sigma \in s, \tau \in t\}\\
     \mymathbb{0} &= \{\}\\
-    \mymathbb{1} &= \{0^{\otimes n}\}
+    \mymathbb{1} &= \{0^{\otimes |V|}\}.
 \end{split}\label{eq:set}
-\end{align}
-where $\lor^\circ$ is the Hadamard logic or operation over two bit strings, which means joining of two local configurations.
-The variable $x$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$,
-where $\boldsymbol{e}_i$ is a one hot vector of size $|G|$.
-As an example, if we want to enumerate all maximum independent sets, we can use the above set as the factors in \Eq{eq:countingtropical}.
-We get the following new algebra.
-\begin{align}
+\end{equation}
+where $s$ and $t$ are each a set of $|V|$-bit strings and $\lor^\circ$ is the bitwise OR operation over two bit strings.
+\red{This is the bitwise OR operation right?
+I can't seem to find online what you call Hadamard.
+Is there a definition somewhere?} \red{it would be useful to give an example of the operations above, $s = ...
+, t = ..., s \oplus t = ..., s \odot t = ...$.} \red{do we need to define $ \{\} \lor^\circ \sigma  = \sigma \lor^\circ \{\} = \{\}$?} The variable $x_{i}$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
+The vertex and edge tensors are thus
+\begin{equation}
+    W_{s_i}^{\rm enum} = \left(\begin{matrix}
+        \mymathbb{1} \\
+        \{\boldsymbol{e}_{i}\}
+    \end{matrix}\right),   
+    \qquad \qquad
+        B_{s_i s_j}^{\rm enum} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
+\end{equation}
+Contraction of the tensor network enumerates all the independent sets.
+To enumerate only the MISs, we can combine the above algebra \Eq{eq:set} with the tropical algebra in \Eq{eq:countingtropical} and define $s(k) = (s_{k}, k)$, where the first element follows the algebra in \Eq{eq:set} and the second element follows the max-plus tropical algebra.
+The combined operations become:
+\begin{equation}
 \begin{split}
-    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
-        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
-        s_y\infty^{\max(x,y)}, & x < y\\
-        s_x\infty^{\max(x,y)}, & x > y
-    \end{cases},\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
-    \mymathbb{0} &= \{\}\infty^{-\infty},\\
-    \mymathbb{1} &= \{0^{\otimes n}\}\infty^{0},
+    s(k) \oplus s(j) &= \begin{cases}
+        \left(s_k \cup s_j, \max(k,j) \right), & k = j \\
+        \left(s_j, \max(k,j) \right), & k < j \\
+        \left(s_k, \max(k,j) \right), & k > j
+    \end{cases}, \\
+    s(k) \odot s(j) &= (\{\sigma \lor^\circ \tau \, | \, \sigma \in s_k, \tau \in s_j\}, k+j) \\
+    \mymathbb{0} &= (\{ \}, -\infty)\\
+    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropical}
 \end{split}
-\end{align}
-One can easily check if the factor algebra is a commutative semiring,
-when we use the above algebra as factors of independence polynomials, the resulting algebra is also a commutative semiring.
-If one is only interested in obtaining a single configuration, one can also just keep a single configuration to save the computational effort.
-We arrive at a new algebra defined on bit strings.
+\end{equation}
+%\begin{equation}
+%\begin{split}
+%    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
+%        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
+%        s_y\infty^{\max(x,y)}, & x < y\\
+%        s_x\infty^{\max(x,y)}, & x > y
+%    \end{cases},\\
+%    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+%    \mymathbb{0} &= \{\}\infty^{-\infty},\\
+%    \mymathbb{1} &= \{0^{\otimes |V|}\}\infty^{0},
+%\end{split}
+%\end{equation}
+Clearly, the vertex tensor and edge tensor become
+\begin{equation}
+    W_{s_i}^{\rm MISenum} = \left(\begin{matrix}
+        \mymathbb{1} \\
+        \left({\{\boldsymbol{e}_{i}\}, 1} \right)
+    \end{matrix}\right),   
+    \qquad \qquad
+        B_{s_i s_j}^{\rm MISenum} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
+\end{equation}
+The contraction of the corresponding tensor network yields an enumeration of all MIS configurations.
+If one is interested in obtaining only a single MIS configuration, one can just keep a single configuration in the intermediate computations to save the computational effort.
+Here is a new algebra defined on the bit strings, replacing the sets of bit strings in \Eq{eq:set},
 %We leave this as an exercise for readers.
-
-\iffalse
-\begin{align}
+%
+%\iffalse
+%\begin{equation}
+%\begin{split}
+%    \sigma_x\infty^x \oplus \sigma_y\infty^y &= \begin{cases}
+%        {\rm select}(\sigma_x, \sigma_y)\infty^{\max(x,y)}, & x = y\\
+%        \sigma_y\infty^{\max(x,y)}, & x < y\\
+%        \sigma_x\infty^{\max(x,y)}, & x > y
+%    \end{cases},\\
+%    \sigma_x\infty^x \odot \sigma_y\infty^y &= (\sigma_x \lor^\circ \sigma_y)\infty^{x+y},\\
+%    \mymathbb{0} &= 1^{\otimes n}\infty^{-\infty},\\
+%    \mymathbb{1} &= 0^{\otimes n}\infty^{0},
+%\end{split}
+%\end{equation}
+%\fi
+\begin{equation}
 \begin{split}
-    \sigma_x\infty^x \oplus \sigma_y\infty^y &= \begin{cases}
-        {\rm select}(\sigma_x, \sigma_y)\infty^{\max(x,y)}, & x = y\\
-        \sigma_y\infty^{\max(x,y)}, & x < y\\
-        \sigma_x\infty^{\max(x,y)}, & x > y
-    \end{cases},\\
-    \sigma_x\infty^x \odot \sigma_y\infty^y &= (\sigma_x \lor^\circ \sigma_y)\infty^{x+y},\\
-    \mymathbb{0} &= 1^{\otimes n}\infty^{-\infty},\\
-    \mymathbb{1} &= 0^{\otimes n}\infty^{0},
+    \sigma \oplus \tau &= {\rm select}(\sigma, \tau), \\
+    \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
+    \mymathbb{0} &= 1^{\otimes |V|}, \red{\text{should be } \mymathbb{0} = \{\}?} \\
+    \mymathbb{1} &= 0^{\otimes |V|},
+\end{split}\label{eq:singleconfig}
+\end{equation}
+where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking one with a larger integer value.
+In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
+
+\red{The zero element doesn't seem right to me. Do we need to separately define 
+\begin{align*}
+a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
+a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
+\end{align*}
+}
+
+\red{Can we also enumerate all maximal independent sets by combining with \Eq{eq:maximal} or enumerate suboptimal solutions by combining with the truncated polynomial?}
+
+\subsection{Bounding the MIS enumeration space}
+When we use the algebra in \Eq{eq:countingtropical} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
+To speed up the computation and reduce space overhead, we use $\alpha(G)$ to bound the searching space.
+First, we compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
+Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
+Finally, we perform masked matrix multiplication using the new element type with the above algebra, \Eq{eq:countingtropical}, for obtaining all configurations.
+Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagation of the gradients.
+To derive the back-propagation rule for tensor contraction, we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
+Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
+\begin{equation}
+    A_{ij} \odot B_{jk} \leq C_{ik}.
+\end{equation}
+Here $\leq$ on tropical numbers are the same as the real-number algebra.
+The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
+Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality:
+\begin{equation}
+    A_{ij} \leq C_{ik} \odot B_{jk}^{\circ -1}
+\end{equation}
+where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers). The inequality still holds if we take the minimum over $k$: 
+\begin{equation}
+    \begin{split}
+    A_{ij} &\leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
     \end{split}
-\end{align}
-\fi
-\begin{align}
-\begin{split}
-    \sigma \oplus \tau &= {\rm select}(\sigma, \tau)\\
-    \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
-    \mymathbb{0} &= 1^{\otimes n},\\
-    \mymathbb{1} &= 0^{\otimes n},
-\end{split}\label{eq:singleconfig}
-\end{align}
-where the \texttt{select} function picks one of $\sigma_x$ and $\sigma_y$ by some criteria to make the algebra commutative and associative, e.g. by their integer values.
-In practise, one can just pick randomly from them, then the program will output one of the configurations randomly.
-
-\subsection{Bounding the enumeration space}
-When one uses the set algebra in \Eq{eq:set} to represent the factors in \Eq{eq:countingtropical} for enumerating all optimum configurations, he will find the program stores more than necessary intermediate configurations and cause significant overheads in space.
-To speed up the computation, we use $\alpha(G)$ to bound the searching space.
-We first compute the value of $\alpha(G)$ with tropical numbers and cache all intermediate tensors.
-Then we compute a boolean masks for each cached tensor, where we use a boolean true to represent a tensor element having contribution to the maximum independent set (i.e.
-with a non-zero gradient) and boolean false otherwise.
-Finally, we perform masked matrix multiplication using the new element type with the above algebra for obtaining all configurations.
-Notice that these masks are in fact tensor elements with non-zero gradients with respect to MIS size, we compute these masks by back propagating gradients.
-To derive the backward rule for tensor contraction,
-we first reduce the problem to finding the backward rule of a tropical matrix multiplication $C = A B$,
-where we have the following inequality
-\begin{align}
-    A_{ij} \odot B_{jk} &\leq C_{ik}.
-\end{align}
-Here is $\leq$ on tropical numbers are same as regular algebra.
-The tropical multiplication $\odot$ is the same as the regular $+$, then
-one can move $B_{ik}$ to the right hand side and get
-\begin{align}
-    A_{ij} &\leq C_{ik} \odot B_{jk}^{\circ -1}
-\end{align}
-where the tropical multiplicative inverse is defined as the additive inverse of the regular algebra.
-The inequality still holds if we take the minimum over $k$
-\begin{align}
-    \begin{split}
-    A_{ij} &\leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = (\oplus_{k} (C_{ik}^{-1} \odot B_{jk}))^{\circ -1}.
-    \end{split}
-\end{align}
-On the right hand side, we transformed the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines.
-The equality holds if and only if element $A_{ij}$ has contribution to $C$ (i.e. has non-zero gradient).
-Let the gradient mask for $C$ being $\overline C$, the backward rule for gradient masks reads
-\begin{align}
-\overline{A}_{ij} = \delta(A_{ij}, ((C^{\circ-1} \circ \overline C )B^T)_{ij}^{\circ -1}),
-\end{align}
-where ${}^{\circ -1}$ is the Hadamard inverse, $\circ$ is the Hadamard product, boolean false is treated as tropical zero and boolean true is treated as tropical one.
-This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^T$ by a tensor contraction.~\cite{} \blue{maybe add an appendix?}  % my blog
-
-\section{Benchmarks and case study}
-We run a sequetial program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results bellow.
+\end{equation}
+On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines \red{do we need to cite here?}.
+Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
+Let the gradient mask for $C$ being $\overline C$, the back-propagation rule for gradient masks reads
+\begin{equation}
+\overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
+\end{equation}
+where $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
+This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
+With the above method, one can significantly reduce the space needed to store the intermediate configurations.
+\blue{maybe add an appendix?} \red{I've edited this section a bit, and I think it's okay now - probably don't need an appendix.}  % my blog
+%
+%\section{Tropical tensors for automated branching}\blue{$?$}
+%% check http://www.tcs.rwth-aachen.de/independentset/ for more rules
+%Branching rules can be automatically discovered by contracting the tensor network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
+%Let $C$ be the set of boundary vertices defined as $C := \{u | u\in R \land (\exists v \in (G\backslash R) \land {\rm adj}(u, v))\}$, then the rank of the resulting tensor $A$ is $|C|$.
+%Here, we use ${\rm adj}(u, v)$ to denote two vertices $u$ and $v$ are adjacent to each other.
+%Each tensor entry $A_{\sigma}$ is a local maximum independent set size for the fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$.
+%Suppose our goal is to find the maximum independent set size,
+%then this tensor can be further ``compactified'' by removing some entries.
+%To determine which entry can be removed, let us define a relation of \textit{less restrictive} as
+%\begin{align}
+%(\sigma_a \prec \sigma_b) := (\sigma_a \neq \sigma_b) \land (\sigma_a \leq^\circ \sigma_b)
+%\end{align}
+%where $\leq^\circ$ is the Hadamard less or equal to operation.
+%
+%\begin{definition}
+%A tensors $A$ is \textit{MIS-compact} if
+%\begin{align}
+%\forall{\sigma_b}\neg \exists{\sigma_a}(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
+%\end{align}
+%\end{definition}
+%
+%If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranteed to give the same maximum independent set size.
+%It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compactifying} (a) and (b).
+%If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independent sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
+%Hence, we can remove entry $A_{\sigma_b}$ safely.
+%%among boundary configurations with equal local maximum independent sizes,
+%%we only retain those least restrictive (less ones at the boundary) to exterial configurations.
+%
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
+%    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compactifying}
+%\end{figure}
+%
+%\begin{theorem}
+%    A MIS-compact tropical tensor can not be further reduce without gloal information, i.e. any of its non-zero entries can produce the only global optimal solution given a proper environment.
+%\end{theorem}
+%
+%\begin{proof}
+%    %Given $A_\{\sigma_a}$ is better than $A_\{\sigma_b\}$, any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
+%    Let us prove it by showing for any $\sigma$ in a MIS-compact tropical tensor of a subgraph $R$, there exists a parent graph $G$ that $R\subseteq G$ and $\sigma$ is the boundary configuration that gives the only maximum independent set.
+%    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the boundary configuration.
+%    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, we connect it with two vertices $u, w \in G \backslash R$ that ${\rm adj}(v, u) \land {\rm adj}(u, w) \land \neg{\rm adj}(v, w)$.
+Otherwise, we attach infinite many disconnected neighbors to $v$.
+%
+%    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 5cm 0cm}, clip]{proofoptimal.pdf}}
+%    Then we have the maximum independent set size $\alpha(G,\sigma) = A_{\sigma} + \infty (|C|-\sum_{v=1}^{|C|}\sigma_v) + \sum_{v=1}^{|C|} 1-\sigma_v$.
+%    Let us assume there exists another configuration $\tau$ that generating the same or better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
+%    Then we have $\tau \prec \sigma$, otherwise it will loss infinite contribution from the environment.
+%    For such a $\tau$, we have $A_\tau < A_\sigma$, otherwise $A_\sigma \prec A_\tau$ contradicts with $A$ being MIS-compact.
+%    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} + \sum_{v=1}^{|C|} 1-\sigma_v < \alpha(G,\sigma)$, hence $\sigma$ is the only boundary configuration that gives the maximum independent set for this graph.
+%\end{proof}
+%
+%\subsection{The tensor network compactification detects branching rules automatically}
+%Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
+%by including its neighbourhoods,
+%and keep only the configurations that has the potential to produce the only maximum independent set.
+%Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for the $k$-th neighbourhood $N^k[v]$, one can discover the optimal branching vector automatically.
+%In the following, we are going to introduce several important rules for branching in the literature and show how it is connected to our tensor formulation.
+%
+%\begin{corollary}\label{rule:one} % basic
+%  If a vertex $v$ is in an independent set $I$, then none of its Neighbors can be in $I$.
+%On the other hand, if $I$ is a maximum (and thus maximal) independent set,
+%and thus if $v$ is not in $I$ then at least one of its Neighbors is in $I$.
+%\end{corollary}
+%
+%Contract $N[v]$ and the resulting tensor $A$ has a rank $|N(v)|$.
+Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independent set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
+%If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independent set size.
+%
+%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/basic.pdf}}
+%
+%After contracting $N[v]$, $v$ becomes an internal degree of freedom.
+%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
+%
+%\begin{align}
+%    T_{juwk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        ~~~~1 & -\infty \\
+%        -\infty & ~~~~2
+%        \end{matrix}\right)_{ju}&
+%        \left(\begin{matrix}
+%        -\infty & ~~~~2 \\
+%        ~~~~2 & ~~~~3
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        -\infty & ~~~~2 \\
+%        ~~~~2 & ~~~~3
+%        \end{matrix}\right)_{ju} &
+%        \left(\begin{matrix}
+%        ~~~~2 & ~~~~3 \\
+%        ~~~~3 & ~~~~4
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{wk},
+%\end{align}
+%where we use ``-'' to denote an entry is forbidden.
+%If we use sets for counting, one can check all configurations too. The resulting polynomial tensor is
+%\begin{align}
+%    P_{juwk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        1+x_v & - \\
+%        - & ~~x_jx_u
+%        \end{matrix}\right)_{ju}&
+%        \left(\begin{matrix}
+%        - & x_ux_k \\
+%        ~~~~x_jx_k & ~~~~x_ux_jx_k
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        - & x_wx_u \\
+%        x_wx_j & x_wx_jx_u
+%        \end{matrix}\right)_{ju} &
+%        \left(\begin{matrix}
+%        x_wx_k & x_wx_kx_u \\
+%        x_wx_kx_j & x_jx_ux_wx_k
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{wk}.
+%\end{align}
+%
+%By studying the correlation between vertex variables, one can easily see $x_v$ does not co-exist with other vertex variables.
+%These anti-correlation determines possible branching vectors in the maximum independent set problem.
+%It is easier to see if we list the set of optimal solutions as
+%\begin{align}
+%    \begin{split}
+%    S_{juwkv} = \{&00001, 10001, 01010, 10010, 11010, 10100,\\&01100, 11100, 00110, 01110, 10110, 11110\}.
+%    \end{split}
+%\end{align}
+%%If we denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
+%%The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
+%%It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
+%The branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
+%
+%\begin{corollary}[mirror rule] % 2.7
+%For some $v \in V$, a node $u \in N^2(v)$ is called mirror of $v$, if $N(v) \backslash N(u)$ is a clique. We denote the set of of a node $v$ mirrors~\cite{Fomin2013} by $M(v)$.
+%Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
+%\begin{equation}
+%\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
+%\end{equation}
+%\end{corollary}
+%
+%This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
+%otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
+%Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighbourhood of $v$.
+%If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
+%since clique has at most one node in the MIS, by moving the occupied node to the interior, we obtain a ``better'' solution.
+%%Hence, the \textit{least restrictive principle} captures the mirror rule.
+%In the following example, since $u\in N^2(v)$ and $N(v) \backslash N(u)$ is a clique, $u$ is a mirror of $v$.
+%
+%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/mirror.pdf}}
+%
+%After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
+%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
+%
+%\begin{align}
+%    T_{juwk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        ~~~~1 & ~~~~2 \\
+%        ~~~~\cancel{1} & ~~~~\cancel{2}
+%        \end{matrix}\right)_{ju}&
+%        \left(\begin{matrix}
+%        ~~~~\cancel{1} & -\infty \\
+%        ~~~~2 & -\infty
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        ~~~~\cancel{1} & ~~~~\cancel{2} \\
+%        -\infty & -\infty
+%        \end{matrix}\right)_{ju} &
+%        \left(\begin{matrix}
+%        -\infty & -\infty \\
+%        -\infty & -\infty
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{wk},
+%\end{align}
+%where entries stroked through are removed by compactification. The corresponding polynomial tensor is
+%
+%\begin{align}
+%    P_{juwk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        1+x_v & x_u+x_ux_v \\
+%        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{}\\
+%        \end{matrix}\right)_{ju}&
+%        \left(\begin{matrix}
+%        ~~~~\cancel{} & - \\
+%        x_jx_k & -
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{} \\
+%        ~~~~~~~- & ~~~~~~~~~~~~~-
+%        \end{matrix}\right)_{ju} &
+%        \left(\begin{matrix}
+%        ~~~~- & - \\
+%        ~~~~- & -
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{wk}.
+%\end{align}
+%One can see $w$, as a mirror of $v$ does not appear in the maximum independent set after compactification.
+%
+%%In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
+%%which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
+%\begin{align}
+%    \begin{split}
+%    S_{juwkv} = \{&00001, 01001, 10010\}.
+%    \end{split}
+%\end{align}
+%
+%\begin{corollary}[satellite rule] % satellite rule
+%Let $G$ be a graph, $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
+%The set of satellites of a node $v$ is denoted by $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
+%\begin{equation}
+%\alpha(G) = \max\{\alpha(G \backslash \{v\}), \alpha(G \backslash N[S[v]]) + |S(v)| + 1\}.
+%\end{equation}
+%\end{corollary}
+%
+%This rule can be capture by contracting $N[v] \cup S(v)$.
+%In the following example, since $u \in N^2(v)$ and $w \in N(v)$ satisfies $N[w] \backslash N[v] = \{u\}$, $u$ is a satellite of $v$.
+%
+%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/satellite.pdf}}
+%
+%After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
+%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 3 polynomial tensor is
+%\iffalse
+%\begin{align}
+%    T_{juk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        ~~~~1 & ~~~~2 \\
+%        ~~~~2 & ~~~~\cancel{2}
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        ~~~~\cancel{1} & -\infty \\
+%        ~~~~\cancel{2} & -\infty
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{k}.
+%\end{align}
+%\fi
+%
+%\begin{align}
+%    P_{juk} = \left(\begin{matrix}
+%        \left(\begin{matrix}
+%        1+x_w+x_v & x_u + x_ux_v \\
+%        x_j+x_wx_j & ~~~~~~~~~~~~\cancel{}
+%        \end{matrix}\right)_{ju}\\
+%        \left(\begin{matrix}
+%        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~- \\
+%        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~-
+%        \end{matrix}\right)_{ju}
+%    \end{matrix}\right)_{k}.
+%\end{align}
+%
+%By choosing one of the optimal configurations in each entry,
+%we can see the satellite rule of either ${v, u} \in I$ or $v \notin I$ is satisfied.
+%
+%\begin{align}
+%    \begin{split}
+%    S_{juwkv} = \{&\{00100,00001\}, 10100, 01001\}.
+%    \end{split}
+%\end{align}
+%%In this case, the effective branching number is $3^{1/5}\approx 1.2457$. 
+%
+%%We can use the conditional entropy to discover branching rules automatically. 
+%%Let us take one best configuration a time from each entry of the compact polynomial matrix,
+%%and denote the resulting configuration set as $S$.
+%%The conditional entropy matrix here can be defined as
+%%\begin{align}
+%%    C_{uv} = H(s_u|s_v)
+%%\end{align}
+%%when two variables are strongly correlated to each other, the corresponding entry should be zero.
+%
+%\subsection{gadget design}\blue{$\times$}
+%
+%Suppose we have a local structure as the following.
+%
+%\centerline{\begin{tikzpicture}[scale=1.0]
+%    \def\r{0.2}
+%    \foreach \x/\y [count=\i] in {0.17/0.5,0.83/0.5,0.5/0.67,0.5/0.33}
+%        \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+%    \draw (1) -- (2);
+%    \draw (3) -- (4);
+%\end{tikzpicture}}
+%
+%
+%Contract this local structure gives the tropical tensor
+%
+%\begin{align}
+%    \left(\begin{matrix}
+%        \left(\begin{matrix}
+%            ~~~~0 & ~~~~1\\
+%            ~~~~1 & ~~~~2
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~1 & -\infty\\
+%            ~~~~2 & -\infty
+%        \end{matrix}\right) \\
+%        \left(\begin{matrix}
+%            ~~~~1 & ~~~~2\\
+%            -\infty & -\infty
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~2 & -\infty\\
+%            -\infty & -\infty
+%        \end{matrix}\right)
+%    \end{matrix}\right).
+%\end{align}
+%
+%The following gadget is equivalent to the above diagram up to a constant $2$.
+%
+%\centerline{\begin{tikzpicture}
+%    \def\nodes{(0.5, 0.33), (0.17, 0.5), (0.5, 0.67), (0.83, 0.5), (0.32, 0.44), (0.44, 0.44), (0.56, 0.44), (0.68, 0.44), (0.32, 0.56), (0.44, 0.56), (0.56, 0.56), (0.68, 0.56)}
+%    \def\edges{(1, 5), (1, 6), (1, 7), (1, 8), (2, 5), (2, 9), (3, 9), (3, 10), (3, 11), (3, 12), (4, 8), (4, 12), (5, 6), (5, 9), (5, 10), (6, 7), (6, 9), (6, 10), (6, 11), (7, 8), (7, 10), (7, 11), (7, 12), (8, 11), (8, 12), (9, 10), (10, 11), (11, 12)}
+%    \def\r{0.2}
+%    \foreach \p [count=\i] in \nodes{
+%        \parsept{\x}{\y}{\p}
+%        \pgfmathparse{((\x<0.2 || \x>0.8 || \y<0.35 || \y>0.65) ? 1 : 0)}
+%        \ifnum\pgfmathresult>0
+%            \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+%        \else
+%            \node[fill,circle,radius=\r] at (\x*8, \y*8) (\i) {};
+%        \fi
+%    }
+%    \foreach \e [count=\i] in \edges{
+%        \parsept{\x}{\y}{\e}
+%        \draw (\x) -- (\y);
+%    }
+%\end{tikzpicture}}
+%
+%\begin{align}
+%    \left(\begin{matrix}
+%        \left(\begin{matrix}
+%            ~~~~2 & ~~~~3\\
+%            ~~~~3 & ~~~~4
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~3 & ~~~~3\\
+%            ~~~~4 & ~~~~4
+%        \end{matrix}\right) \\
+%        \left(\begin{matrix}
+%            ~~~~3 & ~~~~4\\
+%            ~~~~2 & ~~~~3
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~4 & ~~~~4\\
+%            ~~~~3 & ~~~~4
+%        \end{matrix}\right)
+%    \end{matrix}\right)
+%    \xrightarrow[\text{compactify, -2}]{}
+%    \left(\begin{matrix}
+%        \left(\begin{matrix}
+%            ~~~~0 & ~~~~1\\
+%            ~~~~1 & ~~~~2
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~1 & ~~~~\cancel{1}\\
+%            ~~~~2 & ~~~~\cancel{2}
+%        \end{matrix}\right) \\
+%        \left(\begin{matrix}
+%            ~~~~1 & ~~~~2\\
+%            ~~~~\cancel{0} & \cancel{1}
+%        \end{matrix}\right) &
+%        \left(\begin{matrix}
+%            ~~~~2 & ~~~~\cancel{2}\\
+%            ~~~~\cancel{1} & ~~~~\cancel{2}
+%        \end{matrix}\right)
+%    \end{matrix}\right)
+%\end{align}
+%
+%We can see these two subgraphs produce exactly the same compact tensor.
+%When we replace the original tensor with this gadget, the solution.
+
+\section{Benchmarks and case studies}
+\subsection{Performance benchmarks}
+We run a sequential program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results in Figure~\ref{fig:benchmark}.
+Tensor network contraction can be parallelized.
+When the element type is immutable, one can also run it on GPUs to speed up the computation.
+
 \begin{figure} 
@@
     \includegraphics[width=0.8\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{benchmark.pdf}
-    \caption{Benchmark results for computing different properties with different element types.
+    \caption{\red{label x-axis as ``number of vertices, $|V|$''} Benchmark results for computing different properties of independent sets with different tensor element types.
 The right axis is only for the dashed line.
-    }\label{fig:benchmark}
+    }\red{split into two graphs: one with time versus number of vertices, $|V|$, and one with time versus tree width.}
+    \red{We also need to show/say what types of graphs is used here for benchmarking.}
+    \label{fig:benchmark}
 \end{figure}
-Tensor network contraction is parallelizable. When the element type is immutable, one can just upload the data to GPU to enjoy the speed up.
-
-\section{Discussion}
-We introduced in the main text how to compute the independence polynomial, maximum independent set and optimal configurations,
-derived the backward rule for tropical tensor network to bound the search of solution space.
-%And, we also discussed how to use @tensor network to study the local properties of a graph.
-Although many of these properties are global,
-we can encode it to different tensor element types as commutative semirings.
-The power of tensor network's is not limited to the indenepent set problem, in \App{app:otherproblems} we show how to map matching problem and k-coloring to a tensor network.
+
+\subsection{Example case studies}
+\subsubsection{Hard-square constant}
+
+\subsubsection{Euler characteristics of independence complex}
+
+\subsubsection{Partition functions and finite-temperature phase transitions}
+
+\section{Discussion and conclusion}
+We have introduced a new approach based on tensor network contraction to compute the independence number, independence polynomial, maximal independence polynomial, and enumeration of MIS configurations.
+We derived the backward rule for tropical tensor network to bound the search of solution space.
+Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
+The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem and $k$-coloring problem to a tensor network.
 Here, we want to discuss more from the programming perspective.
-We show some of the Julia language~\cite{Bezanson2012} implementations in Appendix \ref{sec:technical}, you will find it being surprisingly short.
+We show some of the Julia language~\cite{Bezanson2012} implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
 What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
-The style that we program is called generic programming,
-meaning one can feed different data types into a same program, and the program will compute the result with a proper performance.
-In C++, users can use templates for such a purpose.
-We chose Julia because its just in time compiling is very powerful that it can generate fast code dynamically for users.
-Elements of fixed size, such as the finite field algebra, truncated polynomial, tropical number and tropical number with counting or configuration field used in the main text can be inlined in an array.
-Furthermore, these inlined arrays can be upload to GPU devices for faster generic matrix multiplication implemented in CUDA.jl~\cite{Besard2018}.
-
-\begin{table}[h!]\centering
-\begin{minipage}{0.9\columnwidth}
-\ra{1.3}
-    \scalebox{1.0}{
-        \begin{tabularx}{\textwidth}{bb}\toprule
-            \hline
-            \textbf{element type}     & \textbf{purpose} \\
-            {regular number}     & {counting all indenepent sets} \\
-            {tropical number} (\Eq{eq:countingtropical})    & {finding the maximum independent set size} \\
-            {tropical number with counting} (\Eq{eq:countingtropical})     & {finding both the maximum independent set size and its degeneracy} \\
-            {tropical number with configurations} (\Eq{eq:singleconfig})     & {finding the maximum independent set size and one of the optimal configurations} \\
-            {tropical number with sets} (\Eq{eq:set})    & {finding the maximum independent set size and all optimal configurations} \\
-            {polynomial} (\Eq{eq:polynomial})     & {computing the indenpendence polynomials exactly} \\
-            {truncated polynomial} (\Eq{eq:max2poly})     & {counting the suboptimal independent sets} \\
-            {complex number}     & {fitting the indenpendence polynomials with fast fourier transformation} \\
-            {finite field algebra} \Eq{eq:finitefield}    & {fitting the indenpendence polynomials exactly using number theory} \\
-            \bottomrule
-        \end{tabularx}
-    }
-    \caption{Tensor element types used in the main text and their purposes.}\label{tbl:generictypes}
-\end{minipage}
-\end{table}
-
-\section*{Acknowledgments}
-We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
-their questions are the driving force of this project.
-Thank Chris Elord for helping us writting the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
-\blue{funding information}
+The style that we program is called generic programming, meaning one can feed different data types into the same program, and the program will compute the result with a proper performance.
+In C++, one can use templates for such a purpose.
+We chose Julia because its just-in-time compiling is very powerful that it can generate fast code dynamically for users.
+Elements of fixed size, such as the finite-field algebra, truncated polynomial, tropical number and tropical number with counting or configuration field described in this paper can all be inlined in an array.
+Furthermore, these inlined arrays can be uploaded to GPU devices for faster computation with generic matrix multiplication implemented in CUDA.jl~\cite{Besard2018}.
 
@@
 
-In the above examples, the configuration enumeration is very slow, one should use the optimal MIS size for bounding as decribed in the main text.
+In the above examples, the configuration enumeration is very slow, one should use the optimal MIS size for bounding as described in the main text.
 We will not show any example about implementing the backward rule here because it has approximately 100 lines of code.
@@
 a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded tree width $k$ can be solved in linear time with respect to the graph size.
+Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded treewidth $k$ can be solved in linear time with respect to the graph size.
 Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
@@
 The cost is, the tensor network is less expressive than dynamic programming,
-\iffalse
-The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:wtensor} and \Eq{eq:btensor} can be expressed in MSO as
-\begin{align}
-    \begin{split}
-    \exists_X\forall_{u}&(\\
-    &\quad\forall_{v} 
-    \neg {\rm adj}(u, v) \lor
-    ({\rm adj}(u, v) \land ( \hspace{5em}\text{$\triangleright$ restrictions on edges}\\
-    &\quad\quad(u \not\in X \land v \not\in X \land B_{00}) \lor\\
-    &\quad\quad(u \not\in X \land v \in X \land B_{01}) \lor\\
-    &\quad\quad(u \in X \land v \not\in X \land B_{10}) \lor\\
-    &\quad\quad(u \in X \land v \in X \land B_{11})\\
-    &\quad)\\
-    &))\land\\
-    &(\hspace{16.5em}\text{$\triangleright$ restrictions on vertices}\\
-    &\quad(u \not\in X \land W_{0}) \lor\\
-    &\quad(u \in X \land W_{1})\\
-    &),
-    \end{split}
-\end{align}
-while not all monadic second order logic can be represented as a tensor network contraction,
-for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
-At the cost of losing expressiveness, we can encode the properties of the graph into the tensor elements.
-\fi
+%\iffalse
+%The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:tensor} can be expressed in MSO as
+%\begin{align}
+%    \begin{split}
+%    \exists_X\forall_{u}&(\\
+%    &\quad\forall_{v} 
+%    \neg {\rm adj}(u, v) \lor
+%    ({\rm adj}(u, v) \land ( \hspace{5em}\text{$\triangleright$ restrictions on edges}\\
+%    &\quad\quad(u \not\in X \land v \not\in X \land B_{00}) \lor\\
+%    &\quad\quad(u \not\in X \land v \in X \land B_{01}) \lor\\
+%    &\quad\quad(u \in X \land v \not\in X \land B_{10}) \lor\\
+%    &\quad\quad(u \in X \land v \in X \land B_{11})\\
+%    &\quad)\\
+%    &))\land\\
+%    &(\hspace{16.5em}\text{$\triangleright$ restrictions on vertices}\\
+%    &\quad(u \not\in X \land W_{0}) \lor\\
+%    &\quad(u \in X \land W_{1})\\
+%    &),
+%    \end{split}
+%\end{align}
+%while not all monadic second order logic can be represented as a tensor network contraction,
+%for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
+%At the cost of losing expressiveness, we can encode the properties of the graph into the tensor elements.
+%\fi
 However, that are still some other problems that can be expressed in the framework of generic tensor network.
@@
 A matching polynomial of a graph $G$ is defined as
-\begin{align}
+\begin{equation}
     M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
-\end{align}
+\end{equation}
 where $k$ is the number of matches, and coefficients $c_k$ are countings.
@@
 We define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
-\begin{align}
+\begin{equation}
     W_{v\rightarrow n_1, v\rightarrow n_2, \ldots, v\rightarrow n_{d(v)}} = \begin{cases}
         1, & \sum_{i=1}^{d(v)} v\rightarrow n_i \leq 1,\\
-        0, & otherwise,
+        0, & \text{otherwise},
     \end{cases}
-\end{align}
+\end{equation}
 and a tensor of rank $1$ on the bond
-\begin{align}
+\begin{equation}
     B_{v\rightarrow w} = \begin{cases}
@@
 \end{cases}
-\end{align}
+\end{equation}
 Here, we use bond index $v \rightarrow w$ to label tensors.
 
-\subsection{k-Colouring}
-Let us use 3-colouring on the vertex as an example. We can define a vertex tensor as
-\begin{align}
+\subsection{k-Coloring}
+Let us use 3-coloring on the vertex as an example. We can define a vertex tensor as
+\begin{equation}
     W = \left(\begin{matrix}
@@
     \end{matrix}\right),
-\end{align}
+\end{equation}
 and an edge tensor as
-\begin{align}
+\begin{equation}
     B = \left(\begin{matrix}
@@
     \end{matrix}\right).
-\end{align}
-The number of possible colouring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
-By designing generic types as tensor elements, one should be able to get all possible colourings.
-It is straight forward to define the k-colouring problem on edges hence we will not discuss the detailed construction here.
-
-\section{The fitting and Fourier transformation approaches to computing independence polynomial}\label{app:fft}
-Let $m=\alpha(G)$ be the maximum independent set size and $X$ be a set of real numbers of cardinality $m+1$.
-We compute the tensor network contraction for each $x_i \in X$ and obtain the following relations
-\begin{align}
-    \begin{split}
-a_0 + a_1 x_1 + a_1 x_1^2 + \ldots + a_m x_1^m &= y_0\\
-a_0 + a_1 x_2 + a_2 x_2^2 + \ldots + a_m x_2^m &= y_1\\
-\ldots&\\
-a_0 + a_1 x_m + a_2 x_m^2 + \ldots + a_m x_m^m& = y_m
-    \end{split}
-\end{align}
-The polynomial fitting between $X$ and $Y = \{y_0, y_1, \ldots, y_m\}$ gives us the factors.
-The polynomial fitting is essentially about solving the following linear equation
-\begin{align}
+\end{equation}
+The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+By designing generic types as tensor elements, one should be able to get all possible colorings.
+It is straight forward to define the k-coloring problem on edges hence we will not discuss the detailed construction here.
+
+\section{Discrete Fourier transform for computing the independence polynomial}\label{app:fft}
+
+In section~\ref{sec:indpoly}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq}.
+Since the coefficients of the independence polynomial can range many orders of magnitude, the round-off errors in fitting can be significant if we use random floating point numbers for $x_{i}$.
+In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent overflow and round-off errors.
+Here, we give another method based on discrete Fourier transform.
+Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
+The linear equation thus becomes
+\begin{equation}
 \left(\begin{matrix}
-1 & x_1 & x_1^2 & \ldots & x_1^m \\
-1 & x_2 & x_2^2 & \ldots & x_2^m \\
+1 & r & r^2 & \ldots & r^{\alpha(G)} \\
+1 & r\omega & r^2\omega^2 & \ldots & r^{\alpha(G)} \omega^{\alpha(G)} \\
 \vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_m & x_m^2 & \ldots & x_m^m
+1 & r\omega^{\alpha(G)} & r^2\omega^{2{\alpha(G)}} & \ldots & r^{\alpha(G)}\omega^{{\alpha(G)}^2}
 \end{matrix}\right)
 \left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
+a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
 \end{matrix}\right)
 = \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
-\end{matrix}\right).\label{eq:lineareq}
-\end{align}
-
-In practise, the fitting can suffer from the non-negligible round off errors of floating point operations and produce unreliable results.
-This is because the factors of independence polynomial can be different in magnitude by many orders.
-Instead of choosing $X$ as a set of random real numbers, we make it form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/(m+1)}$.
-The above linear equation becomes
-\begin{align}
-\left(\begin{matrix}
-1 & r\omega & r^2\omega^2 & \ldots & r^m\omega^m \\
-1 & r\omega^2 & r^2\omega^4 & \ldots & r^m\omega^{2m} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & r\omega^m & r^2\omega^{2m} & \ldots & r^m\omega^{m^2}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_m
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_m
+y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
 \end{matrix}\right).
-\end{align}
-
-Let us rearrange the factors $r^j$ to $a_j$, the matrix on left side is exactly the a discrete Fourier transformation (DFT) matrix.
-Then we can obtain the factors using the inverse Fourier transformation $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) and high independent set size region ($\omega>1$).
+\end{equation}
+
+Let us rearrange the coefficients $r^j$ to $a_j$, the matrix on the left side becomes the discrete Fourier transform matrix.
+Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
+By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) or high independent set size region ($\omega>1$). \red{is that $\omega < 1$ or $r <1$?}
 

### 2021-09-08 paper/paper.tex
acknowledge

--- 2021-09-04 paper/paper.tex
@@
 \section*{Acknowledgments}
+We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network, his code plays a crucial role in our code base.
 We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,

### 2021-09-08 paper/paper.tex
add example sections, data, and some Matlab scripts

--- 2021-09-07 paper/paper.tex
@@
 Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods; on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
 \end{abstract}
@@
 We benchmark our algorithms, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
-Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
+Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
 
@@
 \begin{table}[t!]\centering
-\begin{minipage}{0.9\columnwidth}
+\begin{minipage}{\columnwidth}
 \ra{1.3}
-    \scalebox{1.0}{
         \begin{tabularx}{\textwidth}{bb}\toprule
@@
         \end{tabularx}
-    }
     \caption{Tensor element types and their purposes in calculating various independent set properties.}\label{tbl:generictypes}
@@
 
-\subsection{Example case studies}
-\subsubsection{Hard-square constant}
+\subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
+In all the examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
+The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices; the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$.
+
+\begin{figure}[t] 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{lattices.pdf}
+    \caption{The types of graphs used in the benchmark and case studies.
+The lattice dimensions are $L\times L$.
+(a) Square grid graph denoted as SG.
+(b) Square grid graph with a filling factor $p=0.8$, denoted as SG(0.8).
+(c) King's graph denoted as K.
+(d) King's graph with a filling factor $p=0.8$, denoted as K(0.8).}
+    \label{fig:lattices}
+\end{figure}
+
+\subsubsection{Number of independent sets and hard-square entropy constant}
+The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
 
@@
 
+\section{Integer sequences formed by the number of independent sets}
+
+\begin{table}[h]
+\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.}
+\begin{center}
+\scalebox{0.9}{
+\begin{tabular}{|c| >{\centering\arraybackslash} p{0.95\linewidth}|}
+ \hline $L$  & square grid graphs \\
+ \hline $ 1$ & 2  \\
+ \hline $ 2$ & 7  \\
+ \hline $ 3$ & 63  \\
+ \hline $ 4$ & 1 234  \\
+ \hline $ 5$ & 55 447  \\
+ \hline $ 6$ & 5 598 861  \\
+ \hline $ 7$ & 1 280 128 950  \\
+ \hline $ 8$ & 660 647 962 955  \\
+ \hline $ 9$ & 770 548 397 261 707  \\
+ \hline $ 10$ & 2 030 049 051 145 980 050  \\
+ \hline $ 11$ & 12 083 401 651 433 651 945 979  \\
+ \hline $ 12$ & 162 481 813 349 792 588 536 582 997  \\
+ \hline $ 13$ & 4 935 961 285 224 791 538 367 780 371 090  \\
+ \hline $ 14$ & 338 752 110 195 939 290 445 247 645 371 206 783  \\
+ \hline $ 15$ & 52 521 741 712 869 136 440 040 654 451 875 316 861 275  \\
+ \hline $ 16$ &  18 396 766 424 410 124 752 958 806 046 933 947 217 821 482 942 \\
+ \hline $ 17$ &  14 557 601 701 834 111 295 974 187 104 248 827 765 798 599 152 358 303 \\
+ \hline $ 18$ &  26 024 585 612 650 837 861 658 126 921 792 857 026 992 497 268 285 945 167 621 \\
+ \hline $ 19$ &  105 105 055 066 577 962 012 604 229 608 317 915 229 737 651 637 019 975 757 755 051 314 \\
+ \hline $ 20$ &  958 979 036 662 929 619 406 859 624 886 958 746 851 620 546 557 485 230 898 539 651 354 907 499 \\
+ \hline $ 21$ &  19 766 982 580 727 525 559 447 459 703 066 410 506 378 295 841 376 040 664 015 562 851 325 369 819 076 327 \\
+ \hline $ 22$ &  920 486 427 724 231 647 653 646 535 134 255 190 048 558 085 587 696 509 535 085 179 014 710 020 739 303 637 413 062 \\
+ \hline $ 23$ & 96 836 737 362 332 577 228 126 233 146 266 027 907 220 602 904 916 569 863 928 397 932 638 147 313 462 817 836 132 159 477 643 \\
+ \hline $ 24$ & 23 014 876 830 102 973 080 295 375 510 481 185 265 791 418 130 718 634 637 816 237 986 620 978 856 344 595 418 898 906 840 911 239 867 869 \\
+ \hline $ 25$ & 12 357 280 628 458 621 610 261 003 683 798 282 889 567 362 022 871 449 310 490 079 744 330 288 088 293 888 381 458 751 196 205 785 114 467 063 479 978 \\
+ \hline $ 26$ & 14 989 353 830 657 887 045 253 535 577 369 170 604 561 059 504 403 111 230 207 533 142 521 161 755 543 754 839 412 836 401 335 298 693 619 461 437 872 472 165 615 \\
+ \hline $ 27$ &  41 076 048 814 756 904 170 038 431 958 637 474 710 328 322 517 168 428 037 124 975 797 939 221 729 929 250 098 889 601 666 346 169 376 778 430 801 983 574 787 538 529 309 191 \\
+ \hline $ 28$ &  254 296 368 874 677 123 746 928 211 898 730 495 474 495 246 876 690 760 159 507 126 754 738 599 026 016 292 991 448 162 576 157 292 681 301 528 315 863 006 160 203 433 527 765 235 617 478 \\
+ \hline $ 29$ & 3 556 619 491 488 838 337 298 644 336 171 591 528 960 687 731 348 622 394 588 805 214 244 031 766 315 339 709 627 465 589 460 212 852 431 000 227 410 783 701 037 177 097 019 793 172 369 009 198 594 591 \\
+ \hline $ 30$ &  112 377 766 778 527 126 203 646 648 402 050 958 984 330 252 199 994 469 198 044 986 979 798 657 215 652 532 005 142 877 926 040 203 499 014 641 860 333 039 219 325 350 361 465 468 647 055 420 204 598 509 312 491 705 \\
+  \hline
+\end{tabular}
+}
+\end{center}
+\label{tbl:squaregrid}
+\end{table}
+
+\begin{table}[h]
+\caption{The number of independent sets for King's graphs of size $L\times L$.}
+\begin{center}
+\begin{tabular}{|c| >{\centering\arraybackslash} p{0.85\linewidth}|}
+ \hline $L$  & King's graphs \\
+ \hline $ 1$ &   \\
+ \hline $ 2$ &   \\
+ \hline $ 3$ &   \\
+ \hline $ 4$ &   \\
+ \hline $ 5$ &   \\
+ \hline $ 6$ &   \\
+ \hline $ 7$ &   \\
+ \hline $ 8$ &   \\
+ \hline $ 9$ &   \\
+ \hline $ 10$ & 94 707 789 944 544 \\
+ \hline $ 11$ & 60 711 713 670 028 729  \\
+ \hline $ 12$ & 69 645 620 389 200 894 313  \\
+ \hline $ 13$ &  144 633 664 064 386 054 815 370 \\
+ \hline $ 14$ & 540 156 683 236 043 677 756 331 721  \\
+ \hline $ 15$ & 3 641 548 665 525 780 178 990 584 908 643  \\
+ \hline $ 16$ & 44 222 017 282 082 621 251 230 960 522 832 336 \\
+ \hline $ 17$ & 968 503 939 616 343 947 563 582 929 715 005 880 647 \\
+ \hline $ 18$ & 38 227 887 218 717 761 202 510 261 178 854 062 185 464 315 \\
+ \hline $ 19$ & 2 720 444 488 584 821 384 410 936 779 813 343 554 469 758 172 682 \\
+ \hline $ 20$ & 348 970 226 122 589 397 373 342 369 495 005 120 745 703 462 667 115 175 \\
+ \hline $ 21$ & 80 700 603 403 721 730 646 640 814 391 653 008 712 705 595 500 769 624 448 529 \\
+ \hline $ 22$ & 33 641 616 174 796 469 294 898 513 022 199 100 689 671 634 779 118 656 571 910 751 320 \\
+ \hline $ 23$ & 25 281 578 706 433 684 460 290 055 263 926 749 952 595 755 044 481 112 956 327 672 312 862 611  \\
+ \hline $ 24$ & 34 249 181 078 331 384 968 700 380 345 306 575 903 108 280 266 841 066 358 396 857 518 201 026 192 547 \\
+ \hline $ 25$ & 83 641 072 313 734 275 009 578 098 702 552 656 178 287 685 025 530 905 558 603 555 359 601 823 180 929 638 318  \\
+ \hline $ 26$ & 368 222 048 967 797 645 785 624 418 568 072 838 671 415 214 857 177 141 161 824 615 541 365 640 076 045 923 328 316 979  \\
+ \hline $ 27$ & 2 922 282 601 123 898 422 508 409 690 495 824 015 239 663 506 989 438 099 254 205 806 998 557 618 858 143 959 252 475 337 777 029  \\
+ \hline $ 28$ & 41 807 680 908 633 213 277 041 952 346 680 116 482 996 387 928 973 684 599 097 559 098 879 721 953 006 036 791 335 134 446 016 561 667 772 \\
+  \hline
+\end{tabular}
+\end{center}
+\label{tbl:squaregrid}
+\end{table}
+
 \end{document}

### 2021-09-08 paper/paper.tex
add generic programming

@@
 The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of the maximum independence set configurations.
-Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods; on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
+Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods;
+on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
@@
 \section{Introduction}
-\blue{efficient counting maximal independent sets~\cite{Manne2013}}
+\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}, treewidth of 3-regular graphs ~\cite{Fomin2006},
+branching algorithm~\cite{Tarjan1977,Robson1986}
+}
 In graph theory and combinatorics, there are many interesting but hard computational problems concerning properties of independent sets.
@@
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for the MIS requires time $O(2^{|V|})$.
-More efficient exact algorithms include the branching algorithms and dynamic programming.
-Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1893^n n ^{O(1)}$~\cite{Xiao2017} \red{reading the abstract, I think the algorithm is $1.1996^{|V|} {|V|}^{O(1)}$.
-The $1.1893^{|V|} {|V|}^{O(1)}$ scaling is for graphs with maximum degree 6}.
-Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$; these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-
-The independent set problem is closely related to the clique problem and the vertex cover problem~\cite{Moore2011}; more concretely, an MIS of a graph $G$ corresponds to a maximum clique in the complement graph of $G$, and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
-Together, these problems find a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication, map labelling, computer vision, etc.~\cite{Butenko2003Maximum, Wu2015review}.
-Besides the standard MIS problem, there are many other interesting problems pertaining to independent sets, such as the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of optimal and sub-optimal configurations.
-Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007Monte} in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready}; they can, for example, be used to understand phase transitions and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
+Naive exhaustive search for the MIS requires time $O(2^{|V|})$. More efficient exact algorithms include the branching algorithms and dynamic programming.
+Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^n n ^{O(1)}$~\cite{Xiao2017}.
+Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
+these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
+
+The independent set problem is closely related to the clique problem and the vertex cover problem~\cite{Moore2011};
+more concretely, an MIS of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
+and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
+Together, these problems find a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
+map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}.
+Besides the standard MIS problem, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
+independence polynomial, maximal independence polynomial, and enumeration of optimal and sub-optimal configurations.
+Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready};
+they can, for example, be used to understand phase transitions and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
 
@@
 We map different problems into generic tensor network contraction with various tensor element algebra.
-Our approach does not necessarily provide a better time complexity compared to dynamic programming, but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts.
+Our approach does not necessarily provide a better time complexity compared to dynamic programming,
+but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts.
 We benchmark our algorithms, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
-Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
-
-\section{Tensor networks}\red{I removed the superscript and subscript, since I think it's not necessary to introduce those.}
-A tensor network~\cite{Cirac2020Matrix, Orus2014} can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
+Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant,
+Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
+
+\section{Tensor networks}
+A tensor network~\cite{Cirac2020, Orus2014} can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
 Let $A, B$ be two matrices; the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
 Using the Einstein notation, we can write $C_{ik} = A_{ij}B_{jk}$, where $j$ is implicitly summed over.
-In the standard notation, each index can appear at most twice.
-A tensor network consists of multiple tensors performing the sum-product operation, i.e., contraction, and the tensor network can be represented as a multigraph with open edges by viewing a tensor as a vertex, a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
+In the standard notation, each index can appear at most twice. A tensor network consists of multiple tensors performing the sum-product operation,
+i.e., contraction, and the tensor network can be represented as a multigraph with open edges by viewing a tensor as a vertex,
+a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
 
@@
 One can generalize the tensor network notation by removing the restriction that each index can appear at most twice.
-The notation can be considered as a generalized Einstein notation, which is sometimes called einsum, sum-product network or factor graph~\cite{Bishop2006} in different contexts.
+The notation can be considered as a generalized Einstein notation, which is sometimes called einsum,
+sum-product network or factor graph~\cite{Bishop2006} in different contexts.
 The graphical representation of a tensor network we use in this paper is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
@@
 \begin{example}
-$C_{ijkl} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijkl} = \sum_{m}A_{jkm} B_{mil} V_{jm}$  \red{I've changed this.
-please check.
-The original was $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ and $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$}.
-Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$ 
+\red{I've changed this. please check. The original was $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ and $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$}.
+\blue{changed back because $l$ is not an open edge. Is it still confusing if I introduce open circles for open edges?}
+Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges and open circles to denote open edges.
 
@@
     \def\r{0.5cm}
+    \def\sr{0.15cm}
     \def\ax{0}
@@
     \node[color=white,fill=black,dot=\r] at (\cx+\dx,\cy) (v) {V};
+    \node[color=white,draw=black,dot=\sr] at (\ax-1,\by) (o1) {};
+    \node[color=white,draw=black,dot=\sr] at (\ax-1.5,\ay) (o2) {};
+    \node[color=white,draw=black,dot=\sr] at (\ax-1,\cy) (o3) {};
     \node at (\ax-0.8,\ay) (k) {k};
@@
     \node at (\bx-1,\by) (i) {i};
-    \draw[color=blue] (i) -- (b);
-    \draw[color=blue] (i) -- (\ax-1,\by);
+    \draw[color=blue,thick] (i) -- (b);
+    \draw[color=blue,thick] (i) -- (o1);
     \draw[color=cyan,thick] (l) -- (b);
     \draw[color=violet,thick] (k) -- (a);
-    \draw[color=violet,thick] (k) -- (\ax-1.5,\ay);
+    \draw[color=violet,thick] (k) -- (o2);
     \draw[color=black,thick] (b) -- (m);
@@
     \draw[color=red,thick] (v) -- (j);
-    \draw[color=red,thick] (\ax-1,\cy) -- (j);
+    \draw[color=red,thick] (o3) -- (j);
 \end{tikzpicture}}
@@
 
-In the spirit of generic programming, the elements of the tensors in the tensor network do not always need to be floating point numbers or integers.
-In fact, for the tensor network contraction to make sense, one only needs the tensor elements to form a commutative semiring.
+In previous works combining tensor network and combinatoric problems~\cite{},
+the elements in tensor networks are limited to regular number types such as floating point numbers and integers.
+As the development of modern compiling technology, we do not need to limit our imaginations to regular number types anymore.
+The key technology is called the generic programming:
+
+\begin{definition}[Generic programming]
+   Generic programming is an approach to programming that focuses on designing algorithms and data structures so that they work in the most general setting without loss of efficiency.
+~\cite{Stepanov2014}
+\end{definition}
+
+This definition of generic programming contains two major pieces, one is a single program for the general setting, and another is performance.
+To understand the first point, suppose we want to write a function to take the power of an element $f(x, n) := x^n$,
+the generic programming approach does not assume $x$ being a regular number,
+instead it treats $x$ as an element with an associative multiplication operation $\odot$ and multiplicative identity $\mymathbb{1}$.
+In such a way, when the program takes a matrix as input, it computes the matrix power without rewriting this function for matrices.
+The second point about performance basically rules out dynamic typed languages like Python,
+because in these languages, the efficiency of a generic type is not guaranteed.
+Imagine the speed of computing the matrix multiplication between two numpy arrays with python objects as elements.
+The generic programming that we want to discuss is those in static types languages like C++, and Julia~\cite{Bezanson2012}.
+C++ uses templates for generic programming while Julia has just in time compiling and multiple dispatch.
+When the program ``sees'' a new input type, the compiler recompiles the generic program for the new type.
+A lot optimization can be done during the compiling, like inlining immutable elements with fixed sizes in an array.
+In Julia, these inlined arrays can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
+
+This leads us to think about what is the most general element type that allowed in a tensor network contraction program.
+We find as long as the tensor elements form a commutative semiring, the tensor network contraction result can be contraction order independent.
 A semiring is a ring without additive inverse, while a commutative semiring is a semiring where the multiplication operation is commutative.
@@
 The requirement of being commutative is for the tensor contraction result to be independent of the contraction order, which could be relaxed in certain cases.
-In the following sections, we show how to compute the independence polynomial, the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+In the following sections, we show how to compute the independence polynomial,
+the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
 Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.
@@
             {tropical number with configurations} (\Eq{eq:singleconfig})     & {finding the independence number and one MIS} \\
-            {tropical number with sets} (\Eq{eq:set})    & {finding the independence number and enumeration of all MISs} \\
+            {tropical number with sets} (\Eq{eq:countingtropicalset})    & {finding the independence number and enumeration of all MISs} \\
             {polynomial} (\Eq{eq:polynomial})     & {computing the independence polynomial exactly} \\
@@
 \end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the independence number.
-The total number of independent sets is thus equal to $I(G, 1)$.
+where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the independence number. The total number of independent sets is thus equal to $I(G, 1)$.
 The problem of computing the independence polynomial belongs to the complexity class \#P-hard.
-One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
+One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}
+\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
 There are some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact methods to compute the independence polynomial.
@@
 The independence polynomial is closely related to the matching polynomial, the clique polynomial, and the vertex cover polynomial.
-In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{levit2005Independence}.
+In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{Levit2005}.
 Thus, our algorithm to compute the independence polynomial can also be used to compute the above graph polynomials.
-Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{levit2005Independence}.
+Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
 We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
@@
 \red{I removed the indices $s_{i}$ etc, on the right of the equations, since that looks confusing to me. If I understand correctly, $s_{i}, s_{j}$ just denotes the index of the vector/matrix.}
+\blue{To be consistent, we should also remove the index on the LHS. It is better not removing the label information.}
 \begin{equation}
@@
 In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
-The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size, and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise.
-In the implementation of the algorithm, we benefit from recent advances in tensor network contraction, where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a good heuristic order~\cite{Gray2021, Pan2021}.
+The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
+and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise.
+In the implementation of the algorithm, we benefit from recent advances in tensor network contraction,
+where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a good heuristic order~\cite{Gray2021, Pan2021}.
 A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
@@
 
-Before contracting the tensor network and evaluating the independence polynomial numerically, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from integers and floating point numbers to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+Before contracting the tensor network and evaluating the independence polynomial numerically, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from integers and floating point numbers to the additive identity,
+$\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
 The most natural approach is to treat the tensor elements as polynomials and evaluate the polynomial directly.
@@
 
-\subsection{Maximal independence polynomial} \red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} Instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017On}.
+\subsection{Maximal independence polynomial}
+\red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} 
+Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
+In this paper, the word ``maximal'' is different with the ``maximum'' discussed the previous discussion in such a way that it is not necessarily refer to the gloal optimum.
+Instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017}.
  Concretely, it is defined as
@@
 Obviously, $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012On, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012On}.
+$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
 For the problem of finding the MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
-The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017On}.
+The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
 
@@
 \end{equation}
-Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$, and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t.
-$s_{i} = 1$, then $v$ cannot be in $I_{m}$.
+Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$,
+and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t. $s_{i} = 1$, then $v$ cannot be in $I_{m}$.
 As an example, for a vertex of degree 2, the resulting rank-3 tensor is
@@
 The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
-However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973Algorithm}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
 
@@
 In the previous section, we focused on computing the independence polynomial for a graph $G$ of given independence number $\alpha(G)$, but we did not show how to compute this number.
-The method we use to compute this quantity is based on the following observations.
-Let $x=\infty$, the independence polynomial becomes
+The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
 \begin{equation}
@@
 We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with $a(k) = (a_{k}, k)$, where the second element stores the largest exponent $k$ and the first element stores the corresponding coefficient $a_{k}$.
-From this, we can define a new algebra as \red{I've changed this, but I don't have strong feelings about this.
-We can certainly consider changing back.
+From this, we can define a new algebra as \red{I've changed this, but I don't have strong feelings about this. We can certainly consider changing back.
 I thought this would be more consistent with the earlier notations and show how it's stored in the program as well.}
@@
 \subsection{Enumeration of MIS configurations}
-The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973Algorithm, Eppstein2010Listing, Johnson1988On}, including, for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
-The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973Algorithm}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
+The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973, Eppstein2010, Johnson1988}, including,
+for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
+The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
 Here, we adapt the tensor element types for different enumeration problems.
@@
 I can't seem to find online what you call Hadamard.
-Is there a definition somewhere?} \red{it would be useful to give an example of the operations above, $s = ...
-, t = ..., s \oplus t = ..., s \odot t = ...$.} \red{do we need to define $ \{\} \lor^\circ \sigma  = \sigma \lor^\circ \{\} = \{\}$?} The variable $x_{i}$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
+Is there a definition somewhere?}
+\red{it would be useful to give an example of the operations above, $s = ...
+, t = ..., s \oplus t = ..., s \odot t = ...$.} \red{do we need to define $ \{\} \lor^\circ \sigma  = \sigma \lor^\circ \{\} = \{\}$?}
+The variable $x_{i}$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
 The vertex and edge tensors are thus
@@
     \mymathbb{0} &= (\{ \}, -\infty)\\
-    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropical}
+    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropicalset}
 \end{split}
@@
 \end{equation}
-where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking one with a larger integer value.
-In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
+where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking one with a smaller integer value.
+%In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
 
@@
 \end{align*}
-}
+}\blue{I think picking the smaller one would solve the issue.}
 
@@
 \subsection{Bounding the MIS enumeration space}
-When we use the algebra in \Eq{eq:countingtropical} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
+When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
 To speed up the computation and reduce space overhead, we use $\alpha(G)$ to bound the searching space.
@@
 Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
-Finally, we perform masked matrix multiplication using the new element type with the above algebra, \Eq{eq:countingtropical}, for obtaining all configurations.
+Finally, we perform masked matrix multiplication using the new element type with the above algebra, \Eq{eq:countingtropicalset}, for obtaining all configurations.
 Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagation of the gradients.
-To derive the back-propagation rule for tensor contraction, we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
+To derive the back-propagation rule for tensor contraction,
+we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
 Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
@@
 \end{equation}
-where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers). The inequality still holds if we take the minimum over $k$: 
-\begin{equation}
-    \begin{split}
-    A_{ij} &\leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
-    \end{split}
+where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers).
+The inequality still holds if we take the minimum over $k$: 
+\begin{equation}
+    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
 \end{equation}
@@
 \blue{maybe add an appendix?} \red{I've edited this section a bit, and I think it's okay now - probably don't need an appendix.}  % my blog
-%
-%\section{Tropical tensors for automated branching}\blue{$?$}
-%% check http://www.tcs.rwth-aachen.de/independentset/ for more rules
-%Branching rules can be automatically discovered by contracting the tensor network on a subgraph $R \subseteq G$ with tropical numbers as its element type.
-%Let $C$ be the set of boundary vertices defined as $C := \{u | u\in R \land (\exists v \in (G\backslash R) \land {\rm adj}(u, v))\}$, then the rank of the resulting tensor $A$ is $|C|$.
-%Here, we use ${\rm adj}(u, v)$ to denote two vertices $u$ and $v$ are adjacent to each other.
-%Each tensor entry $A_{\sigma}$ is a local maximum independent set size for the fixed boundary configuration $\sigma \in \{0,1\}^{|C|}$.
-%Suppose our goal is to find the maximum independent set size,
-%then this tensor can be further ``compactified'' by removing some entries.
-%To determine which entry can be removed, let us define a relation of \textit{less restrictive} as
-%\begin{align}
-%(\sigma_a \prec \sigma_b) := (\sigma_a \neq \sigma_b) \land (\sigma_a \leq^\circ \sigma_b)
-%\end{align}
-%where $\leq^\circ$ is the Hadamard less or equal to operation.
-%
-%\begin{definition}
-%A tensors $A$ is \textit{MIS-compact} if
-%\begin{align}
-%\forall{\sigma_b}\neg \exists{\sigma_a}(\sigma_a \prec \sigma_b) \land (A_{\sigma_a} \geq A_{\sigma_b})\label{eq:compactifying}.
-%\end{align}
-%\end{definition}
-%
-%If we remove such $A_{\sigma_b}$, the contraction over the whole graph is guaranteed to give the same maximum independent set size.
-%It can be seen by considering two entries with the same local maximum independent set sizes and different boundary configurations as shown in \Fig{fig:compactifying} (a) and (b).
-%If we have $\sigma_b \cup \overline{\sigma_b}$ being one of the solutions for maximum independent sets in $G$, then $\sigma_a \cup \overline{\sigma_b}$ is another solution giving the same $\alpha(G)$.
-%Hence, we can remove entry $A_{\sigma_b}$ safely.
-%%among boundary configurations with equal local maximum independent sizes,
-%%we only retain those least restrictive (less ones at the boundary) to exterial configurations.
-%
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=0.8\textwidth, trim={5cm 4cm 5cm 4cm}, clip]{compressionrule.pdf}
-%    \caption{Two configurations with the same local independent size $A_{\sigma_a} = A_{\sigma_b} = 3$ and different boundary configurations (a) $\sigma_a=\{001\}$ and (b) $\sigma_b = \{101\}$, where black nodes are $1$s (in the independent set) and white nodes are $0$s (not in the independent set).}\label{fig:compactifying}
-%\end{figure}
-%
-%\begin{theorem}
-%    A MIS-compact tropical tensor can not be further reduce without gloal information, i.e. any of its non-zero entries can produce the only global optimal solution given a proper environment.
-%\end{theorem}
-%
-%\begin{proof}
-%    %Given $A_\{\sigma_a}$ is better than $A_\{\sigma_b\}$, any exterior configuration $\overline{\sigma}$ making $\overline{\sigma} \cup \sigma_b$ a global maximum independent set also makes $\overline{\sigma} \cup \sigma_a$ a maximum independent set.
-%    Let us prove it by showing for any $\sigma$ in a MIS-compact tropical tensor of a subgraph $R$, there exists a parent graph $G$ that $R\subseteq G$ and $\sigma$ is the boundary configuration that gives the only maximum independent set.
-%    Let $A$ be a tropical tensor, and an entry of it being $A_{\sigma}$, where $\sigma$ is the boundary configuration.
-%    Let us construct a graph $G$ such that for a vertex $v \in C$, if $\sigma_v=1$, we connect it with two vertices $u, w \in G \backslash R$ that ${\rm adj}(v, u) \land {\rm adj}(u, w) \land \neg{\rm adj}(v, w)$.
-Otherwise, we attach infinite many disconnected neighbors to $v$.
-%
-%    \centerline{\includegraphics[width=0.35\textwidth, trim={0cm 2cm 5cm 0cm}, clip]{proofoptimal.pdf}}
-%    Then we have the maximum independent set size $\alpha(G,\sigma) = A_{\sigma} + \infty (|C|-\sum_{v=1}^{|C|}\sigma_v) + \sum_{v=1}^{|C|} 1-\sigma_v$.
-%    Let us assume there exists another configuration $\tau$ that generating the same or better maximum independent set size $\alpha(G, \tau) \geq \alpha(G, \sigma)$.
-%    Then we have $\tau \prec \sigma$, otherwise it will loss infinite contribution from the environment.
-%    For such a $\tau$, we have $A_\tau < A_\sigma$, otherwise $A_\sigma \prec A_\tau$ contradicts with $A$ being MIS-compact.
-%    Finally, we have $\alpha(G,\tau) = \infty (|C|-|\sigma|) + A_{\tau} + \sum_{v=1}^{|C|} 1-\sigma_v < \alpha(G,\sigma)$, hence $\sigma$ is the only boundary configuration that gives the maximum independent set for this graph.
-%\end{proof}
-%
-%\subsection{The tensor network compactification detects branching rules automatically}
-%Almost all branching rules are based on the same idea of analysing a local subgraph induced by a vertex $v$
-%by including its neighbourhoods,
-%and keep only the configurations that has the potential to produce the only maximum independent set.
-%Since an MIS-compact tensor is optimal, by analysing the correlation of vertex configurations on the resulting tensor for the $k$-th neighbourhood $N^k[v]$, one can discover the optimal branching vector automatically.
-%In the following, we are going to introduce several important rules for branching in the literature and show how it is connected to our tensor formulation.
-%
-%\begin{corollary}\label{rule:one} % basic
-%  If a vertex $v$ is in an independent set $I$, then none of its Neighbors can be in $I$.
-%On the other hand, if $I$ is a maximum (and thus maximal) independent set,
-%and thus if $v$ is not in $I$ then at least one of its Neighbors is in $I$.
-%\end{corollary}
-%
-%Contract $N[v]$ and the resulting tensor $A$ has a rank $|N(v)|$.
-Each tensor entry $A_{\sigma}$ corresponds to a locally maximized independent set size with fixed boundary configuration $\sigma \in \{0, 1\}^{|N(v)|}$.
-%If the boundary configuration is a bit string of 0s, $\sigma_v$ will takes value $1$ to maximize the local independent set size.
-%
-%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/basic.pdf}}
-%
-%After contracting $N[v]$, $v$ becomes an internal degree of freedom.
-%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
-%
-%\begin{align}
-%    T_{juwk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        ~~~~1 & -\infty \\
-%        -\infty & ~~~~2
-%        \end{matrix}\right)_{ju}&
-%        \left(\begin{matrix}
-%        -\infty & ~~~~2 \\
-%        ~~~~2 & ~~~~3
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        -\infty & ~~~~2 \\
-%        ~~~~2 & ~~~~3
-%        \end{matrix}\right)_{ju} &
-%        \left(\begin{matrix}
-%        ~~~~2 & ~~~~3 \\
-%        ~~~~3 & ~~~~4
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{wk},
-%\end{align}
-%where we use ``-'' to denote an entry is forbidden.
-%If we use sets for counting, one can check all configurations too. The resulting polynomial tensor is
-%\begin{align}
-%    P_{juwk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        1+x_v & - \\
-%        - & ~~x_jx_u
-%        \end{matrix}\right)_{ju}&
-%        \left(\begin{matrix}
-%        - & x_ux_k \\
-%        ~~~~x_jx_k & ~~~~x_ux_jx_k
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        - & x_wx_u \\
-%        x_wx_j & x_wx_jx_u
-%        \end{matrix}\right)_{ju} &
-%        \left(\begin{matrix}
-%        x_wx_k & x_wx_kx_u \\
-%        x_wx_kx_j & x_jx_ux_wx_k
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{wk}.
-%\end{align}
-%
-%By studying the correlation between vertex variables, one can easily see $x_v$ does not co-exist with other vertex variables.
-%These anti-correlation determines possible branching vectors in the maximum independent set problem.
-%It is easier to see if we list the set of optimal solutions as
-%\begin{align}
-%    \begin{split}
-%    S_{juwkv} = \{&00001, 10001, 01010, 10010, 11010, 10100,\\&01100, 11100, 00110, 01110, 10110, 11110\}.
-%    \end{split}
-%\end{align}
-%%If we denote the effective branching number of contracting the local degrees of freedoms as $\left|\{A_{\sigma} \neq \mymathbb{0}\right|\sigma \in \{0, 1\}^{|C|}\}|/2^{|R|}$.
-%%The effective branching value is $11^{1/5} \approx 1.6154$, which is larger than the branching number $\tau(1, 5) \approx 1.3247$.
-%%It does not mean the tropical tensor does not find all the branches, if we contract $N^2[v]$.
-%The branching vector $(1,5)$ gives a branching number $\tau(1, 5) \approx 1.3247$
-%
-%\begin{corollary}[mirror rule] % 2.7
-%For some $v \in V$, a node $u \in N^2(v)$ is called mirror of $v$, if $N(v) \backslash N(u)$ is a clique. We denote the set of of a node $v$ mirrors~\cite{Fomin2013} by $M(v)$.
-%Let $G = (V, E)$ be a graph and $v$ a vertex of $G$. Then
-%\begin{equation}
-%\alpha(G) = \max(1 + \alpha(G \backslash N[v]), \alpha(G \backslash (M(v) \cup \{v\})).
-%\end{equation}
-%\end{corollary}
-%
-%This rule states that if $v$ is not in $M$, there exists an MIS $I$ that $M(v)\notin I$.
-%otherwise, there must be one of $N(v)$ in the MIS (\textit{local maximum rule}).
-%Although this statement involves $N(u)$, however, deriving this rule only requires information upto second neighbourhood of $v$.
-%If $w$ is in $I$, then none of $N(v) \cap N(w)$ is in $I$, then there must be one of node in the clique $N(v)\backslash N(w)$ in $I$ (\textit{local maximum rule}),
-%since clique has at most one node in the MIS, by moving the occupied node to the interior, we obtain a ``better'' solution.
-%%Hence, the \textit{least restrictive principle} captures the mirror rule.
-%In the following example, since $u\in N^2(v)$ and $N(v) \backslash N(u)$ is a clique, $u$ is a mirror of $v$.
-%
-%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/mirror.pdf}}
-%
-%After contracting $N[v]\cup u$, $v$ becomes an internal degree of freedom.
-%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 4 tropical tensor is
-%
-%\begin{align}
-%    T_{juwk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        ~~~~1 & ~~~~2 \\
-%        ~~~~\cancel{1} & ~~~~\cancel{2}
-%        \end{matrix}\right)_{ju}&
-%        \left(\begin{matrix}
-%        ~~~~\cancel{1} & -\infty \\
-%        ~~~~2 & -\infty
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        ~~~~\cancel{1} & ~~~~\cancel{2} \\
-%        -\infty & -\infty
-%        \end{matrix}\right)_{ju} &
-%        \left(\begin{matrix}
-%        -\infty & -\infty \\
-%        -\infty & -\infty
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{wk},
-%\end{align}
-%where entries stroked through are removed by compactification. The corresponding polynomial tensor is
-%
-%\begin{align}
-%    P_{juwk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        1+x_v & x_u+x_ux_v \\
-%        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{}\\
-%        \end{matrix}\right)_{ju}&
-%        \left(\begin{matrix}
-%        ~~~~\cancel{} & - \\
-%        x_jx_k & -
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        ~~~~~~~\cancel{} & ~~~~~~~~~~~~~\cancel{} \\
-%        ~~~~~~~- & ~~~~~~~~~~~~~-
-%        \end{matrix}\right)_{ju} &
-%        \left(\begin{matrix}
-%        ~~~~- & - \\
-%        ~~~~- & -
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{wk}.
-%\end{align}
-%One can see $w$, as a mirror of $v$ does not appear in the maximum independent set after compactification.
-%
-%%In this case, the effective branching number is $3^{1/5}\approx 1.2457$,
-%%which is smaller than the branching number $\tau(4, 2) = 1.2721$ by simply applying the mirror rule.
-%\begin{align}
-%    \begin{split}
-%    S_{juwkv} = \{&00001, 01001, 10010\}.
-%    \end{split}
-%\end{align}
-%
-%\begin{corollary}[satellite rule] % satellite rule
-%Let $G$ be a graph, $v \in V$. A node $u \in N^2(v)$ is called satellite~\cite{Kneis2009} of $v$, if there is some $u' \in N(v)$ such that $N[u'] \backslash N[v] = \{u\}$.
-%The set of satellites of a node $v$ is denoted by $S(v)$, and we also use the notation $S[v] := S(v) \cup {v}$. Then 
-%\begin{equation}
-%\alpha(G) = \max\{\alpha(G \backslash \{v\}), \alpha(G \backslash N[S[v]]) + |S(v)| + 1\}.
-%\end{equation}
-%\end{corollary}
-%
-%This rule can be capture by contracting $N[v] \cup S(v)$.
-%In the following example, since $u \in N^2(v)$ and $w \in N(v)$ satisfies $N[w] \backslash N[v] = \{u\}$, $u$ is a satellite of $v$.
-%
-%\centerline{\includegraphics[width=0.4\columnwidth,trim={0 3.5cm 0 1cm},clip]{../notebooks/satellite.pdf}}
-%
-%After contracting $N[v] \cup u$, both $v$ and $w$ become internal degrees of freedoms.
-%Applying tensor compactification rule \Eq{eq:compactifying}, the resulting rank 3 polynomial tensor is
-%\iffalse
-%\begin{align}
-%    T_{juk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        ~~~~1 & ~~~~2 \\
-%        ~~~~2 & ~~~~\cancel{2}
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        ~~~~\cancel{1} & -\infty \\
-%        ~~~~\cancel{2} & -\infty
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{k}.
-%\end{align}
-%\fi
-%
-%\begin{align}
-%    P_{juk} = \left(\begin{matrix}
-%        \left(\begin{matrix}
-%        1+x_w+x_v & x_u + x_ux_v \\
-%        x_j+x_wx_j & ~~~~~~~~~~~~\cancel{}
-%        \end{matrix}\right)_{ju}\\
-%        \left(\begin{matrix}
-%        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~- \\
-%        ~~~~~~~~~~~~~~~~\cancel{} & ~~~~~~~~~~~~~~~-
-%        \end{matrix}\right)_{ju}
-%    \end{matrix}\right)_{k}.
-%\end{align}
-%
-%By choosing one of the optimal configurations in each entry,
-%we can see the satellite rule of either ${v, u} \in I$ or $v \notin I$ is satisfied.
-%
-%\begin{align}
-%    \begin{split}
-%    S_{juwkv} = \{&\{00100,00001\}, 10100, 01001\}.
-%    \end{split}
-%\end{align}
-%%In this case, the effective branching number is $3^{1/5}\approx 1.2457$. 
-%
-%%We can use the conditional entropy to discover branching rules automatically. 
-%%Let us take one best configuration a time from each entry of the compact polynomial matrix,
-%%and denote the resulting configuration set as $S$.
-%%The conditional entropy matrix here can be defined as
-%%\begin{align}
-%%    C_{uv} = H(s_u|s_v)
-%%\end{align}
-%%when two variables are strongly correlated to each other, the corresponding entry should be zero.
-%
-%\subsection{gadget design}\blue{$\times$}
-%
-%Suppose we have a local structure as the following.
-%
-%\centerline{\begin{tikzpicture}[scale=1.0]
-%    \def\r{0.2}
-%    \foreach \x/\y [count=\i] in {0.17/0.5,0.83/0.5,0.5/0.67,0.5/0.33}
-%        \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-%    \draw (1) -- (2);
-%    \draw (3) -- (4);
-%\end{tikzpicture}}
-%
-%
-%Contract this local structure gives the tropical tensor
-%
-%\begin{align}
-%    \left(\begin{matrix}
-%        \left(\begin{matrix}
-%            ~~~~0 & ~~~~1\\
-%            ~~~~1 & ~~~~2
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~1 & -\infty\\
-%            ~~~~2 & -\infty
-%        \end{matrix}\right) \\
-%        \left(\begin{matrix}
-%            ~~~~1 & ~~~~2\\
-%            -\infty & -\infty
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~2 & -\infty\\
-%            -\infty & -\infty
-%        \end{matrix}\right)
-%    \end{matrix}\right).
-%\end{align}
-%
-%The following gadget is equivalent to the above diagram up to a constant $2$.
-%
-%\centerline{\begin{tikzpicture}
-%    \def\nodes{(0.5, 0.33), (0.17, 0.5), (0.5, 0.67), (0.83, 0.5), (0.32, 0.44), (0.44, 0.44), (0.56, 0.44), (0.68, 0.44), (0.32, 0.56), (0.44, 0.56), (0.56, 0.56), (0.68, 0.56)}
-%    \def\edges{(1, 5), (1, 6), (1, 7), (1, 8), (2, 5), (2, 9), (3, 9), (3, 10), (3, 11), (3, 12), (4, 8), (4, 12), (5, 6), (5, 9), (5, 10), (6, 7), (6, 9), (6, 10), (6, 11), (7, 8), (7, 10), (7, 11), (7, 12), (8, 11), (8, 12), (9, 10), (10, 11), (11, 12)}
-%    \def\r{0.2}
-%    \foreach \p [count=\i] in \nodes{
-%        \parsept{\x}{\y}{\p}
-%        \pgfmathparse{((\x<0.2 || \x>0.8 || \y<0.35 || \y>0.65) ? 1 : 0)}
-%        \ifnum\pgfmathresult>0
-%            \node[fill=red,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-%        \else
-%            \node[fill,circle,radius=\r] at (\x*8, \y*8) (\i) {};
-%        \fi
-%    }
-%    \foreach \e [count=\i] in \edges{
-%        \parsept{\x}{\y}{\e}
-%        \draw (\x) -- (\y);
-%    }
-%\end{tikzpicture}}
-%
-%\begin{align}
-%    \left(\begin{matrix}
-%        \left(\begin{matrix}
-%            ~~~~2 & ~~~~3\\
-%            ~~~~3 & ~~~~4
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~3 & ~~~~3\\
-%            ~~~~4 & ~~~~4
-%        \end{matrix}\right) \\
-%        \left(\begin{matrix}
-%            ~~~~3 & ~~~~4\\
-%            ~~~~2 & ~~~~3
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~4 & ~~~~4\\
-%            ~~~~3 & ~~~~4
-%        \end{matrix}\right)
-%    \end{matrix}\right)
-%    \xrightarrow[\text{compactify, -2}]{}
-%    \left(\begin{matrix}
-%        \left(\begin{matrix}
-%            ~~~~0 & ~~~~1\\
-%            ~~~~1 & ~~~~2
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~1 & ~~~~\cancel{1}\\
-%            ~~~~2 & ~~~~\cancel{2}
-%        \end{matrix}\right) \\
-%        \left(\begin{matrix}
-%            ~~~~1 & ~~~~2\\
-%            ~~~~\cancel{0} & \cancel{1}
-%        \end{matrix}\right) &
-%        \left(\begin{matrix}
-%            ~~~~2 & ~~~~\cancel{2}\\
-%            ~~~~\cancel{1} & ~~~~\cancel{2}
-%        \end{matrix}\right)
-%    \end{matrix}\right)
-%\end{align}
-%
-%We can see these two subgraphs produce exactly the same compact tensor.
-%When we replace the original tensor with this gadget, the solution.
 
@@
 We run a sequential program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results in Figure~\ref{fig:benchmark}.
-Tensor network contraction can be parallelized.
-When the element type is immutable, one can also run it on GPUs to speed up the computation.
+Tensor network contraction can be parallelized. When the element type is immutable, one can also run it on GPUs to speed up the computation.
 
@@
 In all the examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
-The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices; the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$.
+The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices;
+the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$.
 
@@
     \caption{The types of graphs used in the benchmark and case studies.
-The lattice dimensions are $L\times L$.
-(a) Square grid graph denoted as SG.
-(b) Square grid graph with a filling factor $p=0.8$, denoted as SG(0.8).
-(c) King's graph denoted as K.
-(d) King's graph with a filling factor $p=0.8$, denoted as K(0.8).}
+    The lattice dimensions are $L\times L$. (a) Square grid graph denoted as SG. (b) Square grid graph with a filling factor $p=0.8$, denoted as SG(0.8).
+    (c) King's graph denoted as K. (d) King's graph with a filling factor $p=0.8$, denoted as K(0.8).}
     \label{fig:lattices}
@@
 What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
-The style that we program is called generic programming, meaning one can feed different data types into the same program, and the program will compute the result with a proper performance.
+The style that we program is called generic programming,
+meaning one can feed different data types into the same program, and the program will compute the result with a proper performance.
 In C++, one can use templates for such a purpose.
@@
 Furthermore, these inlined arrays can be uploaded to GPU devices for faster computation with generic matrix multiplication implemented in CUDA.jl~\cite{Besard2018}.
+
+\section*{Acknowledgments}
+We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network, his code plays a crucial role in our code base.
+We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
+their questions are the driving force of this project.
+Thank Chris Elord for helping us writing the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
+\blue{funding information}
 
@@
 
-\section{Why not introducing $\delta$ tensors}\label{app:tensorbad}
+\section{Why not introducing \texorpdfstring{$\delta$} tensors}\label{app:tensorbad}
 
@@
             \xdefinecolor{MyColor}{RGB}{\R,\G,\B}
-            %\filldraw [red, opacity=0.3] plot [smooth cycle] coordinates {(\x-\L,\y+\l) (\x-\l*2.5,\y+\l) (\x-\L*0.75,\y+\L*0.6) (\x-\L*0.6,\y+\L*0.75) (\x-\l,\y+\l*2.5) (\x-\l, \y+\L) (\x+\l,\y+\L) (\x+\l,\y+\l*2.5) (\x+\L*0.6,\y+\L*0.75) (\x+\L*0.75,\y+\L*0.6) (\x+\l*2.5,\y+\l) (\x+\L,\y+\l) (\x+\L,\y-\l) (\x+\l,\y-\l) (\x+\l,\y-\L) (\x-\l,\y-\L) (\x-\l,\y-\l) (\x-\L,\y-\l)};
             \ifnum \x < 5
@@
 \end{equation}
-where $k$ is the number of matches, and coefficients $c_k$ are countings.
+where $k$ is the number of matches, and coefficients $c_k$ are the corresponding counting.
 
@@
 Since the coefficients of the independence polynomial can range many orders of magnitude, the round-off errors in fitting can be significant if we use random floating point numbers for $x_{i}$.
-In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent overflow and round-off errors.
-Here, we give another method based on discrete Fourier transform.
+In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent overflow and round-off errors. Here, we give another method based on discrete Fourier transform.
 Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
@@
  \hline $L$  & King's graphs \\
- \hline $ 1$ &   \\
- \hline $ 2$ &   \\
- \hline $ 3$ &   \\
- \hline $ 4$ &   \\
- \hline $ 5$ &   \\
- \hline $ 6$ &   \\
- \hline $ 7$ &   \\
- \hline $ 8$ &   \\
- \hline $ 9$ &   \\
+ \hline $ 1$ & 2  \\
+ \hline $ 2$ & 5  \\
+ \hline $ 3$ & 35  \\
+ \hline $ 4$ & 314 \\
+ \hline $ 5$ & 6 427 \\
+ \hline $ 6$ & 202 841 \\
+ \hline $ 7$ & 12 727 570  \\
+ \hline $ 8$ & 1 355 115 601 \\
+ \hline $ 9$ & 269 718 819 131 \\
  \hline $ 10$ & 94 707 789 944 544 \\
@@
 \end{center}
-\label{tbl:squaregrid}
+\label{tbl:kingsgrid}
 \end{table}

### 2021-09-08 paper/paper.tex
address comments

@@
 I think it doesn't need to be long.
-Jinguo, could you write one or two paragraphs introducing generic programming?}
-
-\red{Generic programming is ...}
-\red{dispatch to different types etc. ...}
-
-In previous works combining tensor network and combinatoric problems~\cite{},
+Jinguo, could you write one or two paragraphs introducing generic programming?}\blue{I wrote a draft here, does it look ok in general?}
+In previous works combining tensor network and combinatoric problems~\cite{Kourtis2019,Biamonte2017},
 the elements in tensor networks are limited to regular number types such as floating point numbers and integers.
 As the development of modern compiling technology, we do not need to limit our imaginations to regular number types anymore.
-The key technology is called the generic programming:
+The key technology playing the role is called the generic programming:
 
@@
 
-This definition of generic programming contains two major pieces, one is a single program for the general setting, and another is performance.
-To understand the first point, suppose we want to write a function to take the power of an element $f(x, n) := x^n$,
-the generic programming approach does not assume $x$ being a regular number,
+This definition of generic programming contains two major pieces, one is a single program for the general setting, and another is about efficiency.
+To understand the first point, suppose we want to write a function to take the power of an element $f(x, n) := x^n$.
+One can easily write a function for regular numbers that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
+A generic programmer does not assume $x$ being a regular number type,
 instead it treats $x$ as an element with an associative multiplication operation $\odot$ and multiplicative identity $\mymathbb{1}$.
-In such a way, when the program takes a matrix as input, it computes the matrix power without rewriting this function for matrices.
-The second point about performance basically rules out dynamic typed languages like Python,
-because in these languages, the efficiency of a generic type is not guaranteed.
+In such a way, when the program takes a matrix as input, it computes the matrix power without extra efforts.
+The second point about performance. For dynamic typed languages like Python,
+one can easily write very general codes, however, the efficiency is not guaranteed.
 Imagine the speed of computing the matrix multiplication between two numpy arrays with python objects as elements.
@@
 C++ uses templates for generic programming while Julia has just in time compiling and multiple dispatch.
-When the program ``sees'' a new input type, the compiler recompiles the generic program for the new type.
-A lot optimization can be done during the compiling, like inlining immutable elements with fixed sizes in an array.
+When they ``sees'' a new input type, the compiler recompiles the generic program for the new type.
+A lot optimization can be done during the compiling, like inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
 In Julia, these inlined arrays can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
@@
 This leads us to think about what is the most general element type that allowed in a tensor network contraction program.
-We find as long as the tensor elements form a commutative semiring, the tensor network contraction result can be contraction order independent.
+Our finding is: as long as the tensor elements form a commutative semiring, the tensor network contraction result can be contraction order independent.
+So what is a commutative semiring?
 A semiring is a ring without additive inverse, while a commutative semiring is a semiring where the multiplication operation is commutative.
@@
 In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge, and an edge is mapped to an edge tensor.
-\red{a vertex is mapped to a hyperedge?}
+\red{a vertex is mapped to a hyperedge?}\blue{$\checkmark$}
 
@@
     a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, a_{2}b_{0} + a_{1}b_{1} + a_{0}b_{2},  \ldots, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (), \text{\red{should this be (0)?}} \\
+    \mymathbb{0} &= (), \text{\red{should this be (0)?}}\blue{\text{both are ok}} \\
     \mymathbb{1} &= (1).\label{eq:polynomial}
@@
 With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-In the algorithm, except the computation using the Chinese remainder theorem, all computations are done with integers of fixed width $W$.
+This is an iterative algorithm that tries different prime numbers $p$ until convergence.
+In each iteration, we contract tensor networks to evaluate the polynomial for each $x\in X$ on the finite field algebra ${\rm GF}(p)$.
+Let use denote the results as $Y$, then we solve a linear equation $Y = \hat X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient moduluses $A_p \equiv A \pmod p$.
+Finally we apply the Chinese remainder theorem to get $A \pmod P$, where $P$ is a product of all prime numbers chosen in current and previous iterations.
+If this number does not change comparing with the previous iteration, it indicates a convergent result.
+All computations are done with integers of fixed width $W$ except the last step of applying Chinese remainder theorem.
 In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transform.
@@
 
-        compute the tensor contraction on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\; \red{tensor network contraction for each $i$}
+        compute the tensor contraction for each $x = X_i \pmod p$ on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\;
 
@@
         $P = P \times p$\;
-    }\caption{Exactly compute the independence polynomial of a graph $G$ without integer overflow}\label{alg:finitefield} \red{discuss this algorithm table, $X_{ij}$, etc.}
+    }\caption{Compute the independence polynomial exactly without integer overflow}\label{alg:finitefield} \red{discuss this algorithm table, $X_{ij}$, etc.}\blue{done}
 \end{algorithm}
@@
 \subsection{Maximal independence polynomial}
-\red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} 
+\red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} \blue{done}
 Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
@@
 With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
+
+    \centerline{\begin{tikzpicture}[
+    dot/.style = {circle, fill, minimum size=#1,
+                inner sep=0pt, outer sep=0pt},
+    dot/.default = 6pt  % size of the circle diameter 
+                    ]  
+        \def\dx{0};
+        \def\r{0.5cm}
+        \def\G{1.0}
+        \foreach \x/\y/\v in {0/0/a, 1/0/b, 2/0/c, 3/0/d, 4/0/e}
+            \node[color=black] at (\x*\G+\dx,\y) (\v) {$s_\v$};
+        \foreach \x/\v/\t in {0/A/$T_a$, 1/B/$T_b$, 2/C/$T_c$, 3/D/$T_d$, 4/E/$T_e$}
+            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\t};
+        \draw [cyan,thick] (a) -- (A);
+        \draw [cyan,thick] (a) -- (B);
+        \draw [cyan,thick] (a) -- (C);
+        \draw [blue,thick] (b) -- (B);
+        \draw [blue,thick] (b) -- (A);
+        \draw [blue,thick] (b) -- (C);
+        \draw [blue,thick] (b) -- (D);
+        \draw [red,thick] (c) -- (C);
+        \draw [red,thick] (c) -- (A);
+        \draw [red,thick] (c) -- (B);
+        \draw [red,thick] (c) -- (D);
+        \draw [green,thick] (d) -- (D);
+        \draw [green,thick] (d) -- (B);
+        \draw [green,thick] (d) -- (C);
+        \draw [green,thick] (d) -- (E);
+        \draw [orange,thick] (e) -- (E);
+        \draw [orange,thick] (e) -- (D);
+    \end{tikzpicture}}
+
+One can see the average degree of a tensor is increase.
 The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
 However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+Let us consider the example in \Sec{eg:tensorcontraction}, its corresponding tensor network structure for computing maximal independent sets now becomes:
 
@@
 I thought this would be more consistent with the earlier notations and show how it's stored in the program as well.}
+\blue{I prefer the previous one, what about you @XG?}
 \begin{equation}
@@
     a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (), \text{\red{should this be (0)?}}  \\
+    \mymathbb{0} &= (), \text{\red{should this be (0)?}} \blue{\text{both are fine}} \\
     \mymathbb{1} &= (1).\label{eq:max2poly}
@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
+As will be shown bellow, this algebra can also be extended to enumerate suboptimal solutions.
 \red{can be used to enumerate suboptimal solution as well?}
+\blue{added some description}
 
@@
 Is there a definition somewhere?}
+\blue{bitwise OR is more often used. I think Hadamard xxx means broadcasted xxx, is this confusing?}
 \red{it would be useful to give an example of the operations above, $s = ...
 , t = ..., s \oplus t = ..., s \odot t = ...$.} \red{do we need to define $ \{\} \lor^\circ \sigma  = \sigma \lor^\circ \{\} = \{\}$?}
+\blue{we do not need an extra definition, see my example.}
+\begin{example}\label{eg:setalgebra}
+    For elements being bit vectors of length $5$, we have the following set algebra
+\begin{equation*}
+\begin{split}
+    &\{00001\} \oplus \{01110, 01000\} = \{01110, 01000\} \oplus \{00001\} = \{00001,01110, 01000\}\\
+    &\{00001\} \oplus \{\} = \{\}\\
+&\\
+    &\{00001\} \odot \{01110, 01000\} = \{01110, 01000\} \odot \{00001\} = \{01111, 01001\}\\
+    &\{00001\} \odot \{\} = \{\}\\
+    &\{00001\} \odot \{00000\} = \{00001\}
+\end{split}
+\end{equation*}
+\end{example}
+
 The variable $x_{i}$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
@@
     \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
-    \mymathbb{0} &= 1^{\otimes |V|}, \red{\text{should be } \mymathbb{0} = \{\}?} \\
+    \mymathbb{0} &= 1^{\otimes |V|}, \red{\text{should be } \mymathbb{0} = \{\}?}\\
+     &\blue{\text{I do not think so, in that way, we need an extra bit to represent an empty set}} \\
     \mymathbb{1} &= 0^{\otimes |V|},
@@
 \end{equation}
-On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines \red{do we need to cite here?}.
+On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM} \red{do we need to cite here?}\blue{would a link to github be good?}.
 Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
@@
 With the above method, one can significantly reduce the space needed to store the intermediate configurations.
-\blue{maybe add an appendix?} \red{I've edited this section a bit, and I think it's okay now - probably don't need an appendix.}  % my blog
 
@@
 Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision in low independent set size region  ($\omega<1$) or high independent set size region ($\omega>1$). \red{is that $\omega < 1$ or $r <1$?}
+By choosing different $r$, one can obtain better precision in low independent set size region  ($r<1$) or high independent set size region ($r>1$).
+\red{is that $\omega < 1$ or $r <1$?}\blue{it is $r$, fixed}
 

### 2021-09-09 paper/paper.tex
clean up

@@
 \section{Introduction}
-\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}, treewidth of 3-regular graphs ~\cite{Fomin2006},
+\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009},
 branching algorithm~\cite{Tarjan1977,Robson1986}
@@
 Tensor network contraction can be parallelized. When the element type is immutable, one can also run it on GPUs to speed up the computation.
+The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $tw(G) \leq |V|/6$~\cite{Fomin2006}.
 

### 2021-09-09 project/UnitDiskGraph.m

@@ -1,66 +1,0 @@
-function [edges, AdjMat, xy] = UnitDiskGraph(varargin)
-%UnitDiskGraph creates unit disk graph
-%
-%   Usages:
-%   [edges, AdjMat, xy] = UnitDiskGraph(xy)
-%       generates unit disk graph from coordinates of vertices, where any
-%       two vertices with <= 1 distance are connected by an edge
-%
-%   [edges, AdjMat, xy] = UnitDiskGraph(xy, rho, 1)
-%       generates unit disk graph from coordinates of vertices, where any
-%       two vertices with <= 1 distance on a LxL torus [L=sqrt(N/rho)] are
-%       connected by an edge [N = size(xy,1)]
-%
-%   [edges, AdjMat, xy] = UnitDiskGraph(N, rho)
-%       generates unit disk graph of N vertices with target density rho (open boundaries) 
-% 
-%   [edges, AdjMat, xy] = UnitDiskGraph(N, rho,0)
-%       generates unit disk graph of N vertices with target density rho (open boundaries)
-%
-%   [edges, AdjMat, xy] = UnitDiskGraph(N, rho,1)
-%       generates unit disk graph of N vertices with target density rho (periodic boundaries)
-%
-%   Output: edges = list of edges (i, j)
-%           AdjMat = adjacency matrix
-%           xy = coordinates of vertices
-
-
-if numel(varargin{1}) == 1
-    NNodes = varargin{1};
-    rho = varargin{2};
-    L = sqrt(NNodes/rho);
-    xy = rand(NNodes, 2)*L;
-else
-    xy = varargin{1};
-    NNodes = size(xy,1);
-    
-    if nargin >= 2
-        rho = varargin{2};
-        L = sqrt(NNodes/rho);
-    end
-end
-
-AdjMat = zeros(NNodes);
-
-if nargin <= 2 || (nargin == 3 && varargin{3} == 0) % open boundary condition
-    for ind = 1:NNodes
-        myXY = repmat(xy(ind, :), NNodes, 1);
-        dist = sum((xy - myXY).^2,2);
-        AdjMat(dist <= 1, ind) = 1;
-        AdjMat(ind, ind) = 0;
-    end
-end
-
-if nargin == 3 && varargin{3} == 1 % periodic boundary condition
-    for ind = 1:NNodes
-        myXY = repmat(xy(ind, :), NNodes, 1);
[…]

### 2021-09-09 project/configurations2.jl

@@ -1,59 +1,0 @@
-using DelimitedFiles, NoteOnTropicalMIS
-using NoteOnTropicalMIS.OMEinsumContractionOrders
-using NoteOnTropicalMIS.OMEinsum
-using NoteOnTropicalMIS.TropicalNumbers
-
-function mis_configurations(n, seed; writefile, sc_target=12)
-    folder = joinpath("/home/leo/.julia/dev/TropicalMIS", "project", "data")
-    fname = joinpath(folder, "mis_degeneracy_L$n.dat")
-    mask = Matrix{Bool}(reshape(readdlm(fname)[seed+1,4:end], n, n))
-    g = diagonal_coupled_graph(mask)
-    code = NoteOnTropicalMIS.idp_code(g; method=:kahypar, sc_target=sc_target, max_group_size=50, imbalances=0.0:0.003:0.8)
-    s, c = (res = mis_contract(CountingTropical{Int,Int}(1,1), code)[]; (res.n, res.c))
-    println("Graph $seed, n = $n, MIS size = $s, degeneracy = $c")
-    if c > 1000000
-        @warn "degeneracy too high, got: $c"
-    end
-    s2, config1, config0 = (res = mis_max2_config(code)[]; (res.maxorder, res.a, res.b))
-    @assert s == s2
-    @assert length(config0) == c
-    ofname = joinpath(folder, "configurations_$(n)x$(n)_$seed.dat")
-    ofname1 = joinpath(folder, "configurations_suboptimal_$(n)x$(n)_$seed.dat")
-    writefile && write(ofname, toMatrix(config0))
-    writefile && write(ofname1, toMatrix(config1))
-    return s, config0, config1
-end
-
-function toMatrix(x::ConfigEnumerator{N,C}) where {N,C}
-    m = zeros(UInt64, C, length(x))
-    for i=1:length(x)
-        m[:,i] .= x.data[i].data
-    end
-    return m
-end
-
-for (n, seeds) in [
-    #(5, [410, 407, 396]),
-    #(6, [667, 557, 78]),
-    #(7, [189, 623, 354]),
-    #(10, [983, 828, 61]),
-    #(11, [571, 808, 438]),
-    #(15, [612, 907, 758])
-    #(10, [982, 456, 843]),  # easy, ~25
-    #(10, [347, 793, 82]),  # intermediate, ~85
[…]

### 2021-09-09 project/maximal2.jl

@@ -1,55 +1,0 @@
-using NoteOnTropicalMIS, Polynomials, Random, OMEinsum
-
-using DelimitedFiles
-using NoteOnTropicalMIS.OMEinsum
-
-function mis_maximal_counting(n, seed; writefile, sc_target=24, usecuda=false, imbalances=0.0:0.002:1.0)
-    folder = joinpath(homedir(), ".julia/dev/TropicalMIS", "project", "data")
-    fname = joinpath(folder, "mis_degeneracy_L$n.dat")
-    mask = Matrix{Bool}(reshape(readdlm(fname)[seed+1,4:end], n, n))
-    g = diagonal_coupled_graph(mask)
-    println("Graph $seed")
-    res = maximal_polynomial(Val(:finitefield), g; sc_target=sc_target, imbalances=imbalances, max_group_size=50, usecuda=usecuda)
-    folderout = joinpath(folder, "maximal_polynomial_L$(n)")
-    if !isdir(folderout)
-        mkdir(folderout)
-    end
-    ofname = joinpath(folderout, "$(seed).dat")
-    writefile && writedlm(ofname, res.coeffs)
-end
-
-# patch
-using GPUArrays, CUDA, LinearAlgebra
-function LinearAlgebra.permutedims!(dest::AbstractGPUArray, src::AbstractGPUArray,
-                                    perm::NTuple)
-    Base.checkdims_perm(dest, src, perm)
-    function permutedims_kernel(ctx, dest, src, perm)
-        I = @cartesianidx src
-        @inbounds begin
-            J = CartesianIndex(map(i->I[i], perm))
-            dest[J] = src[I]
-        end
-        return
-    end
-    gpu_call(permutedims_kernel, dest, src, perm)
-    return dest
-end
-
-const DEVICE = length(ARGS) >= 1 ? parse(Int, ARGS[1]) : -1
-
-if DEVICE >= 0
-    CUDA.device!(DEVICE)
-end
-
-#for seed in [0, 2, 4, 9, 50]
-#    @time mis_maximal_counting(10, seed; writefile=true, sc_target=20, usecuda=DEVICE>=0)
-#end
-
-for n = [11]
-    for seed in 488:699
-        try
-            @time mis_maximal_counting(n, seed; writefile=true, sc_target=20, usecuda=DEVICE>=0, imbalances=0.03:0.001:1.0)
-        catch e
-        end
-    end
-end

### 2021-09-09 project/proofs.jl

@@ -1,4 +1,0 @@
-using TropicalNumbers, OMEinsum, NoteOnTropicalMIS
-
-code = ein"u,v,w,j,k,vw,vj,vk,ku,wu,wk->juk"
-mis_contract(Tropical(1.0), code)

### 2021-09-09 src/NoteOnTropicalMIS.jl

@@ -1,40 +1,10 @@
 module NoteOnTropicalMIS
 
-using OMEinsumContractionOrders: OMEinsum
-using Core: Argument
-using TropicalGEMM, TropicalNumbers
-using OMEinsum
+using GraphTensorNetworks
 
 project_relative_path(xs...) = normpath(joinpath(dirname(dirname(pathof(@__MODULE__))), xs...))
 
-# patch
-if isdefined(OMEinsum, :flatten)
-    using OMEinsum: flatten
-else
-    flatten(code) = Iterators.flatten(code::Union{NestedEinsum,EinCode})
-end
-
-using TensorOperations, LinearAlgebra
-function LinearAlgebra.permutedims!(C::Array{T,N}, A::StridedArray{T,N}, perm) where {T,N}
-    if isbitstype(T)
-        TensorOperations.tensorcopy!(A, ntuple(identity,N), C, perm)
-    else
-        invoke(permutedims!, Tuple{Any,AbstractArray,Any}, C, A, perm)
-    end
-end
-
-include("arithematics.jl")
 include("widgets.jl")
-include("independence_polynomial.jl")
-include("configurations.jl")
-include("graphs.jl")
-include("bounding.jl")
-include("viz.jl")
 include("demos.jl")
-
-using Requires
-function __init__()
-    @require CUDA="052768ef-5323-5732-b1bb-66c8b64840ba" include("cuda.jl")
-end
 
 end

### 2021-09-09 src/cuda.jl

@@ -1,9 +1,0 @@
-using .CUDA
-
-function onehotmask(A::CuArray{T}, X::CuArray{T}) where T
-    mask = X .== inv.(A)
-    ci = argmax(mask)
-    mask .= false
-    mask[CuArray([ci])] = true
-    return mask
-end

### 2021-09-09 src/independence_polynomial.jl

@@ -1,295 +1,0 @@
-using Polynomials
-using OMEinsum: NestedEinsum, getixs, getiy
-
-export independence_polynomial, match_polynomial
-export misb, misv, mis_size, mis_count, mis_contract
-
-# MIS bond tensor
-misb(::Type{T}) where T = [one(T) one(T); one(T) zero(T)]
-# MIS vertex tensor
-misv(::Type{T}, val) where T = [one(T), convert(T, val)]
-
-function neighbortensor(x::T, d::Int) where T
-    t = zeros(T, fill(2, d)...)
-    for i = 2:1<<(d-1)
-        t[i] = one(T)
-    end
-    t[1<<(d-1)+1] = x
-    return t
-end
-
-function mis_contract(x::T, code; usecuda=false) where {T}
-    tensors = map(getixs(flatten(code))) do ix
-        # if the tensor rank is 1, create a vertex tensor.
-        # otherwise the tensor rank must be 2, create a bond tensor.
-        t = length(ix)==1 ? misv(T, x) : misb(T)
-        usecuda ? CuArray(t) : t
-    end
-	dynamic_einsum(code, tensors)
-end
-
-mis_size(code; usecuda=false) = Int(asscalar(mis_contract(TropicalF64(1.0), code; usecuda=usecuda)).n)
-mis_count(code; usecuda=false) = asscalar(mis_contract(CountingTropical{Float64,Float64}(1.0, 1.0), code; usecuda=usecuda)).c
-
-function independence_polynomial(::Val{:fft}, code; mis_size=mis_size(code), r=1.0, usecuda=false)
-	ω = exp(-2im*π/(mis_size+1))
-	xs = r .* collect(ω .^ (0:mis_size))
-	ys = [asscalar(mis_contract(x, code; usecuda=usecuda)) for x in xs]
-	Polynomial(ifft(ys) ./ (r .^ (0:mis_size)))
-end
-
-function independence_polynomial(::Val{:fitting}, code; mis_size=mis_size(code), usecuda=false)
-	xs = (0:mis_size)
-	ys = [asscalar(mis_contract(x, code; usecuda=usecuda)) for x in xs]
-	fit(xs, ys, mis_size)
-end
-
-function independence_polynomial(::Val{:polynomial}, code; usecuda=false)
-    @assert !usecuda "Polynomial type can not be computed on GPU!"
-    mis_contract(Polynomial([0, 1.0]), code)
-end
-
-using Mods, Primes
-
-# pirate
[…]

### 2021-09-09 test/bounding.jl

@@ -1,37 +1,0 @@
-using Test, OMEinsum, NoteOnTropicalMIS, TropicalNumbers, Random
-using NoteOnTropicalMIS: cached_einsum, generate_masktree, masked_einsum, CacheTree
-
-@testset "cached einsum" begin
-    xs = map(x->Tropical.(x), [randn(2,2), randn(2), randn(2,2), randn(2,2), randn(2,2)])
-    code = ein"((ij,j),jk, kl), ii->kli"
-    size_dict = uniformsize(code, 2)
-    c = cached_einsum(code, xs, size_dict)
-    @test c.content == code(xs...)
-    mt = generate_masktree(code, c, rand(Bool,2,2,2), size_dict)
-    @test mt isa CacheTree{Bool}
-    y = masked_einsum(code, xs, mt, size_dict)
-    @test y isa AbstractArray
-end
-
-@testset "bounding contract" begin
-    for seed in 1:100
-        Random.seed!(seed)
-        xs = map(x->TropicalF64.(x), [rand(1:5,2,2), rand(1:5,2), rand(1:5,2,2), rand(1:5,2,2), rand(1:5,2,2)])
-        code = ein"((ij,j),jk, kl), ii->kli"
-        y1 = code(xs...)
-        y2 = bounding_contract(code, xs, BitArray(ones(Bool,2,2,2)), xs)
-        @test y1 ≈ y2
-    end
-    rawcode = random_regular_eincode(10, 3)
-    optcode = OMEinsum.optimize_greedy(rawcode, uniformsize(rawcode, 2))
-    xs = map(OMEinsum.getixs(rawcode)) do ix
-        length(ix)==1 ? misv(TropicalF64,TropicalF64(1.0)) : misb(TropicalF64)
-    end
-    y1 = rawcode(xs...)
-    y2 = bounding_contract(rawcode, xs, BitArray(fill(true)), xs)
-    @test y1 ≈ y2
-    y1 = optcode(xs...)
-    y2 = bounding_contract(optcode, xs, BitArray(fill(true)), xs)
-    @test y1 ≈ y2
-end
-

### 2021-09-09 test/configurations.jl

@@ -1,30 +1,0 @@
-using NoteOnTropicalMIS, Test, LightGraphs
-using OMEinsum
-
-@testset "ConfigTropical" begin
-    x = one(ConfigTropical{Float64, 5, 1})
-    @test x.n == 0
-    @test x.config == falses(5)
-    x = zero(ConfigTropical{Float64, 5, 1})
-    @test x.n == -Inf
-    @test x.config == trues(5)
-end
-
-@testset "enumerating" begin
-    rawcode = random_regular_eincode(10, 3)
-    optcode = OMEinsum.optimize_greedy(rawcode, uniformsize(rawcode, 2))
-    for code in [rawcode, optcode]
-        res0 = mis_size(code)
-        res1 = mis_count(code)
-        res2 = mis_config(code; all=true, bounding=true)[]
-        res3 = mis_config(code; all=false, bounding=false)[]
-        res4 = mis_config(code; all=true, bounding=false)[]
-        @test res0 == res2.n == res3.n == res4.n
-        @test res1 == length(res2.c) == length(res4.c)
-        @test res3.config ∈ res2.c.data
-        @test res3.config ∈ res4.c.data
-        res5 = mis_config(code; all=false, bounding=true)[]
-        @test res5.n == res0
-        @test res5.config ∈ res2.c.data
-    end
-end

### 2021-09-09 test/runtests.jl

@@ -1,14 +1,2 @@
 using NoteOnTropicalMIS
 using Test
-
-@testset "independence polynomial" begin
-    include("independence_polynomial.jl")
-end
-
-@testset "configurations" begin
-    include("configurations.jl")
-end
-
-@testset "bounding" begin
-    include("bounding.jl")
-end

### 2021-09-09 benchmarks/benchmarks.jl
add manifest

@@ -1,6 +1,33 @@
-using NoteOnTropicalMIS, DelimitedFiles
+using GraphTensorNetworks, DelimitedFiles
 using LightGraphs
 using BenchmarkTools
+
+function case_r3(n, k=3; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    graph = (Random.seed!(seed); LightGraphs.random_regular_graph(n, k))
+    @assert length(connected_components(graph)) == 1  # connected graph
+    # optimize the contraction order using KaHyPar + Greedy
+    optcode = Independence(graph; optmethod=:kahypar, sc_target=sc_target, max_group_size=40, imbalances=0:0.001:1)
+    return optcode
+end
+
+function case_dc(L::Int, ρ; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    Random.seed!(seed)
+    graph = diagonal_coupled_graph(rand(L, L) .< ρ)
+    # optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+    optcode = Independence(graph; optmethod=:kahypar, sc_target=sc_target, max_group_size=40)
+    return optcode
+end
+
+function case_sq(L::Int, ρ; sc_target, seed=2)
+    # generate a random regular graph of size 100, degree 3
+    Random.seed!(seed)
+    graph = square_lattice_graph(rand(L, L) .< ρ)
+    # optimize the contraction order using KaHyPar + Greedy, target space complexity is 2^20
+    optcode = idp_code(graph; method=:kahypar, sc_target=sc_target, max_group_size=40)
+    return optcode
+end
 
 # setup global arguments
 const GRAPH = length(ARGS) >= 1 ? ARGS[1] : "r3"
@@ -56,11 +83,12 @@ const truncatedict = Dict(
     "r3"=>Dict([string(task)=>ntruncate for (task, ntruncate) in [
         (:totalsize, 0), (:maxsize, 0), (:counting, 0),
         (:idp_polynomial, 3), (:idp_fft, 0), (:idp_finitefield, 3),
-        (:config_single, 0), (:config_all, 6), (:config_single_bounded, 0), (:config_all_bounded, 3)
+        (:config_single, 0), (:config_all, 3), (:config_single_bounded, 0), (:config_all_bounded, 0)
         ]]),
[…]

### 2021-09-10 paper/paper.tex
add manifest
update benchmarks

@@
 \blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009},
-branching algorithm~\cite{Tarjan1977,Robson1986}
+branching algorithm~\cite{Tarjan1977,Robson1986},
+two motivations of computing independence polynomial: 1. Lee-Yang zero~\cite{Lee1952,Yang1952}, 2. Lov{\'a}sz local lemma~\cite{Scott2005}.
 }
@@
 This leads us to think about what is the most general element type that allowed in a tensor network contraction program.
-Our finding is: as long as the tensor elements form a commutative semiring, the tensor network contraction result can be contraction order independent.
-So what is a commutative semiring?
-A semiring is a ring without additive inverse, while a commutative semiring is a semiring where the multiplication operation is commutative.
+Our finding is: as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result is contraction order independent.
+A commutative semiring is a semiring with its multiplication operation being commutative, while a semiring is a ring without additive inverse.
 To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
@@
 \subsection{Performance benchmarks}
-We run a sequential program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results in Figure~\ref{fig:benchmark}.
-Tensor network contraction can be parallelized. When the element type is immutable, one can also run it on GPUs to speed up the computation.
+We run a single thread benchmark on CPU Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
+and its CUDA version on a GPU Tesla V100.
+The results are shown in Figure~\ref{fig:benchmark}.
 The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $tw(G) \leq |V|/6$~\cite{Fomin2006}.
@@
     \centering
-    \includegraphics[width=0.8\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{benchmark.pdf}
-    \caption{\red{label x-axis as ``number of vertices, $|V|$''} Benchmark results for computing different properties of independent sets with different tensor element types.
-The right axis is only for the dashed line.
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
+    \caption{Benchmark results for computing different properties of independent sets on a random three regular graph with different tensor element types.
+    (b) is the computing time for computing maximum independent set size, number of independent sets and suboptimal sets.
+    (c) is the computing time for independence polynomials with different approaches.
+    (d) is the computing time for finding all configurations and a single configuration, with or without bounding.
     }\red{split into two graphs: one with time versus number of vertices, $|V|$, and one with time versus tree width.}
@@
 \end{figure}
+
+Among the benchmarks shown in \Fig{fig:benchmark}, computing \texttt{max size (CPU)},
+\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS libraries,
+hence they are relatively faster comparing to other methods in the same category.
+Only algebras requiring dynamic sized structures can not be computed on GPU, here are polynomial algebra for computing independence polynomial and set algebra for enumerating configurations.
+When computing the independence polynomial, the finite field approach is the only method without round off error that can run on GPU.
 

### 2021-09-10 paper/paper.tex
resolve comments

@@
 The generalized tensor network can be easily translated to the standard notation by adding identity tensors denoted as $\delta$ tensors.
-The example above can be written as $C_{ijkl} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}$ in the standard notion.
+The example above can be written as $C_{ijkl} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}$ \red{update this} in the standard notion.
 However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
@@
 Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
-We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
+We hope our algorithms to calculate the independence polynomial can also help further research in these directions. \red{possibly add set packing problem relationship}
 
@@
     \end{matrix}\right), \label{eq:tensor}
-\end{equation}
+\end{equation} \red{remove subscript $s_{i} s_{j}$ and add description after the next equation}
 where the tensor index $s_i$ is a boolean variable; $s_{i} = 1$ corresponds that the vertex $i$ is in the independent set, and $s_{i} = 0$ means otherwise.
@@
 Mapping a graph (left) to a tensor network (right) that encodes the independence polynomial.
-In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge, and an edge is mapped to an edge tensor.
-\red{a vertex is mapped to a hyperedge?}\blue{$\checkmark$}
+In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge, and a vertex tensor is connected to the hyperedge.
+An edge is mapped to an edge tensor connected to the hyperedge.
+\red{come back to this to change}\blue{$\checkmark$}
 
@@
     a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, a_{2}b_{0} + a_{1}b_{1} + a_{0}b_{2},  \ldots, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (), \text{\red{should this be (0)?}}\blue{\text{both are ok}} \\
+    \mymathbb{0} &= (),  \\
     \mymathbb{1} &= (1).\label{eq:polynomial}
@@
 \begin{equation}
-    W_{s_i}^{\rm poly} = \left(\begin{matrix}
+    W^{\rm poly} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B_{s_i s_j}^{\rm poly} = \left(\begin{matrix}
+        B^{\rm poly} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 In each iteration, we contract tensor networks to evaluate the polynomial for each $x\in X$ on the finite field algebra ${\rm GF}(p)$.
-Let use denote the results as $Y$, then we solve a linear equation $Y = \hat X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient moduluses $A_p \equiv A \pmod p$.
+Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient moduluses $A_p \equiv A \pmod p$.
 Finally we apply the Chinese remainder theorem to get $A \pmod P$, where $P$ is a product of all prime numbers chosen in current and previous iterations.
@@
     \LinesNumbered
-    Let $P = 1$, $W$ be the integer width, vector $X = (0,1,2, \ldots, \alpha(G))$, matrix $\hat X_{ij} = X_i^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
+    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
 
@@
 
-        compute the tensor contraction for each $x = X_i \pmod p$ on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\;
-
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(\hat X, Y \pmod p) $\;
+        compute the tensor contraction for each $x = \chi_i \pmod p$ on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\; \red{for each $i$}
+
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, Y \pmod p) $\;
 
@@
         $P = P \times p$\;
-    }\caption{Compute the independence polynomial exactly without integer overflow}\label{alg:finitefield} \red{discuss this algorithm table, $X_{ij}$, etc.}\blue{done}
+    }\caption{Compute the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
 \end{algorithm}
@@
 \subsection{Maximal independence polynomial}
-\red{It might be helpful to add a figure of the tensor network for computing the maximal independence polynomial.} \blue{done}
 Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
@@
 However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
-Let us consider the example in \Sec{eg:tensorcontraction}, its corresponding tensor network structure for computing maximal independent sets now becomes:
+Let us consider the example in~\Sec{eg:tensorcontraction}, its corresponding tensor network structure for computing maximal independent sets now becomes:
 
@@
 \begin{equation}
-    W_{s_i}^{\rm tropical} = \left(\begin{matrix}
+    W^{\rm tropical} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B_{s_i s_j}^{\rm tropical} = \left(\begin{matrix}
+        B^{\rm tropical} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
     a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (), \text{\red{should this be (0)?}} \blue{\text{both are fine}} \\
+    \mymathbb{0} &= (), \\
     \mymathbb{1} &= (1).\label{eq:max2poly}
@@
 As will be shown bellow, this algebra can also be extended to enumerate suboptimal solutions.
-\red{can be used to enumerate suboptimal solution as well?}
-\blue{added some description}
 
@@
 where $s$ and $t$ are each a set of $|V|$-bit strings and $\lor^\circ$ is the bitwise OR operation over two bit strings.
-\red{This is the bitwise OR operation right?
-I can't seem to find online what you call Hadamard.
-Is there a definition somewhere?}
-\blue{bitwise OR is more often used. I think Hadamard xxx means broadcasted xxx, is this confusing?}
-\red{it would be useful to give an example of the operations above, $s = ...
-, t = ..., s \oplus t = ..., s \odot t = ...$.} \red{do we need to define $ \{\} \lor^\circ \sigma  = \sigma \lor^\circ \{\} = \{\}$?}
-\blue{we do not need an extra definition, see my example.}
 \begin{example}\label{eg:setalgebra}
@@
 \begin{equation}
-    W_{s_i}^{\rm enum} = \left(\begin{matrix}
+    W^{\rm enum}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B_{s_i s_j}^{\rm enum} = \left(\begin{matrix}
+        B^{\rm enum} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \begin{equation}
-    W_{s_i}^{\rm MISenum} = \left(\begin{matrix}
+    W^{\rm MISenum}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B_{s_i s_j}^{\rm MISenum} = \left(\begin{matrix}
+        B^{\rm MISenum} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
     \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
-    \mymathbb{0} &= 1^{\otimes |V|}, \red{\text{should be } \mymathbb{0} = \{\}?}\\
-     &\blue{\text{I do not think so, in that way, we need an extra bit to represent an empty set}} \\
+    \mymathbb{0} &= 1^{\otimes |V|}, \\
     \mymathbb{1} &= 0^{\otimes |V|},
@@
 %In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
-
-\red{The zero element doesn't seem right to me. Do we need to separately define 
-\begin{align*}
-a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
-a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
-\end{align*}
-}\blue{I think picking the smaller one would solve the issue.}
-
 \red{Can we also enumerate all maximal independent sets by combining with \Eq{eq:maximal} or enumerate suboptimal solutions by combining with the truncated polynomial?}
@@
 \end{equation}
-On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM} \red{do we need to cite here?}\blue{would a link to github be good?}.
+On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
 Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
@@
 The results are shown in Figure~\ref{fig:benchmark}.
-The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $tw(G) \leq |V|/6$~\cite{Fomin2006}.
+The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
 
@@
 By choosing different $r$, one can obtain better precision in low independent set size region  ($r<1$) or high independent set size region ($r>1$).
-\red{is that $\omega < 1$ or $r <1$?}\blue{it is $r$, fixed}
 

### 2021-09-11 paper/paper.tex
complete benchmark

@@
 \begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$ 
-\red{I've changed this. please check. The original was $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ and $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$}.
-\blue{changed back because $l$ is not an open edge. Is it still confusing if I introduce open circles for open edges?}
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
+where $i,j,k$ in the output tensor are open edges.
 Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges and open circles to denote open edges.
@@
     \node[color=white,fill=black,dot=\r] at (\cx+\dx,\cy) (v) {V};
-    \node[color=white,draw=black,dot=\sr] at (\ax-1,\by) (o1) {};
-    \node[color=white,draw=black,dot=\sr] at (\ax-1.5,\ay) (o2) {};
-    \node[color=white,draw=black,dot=\sr] at (\ax-1,\cy) (o3) {};
+    \node[color=transparent,draw=transparent,dot=0] at (\ax-1,\by) (o1) {};
+    \node[color=transparent,draw=transparent,dot=0] at (\ax-1.5,\ay) (o2) {};
+    \node[color=transparent,draw=transparent,dot=0] at (\ax-1,\cy) (o3) {};
     \node at (\ax-0.8,\ay) (k) {k};
@@
 The generalized tensor network can be easily translated to the standard notation by adding identity tensors denoted as $\delta$ tensors.
-The example above can be written as $C_{ijkl} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}$ \red{update this} in the standard notion.
+The example above can be written as $C_{ijk} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$ in the standard notion.
 However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
@@
 \section{Generic programming}\label{sec:generic}
-\red{I suggest we have a section on generic programming, putting both the semiring stuff and the summary table to this section, since generic programming is one of the highlights of this paper as well.
-I think it doesn't need to be long.
-Jinguo, could you write one or two paragraphs introducing generic programming?}\blue{I wrote a draft here, does it look ok in general?}
 In previous works combining tensor network and combinatoric problems~\cite{Kourtis2019,Biamonte2017},
@@
 Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
-We hope our algorithms to calculate the independence polynomial can also help further research in these directions. \red{possibly add set packing problem relationship}
+We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
+\red{possibly add set packing problem relationship} \blue{I added a subsection in \App{app:otherproblems}?}
 
 To compute the independence polynomial of a graph $G$, we encode it to a tensor network.
-On the vertex $i$ of the graph $G$, we place a rank-one vertex tensor, $W(x_i)$, of size $2$ parametrized by $x_{i}$ and a rank-two edge tensor, $B$, of size $2 \times 2$ on an edge $(i,j)$
+On the vertex $i$ of the graph $G$, we place a rank-one vertex tensor, $W(x_i)$, of size $2$ parametrized by $x_{i}$ and a rank-two edge tensor, $B$, of size $2 \times 2$ on an edge
 \red{I removed the indices $s_{i}$ etc, on the right of the equations, since that looks confusing to me. If I understand correctly, $s_{i}, s_{j}$ just denotes the index of the vector/matrix.}
 \blue{To be consistent, we should also remove the index on the LHS. It is better not removing the label information.}
-\begin{equation}
-    W(x_i)_{s_i} = \left(\begin{matrix}
+\blue{now?}
+\begin{equation}
+    W(x_i) = \left(\begin{matrix}
         1 \\
@@
     \qquad \quad 
-       B_{s_i s_j} = \left(\begin{matrix}
+       B = \left(\begin{matrix}
         1  & 1\\
@@
     \end{matrix}\right), \label{eq:tensor}
-\end{equation} \red{remove subscript $s_{i} s_{j}$ and add description after the next equation}
-where the tensor index $s_i$ is a boolean variable; $s_{i} = 1$ corresponds that the vertex $i$ is in the independent set, and $s_{i} = 0$ means otherwise.
+\end{equation}
+The corresponding tensor network contraction gives
+\begin{equation}
+    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
+\end{equation}
+where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$ (see Example \ref{eg:tensorcontraction} for a concrete example).
+The tensor index $s_i$ is a boolean variable; $s_{i} = 1$ corresponds that the vertex $i$ is in the independent set, and $s_{i} = 0$ means otherwise.
 Let us assume the tensor elements are real numbers for now.
@@
 The contraction of the tensor network representing $G$ gives
-\begin{equation}
-    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
-\end{equation}
-where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the scalar output $P$ (see Example \ref{eg:tensorcontraction} for a concrete example).
 In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
@@
 Mapping a graph (left) to a tensor network (right) that encodes the independence polynomial.
-In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge, and a vertex tensor is connected to the hyperedge.
-An edge is mapped to an edge tensor connected to the hyperedge.
-\red{come back to this to change}\blue{$\checkmark$}
+In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge.
+We attach a vertex tensor on each hyperedge and an edge tensor between two hyperedges if vertices of the two hyperedges are connected in the original graph.
+\red{come back to this to change}\blue{now?}
 
@@
 Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient moduluses $A_p \equiv A \pmod p$.
-Finally we apply the Chinese remainder theorem to get $A \pmod P$, where $P$ is a product of all prime numbers chosen in current and previous iterations.
+Finally we apply the Chinese remainder theorem to get $A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
 If this number does not change comparing with the previous iteration, it indicates a convergent result.
@@
 
+\LinesNumberedHidden
 \begin{algorithm}[!ht]
@@
     \SetAlgoNoLine
-    \LinesNumbered
+    %\LinesNumbered
     Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
@@
 
-        compute the tensor contraction for each $x = \chi_i \pmod p$ on $\text{GF}(p)$ and obtain $Y = (y_0, y_1, \ldots , y_{\alpha(G)}) \pmod p $\; \red{for each $i$}
+        \For{$i=1\ldots\alpha(G)$}{
+            t = ${\rm tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{defined on $\text{GF}(p)$}
+
+            $Y_i \pmod p  = {\rm contract}(t)$\;
+        }
 
@@
 \end{equation}
-Contraction of the tensor network enumerates all the independent sets.
-To enumerate only the MISs, we can combine the above algebra \Eq{eq:set} with the tropical algebra in \Eq{eq:countingtropical} and define $s(k) = (s_{k}, k)$, where the first element follows the algebra in \Eq{eq:set} and the second element follows the max-plus tropical algebra.
+
+This sets algebra can serve as the coefficients in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
+or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
+For example, to enumerate only the MISs, with the tropical algebra, we define $s(k) = (s_{k}, k)$, where the first element follows the algebra in \Eq{eq:set} and the second element follows the max-plus tropical algebra.
 The combined operations become: 
@@
 The contraction of the corresponding tensor network yields an enumeration of all MIS configurations.
+
 If one is interested in obtaining only a single MIS configuration, one can just keep a single configuration in the intermediate computations to save the computational effort.
@@
 \red{Can we also enumerate all maximal independent sets by combining with \Eq{eq:maximal} or enumerate suboptimal solutions by combining with the truncated polynomial?}
+\blue{now?}
+
+Although the above discussion is in the context of the the MIS problem, we can also combine the above algebras with the maximal independence network in \Eq{eq:maximal} to enumerate or sample maximal independent sets,
+as well as other problems in \App{app:otherproblems} for configuration enumeration and sampling.
 
@@
     (d) is the computing time for finding all configurations and a single configuration, with or without bounding.
-    }\red{split into two graphs: one with time versus number of vertices, $|V|$, and one with time versus tree width.}
-    \red{We also need to show/say what types of graphs is used here for benchmarking.}
+    }
     \label{fig:benchmark}
@@
 Among the benchmarks shown in \Fig{fig:benchmark}, computing \texttt{max size (CPU)},
-\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS libraries,
+\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions,
 hence they are relatively faster comparing to other methods in the same category.
@@
 When computing the independence polynomial, the finite field approach is the only method without round off error that can run on GPU.
+To enumerate the MISs, the technique to bound the enumeration space is important,
+without which the largest enumeratible size is only $150$ with 32G memory while being one order slower.
 
@@
 It is straight forward to define the k-coloring problem on edges hence we will not discuss the detailed construction here.
+
+\subsection{Max cut problem}
+Max cut problem is also known as the boolean spinglass problem.
+Its tensor network representation does not contain vertex tensors.
+The edge tensor can be defined as
+\begin{equation}
+    B(x_{ij}) = \left(\begin{matrix}
+        1 & x_{ij}\\
+        x_{ij} & 1
+    \end{matrix}\right).
+\end{equation}
+We can also define a polynomial about edges variables by setting $x_{ij} = x$,
+its $k$th coefficient is two times the number of configurations of cut size $k$.
+
+\subsection{Set packing}
+Set packing the the hypergraph version of the maximum independent set problem, where each set corresponds to a vertex, each element corresponds to a hyperedge.
+To solve the set packing problem, we just remove the rank 2 restriction of an edge tensor
+\begin{equation}
+    B_{v,w,\ldots, z} = \begin{cases}
+        1, & v+w+\ldots+z\leq 1,\\
+        0, & otherwise
+    \end{cases}
+\end{equation}
 
@@
 
+We also computed independence polynomial rigorously for these lattices in our Github repo\blue{add link to the repo}.
+
 \end{document}

### 2021-09-11 paper/paper.tex
small revision on abstract and intro

@@
 \begin{abstract}
-We introduce a new approach to compute various properties of independent sets by encoding the problems into tensor networks with different tensor element algebra.
-The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of the maximum independence set configurations.
-Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods;
-on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
+We introduce a new approach to compute various properties of independent sets by encoding the problems and the graph into tensor networks with different tensor element algebra.
+The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
+Although the computational complexity inevitably scales exponentially with the graph size, our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
+At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
@@
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for the MIS requires time $O(2^{|V|})$. More efficient exact algorithms include the branching algorithms and dynamic programming.
-Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^n n ^{O(1)}$~\cite{Xiao2017}.
+Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms and dynamic programming.
+Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}.
 Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
@@
 map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}.
-Besides the standard MIS problem, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
-independence polynomial, maximal independence polynomial, and enumeration of optimal and sub-optimal configurations.
+Besides the standard problem of finding the independence number and an MIS, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
+independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent set configurations.
 Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 Our approach does not necessarily provide a better time complexity compared to dynamic programming,
-but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts.
-We benchmark our algorithms, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
+but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
+We benchmark our algorithms by computing various independent set properties on CPUs and GPUs, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
 Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant,

### 2021-09-11 paper/paper.tex
small revision on section 2

@@
 $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
-where $i,j,k$ in the output tensor are open edges.
-Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges and open circles to denote open edges.
+where $i,j,k$ in the output tensor are open edges (note that $j$ is not an open edge and thus summed over).
+Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
 

### 2021-09-11 paper/paper.tex
small revision on section 3

@@
 \section{Generic programming}\label{sec:generic}
-In previous works combining tensor network and combinatoric problems~\cite{Kourtis2019,Biamonte2017},
-the elements in tensor networks are limited to regular number types such as floating point numbers and integers.
-As the development of modern compiling technology, we do not need to limit our imaginations to regular number types anymore.
-The key technology playing the role is called the generic programming:
+In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
+the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
+Owning to the development of modern compiling technology, we no longer need to limit our imagination to standard number types.
+One of the key concepts that push the technology forward is called generic programming:
 
@@
 
-This definition of generic programming contains two major pieces, one is a single program for the general setting, and another is about efficiency.
-To understand the first point, suppose we want to write a function to take the power of an element $f(x, n) := x^n$.
-One can easily write a function for regular numbers that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
-A generic programmer does not assume $x$ being a regular number type,
-instead it treats $x$ as an element with an associative multiplication operation $\odot$ and multiplicative identity $\mymathbb{1}$.
-In such a way, when the program takes a matrix as input, it computes the matrix power without extra efforts.
-The second point about performance. For dynamic typed languages like Python,
-one can easily write very general codes, however, the efficiency is not guaranteed.
-Imagine the speed of computing the matrix multiplication between two numpy arrays with python objects as elements.
-The generic programming that we want to discuss is those in static types languages like C++, and Julia~\cite{Bezanson2012}.
-C++ uses templates for generic programming while Julia has just in time compiling and multiple dispatch.
-When they ``sees'' a new input type, the compiler recompiles the generic program for the new type.
-A lot optimization can be done during the compiling, like inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
+This definition of generic programming contains two major aspects: a single program for the general setting and efficiency.
+To understand the first aspect, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
+One can easily write a function for standard number types that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
+Generic programming does not require $x$ to be a standard number type,
+instead it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
+In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
+The second aspect is about performance. For dynamically typed languages such as Python,
+one can easily write very general codes, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two numpy arrays with python objects as elements is much slower than statically typed languages such as C++ and Julia~\cite{Bezanson2012}.
+C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatch.
+When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.
+A myriad of optimizations can be done during the compilation, such as inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
 In Julia, these inlined arrays can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
 
-This leads us to think about what is the most general element type that allowed in a tensor network contraction program.
-Our finding is: as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result is contraction order independent.
+This motivates us to think about what is the most general element type that is allowed in a tensor network contraction program.
+We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
 A commutative semiring is a semiring with its multiplication operation being commutative, while a semiring is a ring without additive inverse.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
+To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for any arbitrary three elements $a, b, c \in R$.
 \begin{align*}
@@
 In the following sections, we show how to compute the independence polynomial,
-the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent set configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
 Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.

### 2021-09-12 paper/paper.tex
small revision on section 4

@@
 We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
-\red{possibly add set packing problem relationship} \blue{I added a subsection in \App{app:otherproblems}?}
 
@@
 On the vertex $i$ of the graph $G$, we place a rank-one vertex tensor, $W(x_i)$, of size $2$ parametrized by $x_{i}$ and a rank-two edge tensor, $B$, of size $2 \times 2$ on an edge
-\red{I removed the indices $s_{i}$ etc, on the right of the equations, since that looks confusing to me. If I understand correctly, $s_{i}, s_{j}$ just denotes the index of the vector/matrix.}
-\blue{To be consistent, we should also remove the index on the LHS. It is better not removing the label information.}
-\blue{now?}
 \begin{equation}
@@
 The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
-The contraction of the tensor network representing $G$ gives
 In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
@@
 We attach a vertex tensor on each hyperedge and an edge tensor between two hyperedges if vertices of the two hyperedges are connected in the original graph.
-\red{come back to this to change}\blue{now?}
 
@@
 This is an iterative algorithm that tries different prime numbers $p$ until convergence.
-In each iteration, we contract tensor networks to evaluate the polynomial for each $x\in X$ on the finite field algebra ${\rm GF}(p)$.
-Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient moduluses $A_p \equiv A \pmod p$.
+In each iteration, we contract the tensor networks to evaluate the polynomial for each $x_{i}$ on the finite field algebra ${\rm GF}(p)$.
+Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv A \pmod p$.
 Finally we apply the Chinese remainder theorem to get $A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change comparing with the previous iteration, it indicates a convergent result.
-All computations are done with integers of fixed width $W$ except the last step of applying Chinese remainder theorem.
+If this number does not change compared with the previous iteration, it indicates the result has converged.
+All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem.
 In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transform.
@@
 \subsection{Maximal independence polynomial}
-Sometimes people are interested in knowing maximal solutions to understand why their programs are trapped in a local minimal.
-In this paper, the word ``maximal'' is different with the ``maximum'' discussed the previous discussion in such a way that it is not necessarily refer to the gloal optimum.
+Sometimes, one may be interested in knowing maximal solutions to understand why his or her programs are trapped in a local minimum.
+In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed in the previous sections; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
 Instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017}.
@@
 $I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-For the problem of finding the MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
+If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
 The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
@@
         s_vx_v & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
-        1-s_v& otherwise.\\
+        1-s_v& \text{otherwise}.\\
     \end{cases}
@@
 With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
+Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
 
@@
 
-One can see the average degree of a tensor is increase.
+One can see that the average degree of a tensor is increased.
 The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
 However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
-Let us consider the example in~\Sec{eg:tensorcontraction}, its corresponding tensor network structure for computing maximal independent sets now becomes:
 

### 2021-09-12 paper/paper.tex
small revision on section 5 and 6

@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
-As will be shown bellow, this algebra can also be extended to enumerate suboptimal solutions.
+As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
 
@@
 
-This sets algebra can serve as the coefficients in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
+This set algebra can serve as the first element in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
 or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
@@
 %In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
-\red{Can we also enumerate all maximal independent sets by combining with \Eq{eq:maximal} or enumerate suboptimal solutions by combining with the truncated polynomial?}
-\blue{now?}
-
-Although the above discussion is in the context of the the MIS problem, we can also combine the above algebras with the maximal independence network in \Eq{eq:maximal} to enumerate or sample maximal independent sets,
-as well as other problems in \App{app:otherproblems} for configuration enumeration and sampling.
+
+% Although the above discussion is in the context of the MIS problem, we can also combine the above algebras with the maximal independence network in \Eq{eq:maximal} to enumerate or sample maximal independent sets,
+% as well as other problems in \App{app:otherproblems} for configuration enumeration and sampling.
 
@@
 Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
-Let the gradient mask for $C$ being $\overline C$, the back-propagation rule for gradient masks reads
+Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
 \begin{equation}

### 2021-09-12 paper/paper.tex
add matlab plotting scripts back

--- 2021-09-11 paper/paper.tex
@@
 \begin{abstract}
-We introduce a new approach to compute various properties of independent sets by encoding the problems and the graph into tensor networks with different tensor element algebra.
-The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
-Although the computational complexity inevitably scales exponentially with the graph size, our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
-At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
+We introduce a new approach to compute various properties of independent sets by encoding the problems into tensor networks with different tensor element algebra.
+The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and enumeration of the maximum independence set configurations.
+Although the computational complexity inevitably scales exponentially with the graph size, the performance of our method using tensor network contraction with generic programming is on par or outperforms state-of-the-art, sophisticated methods;
+on the other hand, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
@@
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms and dynamic programming.
-Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}.
+Naive exhaustive search for the MIS requires time $O(2^{|V|})$. More efficient exact algorithms include the branching algorithms and dynamic programming.
+Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^n n ^{O(1)}$~\cite{Xiao2017}.
 Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
@@
 map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}.
-Besides the standard problem of finding the independence number and an MIS, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
-independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent set configurations.
+Besides the standard MIS problem, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
+independence polynomial, maximal independence polynomial, and enumeration of optimal and sub-optimal configurations.
 Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 Our approach does not necessarily provide a better time complexity compared to dynamic programming,
-but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties on CPUs and GPUs, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
+but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts.
+We benchmark our algorithms, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
 Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant,
@@
 $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
-where $i,j,k$ in the output tensor are open edges (note that $j$ is not an open edge and thus summed over).
-Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
+where $i,j,k$ in the output tensor are open edges.
+Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges and open circles to denote open edges.
 
@@
 \section{Generic programming}\label{sec:generic}
-In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
-the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
-Owning to the development of modern compiling technology, we no longer need to limit our imagination to standard number types.
-One of the key concepts that push the technology forward is called generic programming:
+In previous works combining tensor network and combinatoric problems~\cite{Kourtis2019,Biamonte2017},
+the elements in tensor networks are limited to regular number types such as floating point numbers and integers.
+As the development of modern compiling technology, we do not need to limit our imaginations to regular number types anymore.
+The key technology playing the role is called the generic programming:
 
@@
 
-This definition of generic programming contains two major aspects: a single program for the general setting and efficiency.
-To understand the first aspect, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
-One can easily write a function for standard number types that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
-Generic programming does not require $x$ to be a standard number type,
-instead it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
-In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
-The second aspect is about performance. For dynamically typed languages such as Python,
-one can easily write very general codes, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two numpy arrays with python objects as elements is much slower than statically typed languages such as C++ and Julia~\cite{Bezanson2012}.
-C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatch.
-When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.
-A myriad of optimizations can be done during the compilation, such as inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
+This definition of generic programming contains two major pieces, one is a single program for the general setting, and another is about efficiency.
+To understand the first point, suppose we want to write a function to take the power of an element $f(x, n) := x^n$.
+One can easily write a function for regular numbers that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
+A generic programmer does not assume $x$ being a regular number type,
+instead it treats $x$ as an element with an associative multiplication operation $\odot$ and multiplicative identity $\mymathbb{1}$.
+In such a way, when the program takes a matrix as input, it computes the matrix power without extra efforts.
+The second point about performance. For dynamic typed languages like Python,
+one can easily write very general codes, however, the efficiency is not guaranteed.
+Imagine the speed of computing the matrix multiplication between two numpy arrays with python objects as elements.
+The generic programming that we want to discuss is those in static types languages like C++, and Julia~\cite{Bezanson2012}.
+C++ uses templates for generic programming while Julia has just in time compiling and multiple dispatch.
+When they ``sees'' a new input type, the compiler recompiles the generic program for the new type.
+A lot optimization can be done during the compiling, like inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
 In Julia, these inlined arrays can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
 
-This motivates us to think about what is the most general element type that is allowed in a tensor network contraction program.
-We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
+This leads us to think about what is the most general element type that allowed in a tensor network contraction program.
+Our finding is: as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result is contraction order independent.
 A commutative semiring is a semiring with its multiplication operation being commutative, while a semiring is a ring without additive inverse.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for any arbitrary three elements $a, b, c \in R$.
+To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for arbitrary three elements $a, b, c \in R$.
 \begin{align*}
@@
 In the following sections, we show how to compute the independence polynomial,
-the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent set configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
 Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.
@@
 without which the largest enumeratible size is only $150$ with 32G memory while being one order slower.
+All these computing times have strong correlation with the tree width,
+while the computing times of configurations enumeration also depends on the size of target configuration space.
 

### 2021-09-12 paper/figures/examples.m

@@ -1,0 +1,50 @@
+%% load independence polynomial for fully-filled lattice
+
+data_SG = load_full_lattice('../../data/independence_polynomial_square_grid/independence_polynomial_square_lattice', (10:30)');
+data_K = load_full_lattice('../../data/independence_polynomial_kings_graphs/independence_polynomial_diagonal_coupled', (10:28)');
+
+
+
+%% functions
+function data = load_full_lattice(file_string, L_ind)
+data = struct;
+for ind = 1:numel(L_ind)
+    L = L_ind(ind);
+    fid = fopen(sprintf([file_string, '_n%d.dat'],L));
+    ind_poly = sym(textscan(fid, '%s'));
+    fclose(fid);
+    
+    no_ind_sets = sum(ind_poly);
+    entropy_constant = double(no_ind_sets^(1/L^2));
+    
+    data(ind).ind_poly = ind_poly;
+    data(ind).L = L_ind(ind);
+    data(ind).no_ind_sets = no_ind_sets;
+    data(ind).entropy_constant = entropy_constant;
+end
+end
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2021-09-12 paper/paper.tex
editing the benchmark section and adding comments

--- 2021-09-12 paper/paper.tex
@@
 \end{minipage}
+\red{we should include maximal independence polynomial and counting, enumeration in this table as well.}
 \end{table}
@@
 and its CUDA version on a GPU Tesla V100.
-The results are shown in Figure~\ref{fig:benchmark}.
-The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
+The results are summarized in Figure~\ref{fig:benchmark}.
+The type of graphs we used for benchmarks here are random 3 regular graphs, a typical type of sparse graphs that has a small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
 
@@
     \caption{Benchmark results for computing different properties of independent sets on a random three regular graph with different tensor element types.
-    (b) is the computing time for computing maximum independent set size, number of independent sets and suboptimal sets.
-    (c) is the computing time for independence polynomials with different approaches.
-    (d) is the computing time for finding all configurations and a single configuration, with or without bounding.
+\red{for each graph size, is there only one graph?} (a) treewidth versus the number of vertices for the benchmarked graphs.
+    (b) The computing time for calculating the independence number and for counting of the number of independent sets, the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
+    (c) The computing time for calculating the independence polynomials with different approaches.
+    (d) The computing time for enumeration problems, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
+    \red{suggestions for the figure: 1.
+the legend seems to overlap the lines, especially the large subfigure.
+Not sure what's a better way to include the legend there.
+2.
+I see you guys don't typically use markers.
+We typically use markers to distinguish the different lines, as well as using the color.
+Especially, for some journals, there is a physical non-color copy, so some requires the figures to be understandable without colors.}
     }
@@
 
-Among the benchmarks shown in \Fig{fig:benchmark}, computing \texttt{max size (CPU)},
-\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions,
-hence they are relatively faster comparing to other methods in the same category.
-Only algebras requiring dynamic sized structures can not be computed on GPU, here are polynomial algebra for computing independence polynomial and set algebra for enumerating configurations.
-When computing the independence polynomial, the finite field approach is the only method without round off error that can run on GPU.
-To enumerate the MISs, the technique to bound the enumeration space is important,
-without which the largest enumeratible size is only $150$ with 32G memory while being one order slower.
+The computations shown in \Fig{fig:benchmark} include \texttt{max size} (independence number, $\alpha(G)$), \red{we can consider changing `max size' to `ind number', but I am okay with both}
+ \texttt{total counting} (total number of independent sets) \red{should we change total size to total counting here, since max size meant max size of the set}, 
+ \texttt{max counting} (counting of MISs), 
+ \texttt{max2 counting} (counting of independent sets having a size $\alpha(G)$ or $\alpha(G)-1$), \red{we can consider changing `max counting' and `max2 counting' to `MIS counting' and `MIS and MIS-1 counting', but I am okay with both notations}
+ \texttt{IDP} (independence polynomial), 
+ \texttt{single MIS} (find one MIS configuration), 
+ \texttt{single MIS (bounding)} (find one MIS configuration including the bounding of enumeration space), \texttt{all MIS} (enumerate all MIS configurations), 
+\texttt{all MIS (bounding)} (enumerate all MIS configurations including the bounding of enumeration space),
+\texttt{all MIS and MIS-1} (enumeration of all independent sets having a size $\alpha(G)$ or $\alpha(G)-1$),
+\texttt{all IS} (enumeration of all independent sets).
+\red{Jinguo, should we include maximal independence polynomial and enumeration of all maximal independent sets as well? I think that will make the benchmark more complete.}
+
+Among the benchmarks, computing \texttt{max size (CPU)},
+\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions, and hence 
+they are faster comparing to non-BLAS methods in the same category.
+Only algebras requiring dynamic sized structures cannot be computed on GPU, which includes the polynomial algebra for computing the independence polynomial and the set algebra for enumerating configurations.
+When computing the independence polynomial, the finite field approach is the only method that does not incur round-off errors and that can be run on a GPU.
+To enumerate the MISs, the technique to bound the enumeration space is indispensible,
+without which the largest enumerable size is about $150$ vertices with 32G memory while also being one order-of-magnitude slower.
+All these computing times have a strong correlation with the treewidth, 
+and the computing times of configuration enumeration also depend on the size of the target configuration space.
 

### 2021-09-12 paper/paper.tex
update paper

--- 2021-09-12 paper/paper.tex
@@
 The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
-Although the computational complexity inevitably scales exponentially with the graph size, our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
+Although the computational complexity inevitably scales exponentially with treewidth of the graph, our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
 At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
@@
 Besides the standard problem of finding the independence number and an MIS, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
-independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent set configurations.
+independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent sets.
 Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 $C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
-where $i,j,k$ in the output tensor are open edges (note that $j$ is not an open edge and thus summed over).
+where $i,j,k$ in the output tensor are open edges (note that $l$ is not an open edge and thus summed over).
 Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
@@
 In the following sections, we show how to compute the independence polynomial,
-the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent set configurations of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent sets of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
 Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.
@@
 This is an iterative algorithm that tries different prime numbers $p$ until convergence.
-In each iteration, we contract the tensor networks to evaluate the polynomial for each $x_{i}$ on the finite field algebra ${\rm GF}(p)$.
+In each iteration, we contract the tensor networks to evaluate the polynomial for each $\chi_{i}$ on the finite field algebra ${\rm GF}(p)$.
 Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv A \pmod p$.
@@
 We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with $a(k) = (a_{k}, k)$, where the second element stores the largest exponent $k$ and the first element stores the corresponding coefficient $a_{k}$.
-From this, we can define a new algebra as \red{I've changed this, but I don't have strong feelings about this. We can certainly consider changing back.
-I thought this would be more consistent with the earlier notations and show how it's stored in the program as well.}
-\blue{I prefer the previous one, what about you @XG?}
-\begin{equation}
-\begin{split}
-    a(k) \oplus a(j) &= \begin{cases}
-        \left(a_k + a_j, \max(k,j) \right), & k = j \\
-        \left(a_j, \max(k,j) \right), & k < j \\
-        \left(a_k, \max(k,j) \right), & k > j
-    \end{cases}, \\
-    a(k) \odot a(j) &= (a_k a_j, k+j) \\
-    \mymathbb{0} &= (0, -\infty)\\
-    \mymathbb{1} &= (1, 0). \label{eq:countingtropical}
-\end{split}
-\end{equation}
+From this, we can define a new algebra as
 %\begin{equation}
 %\begin{split}
-%    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
-%        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
-%        a_y\infty^{\max(x,y)}, & x < y\\
-%        a_x\infty^{\max(x,y)}, & x > y
+%    a(k) \oplus a(j) &= \begin{cases}
+%        \left(a_k + a_j, \max(k,j) \right), & k = j \\
+%        \left(a_j, \max(k,j) \right), & k < j \\
+%        \left(a_k, \max(k,j) \right), & k > j
 %    \end{cases}, \\
-%    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-%    \mymathbb{0} &= 0\infty^{-\infty}\\
-%    \mymathbb{1} &= 1\infty^{0}. \label{eq:countingtropical}
+%    a(k) \odot a(j) &= (a_k a_j, k+j) \\
+%    \mymathbb{0} &= (0, -\infty)\\
+%    \mymathbb{1} &= (1, 0). \label{eq:countingtropical}
 %\end{split}
 %\end{equation}
-% In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
-The algebra of the exponents becomes the max-plus tropical algebra: $k \oplus j = \max(k,j)$ and $k \odot j = k + j$~\cite{Maclagan2015, Moore2011}.
+\begin{equation}
+\begin{split}
+    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
+        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
+        a_y\infty^{\max(x,y)}, & x < y\\
+        a_x\infty^{\max(x,y)}, & x > y
+    \end{cases}, \\
+    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
+    \mymathbb{0} &= 0\infty^{-\infty}\\
+    \mymathbb{1} &= 1\infty^{0}. \label{eq:countingtropical}
+\end{split}
+\end{equation}
+In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
+The algebra of the exponents becomes the max-plus tropical algebra: $x \oplus y = \max(x,y)$ and $x \odot y = x + y$~\cite{Maclagan2015, Moore2011}.
 This algebra is the same as the one used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
@@
 
-This set algebra can serve as the first element in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
+This set algebra can serve as the coefficients in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
 or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
@@
 The combined operations become: 
-\begin{equation}
-\begin{split}
-    s(k) \oplus s(j) &= \begin{cases}
-        \left(s_k \cup s_j, \max(k,j) \right), & k = j \\
-        \left(s_j, \max(k,j) \right), & k < j \\
-        \left(s_k, \max(k,j) \right), & k > j
-    \end{cases}, \\
-    s(k) \odot s(j) &= (\{\sigma \lor^\circ \tau \, | \, \sigma \in s_k, \tau \in s_j\}, k+j) \\
-    \mymathbb{0} &= (\{ \}, -\infty)\\
-    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropicalset}
-\end{split}
-\end{equation}
 %\begin{equation}
 %\begin{split}
-%    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
-%        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
-%        s_y\infty^{\max(x,y)}, & x < y\\
-%        s_x\infty^{\max(x,y)}, & x > y
-%    \end{cases},\\
-%    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
-%    \mymathbb{0} &= \{\}\infty^{-\infty},\\
-%    \mymathbb{1} &= \{0^{\otimes |V|}\}\infty^{0},
+%    s(k) \oplus s(j) &= \begin{cases}
+%        \left(s_k \cup s_j, \max(k,j) \right), & k = j \\
+%        \left(s_j, \max(k,j) \right), & k < j \\
+%        \left(s_k, \max(k,j) \right), & k > j
+%    \end{cases}, \\
+%    s(k) \odot s(j) &= (\{\sigma \lor^\circ \tau \, | \, \sigma \in s_k, \tau \in s_j\}, k+j) \\
+%    \mymathbb{0} &= (\{ \}, -\infty)\\
+%    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropicalset}
 %\end{split}
 %\end{equation}
+\begin{equation}
+\begin{split}
+    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
+        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
+        s_y\infty^{\max(x,y)}, & x < y\\
+        s_x\infty^{\max(x,y)}, & x > y
+    \end{cases},\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+    \mymathbb{0} &= \{\}\infty^{-\infty},\\
+    \mymathbb{1} &= \{0^{\otimes |V|}\}\infty^{0}. \label{eq:countingtropicalset}
+\end{split}
+\end{equation}
 Clearly, the vertex tensor and edge tensor become

### 2021-09-12 paper/paper.tex

@@
 
-Among the benchmarks shown in \Fig{fig:benchmark}, computing \texttt{max size (CPU)},
-\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions,
-hence they are relatively faster comparing to other methods in the same category.
-Only algebras requiring dynamic sized structures can not be computed on GPU, here are polynomial algebra for computing independence polynomial and set algebra for enumerating configurations.
-When computing the independence polynomial, the finite field approach is the only method without round off error that can run on GPU.
-To enumerate the MISs, the technique to bound the enumeration space is important,
-without which the largest enumeratible size is only $150$ with 32G memory while being one order slower.
-All these computing times have strong correlation with the tree width,
-while the computing times of configurations enumeration also depends on the size of target configuration space.
+The computations shown in \Fig{fig:benchmark} include \texttt{max size} (independence number, $\alpha(G)$), \red{we can consider changing `max size' to `ind number', but I am okay with both}
+ \texttt{total counting} (total number of independent sets) \red{should we change total size to total counting here, since max size meant max size of the set}, 
+ \texttt{max counting} (counting of MISs), 
+ \texttt{max2 counting} (counting of independent sets having a size $\alpha(G)$ or $\alpha(G)-1$), \red{we can consider changing `max counting' and `max2 counting' to `MIS counting' and `MIS and MIS-1 counting', but I am okay with both notations}
+ \texttt{IDP} (independence polynomial), 
+ \texttt{single MIS} (find one MIS configuration), 
+ \texttt{single MIS (bounding)} (find one MIS configuration including the bounding of enumeration space), \texttt{all MIS} (enumerate all MIS configurations), 
+\texttt{all MIS (bounding)} (enumerate all MIS configurations including the bounding of enumeration space),
+\texttt{all MIS and MIS-1} (enumeration of all independent sets having a size $\alpha(G)$ or $\alpha(G)-1$),
+\texttt{all IS} (enumeration of all independent sets).
+\red{Jinguo, should we include maximal independence polynomial and enumeration of all maximal independent sets as well? I think that will make the benchmark more complete.}
+
+Among the benchmarks, computing \texttt{max size (CPU)},
+\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions, and hence 
+they are faster comparing to non-BLAS methods in the same category.
+Only algebras requiring dynamic sized structures cannot be computed on GPU, which includes the polynomial algebra for computing the independence polynomial and the set algebra for enumerating configurations.
+When computing the independence polynomial, the finite field approach is the only method that does not incur round-off errors and that can be run on a GPU.
+To enumerate the MISs, the technique to bound the enumeration space is indispensible,
+without which the largest enumerable size is about $150$ vertices with 32G memory while also being one order-of-magnitude slower.
+All these computing times have a strong correlation with the treewidth, 
+and the computing times of configuration enumeration also depend on the size of the target configuration space.
 

### 2021-09-13 paper/paper.tex
maximal benchmark update

@@
 
+\newcommand{\eqname}[1]{\stepcounter{equation}\tag{\theequation : #1}}
 %%%%%% Shortcut related
@@
 \begin{equation}
+    \eqname{PN}
     \begin{split}
@@
 \begin{equation}
+    \eqname{P1}
 \begin{split}
@@
     \mymathbb{0} &= 0\infty^{-\infty}\\
-    \mymathbb{1} &= 1\infty^{0}. \label{eq:countingtropical}
+    \mymathbb{1} &= 1\infty^{0}.
+\end{split}%& \text{\rlap{(P1)}}
+\label{eq:countingtropical}
+\end{equation}
+In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
+The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}.:
+\begin{equation}\eqname{T}
+    \begin{split}
+        x \oplus y &= \max(x,y)\\
+        x \odot y &= x + y\\
+        \mymathbb{0} &= -\infty\\
+        \mymathbb{1} &= 0.
     \end{split}
 \end{equation}
-In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
-The algebra of the exponents becomes the max-plus tropical algebra: $x \oplus y = \max(x,y)$ and $x \odot y = x + y$~\cite{Maclagan2015, Moore2011}.
 This algebra is the same as the one used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
@@
 \begin{equation}
+    \eqname{P2}
     \begin{split}
@@
 \begin{equation}
+\eqname{SN}
 \begin{split}
@@
 or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
-For example, to enumerate only the MISs, with the tropical algebra, we define $s(k) = (s_{k}, k)$, where the first element follows the algebra in \Eq{eq:set} and the second element follows the max-plus tropical algebra.
+For example, to enumerate only the MISs, with the tropical algebra, we define $s(k) = (s_{k}, k)$, where the coefficients follows the algebra in \Eq{eq:set} and the orders follows the max-plus tropical algebra.
 The combined operations become: 
@@
 \begin{equation}
+\eqname{P1+SN}
 \begin{split}
@@
 \begin{equation}
+\eqname{S1}
 \begin{split}
@@
     \caption{Benchmark results for computing different properties of independent sets on a random three regular graph with different tensor element types.
-\red{for each graph size, is there only one graph?} (a) treewidth versus the number of vertices for the benchmarked graphs.
+\red{for each graph size, is there only one graph?}\blue{yes} (a) treewidth versus the number of vertices for the benchmarked graphs.
     (b) The computing time for calculating the independence number and for counting of the number of independent sets, the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.

### 2021-09-14 paper/paper.tex
add maximal benchmark

@@
 \ra{1.3}
-        \begin{tabularx}{\textwidth}{bb}\toprule
+        \begin{tabularx}{\textwidth}{sb}\toprule
             \hline
             \textbf{element type}     & \textbf{purpose} \\
-            {real number}     & {counting all independent sets} \\
-            {tropical number} (\Eq{eq:countingtropical})    & {finding the independence number} \\
-            {tropical number with counting} (\Eq{eq:countingtropical})     & {finding the independence number and the number of MISs} \\
-            {tropical number with configurations} (\Eq{eq:singleconfig})     & {finding the independence number and one MIS} \\
-            {tropical number with sets} (\Eq{eq:countingtropicalset})    & {finding the independence number and enumeration of all MISs} \\
-            {polynomial} (\Eq{eq:polynomial})     & {computing the independence polynomial exactly} \\
-            {truncated polynomial} (\Eq{eq:max2poly})     & {counting MISs and independent sets of size $\alpha(G)-1$} \\
-            {complex number}     & {fitting the independence polynomial with fast Fourier transform} \\
-            {finite-field algebra (\Eq{eq:finitefield})} & {fitting the independence polynomial exactly using number theory} \\
+            {$\mathbbm{R}$}     & {real number for counting all independent sets} \\
+            {$\mathbbm{C}$}     & {complex number for fitting the independence polynomial with fast Fourier transform} \\
+            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {number on finite field algebra for fitting the independence polynomial exactly using number theory} \\
+            {T} (\Eq{eq:tropical})    & {tropical number for finding the independence number} \\
+            {P1} (\Eq{eq:countingtropical})     & {polynomial truncated to largest order, i.e. the tropical number with counting field for finding the independence number and the number of MISs} \\
+            {P2} (\Eq{eq:max2poly})     & {counting MISs and independent sets of size $\alpha(G)-1$} \\
+            {PN} (\Eq{eq:polynomial})     & {computing the independence polynomial exactly} \\
+            {P1+S1}     & {replacing the counting field in P1 to configuration sampler defined in $\Eq{eq:singleconfig}$ for finding the independence number and one MIS} \\
+            {P1+SN} (\Eq{eq:countingtropicalset})    & {replacing the counting field in P1 to configuration sampler defined in $\Eq{eq:set}$ for finding the independence number and enumeration of all MISs} \\
             \bottomrule
@@
         \mymathbb{1} &= 0.
-    \end{split}
+    \end{split}\label{eq:tropical}
 \end{equation}
@@
 and the computing times of configuration enumeration also depend on the size of the target configuration space.
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
+    \caption{Benchmark results for computing different properties of maximal independent sets on a random three regular graph with different tensor element types.
+    (a) treewidth versus the number of vertices for the benchmarked graphs. 
+    (b) The computing time for calculating the number of independent sets and enumerate all MISs.
+    }
+    \label{fig:benchmark-maximal}
+\end{figure}
+
+We also benchmarked our method with the Bron-Kerbosch method to enumerate and count maximal independent sets in \Fig{fig:benchmark-maximal}.
+We can see the tree width of this tensor network is nearly doubled comparing with the one for computing independent sets, hence only small graphs can be benchmarked.
+The time for the tensor netwrok approach and Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
+while the counting can be much faster.
 

### 2021-09-15 paper/paper.tex
update benchmark script

@@
 \red{we should include maximal independence polynomial and counting, enumeration in this table as well.}
+\blue{I do not think so. Network structure and element types are two degree of freedoms,
+maximal IS is different network structure. We can use the above algebra in any network structure.}
 \end{table}
@@
 \red{for each graph size, is there only one graph?}\blue{yes} (a) treewidth versus the number of vertices for the benchmarked graphs.
+    Legends are the data types that we used in the computation, one can find the corresponding computational task in \Tbl{tbl:generictypes}.
     (b) The computing time for calculating the independence number and for counting of the number of independent sets, the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
@@
 Especially, for some journals, there is a physical non-color copy, so some requires the figures to be understandable without colors.}
+    \blue{If we use markers, the data poitns are too dense. I prefer not adding markers, not much people read papers with kindle or on paper.}
+    \blue{I used a smaller fontsize, there are still some overlaps. Does it look better (or worse) now?}
     }
@@
 
-The computations shown in \Fig{fig:benchmark} include \texttt{max size} (independence number, $\alpha(G)$), \red{we can consider changing `max size' to `ind number', but I am okay with both}
- \texttt{total counting} (total number of independent sets) \red{should we change total size to total counting here, since max size meant max size of the set}, 
- \texttt{max counting} (counting of MISs), 
- \texttt{max2 counting} (counting of independent sets having a size $\alpha(G)$ or $\alpha(G)-1$), \red{we can consider changing `max counting' and `max2 counting' to `MIS counting' and `MIS and MIS-1 counting', but I am okay with both notations}
- \texttt{IDP} (independence polynomial), 
- \texttt{single MIS} (find one MIS configuration), 
- \texttt{single MIS (bounding)} (find one MIS configuration including the bounding of enumeration space), \texttt{all MIS} (enumerate all MIS configurations), 
-\texttt{all MIS (bounding)} (enumerate all MIS configurations including the bounding of enumeration space),
-\texttt{all MIS and MIS-1} (enumeration of all independent sets having a size $\alpha(G)$ or $\alpha(G)-1$),
-\texttt{all IS} (enumeration of all independent sets).
+The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
+computing independence polynomial (panel c) and enumerating and sampling independent sets (panel d).
+\blue{I cleaned up this paragraph, because one can check the table \Tbl{tbl:generictypes} now.}
 \red{Jinguo, should we include maximal independence polynomial and enumeration of all maximal independent sets as well? I think that will make the benchmark more complete.}
-
-Among the benchmarks, computing \texttt{max size (CPU)},
-\texttt{total size (CPU)}, \texttt{total size (GPU)}, \texttt{IDP (FFT) (CPU)}, \texttt{IDP (FFT) (GPU)} and \texttt{single configuration (bounding) (CPU)} can utilize fast BLAS functions, and hence 
+\blue{added a new paragraph.}
+Among the benchmarks, computing \texttt{T (CPU)},
+\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions, and hence 
 they are faster comparing to non-BLAS methods in the same category.
-Only algebras requiring dynamic sized structures cannot be computed on GPU, which includes the polynomial algebra for computing the independence polynomial and the set algebra for enumerating configurations.
-When computing the independence polynomial, the finite field approach is the only method that does not incur round-off errors and that can be run on a GPU.
+Only algebras requiring dynamic sized structures cannot be computed on GPU, which includes \texttt{PN} and \texttt{SN}.
+When computing the independence polynomial, the finite field (GF$(p)$) approach is the only method that does not incur round-off errors and that can be run on a GPU.
 To enumerate the MISs, the technique to bound the enumeration space is indispensible,
@@
 We also benchmarked our method with the Bron-Kerbosch method to enumerate and count maximal independent sets in \Fig{fig:benchmark-maximal}.
-We can see the tree width of this tensor network is nearly doubled comparing with the one for computing independent sets, hence only small graphs can be benchmarked.
-The time for the tensor netwrok approach and Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
-while the counting can be much faster.
+Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
+the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
+The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
+while the tensor network does counting much more efficiently.
+The implementation of Bron-Kerbosch algorithm is from the package LightGraphs~\cite{LightGraphs},
+due to the memory limit, this algorithm stops working at size $70$ and above.
 

### 2021-09-15 paper/figures/plot.py

@@ -14,7 +14,7 @@ class PLT(object):
         nw = [(10, 3), (20, 4), (30, 6), (40, 7), (50, 8), (60, 10), (70, 11), (80, 11), (90, 15), (100, 15),
             (110, 15), (120, 18), (130, 17), (140, 16), (150, 21), (160, 20), (170, 22), (180, 24), (190, 26), (200, 25)]
         ns = [x[0] for x in nw]
-        FS = 10
+        FS = 8
         with DataPlt(filename="fig1.%s"%tp, figsize=(10,6)) as dp:
             ax = plt.subplot(221)   # treewidth
             cornertex("(a)", ax, offset=(0,0))
@@ -33,7 +33,7 @@ class PLT(object):
             plt.yscale("log")
             plt.xlabel("number of vertices, $|V|$")
             plt.ylabel("time/s")
-            plt.legend(loc="upper left", fontsize=FS)
+            plt.legend(loc="upper left", fontsize=FS, ncol=2)
             plt.ylim(1e-3,3e3)
 
             ax = plt.subplot(223)   # IDP

### 2021-09-15 paper/paper.tex
update paper

@@
 \begin{abstract}
-We introduce a new approach to compute various properties of independent sets by encoding the problems and the graph into tensor networks with different tensor element algebra.
+We introduce a new approach to compute various properties of independent sets by encoding the problems and graphs into tensor networks with different tensor element algebra.
 The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
@@
 \blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009},
-branching algorithm~\cite{Tarjan1977,Robson1986},
 two motivations of computing independence polynomial: 1. Lee-Yang zero~\cite{Lee1952,Yang1952}, 2. Lov{\'a}sz local lemma~\cite{Scott2005}.
@@
 The problem of finding an independent set of the largest possible size, the maximum independent set (MIS), is a paradigmatic NP-complete problem~\cite{Hastad1996}.
-The size of the MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$.
-
+The size of an MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$. 
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms and dynamic programming.
+Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms~\cite{Tarjan1977,Robson1986} and dynamic programming.
 Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}.
@@
 The independent set problem is closely related to the clique problem and the vertex cover problem~\cite{Moore2011};
-more concretely, an MIS of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
+more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
 and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
+In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
 Together, these problems find a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
@@
 In this work, we introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
-We map different problems into generic tensor network contraction with various tensor element algebra.
-Our approach does not necessarily provide a better time complexity compared to dynamic programming,
+We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
+Our approach does not necessarily provide a better time complexity compared to dynamic programming considering the fact that the tensor network contraction can be regarded as a type of concrete implementation of dynamic programming,
 but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties on CPUs and GPUs, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021}.
+We benchmark our algorithms by computing various independent set properties on CPUs and GPUs, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
 Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant,
@@
 In the standard notation, each index can appear at most twice. A tensor network consists of multiple tensors performing the sum-product operation,
-i.e., contraction, and the tensor network can be represented as a multigraph with open edges by viewing a tensor as a vertex,
+i.e., contraction, and it can be represented as a multigraph with open edges by viewing a tensor as a vertex,
 a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
@@
 \begin{example}
-   A tensor network $C_{il} = A_{ijkm} B_{kml} V_{j}$ has the following multigraph representation.
+   A standard tensor network $C_{il} = A_{ijkm} B_{kml} V_{j}$ has the following multigraph representation.
 
@@
 
-One can generalize the tensor network notation by removing the restriction that each index can appear at most twice.
-The notation can be considered as a generalized Einstein notation, which is sometimes called einsum,
+In the main text, we use a generalized tensor network notation that an index can appear arbitrary times.
+It is sometimes called einsum,
 sum-product network or factor graph~\cite{Bishop2006} in different contexts.
-The graphical representation of a tensor network we use in this paper is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
+The graphical representation of a generlized tensor network is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
+These two notations are equivalent in the representation power because one can easily translate a generalized tensor network to the standard notation by adding identity tensors denoted as $\delta$ tensors.
+However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
 
@@
 Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
+It's equivalent standard notation is $C_{ijk} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$.
 
@@
 
-In the main text, we use the generalized tensor network notation.
-The generalized tensor network can be easily translated to the standard notation by adding identity tensors denoted as $\delta$ tensors.
-The example above can be written as $C_{ijk} = A_{jkm} B_{mil} V_{jm} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$ in the standard notion.
-However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
-
 \section{Generic programming}\label{sec:generic}
@@
 
-The independence polynomial is closely related to the matching polynomial, the clique polynomial, and the vertex cover polynomial.
+The independence polynomial is closely related to the matching polynomial, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013}.
 In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{Levit2005}.
@@
 In the implementation of the algorithm, we benefit from recent advances in tensor network contraction,
-where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a good heuristic order~\cite{Gray2021, Pan2021}.
+where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
 A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
@@
 \end{equation}
+One way to efficiently evaluate the multiplication operation is to use the convolution theorem~\cite{Schonhage1971}.
 We can see these operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
@@
 By contracting the tensor network with the polynomial type, the final result is the exact representation of the independence polynomial.
-One way to efficiently evaluate the multiplication operation is to use the convolution theorem~\cite{Schonhage1971}, but this approach suffers from a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients.
-
+However, using polynomial numbers suffers from a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random values of $x_{i}$ and $y_{i} = I(G,x_{i})$.
@@
 With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-This is an iterative algorithm that tries different prime numbers $p$ until convergence.
-In each iteration, we contract the tensor networks to evaluate the polynomial for each $\chi_{i}$ on the finite field algebra ${\rm GF}(p)$.
-Let use denote the results as $Y$, then we solve a linear equation $Y = X A_p$ using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv A \pmod p$.
+This is an iterative algorithm that iterates over a sequence of large prime numbers until convergence.
+In each iteration, we contract the tensor networks to evaluate the polynomial for each variable $x = \chi_{i}$ on ${\rm GF}(p)$ and denote the outputs as $Y$.
+Then we solve a linear equation $Y = X A_p$ using the gaussian elimination to find the coefficient modulo $p$, $A_p \equiv A \pmod p$.
 Finally we apply the Chinese remainder theorem to get $A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
 If this number does not change compared with the previous iteration, it indicates the result has converged.
-All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem.
+All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
 In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transform.
@@
 \subsection{Maximal independence polynomial}
-Sometimes, one may be interested in knowing maximal solutions to understand why his or her programs are trapped in a local minimum.
-In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed in the previous sections; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-Instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017}.
+Sometimes, one may be interested in knowing maximal solutions to understand why his or her \blue{Is this a convention to use both "he" and "her"?} program is trapped in a local minimum.
+Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
  Concretely, it is defined as
@@
 \end{equation}
-where the lower-order terms vanish.
-We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with $a(k) = (a_{k}, k)$, where the second element stores the largest exponent $k$ and the first element stores the corresponding coefficient $a_{k}$.
+where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
 From this, we can define a new algebra as
@@
 \end{equation}
-In the program, we only need to store the exponent $x$ and the corresponding coefficient $a_x$ initialized to $1$. 
+When we are only interested in knowing the MIS size, we can drop the counting field.
 The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}.:
@@
         \mymathbb{1} \\
-        (1,1)
+        \infty
     \end{matrix}\right),   
@@
 \section{Enumeration of configurations and enumeration bounds}
-\subsection{Enumeration of MIS configurations}
+\subsection{Enumeration of independent sets}
 The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973, Eppstein2010, Johnson1988}, including,

### 2021-09-15 paper/paper.tex
update

@@
     &\{00001\} \oplus \{01110, 01000\} = \{01110, 01000\} \oplus \{00001\} = \{00001,01110, 01000\}\\
-    &\{00001\} \oplus \{\} = \{\}\\
+    &\{00001\} \oplus \{\} = \{00001\}\\
 &\\
@@
 
-The variable $x_{i}$ in the vertex tensor is initialized to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
+To enumerate all independent sets, 
+we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
 The vertex and edge tensors are thus
@@
         \mymathbb{1} \\
-        \left({\{\boldsymbol{e}_{i}\}, 1} \right)
+        \{\boldsymbol{e}_{i}\}\infty^1
     \end{matrix}\right),   
@@
 \end{equation}
-where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking one with a smaller integer value.
+where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking the one with a smaller integer value.
 %In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
@@
 The results are summarized in Figure~\ref{fig:benchmark}.
-The type of graphs we used for benchmarks here are random 3 regular graphs, a typical type of sparse graphs that has a small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
+The graphs that we use in benchmarks are random 3 regular graphs, a typical type of sparse graphs that has a small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
 
@@
 they are faster comparing to non-BLAS methods in the same category.
-Only algebras requiring dynamic sized structures cannot be computed on GPU, which includes \texttt{PN} and \texttt{SN}.
-When computing the independence polynomial, the finite field (GF$(p)$) approach is the only method that does not incur round-off errors and that can be run on a GPU.
-To enumerate the MISs, the technique to bound the enumeration space is indispensible,
-without which the largest enumerable size is about $150$ vertices with 32G memory while also being one order-of-magnitude slower.
+Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e. \texttt{PN} and \texttt{SN}.
+Fourier transformation based method is the fastest in computing the independence polynomial,
+while the finite field (GF$(p)$) approach is the only method that does not incur round-off errors and that can be run on a GPU.
+In the benchmark of enumerating the MISs (panel d), one can see the technique to bound the enumeration space improves the performance for more than one order.
+Bounding can also reduce the memory usage significantly, without which the largest enumerable size is about $150$ vertices on a 32G memory device.
 All these computing times have a strong correlation with the treewidth, 
@@
 Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
-The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem and $k$-coloring problem to a tensor network.
-Here, we want to discuss more from the programming perspective.
-We show some of the Julia language~\cite{Bezanson2012} implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
-What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
-The style that we program is called generic programming,
-meaning one can feed different data types into the same program, and the program will compute the result with a proper performance.
-In C++, one can use templates for such a purpose.
-We chose Julia because its just-in-time compiling is very powerful that it can generate fast code dynamically for users.
-Elements of fixed size, such as the finite-field algebra, truncated polynomial, tropical number and tropical number with counting or configuration field described in this paper can all be inlined in an array.
-Furthermore, these inlined arrays can be uploaded to GPU devices for faster computation with generic matrix multiplication implemented in CUDA.jl~\cite{Besard2018}.
+The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
+We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
+The full code base can be found in ~\cite{GraphTensorNetworks}.
+%What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
+%The style that we program is called generic programming,
 
 \section*{Acknowledgments}
-We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network, his code plays a crucial role in our code base.
-We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions,
-their questions are the driving force of this project.
-Thank Chris Elord for helping us writing the fastest matrix multiplication libary for GEMM, TropicalGEMM.jl, he is a remarkable guy!
+We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network.
+We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions about independent sets,
+their questions are one of the driving forces of this project.
+Thank Chris Elord for helping us writing the fastest matrix multiplication libary for tropical numbers, TropicalGEMM.jl, he is a remarkable guy!
 \blue{funding information}

### 2021-09-16 paper/paper.tex
fix appendix ABC

@@
 \begin{description}
-	\item[OMEinsum] a package for the \texttt{einsum} function,
-	\item[OMEinsumContractionOrders] a package for finding the optimal contraction order for the \texttt{einsum} function \\ \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl},
-	\item[TropicalGEMM] a package for efficient tropical matrix multiplication (compatible with OMEinsum),
-	\item[TropicalNumbers] a package providing tropical number types and tropical algebra, one o the dependency of TropicalGEMM,
-	\item[LightGraphs] a package providing graph utilities, like random regular graph generator,
-	\item[Polynomials] a package providing polynomial algebra and polynomial fitting,
-	\item[Mods and Primes] packages providing finite field algebra and prime number generators.
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
+    \texttt{OMEinsumContractionOrders} implements state of art algorithms for finding the optimal contraction order for the an tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
+	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
+	\item[\href{https://github.com/JuliaGraphs/LightGraphs.jl}{LightGraphs}] is a package providing graph utilities, like random regular graph generator,
+	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
+	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
 \end{description}
@@
 \begin{lstlisting}
-pkg> add OMEinsum LightGraphs Mods Primes FFTW Polynomials TropicalNumbers
+pkg> add OMEinsum LightGraphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
 \end{lstlisting}
 
-It may surprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding and sparsity related parts,
+It may surprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding algorithm,
 all are contained in this appendix. After installing required packages, one can open a Julia REPL and copy the following code into it.
@@
 
-In the above examples, the configuration enumeration is very slow, one should use the optimal MIS size for bounding as described in the main text.
-We will not show any example about implementing the backward rule here because it has approximately 100 lines of code.
-Please checkout our GitHub repository \href{https://github.com/Happy-Diode/NoteOnTropicalMIS}{https://github.com/Happy-Diode/NoteOnTropicalMIS}.
-
-\section{Why not introducing \texorpdfstring{$\delta$} tensors}\label{app:tensorbad}
+Please checkout our GitHub repository for the full featured version:
+
+\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}
+
+\section{Why not using the standard tensor network notations}\label{app:tensorbad}
+As we have mentioned in the main text,
+a standard tensor network notation inevitably introduces $\delta$ tensors to encode some graph problems.
+A $\delta$ tensor of rank $d$ is defined as
+\begin{equation}
+    \delta_{i_1, i_2,\ldots,i_d} = \begin{cases}
+        1, & i_1=i_2=\ldots =i_d,\\
+        0, & \text{otherwise}.
+    \end{cases}
+\end{equation}
 
@@
 
-Its traditional tensor network representation with $\delta$ tensors is
+Its standard tensor network representation includes a $\delta$ tensors on each vertex, so its graphical representation is as bellow.
 
@@
 \end{tikzpicture}}
-where a small circle on an edge is a diagonal tensor.
+Here, we use a small circle on a vertex to represent a diagonal $\delta$ tensor.
 Its rank is $8$ in the bulk.
-If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor is approximately $3L$, giving a space complexity $\approx 2^{3L}$.
+If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has a rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
 If we treat it as the following generalized tensor network
@@
 \end{tikzpicture}}
-where we use different colors to distinguish different hyperedges.
-Now, the vertex tensor is always rank $1$.
-With the same naive contraction order, we can see the maximum intermediate tensor is approximately of size $2^L$ by counting the colors.
+Here, we use different colors to distinguish different hyperedges.
+The vertex tensor is always rank $1$ in this representation.
+Again, if we contract this tensor network in the columnwise contraction order, we can see the maximum intermediate tensor has rank $\sim L$ by counting the colors.
 
 \section{Generalizing to other graph problems}\label{app:otherproblems}
-There are some other graph problems that can be encoded in a tensor network.
+There are some other graph problems that can be encoded to a tensor network.
 To understand its representation power, it is a good starting point to connect it with dynamic programming because
 a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-Courcelle’s theorem~\cite{Courcelle1990,Barr2020} states that a problem quantified by monadic second order logic (MSO) on a graph with bounded treewidth $k$ can be solved in linear time with respect to the graph size.
-Dynamic programming is a traditional approach to attack a MSO problem, it can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
-We mentioned in the main text that tensor network has nice analytic property make it easier for generic programming.
-The cost is, the tensor network is less expressive than dynamic programming,
+Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small tree width efficiently~\cite{Courcelle1990,Barr2020}.
+It can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
+The graph problem can be expressed in the tensor network language is clearly much less than that can be expressed by dynamic programming.
+For example, it is hard to determine whether a collection of vertices forms a path in a graph using the tensor network language, while this problem is MSO definable.
+As a gain, a tensor network has a nicer analytic property, which makes contraction order optimization, generic programming and utilizing BLAS libaries very convenient.
 %\iffalse
@@
 %\fi
-However, that are still some other problems that can be expressed in the framework of generic tensor network.
+In the following, we introduce some other problems that can be expressed by a tensor network.
 \subsection{Matching problem}
@@
 where $k$ is the number of matches, and coefficients $c_k$ are the corresponding counting.
-
 We define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
 \begin{equation}
-    W_{v\rightarrow n_1, v\rightarrow n_2, \ldots, v\rightarrow n_{d(v)}} = \begin{cases}
-        1, & \sum_{i=1}^{d(v)} v\rightarrow n_i \leq 1,\\
+    W_{\langle v, n_1\rangle, \langle v, n_2 \rangle, \ldots, \langle v, n_{d(v)}\rangle} = \begin{cases}
+        1, & \sum_{i=1}^{d(v)} \langle v, n_i \rangle \leq 1,\\
         0, & \text{otherwise},
@@
 \begin{equation}
-    B_{v\rightarrow w} = \begin{cases}
-    1, & v \rightarrow w = 0 \\
-    x, & v \rightarrow w = 1.
+    B_{\langle v, w\rangle} = \begin{cases}
+    1, & \langle v, w \rangle = 0 \\
+    x, & \langle v, w \rangle = 1.
 \end{cases}
 \end{equation}
-Here, we use bond index $v \rightarrow w$ to label tensors.
+Here, we use bond index $\langle v, w \rangle \in \{0, 1\}$ ($\langle v, w \rangle$ and $\langle w,v\rangle$ are equivalent) to label tensors,
+where $1$ means two vertices of an edge are matched, $0$ means otherwise.
 
@@
 The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
-By designing generic types as tensor elements, one should be able to get all possible colorings.
-It is straight forward to define the k-coloring problem on edges hence we will not discuss the detailed construction here.
+By designing generic types as tensor elements, one can get all possible colorings.
+Similarly, one can define the k-coloring problem on edges too.
 
@@
 \begin{equation}
-    B(x_{ij}) = \left(\begin{matrix}
-        1 & x_{ij}\\
-        x_{ij} & 1
+    B(x_{\langle i, j\rangle}) = \left(\begin{matrix}
+        1 & x_{\langle i, j\rangle}\\
+        x_{\langle i, j\rangle} & 1
     \end{matrix}\right).
 \end{equation}
-We can also define a polynomial about edges variables by setting $x_{ij} = x$,
-its $k$th coefficient is two times the number of configurations of cut size $k$.
+We can also define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,
+where its $k$th coefficient is two times the number of configurations of cut size $k$.
 
 \subsection{Set packing}
-Set packing the the hypergraph version of the maximum independent set problem, where each set corresponds to a vertex, each element corresponds to a hyperedge.
+Set packing is the hypergraph version of the maximum independent set problem, where each set corresponds to a vertex, each element corresponds to a hyperedge.
 To solve the set packing problem, we just remove the rank 2 restriction of an edge tensor

### 2021-09-16 paper/paper.tex
update appendix D

@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
-    \caption{Benchmark results for computing different properties of independent sets on a random three regular graph with different tensor element types.
-\red{for each graph size, is there only one graph?}\blue{yes} (a) treewidth versus the number of vertices for the benchmarked graphs.
+    \caption{Benchmark results for computing different properties of independent sets of a random three regular graph with different tensor element types.
+    The time in these plots only includes tensor network contraction process, without taking the just in time compiling time into account.
+    \red{for each graph size, is there only one graph?}\blue{yes}
+    (a) treewidth versus the number of vertices for the benchmarked graphs. 
     Legends are the data types that we used in the computation, one can find the corresponding computational task in \Tbl{tbl:generictypes}.
@@
 \section{Technical guide}\label{sec:technical}
+Before showing the codes,
+we want to introduce some Julia packages that playing important roles in our code base.
+
 \begin{description}
@@
         1, & v+w+\ldots+z\leq 1,\\
-        0, & otherwise
+        0, & \text{otherwise}.
     \end{cases}
@@
 Since the coefficients of the independence polynomial can range many orders of magnitude, the round-off errors in fitting can be significant if we use random floating point numbers for $x_{i}$.
-In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent overflow and round-off errors. Here, we give another method based on discrete Fourier transform.
+In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent integer overflow and round-off errors.
+One drawback of using finite field algebra is its matrix multiplication is less computational efficient compared with floating point matrix multiplication.
+Here, we give an alternative method based on discrete Fourier transform with controllable round off errors.
 Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
@@
 Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision in low independent set size region  ($r<1$) or high independent set size region ($r>1$).
+By choosing different $r$, one can obtain better precision in low independent set size region by choosing $r<1$ or high independent set size region by choosing $r>1$.
 

### 2021-09-19 paper/paper.tex
update

@@
 
+\subsubsection{Computing the Hamming distance statistics}
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
+    \caption{The statistics of Hamming distances between two MIS configurations for a specific three regular graph instance of size $200$.}
+    \label{fig:hamming}
+\end{figure}
+
 \section{Discussion and conclusion}
@@
 We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
-The full code base can be found in ~\cite{GraphTensorNetworks}.
+A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}.
 %What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.

### 2021-09-19 paper/figures/plot.py

@@ -11,8 +11,8 @@ import os
 
 class PLT(object):
     def fig1(self, tp="pdf"):  # independence polynomials
-        nw = [(10, 3), (20, 4), (30, 6), (40, 7), (50, 8), (60, 10), (70, 11), (80, 11), (90, 15), (100, 15),
-            (110, 15), (120, 18), (130, 17), (140, 16), (150, 21), (160, 20), (170, 22), (180, 24), (190, 26), (200, 25)]
+        nw = [(10, 3), (20, 4), (30, 4), (40, 5), (50, 8), (60, 8), (70, 8), (80, 10), (90, 13), (100, 13),
+            (110, 15), (120, 15), (130, 13), (140, 17), (150, 18), (160, 20), (170, 19), (180, 25), (190, 24), (200, 25)]
         ns = [x[0] for x in nw]
         FS = 8
         with DataPlt(filename="fig1.%s"%tp, figsize=(10,6)) as dp:
@@ -70,7 +70,7 @@ class PLT(object):
 
 
     def fig2(self, tp="pdf"):  # independence polynomials
-        nw = [(10, 6), (20, 8), (30, 10), (40, 11), (50, 16), (60, 17), (70, 17), (80, 21), (90, 27), (100, 26)]
+        nw = [(10, 6), (20, 8), (30, 9), (40, 11), (50, 16), (60, 17), (70, 16), (80, 20), (90, 26), (100, 26)]
         ns = [x[0] for x in nw]
         FS = 10
         with DataPlt(filename="fig2.%s"%tp, figsize=(8,3)) as dp:
@@ -97,6 +97,17 @@ class PLT(object):
             plt.legend(loc="upper left", fontsize=FS)
             plt.ylim(1e-3,3e3)
 
+            plt.tight_layout()
+
+    def fig3(self, tp="pdf", seed=3):  # independence polynomials
+        with DataPlt(filename="fig3.%s"%tp, figsize=(6,3)) as dp:
+            datafile = "../../democode/data/r3_n200_hamming_%d.txt"%seed
+            y = np.loadtxt(datafile)
+            n = 18
+            plt.bar(range(n), y[:n], lw=1.5, color="C4", ls="-")
+            plt.xticks(range(0,n+1,2))
+            plt.xlabel("Hamming distance")
+            plt.ylabel("Count")
             plt.tight_layout()
 
 fire.Fire(PLT())

### 2021-09-23 paper/paper.tex

@@
 
+With the ability to enumerate configurations, we can analyse the landscape of the target problem, like the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+We compute all MIS configurations for two random 3 regular graph instances of size 200, and show the Hamming distance statistics in \Fig{fig:hamming}.
+Some figure has single peak structure while some other has multiple peaks. Multiple peak structure indicates disconnected clusters in the configuration space.
 \begin{figure} 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    \caption{The statistics of Hamming distances between two MIS configurations for a specific three regular graph instance of size $200$.}
+    \caption{The statistics of Hamming distances between two MIS configurations for two specific three regular graph instance of size $200$.}
     \label{fig:hamming}

### 2021-11-22 paper/paper.tex
update ref 27

@@
 The size of an MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$. 
-Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
+Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for any positive $\epsilon$.
 Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms~\cite{Tarjan1977,Robson1986} and dynamic programming.

### 2021-11-22 project/configurations.jl

@@ -11,23 +11,21 @@ function mis_configurations(n, seed; order, writefile, sc_target=12)
     fname = joinpath(dirname(folder), "mis_degeneracy_L$n.dat")
     mask = Matrix{Bool}(reshape(readdlm(fname)[seed+1,4:end], n, n))
     g = diagonal_coupled_graph(mask)
-    code = Independence(g; optimizer=GreedyMethod(), simplifier=MergeGreedy())
-    #code = Independence(g; optimizer=TreeSA(sc_target=sc_target), simplifier=MergeGreedy())
-    s, c = max_size_count(code)
-    println("Graph $seed, n = $n, MIS size = $s, degeneracy = $c")
-    if c > 1000000
-        @warn "degeneracy too high, got: $c"
+    gp = Independence(g; optimizer=GreedyMethod(), simplifier=MergeGreedy())
+    res_c = solve(gp, "counting max$order")[]
+    println("Graph $seed, n = $n, max2 count = $res_c")
+    if sum(res_c.coeffs) > 10000000
+        @warn "degeneracy too high!"
+        return res_c, nothing
     end
-    #s2, config1, config0 = (res = best2_solutions(code; all=true)[]; (res.maxorder, res.coeffs...))
-    res_c = solve(code, "counting max$order")[]
-    s2, configs = (res = solve(code, "configs max$order (bounded)")[]; (res.maxorder, res.coeffs))
-    @assert s2 == s2
+    gp = Independence(g; optimizer=TreeSA(sc_target=sc_target), simplifier=MergeGreedy())
+    s2, configs = (res = solve(gp, "configs max$order (bounded)")[]; (res.maxorder, res.coeffs))
     @assert all(res_c.coeffs .== length.(configs))
     for i=1:order
         ofname = joinpath(folder, "$seed-$(i-1).dat")
         writefile && write(ofname, toMatrix(configs[order-i+1]))
     end
-    return s, configs
+    return res_c, configs
 end
 
 function toMatrix(x::ConfigEnumerator{N,K,C}) where {N,K,C}
@@ -63,7 +61,10 @@ for (n, seeds) in [
     #(6, [667, 557, 78, 312, 807, 776, 485, 980, 71, 50, 521, 773, 549, 523, 374, 515, 669, 344, 21, 107, 201,
[…]

### 2021-12-23 paper/paper.tex
update

@@
 \begin{abstract}
-We introduce a new approach to compute various properties of independent sets by encoding the problems and graphs into tensor networks with different tensor element algebra.
-The type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
-Although the computational complexity inevitably scales exponentially with treewidth of the graph, our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
-At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques.
+We introduce a method of using generic programming tensor network to compute various properties of independent sets.
+This method is versertile.
+By engineering tensor element algebra, the type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
+%Although the computational complexity inevitably scales exponentially with treewidth of the graph,
+%our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
+At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques like near optimal contraction order finding and slicing.
+We can easily contract a tensor network with thousands of tensors with an algorithmic complexity $2^{{\rm tw}(G)}$, with ${\rm tw} (G)$ the tree width of the problem graph.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
@@
 \section{Introduction}
-\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009},
+\blue{independence polynomial at -1~\cite{Bousquet2008,Levit2009},
 two motivations of computing independence polynomial: 1. Lee-Yang zero~\cite{Lee1952,Yang1952}, 2. Lov{\'a}sz local lemma~\cite{Scott2005}.
 }
-In graph theory and combinatorics, there are many interesting but hard computational problems concerning properties of independent sets.
-An independent set is a set of vertices in a graph where no two vertices are adjacent to each other.
-More formally, given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
-The problem of finding an independent set of the largest possible size, the maximum independent set (MIS), is a paradigmatic NP-complete problem~\cite{Hastad1996}.
-The size of an MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$. 
-Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for any positive $\epsilon$.
-Naive exhaustive search for the MIS requires time $O\left(2^{|V|} \right)$. More efficient exact algorithms include the branching algorithms~\cite{Tarjan1977,Robson1986} and dynamic programming.
-Sophisticated branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}.
-Dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
+In graph theory and combinatorial optimization, there are many interesting hard computational problems concerning properties of independent sets.
+%An independent set of a graph is a subset of its vertices that no two vertices in this set are adjacent to each other.
+For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$.
+The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets be $\alpha(G) \equiv \max_{I}|I|$ and one of the sets having this size.
+Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$ ~\cite{Hastad1996}.
+Naive exhaustive search for an MIS requires computing time $O\left(2^{|V|} \right)$.
+People developed more efficient exact algorithms for finding MISs, including the branching algorithms~\cite{Tarjan1977,Robson1986} and dynamic programming.
+The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
+while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
 these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-
-The independent set problem is closely related to the clique problem and the vertex cover problem~\cite{Moore2011};
-more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
-and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
-In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-Together, these problems find a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
-map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}.
-Besides the standard problem of finding the independence number and an MIS, there are many other interesting problems pertaining to independent sets, such as the number of independent sets,
+Although it is a hard problem, people keep chanllenging themself to find a better algorithm for solving the MIS problem;
+not only for it has a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
+map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}, but also for it is a well know NP-complete problem that can be mapped from
+ to many other important combinatorial optimization problems in polynomial time such as circuit satisfiability~\cite{}, the maximum clique problem and the maximum vertex cover~\cite{Moore2011} problems.
+
+%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
+%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
+%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+In this paper, we do not limit our discussion the finding one of the maximum indepedent sets and its size.
+There are many other interesting problems pertaining to independent sets, such as the number of independent sets,
 independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent sets.
@@
 in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready};
-they can, for example, be used to understand phase transitions and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
+they can, for example, be used to understand phase transitions, to analyse the overlap gap properties~\cite{Gamarnik2013, Gamarnik2019} and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
 
@@
 We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
-Our approach does not necessarily provide a better time complexity compared to dynamic programming considering the fact that the tensor network contraction can be regarded as a type of concrete implementation of dynamic programming,
-but the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties on CPUs and GPUs, the implementation of which benefits from recent advances in tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
-Lastly, we provide a few examples and show that the toolbox can be used to calculate the hard-square entropy constant,
+Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as the tree width of the graph ${\rm tw}(G)$.
+%But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
+We benchmark our algorithms by computing various independent set properties on CPUs and GPUs.
+Its high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
+People developed algorithms to optimize the contraction order for tensor networks with thousands of vertices,
+while the optimized contraction order gives us a near optimal space complexity $2^{\sim{\rm tw}(G)}$ to contract the tensor network.
+For cases when the tensors being too large to fit into a GPU, slicing technique can be used to further reduce the space consumption.
+The implementation of our algorithm is publicly available online: ~\cite{repolink}.
+Lastly, we provide a few examples and show that this toolbox can be used to calculate the hard-square entropy constant,
 Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.

### 2021-12-23 paper/paper.tex
update paper

@@
 We introduce a method of using generic programming tensor network to compute various properties of independent sets.
-This method is versertile.
-By engineering tensor element algebra, the type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
+This method is versertile such that by engineering tensor element algebra, the type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
 %Although the computational complexity inevitably scales exponentially with treewidth of the graph,
@@
 At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques like near optimal contraction order finding and slicing.
-We can easily contract a tensor network with thousands of tensors with an algorithmic complexity $2^{{\rm tw}(G)}$, with ${\rm tw} (G)$ the tree width of the problem graph.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs.
+One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices.
+This contraction order gives tensor network contraction complexity $2^{{\rm tw}(G)}$, with ${\rm tw} (G)$ the tree width of the problem graph.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs\blue{remove some examples}.
 \end{abstract}
@@
 
-\section{Introduction}
 \blue{independence polynomial at -1~\cite{Bousquet2008,Levit2009},
@@
 }
+\section{Introduction}
 In graph theory and combinatorial optimization, there are many interesting hard computational problems concerning properties of independent sets.
 %An independent set of a graph is a subset of its vertices that no two vertices in this set are adjacent to each other.
-For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$.
-The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets be $\alpha(G) \equiv \max_{I}|I|$ and one of the sets having this size.
+For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$.
+The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$ ~\cite{Hastad1996}.
@@
 these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-Although it is a hard problem, people keep chanllenging themself to find a better algorithm for solving the MIS problem;
+Although finding MIS is hard, people keep chanllenging themselves to find better algorithms for solving the MIS problem;
 not only for it has a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we do not limit our discussion the finding one of the maximum indepedent sets and its size.
+In this paper, we do not limit our discussion to finding one of the maximum indepedent sets and its size.
 There are many other interesting problems pertaining to independent sets, such as the number of independent sets,
@@
 they can, for example, be used to understand phase transitions, to analyse the overlap gap properties~\cite{Gamarnik2013, Gamarnik2019} and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
-
-In this work, we introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
+The problem of computing the independence polynomial belongs to the complexity class \#P-hard.
+One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}
+\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
+There are some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on computing the independence polynomial exactly.
+We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
 We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
-Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as the tree width of the graph ${\rm tw}(G)$.
+Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as ${\rm tw}(G)$.
 %But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties on CPUs and GPUs.
+We benchmark our algorithms by computing various independent set properties on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance on sparse graphs.
 Its high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
 People developed algorithms to optimize the contraction order for tensor networks with thousands of vertices,
-while the optimized contraction order gives us a near optimal space complexity $2^{\sim{\rm tw}(G)}$ to contract the tensor network.
+and the optimized contraction order gives us a near optimal space complexity $2^{\sim{\rm tw}(G)}$ to contract the tensor network.
 For cases when the tensors being too large to fit into a GPU, slicing technique can be used to further reduce the space consumption.
-The implementation of our algorithm is publicly available online: ~\cite{repolink}.
 Lastly, we provide a few examples and show that this toolbox can be used to calculate the hard-square entropy constant,
 Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs. 
+The implementation of our algorithm is publicly available online: ~\cite{repolink}.
 
 \section{Tensor networks}
-A tensor network~\cite{Cirac2020, Orus2014} can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
-Let $A, B$ be two matrices; the matrix multiplication is defined as $C_{ik} = \sum_{j}A_{ij}B_{jk}$.
-Using the Einstein notation, we can write $C_{ik} = A_{ij}B_{jk}$, where $j$ is implicitly summed over.
-In the standard notation, each index can appear at most twice. A tensor network consists of multiple tensors performing the sum-product operation,
-i.e., contraction, and it can be represented as a multigraph with open edges by viewing a tensor as a vertex,
-a label pairing two tensors as an edge, and the remaining unpaired labels as open edges.
+Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts,
+it can be viewed as a generalization of matrix multiplication to multiple tensors contraction.
+People often use Einstein's notation to represent a tensor network, e.g.
+the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
+where we use a label in subscripts to represent a degree of freedom.
+We enumerate these degree of freedoms and accumulate the product of tensor elements to the output tensor.
+In the standard notation of Einstein's summation or tensor network in physics, each index appears precisely twice.
+Hence people can represent a tensor network as a simple graph,
+where a tensor is a vertex and two tensors sharing the same label are connected.
+In the main text, we do not have this restriction. An index can appear arbitrary times.
+The graphical representation of our generlized tensor network is hypergraph, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
+These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors - a high dimensional equivalence of identity matrix.
+However, introducing $\delta$ tensors can potentially increase the contraction complexity a lot. We illustrate this point in \App{app:tensorbad}.
+\blue{introduce contraction orders}
 
 \begin{example}
-   A standard tensor network $C_{il} = A_{ijkm} B_{kml} V_{j}$ has the following multigraph representation.
-
-\centerline{\begin{tikzpicture}[
-    dot/.style = {circle, fill, minimum size=#1,
-                inner sep=0pt, outer sep=0pt},
-    dot/.default = 6pt  % size of the circle diameter 
-                    ]
-    \def\dx{0};
-    \def\r{0.25cm}
-    \def\ax{0}
-    \def\ay{0}
-    \def\bx{1}
-    \def\by{1}
-    \def\cx{1}
-    \def\cy{-1}
-    \node[color=white, fill=black, dot=2*\r] at (\ax+\dx,\ax) (a) {A};
-    \node[color=white, fill=black, dot=2*\r] at (\bx+\dx,\by) (b) {B};
-    \node[color=white, fill=black, dot=2*\r] at (\cx+\dx,\cy) (c) {V};
-    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx+0.2,0.5*\ay+0.5*\by-0.2) .. (\bx+\dx,\by);
-    %\draw [black,thick] (\ax+\dx,\ay) .. controls (0.5*\ax+0.5*\bx+\dx-0.2,0.5*\ay+0.5*\by+0.2) .. (\bx+\dx,\by);
-    \draw [black,thick] (a) .. controls (0.4, 0.6) .. (b);
-    \draw [black,thick] (a) .. controls (0.6, 0.4) .. (b);
-    \draw [black,thick] (a) -- (c);
-    \draw [black,thick] (a) -- (\ax+\dx-0.8,\ay);
-    \draw [black,thick] (b) -- (\bx+\dx+0.8,\by);
-    \node[color=black] at (0.5*\ax+0.5*\bx-0.3+\dx,0.5*\ay+0.5\by+0.3) {k};
-    \node[color=black] at (0.5*\ax+0.5*\bx+0.3+\dx,0.5*\ay+0.5\by-0.3) {m};
-    \node[color=black] at (0.5*\ax+0.5*\cx+\dx+0.2,0.5*\ay+0.5\cy+0.2) {j};
-    \node[color=black] at (\ax+\dx-0.5,\ay-0.2) {i};
-    \node[color=black] at (\bx+\dx+0.5,\by-0.2) {l};
-\end{tikzpicture}}
-\end{example}
-
-In the main text, we use a generalized tensor network notation that an index can appear arbitrary times.
-It is sometimes called einsum,
-sum-product network or factor graph~\cite{Bishop2006} in different contexts.
-The graphical representation of a generlized tensor network is a hypergraph, where an edge (label) can be shared by an arbitrary number of vertices (tensors).
-These two notations are equivalent in the representation power because one can easily translate a generalized tensor network to the standard notation by adding identity tensors denoted as $\delta$ tensors.
-However, by adding the $\delta$ tensors, one may unnecessarily increase the contraction complexity of a graph, which we illustrate in \App{app:tensorbad}.
-
-\begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network representing $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$,
-where $i,j,k$ in the output tensor are open edges (note that $l$ is not an open edge and thus summed over).
-Its hypergraph representation is shown below, where we use different colors to annotate different hyperedges.
-It's equivalent standard notation is $C_{ijk} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$.
-
+$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network that can be evaluated as $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
+Its hypergraph representation is shown below, where we use different colors to represent different hyperedges.
+%It's equivalent standard notation is $C_{ijk} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$.
+
+\vspace{1em}
 \centerline{\begin{tikzpicture}[
@@
 
-This definition of generic programming contains two major aspects: a single program for the general setting and efficiency.
+This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
 To understand the first aspect, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
@@
 We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
-A commutative semiring is a semiring with its multiplication operation being commutative, while a semiring is a ring without additive inverse.
+A commutative semiring is a semiring with its multiplication operation being commutative, and a semiring is a ring without additive inverse.
 To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for any arbitrary three elements $a, b, c \in R$.
@@
 \end{align*}
-The requirement of being commutative is for the tensor contraction result to be independent of the contraction order, which could be relaxed in certain cases.
-In the following sections, we show how to compute the independence polynomial,
+The requirement of being commutative is for the tensor contraction result to be independent of the contraction order. In the following sections, we show how to compute the independence polynomial,
 the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent sets of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
@@
 \end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$, and $\alpha(G)$ is the independence number. The total number of independent sets is thus equal to $I(G, 1)$.
-The problem of computing the independence polynomial belongs to the complexity class \#P-hard.
-One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}
-\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
-There are some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact methods to compute the independence polynomial.
-
-The independence polynomial is closely related to the matching polynomial, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013}.
-In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{Levit2005}.
-Thus, our algorithm to compute the independence polynomial can also be used to compute the above graph polynomials.
-Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
-We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
-
-To compute the independence polynomial of a graph $G$, we encode it to a tensor network.
-On the vertex $i$ of the graph $G$, we place a rank-one vertex tensor, $W(x_i)$, of size $2$ parametrized by $x_{i}$ and a rank-two edge tensor, $B$, of size $2 \times 2$ on an edge
+where $a_k$ is the number of independent sets of size $k$ in $G$. The total number of independent sets is thus equal to $I(G, 1)$.
+To compute the independence polynomial of a graph $G = (V, E)$, we reinterpret this problem as a tensor network contraction problem.
+We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex absent (exists) in the set.
+For each label $s_i$, we defined a prametrized rank-one vertex tensor $W(x_i)$ indexed by it as
 \begin{equation}
@@
         x_i
-    \end{matrix}\right),
+    \end{matrix}\right).
+\end{equation}
+On each edge $(u, v)$, we define a matrix $B$ indexed by $(s_u, s_v)$ as
+\begin{equation}
     \qquad \quad 
@@
 The corresponding tensor network contraction gives
-\begin{equation}
+\begin{equation}\label{eq:idp}
     P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
@@
 where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$ (see Example \ref{eg:tensorcontraction} for a concrete example).
-The tensor index $s_i$ is a boolean variable; $s_{i} = 1$ corresponds that the vertex $i$ is in the independent set, and $s_{i} = 0$ means otherwise.
-Let us assume the tensor elements are real numbers for now.
 The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
@@
 and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise.
-In the implementation of the algorithm, we benefit from recent advances in tensor network contraction,
-where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
+
+%In the implementation of the algorithm, we benefit from recent advances in tensor network contraction,
+%where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
+To evalute \Eq{eq:idp}, summing up the products directly is apparently computational inefficient.
+The standard approach to evaluate a tensor network is to contract two tensors a time with a certain order utilizing the associativity and commutativity of tensor elements.
 A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
@@
 
-    The contraction of this tensor network can be done in a pairwise order:
+    The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity and multiplicative commutativity of tensor elements:
     \begin{align*}
@@
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
-The most natural approach is to treat the tensor elements as polynomials and evaluate the polynomial directly.
+Then we can treat the tensor elements as polynomials and evaluate the polynomial directly.
 Let us create a polynomial type, and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $(a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
@@
 \end{equation}
-One way to efficiently evaluate the multiplication operation is to use the convolution theorem~\cite{Schonhage1971}.
+Here, the multiplication operation can be evaluated efficiently using the convolution theorem~\cite{Schonhage1971}.
 We can see these operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
@@
 \end{equation}
-By contracting the tensor network with the polynomial type, the final result is the exact representation of the independence polynomial.
+By contracting the tensor network with the polynomial type, we have contraction result the exact representation of the independence polynomial.
 However, using polynomial numbers suffers from a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random values of $x_{i}$ and $y_{i} = I(G,x_{i})$.
+Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
 One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
@@
 In addition, the number could easily overflow if we use fixed-width integer types.
-The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with graphics processing unit (GPU) devices.
+The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
 These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
@@
 This is an iterative algorithm that iterates over a sequence of large prime numbers until convergence.
-In each iteration, we contract the tensor networks to evaluate the polynomial for each variable $x = \chi_{i}$ on ${\rm GF}(p)$ and denote the outputs as $Y$.
-Then we solve a linear equation $Y = X A_p$ using the gaussian elimination to find the coefficient modulo $p$, $A_p \equiv A \pmod p$.
-Finally we apply the Chinese remainder theorem to get $A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change compared with the previous iteration, it indicates the result has converged.
+In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
+Then we solve \Eq{eq:lineareq} using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
+As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
+If this number does not change compared with the previous iteration, it indicates the convergence of result and the program terminates.
 All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
-In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transform.
+In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transformation.
 
@@
     \While{true}{
-        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p \leq 2^W$\;
-
-        \For{$i=1\ldots\alpha(G)$}{
-            t = ${\rm tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{defined on $\text{GF}(p)$}
-
-            $Y_i \pmod p  = {\rm contract}(t)$\;
-        }
-
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, Y \pmod p) $\;
+        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
+
+        \For{$i=0\ldots\alpha(G)$}{
+            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
+        }
+
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha{G}}) \pmod p) $\;
 
@@
         $P = P \times p$\;
-    }\caption{Compute the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
+    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
 \end{algorithm}
 
+\blue{I am here!}
+
 \subsection{Maximal independence polynomial}
-Sometimes, one may be interested in knowing maximal solutions to understand why his or her \blue{Is this a convention to use both "he" and "her"?} program is trapped in a local minimum.
+Sometimes, one may be interested in knowing maximal solutions to understand why his or her program is trapped in a local minimum.
 Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
@@
 The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
+The independence polynomial is closely related to the matching polynomial, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013}.
+In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{Levit2005}.
+Thus, our algorithm to compute the independence polynomial can also be used to compute the above graph polynomials.
+Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
+We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
 We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.

### 2021-12-23 paper/paper.tex
update

@@
 these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-Although finding MIS is hard, people keep chanllenging themselves to find better algorithms for solving the MIS problem;
+People are eager to find better algorithms for solving the MIS problem;
 not only for it has a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
@@
 However, introducing $\delta$ tensors can potentially increase the contraction complexity a lot. We illustrate this point in \App{app:tensorbad}.
-\blue{introduce contraction orders}
+\blue{Is it better to introduce the contraction orders here or in example~\ref{eg:tensorcontraction}?}
 
@@
             \textbf{element type}     & \textbf{purpose} \\
-            {$\mathbbm{R}$}     & {real number for counting all independent sets} \\
+            {$\mathbbm{R}$}     & {real number for counting independent sets} \\
             {$\mathbbm{C}$}     & {complex number for fitting the independence polynomial with fast Fourier transform} \\
-            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {number on finite field algebra for fitting the independence polynomial exactly using number theory} \\
+            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {finite field algebra for fitting the independence polynomial exactly using number theory} \\
             {T} (\Eq{eq:tropical})    & {tropical number for finding the independence number} \\
             {P1} (\Eq{eq:countingtropical})     & {polynomial truncated to largest order, i.e. the tropical number with counting field for finding the independence number and the number of MISs} \\
-            {P2} (\Eq{eq:max2poly})     & {counting MISs and independent sets of size $\alpha(G)-1$} \\
-            {PN} (\Eq{eq:polynomial})     & {computing the independence polynomial exactly} \\
-            {P1+S1}     & {replacing the counting field in P1 to configuration sampler defined in $\Eq{eq:singleconfig}$ for finding the independence number and one MIS} \\
-            {P1+SN} (\Eq{eq:countingtropicalset})    & {replacing the counting field in P1 to configuration sampler defined in $\Eq{eq:set}$ for finding the independence number and enumeration of all MISs} \\
+            {P2} (\Eq{eq:max2poly})     & {polynomial truncated to largest two orders for counting MISs and independent sets of size $\alpha(G)-1$} \\
+            {PN} (\Eq{eq:polynomial})     & {polynomial number for computing the independence polynomial directly} \\
+            {P1+S1}     & {P1 with configuration sampler (\Eq{eq:singleconfig}) as its counting field for finding the independence number and one MIS} \\
+            {P1+SN} (\Eq{eq:countingtropicalset})    & {P1 with configuration enumerator (\Eq{eq:set}) as its counting field for finding the independence number and enumeration of all MISs} \\
             \bottomrule

### 2021-12-24 paper/paper.tex
update

@@
 \begin{abstract}
-We introduce a method of using generic programming tensor network to compute various properties of independent sets.
-This method is versertile such that by engineering tensor element algebra, the type of graph problems that can be computed using this method includes: independence number, the number of independent sets, independence polynomial, maximal independence polynomial, and both counting and enumeration of all maximum independence sets, the large-size independent sets, and all maximal independent sets.
+We introduce a method of using generic programming tensor network to compute various properties of independent sets,
+which includes: maximum size of such sets, the number of sets of a given size, enumeration of sets of a given size.
+It can be generalized to compute properties of other problems like cut size, coloring, maximal cliques et al.
 %Although the computational complexity inevitably scales exponentially with treewidth of the graph,
@@
 At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques like near optimal contraction order finding and slicing.
-One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices.
-This contraction order gives tensor network contraction complexity $2^{{\rm tw}(G)}$, with ${\rm tw} (G)$ the tree width of the problem graph.
+%One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices. 
+The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ the tree width of the problem graph.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs\blue{remove some examples}.
@@
 In this paper, we do not limit our discussion to finding one of the maximum indepedent sets and its size.
-There are many other interesting problems pertaining to independent sets, such as the number of independent sets,
-independence polynomial, maximal independence polynomial, and enumeration of MIS or maximal independent sets.
+There are many other interesting problems pertaining to independent sets, such as the number of independent sets at a given size
+and enumerating independent sets at a give size or what we call computing \textit{properties}.
 Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 \end{align*}
-The requirement of being commutative is for the tensor contraction result to be independent of the contraction order. In the following sections, we show how to compute the independence polynomial,
-the maximal independence polynomial, independence number, the number of independent sets, and enumeration of the MIS and maximal independent sets of a general graph $G$ by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
-Table~\ref{tbl:generictypes} summarizes the problems that can be solved by various tensor element types.
+The requirement of being commutative is for the tensor contraction result to be independent of the contraction order.
+In the following sections, we show how to compute the properties of independent sets by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+Table~\ref{tbl:generictypes} summarizes the properties that can be solved by various tensor element types.
 
@@
 
-\section{Independence polynomial and maximal independence polynomial}
+\section{Independence polynomial}
 \subsection{Independence polynomial}\label{sec:indpoly}
@@
 
-\blue{I am here!}
-
-\subsection{Maximal independence polynomial}
-Sometimes, one may be interested in knowing maximal solutions to understand why his or her program is trapped in a local minimum.
-Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
- Concretely, it is defined as
-\begin{equation}
-I_{\rm max}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
-\end{equation}
-where $b_k$ is the number of maximal independent sets of size $k$ in $G$.
-Obviously, $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
-The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
-
-Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent set where there exists no vertex $v$ such that $I_m \cap N[v]  = \emptyset$.
-We can modify the tensor network for computing the independence polynomial to include this restriction.
-Instead of defining the restriction on vertices and edges, it is more natural to define it on $N[v]$:
-\begin{equation}\label{eq:maximal}
-    T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx_v & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
-        1-s_v& \text{otherwise}.\\
-    \end{cases}
-\end{equation}
-Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$,
-and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t. $s_{i} = 1$, then $v$ cannot be in $I_{m}$.
-As an example, for a vertex of degree 2, the resulting rank-3 tensor is
-\begin{equation}
-    T(x_v)=\left(\begin{matrix}
-    \left(\begin{matrix}
-        0 &1 \\
-        1 &1
-    \end{matrix}\right)\\
-    \left(\begin{matrix}
-        x_v &0 \\
-        0 &0
-    \end{matrix}\right)
-    \end{matrix}\right).
-\end{equation}
-
-With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
-Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
-
-    \centerline{\begin{tikzpicture}[
-    dot/.style = {circle, fill, minimum size=#1,
-                inner sep=0pt, outer sep=0pt},
-    dot/.default = 6pt  % size of the circle diameter 
-                    ]  
-        \def\dx{0};
-        \def\r{0.5cm}
-        \def\G{1.0}
-        \foreach \x/\y/\v in {0/0/a, 1/0/b, 2/0/c, 3/0/d, 4/0/e}
-            \node[color=black] at (\x*\G+\dx,\y) (\v) {$s_\v$};
-        \foreach \x/\v/\t in {0/A/$T_a$, 1/B/$T_b$, 2/C/$T_c$, 3/D/$T_d$, 4/E/$T_e$}
-            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\t};
-        \draw [cyan,thick] (a) -- (A);
-        \draw [cyan,thick] (a) -- (B);
-        \draw [cyan,thick] (a) -- (C);
-        \draw [blue,thick] (b) -- (B);
-        \draw [blue,thick] (b) -- (A);
-        \draw [blue,thick] (b) -- (C);
-        \draw [blue,thick] (b) -- (D);
-        \draw [red,thick] (c) -- (C);
-        \draw [red,thick] (c) -- (A);
-        \draw [red,thick] (c) -- (B);
-        \draw [red,thick] (c) -- (D);
-        \draw [green,thick] (d) -- (D);
-        \draw [green,thick] (d) -- (B);
-        \draw [green,thick] (d) -- (C);
-        \draw [green,thick] (d) -- (E);
-        \draw [orange,thick] (e) -- (E);
-        \draw [orange,thick] (e) -- (D);
-    \end{tikzpicture}}
-
-One can see that the average degree of a tensor is increased.
-The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
-However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
-
 \section{Maximum independent sets and its counting problem}
@@
 
-\section{Enumeration of configurations and enumeration bounds}
-\subsection{Enumeration of independent sets}
+\section{Enumeration of independent sets}
+\subsection{Set algebra for configuration enumeration}
 The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973, Eppstein2010, Johnson1988}, including,
 for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
-The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
-Here, we adapt the tensor element types for different enumeration problems.
-For example, our tensor-network based algorithm to enumerate all MISs is expectedly much faster and more space-efficient than the Bron-Kerbosch algorithm, which lists all maximal independent sets.
-
-To enumerate all independent sets, we input a set of configurations into the tensor elements. More concretely, we design a new element type having the following algebra
+Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
+a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+We can also compute the maximal independence polynomial and enumerate maximal independent sets with a different tensor network mapping, and this is described in \Sec{sec:maximal}.
+To enumerate all independent sets, we designed an algebra defined on sets of bitstrings.
 \begin{equation}
@@
 When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
-To speed up the computation and reduce space overhead, we use $\alpha(G)$ to bound the searching space.
+To speed up the computation and reduce space overhead, we bound the searching space using the MIS size $\alpha(G)$.
 First, we compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
@@
 Finally, we perform masked matrix multiplication using the new element type with the above algebra, \Eq{eq:countingtropicalset}, for obtaining all configurations.
-Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagation of the gradients.
-To derive the back-propagation rule for tensor contraction,
+Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
+To derive the back-propagation rule for tropical tensor contraction,
 we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
@@
 The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
+Intuitively, one can use this relation to indentify elements with nonzero gradients in $A$ and $B$ directly,
+however, doing this might make us lost the advantage of using BLAS libraries~\cite{TropicalGEMM}.
 Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 
@@
 This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
-With the above method, one can significantly reduce the space needed to store the intermediate configurations.
+With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.
+
+\blue{I am here!}
 
@@
 
+The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
 We also benchmarked our method with the Bron-Kerbosch method to enumerate and count maximal independent sets in \Fig{fig:benchmark-maximal}.
@@
 \section{Discussion and conclusion}
-We have introduced a new approach based on tensor network contraction to compute the independence number, independence polynomial, maximal independence polynomial, and enumeration of MIS configurations.
+We have introduced a new approach based on tensor network contraction to compute various properties of independent sets,
+including the independence number, number of independent set of a given size, and enumeration of independent sets of a give size.
 We derived the backward rule for tropical tensor network to bound the search of solution space.
@@
 In the following, we introduce some other problems that can be expressed by a tensor network.
+\subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
+Sometimes, one may be interested in knowing maximal solutions to understand why his or her program is trapped in a local minimum.
+Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
+ Concretely, it is defined as
+\begin{equation}
+I_{\rm max}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
+\end{equation}
+where $b_k$ is the number of maximal independent sets of size $k$ in $G$.
+Obviously, $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
+$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
+If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
+The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
+
+Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent set where there exists no vertex $v$ such that $I_m \cap N[v]  = \emptyset$.
+We can modify the tensor network for computing the independence polynomial to include this restriction.
+Instead of defining the restriction on vertices and edges, it is more natural to define it on $N[v]$:
+\begin{equation}\label{eq:maximal}
+    T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+        s_vx_v & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
+        1-s_v& \text{otherwise}.\\
+    \end{cases}
+\end{equation}
+Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$,
+and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t. $s_{i} = 1$, then $v$ cannot be in $I_{m}$.
+As an example, for a vertex of degree 2, the resulting rank-3 tensor is
+\begin{equation}
+    T(x_v)=\left(\begin{matrix}
+    \left(\begin{matrix}
+        0 &1 \\
+        1 &1
+    \end{matrix}\right)\\
+    \left(\begin{matrix}
+        x_v &0 \\
+        0 &0
+    \end{matrix}\right)
+    \end{matrix}\right).
+\end{equation}
+
+With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
+Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
+
+    \centerline{\begin{tikzpicture}[
+    dot/.style = {circle, fill, minimum size=#1,
+                inner sep=0pt, outer sep=0pt},
+    dot/.default = 6pt  % size of the circle diameter 
+                    ]  
+        \def\dx{0};
+        \def\r{0.5cm}
+        \def\G{1.0}
+        \foreach \x/\y/\v in {0/0/a, 1/0/b, 2/0/c, 3/0/d, 4/0/e}
+            \node[color=black] at (\x*\G+\dx,\y) (\v) {$s_\v$};
+        \foreach \x/\v/\t in {0/A/$T_a$, 1/B/$T_b$, 2/C/$T_c$, 3/D/$T_d$, 4/E/$T_e$}
+            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\t};
+        \draw [cyan,thick] (a) -- (A);
+        \draw [cyan,thick] (a) -- (B);
+        \draw [cyan,thick] (a) -- (C);
+        \draw [blue,thick] (b) -- (B);
+        \draw [blue,thick] (b) -- (A);
+        \draw [blue,thick] (b) -- (C);
+        \draw [blue,thick] (b) -- (D);
+        \draw [red,thick] (c) -- (C);
+        \draw [red,thick] (c) -- (A);
+        \draw [red,thick] (c) -- (B);
+        \draw [red,thick] (c) -- (D);
+        \draw [green,thick] (d) -- (D);
+        \draw [green,thick] (d) -- (B);
+        \draw [green,thick] (d) -- (C);
+        \draw [green,thick] (d) -- (E);
+        \draw [orange,thick] (e) -- (E);
+        \draw [orange,thick] (e) -- (D);
+    \end{tikzpicture}}
+
+One can see that the average degree of a tensor is increased.
+The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
+However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+
 \subsection{Matching problem}

### 2021-12-24 paper/paper.tex
update

@@
 
-\blue{I am here!}
-
 \section{Benchmarks and case studies}
@@
 The results are summarized in Figure~\ref{fig:benchmark}.
-The graphs that we use in benchmarks are random 3 regular graphs, a typical type of sparse graphs that has a small tree width $\text{tw}(G) \leq |V|/6$~\cite{Fomin2006}.
+The graphs that we use in benchmarks are random three regular graphs,
+ a typical type of sparse graphs that has a small tree width asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
 
@@
     \caption{Benchmark results for computing different properties of independent sets of a random three regular graph with different tensor element types.
-    The time in these plots only includes tensor network contraction process, without taking the just in time compiling time into account.
+    The time in these plots only includes tensor network contraction, without taking the contraction order finding and just in time compiling time into account.
     \red{for each graph size, is there only one graph?}\blue{yes}
-    (a) treewidth versus the number of vertices for the benchmarked graphs. 
-    Legends are the data types that we used in the computation, one can find the corresponding computational task in \Tbl{tbl:generictypes}.
+    (a) tree width versus the number of vertices for the benchmarked graphs. 
+    Legends are the data types that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
     (b) The computing time for calculating the independence number and for counting of the number of independent sets, the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
     (c) The computing time for calculating the independence polynomials with different approaches.
-    (d) The computing time for enumeration problems, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
+    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
     \red{suggestions for the figure: 1.
@@
 
-The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
-computing independence polynomial (panel c) and enumerating and sampling independent sets (panel d).
-\blue{I cleaned up this paragraph, because one can check the table \Tbl{tbl:generictypes} now.}
-\red{Jinguo, should we include maximal independence polynomial and enumeration of all maximal independent sets as well? I think that will make the benchmark more complete.}
-\blue{added a new paragraph.}
-Among the benchmarks, computing \texttt{T (CPU)},
-\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions, and hence 
-they are faster comparing to non-BLAS methods in the same category.
+Figure (a) shows the time and space complexity obtained with tensor network optimization algorithm in Ref.~\cite{Kalachev2021}, where the space complexity is the same as the tree width of the problem graph.
+One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
+%The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
+%computing independence polynomial (panel c) and find one independent set and enumerating independent sets (panel d).
+Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
+\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions, hence 
+are much faster comparing to non-BLAS methods in the same category.
+GPU computes much faster than CPU in all cases when the problem scale is large enough so that the actual computing time is comparable or larger than the launching time of CUDA kernels.
 Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e. \texttt{PN} and \texttt{SN}.
-Fourier transformation based method is the fastest in computing the independence polynomial,
-while the finite field (GF$(p)$) approach is the only method that does not incur round-off errors and that can be run on a GPU.
-In the benchmark of enumerating the MISs (panel d), one can see the technique to bound the enumeration space improves the performance for more than one order.
-Bounding can also reduce the memory usage significantly, without which the largest enumerable size is about $150$ vertices on a 32G memory device.
-All these computing times have a strong correlation with the treewidth, 
-and the computing times of configuration enumeration also depend on the size of the target configuration space.
-
-\begin{figure} 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
-    \caption{Benchmark results for computing different properties of maximal independent sets on a random three regular graph with different tensor element types.
-    (a) treewidth versus the number of vertices for the benchmarked graphs. 
-    (b) The computing time for calculating the number of independent sets and enumerate all MISs.
-    }
-    \label{fig:benchmark-maximal}
-\end{figure}
-
-The standard algorithm to enumerate all maximal independent sets is the Bron-Kerbosch algorithm~\cite{Bron1973}, which, of course, includes the enumeration of all MISs and can be used to enumerate all independent sets as well.
-We also benchmarked our method with the Bron-Kerbosch method to enumerate and count maximal independent sets in \Fig{fig:benchmark-maximal}.
-Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
-the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
-The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
-while the tensor network does counting much more efficiently.
-The implementation of Bron-Kerbosch algorithm is from the package LightGraphs~\cite{LightGraphs},
-due to the memory limit, this algorithm stops working at size $70$ and above.
+In figure (c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
+however, it maybe suffer from the round off errors. The finite field (GF$(p)$) approach is the only method that does not incur round-off errors and can run on a GPU.
+In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order in enumerating the MISs.
+Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a 32G memory device.
+%and the computing times of configuration enumeration also depend on the size of the target configuration space.
+
+\blue{I am here!}
 
@@
 	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
-	\item[\href{https://github.com/JuliaGraphs/LightGraphs.jl}{LightGraphs}] is a package providing graph utilities, like random regular graph generator,
+	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
 	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
@@
 \begin{lstlisting}
-pkg> add OMEinsum LightGraphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
+pkg> add OMEinsum Graphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
 \end{lstlisting}
@@
 \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}
+
+Here is a short introduction to the functionalities in this libary.
+
+\lstinputlisting[breaklines]{../democode/tutorial.jl}
 
@@
 
+\begin{figure} 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
+    \caption{Benchmark results for computing different properties of maximal independent sets on a random three regular graph with different tensor element types.
+    (a) treewidth versus the number of vertices for the benchmarked graphs. 
+    (b) The computing time for calculating the number of independent sets and enumerate all MISs.
+    }
+    \label{fig:benchmark-maximal}
+\end{figure}
+
+We show the benchmark of computing the maximal independent set properties in \Fig{fig:benchmark-maximal},
+including a comparison to the Bron-Kerbosch algorithm from the package Graphs~\cite{Graphs}.
+Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
+the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
+The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
+while the tensor network does counting much more efficiently.
+Due to the memory limit, this Bron-Kerbosch algorithm stops working at size $70$ and above.
+
 \subsection{Matching problem}

### 2021-12-24 democode/tutorial.jl

@@ -1,0 +1,72 @@
+julia> using GraphTensorNetworks, Random, Graphs
+
+julia> graph = (Random.seed!(2); Graphs.smallgraph(:petersen))
+{10, 15} undirected simple Int64 graph
+
+julia> problem = Independence(graph; optimizer=TreeSA(sc_target=0, sc_weight=1.0, ntrials=10, βs=0.01:0.1:15.0, niters=20, rw_weight=0.2));
+┌ Warning: target space complexity not found, got: 4.0, with time complexity 7.965784284662087, read-right complexity 8.661778097771988.
+└ @ OMEinsumContractionOrders ~/.julia/dev/OMEinsumContractionOrders/src/treesa.jl:71
+time/space complexity is (7.965784284662086, 4.0)
+
+# maximum independent set size
+julia> solve(problem, "size max")
+0-dimensional Array{TropicalNumbers.TropicalF64, 0}:
+4.0ₜ
+
+# all independent sets
+julia> solve(problem, "counting sum")
+0-dimensional Array{Float64, 0}:
+76.0
+
+# counting maximum independent sets
+julia> solve(problem, "counting max")
+0-dimensional Array{TropicalNumbers.CountingTropicalF64, 0}:
+(4.0, 5.0)ₜ
+
+# counting independent sets of max two sizes
+julia> solve(problem, "counting max2")
+0-dimensional Array{Max2Poly{Float64, Float64}, 0}:
+30.0*x^3 + 5.0*x^4
+
+# using `Polynomial` type
+julia> solve(problem, "counting all")
+0-dimensional Array{Polynomial{Float64, :x}, 0}:
+Polynomial(1.0 + 10.0*x + 30.0*x^2 + 30.0*x^3 + 5.0*x^4)
+
+# using the finitefield approach
+julia> solve(problem, "counting all (finitefield)")
+0-dimensional Array{Polynomial{BigInt, :x}, 0}:
+Polynomial(1 + 10*x + 30*x^2 + 30*x^3 + 5*x^4)
+
+# using the fourier approach
+julia> solve(problem, "counting all (fft)", r=1.0)
+0-dimensional Array{Polynomial{ComplexF64, :x}, 0}:
[…]

### 2021-12-24 paper/paper.tex
update slicing

@@
 
-\section{Maximum independent sets and its counting problem}
+\section{Maximum independent sets and its counting}
 \subsection{Tropical algebra for finding the independence number and counting MISs}
@@
 \section{Discussion and conclusion}
-We have introduced a new approach based on tensor network contraction to compute various properties of independent sets,
-including the independence number, number of independent set of a given size, and enumeration of independent sets of a give size.
-We derived the backward rule for tropical tensor network to bound the search of solution space.
-Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
-The power of our tensor network approach is not only limited to the independent set problem, in \App{app:otherproblems}, we show how to map the matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
-The independence polynomial is closely related to the matching polynomial, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013}.
-In fact, the independence polynomial can be viewed as a generalization of the matching polynomial, since the matching polynomial of a graph $G$ is the same as the independence polynomial of the line graph of $G$~\cite{Levit2005}.
-Thus, our algorithm to compute the independence polynomial can also be used to compute the above graph polynomials.
-Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
-We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
+In this paper, we introduce an abstract algebra formalism to compute properties of independent sets.
+The properties include the independence number, number of independent set of a given size, and enumeration of independent sets of a give size.
+For each property, we design a algebra being a commutative semiring, and map the property computation to the contraction of a tensor network with such element type.
+%We derived the backward rule for tropical tensor network to bound the search of solution space.
+%Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
+We call this method generic programming tensor network, and its power is not limited to the independent set problem.
+In \App{app:otherproblems}, we show how to map the maximal independent set problem, matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
+Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
+our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
+%Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
+%We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
 We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
@@
 \section*{Acknowledgments}
-We would like to thank Pan Zhang for sharing his code for optimizing contraction orders of a tensor network.
+We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
 We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions about independent sets,
-their questions are one of the driving forces of this project.
-Thank Chris Elord for helping us writing the fastest matrix multiplication libary for tropical numbers, TropicalGEMM.jl, he is a remarkable guy!
+their questions are driving forces of this project.
+Thank Chris Elord for helping us writing the fastest matrix multiplication libary for tropical numbers, TropicalGEMM.jl, he is a man of speed!
 \blue{funding information}

### 2021-12-24 project/sequencing.jl

@@ -1,0 +1,33 @@
+using GraphTensorNetworks, Random
+using CUDA
+CUDA.allowscalar(false)
+
+using DelimitedFiles
+
+function sequencing(n; writefile, sc_target, usecuda, nslices=1)
+    g = square_lattice_graph(trues(n, n))
+    gp = Independence(g; optimizer=TreeSA(sc_target=sc_target, sc_weight=1.0, nslices=nslices;
+        ntrials=5, βs=0.01:0.05:22.0, niters=20, rw_weight=0.2), simplifier=MergeGreedy())
+    println("Graph size $n, usecuda = $usecuda")
+    @show timespace_complexity(gp)
+    return
+    res = GraphTensorNetworks.big_integer_solve(Int32, 100) do T
+        GraphTensorNetworks.contractx(gp, one(T); usecuda=usecuda)
+    end
+    #res = GraphTensorNetworks.contractx(gp, 1.0; usecuda=usecuda)[]
+    @show res
+    ofname = joinpath(@__DIR__, "data", "$n.dat")
+    writefile && writedlm(ofname, res)
+end
+
+# patch
+const DEVICE = length(ARGS) >= 1 ? parse(Int, ARGS[1]) : -1
+
+if DEVICE >= 0
+    CUDA.device!(DEVICE)
+end
+
+for L = [11]
+    println("computing L = $L")
+    @time sequencing(L; writefile=false, sc_target=10, usecuda=DEVICE>=0)
+end

### 2021-12-25 paper/paper.tex
update appendix

@@
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
-\begin{equation}
+\begin{equation}\label{eq:idpdef}
 I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
@@
         1 & 0
-    \end{matrix}\right), \label{eq:tensor}
+    \end{matrix}\right), \label{eq:edgetensor}
 \end{equation}
@@
 
-\blue{I am here!}
-
 \subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
@@
 
+\blue{I am here!}
+
 \bibliographystyle{siamplain}
@@
 \section{Technical guide}\label{sec:technical}
-Before showing the codes,
-we want to introduce some Julia packages that playing important roles in our code base.
+This project depends on multiple open source packages in Julia ecosystem.
+We list the Julia packages playing important roles in our code base as follows.
 
@@
 
-Please checkout our GitHub repository for the full featured version:
-
-\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}
-
-Here is a short introduction to the functionalities in this libary.
+For performance reason, we still recommend checking our GitHub repository for the full featured version:
+\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
+It can be installed in a similar style to other packages. Here is a short introduction to the functionalities in this package.
 
@@
 
-\section{Why not using the standard tensor network notations}\label{app:tensorbad}
+\section{The reason to not using the standard tensor network notations}\label{app:tensorbad}
 As we have mentioned in the main text,
-a standard tensor network notation inevitably introduces $\delta$ tensors to encode some graph problems.
-A $\delta$ tensor of rank $d$ is defined as
+a standard tensor network notation is equivalent to the generalized tensor network by introducing $\delta$ tensors,
+where a $\delta$ tensor of rank $d$ is defined as
 \begin{equation}
@@
 
-Given a graph
+Let us consider the following King's graph.
 
@@
 
-Its standard tensor network representation includes a $\delta$ tensors on each vertex, so its graphical representation is as bellow.
+By mapping the independent set problem to a standard tensor network, we have the following graphical representation.
 
@@
         \foreach \y in {1,...,5}
-            \filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
     \foreach \x in {1,...,5}
@@
 \end{tikzpicture}}
-Here, we use a small circle on a vertex to represent a diagonal $\delta$ tensor.
-Its rank is $8$ in the bulk.
-If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has a rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
-If we treat it as the following generalized tensor network
+
+In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor of rank $8$.
+If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
+If we relax the restriction that each label appears exactly twice. We have the following hypergraph representation of a generalized tensor network.
 
@@
         \foreach \y in {1,...,5}{
-            \filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
+            %\filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
         }
@@
 Here, we use different colors to distinguish different hyperedges.
-The vertex tensor is always rank $1$ in this representation.
-Again, if we contract this tensor network in the columnwise contraction order, we can see the maximum intermediate tensor has rank $\sim L$ by counting the colors.
+A vertex tensor always has rank $1$ and is not shown here since it does not change the contraction complexity.
+Again, if we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be see by counting the number of colors.
 
 \section{Generalizing to other graph problems}\label{app:otherproblems}
-There are some other graph problems that can be encoded to a tensor network.
-To understand its representation power, it is a good starting point to connect it with dynamic programming because
-a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small tree width efficiently~\cite{Courcelle1990,Barr2020}.
-It can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
-The graph problem can be expressed in the tensor network language is clearly much less than that can be expressed by dynamic programming.
-For example, it is hard to determine whether a collection of vertices forms a path in a graph using the tensor network language, while this problem is MSO definable.
-As a gain, a tensor network has a nicer analytic property, which makes contraction order optimization, generic programming and utilizing BLAS libaries very convenient.
+%There are some other graph problems that can be encoded to a tensor network.
+%To understand its representation power, it is a good starting point to connect it with dynamic programming because
+%a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
+%Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small tree width efficiently~\cite{Courcelle1990,Barr2020}.
+%It can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
+%The graph problem can be expressed in the tensor network language is clearly much less than that can be expressed by dynamic programming.
+%For example, it is hard to determine whether a collection of vertices forms a path in a graph using the tensor network language, while this problem is MSO definable.
+%As a gain, a tensor network has a nicer analytic property, which makes contraction order optimization, generic programming and utilizing BLAS libaries very convenient.
 %\iffalse
-%The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:tensor} can be expressed in MSO as
+%The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:edgetensor} can be expressed in MSO as
 %\begin{align}
@@
 %\fi
-In the following, we introduce some other problems that can be expressed by a tensor network.
+%In the following, we introduce some other problems that can be expressed by a tensor network.
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-Sometimes, one may be interested in knowing maximal solutions to understand why his or her program is trapped in a local minimum.
+Finding maximal independent sets of a graph is equivalent to finding the maximal cliques of its complement graph, so in the following we only discuss how to find maximal independent sets.
+Sometimes, one may be interested in knowing maximal independent sets to understand why his or her program for solving MIS is trapped in a local minimum.
 Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
@@
 \end{equation}
-where $b_k$ is the number of maximal independent sets of size $k$ in $G$.
-Obviously, $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
+where $b_k$ is the number of maximal independent sets of size $k$ in graph $G=(V, E)$.
+Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
 $I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
@@
 Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent set where there exists no vertex $v$ such that $I_m \cap N[v]  = \emptyset$.
+A maximal independent set $I_m$ is an independent set where there exists no vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$.
 We can modify the tensor network for computing the independence polynomial to include this restriction.
@@
 \end{equation}
-Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$, counted as $x_{v}$,
-and if any of the neighborhood vertices is in $I_{m}$, i.e., $\exists i \in \{1,2,\ldots, |N(v)|\}$ s.t. $s_{i} = 1$, then $v$ cannot be in $I_{m}$.
+Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$ and contribute a factor $x_{v}$,
+otherwise, if any of the neighborhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
 As an example, for a vertex of degree 2, the resulting rank-3 tensor is
@@
 
-With the tensors defined as $T(x_v)$, we can perform a similar computation of contracting the tensor network with the same tensor element types as described in the previous section~\ref{sec:indpoly}, the result of which then produces the maximal independence polynomial.
+By contracting this tensor network with generic element type,
+we can compute the maximum independent set properties such as maximal independence polynomial, enumerating maximal independent sets.
 Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
@@
 The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
-However, in most sparse graphs, this tensor network contraction approach is still significantly faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+However, for most sparse graphs, this tensor network contraction approach is still much faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+We show the benchmark of computing the maximal independent set properties in \Fig{fig:benchmark-maximal},
+including a comparison to the Bron-Kerbosch algorithm from Julia package Graphs~\cite{Graphs}.
+%Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
+the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
+The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
+while the tensor network does counting much more efficiently.
+Due to the memory limit, this Bron-Kerbosch algorithm stops working at size $70$ and above.
 
@@
 
-We show the benchmark of computing the maximal independent set properties in \Fig{fig:benchmark-maximal},
-including a comparison to the Bron-Kerbosch algorithm from the package Graphs~\cite{Graphs}.
-Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
-the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
-The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
-while the tensor network does counting much more efficiently.
-Due to the memory limit, this Bron-Kerbosch algorithm stops working at size $70$ and above.
-
 \subsection{Matching problem}
@@
 where $k$ is the number of matches, and coefficients $c_k$ are the corresponding counting.
-We define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
+We map an edge $(u, v) \in E$ to a label $\langle u, v\rangle \in \{0, 1\}$ in a tensor network,
+where $1$ means two vertices of an edge are matched, $0$ means otherwise.
+Then we define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
 \begin{equation}
@@
     1, & \langle v, w \rangle = 0 \\
-    x, & \langle v, w \rangle = 1.
+    x, & \langle v, w \rangle = 1,
 \end{cases}
 \end{equation}
-Here, we use bond index $\langle v, w \rangle \in \{0, 1\}$ ($\langle v, w \rangle$ and $\langle w,v\rangle$ are equivalent) to label tensors,
-where $1$ means two vertices of an edge are matched, $0$ means otherwise.
+where label $\langle v, w \rangle$ is equivalent to $\langle w,v\rangle$.
+Here, a vertex tensor specifies the restriction that a vertex can not be in two matched edges, while an edge tensor contributes the variable in the polynomial.
 
 \subsection{k-Coloring}
-Let us use 3-coloring on the vertex as an example. We can define a vertex tensor as
-\begin{equation}
-    W = \left(\begin{matrix}
+Let us use 3-coloring problem defined on vertices as an example.
+For a vertex $v$, we define the degree of freedoms $c_v\in\{1,2,3\}$ and a vertex tensor labeled by it as
+\begin{equation}
+    W(v) = \left(\begin{matrix}
         r_v\\
@@
         b_v
-    \end{matrix}\right),
-\end{equation}
-and an edge tensor as
+    \end{matrix}\right).
+\end{equation}
+For an edge $(u, v)$, we define an edge tensor as a matrix labeled by $(c_u, c_v)$ to specify the constraint
 \begin{equation}
@@
 The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
-By designing generic types as tensor elements, one can get all possible colorings.
-Similarly, one can define the k-coloring problem on edges too.
+By designing generic types as tensor elements, one can get other properties.
+Similarly, one can define the k-coloring problem on edges too by switching the roles of edges and vertices.
 
@@
 Max cut problem is also known as the boolean spinglass problem.
-Its tensor network representation does not contain vertex tensors.
-The edge tensor can be defined as
+For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
+Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labeled by $(s_i, s_j)$
 \begin{equation}
@@
 \end{equation}
-We can also define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,
+Similar to other problems, we can define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,
 where its $k$th coefficient is two times the number of configurations of cut size $k$.
@@
 \subsection{Set packing}
-Set packing is the hypergraph version of the maximum independent set problem, where each set corresponds to a vertex, each element corresponds to a hyperedge.
-To solve the set packing problem, we just remove the rank 2 restriction of an edge tensor
+Set packing is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
+To solve the set packing problem, we just remove the rank 2 restriction of the edge tensor in \Eq{eq:edgetensor}
 \begin{equation}
@@
 
-\section{Discrete Fourier transform for computing the independence polynomial}\label{app:fft}
+\section{The discrete Fourier transform approach to computing the independence polynomial}\label{app:fft}
 

### 2021-12-26 paper/figures/masktree.tex
fix figures

\documentclass[crop,tikz]{standalone}

\begin{document}
\begin{tikzpicture}[scale=1.5]
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.0, 0.0) (1234) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.8, -0.6) (1235) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.8, -0.6) (1236) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.3, -1.2) (1237) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.30000000000000004, -1.2) (1238) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (1.3, -1.2) (1239) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.30000000000000004, -1.2) (1240) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.6, -1.8) (1241) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.0, -1.8) (1242) {};
\draw[<-, line width=0.5pt] (1234) -- (1235);
\draw[<-, line width=0.5pt] (1234) -- (1236);
\draw[<-, line width=0.5pt] (1235) -- (1237);
\draw[<-, line width=0.5pt] (1235) -- (1238);
\draw[<-, line width=0.5pt] (1236) -- (1239);
\draw[<-, line width=0.5pt] (1236) -- (1240);
\draw[<-, line width=0.5pt] (1237) -- (1241);
\draw[<-, line width=0.5pt] (1237) -- (1242);
\node[] at (0.0, 0.3) {$\alpha(G)$};
\node[] at (-1.6, -1.2) {$A$};
\node[] at (-0.30000000000000004, -1.5) {$B$};
\node[] at (-0.8, -0.3) {$C$};
\node[] at (-0.8, -0.8999999999999999) {$*$};
\node[] at (0.0, -2.2) {\large (a)};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.0, 0.0) (1243) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.2, -0.6) (1244) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.8, -0.6) (1245) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.7, -1.2) (1246) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.7, -1.2) (1247) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (5.3, -1.2) (1248) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.3, -1.2) (1249) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.4, -1.8) (1250) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.0, -1.8) (1251) {};
\draw[->, draw=red, line width=0.5pt] (1243) -- (1244);
\draw[->, draw=red, line width=0.5pt] (1243) -- (1245);
\draw[->, draw=red, line width=0.5pt] (1244) -- (1246);
\draw[->, draw=red, line width=0.5pt] (1244) -- (1247);
\draw[->, draw=red, line width=0.5pt] (1245) -- (1248);
\draw[->, draw=red, line width=0.5pt] (1245) -- (1249);
\draw[->, draw=red, line width=0.5pt] (1246) -- (1250);
\draw[->, draw=red, line width=0.5pt] (1246) -- (1251);
\node[] at (4.0, 0.3) {$\overline{\alpha(G)}$};
\node[] at (2.4000000000000004, -1.2) {$\overline{A}$};
\node[] at (3.7, -1.5) {$\overline{B}$};
\node[] at (3.2, -0.3) {$\overline{C}$};
\node[] at (3.2, -1.0) {\small Eq. 6.9};
\node[] at (4.0, -2.2) {\large (b)};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.0, 0.0) (1252) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.2, -0.6) (1253) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.8, -0.6) (1254) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.7, -1.2) (1255) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.7, -1.2) (1256) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (9.3, -1.2) (1257) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.3, -1.2) (1258) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.4, -1.8) (1259) {};
\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.0, -1.8) (1260) {};
\draw[<-, draw=black, line width=0.5pt] (1252) -- (1253);
\draw[<-, draw=black, line width=0.5pt] (1252) -- (1254);
\draw[<-, draw=black, line width=0.5pt] (1253) -- (1255);
\draw[<-, draw=black, line width=0.5pt] (1253) -- (1256);
\draw[<-, draw=black, line width=0.5pt] (1254) -- (1257);
\draw[<-, draw=black, line width=0.5pt] (1254) -- (1258);
\draw[<-, draw=black, line width=0.5pt] (1255) -- (1259);
\draw[<-, draw=black, line width=0.5pt] (1255) -- (1260);
\node[] at (8.0, 0.3) {$s_{\alpha(G)}\infty^{\alpha(G)}$};
\node[] at (6.25, -1.2) {$A'\circ\overline{A}$};
\node[] at (7.7, -1.5) {$B'\circ\overline{B}$};
\node[] at (7.2, -0.3) {$C'\circ\overline{C}$};
\node[] at (7.2, -0.8999999999999999) {$*$};
\node[] at (8.0, -2.2) {\large (c)};
\end{tikzpicture}
\end{document}

### 2021-12-26 paper/paper.tex
fix figures

@@
 which includes: maximum size of such sets, the number of sets of a given size, enumeration of sets of a given size.
-It can be generalized to compute properties of other problems like cut size, coloring, maximal cliques et al.
 %Although the computational complexity inevitably scales exponentially with treewidth of the graph,
@@
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ the tree width of the problem graph.
+Our generic programming tensor network method can be used to compute properties of other problems like cut size, coloring, maximal cliques et al.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs\blue{remove some examples}.
@@
 Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs. 
+Our method can also be used for finding ``maximal'' independent set properties.
+Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
+a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+We show how to compute properties related to maximal independent sets as well as other combinatorial optimization problems in \App{app:otherproblems}.
 The implementation of our algorithm is publicly available online: ~\cite{repolink}.
@@
             \hline
-            \textbf{element type}     & \textbf{purpose} \\
-            {$\mathbbm{R}$}     & {real number for counting independent sets} \\
-            {$\mathbbm{C}$}     & {complex number for fitting the independence polynomial with fast Fourier transform} \\
-            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {finite field algebra for fitting the independence polynomial exactly using number theory} \\
-            {T} (\Eq{eq:tropical})    & {tropical number for finding the independence number} \\
-            {P1} (\Eq{eq:countingtropical})     & {polynomial truncated to largest order, i.e. the tropical number with counting field for finding the independence number and the number of MISs} \\
-            {P2} (\Eq{eq:max2poly})     & {polynomial truncated to largest two orders for counting MISs and independent sets of size $\alpha(G)-1$} \\
-            {PN} (\Eq{eq:polynomial})     & {polynomial number for computing the independence polynomial directly} \\
-            {P1+S1}     & {P1 with configuration sampler (\Eq{eq:singleconfig}) as its counting field for finding the independence number and one MIS} \\
-            {P1+SN} (\Eq{eq:countingtropicalset})    & {P1 with configuration enumerator (\Eq{eq:set}) as its counting field for finding the independence number and enumeration of all MISs} \\
+            \textbf{element type}     & \textbf{property} \\
+            {$\mathbbm{R}$}     & {independent sets} \\
+            {$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
+            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
+            {T} (\Eq{eq:tropical})    & {MIS size} \\
+            {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
+            {P2} (\Eq{eq:max2poly})     & {MISs and independent sets of size $\alpha(G)-1$} \\
+            {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
+            {P1+S1}     & {MIS size and one MIS} \\
+            {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
             \bottomrule
         \end{tabularx}
-    \caption{Tensor element types and their purposes in calculating various independent set properties.}\label{tbl:generictypes}
+    \caption{Tensor element types and the property we want to calculate when we introduce them.}\label{tbl:generictypes}
 \end{minipage}
-\red{we should include maximal independence polynomial and counting, enumeration in this table as well.}
-\blue{I do not think so. Network structure and element types are two degree of freedoms,
-maximal IS is different network structure. We can use the above algebra in any network structure.}
 \end{table}
@@
 \section{Maximum independent sets and its counting}
-\subsection{Tropical algebra for finding the independence number and counting MISs}
-In the previous section, we focused on computing the independence polynomial for a graph $G$ of given independence number $\alpha(G)$, but we did not show how to compute this number.
+\subsection{Tropical algebra for finding the MIS size and counting MISs}
+In the previous section, we focused on computing the independence polynomial for a graph $G$ of given MIS size $\alpha(G)$, but we did not show how to compute this number.
 The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
@@
 for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
-Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
-a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-We can also compute the maximal independence polynomial and enumerate maximal independent sets with a different tensor network mapping, and this is described in \Sec{sec:maximal}.
 To enumerate all independent sets, we designed an algebra defined on sets of bitstrings.
@@
 \subsection{Bounding the MIS enumeration space}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
+    \caption{Bounded enumeration of maximum independent sets.
+In the graph, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard multiplication.
+(a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
+     (b) is the backward pass for computing boolean gradients as masks.
+     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
+     \label{fig:bounding}
+\end{figure}
+
 When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
 To speed up the computation and reduce space overhead, we bound the searching space using the MIS size $\alpha(G)$.
-First, we compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
-Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
-Finally, we perform masked matrix multiplication using the new element type with the above algebra, \Eq{eq:countingtropicalset}, for obtaining all configurations.
+As shown in \Fig{fig:bounding}, (a) we first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
+(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
+(c) Finally, we perform masked tensor network contraction using the element type with the algebra in \Eq{eq:countingtropicalset} to obtaining all configurations.
 Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
@@
 Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
-\begin{equation}
+\begin{equation}\label{eq:adrule}
 \overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
@@
     The time in these plots only includes tensor network contraction, without taking the contraction order finding and just in time compiling time into account.
-    \red{for each graph size, is there only one graph?}\blue{yes}
     (a) tree width versus the number of vertices for the benchmarked graphs. 
     Legends are the data types that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
-    (b) The computing time for calculating the independence number and for counting of the number of independent sets, the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
+    (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$ (denoted as ``MISs and (MIS-1)s'').
     (c) The computing time for calculating the independence polynomials with different approaches.
@@
 In this paper, we introduce an abstract algebra formalism to compute properties of independent sets.
-The properties include the independence number, number of independent set of a given size, and enumeration of independent sets of a give size.
+The properties include the MIS size, number of independent set of a given size, and enumeration of independent sets of a give size.
 For each property, we design a algebra being a commutative semiring, and map the property computation to the contraction of a tensor network with such element type.
@@
 \begin{table}[h]
-\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.}
+\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
+Here we only show two updated entries for $L=38,39$ that has not been computed before.}
 \begin{center}
@@
  \hline $L$  & square grid graphs \\
- \hline $ 1$ & 2  \\
- \hline $ 2$ & 7  \\
- \hline $ 3$ & 63  \\
- \hline $ 4$ & 1 234  \\
- \hline $ 5$ & 55 447  \\
- \hline $ 6$ & 5 598 861  \\
- \hline $ 7$ & 1 280 128 950  \\
- \hline $ 8$ & 660 647 962 955  \\
- \hline $ 9$ & 770 548 397 261 707  \\
- \hline $ 10$ & 2 030 049 051 145 980 050  \\
- \hline $ 11$ & 12 083 401 651 433 651 945 979  \\
- \hline $ 12$ & 162 481 813 349 792 588 536 582 997  \\
- \hline $ 13$ & 4 935 961 285 224 791 538 367 780 371 090  \\
- \hline $ 14$ & 338 752 110 195 939 290 445 247 645 371 206 783  \\
- \hline $ 15$ & 52 521 741 712 869 136 440 040 654 451 875 316 861 275  \\
- \hline $ 16$ &  18 396 766 424 410 124 752 958 806 046 933 947 217 821 482 942 \\
- \hline $ 17$ &  14 557 601 701 834 111 295 974 187 104 248 827 765 798 599 152 358 303 \\
- \hline $ 18$ &  26 024 585 612 650 837 861 658 126 921 792 857 026 992 497 268 285 945 167 621 \\
- \hline $ 19$ &  105 105 055 066 577 962 012 604 229 608 317 915 229 737 651 637 019 975 757 755 051 314 \\
- \hline $ 20$ &  958 979 036 662 929 619 406 859 624 886 958 746 851 620 546 557 485 230 898 539 651 354 907 499 \\
- \hline $ 21$ &  19 766 982 580 727 525 559 447 459 703 066 410 506 378 295 841 376 040 664 015 562 851 325 369 819 076 327 \\
- \hline $ 22$ &  920 486 427 724 231 647 653 646 535 134 255 190 048 558 085 587 696 509 535 085 179 014 710 020 739 303 637 413 062 \\
- \hline $ 23$ & 96 836 737 362 332 577 228 126 233 146 266 027 907 220 602 904 916 569 863 928 397 932 638 147 313 462 817 836 132 159 477 643 \\
- \hline $ 24$ & 23 014 876 830 102 973 080 295 375 510 481 185 265 791 418 130 718 634 637 816 237 986 620 978 856 344 595 418 898 906 840 911 239 867 869 \\
- \hline $ 25$ & 12 357 280 628 458 621 610 261 003 683 798 282 889 567 362 022 871 449 310 490 079 744 330 288 088 293 888 381 458 751 196 205 785 114 467 063 479 978 \\
- \hline $ 26$ & 14 989 353 830 657 887 045 253 535 577 369 170 604 561 059 504 403 111 230 207 533 142 521 161 755 543 754 839 412 836 401 335 298 693 619 461 437 872 472 165 615 \\
- \hline $ 27$ &  41 076 048 814 756 904 170 038 431 958 637 474 710 328 322 517 168 428 037 124 975 797 939 221 729 929 250 098 889 601 666 346 169 376 778 430 801 983 574 787 538 529 309 191 \\
- \hline $ 28$ &  254 296 368 874 677 123 746 928 211 898 730 495 474 495 246 876 690 760 159 507 126 754 738 599 026 016 292 991 448 162 576 157 292 681 301 528 315 863 006 160 203 433 527 765 235 617 478 \\
  \hline $ 29$ & 3 556 619 491 488 838 337 298 644 336 171 591 528 960 687 731 348 622 394 588 805 214 244 031 766 315 339 709 627 465 589 460 212 852 431 000 227 410 783 701 037 177 097 019 793 172 369 009 198 594 591 \\

### 2021-12-26 paper/figures/plot.py

@@ -21,31 +21,37 @@ class PLT(object):
             plt.plot(ns, [x[1] for x in nw], label="space complexity (tree width)")
             plt.plot(ns, [x[2] for x in nw], label="time complexity")
             plt.xlabel("number of vertices, $|V|$")
-            plt.ylabel("log2 value")
+            plt.ylabel("complexity")
+            tws = np.arange(0, 35, 5)
+            plt.yticks(tws, ["$2^{%d}$"%tw for tw in tws])
             plt.legend(loc="upper left", fontsize=FS, ncol=1)
 
             ax=plt.subplot(222)   # size
             cornertex("(b)", ax, offset=(0,0))
-            for k,(prefix, l) in enumerate([("counting_sum", r"$\mathbb{R}$"), ("size_max", "T"), ("counting_max", "P1"), ("counting_max2", "P2")]):
+            for k,(prefix, l) in enumerate([("counting_sum", r"counting ISs ($\mathbb{R}$"), ("size_max", "MIS size (T"), ("counting_max", "counting MISs (P1"), ("counting_max2", r"counting MISs and (MIS-1)s (P2")]):
                 for device in ["CPU", "GPU"]:
                     datafile = "../../benchmarks/data/"+prefix+"-r3-"+device+".dat"
                     if os.path.exists(datafile):
                         y = np.loadtxt(datafile) / 1e9
-                        plt.plot(ns[:len(y)], y, label="%s (%s)"%(l, device), lw=1.5, color="C%d"%k, ls="--" if device=="GPU" else "-")
+                        plt.plot(ns[:len(y)], y, label="%s, %s)"%(l, device), lw=1.5, color="C%d"%k, ls="--" if device=="GPU" else "-")
             plt.yscale("log")
             plt.xlabel("number of vertices, $|V|$")
             plt.ylabel("time/s")
-            plt.legend(loc="upper left", fontsize=FS, ncol=2)
+            plt.legend(loc="upper left", fontsize=FS, ncol=1)
             plt.ylim(1e-3,3e3)
 
             ax = plt.subplot(223)   # IDP
             cornertex("(c)", ax, offset=(0,0))
-            for k,(prefix, l) in enumerate([("counting_all_(fft)", r"$\mathbb{C}$"), ("counting_all_(finitefield)", r"GF$(p)$"), ("counting_all", "PN")]):
+            for k,(prefix, l) in enumerate([
[…]

### 2021-12-27 paper/paper.tex
fix xungao comments

@@
 Our generic programming tensor network method can be used to compute properties of other problems like cut size, coloring, maximal cliques et al.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant, Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs\blue{remove some examples}.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant and overlap gap property of three regular graphs.
 \end{abstract}
@@
 
-\blue{independence polynomial at -1~\cite{Bousquet2008,Levit2009},
-two motivations of computing independence polynomial: 1. Lee-Yang zero~\cite{Lee1952,Yang1952}, 2. Lov{\'a}sz local lemma~\cite{Scott2005}.
-}
 \section{Introduction}
@@
 The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
-Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within a factor $|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$ ~\cite{Hastad1996}.
+Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
+meaning there is unlikely a polynomial time algorithm to find an independent set with size $\alpha(G)/|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
 Naive exhaustive search for an MIS requires computing time $O\left(2^{|V|} \right)$.
@@
 map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}, but also for it is a well know NP-complete problem that can be mapped from
- to many other important combinatorial optimization problems in polynomial time such as circuit satisfiability~\cite{}, the maximum clique problem and the maximum vertex cover~\cite{Moore2011} problems.
+ many other important combinatorial optimization problems in polynomial time such as 3-satisfiability problem, the maximum clique problem and the maximum vertex cover problem~\cite{Moore2011}.
 
@@
 In this paper, we do not limit our discussion to finding one of the maximum indepedent sets and its size.
-There are many other interesting problems pertaining to independent sets, such as the number of independent sets at a given size
+There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
 and enumerating independent sets at a give size or what we call computing \textit{properties}.
@@
 in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready};
-they can, for example, be used to understand phase transitions, to analyse the overlap gap properties~\cite{Gamarnik2013, Gamarnik2019} and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
-The problem of computing the independence polynomial belongs to the complexity class \#P-hard.
-One approach to exactly compute the independence polynomial requires a computational time of $O(1.442^{|V|})$~\cite{Ferrin2014}
-\blue{I am not sure about this complexity, this is based on the naive analysis of theorem 2.2 in ~\cite{Ferrin2014}}.
-There are some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on computing the independence polynomial exactly.
+they can, for example, be used to understand phase transitions, to analyse the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
+Finding the number of independent sets of a given size is equivalent to computing the coefficients of independence polynomial,
+which is a useful graph characteristics that can related to Euler characteristics of the independence complex~\cite{Bousquet2008,Levit2009}, partition functions~\cite{Lee1952,Yang1952} et al.
+Computing independence polynomials belongs to the complexity class \#P-hard 
+and only exponential algorithms~\cite{Ferrin2014} are known to compute it exactly.
+There are also some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we mainly focus on computing the independence polynomial exactly.
 We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
@@
 For cases when the tensors being too large to fit into a GPU, slicing technique can be used to further reduce the space consumption.
-Lastly, we provide a few examples and show that this toolbox can be used to calculate the hard-square entropy constant,
-Euler characteristics of the independence complex, partition functions, and finite-temperature phase transitions on square-lattice graphs. 
+Lastly, we provide a few examples and show that this toolbox can be used to calculate the hard-square entropy constant and overlap gap property. 
 Our method can also be used for finding ``maximal'' independent set properties.
@@
 
-\begin{definition}[Generic programming]
+\begin{definition}[Generic programming ~\cite{Stepanov2014}]
    Generic programming is an approach to programming that focuses on designing algorithms and data structures so that they work in the most general setting without loss of efficiency.
-~\cite{Stepanov2014}
 \end{definition}
@@
 \end{equation}
-On each edge $(u, v)$, we define a matrix $B$ indexed by $(s_u, s_v)$ as
+We use subscripts to index tensor elements, e.g. $W(x_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i)_1=x_i$ is the second element associated with to $s_i=1$.
+Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
 \begin{equation}
@@
         1 & 0
-    \end{matrix}\right), \label{eq:edgetensor}
+    \end{matrix}\right). \label{eq:edgetensor}
 \end{equation}
@@
 \end{equation}
+To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
+and define the above operations and constants correspondingly.
 When we are only interested in knowing the MIS size, we can drop the counting field.
@@
 \begin{example}\label{eg:setalgebra}
-    For elements being bit vectors of length $5$, we have the following set algebra
+    For elements being bit strings of length $5$, we have the following set algebra
 \begin{equation*}
@@
 To enumerate all independent sets, 
-we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is the standard basis vector of size $|V|$ and having 1 at index $i$.
+we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
 The vertex and edge tensors are thus
@@
 or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
-For example, to enumerate only the MISs, with the tropical algebra, we define $s(k) = (s_{k}, k)$, where the coefficients follows the algebra in \Eq{eq:set} and the orders follows the max-plus tropical algebra.
+As long as the coefficients in a truncated polynomial forms a commutative semiring, the polynomial itself is a commutative semiring.
+For example, to enumerate only the MISs, with the tropical algebra, we define $s_{k}\infty^k$,
+where the coefficient follows the algebra in \Eq{eq:set} and the orders follows the max-plus tropical algebra.
 The combined operations become: 
@@
     The time in these plots only includes tensor network contraction, without taking the contraction order finding and just in time compiling time into account.
+    Legends are properties, data types and devices that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
     (a) tree width versus the number of vertices for the benchmarked graphs. 
-    Legends are the data types that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
     (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$ (denoted as ``MISs and (MIS-1)s'').
@@
 
-\subsubsection{Euler characteristics of independence complex}
-
-\subsubsection{Partition functions and finite-temperature phase transitions}
-
-\subsubsection{Computing the Hamming distance statistics}
+\subsubsection{Computing the overlap gap property}
 
@@
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-Finding maximal independent sets of a graph is equivalent to finding the maximal cliques of its complement graph, so in the following we only discuss how to find maximal independent sets.
-Sometimes, one may be interested in knowing maximal independent sets to understand why his or her program for solving MIS is trapped in a local minimum.
-Then instead of counting all independent sets, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017} would be more helpful.
+Finding maximal independent sets of a graph is equivalent to finding the maximal cliques of its complement graph, so in the following we mainly discuss how to find maximal independent sets.
+Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent set where there exists no vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$.
+Similar to the independence polynomial, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017},
+which can help us understand why the program for solving MIS is trapped in a local minimum.
 Concretely, it is defined as
@@
 
-Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent set where there exists no vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$.
 We can modify the tensor network for computing the independence polynomial to include this restriction.
@@
 For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
-Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labeled by $(s_i, s_j)$
+Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labeled by $s_is_j$
 \begin{equation}
@@
         x_{\langle i, j\rangle} & 1
-    \end{matrix}\right).
-\end{equation}
+    \end{matrix}\right),
+\end{equation}
+where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spinglass.
 Similar to other problems, we can define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,
@@
 
-We also computed independence polynomial rigorously for these lattices in our Github repo\blue{add link to the repo}.
+We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
 

### 2021-12-27 paper/paper.tex
new data n=100 configurations

@@
 We show how to compute properties related to maximal independent sets as well as other combinatorial optimization problems in \App{app:otherproblems}.
-The implementation of our algorithm is publicly available online: ~\cite{repolink}.
 
@@
     The time in these plots only includes tensor network contraction, without taking the contraction order finding and just in time compiling time into account.
-    Legends are properties, data types and devices that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
+    Legends are properties, algebra and devices that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
     (a) tree width versus the number of vertices for the benchmarked graphs. 
@@
 With the ability to enumerate configurations, we can analyse the landscape of the target problem, like the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-We compute all MIS configurations for two random 3 regular graph instances of size 200, and show the Hamming distance statistics in \Fig{fig:hamming}.
-Some figure has single peak structure while some other has multiple peaks. Multiple peak structure indicates disconnected clusters in the configuration space.
+We compute all MIS and MIS-1 configurations for two random 3 regular graph instances of size 100, and show the Hamming distance statistics in \Fig{fig:hamming}.
+The multiple peak structure indicates disconnected clusters in the configuration space.
 \begin{figure} 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    \caption{The statistics of Hamming distances between two MIS configurations for two specific three regular graph instance of size $200$.}
+    \caption{The statistics of Hamming distances between two MIS or MIS-1 configurations for two random three regular graph instances of size $100$.}
     \label{fig:hamming}

### 2021-12-27 democode/hamming.jl

@@ -1,33 +1,48 @@
-using GraphTensorNetworks, Random, LightGraphs
+using GraphTensorNetworks, Random, Graphs
 using DelimitedFiles
 
 function case_r3(n, k=3; sc_target, seed=2)
     # generate a random regular graph of size 100, degree 3
-    graph = (Random.seed!(seed); LightGraphs.random_regular_graph(n, k))
+    graph = (Random.seed!(seed); Graphs.random_regular_graph(n, k))
     @assert length(connected_components(graph)) == 1  # connected graph
-    optcode = Independence(graph; optmethod=:tree, sc_target=sc_target, sc_weight=1.0, ntrials=20, βs=0.01:0.05:15.0, niters=50, rw_weight=0.2)
+    optcode = Independence(graph; optimizer=TreeSA(sc_target=sc_target,
+                sc_weight=1.0, ntrials=10, βs=0.01:0.05:25.0, niters=20, rw_weight=2.0))
     return optcode
 end
 
-function compute_configs(filename; seed)
-    se = best_solutions(case_r3(200, 3; sc_target=25, seed=seed); all=true)[].c
-    save_configs(filename, se, format=:text)
+function count_configs(n, seed)
+    se = solve(case_r3(n, 3; sc_target=25, seed=seed), "counting max2")[].coeffs
+    return se
 end
 
-function analyse_hamming(filename)
+function compute_configs(n; seed)
+    se = solve(case_r3(n, 3; sc_target=25, seed=seed), "configs max2 (bounded)")[].coeffs
+    filename = joinpath(@__DIR__, "data", "r3_n$(n)_optconfigs_$seed.dat")
+    save_configs(filename, se[2], format=:binary)
+    filename = joinpath(@__DIR__, "data", "r3_n$(n)_suboptconfigs_$seed.dat")
+    save_configs(filename, se[1], format=:binary)
+end
+
+function analyse_hamming(n; seed)
     hamming = zeros(201)
-    configs = load_configs(filename; format=:text, nflavors=2)
+    f1 = joinpath(@__DIR__, "data", "r3_n$(n)_optconfigs_$seed.dat")
+    f2 = joinpath(@__DIR__, "data", "r3_n$(n)_suboptconfigs_$seed.dat")
+    filename = joinpath(@__DIR__, "data", "r3_n$(n)_hamming_$seed.txt")
+    C1 = load_configs(f1; format=:binary, nflavors=2, bitlength=n)
[…]

### 2021-12-27 paper/figures/plot.py

@@ -137,4 +137,31 @@ class PLT(object):
 
             plt.tight_layout(h_pad=30.0)
 
+    def fig4(self, tp="pdf"):  # independence polynomials
+        with DataPlt(filename="fig3.%s"%tp, figsize=(7,3)) as dp:
+            ax = plt.subplot(121)   # treewidth
+            cornertex2("(a)", ax, offset=(0,0))
+            nv = 100
+            seed = 3
+            datafile = "../../democode/data/r3_n%d_hamming_%d.txt"%(nv,seed)
+            y = np.loadtxt(datafile)
+            n = np.max(np.where(y > 0)[0])
+            plt.bar(range(n), y[:n], lw=1.5, color="C4", ls="-")
+            plt.xlabel("Hamming distance")
+            plt.ylabel("Count")
+            plt.xlim(0, nv)
+            ax.ticklabel_format(style="scientific", scilimits=(-3, 3))
+
+            ax = plt.subplot(122)   # treewidth
+            cornertex2("(b)", ax, offset=(0,0))
+            seed = 5
+            datafile = "../../democode/data/r3_n%d_hamming_%d.txt"%(nv,seed)
+            y = np.loadtxt(datafile)
+            n = np.max(np.where(y > 0)[0])
+            plt.bar(range(n), y[:n], lw=1.5, color="C4", ls="-")
+            plt.xlabel("Hamming distance")
+            plt.xlim(0, nv)
+
+            plt.tight_layout(h_pad=30.0)
+
 fire.Fire(PLT())

### 2021-12-28 paper/paper.tex
update benchmark plot

@@
 The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
-while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$;
+while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, and
 these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
@@
 Especially, for some journals, there is a physical non-color copy, so some requires the figures to be understandable without colors.}
-    \blue{If we use markers, the data poitns are too dense. I prefer not adding markers, not much people read papers with kindle or on paper.}
-    \blue{I used a smaller fontsize, there are still some overlaps. Does it look better (or worse) now?}
     }
@@
 Thank Chris Elord for helping us writing the fastest matrix multiplication libary for tropical numbers, TropicalGEMM.jl, he is a man of speed!
+Thank other open source software developers: Roger Luo, Time Besard and Katharine Hyatt for solving issues voluntarily.
 \blue{funding information}
-
-\blue{I am here!}
 

### 2021-12-28 paper/figures/plot.py

@@ -11,15 +11,14 @@ import os
 
 class PLT(object):
     def fig1(self, tp="pdf"):  # independence polynomials
-        nw = [(10, 3, 7.66), (20, 4, 9.01), (30, 4,9.63), (40, 5,10.36), (50, 8,12.32), (60, 8,12.63), (70, 8,12.55), (80, 10,14.68), (90, 13,16.76), (100, 13,17.67),
-            (110, 15, 18.94), (120, 15, 20.47), (130, 13, 18.23), (140, 17, 21.57), (150, 18, 22.41), (160, 20, 26.23), (170, 19, 24.15), (180, 24, 32.04), (190, 24, 30.27), (200, 25, 32.10)]
-        ns = [x[0] for x in nw]
+        ns =[10*i for i in range(1, 26)]
+        treewidth = np.loadtxt("../../benchmarks/data/treewidth.dat")
         FS = 8
-        with DataPlt(filename="fig1.%s"%tp, figsize=(10,6)) as dp:
+        with DataPlt(filename="fig1.%s"%tp, figsize=(10,7)) as dp:
             ax = plt.subplot(221)   # treewidth
             cornertex("(a)", ax, offset=(0,0))
-            plt.plot(ns, [x[1] for x in nw], label="space complexity (tree width)")
-            plt.plot(ns, [x[2] for x in nw], label="time complexity")
+            plt.plot(ns, treewidth[:,1], label="space complexity (tree width)")
+            plt.plot(ns, treewidth[:,0], label="time complexity")
             plt.xlabel("number of vertices, $|V|$")
             plt.ylabel("complexity")
             tws = np.arange(0, 35, 5)

### 2021-12-28 paper/paper.tex
update benchmark figure

@@
 The graphs that we use in benchmarks are random three regular graphs,
- a typical type of sparse graphs that has a small tree width asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+ a typical type of sparse graphs that has a small tree width that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
 
@@
     Legends are properties, algebra and devices that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
-    (a) tree width versus the number of vertices for the benchmarked graphs. 
+    (a) time and space complexity versus the number of vertices for the benchmarked graphs.
     (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$ (denoted as ``MISs and (MIS-1)s'').
@@
 
-Figure (a) shows the time and space complexity obtained with tensor network optimization algorithm in Ref.~\cite{Kalachev2021}, where the space complexity is the same as the tree width of the problem graph.
+Figure (a) shows the time and space complexity (without slicing) of tensor network contraction for variaty of graph sizes, where the space complexity is the same as the tree width of the problem graph.
+It is obtained with tensor network contraction order optimization algorithm in Ref.~\cite{Kalachev2021}.
+In practice, slicing technique is used to fit the computation into a 32GB memory, the target tree width of slicing is $27$.
 One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
@@
 In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order in enumerating the MISs.
-Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a 32G memory device.
-%and the computing times of configuration enumeration also depend on the size of the target configuration space.
+Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a 32GB memory device.
 

### 2022-01-03 paper/paper.tex
update paper
update

@@
 
+We computed the number of independent sets on square lattices and King's graphs
+with our generic tensor network contraction on GPUs.
+The tensor element type is finite field algebra so that we can reach arbitrary precision.
+We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
+
 \begin{table}[h]
 \caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
-Here we only show two updated entries for $L=38,39$ that has not been computed before.}
+Here we only show two updated entries for $L=38,39$, which to our knowledge, has not been computed before.~\cite{Butera2014}
+}
 \begin{center}
@@
  \hline $L$  & square grid graphs \\
- \hline $ 29$ & 3 556 619 491 488 838 337 298 644 336 171 591 528 960 687 731 348 622 394 588 805 214 244 031 766 315 339 709 627 465 589 460 212 852 431 000 227 410 783 701 037 177 097 019 793 172 369 009 198 594 591 \\
- \hline $ 30$ &  112 377 766 778 527 126 203 646 648 402 050 958 984 330 252 199 994 469 198 044 986 979 798 657 215 652 532 005 142 877 926 040 203 499 014 641 860 333 039 219 325 350 361 465 468 647 055 420 204 598 509 312 491 705 \\
+ \hline $38$ & 616 412 251 028 728 207 385 738 562 656 236 093 713 609 747 387 533 907 560 081 990 229 746 115 948 572 583 817 557 035 128 726 922 565 913 748 716 778 414 190 432 479 964 245 067 083 441 583 742 870 993 696 157 129 887 194 203 643 048 435 362 875 885 498 554 979 326 352 127 528 330 481 118 313 702 375 541 902 300 956 879 563 063 343 972 979\\
+ \hline $39$ &  29 855 612 447 544 274 159 031 389 813 027 239 335 497 014 990 491 494 036 487 199 167 155 042 005 286 230 480 609 472 592 158 583 920 411 213 748 368 073 011 775 053 878 033 685 239 323 444 700 725 664 632 236 525 923 258 394 737 964 155 747 730 125 966 370 906 864 022 395 459 136 352 378 231 301 643 917 282 836 792 261 715 266 731 741 625 623 207 330 411 607\\
   \hline
@@
 \end{table}
+% online digit seperator: https://www.browserling.com/tools/thousands-separator
 
@@
 
-We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
-
 \end{document}

### 2022-01-03 paper/paper.tex
revise abstract

@@
 We introduce a method of using generic programming tensor network to compute various properties of independent sets,
-which includes: maximum size of such sets, the number of sets of a given size, enumeration of sets of a given size.
+which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
 %Although the computational complexity inevitably scales exponentially with treewidth of the graph,
 %our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
-At the same time, our algorithms are very simple to implement and one can directly utilize recent advances in tensor network contraction techniques like near optimal contraction order finding and slicing.
+By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
 %One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices. 
-The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ the tree width of the problem graph.
-Our generic programming tensor network method can be used to compute properties of other problems like cut size, coloring, maximal cliques et al.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant and overlap gap property of three regular graphs.
+The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the tree width of the problem graph.
+Our framework can be easily extended to compute properties of other problems such as the cut size, coloring, and maximal cliques, among others.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the overlap gap property on three regular graphs.
 \end{abstract}

### 2022-01-04 paper/paper.tex
fix typos

--- 2022-01-03 paper/paper.tex
@@
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ the tree width of the problem graph.
-Our generic programming tensor network method can be used to compute properties of other problems like cut size, coloring, maximal cliques et al.
+Our generic programming tensor network method can be used to compute properties of other problems like cut size, colouring, maximal cliques et al.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the hard-square entropy constant and overlap gap property of three regular graphs.
@@
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$.
-The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
+The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
 Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
@@
 The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
-while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, and
+while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small tree width $\text{tw}(G)$, and
 these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we do not limit our discussion to finding one of the maximum indepedent sets and its size.
+In this paper, we do not limit our discussion to finding one of the maximum independent sets and its size.
 There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
@@
 In the main text, we do not have this restriction. An index can appear arbitrary times.
-The graphical representation of our generlized tensor network is hypergraph, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
+The graphical representation of our generalized tensor network is hypergraph, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
 These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors - a high dimensional equivalence of identity matrix.
@@
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex absent (exists) in the set.
-For each label $s_i$, we defined a prametrized rank-one vertex tensor $W(x_i)$ indexed by it as
+For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i)$ indexed by it as
 \begin{equation}
@@
 %where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
-To evalute \Eq{eq:idp}, summing up the products directly is apparently computational inefficient.
+To evaluate \Eq{eq:idp}, summing up the products directly is apparently computational inefficient.
 The standard approach to evaluate a tensor network is to contract two tensors a time with a certain order utilizing the associativity and commutativity of tensor elements.
@@
 
+% \begin{algorithm}[!ht]
+%     \small
+%     \SetAlgoNoLine
+%     %\LinesNumbered
+%     Let vector $\chi = (\chi_0,\chi_1,\chi_2, \ldots, \chi_{\alpha(G)})$ be a random sequence, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
+
+%     \For{$i=0\ldots\alpha(G)$}{
+%         $y_i$ = ${\rm contract\_tensor\_network}(\chi_i)$
+%     }
+
+%     \Return ${\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha{G}})) $\;
+% \end{algorithm}
+
 \section{Maximum independent sets and its counting}
@@
 \begin{equation}
-    W^{\rm MISenum}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
+    W^{\rm MISenum}(\{\boldsymbol{e}_{i}\infty^1\}) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
 The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
-Intuitively, one can use this relation to indentify elements with nonzero gradients in $A$ and $B$ directly,
+Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$ directly,
 however, doing this might make us lost the advantage of using BLAS libraries~\cite{TropicalGEMM}.
@@
     \red{suggestions for the figure: 1.
-the legend seems to overlap the lines, especially the large subfigure.
+the legend seems to overlap the lines, especially the large sub-figure.
 Not sure what's a better way to include the legend there.
@@
 
-Figure (a) shows the time and space complexity (without slicing) of tensor network contraction for variaty of graph sizes, where the space complexity is the same as the tree width of the problem graph.
+Figure (a) shows the time and space complexity (without slicing) of tensor network contraction for variety of graph sizes, where the space complexity is the same as the tree width of the problem graph.
 It is obtained with tensor network contraction order optimization algorithm in Ref.~\cite{Kalachev2021}.
 In practice, slicing technique is used to fit the computation into a 32GB memory, the target tree width of slicing is $27$.
-One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
+One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the tree width.
 %The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
@@
 We call this method generic programming tensor network, and its power is not limited to the independent set problem.
-In \App{app:otherproblems}, we show how to map the maximal independent set problem, matching problem, $k$-coloring problem, max cut problem and set packing problem to tensor networks.
+In \App{app:otherproblems}, we show how to map the maximal independent set problem, matching problem, $k$-colouring problem, max cut problem and set packing problem to tensor networks.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 \end{equation}
-Intuitively, it means if all the neighborhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$ and contribute a factor $x_{v}$,
-otherwise, if any of the neighborhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
+Intuitively, it means if all the neighbourhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$ and contribute a factor $x_{v}$,
+otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
 As an example, for a vertex of degree 2, the resulting rank-3 tensor is
@@
 the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
-The time for the tensor netwrok approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
+The time for the tensor network approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
 while the tensor network does counting much more efficiently.
@@
 
-\subsection{k-Coloring}
-Let us use 3-coloring problem defined on vertices as an example.
-For a vertex $v$, we define the degree of freedoms $c_v\in\{1,2,3\}$ and a vertex tensor labeled by it as
+\subsection{k-Colouring}
+Let us use 3-colouring problem defined on vertices as an example.
+For a vertex $v$, we define the degree of freedoms $c_v\in\{1,2,3\}$ and a vertex tensor labelled by it as
 \begin{equation}
@@
 \end{equation}
-For an edge $(u, v)$, we define an edge tensor as a matrix labeled by $(c_u, c_v)$ to specify the constraint
+For an edge $(u, v)$, we define an edge tensor as a matrix labelled by $(c_u, c_v)$ to specify the constraint
 \begin{equation}
@@
 \end{equation}
-The number of possible coloring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+The number of possible colouring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
 By designing generic types as tensor elements, one can get other properties.
-Similarly, one can define the k-coloring problem on edges too by switching the roles of edges and vertices.
+Similarly, one can define the k-colouring problem on edges too by switching the roles of edges and vertices.
 
 \subsection{Max cut problem}
-Max cut problem is also known as the boolean spinglass problem.
+Max cut problem is also known as the boolean spin glass problem.
 For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
-Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labeled by $s_is_j$
+Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labelled by $s_is_j$
 \begin{equation}
@@
 \end{equation}
-where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spinglass.
+where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
 Similar to other problems, we can define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,

### 2022-01-05 paper/paper.tex
revise abstract and introduction

--- 2022-01-03 paper/paper.tex
@@
 We introduce a method of using generic programming tensor network to compute various properties of independent sets,
-which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
+which include the size of the maximum independent sets, the number and enumeration of independent sets and maximal independent sets of a given size.
+% which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
 %Although the computational complexity inevitably scales exponentially with treewidth of the graph,
@@
 \begin{keywords}
-independent set, tensor network, maximum independent set, independence polynomial
+independent set, tensor network, maximum independent set, independence polynomial, generic programming
 \end{keywords}
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there are many interesting hard computational problems concerning properties of independent sets.
+In graph theory and combinatorial optimization, there are many interesting and hard computational problems concerning various properties of independent sets.
 %An independent set of a graph is a subset of its vertices that no two vertices in this set are adjacent to each other.
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
-The primary insterest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
-Finding $\alpha(G)$ is a hard computational problem; moreover, it is NP-hard to even approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
+One of the independent set properties that many computational complexity theorists are most interested in is to find a maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$.
+% The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
+Finding $\alpha(G)$ exactly is a hard computational problem, and it is NP-hard even to approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
 meaning there is unlikely a polynomial time algorithm to find an independent set with size $\alpha(G)/|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for an MIS requires computing time $O\left(2^{|V|} \right)$.
-People developed more efficient exact algorithms for finding MISs, including the branching algorithms~\cite{Tarjan1977,Robson1986} and dynamic programming.
+Naive exhaustive search for an MIS requires a computational time of $O\left(2^{|V|} \right)$.
+More efficient exact algorithms have been developed for finding MISs, such as the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
 The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
-while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, and
-these methods can produce algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-People are eager to find better algorithms for solving the MIS problem;
-not only for it has a wide range of applications in scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
-map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}, but also for it is a well know NP-complete problem that can be mapped from
- many other important combinatorial optimization problems in polynomial time such as 3-satisfiability problem, the maximum clique problem and the maximum vertex cover problem~\cite{Moore2011}.
+while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
+% People are eager to find better algorithms for solving the MIS problem;
+There is immense interest in finding better algorithms to solve the MIS problem, not only because it has 
+a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
+% scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
+% map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}, 
+but also because it is a well-known NP-complete problem that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
 
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we do not limit our discussion to finding one of the maximum indepedent sets and its size.
-There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
-and enumerating independent sets at a give size or what we call computing \textit{properties}.
+In this paper, we do not limit our study to just finding an MIS and its size. 
+We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
+These properties include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
+We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.
+% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
+% and enumerating independent sets at a give size or what we call computing \textit{properties}.
 Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018} \red{cite experiment when it's ready};
-they can, for example, be used to understand phase transitions, to analyse the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} and to identify harder graphs in an ensemble of graphs \red{cite experiment}.
-Finding the number of independent sets of a given size is equivalent to computing the coefficients of independence polynomial,
-which is a useful graph characteristics that can related to Euler characteristics of the independence complex~\cite{Bousquet2008,Levit2009}, partition functions~\cite{Lee1952,Yang1952} et al.
-Computing independence polynomials belongs to the complexity class \#P-hard 
-and only exponential algorithms~\cite{Ferrin2014} are known to compute it exactly.
-There are also some interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we mainly focus on computing the independence polynomial exactly.
-We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
-We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
-Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as ${\rm tw}(G)$.
+in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
+they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+
+Finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial,
+which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
+The computation of independence polynomials belongs to the complexity class \#P-hard 
+and only exponential algorithms~\cite{Ferrin2014} are known to exist for exact computations.
+There are also interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact computations. 
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming, which scales exponentially with the treewidth, ${\rm tw}(G)$, of the graph.
+% We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
+% We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
+% Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as ${\rm tw}(G)$.
 %But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance on sparse graphs.
-Its high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
-People developed algorithms to optimize the contraction order for tensor networks with thousands of vertices,
-and the optimized contraction order gives us a near optimal space complexity $2^{\sim{\rm tw}(G)}$ to contract the tensor network.
-For cases when the tensors being too large to fit into a GPU, slicing technique can be used to further reduce the space consumption.
-Lastly, we provide a few examples and show that this toolbox can be used to calculate the hard-square entropy constant and overlap gap property. 
-Our method can also be used for finding ``maximal'' independent set properties.
-Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
+We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs); the high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
+Algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices, which produces a near-optimal space complexity of $2^{\sim{\rm tw}(G)}$ for contracting the tensor network.
+For cases where the tensors are too large to fit into a GPU, slicing techniques can be used to further reduce the space consumption.
+Lastly, we provide a few examples and demonstrate the versatility of our tool by computing the entropy constant for some hardcore lattice gases on 2D square lattices and analyzing the overlap gap property on three regular graphs.
+Our method can also be used to find ``maximal'' independent set properties; 
+% Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
 a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum. 
-We show how to compute properties related to maximal independent sets as well as other combinatorial optimization problems in \App{app:otherproblems}.
+We show how to compute properties related to maximal independent sets and properties for other combinatorial optimization problems in \App{app:otherproblems}.
 

### 2022-01-05 paper/paper.tex

@@
 One of the independent set properties that many computational complexity theorists are most interested in is to find a maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$.
-% The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.
+\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
 Finding $\alpha(G)$ exactly is a hard computational problem, and it is NP-hard even to approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
@@
 while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-% People are eager to find better algorithms for solving the MIS problem;
 There is immense interest in finding better algorithms to solve the MIS problem, not only because it has 
 a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
-% scheduling, logistics, social network analysis, bioinformatics, wireless networks and telecommunication,
-% map labelling, computer vision, etc.~\cite{Butenko2003, Wu2015}, 
 but also because it is a well-known NP-complete problem that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+\blue{We need to distinguish ourself in the problem to solve.}
 In this paper, we do not limit our study to just finding an MIS and its size. 

### 2022-01-05 paper/paper.tex
merge Shengtao's branch
new figure

@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-\blue{We need to distinguish ourself in the problem to solve.}
+\blue{We need to distinct ourself in the problem we want to solve.}
 In this paper, we do not limit our study to just finding an MIS and its size. 
@@
 
+\begin{figure}[t] 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
+    \caption{Square square entropy constants for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $1000$.}
+    \label{fig:lattices}
+\end{figure}
+
 \subsubsection{Number of independent sets and hard-square entropy constant}

### 2022-01-05 paper/figures/plot.py

@@ -173,12 +173,34 @@ class PLT(object):
             plt.tight_layout(h_pad=30.0)
 
     def fig5(self, tp="pdf"):  # 
-        with DataPlt(filename="fig2.%s"%tp, figsize=(8,3)) as dp:
+        def plot_and_plot(which, label, errorbase):
+            filename = "../../project/data/%s/entropyconstant_summary.dat"%which
+            mean = np.loadtxt(filename)[:,0]
+            error = np.sqrt(np.loadtxt(filename)[:,1]/1000*1000)
+            ns = np.arange(2,len(mean)+2)
+            if errorbase:
+                plt.errorbar(ns, mean, label=label, yerr=error)
+            else:
+                plt.plot(ns, mean, label=label)
+        with DataPlt(filename="fig5.%s"%tp, figsize=(8,3)) as dp:
             ax = plt.subplot(121)   # treewidth
             cornertex("(a)", ax, offset=(-0.02,0))
-            filename = "../../project/data/square/entropyconstant-%d.dat"%(which, n)
+            plot_and_plot("square", "Square lattice", False)
+            #plot_and_plot("square-0.8", "Square lattice (0.8 filling)", True)
+            plt.xlim(0, 42)
+            plt.ylim(1.3, 1.7)
+            plt.legend()
+            plt.xlabel("lattice size L")
+            plt.ylabel(r"$F(L,L)^{1/{L^2}}$")
             ax=plt.subplot(122)   # size
             cornertex("(b)", ax, offset=(-0.02,0))
+            plot_and_plot("diag", "King's graph", False)
+            plot_and_plot("diag-0.8", "King's graph (0.8 filling)", True)
+            plt.ylim(1.3, 1.7)
+            plt.xlim(0, 34)
+            plt.xlabel("lattice size L")
+            plt.ylabel(r"$F(L,L)^{1/{L^2}}$")
+            plt.legend()
             plt.tight_layout()
 
     def preprocess_entropy(self, which, nmax):

### 2022-01-05 paper/paper.tex
update

@@
 \subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
-In all the examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
+
+\subsubsection{Number of independent sets and hard-square entropy constant}
+In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
 The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices;
 the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
+The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
+We computed the integer sequences for $L=38$ and $L=39$, which is not known before to our knowledge.
+In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
+We also computed hard square entropies for these lattices and shown the results in \Fig{fig:hardsquare}.
 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
-    \caption{Square square entropy constants for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $1000$.}
-    \label{fig:lattices}
+    \caption{Hard square entropy for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $100$.}
+    \label{fig:hardsquare}
 \end{figure}
-
-\subsubsection{Number of independent sets and hard-square entropy constant}
-The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
 

### 2022-01-05 paper/paper.tex
slight change to intro

--- 2022-01-05 paper/paper.tex
@@
 \blue{We need to distinct ourself in the problem we want to solve.}
-In this paper, we do not limit our study to just finding an MIS and its size. 
-We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
-These properties include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
+In this paper, we introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
+%In this paper, we do not limit our study to just finding an MIS and its size. 
+% We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
+Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
 We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.

### 2022-01-05 paper/paper.tex
section 2 revision

@@
 \section{Tensor networks}
-Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts,
-it can be viewed as a generalization of matrix multiplication to multiple tensors contraction.
-People often use Einstein's notation to represent a tensor network, e.g.
-the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
-where we use a label in subscripts to represent a degree of freedom.
-We enumerate these degree of freedoms and accumulate the product of tensor elements to the output tensor.
-In the standard notation of Einstein's summation or tensor network in physics, each index appears precisely twice.
-Hence people can represent a tensor network as a simple graph,
+Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
+it can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
+Einstein's notation is often used to represent a tensor network, e.g.\ the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
+where we use a label in the subscript to represent a degree of freedom.
+One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
+In the standard notation of Einstein's summation or tensor networks in physics, each index appears precisely twice.
+Hence a tensor network can be represented as a simple graph,
 where a tensor is a vertex and two tensors sharing the same label are connected.
-In the main text, we do not have this restriction. An index can appear arbitrary times.
-The graphical representation of our generalized tensor network is hypergraph, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
-These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors - a high dimensional equivalence of identity matrix.
-However, introducing $\delta$ tensors can potentially increase the contraction complexity a lot. We illustrate this point in \App{app:tensorbad}.
+In this work, we do not impose such a restriction, so an index can appear an arbitrary number of times. 
+%In the main text, we do not have this restriction. An index can appear arbitrary times.
+The graphical representation of these generalized tensor networks is hypergraphs, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
+These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, which is a high dimensional equivalence of the identity matrix.
+However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
 \blue{Is it better to introduce the contraction orders here or in example~\ref{eg:tensorcontraction}?}

### 2022-01-05 paper/paper.tex
minor change to intro again to highlight difference in tensor element types

@@
 Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
-We map these independent set problems into generic tensor network contraction with specially designed tensor element algebra.
 % There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
@@
 they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra.
+This is different from standard tensor network methods, where tensor elements are restricted to standard number types such as floating point numbers and integers.
 

### 2022-01-05 paper/paper.tex
section 3 revision

@@
 This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
-To understand the first aspect, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
-One can easily write a function for standard number types that computes the power of $x$ in $\log(n)$ steps using the multiply and square trick.
+To understand the first aspect on generality, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
+One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
 Generic programming does not require $x$ to be a standard number type,
@@
 
-This motivates us to think about what is the most general element type that is allowed in a tensor network contraction program.
+This motivates us to think about what is the most general element type allowed in a tensor network contraction program.
 We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
-A commutative semiring is a semiring with its multiplication operation being commutative, and a semiring is a ring without additive inverse.
+A commutative semiring is a ring with its multiplication operation being commutative and without an additive inverse.
 To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for any arbitrary three elements $a, b, c \in R$.
@@
 The requirement of being commutative is for the tensor contraction result to be independent of the contraction order.
-In the following sections, we show how to compute the properties of independent sets by designing tensor element types as commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
-Table~\ref{tbl:generictypes} summarizes the properties that can be solved by various tensor element types.
+In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
 
@@
             \hline
-            \textbf{element type}     & \textbf{property} \\
+            \textbf{element type}     & \textbf{property/properties to compute} \\
             {$\mathbbm{R}$}     & {independent sets} \\
@@
         \end{tabularx}
-    \caption{Tensor element types and the property we want to calculate when we introduce them.}\label{tbl:generictypes}
+    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
 \end{minipage}

### 2022-01-05 paper/paper.tex
update fig5

@@
 However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
-\blue{Is it better to introduce the contraction orders here or in example~\ref{eg:tensorcontraction}?}
 
@@
             \textbf{element type}     & \textbf{property/properties to compute} \\
-            {$\mathbbm{R}$}     & {independent sets} \\
+            {$\mathbbm{R}$}     & {the number of independent sets} \\
             {$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
@@
             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-            {P2} (\Eq{eq:max2poly})     & {MISs and independent sets of size $\alpha(G)-1$} \\
+            {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
@@
      (b) is the backward pass for computing boolean gradients as masks.
-     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
+     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.\red{line thicker}}
      \label{fig:bounding}
@@
 \end{equation}
+\green{explain delta}
 where $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
@@
 In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
-The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rfloor$ square grids are occupied with vertices;
+The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rceil$ square grids are occupied with vertices;
 the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
@@
 In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
-We also computed hard square entropies for these lattices and shown the results in \Fig{fig:hardsquare}.
+We also computed the quantity $F(L,L)^{1/n}$ as a function of lattice size $L$ for these lattices,
+where $F(L,L)$ is the number of independent sets of a given lattice size and $n$ is the number of vertices.
+The results are shown in \Fig{fig:hardsquare}.
 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
-    \caption{Hard square entropy for lattices defined in \Fig{fig:lattices}, the error bar is scaled by a factor of $100$.}
+    \caption{Mean entropy for lattices defined in \Fig{fig:lattices}.
+    We sampled $1000$ instances for $p=0.8$ lattices, and the error bar is too small to be visible.
+    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/\lfloor pL^2 \rceil}$.
+    }
     \label{fig:hardsquare}
@@
 
-\begin{table}[h]
-\caption{The number of independent sets for King's graphs of size $L\times L$.}
-\begin{center}
-\begin{tabular}{|c| >{\centering\arraybackslash} p{0.85\linewidth}|}
- \hline $L$  & King's graphs \\
- \hline $ 1$ & 2  \\
- \hline $ 2$ & 5  \\
- \hline $ 3$ & 35  \\
- \hline $ 4$ & 314 \\
- \hline $ 5$ & 6 427 \\
- \hline $ 6$ & 202 841 \\
- \hline $ 7$ & 12 727 570  \\
- \hline $ 8$ & 1 355 115 601 \\
- \hline $ 9$ & 269 718 819 131 \\
- \hline $ 10$ & 94 707 789 944 544 \\
- \hline $ 11$ & 60 711 713 670 028 729  \\
- \hline $ 12$ & 69 645 620 389 200 894 313  \\
- \hline $ 13$ &  144 633 664 064 386 054 815 370 \\
- \hline $ 14$ & 540 156 683 236 043 677 756 331 721  \\
- \hline $ 15$ & 3 641 548 665 525 780 178 990 584 908 643  \\
- \hline $ 16$ & 44 222 017 282 082 621 251 230 960 522 832 336 \\
- \hline $ 17$ & 968 503 939 616 343 947 563 582 929 715 005 880 647 \\
- \hline $ 18$ & 38 227 887 218 717 761 202 510 261 178 854 062 185 464 315 \\
- \hline $ 19$ & 2 720 444 488 584 821 384 410 936 779 813 343 554 469 758 172 682 \\
- \hline $ 20$ & 348 970 226 122 589 397 373 342 369 495 005 120 745 703 462 667 115 175 \\
- \hline $ 21$ & 80 700 603 403 721 730 646 640 814 391 653 008 712 705 595 500 769 624 448 529 \\
- \hline $ 22$ & 33 641 616 174 796 469 294 898 513 022 199 100 689 671 634 779 118 656 571 910 751 320 \\
- \hline $ 23$ & 25 281 578 706 433 684 460 290 055 263 926 749 952 595 755 044 481 112 956 327 672 312 862 611  \\
- \hline $ 24$ & 34 249 181 078 331 384 968 700 380 345 306 575 903 108 280 266 841 066 358 396 857 518 201 026 192 547 \\
- \hline $ 25$ & 83 641 072 313 734 275 009 578 098 702 552 656 178 287 685 025 530 905 558 603 555 359 601 823 180 929 638 318  \\
- \hline $ 26$ & 368 222 048 967 797 645 785 624 418 568 072 838 671 415 214 857 177 141 161 824 615 541 365 640 076 045 923 328 316 979  \\
- \hline $ 27$ & 2 922 282 601 123 898 422 508 409 690 495 824 015 239 663 506 989 438 099 254 205 806 998 557 618 858 143 959 252 475 337 777 029  \\
- \hline $ 28$ & 41 807 680 908 633 213 277 041 952 346 680 116 482 996 387 928 973 684 599 097 559 098 879 721 953 006 036 791 335 134 446 016 561 667 772 \\
-  \hline
-\end{tabular}
-\end{center}
-\label{tbl:kingsgrid}
-\end{table}
-
 \end{document}

### 2022-01-05 paper/figures/plot.py

@@ -30,7 +30,7 @@ class PLT(object):
 
             ax=plt.subplot(222)   # size
             cornertex("(b)", ax, offset=(0,0))
-            for k,(prefix, l) in enumerate([("counting_sum", r"counting ISs ($\mathbb{R}$"), ("size_max", "MIS size (T"), ("counting_max", "counting MISs (P1"), ("counting_max2", r"counting MISs and (MIS-1)s (P2")]):
+            for k,(prefix, l) in enumerate([("counting_sum", r"counting ISs ($\mathbb{R}$"), ("size_max", "MIS size (T"), ("counting_max", "counting MISs (P1"), ("counting_max2", r"counting ISs of size $\alpha(G)$ and $\alpha(G)-1$ (P2")]):
                 for device in ["CPU", "GPU"]:
                     datafile = "../../benchmarks/data/"+prefix+"-r3-"+device+".dat"
                     if os.path.exists(datafile):
@@ -42,7 +42,7 @@ class PLT(object):
             plt.legend(loc="upper left", fontsize=FS, ncol=1)
             plt.xticks(range(0, 300, 50))
             plt.xlim(0, 260)
-            plt.ylim(1e-3,3e3)
+            plt.ylim(1e-3,1e4)
 
             ax = plt.subplot(223)   # IDP
             cornertex("(c)", ax, offset=(0,0))
@@ -62,7 +62,7 @@ class PLT(object):
             plt.xticks(range(0, 300, 50))
             plt.xlim(0, 260)
             plt.legend(loc="upper left", fontsize=FS)
-            plt.ylim(1e-3,3e3)
+            plt.ylim(1e-3,1e4)
 
             ax = plt.subplot(224)  # configurations
             cornertex("(d)", ax, offset=(0,0))
@@ -79,7 +79,7 @@ class PLT(object):
             plt.xticks(range(0, 300, 50))
             plt.xlim(0, 260)
             plt.legend(loc="upper left", fontsize=FS)
-            plt.ylim(1e-3,3e3)
+            plt.ylim(1e-3,1e4)
             #plt.plot(twinx(), ns, getindex.(nw, 2), label="tree width",ytickfontsize=12, xticks=:none,yguidefontsize=14,legend=:bottomright, color=:black, ls=:dash, lw=2, ylabel="tree width")
 
             plt.tight_layout()
@@ -115,7 +115,7 @@ class PLT(object):
             plt.xlabel("number of vertices, $|V|$")
             plt.ylabel("time/s")
[…]

### 2022-01-05 paper/paper.tex
section 4 revision

--- 2022-01-05 paper/paper.tex
@@
 
-\section{Independence polynomial}
-\subsection{Independence polynomial}\label{sec:indpoly}
+\section{Independence polynomial} \label{sec:indpoly}
+% \subsection{Independence polynomial}
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
@@
 To compute the independence polynomial of a graph $G = (V, E)$, we reinterpret this problem as a tensor network contraction problem.
-We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex absent (exists) in the set.
-For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i)$ indexed by it as
+We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
+For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i)$ as
 \begin{equation}
@@
 \end{equation}
-We use subscripts to index tensor elements, e.g. $W(x_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i)_1=x_i$ is the second element associated with to $s_i=1$.
+We use subscripts to index tensor elements, e.g.\ $W(x_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i)_1=x_i$ is the second element associated with $s_i=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise.
+and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$.
 
@@
 %where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
-To evaluate \Eq{eq:idp}, summing up the products directly is apparently computational inefficient.
-The standard approach to evaluate a tensor network is to contract two tensors a time with a certain order utilizing the associativity and commutativity of tensor elements.
+To evaluate \Eq{eq:idp}, directly summing up the products is computationally inefficient.
+The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor elements.
 A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
@@
 
-    The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity and multiplicative commutativity of tensor elements:
+    The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements:
     \begin{align*}
@@
         =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e\\
-        =&1+5x+4x^2 \qquad \quad (x_{i} = x)
+        =&1+5x+4x^2 \qquad \quad (x_{i} = x).
     \end{align*}
@@
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
-Then we can treat the tensor elements as polynomials and evaluate the polynomial directly.
-Let us create a polynomial type, and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $(a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
+%Then we can treat the tensor elements as polynomials and evaluate the polynomial directly.
+Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
 We define the algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ as
@@
 Here, the multiplication operation can be evaluated efficiently using the convolution theorem~\cite{Schonhage1971}.
-We can see these operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
-\begin{equation}
-    W^{\rm poly} = \left(\begin{matrix}
+These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
+\begin{equation}
+    W^{\rm PN} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm poly} = \left(\begin{matrix}
+        B^{\rm PN} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \end{equation}
-By contracting the tensor network with the polynomial type, we have contraction result the exact representation of the independence polynomial.
-However, using polynomial numbers suffers from a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
+By contracting the tensor network with the polynomial type, we have the exact representation of the independence polynomial.
+However, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
@@
 With this approach, we do not incur the linear overhead in space.
-However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large independent set sizes.
+However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
 In addition, the number could easily overflow if we use fixed-width integer types.
@@
 \begin{equation}
+\eqname{GF$(p)$}
 \begin{split}
@@
 With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-This is an iterative algorithm that iterates over a sequence of large prime numbers until convergence.
+The algorithm iterates over a sequence of large prime numbers until convergence.
 In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
-Then we solve \Eq{eq:lineareq} using the gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
+Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
 As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change compared with the previous iteration, it indicates the convergence of result and the program terminates.
+If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
 All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
@@
 
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha{G}}) \pmod p) $\;
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
 

### 2022-01-05 paper/paper.tex
update fig5

--- 2022-01-05 paper/paper.tex
@@
 In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
-We also computed the quantity $F(L,L)^{1/n}$ as a function of lattice size $L$ for these lattices,
-where $F(L,L)$ is the number of independent sets of a given lattice size and $n$ is the number of vertices.
+We also computed the quantity $F(L,L)^{1/\lfloor pL^2\rceil}$ as a function of grid size $L$ for these lattices,
+where $F(L,L)$ is the number of independent sets of a given grid size.
 The results are shown in \Fig{fig:hardsquare}.
+Our result for $p=1$ matches those in the literature, and the lattices with hole has much larger average value,
+which has a phsical meaning of the hard lattices with holes have much larger mean entropy than those without holes at the high temperature limit.
 

### 2022-01-05 paper/figures/plot.py

@@ -193,7 +193,7 @@ class PLT(object):
             plt.axhline(y=1.50304, color="k", ls="--")
             plt.legend(fontsize=12)
             plt.xlabel("lattice size L")
-            plt.ylabel(r"$F(L,L)^{1/{L^2}}$")
+            plt.ylabel(r"$F(L,L)^{1/\lfloor pL^2\rceil}$")
             ax=plt.subplot(122)   # size
             cornertex("(b)", ax, offset=(-0.02,0))
             plot_and_plot("diag", "King's graph", False)
@@ -202,7 +202,7 @@ class PLT(object):
             plt.xlim(0, 34)
             plt.axhline(y=1.342643951124, color="k", ls="--")
             plt.xlabel("lattice size L")
-            plt.ylabel(r"$F(L,L)^{1/{L^2}}$")
+            plt.ylabel(r"$F(L,L)^{1/\lfloor pL^2\rceil}$")
             plt.legend(fontsize=12)
             plt.tight_layout()
 

### 2022-01-05 paper/paper.tex

--- 2022-01-05 paper/paper.tex
@@
 In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
-We also computed hard square entropies for these lattices and shown the results in \Fig{fig:hardsquare}.
+We also computed the quantity $F(L,L)^{1/\lfloor pL^2\rceil}$ as a function of grid size $L$ for these lattices,
+where $F(L,L)$ is the number of independent sets of a given grid size.
+The results are shown in \Fig{fig:hardsquare}.
+Our result for $p=1$ matches those in the literature, and the lattices with hole has much larger average value,
+which has a phsical meaning of the hard lattices with holes have much larger mean entropy than those without holes at the high temperature limit.
 

### 2022-01-05 paper/figures/masktree.tex
update bounding

@@
 \begin{tikzpicture}[scale=1.5]
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.0, 0.0) (1234) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.8, -0.6) (1235) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.8, -0.6) (1236) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.3, -1.2) (1237) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.30000000000000004, -1.2) (1238) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (1.3, -1.2) (1239) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.30000000000000004, -1.2) (1240) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.6, -1.8) (1241) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.0, -1.8) (1242) {};
-\draw[<-, line width=0.5pt] (1234) -- (1235);
-\draw[<-, line width=0.5pt] (1234) -- (1236);
-\draw[<-, line width=0.5pt] (1235) -- (1237);
-\draw[<-, line width=0.5pt] (1235) -- (1238);
-\draw[<-, line width=0.5pt] (1236) -- (1239);
-\draw[<-, line width=0.5pt] (1236) -- (1240);
-\draw[<-, line width=0.5pt] (1237) -- (1241);
-\draw[<-, line width=0.5pt] (1237) -- (1242);
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.0, 0.0) (1) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.8, -0.6) (2) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.8, -0.6) (3) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.3, -1.2) (4) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-0.30000000000000004, -1.2) (5) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (1.3, -1.2) (6) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (0.30000000000000004, -1.2) (7) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.6, -1.8) (8) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (-1.0, -1.8) (9) {};
+\draw[latex-, line width=1pt] (1) -- (2);
+\draw[latex-, line width=1pt] (1) -- (3);
+\draw[latex-, line width=1pt] (2) -- (4);
+\draw[latex-, line width=1pt] (2) -- (5);
+\draw[latex-, line width=1pt] (3) -- (6);
+\draw[latex-, line width=1pt] (3) -- (7);
+\draw[latex-, line width=1pt] (4) -- (8);
+\draw[latex-, line width=1pt] (4) -- (9);
 \node[] at (0.0, 0.3) {$\alpha(G)$};
@@
 \node[] at (0.0, -2.2) {\large (a)};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.0, 0.0) (1243) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.2, -0.6) (1244) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.8, -0.6) (1245) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.7, -1.2) (1246) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.7, -1.2) (1247) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (5.3, -1.2) (1248) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.3, -1.2) (1249) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.4, -1.8) (1250) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.0, -1.8) (1251) {};
-\draw[->, draw=red, line width=0.5pt] (1243) -- (1244);
-\draw[->, draw=red, line width=0.5pt] (1243) -- (1245);
-\draw[->, draw=red, line width=0.5pt] (1244) -- (1246);
-\draw[->, draw=red, line width=0.5pt] (1244) -- (1247);
-\draw[->, draw=red, line width=0.5pt] (1245) -- (1248);
-\draw[->, draw=red, line width=0.5pt] (1245) -- (1249);
-\draw[->, draw=red, line width=0.5pt] (1246) -- (1250);
-\draw[->, draw=red, line width=0.5pt] (1246) -- (1251);
-\node[] at (4.0, 0.3) {$\overline{\alpha(G)}$};
-\node[] at (2.4000000000000004, -1.2) {$\overline{A}$};
-\node[] at (3.7, -1.5) {$\overline{B}$};
-\node[] at (3.2, -0.3) {$\overline{C}$};
-\node[] at (3.2, -1.0) {\small Eq. 6.9};
-\node[] at (4.0, -2.2) {\large (b)};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.0, 0.0) (1252) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.2, -0.6) (1253) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.8, -0.6) (1254) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.7, -1.2) (1255) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.7, -1.2) (1256) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (9.3, -1.2) (1257) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.3, -1.2) (1258) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.4, -1.8) (1259) {};
-\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.0, -1.8) (1260) {};
-\draw[<-, draw=black, line width=0.5pt] (1252) -- (1253);
-\draw[<-, draw=black, line width=0.5pt] (1252) -- (1254);
-\draw[<-, draw=black, line width=0.5pt] (1253) -- (1255);
-\draw[<-, draw=black, line width=0.5pt] (1253) -- (1256);
-\draw[<-, draw=black, line width=0.5pt] (1254) -- (1257);
-\draw[<-, draw=black, line width=0.5pt] (1254) -- (1258);
-\draw[<-, draw=black, line width=0.5pt] (1255) -- (1259);
-\draw[<-, draw=black, line width=0.5pt] (1255) -- (1260);
-\node[] at (8.0, 0.3) {$s_{\alpha(G)}\infty^{\alpha(G)}$};
-\node[] at (6.25, -1.2) {$A'\circ\overline{A}$};
-\node[] at (7.7, -1.5) {$B'\circ\overline{B}$};
-\node[] at (7.2, -0.3) {$C'\circ\overline{C}$};
-\node[] at (7.2, -0.8999999999999999) {$*$};
-\node[] at (8.0, -2.2) {\large (c)};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.6, 0.0) (10) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.8, -0.6) (11) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.4, -0.6) (12) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.3, -1.2) (13) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.3, -1.2) (14) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (4.9, -1.2) (15) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (3.9000000000000004, -1.2) (16) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.0, -1.8) (17) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (2.6, -1.8) (18) {};
+\draw[-latex, draw=red, line width=1pt] (10) -- (11);
+\draw[-latex, draw=red, line width=1pt] (10) -- (12);
+\draw[-latex, draw=red, line width=1pt] (11) -- (13);
+\draw[-latex, draw=red, line width=1pt] (11) -- (14);
+\draw[-latex, draw=red, line width=1pt] (12) -- (15);
+\draw[-latex, draw=red, line width=1pt] (12) -- (16);
+\draw[-latex, draw=red, line width=1pt] (13) -- (17);
+\draw[-latex, draw=red, line width=1pt] (13) -- (18);
+\node[] at (3.6, 0.3) {$\overline{\alpha(G)}$};
+\node[] at (1.9999999999999998, -1.2) {$\overline{A}$};
+\node[] at (3.3, -1.5) {$\overline{B}$};
+\node[] at (2.8, -0.3) {$\overline{C}$};
+\node[] at (2.8, -1.0) {\small Eq. 6.9};
+\node[] at (3.6, -2.2) {\large (b)};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.2, 0.0) (19) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.4, -0.6) (20) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.0, -0.6) (21) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (5.9, -1.2) (22) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.9, -1.2) (23) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (8.5, -1.2) (24) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (7.5, -1.2) (25) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (5.6, -1.8) (26) {};
+\node[circle, inner sep=0cm, draw=black, line width=0.03, fill=none, minimum size=0.3cm] at (6.2, -1.8) (27) {};
+\draw[latex-, draw=black, line width=1pt] (19) -- (20);
+\draw[latex-, draw=black, line width=1pt] (19) -- (21);
+\draw[latex-, draw=black, line width=1pt] (20) -- (22);
+\draw[latex-, draw=black, line width=1pt] (20) -- (23);
+\draw[latex-, draw=black, line width=1pt] (21) -- (24);
+\draw[latex-, draw=black, line width=1pt] (21) -- (25);
+\draw[latex-, draw=black, line width=1pt] (22) -- (26);
+\draw[latex-, draw=black, line width=1pt] (22) -- (27);
+\node[] at (7.2, 0.3) {$s_{\alpha(G)}\infty^{\alpha(G)}$};
+\node[] at (5.45, -1.2) {$A'\circ\overline{A}$};
+\node[] at (6.9, -1.5) {$B'\circ\overline{B}$};
+\node[] at (6.4, -0.3) {$C'\circ\overline{C}$};
+\node[] at (6.4, -0.8999999999999999) {$*$};
+\node[] at (7.2, -2.2) {\large (c)};
 \end{tikzpicture}

### 2022-01-05 paper/paper.tex
update bounding

@@
 \end{equation}
-\green{explain delta}
-where $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
+where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
 This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.

### 2022-01-05 paper/paper.tex
update paper figures

@@
      (b) is the backward pass for computing boolean gradients as masks.
-     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.\red{line thicker}}
+     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
      \label{fig:bounding}
@@
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$ (denoted as ``MISs and (MIS-1)s'').
+    (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
     (c) The computing time for calculating the independence polynomials with different approaches.
@@
 With the ability to enumerate configurations, we can analyse the landscape of the target problem, like the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-We compute all MIS and MIS-1 configurations for two random 3 regular graph instances of size 100, and show the Hamming distance statistics in \Fig{fig:hamming}.
+We enumeate all ISs of size $\geq\alpha(G)-1$ for two random 3 regular graph instances of size 100, and show the Hamming distance statistics in \Fig{fig:hamming}.
 The multiple peak structure indicates disconnected clusters in the configuration space.
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    \caption{The statistics of Hamming distances between two MIS or MIS-1 configurations for two random three regular graph instances of size $100$.}
+    \caption{The distribution of Hamming distances between two independent sets of size $\geq\alpha(G)-1$ for two random three regular graph instances of size $100$.}
     \label{fig:hamming}

### 2022-01-07 paper/paper.tex
update paper introduction

@@
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
-One of the independent set properties that many computational complexity theorists are most interested in is to find a maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$.
-\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
-Finding $\alpha(G)$ exactly is a hard computational problem, and it is NP-hard even to approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
-meaning there is unlikely a polynomial time algorithm to find an independent set with size $\alpha(G)/|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-Naive exhaustive search for an MIS requires a computational time of $O\left(2^{|V|} \right)$.
-More efficient exact algorithms have been developed for finding MISs, such as the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
-while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-There is immense interest in finding better algorithms to solve the MIS problem, not only because it has 
-a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
-but also because it is a well-known NP-complete problem that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
+One of the independent set properties that many computational complexity theorists are most interested in is to find a maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$,
+not only because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
+but also because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
+However, a real world application often requires knowing more properties about independent sets,
+which include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
+Some of these properties are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
+they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial,
+which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
+There are also interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact computations~\cite{Ferrin2014}. 
+%\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
+%Finding $\alpha(G)$ exactly is a hard computational problem, and it is NP-hard even to approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
+%meaning there is unlikely a polynomial time algorithm to find an independent set with size $\alpha(G)/|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
+%Naive exhaustive search for an MIS requires a computational time of $O\left(2^{|V|} \right)$.
+%There is immense interest in finding better algorithms to solve the MIS problem, not only because it has 
+%a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
+%but also because it is a well-known NP-complete problem that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
 
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-\blue{We need to distinct ourself in the problem we want to solve.}
 In this paper, we introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
@@
 % We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
-Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
+%Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
 % There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
 % and enumerating independent sets at a give size or what we call computing \textit{properties}.
-Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
-they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+%Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
+%they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
 We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra.
 This is different from standard tensor network methods, where tensor elements are restricted to standard number types such as floating point numbers and integers.
-
-Finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial,
-which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-The computation of independence polynomials belongs to the complexity class \#P-hard 
-and only exponential algorithms~\cite{Ferrin2014} are known to exist for exact computations.
-There are also interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact computations. 
-The complexity of our tensor-network based algorithms is similar to that of dynamic programming, which scales exponentially with the treewidth, ${\rm tw}(G)$, of the graph.
+%The computation of independence polynomials belongs to the complexity class \#P-hard 
+%and only exponential algorithms~\cite{Ferrin2014} are known to exist for exact computations.
+%Traditional algorithms for finding the MIS size problem include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+%The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
+%while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming~\cite{Courcelle1990, Fomin2013},
+which scales exponentially with the tree width, ${\rm tw}(G)$, of the graph.
+For sparse graphs, this quantity is usually much smaller than the number of vertices~\cite{Fomin2006}.
+This indicates it is a method that works better for sparse graphs or graphs,
+unlike another standard approach for solving the MIS size, the branching algorithm ~\cite{Robson1986,Tarjan1977,Xiao2017}, which usually works better for dense graphs.
 % We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.

### 2022-01-07 paper/paper.tex
update paper

@@
 they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial,
+Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-There are also interesting works on efficiently approximating the independence polynomial~\cite{Harvey2018}, but in this work, we focus on exact computations~\cite{Ferrin2014}. 
 %\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
+In this paper, we focus on independent set \textit{property} computation.
+% We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets.
 %In this paper, we do not limit our study to just finding an MIS and its size. 
@@
 %while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-The complexity of our tensor-network based algorithms is similar to that of dynamic programming~\cite{Courcelle1990, Fomin2013},
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving MIS size,
 which scales exponentially with the tree width, ${\rm tw}(G)$, of the graph.

### 2022-01-08 paper/paper.tex
update paper intro

@@
 We introduce a method of using generic programming tensor network to compute various properties of independent sets,
-which include the size of the maximum independent sets, the number and enumeration of independent sets and maximal independent sets of a given size.
+which include the size of the maximum independent sets, the number and enumeration of independent sets of a given size.
 % which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
@@
 but also because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
-However, a real world application often requires knowing more properties about independent sets,
-which include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
-Some of these properties are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+Some other properties, for example, the number and enumeration of independent sets or maximal independent sets of a given size are euqally important in many practical applications, however, are not studied enough.
+Some of them are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
 in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
@@
     (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
-    \red{suggestions for the figure: 1.
-the legend seems to overlap the lines, especially the large sub-figure.
-Not sure what's a better way to include the legend there.
-2.
-I see you guys don't typically use markers.
-We typically use markers to distinguish the different lines, as well as using the color.
-Especially, for some journals, there is a physical non-color copy, so some requires the figures to be understandable without colors.}
     }

### 2022-01-08 paper/figures/plot.py

@@ -87,6 +87,7 @@ class PLT(object):
 
 
     def fig2(self, tp="pdf"):  # independence polynomials
+        ALPHA = 0.5
         nw = [(10, 6, 9.49), (20, 8, 12.40), (30, 9, 13.35), (40, 11, 15.14), (50, 16, 21.26), (60, 17, 22.58), (70, 16, 21.50), (80, 20, 27.48), (90, 26, 35.04), (100, 26, 35.06)]
         ns = [x[0] for x in nw]
         FS = 8
@@ -99,7 +100,7 @@ class PLT(object):
             plt.ylabel("complexity")
             tws = np.arange(0, 36, 5)
             plt.yticks(tws, ["$2^{%d}$"%tw for tw in tws])
-            plt.legend(loc="upper left", fontsize=FS, ncol=1)
+            plt.legend(loc="upper left", fontsize=FS, ncol=1, framealpha=ALPHA)
 
             ax=plt.subplot(122)   # size
             cornertex("(b)", ax, offset=(-0.02,0))
@@ -115,7 +116,7 @@ class PLT(object):
             plt.yscale("log")
             plt.xlabel("number of vertices, $|V|$")
             plt.ylabel("time/s")
-            plt.legend(loc="upper left", fontsize=FS)
+            plt.legend(loc="upper left", fontsize=FS, framealpha=ALPHA)
             plt.ylim(1e-3,1e4)
 
             plt.tight_layout()

### 2022-01-08 paper/paper.tex
finish intro

@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we focus on independent set \textit{property} computation.
+In this paper, we focus on computing various independent set \textit{properties}.
 % We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets.
@@
 We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra.
-This is different from standard tensor network methods, where tensor elements are restricted to standard number types such as floating point numbers and integers.
+It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.
 %The computation of independence polynomials belongs to the complexity class \#P-hard 
@@
 %while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving MIS size,
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving the MIS size,
 which scales exponentially with the tree width, ${\rm tw}(G)$, of the graph.
 For sparse graphs, this quantity is usually much smaller than the number of vertices~\cite{Fomin2006}.
-This indicates it is a method that works better for sparse graphs or graphs,
+This indicates it is a method that works better for sparse graphs,
 unlike another standard approach for solving the MIS size, the branching algorithm ~\cite{Robson1986,Tarjan1977,Xiao2017}, which usually works better for dense graphs.
@@
 %But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs); the high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021}.
-Algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices, which produces a near-optimal space complexity of $2^{\sim{\rm tw}(G)}$ for contracting the tensor network.
+We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performacne.
+The high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
+where efficient heuristic algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices.
 For cases where the tensors are too large to fit into a GPU, slicing techniques can be used to further reduce the space consumption.

### 2022-01-08 paper/paper.tex
update

@@
 %But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performacne.
+We benchmark our algorithms in \Sec{sec:benchmark} by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performacne.
 The high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
@@
 Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
-it can be viewed as a generalization of matrix multiplication to multi-dimensional tensor contraction.
-Einstein's notation is often used to represent a tensor network, e.g.\ the matrix multiplication between two matrices $A$ and $B$ can be represented in Einstein's notation as $C_{ik} = A_{ij}B_{jk}$,
+it can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
+Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
 where we use a label in the subscript to represent a degree of freedom.
 One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard notation of Einstein's summation or tensor networks in physics, each index appears precisely twice.
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice.
 Hence a tensor network can be represented as a simple graph,
-where a tensor is a vertex and two tensors sharing the same label are connected.
+where a tensor is mapped to a vertex and a label shared by two tensors is mapped to an edge.
 In this work, we do not impose such a restriction, so an index can appear an arbitrary number of times. 
 %In the main text, we do not have this restriction. An index can appear arbitrary times.
-The graphical representation of these generalized tensor networks is hypergraphs, in which an edge (label) can be shared by an arbitrary number of vertices (tensors).
-These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, which is a high dimensional equivalence of the identity matrix.
+The graphical representation of a generalized tensor network is a hypergraph, in which an edge (a label in subscript) can be shared by an arbitrary number of vertices (tensors).
+These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
 However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
@@
 \end{align*}
-The requirement of being commutative is for the tensor contraction result to be independent of the contraction order.
-In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings while keeping the tensor network generic~\cite{Stepanov2014}.
+We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we wish this contraction order does not change the contraction results.
+In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
 Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
@@
 \end{equation}
-where $a_k$ is the number of independent sets of size $k$ in $G$. The total number of independent sets is thus equal to $I(G, 1)$.
-To compute the independence polynomial of a graph $G = (V, E)$, we reinterpret this problem as a tensor network contraction problem.
+where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
+To compute this polynomial, we map this expression to a tensor network contraction.
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
@@
 %where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
-To evaluate \Eq{eq:idp}, directly summing up the products is computationally inefficient.
-The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor elements.
-A good contraction order can reduce the time complexity significantly, at the cost of having a space overhead of $O(2^{\text{tw}(G)})$~\cite{Markov2008}.
+To evaluate \Eq{eq:idp}, directly summing up the $2^{|V|}$ product terms is computationally inefficient.
+The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
+A fully optimized contraction order can reduce the time to $O(2^{\text{tw}(G)})$~\cite{Markov2008}, while requiring a space at the same order of magnitude to store intermediate contraction results.
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
@@
 
-\section{Benchmarks and case studies}
+\section{Benchmarks and case studies}\label{sec:benchmark}
 \subsection{Performance benchmarks}
 We run a single thread benchmark on CPU Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
-and its CUDA version on a GPU Tesla V100.
+and its CUDA version on a GPU Tesla V100-SXM2 16G.
 The results are summarized in Figure~\ref{fig:benchmark}.
@@
 
-Figure (a) shows the time and space complexity (without slicing) of tensor network contraction for variety of graph sizes, where the space complexity is the same as the tree width of the problem graph.
-It is obtained with tensor network contraction order optimization algorithm in Ref.~\cite{Kalachev2021}.
-In practice, slicing technique is used to fit the computation into a 32GB memory, the target tree width of slicing is $27$.
+Figure (a) shows the time and space complexity of tensor network contraction for variety of graph sizes, where the space complexity is the same as the tree width of the problem graph.
+The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
+In practice, slicing technique is used for graphs with tree width greater than 27 to fit the computation into a 16GB memory.
 One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the tree width.
@@
 Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
-\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions, hence 
-are much faster comparing to non-BLAS methods in the same category.
-GPU computes much faster than CPU in all cases when the problem scale is large enough so that the actual computing time is comparable or larger than the launching time of CUDA kernels.
+\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions to evaluate tensor contractions, hence
+are much faster comparing to non-BLAS element types in the same category.
+GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
 Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e. \texttt{PN} and \texttt{SN}.
 In figure (c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-however, it maybe suffer from the round off errors. The finite field (GF$(p)$) approach is the only method that does not incur round-off errors and can run on a GPU.
+however, it maybe suffer from the round off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can run on a GPU.
 In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order in enumerating the MISs.
-Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a 32GB memory device.
+Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
 
@@
 \subsubsection{Number of independent sets and hard-square entropy constant}
-In this examples, the types of graphs we used are shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
+We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
 The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rceil$ square grids are occupied with vertices;

### 2022-01-08 paper/paper.tex
further revision to abstract and intro

@@
 We introduce a method of using generic programming tensor network to compute various properties of independent sets,
-which include the size of the maximum independent sets, the number and enumeration of independent sets of a given size.
+which include, for example, the size of the maximum independent sets and the number and enumeration of independent sets of a given size.
 % which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
@@
 %One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices. 
-The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the tree width of the problem graph.
+The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
 Our framework can be easily extended to compute properties of other problems such as the cut size, coloring, and maximal cliques, among others.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the overlap gap property on three regular graphs.
+To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
 \end{abstract}
@@
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
-One of the independent set properties that many computational complexity theorists are most interested in is to find a maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$,
-not only because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
-but also because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
-Some other properties, for example, the number and enumeration of independent sets or maximal independent sets of a given size are euqally important in many practical applications, however, are not studied enough.
-Some of them are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+One of the paradigmatic independent set \textit{properties} % that many computational complexity theorists are most interested in 
+is the maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$. 
+There is widespread interest in this MIS problem not only because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011},
+but also because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+Some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
+These other properties can be found in physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
 in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
-they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
 Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
+However, there is a lack of general and versatile tool to compute the different properties of independent sets.
 %\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
@@
 %In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-In this paper, we focus on computing various independent set \textit{properties}.
 % We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
@@
 %they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-We map the computation of these independent set properties into generic tensor network contraction with specially designed tensor element algebra.
+%In this paper, we focus on computing various independent set \textit{properties}. 
+In this paper, we introduce a generic programming tensor-network framework to compute a number of different independent set properties.
+We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
 It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.
@@
 %while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
-The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} that dedicated to solving the MIS size,
-which scales exponentially with the tree width, ${\rm tw}(G)$, of the graph.
-For sparse graphs, this quantity is usually much smaller than the number of vertices~\cite{Fomin2006}.
-This indicates it is a method that works better for sparse graphs,
-unlike another standard approach for solving the MIS size, the branching algorithm ~\cite{Robson1986,Tarjan1977,Xiao2017}, which usually works better for dense graphs.
+Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013}, which have a complexity scaling exponentially with the treewidth, ${\rm tw}(G)$, of the graph;
+for sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
+Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
+% Thus, we expect our algorithms to works well for sparse graphs,
+% which is complementary to another standard approach for solving the MIS size, the branching algorithm ~\cite{Robson1986, Tarjan1977, Xiao2017}, which usually works better for dense graphs.
 % We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
@@
 %But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
-We benchmark our algorithms in \Sec{sec:benchmark} by computing various independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performacne.
-The high performance of our algorithms benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
+We benchmark our algorithms in \Sec{sec:benchmark} by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
+The high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
 where efficient heuristic algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices.
 For cases where the tensors are too large to fit into a GPU, slicing techniques can be used to further reduce the space consumption.
-Lastly, we provide a few examples and demonstrate the versatility of our tool by computing the entropy constant for some hardcore lattice gases on 2D square lattices and analyzing the overlap gap property on three regular graphs.
+Lastly, we provide a few examples and demonstrate the versatility of our tool by computing the entropy constant for some hardcore lattice gases on 2D square lattices and analyzing the presence of overlap gap property on three regular graphs.
 Our method can also be used to find ``maximal'' independent set properties; 
@@
 The graphs that we use in benchmarks are random three regular graphs,
- a typical type of sparse graphs that has a small tree width that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+ a typical type of sparse graphs that has a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
 
@@
 
-Figure (a) shows the time and space complexity of tensor network contraction for variety of graph sizes, where the space complexity is the same as the tree width of the problem graph.
+Figure (a) shows the time and space complexity of tensor network contraction for variety of graph sizes, where the space complexity is the same as the treewidth of the problem graph.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
-In practice, slicing technique is used for graphs with tree width greater than 27 to fit the computation into a 16GB memory.
-One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the tree width.
+In practice, slicing technique is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
+One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
 %The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
@@
 %a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-%Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small tree width efficiently~\cite{Courcelle1990,Barr2020}.
+%Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small treewidth efficiently~\cite{Courcelle1990,Barr2020}.
 %It can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
@@
 %Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
-the tree width of this tensor network is significantly larger, hence only small graphs can be benchmarked.
+the treewidth of this tensor network is significantly larger, hence only small graphs can be benchmarked.
 The time for the tensor network approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,

### 2022-01-08 paper/paper.tex
update table

--- 2022-01-08 paper/paper.tex
@@
 \usetikzlibrary{snakes}
+\usetikzlibrary{shapes.geometric}
 \usepackage{wrapfig}
@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
-
-\begin{table}[t!]\centering
-\begin{minipage}{\columnwidth}
-\ra{1.3}
-        \begin{tabularx}{\textwidth}{sb}\toprule
-            \hline
-            \textbf{element type}     & \textbf{property/properties to compute} \\
+The following diagram summarizes those properties that can be computed by various tensor element types.
+
+% \begin{table}[t!]\centering
+% \begin{minipage}{\columnwidth}
+% \ra{1.3}
+%         \begin{tabularx}{\textwidth}{sb}\toprule
+%             \hline
+%             \textbf{element type}     & \textbf{property/properties to compute} \\
+%             {$\mathbbm{R}$}     & {the number of independent sets} \\
+%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
+%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
+%             {T} (\Eq{eq:tropical})    & {MIS size} \\
+%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
+%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
+%             {P1+S1}     & {MIS size and one MIS} \\
+%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+%             \bottomrule
+%         \end{tabularx}
+%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
+% \end{minipage}
+% \end{table}
+
+\centerline{\begin{tikzpicture}[]
+    \scriptsize
+    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
+    % set and set sampler
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+    \node[below of=1] at (SN) {Set};
+    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+    \def\dx{-3};
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node at (\dx, -1.2) {$\ldots$};
+    \node[above of=2] at (T) (textT) {Tropical};
+    \draw[black,-latex] (textT) -- (T);
+\end{tikzpicture}}
+\vspace{2em}
+\centering{
+\begin{minipage}{0.8\columnwidth}\scriptsize
+\begin{tabularx}{\textwidth}{bb}
+    \textbf{element type}     & \textbf{property to compute} \\
     {$\mathbbm{R}$}     & {the number of independent sets} \\
-            {$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
     {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
-            {T} (\Eq{eq:tropical})    & {MIS size} \\
-            {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-            {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-            {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
-            {P1+S1}     & {MIS size and one MIS} \\
-            {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-            \bottomrule
+    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
+    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
+    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
+    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
+    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
+    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
+    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
 \end{tabularx}
-    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
 \end{minipage}
-\end{table}
+}
 

### 2022-01-08 paper/paper.tex
update table

@@
     {$\mathbbm{R}$}     & {the number of independent sets} \\
-    {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
     {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\

### 2022-01-08 paper/paper.tex

--- 2022-01-08 paper/paper.tex
@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
-
-\begin{table}[t!]\centering
-\begin{minipage}{\columnwidth}
-\ra{1.3}
-        \begin{tabularx}{\textwidth}{sb}\toprule
-            \hline
-            \textbf{element type}     & \textbf{property/properties to compute} \\
+The following diagram summarizes those properties that can be computed by various tensor element types.
+
+% \begin{table}[t!]\centering
+% \begin{minipage}{\columnwidth}
+% \ra{1.3}
+%         \begin{tabularx}{\textwidth}{sb}\toprule
+%             \hline
+%             \textbf{element type}     & \textbf{property/properties to compute} \\
+%             {$\mathbbm{R}$}     & {the number of independent sets} \\
+%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
+%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
+%             {T} (\Eq{eq:tropical})    & {MIS size} \\
+%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
+%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
+%             {P1+S1}     & {MIS size and one MIS} \\
+%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+%             \bottomrule
+%         \end{tabularx}
+%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
+% \end{minipage}
+% \end{table}
+
+\centerline{\begin{tikzpicture}[]
+    \scriptsize
+    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
+    % set and set sampler
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+    \node[below of=1] at (SN) {Set};
+    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+    \def\dx{-3};
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node at (\dx, -1.2) {$\ldots$};
+    \node[above of=2] at (T) (textT) {Tropical};
+    \draw[black,-latex] (textT) -- (T);
+\end{tikzpicture}}
+\vspace{2em}
+\centering{
+\begin{minipage}{0.8\columnwidth}\scriptsize
+\begin{tabularx}{\textwidth}{bb}
+    \textbf{element type}     & \textbf{property to compute} \\
     {$\mathbbm{R}$}     & {the number of independent sets} \\
-            {$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
-            {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
-            {T} (\Eq{eq:tropical})    & {MIS size} \\
-            {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-            {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-            {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
-            {P1+S1}     & {MIS size and one MIS} \\
-            {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-            \bottomrule
+    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
+    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
+    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
+    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
+    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
+    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
+    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
 \end{tabularx}
-    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
 \end{minipage}
-\end{table}
+}
 

### 2022-01-08 paper/paper.tex
update revert table

@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-The following diagram summarizes those properties that can be computed by various tensor element types.
-
-% \begin{table}[t!]\centering
-% \begin{minipage}{\columnwidth}
-% \ra{1.3}
-%         \begin{tabularx}{\textwidth}{sb}\toprule
-%             \hline
-%             \textbf{element type}     & \textbf{property/properties to compute} \\
-%             {$\mathbbm{R}$}     & {the number of independent sets} \\
-%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
-%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
-%             {T} (\Eq{eq:tropical})    & {MIS size} \\
-%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
-%             {P1+S1}     & {MIS size and one MIS} \\
-%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-%             \bottomrule
-%         \end{tabularx}
-%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
-% \end{minipage}
-% \end{table}
-
-\centerline{\begin{tikzpicture}[]
-    \scriptsize
-    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-    % set and set sampler
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-    \node[below of=1] at (SN) {Set};
-    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
-    \def\dx{-3};
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
-    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
-    \node at (\dx, -1.2) {$\ldots$};
-    \node[above of=2] at (T) (textT) {Tropical};
-    \draw[black,-latex] (textT) -- (T);
-\end{tikzpicture}}
-\vspace{2em}
-\centering{
-\begin{minipage}{0.8\columnwidth}\scriptsize
-\begin{tabularx}{\textwidth}{bb}
+The Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+
+\begin{table}[t!]\centering
+\begin{minipage}{\columnwidth}
+\ra{1.3}
+        \begin{tabularx}{\textwidth}{sb}\toprule
+            \hline
    \textbf{element type}     & \textbf{property to compute} \\
@@
    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+            \bottomrule
         \end{tabularx}
+    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
 \end{minipage}
-}
+\end{table}
+
+% \vspace{2em}
+% \centering{
+% \begin{minipage}{0.8\columnwidth}\scriptsize
+% \begin{tabularx}{\textwidth}{bb}
+%     \textbf{element type}     & \textbf{property to compute} \\
+%     {$\mathbbm{R}$}     & {the number of independent sets} \\
+%     {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
+%     {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
+%     {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
+%     {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%     {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
+%     {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
+%     {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
+%     {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+% \end{tabularx}
+% \end{minipage}
+%}
 
@@
 For each property, we design a algebra being a commutative semiring, and map the property computation to the contraction of a tensor network with such element type.
+The data types introduced in the main text can be diagramatically represented as the following, where we use overlap to represent two algebras can be combined to create a new algebra.
+\centerline{\begin{tikzpicture}[]
+    \scriptsize
+    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
+    % set and set sampler
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+    \node[below of=1] at (SN) {Set};
+    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+    \def\dx{-3};
+    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
+    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node at (\dx, -1.2) {$\ldots$};
+    \node[above of=2] at (T) (textT) {Tropical};
+    \draw[black,-latex] (textT) -- (T);
+\end{tikzpicture}}
 %We derived the backward rule for tropical tensor network to bound the search of solution space.
 %Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
-We call this method generic programming tensor network, and its power is not limited to the independent set problem.
+Except for real numbers, we have polynomials and truncated polynomials algebras. We combine them with set algebra and bit string algebra for set enumeration and sampling.
+We call a tensor network with generic tensor element type a generic tensor network, and its power is not limited to solving the independent set properties.
 In \App{app:otherproblems}, we show how to map the maximal independent set problem, matching problem, $k$-colouring problem, max cut problem and set packing problem to tensor networks.

### 2022-01-08 paper/paper.tex
revision up to section 6.1

--- 2022-01-08 paper/paper.tex
@@
 \vspace{2em}
-\centering{
+{\centering{
 \begin{minipage}{0.8\columnwidth}\scriptsize
@@
 \end{minipage}
-}
+}}
 
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
-In the previous section, we focused on computing the independence polynomial for a graph $G$ of given MIS size $\alpha(G)$, but we did not show how to compute this number.
+In the previous section, we focused on computing the independence polynomial for a graph $G$ of a given MIS size $\alpha(G)$, but we did not show how to compute this number.
 The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
@@
 \end{equation}
-where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
+where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
 From this, we can define a new algebra as
@@
 and define the above operations and constants correspondingly.
-When we are only interested in knowing the MIS size, we can drop the counting field.
-The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}.:
+If one is only interested in finding the MIS size, one can drop the counting field.
+The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}:
 \begin{equation}\eqname{T}
@@
 \begin{equation}
-    W^{\rm tropical} = \left(\begin{matrix}
+    W^{\rm T} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm tropical} = \left(\begin{matrix}
+        B^{\rm T} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 Instead of counting just the MISs, one may be interested in counting the independent sets of large sizes close to the MIS size.
-For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial}:
+For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial} as:
 \begin{equation}
@@
 for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
-To enumerate all independent sets, we designed an algebra defined on sets of bitstrings.
+To enumerate all independent sets, we designed an algebra defined on sets of bitstrings:
 \begin{equation}
@@
     &\{00001\} \odot \{\} = \{\}\\
-    &\{00001\} \odot \{00000\} = \{00001\}
+    &\{00001\} \odot \{00000\} = \{00001\}.
 \end{split}
@@
 \begin{equation}
-    W^{\rm enum}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
+    W^{\rm SN}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm enum} = \left(\begin{matrix}
+        B^{\rm SN} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 
-This set algebra can serve as the coefficients in \Eq{eq:countingtropical} to enumerate all MISs, \Eq{eq:polynomial} to enumerate independent sets of different sizes,
+This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs,
 or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
-As long as the coefficients in a truncated polynomial forms a commutative semiring, the polynomial itself is a commutative semiring.
-For example, to enumerate only the MISs, with the tropical algebra, we define $s_{k}\infty^k$,
-where the coefficient follows the algebra in \Eq{eq:set} and the orders follows the max-plus tropical algebra.
+As long as the coefficients in a truncated polynomial forms a commutative semiring, the polynomial itself is still a commutative semiring.
+For example, to enumerate only the MISs, with the tropical algebra, we can define $s_{k}\infty^k$,
+where the coefficients follow the algebra in \Eq{eq:set} and the orders (exponents) follow the max-plus tropical algebra.
 The combined operations become: 
@@
 \begin{equation}
-    W^{\rm MISenum}(\{\boldsymbol{e}_{i}\infty^1\}) = \left(\begin{matrix}
+    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\infty^1\}) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm MISenum} = \left(\begin{matrix}
+        B^{\rm P1+SN} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
     \caption{Bounded enumeration of maximum independent sets.
-In the graph, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard multiplication.
+In these graphs, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
 (a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.

### 2022-01-08 paper/paper.tex

@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-The following diagram summarizes those properties that can be computed by various tensor element types.
-
-% \begin{table}[t!]\centering
-% \begin{minipage}{\columnwidth}
-% \ra{1.3}
-%         \begin{tabularx}{\textwidth}{sb}\toprule
-%             \hline
-%             \textbf{element type}     & \textbf{property/properties to compute} \\
+%The following diagram summarizes those properties that can be computed by various tensor element types.
+%
+%% \begin{table}[t!]\centering
+%% \begin{minipage}{\columnwidth}
+%% \ra{1.3}
+%%         \begin{tabularx}{\textwidth}{sb}\toprule
+%%             \hline
+%%             \textbf{element type}     & \textbf{property/properties to compute} \\
+%%             {$\mathbbm{R}$}     & {the number of independent sets} \\
+%%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
+%%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
+%%             {T} (\Eq{eq:tropical})    & {MIS size} \\
+%%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
+%%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
+%%             {P1+S1}     & {MIS size and one MIS} \\
+%%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+%%             \bottomrule
+%%         \end{tabularx}
+%%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
+%% \end{minipage}
+%% \end{table}
+%
+%\centerline{\begin{tikzpicture}[]
+%    \scriptsize
+%    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
+%    % set and set sampler
+%    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+%    \node[below of=1] at (SN) {Set};
+%    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+%    \def\dx{-3};
+%    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+%    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
+%    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+%    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+%    \node at (\dx, -1.2) {$\ldots$};
+%    \node[above of=2] at (T) (textT) {Tropical};
+%    \draw[black,-latex] (textT) -- (T);
+%\end{tikzpicture}}
+%\vspace{2em}
+%{\centering{
+%\begin{minipage}{0.8\columnwidth}\scriptsize
+%\begin{tabularx}{\textwidth}{bb}
+%    \textbf{element type}     & \textbf{property to compute} \\
 %    {$\mathbbm{R}$}     & {the number of independent sets} \\
-%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
-%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
-%             {T} (\Eq{eq:tropical})    & {MIS size} \\
-%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
-%             {P1+S1}     & {MIS size and one MIS} \\
-%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-%             \bottomrule
-%         \end{tabularx}
-%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
-% \end{minipage}
-% \end{table}
-
-\centerline{\begin{tikzpicture}[]
-    \scriptsize
-    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-    % set and set sampler
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-    \node[below of=1] at (SN) {Set};
-    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
-    \def\dx{-3};
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
-    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
-    \node at (\dx, -1.2) {$\ldots$};
-    \node[above of=2] at (T) (textT) {Tropical};
-    \draw[black,-latex] (textT) -- (T);
-\end{tikzpicture}}
-\vspace{2em}
-{\centering{
-\begin{minipage}{0.8\columnwidth}\scriptsize
-\begin{tabularx}{\textwidth}{bb}
+%    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
+%    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
+%    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
+%    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
+%    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
+%    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
+%    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+%\end{tabularx}
+%\end{minipage}
+%}}
+The Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+
+\begin{table}[t!]\centering
+\begin{minipage}{\columnwidth}
+\ra{1.3}
+        \begin{tabularx}{\textwidth}{sb}\toprule
+            \hline
    \textbf{element type}     & \textbf{property to compute} \\
@@
    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+            \bottomrule
         \end{tabularx}
+    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
 \end{minipage}
-}}
+\end{table}
+
+% \vspace{2em}
+% \centering{
+% \begin{minipage}{0.8\columnwidth}\scriptsize
+% \begin{tabularx}{\textwidth}{bb}
+%     \textbf{element type}     & \textbf{property to compute} \\
+%     {$\mathbbm{R}$}     & {the number of independent sets} \\
+%     {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
+%     {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
+%     {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
+%     {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
+%     {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
+%     {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
+%     {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
+%     {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+% \end{tabularx}
+% \end{minipage}
+%}
 

### 2022-01-08 paper/paper.tex
revision of section 6.2

@@
 In these graphs, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
+$\overline A$ means the boolean mask of $A$.
 (a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
@@
 When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
-To speed up the computation and reduce space overhead, we bound the searching space using the MIS size $\alpha(G)$.
+To speed up the computation and reduce space overhead, we bound the searching space using the information from the computation of the MIS size $\alpha(G)$.
 As shown in \Fig{fig:bounding}, (a) we first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
 (b) Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
-(c) Finally, we perform masked tensor network contraction using the element type with the algebra in \Eq{eq:countingtropicalset} to obtaining all configurations.
+(c) Finally, we perform masked tensor network contraction (i.e.\ discarding the unnecessary intermediate configurations) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
 Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
@@
 The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
-Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$ directly,
-however, doing this might make us lost the advantage of using BLAS libraries~\cite{TropicalGEMM}.
+Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$,
+but if doing this directly, one loses the advantage of using BLAS libraries~\cite{TropicalGEMM} for high performance.
 Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 

### 2022-01-08 paper/paper.tex
revision of section 7.1

@@
     \caption{Benchmark results for computing different properties of independent sets of a random three regular graph with different tensor element types.
-    The time in these plots only includes tensor network contraction, without taking the contraction order finding and just in time compiling time into account.
-    Legends are properties, algebra and devices that we used in the computation, one can find the corresponding computed property in \Tbl{tbl:generictypes}.
+    The time in these plots only includes tensor network contraction, without taking the contraction order finding and just-in-time compiling time into account.
+    Legends are properties, algebra and devices that we used in the computation; one can find the corresponding computed property in \Tbl{tbl:generictypes}.
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computing time for calculating the MIS size and for counting of the number of independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
+    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
     (c) The computing time for calculating the independence polynomials with different approaches.
@@
 
-Figure (a) shows the time and space complexity of tensor network contraction for variety of graph sizes, where the space complexity is the same as the treewidth of the problem graph.
+Figure (a) shows the time and space complexity of tensor network contraction for different graph sizes, where the space complexity is the same as the treewidth of the problem graph.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
 In practice, slicing technique is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
+One can see that all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
 %The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
@@
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e. \texttt{PN} and \texttt{SN}.
+Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN} and \texttt{SN}.
 In figure (c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-however, it maybe suffer from the round off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can run on a GPU.
-In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order in enumerating the MISs.
+but it may suffer from round-off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
 Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.

### 2022-01-08 paper/paper.tex
revision of section 7

@@
 
-\subsubsection{Number of independent sets and hard-square entropy constant}
+\subsubsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
 We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
-The graphs include: the square grid graphs, denoted as SG; the square grid graphs with a filling factor $p$, denoted as SG$(p)$, where $\lfloor pL^{2} \rceil$ square grids are occupied with vertices;
-the King's graphs, denoted as K; the King's graphs with a filling factor $p$, denoted as K$(p)$. 
+The types of graphs include: the square grid graphs (Figure~\ref{fig:lattices}(a)); the square grid graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ square grids are occupied with vertices  (Figure~\ref{fig:lattices}(b));
+the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)).
 The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
-We computed the integer sequences for $L=38$ and $L=39$, which is not known before to our knowledge.
-In the computation, we have used the finite field algebra trick for contracting arbitrarily high precision integer tensor networks.
-We also computed the quantity $F(L,L)^{1/\lfloor pL^2\rceil}$ as a function of grid size $L$ for these lattices,
-where $F(L,L)$ is the number of independent sets of a given grid size.
-The results are shown in \Fig{fig:hardsquare}.
-Our result for $p=1$ matches those in the literature, and the lattices with hole has much larger average value,
-which has a phsical meaning of the hard lattices with holes have much larger mean entropy than those without holes at the high temperature limit.
+We computed the integer sequence for $L=38$ and $L=39$, which, to the best of our knowledge, is not known before.
+In the computation, we used the finite-field algebra for contracting arbitrarily high precision integer tensor networks.
+
+A useful number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs.
+For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
+This quantity arises in statistical mechanics of hard-square lattice gases~\cite{Baxter1980, Pearce1988} and is used to understand phase transitions for these systems.
+This entropy constant is not known to have an exact representation, but it is accurately known in many digits.
+Similarly, we can define entropy constants for other lattice gases.
+In \Fig{fig:hardsquare}, we look at how $F(L,L)^{1/\lfloor pL^2\rceil}$ scales as a function of the grid size $L$ for all types of graphs shown in Figure~\ref{fig:lattices}.
+Our results match the known results for the non-disordered square grid and King's graphs.
+For disordered square grid and King's graphs with a filling factor $p=0.8$, we randomly sample 1000 graph instances.
+To our knowledge, the entropy constants for these disordered graphs have not been studied before.
+Interestingly, the variations due to different random instances are negligible for this entropy quantity.
+% The lattices with holes have a much larger average value, which has an intuitive physical meaning that the hardcore lattices with holes have a much larger mean entropy than those without holes at the high temperature limit.
 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{lattices.pdf}
-    \caption{The types of graphs used in the benchmark and case studies.
-    The lattice dimensions are $L\times L$. (a) Square grid graph denoted as SG. (b) Square grid graph with a filling factor $p=0.8$, denoted as SG(0.8).
-    (c) King's graph denoted as K. (d) King's graph with a filling factor $p=0.8$, denoted as K(0.8).}
+    \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
+    The lattice dimensions are $L\times L$. (a) Square grid graphs. (b) Square grid graphs with a filling factor $p=0.8$.
+    (c) King's graphs. (d) King's graphs with a filling factor $p=0.8$.}
     \label{fig:lattices}
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
-    \caption{Mean entropy for lattices defined in \Fig{fig:lattices}.
-    We sampled $1000$ instances for $p=0.8$ lattices, and the error bar is too small to be visible.
-    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/\lfloor pL^2 \rceil}$.
+    \caption{Mean entropy for lattice gases on graphs defined in \Fig{fig:lattices}.
+    We sampled $1000$ instances for $p=0.8$ lattices and the error bar is too small to be visible.
+    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$ for the corresponding non-disordered square grid and King's graphs.
     }
@@
 
-\subsubsection{Computing the overlap gap property}
-
-With the ability to enumerate configurations, we can analyse the landscape of the target problem, like the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-We enumeate all ISs of size $\geq\alpha(G)-1$ for two random 3 regular graph instances of size 100, and show the Hamming distance statistics in \Fig{fig:hamming}.
-The multiple peak structure indicates disconnected clusters in the configuration space.
+\subsubsection{The overlap gap property}
+With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs and the geometry of the solution space.
+One of the known barriers for finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+Intuitively, if the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection; it implies that large independent sets are clustered together.
+This clustering property has been used to prove the limitations of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
+Here, we use the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property.
+In particular, in \Fig{fig:hamming}, we enumerated all ISs of size $\geq\alpha(G)-1$ for two random three regular graph instances of size 100 and show the pairwise Hamming distance statistics for the enumerated configurations.
+In \Fig{fig:hamming}(a), we observed the multiple peak structure for the pairwise Hamming distance for one of the graphs.
+This indicates the presence of the overlap gap property and disconnected clusters exist in the configuration space for large independent sets.
+We expect our numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
 \begin{figure} 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    \caption{The distribution of Hamming distances between two independent sets of size $\geq\alpha(G)-1$ for two random three regular graph instances of size $100$.}
+    \caption{The distribution of pairwise Hamming distances between every two independent sets of size $\geq\alpha(G)-1$ for two random three regular graph instances of size $100$.}
     \label{fig:hamming}
@@
 The data types introduced in the main text can be diagramatically represented as the following, where we use overlap to represent two algebras can be combined to create a new algebra.
+
 \centerline{\begin{tikzpicture}[]
@@
 \end{tikzpicture}}
+
 %We derived the backward rule for tropical tensor network to bound the search of solution space.

### 2022-01-08 paper/paper.tex
revision of discussion and acknowledgement

@@
 \section{Discussion and conclusion}
-In this paper, we introduce an abstract algebra formalism to compute properties of independent sets.
-The properties include the MIS size, number of independent set of a given size, and enumeration of independent sets of a give size.
-For each property, we design a algebra being a commutative semiring, and map the property computation to the contraction of a tensor network with such element type.
-The data types introduced in the main text can be diagramatically represented as the following, where we use overlap to represent two algebras can be combined to create a new algebra.
+In this paper, we introduce a method to use generic programming tensor networks to compute a number of different independent set properties, including the size of the MISs and the number and enumeration of independent sets of a given size.
+For each property, we design an algebra of a commutative semiring with a particular element type and map the computation of the property to the contraction of a tensor network with such an element type.
+The data types introduced in the main text can be represented in the following diagram, where we use overlap to represent two algebras that can be combined to create a new algebra.
 
@@
 
-%We derived the backward rule for tropical tensor network to bound the search of solution space.
-%Although many of these properties are global, we can encode them to different tensor element types as commutative semirings.
-Except for real numbers, we have polynomials and truncated polynomials algebras. We combine them with set algebra and bit string algebra for set enumeration and sampling.
-We call a tensor network with generic tensor element type a generic tensor network, and its power is not limited to solving the independent set properties.
-In \App{app:otherproblems}, we show how to map the maximal independent set problem, matching problem, $k$-colouring problem, max cut problem and set packing problem to tensor networks.
+Other than the the case with real numbers, we have polynomials and truncated polynomials as algebra types.
+We combine them with the set algebra and the bitstring algebra for set enumeration and sampling.
+This approach to use generic tensor networks can be easily extended to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 %We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
-We show some of the Julia language implementations in Appendix~\ref{sec:technical} and you will find it surprisingly short.
+By adapting to the style of generic programming, we can implement all the algorithms without much effort.
+We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
 A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
-%What we need to do is just defining two operations $\oplus$ and $\odot$ and two special elements $\mymathbb{0}$ and $\mymathbb{1}$.
-%The style that we program is called generic programming,
+We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
+This approach of generic tensor networks should also inspire future works on tensor network computations.
 
@@
 We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
-We would like to acknowledge Sepehr Ebadi, Maddie Cain and Leo Zhou for popping up inspiring questions about independent sets,
-their questions are driving forces of this project.
-Thank Chris Elord for helping us writing the fastest matrix multiplication libary for tropical numbers, TropicalGEMM.jl, he is a man of speed!
-Thank other open source software developers: Roger Luo, Time Besard and Katharine Hyatt for solving issues voluntarily.
+We acknowledge Sepehr Ebadi, Maddie Cain, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
+We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
+We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt, for solving some implementation issues voluntarily.
 \blue{funding information}

### 2022-01-09 paper/paper.tex
minor fix

@@
 We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
-This approach to use generic tensor networks can be easily extended to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
+These algebras are general purposed, they can be used to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},

### 2022-01-22 paper/paper.tex
minor changes to intro and conclusion

@@
 but also because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
-Some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
+On the other hand, some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
 These other properties can be found in physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
 in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
-they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
 Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-However, there is a lack of general and versatile tool to compute the different properties of independent sets.
+However, there is a lack of general and versatile tool to compute these different properties of independent sets.
 %\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
@@
     \caption{Benchmark results for computing different properties of independent sets of a random three regular graph with different tensor element types.
-    The time in these plots only includes tensor network contraction, without taking the contraction order finding and just-in-time compiling time into account.
+    The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
     Legends are properties, algebra and devices that we used in the computation; one can find the corresponding computed property in \Tbl{tbl:generictypes}.
@@
 
-Figure (a) shows the time and space complexity of tensor network contraction for different graph sizes, where the space complexity is the same as the treewidth of the problem graph.
+Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes, where the space complexity is the same as the treewidth of the problem graph.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
 In practice, slicing technique is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see that all the computing times in figure (b), (c) and (d) have a strong correlation with the treewidth.
+One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth.
 %The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
@@
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN} and \texttt{SN}.
-In figure (c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
+Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN} and \texttt{SN}.
+In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
 but it may suffer from round-off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
-In figure (d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
+In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
 Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
@@
 This clustering property has been used to prove the limitations of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
-Here, we use the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property.
+Here, we use the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property for some given graphs.
 In particular, in \Fig{fig:hamming}, we enumerated all ISs of size $\geq\alpha(G)-1$ for two random three regular graph instances of size 100 and show the pairwise Hamming distance statistics for the enumerated configurations.
@@
 
+\begin{figure}[th]
+   \centering
+%    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{}
 \centerline{\begin{tikzpicture}[]
@@
 
-Other than the the case with real numbers, we have polynomials and truncated polynomials as algebra types.
+    \caption{The element types of the tensor networks used in this work. The overlap between two algebra indicates that a new algebra can be created combining those two types of algebra.}
+     \label{fig:venn-diagram}
+\end{figure}
+
+Other than the case with real numbers, we have polynomials and truncated polynomials as algebra types.
 We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
-These algebras are general purposed, they can be used to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
+These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
-This approach of generic tensor networks should also inspire future works on tensor network computations.
+We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
 

### 2022-01-22 paper/paper.tex
grammar fixes for appendix A

@@
 \section{Technical guide}\label{sec:technical}
-This project depends on multiple open source packages in Julia ecosystem.
-We list the Julia packages playing important roles in our code base as follows.
+This project depends on multiple open source packages in the Julia ecosystem.
+We list the Julia packages that play important roles in our code base as follows:
 
@@
 	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
-    \texttt{OMEinsumContractionOrders} implements state of art algorithms for finding the optimal contraction order for the an tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
+    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
 	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
@@
 
-It may surprise you that the Julia implementation of algorithms introduced in the paper is so short that except the bounding algorithm,
-all are contained in this appendix. After installing required packages, one can open a Julia REPL and copy the following code into it.
+The reader may find it surprising that the Julia implementation of the algorithms introduced in this work is so short that except the bounding algorithm,
+all are contained in this appendix. This is due to the power of generic programming. After installing the required packages, one can open a Julia REPL and copy the following codes into it.
 
@@
 
-For performance reason, we still recommend checking our GitHub repository for the full featured version:
+For better performance, we recommend checking our GitHub repository for the full featured version:
 \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.

### 2022-01-22 democode/demo.jl

@@ -9,16 +9,16 @@ graph = (Random.seed!(2); Graphs.random_regular_graph(50, 3))
 code = EinCode(([minmax(e.src,e.dst) for e in Graphs.edges(graph)]..., # labels for edge tensors
                 [(i,) for i in Graphs.vertices(graph)]...), ())        # labels for vertex tensors
 
-# an einsum contraction without contraction order specified is called `EinCode`,
-# an einsum contraction has contraction order (specified as a tree structure) is called `NestedEinsum`.
-# assign each label a dimension-2, it will be used in contraction order optimization
-# `uniquelabels` function extracts tensor labels into a vector.
+# an einsum contraction without a contraction order specified is called `EinCode`,
+# an einsum contraction having a contraction order (specified as a tree structure) is called `NestedEinsum`.
+# assign each label a dimension-2, it will be used in the contraction order optimization
+# `uniquelabels` function extracts the tensor labels into a vector.
 size_dict = Dict([s=>2 for s in uniquelabels(code)])
-# optimize the contraction order using the `TreeSA` method, target space complexity is 2^17
+# optimize the contraction order using the `TreeSA` method; the target space complexity is 2^17
 optimized_code = optimize_code(code, size_dict, TreeSA())
 println("time/space complexity is $(OMEinsum.timespace_complexity(optimized_code, size_dict))")
 
-# a function for computing independence polynomial
+# a function for computing the independence polynomial
 function independence_polynomial(x::T, code) where {T}
 	xs = map(getixsv(code)) do ix
         # if the tensor rank is 1, create a vertex tensor.
@@ -29,9 +29,9 @@ function independence_polynomial(x::T, code) where {T}
 	code(xs...)
 end
 
-########## COMPUTING MAXIMUM INDEPENDENT SET SIZE AND ITS DEGENERACY ###########
+########## COMPUTING THE MAXIMUM INDEPENDENT SET SIZE AND ITS COUNTING/DEGENERACY ###########
 
-# using Tropical numbers to compute the MIS size and MIS degeneracy.
+# using Tropical numbers to compute the MIS size and the MIS degeneracy.
 using TropicalNumbers
 mis_size(code) = independence_polynomial(TropicalF64(1.0), code)[]
 println("the maximum independent set size is $(mis_size(optimized_code).n)")
[…]

### 2022-01-22 paper/paper.tex
edits on Appendix

@@
 
-\section{The reason to not using the standard tensor network notations}\label{app:tensorbad}
+\section{Additional contraction overhead using the standard tensor network notations}\label{app:tensorbad}
 As we have mentioned in the main text,
@@
 
-In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor of rank $8$.
+In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor up to rank $8$.
 If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
-If we relax the restriction that each label appears exactly twice. We have the following hypergraph representation of a generalized tensor network.
+If we relax the restriction that each label must appears exactly twice, we have the following hypergraph representation of a generalized tensor network.
 
@@
 A vertex tensor always has rank $1$ and is not shown here since it does not change the contraction complexity.
-Again, if we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be see by counting the number of colors.
-
-\section{Generalizing to other graph problems}\label{app:otherproblems}
+If we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be seen by counting the number of colors.
+
+\section{Generalization to other graph problems}\label{app:otherproblems}
 %There are some other graph problems that can be encoded to a tensor network.
@@
 Similar to the independence polynomial, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017},
-which can help us understand why the program for solving MIS is trapped in a local minimum.
+which can be helpful for understanding why the program for solving MIS can be trapped in a local minimum.
 Concretely, it is defined as
@@
 Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
+$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where, to our knowledge, the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
 If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
@@
 
-By contracting this tensor network with generic element type,
-we can compute the maximum independent set properties such as maximal independence polynomial, enumerating maximal independent sets.
+By contracting this tensor network with generic element types,
+we can compute the maximal independent set properties such as the maximal independence polynomial and the enumeration of maximal independent sets.
 Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
@@
 %Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
-the treewidth of this tensor network is significantly larger, hence only small graphs can be benchmarked.
+The treewidth of this tensor network is significantly larger, so benchmark with only a smaller graph size is feasible.
 The time for the tensor network approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
 while the tensor network does counting much more efficiently.
-Due to the memory limit, this Bron-Kerbosch algorithm stops working at size $70$ and above.
+Due to the memory limit, this Bron-Kerbosch algorithm is only feasible up to a graph size around $70$.
 
@@
 \end{equation}
-where $k$ is the number of matches, and coefficients $c_k$ are the corresponding counting.
+where $k$ is the size of a matching, and coefficients $c_k$ are the corresponding counting of the number of matchings of the size $k$.
 We map an edge $(u, v) \in E$ to a label $\langle u, v\rangle \in \{0, 1\}$ in a tensor network,
-where $1$ means two vertices of an edge are matched, $0$ means otherwise.
+where $1$ means two vertices of an edge are matched and $0$ otherwise.
 Then we define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
@@
 where label $\langle v, w \rangle$ is equivalent to $\langle w,v\rangle$.
-Here, a vertex tensor specifies the restriction that a vertex can not be in two matched edges, while an edge tensor contributes the variable in the polynomial.
-
-\subsection{k-Colouring}
-Let us use 3-colouring problem defined on vertices as an example.
-For a vertex $v$, we define the degree of freedoms $c_v\in\{1,2,3\}$ and a vertex tensor labelled by it as
+Here, a vertex tensor specifies the restriction that a vertex cannot be matched by more than one edge, while an edge tensor contributes the variable in the polynomial.
+
+\subsection{$k$-Coloring}
+Let us use the 3-coloring problem defined on vertices as an example.
+For a vertex $v$, we define the degrees of freedom $c_v\in\{1,2,3\}$ and a vertex tensor labelled by it as
 \begin{equation}
@@
 \end{equation}
-The number of possible colouring can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+The number of possible colorings can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
 By designing generic types as tensor elements, one can get other properties.
-Similarly, one can define the k-colouring problem on edges too by switching the roles of edges and vertices.
-
-\subsection{Max cut problem}
-Max cut problem is also known as the boolean spin glass problem.
+Similarly, one can also define the $k$-coloring problem on edges by switching the roles of edges and vertices.
+
+\subsection{Max-Cut problem}
+The Max-Cut problem is also known as the boolean spin glass problem.
 For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
-Then the max cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labelled by $s_is_j$
+Then the Max-Cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labelled by $s_is_j$
 \begin{equation}
@@
 where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
-Similar to other problems, we can define a polynomial about edges variables by setting $x_{\langle i, j\rangle} = x$,
+Similar to other problems, we can define a polynomial with edge variables by setting $x_{\langle i, j\rangle} = x$,
 where its $k$th coefficient is two times the number of configurations of cut size $k$.
@@
 Set packing is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-To solve the set packing problem, we just remove the rank 2 restriction of the edge tensor in \Eq{eq:edgetensor}
+To solve the set packing problem, we can just remove the rank-2 restriction of the edge tensor in \Eq{eq:edgetensor}
 \begin{equation}
@@
 
-\section{Integer sequences formed by the number of independent sets}
+\section{Integer sequence formed by the number of independent sets}
 
 We computed the number of independent sets on square lattices and King's graphs
-with our generic tensor network contraction on GPUs.
-The tensor element type is finite field algebra so that we can reach arbitrary precision.
-We also computed independence polynomial rigorously for these lattices in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
+with our generic tensor network contraction algorithm on GPUs.
+The tensor element type is finite-field algebra so that we can reach arbitrary precision.
+We also computed the independence polynomial exactly for these lattices which can be found in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
 
@@
 \caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
-Here we only show two updated entries for $L=38,39$, which to our knowledge, has not been computed before.~\cite{Butera2014}
+Here we only include two updated entries for $L=38,39$, which, to our knowledge, has not been computed before~\cite{Butera2014}.
 }

### 2022-02-24 paper/paper.tex
rm tutorial
clean up

@@
 
-%\usepackage{CJK}
 %\usepackage[colorlinks, citecolor=blue]{hyperref}
@@
 which include, for example, the size of the maximum independent sets and the number and enumeration of independent sets of a given size.
-% which include the size of the maximum independent sets, the number of independent sets and maximal independent sets of a given size, and enumeration of independent sets and maximal independent sets of a given size.
-%Although the computational complexity inevitably scales exponentially with treewidth of the graph,
-%our method using tensor network contraction with generic programming is highly versatile and is able to compute properties that are otherwise not known to be possible for up to several hundred vertices.
 By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
-%One can easily find a good contraction order for the tensor network representation of a graph $G$ with thousands of vertices. 
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
@@
 In graph theory and combinatorial optimization, there are many interesting and hard computational problems concerning various properties of independent sets.
-%An independent set of a graph is a subset of its vertices that no two vertices in this set are adjacent to each other.
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
@@
 These other properties can be found in physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
+in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
 they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
@@
 However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-%\blue{The primary interest of many computational complexity theorists is finding the maximum size of such vertex sets $\alpha(G) \equiv \max_{I}|I|$ and one of the sets of this size.}
-%Finding $\alpha(G)$ exactly is a hard computational problem, and it is NP-hard even to approximate $\alpha(G)$ within $|V|^{1-\epsilon}$ ~\cite{Hastad1996},
-%meaning there is unlikely a polynomial time algorithm to find an independent set with size $\alpha(G)/|V|^{1-\epsilon}$ for an arbitrarily small positive $\epsilon$.
-%Naive exhaustive search for an MIS requires a computational time of $O\left(2^{|V|} \right)$.
-%There is immense interest in finding better algorithms to solve the MIS problem, not only because it has 
-%a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}, 
-%but also because it is a well-known NP-complete problem that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011}.
-
-%more concretely, an maximal independent set of a graph $G$ corresponds to a maximum clique in the complement graph of $G$,
-%and the complement vertex set of an MIS corresponds to a minimum vertex cover of the graph $G$.
-%In this paper, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above; a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-% We introduce a generic programming tensor-network framework to compute the various \textit{properties} pertaining to independent sets. 
-%In this paper, we do not limit our study to just finding an MIS and its size. 
-% We introduce a tensor-network based framework to compute the various \textit{properties} pertaining to independent sets.
-%Beyond just finding an MIS and its size as described above, these properties also include, for example, the number and enumeration of independent sets or maximal independent sets of a given size.
-% There are many other interesting problems pertaining to independent sets, such as the number of independent sets of a given size
-% and enumerating independent sets at a give size or what we call computing \textit{properties}.
-%Some of these problems are of great interest in physics applications such as the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022} \red{replace with experiment paper when ready};
-%they can, for example, be used to understand phase transitions, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-%In this paper, we focus on computing various independent set \textit{properties}. 
 In this paper, we introduce a generic programming tensor-network framework to compute a number of different independent set properties.
@@
 It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.
-%The computation of independence polynomials belongs to the complexity class \#P-hard 
-%and only exponential algorithms~\cite{Ferrin2014} are known to exist for exact computations.
-%Traditional algorithms for finding the MIS size problem include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-%The branching algorithms can reduce the base of the exponential time scaling to, e.g., $1.1996^{|V|} {|V|}^{O(1)}$~\cite{Xiao2017}, 
-%while dynamic programming approaches~\cite{Courcelle1990, Fomin2013} works better for graphs with a small treewidth $\text{tw}(G)$, producing algorithms of complexity $O(2^{\text{tw}(G)} \text{tw}(G) |V|)$.
 Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
@@
 Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-% Thus, we expect our algorithms to works well for sparse graphs,
-% which is complementary to another standard approach for solving the MIS size, the branching algorithm ~\cite{Robson1986, Tarjan1977, Xiao2017}, which usually works better for dense graphs.
-% We introduce a tensor-network based framework to compute the various properties pertaining to independent sets.
-% We map the independent set problem into generic tensor network contraction with specially designed tensor element algebra.
-% Its algorithmic complexity is similar to that of dynamic programming, i.e. scales exponentially as ${\rm tw}(G)$.
-%But the tensor network approach is highly versatile so different problems can be generically solved with minimal implementation efforts without loss of efficiency.
 We benchmark our algorithms in \Sec{sec:benchmark} by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
@@
 Our method can also be used to find ``maximal'' independent set properties; 
-% Here, the term ``maximal'' has a different meaning from ``maximum''  which we discussed above;
 a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum. 
@@
 In this work, we do not impose such a restriction, so an index can appear an arbitrary number of times. 
-%In the main text, we do not have this restriction. An index can appear arbitrary times.
 The graphical representation of a generalized tensor network is a hypergraph, in which an edge (a label in subscript) can be shared by an arbitrary number of vertices (tensors).
@@
 Its hypergraph representation is shown below, where we use different colors to represent different hyperedges.
-%It's equivalent standard notation is $C_{ijk} = A_{ukm} B_{pil} V_{vq} \delta_{mpq} \delta_{juv}\delta_l$.
 
@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-%The following diagram summarizes those properties that can be computed by various tensor element types.
-%
-%% \begin{table}[t!]\centering
-%% \begin{minipage}{\columnwidth}
-%% \ra{1.3}
-%%         \begin{tabularx}{\textwidth}{sb}\toprule
-%%             \hline
-%%             \textbf{element type}     & \textbf{property/properties to compute} \\
-%%             {$\mathbbm{R}$}     & {the number of independent sets} \\
-%%             %{$\mathbbm{C}$}     & {independence polynomial (approximate)} \\
-%%             {$\text{GF}(p)$} (\Eq{eq:finitefield}) & {independence polynomial} \\
-%%             {T} (\Eq{eq:tropical})    & {MIS size} \\
-%%             {P1} (\Eq{eq:countingtropical})     & {MIS size and the number of MISs} \\
-%%             {P2} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-%%             {PN} (\Eq{eq:polynomial})     & {independence polynomial (direct approach)} \\
-%%             {P1+S1}     & {MIS size and one MIS} \\
-%%             {P1+SN} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-%%             \bottomrule
-%%         \end{tabularx}
-%%     \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
-%% \end{minipage}
-%% \end{table}
-%
-%\centerline{\begin{tikzpicture}[]
-%    \scriptsize
-%    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-%    % set and set sampler
-%    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-%    \node[below of=1] at (SN) {Set};
-%    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
-%    \def\dx{-3};
-%    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-%    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
-%    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
-%    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
-%    \node at (\dx, -1.2) {$\ldots$};
-%    \node[above of=2] at (T) (textT) {Tropical};
-%    \draw[black,-latex] (textT) -- (T);
-%\end{tikzpicture}}
-%\vspace{2em}
-%{\centering{
-%\begin{minipage}{0.8\columnwidth}\scriptsize
-%\begin{tabularx}{\textwidth}{bb}
-%    \textbf{element type}     & \textbf{property to compute} \\
-%    {$\mathbbm{R}$}     & {the number of independent sets} \\
-%    {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
-%    {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
-%    {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
-%    {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-%    {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
-%    {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
-%    {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
-%    {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-%\end{tabularx}
-%\end{minipage}
-%}}
 The Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
@@
 
-% \vspace{2em}
-% \centering{
-% \begin{minipage}{0.8\columnwidth}\scriptsize
-% \begin{tabularx}{\textwidth}{bb}
-%     \textbf{element type}     & \textbf{property to compute} \\
-%     {$\mathbbm{R}$}     & {the number of independent sets} \\
-%     {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
-%     {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
-%     {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
-%     {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-%     {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
-%     {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
-%     {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
-%     {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
-% \end{tabularx}
-% \end{minipage}
-%}
-
 \section{Independence polynomial} \label{sec:indpoly}
-% \subsection{Independence polynomial}
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
@@
 
-%In the implementation of the algorithm, we benefit from recent advances in tensor network contraction,
-%where researchers working on quantum circuit simulation evaluate the tensor network by pairwise contracting tensors in a heuristic order~\cite{Gray2021, Pan2021}.
 To evaluate \Eq{eq:idp}, directly summing up the $2^{|V|}$ product terms is computationally inefficient.
@@
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
-%Then we can treat the tensor elements as polynomials and evaluate the polynomial directly.
 Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
@@
 
-% \begin{algorithm}[!ht]
-%     \small
-%     \SetAlgoNoLine
-%     %\LinesNumbered
-%     Let vector $\chi = (\chi_0,\chi_1,\chi_2, \ldots, \chi_{\alpha(G)})$ be a random sequence, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
-
-%     \For{$i=0\ldots\alpha(G)$}{
-%         $y_i$ = ${\rm contract\_tensor\_network}(\chi_i)$
-%     }
-
-%     \Return ${\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha{G}})) $\;
-% \end{algorithm}
-
 \section{Maximum independent sets and its counting}
@@
 From this, we can define a new algebra as
-%\begin{equation}
-%\begin{split}
-%    a(k) \oplus a(j) &= \begin{cases}
-%        \left(a_k + a_j, \max(k,j) \right), & k = j \\
-%        \left(a_j, \max(k,j) \right), & k < j \\
-%        \left(a_k, \max(k,j) \right), & k > j
-%    \end{cases}, \\
-%    a(k) \odot a(j) &= (a_k a_j, k+j) \\
-%    \mymathbb{0} &= (0, -\infty)\\
-%    \mymathbb{1} &= (1, 0). \label{eq:countingtropical}
-%\end{split}
-%\end{equation}
 \begin{equation}
@@
 The combined operations become: 
-%\begin{equation}
-%\begin{split}
-%    s(k) \oplus s(j) &= \begin{cases}
-%        \left(s_k \cup s_j, \max(k,j) \right), & k = j \\
-%        \left(s_j, \max(k,j) \right), & k < j \\
-%        \left(s_k, \max(k,j) \right), & k > j
-%    \end{cases}, \\
-%    s(k) \odot s(j) &= (\{\sigma \lor^\circ \tau \, | \, \sigma \in s_k, \tau \in s_j\}, k+j) \\
-%    \mymathbb{0} &= (\{ \}, -\infty)\\
-%    \mymathbb{1} &= (\{0^{\otimes |V|}\}, 0). \label{eq:countingtropicalset}
-%\end{split}
-%\end{equation}
 \begin{equation}
@@
 Here is a new algebra defined on the bit strings, replacing the sets of bit strings in \Eq{eq:set},
-%We leave this as an exercise for readers.
-%
-%\iffalse
-%\begin{equation}
-%\begin{split}
-%    \sigma_x\infty^x \oplus \sigma_y\infty^y &= \begin{cases}
-%        {\rm select}(\sigma_x, \sigma_y)\infty^{\max(x,y)}, & x = y\\
-%        \sigma_y\infty^{\max(x,y)}, & x < y\\
-%        \sigma_x\infty^{\max(x,y)}, & x > y
-%    \end{cases},\\
-%    \sigma_x\infty^x \odot \sigma_y\infty^y &= (\sigma_x \lor^\circ \sigma_y)\infty^{x+y},\\
-%    \mymathbb{0} &= 1^{\otimes n}\infty^{-\infty},\\
-%    \mymathbb{1} &= 0^{\otimes n}\infty^{0},
-%\end{split}
-%\end{equation}
-%\fi
+
 \begin{equation}
@@
 where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking the one with a smaller integer value.
-%In practice, we can just pick randomly from them, in which case the program will output one of the MIS configurations randomly.
-
-% Although the above discussion is in the context of the MIS problem, we can also combine the above algebras with the maximal independence network in \Eq{eq:maximal} to enumerate or sample maximal independent sets,
-% as well as other problems in \App{app:otherproblems} for configuration enumeration and sampling.
 
@@
 One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth.
-%The computations shown in \Fig{fig:benchmark} include independent set counting, finding maximum independent set size (panel b),
-%computing independence polynomial (panel c) and find one independent set and enumerating independent sets (panel d).
 Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
@@
 Interestingly, the variations due to different random instances are negligible for this entropy quantity.
-% The lattices with holes have a much larger average value, which has an intuitive physical meaning that the hardcore lattices with holes have a much larger mean entropy than those without holes at the high temperature limit.
 
@@
    \centering
-%    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{}
 \centerline{\begin{tikzpicture}[]
     \scriptsize
-    \node[ellipse,draw,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-    % set and set sampler
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-    \node[below of=1] at (SN) {Set};
-    \node[ellipse,draw,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+    \node[draw,fill=lime!80,fill opacity=1, text opacity=1.0,ellipse,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
     \def\dx{-3};
-    \node[ellipse,draw,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
-    \node[ellipse,draw,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
-    \node[ellipse,draw,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
+    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+    \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
     \node at (\dx, -1.2) {$\ldots$};
@@
     \draw[black,-latex] (textT) -- (T);
+
+    % set and set sampler
+    \node[draw,fill=yellow,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+    \node[below of=1] at (SN) {Set};
+    \node[draw,fill=red!70,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
 \end{tikzpicture}}
 
-    \caption{The element types of the tensor networks used in this work. The overlap between two algebra indicates that a new algebra can be created combining those two types of algebra.}
+    \caption{The the tensor network element types used in this work.
+    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.}
      \label{fig:venn-diagram}
@@
 our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
-%Some properties of the independence polynomial, such as the uni-modality, log-concavity, and roots of the polynomial, are well studied in the literature for special classes of graphs~\cite{Levit2005}.
-%We hope our algorithms to calculate the independence polynomial can also help further research in these directions.
 By adapting to the style of generic programming, we can implement all the algorithms without much effort.
@@
 \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
-It can be installed in a similar style to other packages. Here is a short introduction to the functionalities in this package.
-
-\lstinputlisting[breaklines]{../democode/tutorial.jl}
+It can be installed in a similar style to other packages.
 
@@
 \section{Generalization to other graph problems}\label{app:otherproblems}
-%There are some other graph problems that can be encoded to a tensor network.
-%To understand its representation power, it is a good starting point to connect it with dynamic programming because
-%a tensor network can be viewed as a special type of dynamic programming where its update rule can be characterized by a linear operation.
-%Dynamic programming can solve monadic second order logic (MSO) definable problem on a graph with small treewidth efficiently~\cite{Courcelle1990,Barr2020}.
-%It can solve the maximum independent set problem in $O(2^k)n$, which is similar to the tensor network approach.
-%The graph problem can be expressed in the tensor network language is clearly much less than that can be expressed by dynamic programming.
-%For example, it is hard to determine whether a collection of vertices forms a path in a graph using the tensor network language, while this problem is MSO definable.
-%As a gain, a tensor network has a nicer analytic property, which makes contraction order optimization, generic programming and utilizing BLAS libaries very convenient.
-%\iffalse
-%The cost is, it is less expressive than MSO because the tensor network described by \Eq{eq:edgetensor} can be expressed in MSO as
-%\begin{align}
-%    \begin{split}
-%    \exists_X\forall_{u}&(\\
-%    &\quad\forall_{v} 
-%    \neg {\rm adj}(u, v) \lor
-%    ({\rm adj}(u, v) \land ( \hspace{5em}\text{$\triangleright$ restrictions on edges}\\
-%    &\quad\quad(u \not\in X \land v \not\in X \land B_{00}) \lor\\
-%    &\quad\quad(u \not\in X \land v \in X \land B_{01}) \lor\\
-%    &\quad\quad(u \in X \land v \not\in X \land B_{10}) \lor\\
-%    &\quad\quad(u \in X \land v \in X \land B_{11})\\
-%    &\quad)\\
-%    &))\land\\
-%    &(\hspace{16.5em}\text{$\triangleright$ restrictions on vertices}\\
-%    &\quad(u \not\in X \land W_{0}) \lor\\
-%    &\quad(u \in X \land W_{1})\\
-%    &),
-%    \end{split}
-%\end{align}
-%while not all monadic second order logic can be represented as a tensor network contraction,
-%for example, it is hard to construct a tensor network to decide whether a graph is connected or not.
-%At the cost of losing expressiveness, we can encode the properties of the graph into the tensor elements.
-%\fi
-%In the following, we introduce some other problems that can be expressed by a tensor network.
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
@@
 $I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where, to our knowledge, the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\red{cite experiment}.
+If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
 The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
@@
 including a comparison to the Bron-Kerbosch algorithm from Julia package Graphs~\cite{Graphs}.
-%Since the network for computing maximal independent set properties is different from the one for computing the independence polynomial,
 The treewidth of this tensor network is significantly larger, so benchmark with only a smaller graph size is feasible.

### 2022-02-24 project/configurations.jl

@@ -1,7 +1,4 @@
 using DelimitedFiles, GraphTensorNetworks
-#using GraphTensorNetworks.OMEinsumContractionOrders
-#using GraphTensorNetworks.OMEinsum
-#using GraphTensorNetworks.TropicalNumbers
 
 function mis_configurations(n, seed; order, writefile, sc_target=12)
     folder = joinpath(homedir(), ".julia/dev/TropicalMIS", "project", "data", "configurations_L$(n)")
@@ -64,7 +61,8 @@ for (n, seeds) in [
     #(11, [571, 808, 438, 748, 802, 454, 13, 401, 596, 126, 412, 977, 645, 263, 208, 622, 971, 725, 328, 895])
     #(10, 81:99)
     #(11, 0:99)
-    (12, 51:99)
+    #(12, 51:99)
+    (10, [156, 773, 105, 222, 417, 269, 309, 350, 786, 590, 109, 83, 243, 699, 425, 174, 925])
     ]
     for seed in seeds
         @time mis_configurations(n, seed; order=2, writefile=true, sc_target=14)

### 2022-03-08 paper/paper.tex
update

@@
 
-\section{Generic programming}\label{sec:generic}
+\section{Generic programming tensor contractions}\label{sec:generic}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
@@
 
-\section{Independence polynomial} \label{sec:indpoly}
-The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
-\begin{equation}\label{eq:idpdef}
-I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
-To compute this polynomial, we map this expression to a tensor network contraction.
+\section{Tensor network representation of independent sets} \label{sec:indpoly}
+Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i)$ as
-\begin{equation}
-    W(x_i) = \left(\begin{matrix}
+For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i, w_i)$ as
+\begin{equation}
+    W(x_i, w_i) = \left(\begin{matrix}
         1 \\
-        x_i
+        x_i^{w_i}
     \end{matrix}\right).
 \end{equation}
-We use subscripts to index tensor elements, e.g.\ $W(x_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i)_1=x_i$ is the second element associated with $s_i=1$.
+We use subscripts to index tensor elements, e.g.\ $W(x_i, w_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i, w_i)_1=x_i^{w_i}$ is the second element associated with $s_i=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
+    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i, w_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
 \end{equation}
@@
 The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
-In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
-The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$.
 
@@
         \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-            \node[color=black] at (\x+\dx+0.5,\y) {\scriptsize $W(x_\v)$};
+            \node[color=black] at (\x+\dx+0.5,\y) {\scriptsize $W(x_\v, w_\v)$};
         \draw [cyan,thick] (a) -- (aa);
@@
     The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements:
+    \small{
     \begin{align*}
-        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
-        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e)_{s_e}\right) W(x_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c)_{s_c}\right)\right)\right.\\
-        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a)_{s_a}\right)\right)\right)\right)\\
-        =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e\\
-        =&1+5x+4x^2 \qquad \quad (x_{i} = x).
-    \end{align*}
+        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
+        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
+        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
+        =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}\\
+        =&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
+    \end{align*}}
 \end{example}
 
-Before contracting the tensor network and evaluating the independence polynomial numerically, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from integers and floating point numbers to the additive identity,
+\section{Independence polynomial}
+In the special case of $x_i = x$ and $w_i = 1$, the contraction result directly corresponds to the independence polynomial.
+The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
+\begin{equation}\label{eq:idpdef}
+I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
+Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
+and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
+One can feed the standard computer numbers types into this tensor network and evaluate the independence polynomial by contracting it numerically.
+However, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
+To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
@@
 By contracting the tensor network with the polynomial type, we have the exact representation of the independence polynomial.
-However, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
+In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
@@
 
-\section{Enumeration of independent sets}
+\section{Enumerating and sampling independent sets}
 \subsection{Set algebra for configuration enumeration}
@@
 With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.
+
+\subsection{Extremely large MIS enumeration space}
+In many times, the number of configurations is too large to fit into any type of storage.
+Then instead of using the set algebra, we can use a binary sum-product tree as a compact representation of the results.
+We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
+$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content is a \texttt{LEAF} node,
+$left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
+
+\begin{equation}
+\eqname{EXPR}
+\begin{split}
+    s \oplus t &= (\texttt{SUM}, /, s, t)\\
+    s \odot t &= (\texttt{PROD}, /, s, t)\\
+    \mymathbb{0} &= (\texttt{ZERO}, /, /, /)\\
+    \mymathbb{1} &= (\texttt{LEAF}, 0^{\otimes |V|}, /, /).
+\end{split}\label{eq:expr}
+\end{equation}
+
+This algebra is a commutative semiring because we define the equivalence of two sum-product trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
+Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
+but he can directly sample configurations from this tree.
+This is because once we have this sum-product representation of the configuration space,
+one can compute the number of configurations in each branch rigorously and efficiently.
+One can generate a random number and descent this expression tree by a probability proportional to the size of left and right branches.
+
+\section{Weighted graphs}
+In the previous discussion, we have limited ourselves to unweighted graphs.
+For integer weighted graphs, all results still holds,
+while for general weighted graphs, the independence polynomial is not computable anymore.
+For general weighted graphs, we are more interested to know the total weights of maximum $k$ independent set sizes and their configurations.
+Hence we define the extended tropical numbers as the following
+
+\begin{equation}
+\eqname{Tk}
+\begin{split}
+    s \oplus t &= \texttt{largest}(s \cup t, k)\\
+    s \odot t &= \texttt{largest}(\{a+b| a \in s, b\in t\}, k)\\
+    \mymathbb{0} &= -\infty^{\otimes k}\\
+    \mymathbb{1} &= -\infty^{\otimes k-1} \otimes 0
+\end{split}\label{eq:ext-tropical}
+\end{equation}
+where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
+Similarly, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configuration for each size.
+Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are complete.
 

### 2022-03-09 paper/paper.tex
update

@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there are many interesting and hard computational problems concerning various properties of independent sets.
+In graph theory and combinatorial optimization, there is an important class of problems that can be quantified locally,
+including the independent set problem, the cutting problem, the 3-coloring problem, the 3-satisfiability problem,
+the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
+There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
+wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+\blue{need more diversed applications not limited to IS}
+In combinatorial optimization, the most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. people believe there is unlikely a polynomial time algorithm for solving them.
+In this paper, we study the property computing that can be harder but also more useful for people to understand a problem.
+The properties include finding the maximum/minimum size, counting sets of a give size, enumerating all such sets or direct sampling them when they are not enumeratable.
+For weighted version, it also includes finding sets with the largest/smallest $k$ sizes.
+%are many interesting and hard computational problems concerning various properties of independent sets.
+
+For avoid the discussion being too diversed, we limit the target problem to the independent set problem,
+and discuss other combinatorial optimization problems in \App{app:otherproblems}.
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
@@
 is the maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$.
-There is widespread interest in this MIS problem not only because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011},
-but also because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+
 On the other hand, some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
@@
 However, there is a lack of general and versatile tool to compute these different properties of independent sets.
+
 In this paper, we introduce a generic programming tensor-network framework to compute a number of different independent set properties.
@@
 a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-We show how to compute properties related to maximal independent sets and properties for other combinatorial optimization problems in \App{app:otherproblems}.
 
@@
         \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-            \node[color=black] at (\x+\dx+0.5,\y) {\scriptsize $W(x_\v, w_\v)$};
+            \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v, w_\v)$};
         \draw [cyan,thick] (a) -- (aa);

### 2022-03-09 paper/paper.tex
update

@@
 \blue{need more diversed applications not limited to IS}
-In combinatorial optimization, the most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. people believe there is unlikely a polynomial time algorithm for solving them.
-In this paper, we study the property computing that can be harder but also more useful for people to understand a problem.
-The properties include finding the maximum/minimum size, counting sets of a give size, enumerating all such sets or direct sampling them when they are not enumeratable.
-For weighted version, it also includes finding sets with the largest/smallest $k$ sizes.
+
+The most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. there is unlikely a polynomial time algorithm for solving them.
+In this paper, we focus on the less studied \textit{property} computation of these problems which can be harder but is crutial towards understanding a problem.
+The property computation includes finding the maximum/minimum set size, counting sets of a give size, enumerating all such sets or direct sampling them when they are not enumeratable.
+For the weighted version, it also includes finding largest/smallest $k$ sets and their sizes.
 %are many interesting and hard computational problems concerning various properties of independent sets.
 
-For avoid the discussion being too diversed, we limit the target problem to the independent set problem,
+We provide an abstract algebra view for the computation of all these properties and proposed a unified framework,
+generic tensor-network, to solve them all.
+%We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
+Tensor network is also known as the sum product network or einsum in different fields,
+where its tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
+While generic tensor network is a generalization of which by extending the tensor element type to a generic one being a commutative semiring.
+%Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$, where ${\rm tw}(G)$ is the treewidth of graph $G$.
+Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find the optimal contraction order of a large scale tensor network in reasonable time.
+Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for computing properties.
+%For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
+Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
+
+To avoid the discussion being overly diversed, we limit the target problem to the independent set problem,
 and discuss other combinatorial optimization problems in \App{app:otherproblems}.
-For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
-One of the paradigmatic independent set \textit{properties} % that many computational complexity theorists are most interested in 
-is the maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$.
-
-On the other hand, some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
-These other properties can be found in physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
-they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
+For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
+and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
+%The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
+%Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
+%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
 Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-
-In this paper, we introduce a generic programming tensor-network framework to compute a number of different independent set properties.
-We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.
-Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013}, which have a complexity scaling exponentially with the treewidth, ${\rm tw}(G)$, of the graph;
-for sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
-Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-We benchmark our algorithms in \Sec{sec:benchmark} by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-The high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
-where efficient heuristic algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices.
-For cases where the tensors are too large to fit into a GPU, slicing techniques can be used to further reduce the space consumption.
-Lastly, we provide a few examples and demonstrate the versatility of our tool by computing the entropy constant for some hardcore lattice gases on 2D square lattices and analyzing the presence of overlap gap property on three regular graphs.
-Our method can also be used to find ``maximal'' independent set properties; 
-a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-
-\section{Tensor networks}
+%However, there is a lack of general and versatile tool to compute these different properties of independent sets.
+
+The paper is organized as follows.
+We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
+Then we show how to reduce an independent set problem to a tensor network contraction problem \Sec{sec:tnmap}
+and show how to engineer the element types in \Sec{sec:counting},\Sec{sec:enumeration} and \Sec{sec:weighted} to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs.
+% by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
+Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide a few examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
+We show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices
+and analyzing the presence of overlap gap property on three regular graphs.
+%Our method can also be used to find ``maximal'' independent set properties; 
+%a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+
+\section{Tensor networks}\label{sec:tn}
 Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
@@
 
-\section{Tensor network representation of independent sets} \label{sec:indpoly}
+\section{Tensor network representation of independent sets} \label{sec:tnmap}
 Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
@@
 
-\section{Independence polynomial}
+\section{Independence polynomial}\label{sec:indpoly}
 In the special case of $x_i = x$ and $w_i = 1$, the contraction result directly corresponds to the independence polynomial.
@@
 
-\section{Maximum independent sets and its counting}
+\section{Maximum independent sets and its counting}\label{sec:counting}
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
@@
 
-\section{Enumerating and sampling independent sets}
+\section{Enumerating and sampling independent sets}\label{sec:enumeration}
 \subsection{Set algebra for configuration enumeration}
@@
 
-\section{Weighted graphs}
+\section{Weighted graphs}\label{sec:weighted}
 In the previous discussion, we have limited ourselves to unweighted graphs.
@@
 
-\section{Benchmarks and case studies}\label{sec:benchmark}
-\subsection{Performance benchmarks}
+\section{Performance benchmarks}\label{sec:benchmark}
 We run a single thread benchmark on CPU Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
@@
 
-\subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
-
-\subsubsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
+\section{Example case studies} \label{sec:examples}
+In this section, we give a few examples where the different properties of independence sets are used.
+
+\subsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
 We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
@@
 
-\subsubsection{The overlap gap property}
+\subsection{The overlap gap property}
 With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs and the geometry of the solution space.

### 2022-03-09 paper/paper.tex

@@
 In this paper, we focus on the less studied \textit{property} computation of these problems which can be harder but is crutial towards understanding a problem.
-The property computation includes finding the maximum/minimum set size, counting sets of a give size, enumerating all such sets or direct sampling them when they are not enumeratable.
+Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
+but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.
 For the weighted version, it also includes finding largest/smallest $k$ sets and their sizes.
@@
 
-We provide an abstract algebra view for the computation of all these properties and proposed a unified framework,
-generic tensor-network, to solve them all.
+We propose to view the computation of all these properties from an abstract algebra perspective and use a unified framework,
+generic tensor-network, to solve these seeming unrelated properties all.
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
@@
 where its tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
-While generic tensor network is a generalization of which by extending the tensor element type to a generic one being a commutative semiring.
+We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
 %Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
 Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$, where ${\rm tw}(G)$ is the treewidth of graph $G$.
-Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find the optimal contraction order of a large scale tensor network in reasonable time.
+Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
 Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for computing properties.
@@
 \section{Tensor network representation of independent sets} \label{sec:tnmap}
+This section is about reducing the independent set problem to a tensor network contraction problem,
+for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction and the independence polynomial from the partition function perspective.
 Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
@@
         x_i^{w_i}
-    \end{matrix}\right).
+    \end{matrix}\right).\label{eq:vertextensor}
 \end{equation}
@@
 
+\section{An alternative way to construct the tensor network}\label{sec:energymodel}
+
+Let us characterize the independent set problem on graph $G=(V, E)$ as an energy model
+\begin{equation}
+    \mathcal{E}(G, s) = -\sum_{i\in V(G)} w_i s_i + \infty \sum_{\langle i,j\rangle \in E(G)}s_i s_j
+\end{equation}
+where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term.
+The first term is the energy that corresponds to the inverse of the independent set size and the second term describes the independence contraint.
+In physical systems, this contraint term usually corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hard core lattice model~\cite{Dyre2016, Fernandes2007}.
+Its partition function is defined as
+\begin{equation}
+    \begin{split}
+    Z(G, \beta) = \sum_{s}e^{-\beta \mathcal{E}(G, s)} = \sum_{s\in \mathcal{I}(G)} e^{\beta \sum w_i s_i}\\
+         = \sum_{k=0}^{\alpha(G)}D(k) e^{\beta k}  \qquad \quad (w_i = 1)
+    \end{split}
+\end{equation}
+where $\mathcal{I}(G)$ is the set of independent sets of graph $G$.
+The second line corresponds to the unweighted independent set problem,
+$\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size) and $D(k)$ is the number of states with energy $-k$ (independent sets of size $k$).
+It can be evaluated as a tensor network contraction,
+where the tensor network is constructed by placing a vertex tensor on each vertex $i$
+\begin{equation}
+    W(\beta, w_i) = \left(\begin{matrix}
+        1 \\
+        e^{\beta w_i}
+    \end{matrix}\right),
+\end{equation}
+and a bond tensor on each edge
+\begin{equation}
+       B = \left(\begin{matrix}
+        1  & 1\\
+        1 & 0
+    \end{matrix}\right),
+\end{equation}
+where the $0$ in the bond tensor comes from $e^{-\beta\infty}$ from the second term of the energy model.
+By letting $x = e^{\beta w_i}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
+
 \section{Technical guide}\label{sec:technical}

### 2022-03-09 paper/paper.tex
update

@@
 %Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$, where ${\rm tw}(G)$ is the treewidth of graph $G$.
+Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
@@
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i, w_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
+    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i, w_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
 \end{equation}
@@
 
-To evaluate \Eq{eq:idp}, directly summing up the $2^{|V|}$ product terms is computationally inefficient.
+\begin{example}\label{eg:twonode}
+In the following, we show a minimum example of mapping the independent problem of a 2 vertex graph (left) to a tensor network (right).
+
+\centerline{\begin{tikzpicture}[
+dot/.style = {circle, fill, minimum size=#1,
+            inner sep=0pt, outer sep=0pt},
+dot/.default = 6pt  % size of the circle diameter 
+                ]  
+    \def\dx{0};
+    \def\r{0.5cm}
+    \def\wr{0.25cm}
+    \node[dot=\r, fill=black] at (\dx,0) (a) {\color{white}{a}};
+    \node[dot=\r, fill=black] at (2.5+\dx,0) (b) {\color{white}{b}};
+    \draw [black,thick] (a) -- (b);
+
+    \def\dx{5};
+    \def\r{0.25cm}
+    \foreach \x/\y/\e in {1.25/0/ab}
+        \node[color=black,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize \color{white}{B}};
+    \foreach \x/\y/\v in {0.3/0/a, 2.2/0/b}
+        \node[color=black] at (\x+\dx,\y) (s\v) {$s_\v$};
+    \foreach \x/\y/\v in {-0.5/0/a, 3.0/0.0/b}{
+        \node[dot=\wr, color=black] at (\x+\dx,\y) (w\v) {};
+        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W(x_\v, w_\v)$}};
+    }
+    \draw [cyan,thick] (wa) -- (sa);
+    \draw [cyan,thick] (sa) -- (ab);
+    \draw [red,thick] (wb) -- (sb);
+    \draw [red,thick] (sb) -- (ab);
+\end{tikzpicture}}
+
+In the graphical representation of tensor network on the right panel,
+we use a circle to represent a tensor, a hyperedge in cyan color to represent the degree of freedom $s_a$,
+and a hyperedge in red color to represent a degree of freedom $s_b$.
+Tensors sharing a same degree of freedom are connected by that hyperedge.
+The contraction of this tensor network can be evaluated manually:
+\begin{equation}
+    \begin{split}
+    P(K2,\{x_a^{w_a}, x_b^{w_b}\}) &=
+    \left(\begin{matrix} 1 & x_a^{w_a} \end{matrix}\right)
+    \left(\begin{matrix} 1 & 1\\ 1  & 0 \end{matrix}\right)
+    \left(\begin{matrix} 1 \\ x_b^{w_b} \end{matrix}\right)\\
+    &= 1 + x_a^{w_a} + x_b^{w_b}
+    \end{split}
+\end{equation}
+The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$ and $\{b\}$, with weights being $0$, $w_a$ and $w_b$ respectively.
+\end{example}
+
+It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
 The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
@@
 \begin{example}\label{eg:tensorcontraction}
-Mapping a graph (left) to a tensor network (right) that encodes the independence polynomial.
-In the generalized tensor network's graphical representation, a vertex is mapped to a hyperedge.
-We attach a vertex tensor on each hyperedge and an edge tensor between two hyperedges if vertices of the two hyperedges are connected in the original graph.
+In the following, we mapping a 5 vertex graph (left) to a tensor network (right) and show how the contraction order simplifies the computation.
 
@@
         &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
-        =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}\\
-        =&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
+        =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
+        %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
     \end{align*}}
+
+One can easily check the maximum tensor during computing is rank 2, and the total number of multiplication operations is reduced significantly.
 \end{example}
@@
 \section{Independence polynomial}\label{sec:indpoly}
-In the special case of $x_i = x$ and $w_i = 1$, the contraction result directly corresponds to the independence polynomial.
+In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial.
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as

### 2022-03-10 paper/paper.tex
Updates from Overleaf

--- 2022-03-09 paper/paper.tex
@@
 \newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
+\newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
+\newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
 \newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
@@
 \begin{abstract}
-We introduce a method of using generic programming tensor network to compute various properties of independent sets,
+We introduce a method that uses generic programming tensor network to compute various properties of independent sets,
 which include, for example, the size of the maximum independent sets and the number and enumeration of independent sets of a given size.
@@
 
+\cyan{a comment} and \xcyan{a resolved comment}
+
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be quantified locally,
-including the independent set problem, the cutting problem, the 3-coloring problem, the 3-satisfiability problem,
-the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
-There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
-wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
-\blue{need more diversed applications not limited to IS}
-
-The most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. there is unlikely a polynomial time algorithm for solving them.
-In this paper, we focus on the less studied \textit{property} computation of these problems which can be harder but is crutial towards understanding a problem.
-The property computation includes finding the maximum/minimum set size, counting sets of a give size, enumerating all such sets or direct sampling them when they are not enumeratable.
-For the weighted version, it also includes finding largest/smallest $k$ sets and their sizes.
-%are many interesting and hard computational problems concerning various properties of independent sets.
-
-We provide an abstract algebra view for the computation of all these properties and proposed a unified framework,
-generic tensor-network, to solve them all.
-%We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is also known as the sum product network or einsum in different fields,
-where its tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
-While generic tensor network is a generalization of which by extending the tensor element type to a generic one being a commutative semiring.
-%Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$, where ${\rm tw}(G)$ is the treewidth of graph $G$.
-Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find the optimal contraction order of a large scale tensor network in reasonable time.
-Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for computing properties.
-%For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
-Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-
-To avoid the discussion being overly diversed, we limit the target problem to the independent set problem,
-and discuss other combinatorial optimization problems in \App{app:otherproblems}.
-For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
-and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
-%The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
-%Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
-%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
+In graph theory and combinatorial optimization, there are many interesting and hard computational problems concerning various properties of independent sets.
+For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$. %there is no edge connecting $u$ and $v$ in $G$. 
+One of the paradigmatic independent set \textit{properties} % that many computational complexity theorists are most interested in 
+is the maximum independent set (MIS) and the size of the MIS, $\alpha(G) \equiv \max_{I}|I|$. 
+There is widespread interest in this MIS problem not only because it is a well-known NP-complete problem~\cite{Hastad1996} that can be mapped from many other important combinatorial optimization problems in polynomial time such as the 3-satisfiability problem, the maximum clique problem, and the minimum vertex cover problem~\cite{Moore2011},
+but also because it has a wide range of applications in scheduling, logistics, wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+On the other hand, some other properties, such as the number and enumeration of independent sets or maximal independent sets of a given size, are equally interesting, if not more important, in many practical applications.
+These other properties can be found in physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
+in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
+they can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007}, to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
 Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-%However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-
-The paper is organized as follows.
-We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
-Then we show how to reduce an independent set problem to a tensor network contraction problem \Sec{sec:tnmap}
-and show how to engineer the element types in \Sec{sec:counting},\Sec{sec:enumeration} and \Sec{sec:weighted} to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs.
-% by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide a few examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
-We show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices
-and analyzing the presence of overlap gap property on three regular graphs.
-%Our method can also be used to find ``maximal'' independent set properties; 
-%a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-
-\section{Tensor networks}\label{sec:tn}
+However, there is a lack of general and versatile tool to compute these different properties of independent sets.
+In this paper, we introduce a generic programming tensor-network framework to compute a number of different independent set properties.
+We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
+It is different from the standard tensor network methods in that the tensor elements are not restricted to standard number types such as floating point numbers and integers.
+Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+The complexity of our tensor-network based algorithms is similar to that of dynamic programming algorithms~\cite{Courcelle1990, Fomin2013}, which have a complexity scaling exponentially with the treewidth, ${\rm tw}(G)$, of the graph;
+for sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
+Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
+We benchmark our algorithms in \Sec{sec:benchmark} by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
+The high performance benefits from recent advances in random tensor-network contraction for the purposes of quantum circuit simulations~\cite{Gray2021, Pan2021, Kalachev2021},
+where efficient heuristic algorithms have been developed to optimize the contraction order for tensor networks up to thousands of vertices.
+For cases where the tensors are too large to fit into a GPU, slicing techniques can be used to further reduce the space consumption.
+Lastly, we provide a few examples and demonstrate the versatility of our tool by computing the entropy constant for some hardcore lattice gases on 2D square lattices and analyzing the presence of overlap gap property on three regular graphs.
+Our method can also be used to find ``maximal'' independent set properties; 
+a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum. 
+We show how to compute properties related to maximal independent sets and properties for other combinatorial optimization problems in \App{app:otherproblems}.
+
+\section{Tensor networks}
 Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
@@
 
-\section{Generic programming tensor contractions}\label{sec:generic}
+\section{Generic programming}\label{sec:generic}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
@@
 
-\section{Tensor network representation of independent sets} \label{sec:tnmap}
-Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
+\section{Independence polynomial} \label{sec:indpoly}
+The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
+\begin{equation}\label{eq:idpdef}
+I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
+\end{equation}
+where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
+To compute this polynomial, we map this expression to a tensor network contraction.
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i, w_i)$ as
-\begin{equation}
-    W(x_i, w_i) = \left(\begin{matrix}
+For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i)$ as
+\begin{equation}
+    W(x_i) = \left(\begin{matrix}
         1 \\
-        x_i^{w_i}
+        x_i
     \end{matrix}\right).
 \end{equation}
-We use subscripts to index tensor elements, e.g.\ $W(x_i, w_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i, w_i)_1=x_i^{w_i}$ is the second element associated with $s_i=1$.
+We use subscripts to index tensor elements, e.g.\ $W(x_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i)_1=x_i$ is the second element associated with $s_i=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i, w_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
+    P(G, \{x_1, x_{2}, \ldots,x_{|V|}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
 \end{equation}
@@
 The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
+In the special case of $x_i = x$, the contraction result directly corresponds to the independence polynomial.
+The connection can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
+and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$.
 
@@
         \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-            \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v, w_\v)$};
+            \node[color=black] at (\x+\dx+0.5,\y) {\scriptsize $W(x_\v)$};
         \draw [cyan,thick] (a) -- (aa);
@@
     The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements:
-    \small{
     \begin{align*}
-        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
-        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
-        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
-        =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}\\
-        =&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
-    \end{align*}}
+        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a)_{s_a} W(x_b)_{s_b} W(x_c)_{s_c} W(x_d)_{s_d} W(x_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
+        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e)_{s_e}\right) W(x_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c)_{s_c}\right)\right)\right.\\
+        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a)_{s_a}\right)\right)\right)\right)\\
+        =&1 + x_a + x_b + x_c + x_d + x_e + x_ax_d + x_ax_e + x_cx_e + x_bx_e\\
+        =&1+5x+4x^2 \qquad \quad (x_{i} = x).
+    \end{align*}
 \end{example}
 
-\section{Independence polynomial}\label{sec:indpoly}
-In the special case of $x_i = x$ and $w_i = 1$, the contraction result directly corresponds to the independence polynomial.
-The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
-\begin{equation}\label{eq:idpdef}
-I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
-Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-One can feed the standard computer numbers types into this tensor network and evaluate the independence polynomial by contracting it numerically.
-However, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
-To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
+Before contracting the tensor network and evaluating the independence polynomial numerically, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from integers and floating point numbers to the additive identity,
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
@@
 By contracting the tensor network with the polynomial type, we have the exact representation of the independence polynomial.
-In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
+However, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
@@
 
-\section{Maximum independent sets and its counting}\label{sec:counting}
+\section{Maximum independent sets and its counting}
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
@@
 
-\section{Enumerating and sampling independent sets}\label{sec:enumeration}
+\section{Enumeration of independent sets}
 \subsection{Set algebra for configuration enumeration}
@@
 
-\subsection{Extremely large MIS enumeration space}
-In many times, the number of configurations is too large to fit into any type of storage.
-Then instead of using the set algebra, we can use a binary sum-product tree as a compact representation of the results.
-We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
-$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content is a \texttt{LEAF} node,
-$left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
-
-\begin{equation}
-\eqname{EXPR}
-\begin{split}
-    s \oplus t &= (\texttt{SUM}, /, s, t)\\
-    s \odot t &= (\texttt{PROD}, /, s, t)\\
-    \mymathbb{0} &= (\texttt{ZERO}, /, /, /)\\
-    \mymathbb{1} &= (\texttt{LEAF}, 0^{\otimes |V|}, /, /).
-\end{split}\label{eq:expr}
-\end{equation}
-
-This algebra is a commutative semiring because we define the equivalence of two sum-product trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
-Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
-but he can directly sample configurations from this tree.
-This is because once we have this sum-product representation of the configuration space,
-one can compute the number of configurations in each branch rigorously and efficiently.
-One can generate a random number and descent this expression tree by a probability proportional to the size of left and right branches.
-
-\section{Weighted graphs}\label{sec:weighted}
-In the previous discussion, we have limited ourselves to unweighted graphs.
-For integer weighted graphs, all results still holds,
-while for general weighted graphs, the independence polynomial is not computable anymore.
-For general weighted graphs, we are more interested to know the total weights of maximum $k$ independent set sizes and their configurations.
-Hence we define the extended tropical numbers as the following
-
-\begin{equation}
-\eqname{Tk}
-\begin{split}
-    s \oplus t &= \texttt{largest}(s \cup t, k)\\
-    s \odot t &= \texttt{largest}(\{a+b| a \in s, b\in t\}, k)\\
-    \mymathbb{0} &= -\infty^{\otimes k}\\
-    \mymathbb{1} &= -\infty^{\otimes k-1} \otimes 0
-\end{split}\label{eq:ext-tropical}
-\end{equation}
-where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
-Similarly, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configuration for each size.
-Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are complete.
-
-\section{Performance benchmarks}\label{sec:benchmark}
+\section{Benchmarks and case studies}\label{sec:benchmark}
+\subsection{Performance benchmarks}
 We run a single thread benchmark on CPU Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
@@
 
-\section{Example case studies} \label{sec:examples}
-In this section, we give a few examples where the different properties of independence sets are used.
-
-\subsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
+\subsection{Example case studies} In this section, we give a few examples where the different properties of independence sets are used.
+
+\subsubsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
 We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
@@
 
-\subsection{The overlap gap property}
+\subsubsection{The overlap gap property}
 With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs and the geometry of the solution space.

### 2022-03-10 paper/paper.tex

--- 2022-03-09 paper/paper.tex
@@
 \end{AMS}
+
+\cyan{a comment} and \xcyan{a resolved comment}
 

### 2022-03-11 paper/paper.tex
update

@@
             \hline
-   \textbf{element type}     & \textbf{property to compute} \\
-   {$\mathbbm{R}$}     & {the number of independent sets} \\
-   {Polynomial} (\Eq{eq:polynomial})     & {independence polynomial} \\
-   {Tropical (\Eq{eq:tropical})}    & {MIS size} \\
-   {Polynomial truncated to highest order (\Eq{eq:countingtropical})}     & {MIS size and the number of MISs} \\
-   {Polynomial truncated to 2nd highest order} (\Eq{eq:max2poly})     & {the number of MISs and independent sets of size $\alpha(G)-1$} \\
-   {Set} (\Eq{eq:set})     & {enumeration of independent sets} \\
-   {Bit string} (\Eq{eq:singleconfig})     & {one independent set} \\
-   {Polynomial truncated to highest order combined with Bit string}     & {MIS size and one MIS} \\
-   {Polynomial truncated to highest order combined with Set} (\Eq{eq:countingtropicalset})    & {MIS size and all MISs} \\
+   \textbf{Element type}     & \textbf{Property to compute} \\
+   {$\mathbbm{R}$}     & {Counting of all independent sets} \\
+   {Polynomial} (\Eq{eq:polynomial})     & {Independence polynomial} \\
+   {Tropical (\Eq{eq:tropical})}    & {Maximum independent set size} \\
+   {Extended Tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
+   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their counting} \\
+   {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
+   {Sum Product Tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
+   {Polynomial truncated to highest order combined with Bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
+   {Polynomial truncated to $k$-th order combined with Set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
             \bottomrule
@@
 The contraction of the corresponding tensor network yields an enumeration of all MIS configurations.
+Direct implementing this algebra for configuration MISs might incur significant space overheads for keeping too many intermediate states not contributing to the final maximum independent sets,
+one can avoid this issue by using the bounding technique in \App{sec:bounding}.
 
@@
 
-\subsection{Bounding the MIS enumeration space}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
-    \caption{Bounded enumeration of maximum independent sets.
-In these graphs, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
-$\overline A$ means the boolean mask of $A$.
-(a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
-     (b) is the backward pass for computing boolean gradients as masks.
-     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
-     \label{fig:bounding}
-\end{figure}
-
-When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
-To speed up the computation and reduce space overhead, we bound the searching space using the information from the computation of the MIS size $\alpha(G)$.
-As shown in \Fig{fig:bounding}, (a) we first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
-(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
-(c) Finally, we perform masked tensor network contraction (i.e.\ discarding the unnecessary intermediate configurations) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
-Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
-To derive the back-propagation rule for tropical tensor contraction,
-we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
-Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
-\begin{equation}
-    A_{ij} \odot B_{jk} \leq C_{ik}.
-\end{equation}
-Here $\leq$ on tropical numbers are the same as the real-number algebra.
-The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
-Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$,
-but if doing this directly, one loses the advantage of using BLAS libraries~\cite{TropicalGEMM} for high performance.
-Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 
-\begin{equation}
-    A_{ij} \leq C_{ik} \odot B_{jk}^{\circ -1}
-\end{equation}
-where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers).
-The inequality still holds if we take the minimum over $k$: 
-\begin{equation}
-    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
-\end{equation}
-On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
-Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
-Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
-\begin{equation}\label{eq:adrule}
-\overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
-\end{equation}
-where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
-This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
-With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.
-
-\subsection{Extremely large MIS enumeration space}
+\subsection{Sampling extremely large configuration space}
 In many times, the number of configurations is too large to fit into any type of storage.
@@
 \begin{equation}
-\eqname{EXPR}
+\eqname{SUMPROD}
 \begin{split}
@@
 \end{split}\label{eq:expr}
+\end{equation}
+The vertex tensor and edge tensor become
+\begin{equation}
+    W^{\rm SUMPROD}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
+        \mymathbb{1} \\
+        (\texttt{LEAF},\boldsymbol{e}_i,/,/)
+    \end{matrix}\right),   
+    \qquad
+        B^{\rm SUMPROD} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
 \end{equation}
@@
 where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
-Similarly, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configuration for each size.
+The vertex tensor and edge tensor become
+\begin{equation}
+    W^{\rm Tk}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
+        \mymathbb{1} \\
+        -\infty^{\otimes k-1} \otimes 1
+    \end{matrix}\right),   
+    \qquad
+        B^{\rm Tk} = \left(\begin{matrix}
+        \mymathbb{1}  & \mymathbb{1} \\
+        \mymathbb{1} & \mymathbb{0}
+    \end{matrix}\right).
+\end{equation}
+
+Similar to the Tropical numbers, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configurations of each size.
 Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are complete.
@@
     \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.2cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-0.7cm}Highest order};
-    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=0.7cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.7cm}2nd highest order};
+    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Highest order};
+    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}2nd highest order};
     \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node[draw,fill=brown!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, -0.1) (T2) {};
     \node at (\dx, -1.2) {$\ldots$};
-    \node[above of=2] at (T) (textT) {Tropical};
+    \node[above = 1cm] at (T) (textT) {Tropical};
+    \node[below = 2cm, left=4cm] (textT2) {Extended Tropical};
     \draw[black,-latex] (textT) -- (T);
+    \draw[black,-latex] (textT2) -- (T2);
 
@@
 
+\section{Bounding the MIS enumeration space}\label{sec:bounding}
+\begin{figure}
+    \centering
+    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
+    \caption{Bounded enumeration of maximum independent sets.
+In these graphs, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
+$\overline A$ means the boolean mask of $A$.
+(a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
+     (b) is the backward pass for computing boolean gradients as masks.
+     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
+     \label{fig:bounding}
+\end{figure}
+
+When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
+To speed up the computation and reduce space overhead, we bound the searching space using the information from the computation of the MIS size $\alpha(G)$.
+As shown in \Fig{fig:bounding}, (a) we first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
+(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
+(c) Finally, we perform masked tensor network contraction (i.e.\ discarding the unnecessary intermediate configurations) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
+Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
+To derive the back-propagation rule for tropical tensor contraction,
+we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
+Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
+\begin{equation}
+    A_{ij} \odot B_{jk} \leq C_{ik}.
+\end{equation}
+Here $\leq$ on tropical numbers are the same as the real-number algebra.
+The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
+Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$,
+but if doing this directly, one loses the advantage of using BLAS libraries~\cite{TropicalGEMM} for high performance.
+Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 
+\begin{equation}
+    A_{ij} \leq C_{ik} \odot B_{jk}^{\circ -1}
+\end{equation}
+where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers).
+The inequality still holds if we take the minimum over $k$: 
+\begin{equation}
+    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
+\end{equation}
+On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
+Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
+Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
+\begin{equation}\label{eq:adrule}
+\overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
+\end{equation}
+where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
+This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
+With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.
+
 \section{The discrete Fourier transform approach to computing the independence polynomial}\label{app:fft}

### 2022-03-11 paper/paper.tex
new new networks

@@
 \begin{equation}\label{eq:maximal}
-    T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx_v & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
+    T(x_v, w_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+        s_vx_v^{w_v} & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
         1-s_v& \text{otherwise}.\\
@@
 \begin{equation}
-    T(x_v)=\left(\begin{matrix}
+    T(x_v, w_v)=\left(\begin{matrix}
     \left(\begin{matrix}
@@
     \left(\begin{matrix}
-        x_v &0 \\
+        x_v^{w_v} &0 \\
         0 &0
@@
 Let us use the 3-coloring problem defined on vertices as an example.
-For a vertex $v$, we define the degrees of freedom $c_v\in\{1,2,3\}$ and a vertex tensor labelled by it as
+For a vertex $v$, we define the degrees of freedom $c_v\in\{0,1,2\}$ and a vertex tensor labelled by it as
 \begin{equation}
@@
         b_v
+    \end{matrix}\right),
+\end{equation}
+where $r_v$, $g_v$ and $b_v$ are colors used to label the configurations.
+For an edge $(u, v)$, we define an edge tensor as a matrix labelled by $(c_u, c_v)$ to specify the constraint
+\begin{equation}
+    B(x) = \left(\begin{matrix}
+        0 & x & x\\
+        x & 0 & x\\
+        x & x & 0
     \end{matrix}\right).
 \end{equation}
-For an edge $(u, v)$, we define an edge tensor as a matrix labelled by $(c_u, c_v)$ to specify the constraint
-\begin{equation}
-    B = \left(\begin{matrix}
-        0 & 1 & 1\\
-        1 & 0 & 1\\
-        1 & 1 & 0
-    \end{matrix}\right).
-\end{equation}
-The number of possible colorings can be obtained by contracting this tensor network by setting vertex tensor elements $r_v, g_v$ and $b_v$ to $1$.
+The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
 By designing generic types as tensor elements, one can get other properties.
@@
 where its $k$th coefficient is two times the number of configurations of cut size $k$.
+
+\subsection{Dominating Set}
+Let $G=(V,E)$ be the target graph that we want to solve.
+The tensor network representation map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
+We defined the restriction on a vertex and its neighbouring vertices $N(v)$:
+\begin{equation}
+T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+    0 & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
+    1 & s_v=0,\\
+    x_v^{w_v} & \text{otherwise},
+\end{cases}
+\end{equation}
+where $w_v$ is the weight of vertex $v$.
+This tensor means if both $v$ and its neighbouring vertices are not in $D$, i.e., $s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$,
+this configuration is forbidden because $v$ is not adjacent to any member in the set.
+otherwise, if $v$ is in $D$, it has a contribution $x_v^{w_v}$ to the final result.
+
+\subsection{Satisfiability Problem}
+We can contruct a satisfiability problem to solve the above problem.
+To generate a tensor network, we map a boolean variable $x$ and its negation $\neg x$ to a degree of freedom (label) $s_x \in \{0, 1\}$,
+where 0 stands for variable $x$ having value \texttt{false} while 1 stands for having value \texttt{true}.
+Then we map a clause to a tensor. For example, a clause $\neg x \vee y \vee \neg z$ can be mapped to a tensor labeled by $(s_x, s_y, s_z)$.
+\begin{equation}
+C = \left(\begin{matrix}
+\left(\begin{matrix}
+x & x \\
+x & x
+\end{matrix}\right) \\
+\left(\begin{matrix}
+x & x \\
+1 & x
+\end{matrix}\right)
+\end{matrix}\right).
+\end{equation}
+There is only one entry $(s_x, s_y, s_z) = (1, 0, 1)$ that makes this clause unsatisfied.
+If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
 

### 2022-03-11 paper/paper.tex
update polynomial

@@
 Similarly, one can also define the $k$-coloring problem on edges by switching the roles of edges and vertices.
+Let $x_{\langle i,j\rangle} = x$, we have a graph polynomial,
+where its $k$th coefficient is the number of coloring with $k$ bonds are satisfied.
+If a graph is colorable, the maximum order of this polynomial should be equal to the number of edges in this graph.
 
@@
 where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
-Similar to other problems, we can define a polynomial with edge variables by setting $x_{\langle i, j\rangle} = x$,
+Let $x_{\langle i,j\rangle} = x$, we have a graph polynomial similar to previous ones,
 where its $k$th coefficient is two times the number of configurations of cut size $k$.
@@
 otherwise, if $v$ is in $D$, it has a contribution $x_v^{w_v}$ to the final result.
+The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009},
+which is defined as
+\begin{equation}
+D(G, x) = \sum_{k=0}^{\gamma(G)} d_k x^k,
+\end{equation}
+where $d_k$ is the number of dominating sets of size $k$ in graph $G=(V, E)$.
 
@@
 We can contruct a satisfiability problem to solve the above problem.
-To generate a tensor network, we map a boolean variable $x$ and its negation $\neg x$ to a degree of freedom (label) $s_x \in \{0, 1\}$,
-where 0 stands for variable $x$ having value \texttt{false} while 1 stands for having value \texttt{true}.
-Then we map a clause to a tensor. For example, a clause $\neg x \vee y \vee \neg z$ can be mapped to a tensor labeled by $(s_x, s_y, s_z)$.
+To generate a tensor network, we map a boolean variable $a$ and its negation $\neg a$ to a degree of freedom (label) $s_a \in \{0, 1\}$,
+where 0 stands for variable $a$ having value \texttt{false} while 1 stands for having value \texttt{true}.
+Then we map a clause to a tensor. For example, a clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
 \begin{equation}
@@
 \left(\begin{matrix}
-x & x \\
-x & x
+x & x_{b} \\
+x_a & x_{ab}
 \end{matrix}\right) \\
 \left(\begin{matrix}
-x & x \\
-1 & x
+x_{c} & x_{bc} \\
+1 & x_{abc}
 \end{matrix}\right)
@@
 If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
+Let $x_{ab\ldots} = x$, then we can get a polynomial that its $k$-th coefficients gives us the number of assignments with $k$ clauses satisfied.
 

### 2022-03-11 paper/paper.tex
updat

@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor network to compute various properties of independent sets,
-which include, for example, the size of the maximum independent sets and the number and enumeration of independent sets of a given size.
+We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be quantified locally.
+Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
 By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
-Our framework can be easily extended to compute properties of other problems such as the cut size, coloring, and maximal cliques, among others.
+Other hard graph problems solvable in our framework includes the cutting problem, the K-coloring problem, the maximal clique problem, the dominating set problem, and satisfiability problem, among others.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
+We show how our method helps people understand these hard problems better.
 \end{abstract}
@@
 In graph theory and combinatorial optimization, there is an important class of problems that can be quantified locally,
-including the independent set problem, the cutting problem, the 3-coloring problem, the 3-satisfiability problem,
+including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
 the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
@@
 
-The most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. there is unlikely a polynomial time algorithm for solving them.
-In this paper, we focus on the less studied \textit{property} computation of these problems which can be harder but is crutial towards understanding a problem.
+The most studied version of the above problems is finding the maximum/minimum set size and one of the sets of that size satisfying the contraints,
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
+In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a problem.
 Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
 but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.
-For the weighted version, it also includes finding largest/smallest $k$ sets and their sizes.
+For the weighted version of the above problems, it also includes finding largest/smallest $k$ sets and their sizes.
 %are many interesting and hard computational problems concerning various properties of independent sets.
@@
 To avoid the discussion being overly diversed, we limit the target problem to the independent set problem,
-and discuss other combinatorial optimization problems in \App{app:otherproblems}.
+and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
 For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
@@
 These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
+However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
 
@@
     \begin{split}
-    P(K2,\{x_a^{w_a}, x_b^{w_b}\}) &=
+    P({\rm K2},\{x_a^{w_a}, x_b^{w_b}\}) &=
     \left(\begin{matrix} 1 & x_a^{w_a} \end{matrix}\right)
@@
 In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
-One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
-\begin{equation}
-\left(\begin{matrix}
-1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
-1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
-\end{matrix}\right).\label{eq:lineareq}
-\end{equation}
-With this approach, we do not incur the linear overhead in space.
-However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
-In addition, the number could easily overflow if we use fixed-width integer types.
-The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
-These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
-\begin{equation}
-\eqname{GF$(p)$}
-\begin{split}
-    x ~\oplus~ y &= x+y\pmod p,\\
-    x ~\odot~ y &= xy\pmod p,\\
-    \mymathbb{0} &= 0,\\
-    \mymathbb{1} &= 1.
-\end{split}\label{eq:finitefield}
-\end{equation}
-With a finite-field algebra, we have the following observations:
-\begin{enumerate}
-    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
-The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
-    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
-    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
-\end{enumerate}
-With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-The algorithm iterates over a sequence of large prime numbers until convergence.
-In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
-Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
-As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
-All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
-In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transformation.
-
-\LinesNumberedHidden
-\begin{algorithm}[!ht]
-    \small
-    \SetAlgoNoLine
-    %\LinesNumbered
-    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
-
-    \While{true}{
-        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
-
-        \For{$i=0\ldots\alpha(G)$}{
-            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
-        }
-
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
-
-        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
-
-        \If{$A_P = A_{P \times p}$}{
-            \Return $A_P$ \tcp*[l]{converged}
-        }
-        $P = P \times p$\;
-    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
-\end{algorithm}
+In \App{sec:finitefield}, we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
+Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex number at the cost of precision.
 
@@
 We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
-These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
+These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 
-\section{Additional contraction overhead using the standard tensor network notations}\label{app:tensorbad}
+\section{Additional contraction overhead using the standard tensor network notations}\label{sec:tensorbad}
 As we have mentioned in the main text,
@@
 
-\section{Generalization to other graph problems}\label{app:otherproblems}
+\section{Generalization to other graph problems}\label{sec:otherproblems}
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
@@
 
-\section{The discrete Fourier transform approach to computing the independence polynomial}\label{app:fft}
+\section{The fitting approach to computing the independence polynomial}\label{sec:finitefield}
+In this section, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
+One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
+\begin{equation}
+\left(\begin{matrix}
+1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
+1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
+\end{matrix}\right).\label{eq:lineareq}
+\end{equation}
+With this approach, we do not incur the linear overhead in space.
+However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
+In addition, the number could easily overflow if we use fixed-width integer types.
+The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
+These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
+\begin{equation}
+\eqname{GF$(p)$}
+\begin{split}
+    x ~\oplus~ y &= x+y\pmod p,\\
+    x ~\odot~ y &= xy\pmod p,\\
+    \mymathbb{0} &= 0,\\
+    \mymathbb{1} &= 1.
+\end{split}\label{eq:finitefield}
+\end{equation}
+With a finite-field algebra, we have the following observations:
+\begin{enumerate}
+    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
+The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
+    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
+    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
+\end{enumerate}
+With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
+The algorithm iterates over a sequence of large prime numbers until convergence.
+In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
+Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
+As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
+If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
+All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
+
+\LinesNumberedHidden
+\begin{algorithm}[!ht]
+    \small
+    \SetAlgoNoLine
+    %\LinesNumbered
+    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
+
+    \While{true}{
+        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
+
+        \For{$i=0\ldots\alpha(G)$}{
+            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
+        }
+
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
+
+        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
+
+        \If{$A_P = A_{P \times p}$}{
+            \Return $A_P$ \tcp*[l]{converged}
+        }
+        $P = P \times p$\;
+    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
+\end{algorithm}
+
+\section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
 

### 2022-03-11 paper/paper.tex
update

@@
 while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
-In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a problem.
+In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a hard problem.
 Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 %Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
-Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
+Given a good contraction order, the time complexity of contracting a tensor network is $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
-Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for computing properties.
+Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for property computation.
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 
-To avoid the discussion being overly diversed, we limit the target problem to the independent set problem,
-and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
-For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
-and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
 %The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 %to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
-Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
-which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
 %However, there is a lack of general and versatile tool to compute these different properties of independent sets.
 
+To avoid the discussion being unnecessaryly diversed, we mainly focus on the independent set problem,
+and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
 The paper is organized as follows.
@@
 the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
-Owning to the development of modern compiling technology, we no longer need to limit our imagination to standard number types.
+Owning to the development of modern compiling technology, we no longer need to re our imagination to standard number types.
 One of the key concepts that push the technology forward is called generic programming:
@@
 This section is about reducing the independent set problem to a tensor network contraction problem,
-for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction and the independence polynomial from the partition function perspective.
-Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
+for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction from the partition function perspective.
+Let $G=(V,E)$ be a weighted undirected graph with each vertex $i\in V$ being associated with a weight $w_i$.
+An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
+and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
@@
 \section{Independence polynomial}\label{sec:indpoly}
-In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial.
+In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}.
+which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as

### 2022-03-11 paper/paper.tex
update

@@
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-%Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
 Given a good contraction order, the time complexity of contracting a tensor network is $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
@@
  a typical type of sparse graphs that has a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+In this benchmark, we do not include traditional algorithms for finding the MIS size like the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013},
+because to the best of our knowledge, most of the properties mentioned in this paper are not computable within these frameworks.
 

### 2022-03-11 paper/paper.tex
update

@@
    {Tropical (\Eq{eq:tropical})}    & {Maximum independent set size} \\
-   {Extended Tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
+   {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
    {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their counting} \\
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
-One can generate a random number and descent this expression tree by a probability proportional to the size of left and right branches.
+One can generate a random number and descend this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
 
@@
 while for general weighted graphs, the independence polynomial is not computable anymore.
-For general weighted graphs, we are more interested to know the total weights of maximum $k$ independent set sizes and their configurations.
+For general weighted graphs, we are more interested to know the $k$ most weighted sets and their sizes.
 Hence we define the extended tropical numbers as the following
@@
 \begin{equation}
-\eqname{Tk}
+\eqname{T$k$}
 \begin{split}
@@
 \begin{equation}
-    W^{\rm Tk}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
+    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{\rm Tk} = \left(\begin{matrix}
+        B^{{\rm T}k} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 
-Similar to the Tropical numbers, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configurations of each size.
-Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are complete.
+Similar to the tropical numbers, we can combine it with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
+Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are deterministic and complete.
 
@@
 because to the best of our knowledge, most of the properties mentioned in this paper are not computable within these frameworks.
+The main goal of this section is to show the relative timing for computing different properties.
 
@@
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
+    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs,
+        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest sets sizes.
     (c) The computing time for calculating the independence polynomials with different approaches.
-    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
+    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
+    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum product tree format,
+    with or without bounding the enumeration space.
     }

### 2022-03-11 paper/figures/plot.py

@@ -32,7 +32,7 @@ class PLT(object):
             ax=plt.subplot(222)   # size
             cornertex("(b)", ax, offset=(0,0))
             for k,(prefix, l) in enumerate([("counting_sum", r"counting ISs ($\mathbb{R}$"), ("size_max", "MIS size (T"), ("counting_max", "counting MISs (P1"), ("counting_max2", r"counting ISs of size $\alpha(G)$ and $\alpha(G)-1$ (P2"),
-                ("spectrum_max100", "maximum 100 sizes (T100")]):
+                ("spectrum_max100", "largest 100 sizes (T100")]):
                 for device in ["CPU", "GPU"]:
                     datafile = "../../benchmarks/data/"+prefix+"-r3-"+device+".dat"
                     if os.path.exists(datafile):

### 2022-03-11 paper/paper.tex
update

@@
 \subsection{Sampling extremely large configuration space}
-In many times, the number of configurations is too large to fit into any type of storage.
-Then instead of using the set algebra, we can use a binary sum-product tree as a compact representation of the results.
+When the graph size goes large, the configurations might be impossible to fit into any type of storage.
+Then instead of using the set algebra, one can use a binary sum-product tree as a compact representation of the configurations.
 We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
-$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content is a \texttt{LEAF} node,
+$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content in a \texttt{LEAF} node,
 $left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
@@
 \begin{equation}
-\eqname{SUMPROD}
+\eqname{SPT}
 \begin{split}
@@
 \begin{equation}
-    W^{\rm SUMPROD}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
+    W^{\rm SPT}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{\rm SUMPROD} = \left(\begin{matrix}
+        B^{\rm SPT} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
-One can generate a random number and descend this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
+To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
 

### 2022-03-12 paper/paper.tex
restructure

@@
 We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
-$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content in a \texttt{LEAF} node,
+\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node,
 $left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
@@
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN} and \texttt{SN}.
+Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN}, \texttt{SN}, \texttt{T100} and \texttt{SPT}.
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
@@
 
-\section{Technical guide}\label{sec:technical}
-This project depends on multiple open source packages in the Julia ecosystem.
-We list the Julia packages that play important roles in our code base as follows:
-
-\begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
-    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
-	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
-	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
-	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
-	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
-\end{description}
-
-One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
-\begin{lstlisting}
-pkg> add OMEinsum Graphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
-\end{lstlisting}
-
-The reader may find it surprising that the Julia implementation of the algorithms introduced in this work is so short that except the bounding algorithm,
-all are contained in this appendix. This is due to the power of generic programming. After installing the required packages, one can open a Julia REPL and copy the following codes into it.
-
-\lstinputlisting[breaklines]{../democode/demo.jl}
-
-For better performance, we recommend checking our GitHub repository for the full featured version:
-\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
-It can be installed in a similar style to other packages.
-
-\section{Additional contraction overhead using the standard tensor network notations}\label{sec:tensorbad}
+\section{An example of contraction complexity increase due to introducing $\delta$ tensors}\label{sec:tensorbad}
 As we have mentioned in the main text,
@@
 
+\section{Technical guide}\label{sec:technical}
+This project depends on multiple open source packages in the Julia ecosystem.
+We list the Julia packages that play important roles in our code base as follows:
+
+\begin{description}
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
+    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
+	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
+	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
+	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
+	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
+\end{description}
+
+One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
+\begin{lstlisting}
+pkg> add OMEinsum Graphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
+\end{lstlisting}
+
+The reader may find it surprising that the Julia implementation of the algorithms introduced in this work is so short that except the bounding algorithm,
+all are contained in this appendix. This is due to the power of generic programming. After installing the required packages, one can open a Julia REPL and copy the following codes into it.
+
+\lstinputlisting[breaklines]{../democode/demo.jl}
+
+For better performance, we recommend checking our GitHub repository for the full featured version:
+\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
+It can be installed in a similar style to other packages.
+
 \end{document}

### 2022-03-12 paper/paper.tex
update

@@
 \begin{example}\label{eg:twonode}
-In the following, we show a minimum example of mapping the independent problem of a 2 vertex graph (left) to a tensor network (right).
+In the following, we show a minimum example of mapping the independent problem of a 2 vertex complete graph K2 (left) to a tensor network (right).
 
@@
 \end{equation}
-This algebra is the same as the one used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
+Algebra \Eq{eq:tropical} and \Eq{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
 For independent set calculations here, the vertex tensor and edge tensor becomes:
@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
+Similarly, one can also truncate the polynomial and keep only its smallest several orders, which can be used for e.g. counting the minimum maximal independent sets.
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.

### 2022-03-12 paper/paper.tex
update weights

--- 2022-03-11 paper/paper.tex
@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be quantified locally.
-Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
+We introduce a method that uses generic programming tensor network to compute various properties of independent sets,
+which include, for example, the size of the maximum independent sets and the number and enumeration of independent sets of a given size.
 By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
-Other hard graph problems solvable in our framework includes the cutting problem, the K-coloring problem, the maximal clique problem, the dominating set problem, and satisfiability problem, among others.
+Our framework can be easily extended to compute properties of other problems such as the cut size, coloring, and maximal cliques, among others.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps people understand these hard problems better.
 \end{abstract}
@@
 In graph theory and combinatorial optimization, there is an important class of problems that can be quantified locally,
-including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
+including the independent set problem, the cutting problem, the 3-coloring problem, the 3-satisfiability problem,
 the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
@@
 
-The most studied version of the above problems is finding the maximum/minimum set size and one of the sets of that size satisfying the contraints,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
-In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a hard problem.
+The most studied version of the above problems is finding the maximum/minimum set size and one of the solution with that size satisfying the contraints,
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. there is unlikely a polynomial time algorithm for solving them.
+In this paper, we focus on the less studied \textit{property} computation of these problems which can be harder but is crutial towards understanding a problem.
 Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
 but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.
-For the weighted version of the above problems, it also includes finding largest/smallest $k$ sets and their sizes.
+For the weighted version, it also includes finding largest/smallest $k$ sets and their sizes.
 %are many interesting and hard computational problems concerning various properties of independent sets.
@@
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the time complexity of contracting a tensor network is $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
+%Traditional algorithms for finding the MIS size include the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+Given a good contraction order, contracting a tensor network in general has time complexity $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
-Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for property computation.
+Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for computing properties.
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 
+To avoid the discussion being overly diversed, we limit the target problem to the independent set problem,
+and discuss other combinatorial optimization problems in \App{app:otherproblems}.
+For an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
+and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
 %The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 %to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
+Meanwhile, finding the number of independent sets of a given size is equivalent to computing the coefficients of the independence polynomial~\cite{Harvey2018,Ferrin2014}.
+which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
 %However, there is a lack of general and versatile tool to compute these different properties of independent sets.
 
-To avoid the discussion being unnecessaryly diversed, we mainly focus on the independent set problem,
-and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
 The paper is organized as follows.
@@
 These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
+However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{app:tensorbad}.
 
@@
 the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
-Owning to the development of modern compiling technology, we no longer need to re our imagination to standard number types.
+Owning to the development of modern compiling technology, we no longer need to limit our imagination to standard number types.
 One of the key concepts that push the technology forward is called generic programming:
@@
    {Tropical (\Eq{eq:tropical})}    & {Maximum independent set size} \\
-   {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
+   {Extended Tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
    {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their counting} \\
@@
 This section is about reducing the independent set problem to a tensor network contraction problem,
-for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction from the partition function perspective.
-Let $G=(V,E)$ be a weighted undirected graph with each vertex $i\in V$ being associated with a weight $w_i$.
-An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
-and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
+for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction and the independence polynomial from the partition function perspective.
+Let $G=(V,E)$ be a weighted graph with each vertex $i\in V$ being associated with a weight $w_i$.
 We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
@@
     \begin{split}
-    P({\rm K2},\{x_a^{w_a}, x_b^{w_b}\}) &=
+    P(K2,\{x_a^{w_a}, x_b^{w_b}\}) &=
     \left(\begin{matrix} 1 & x_a^{w_a} \end{matrix}\right)
@@
 \section{Independence polynomial}\label{sec:indpoly}
-In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}.
-which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
+In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial.
 The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
@@
 In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-In \App{sec:finitefield}, we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex number at the cost of precision.
+Here, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
+One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
+\begin{equation}
+\left(\begin{matrix}
+1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
+1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
+\end{matrix}\right).\label{eq:lineareq}
+\end{equation}
+With this approach, we do not incur the linear overhead in space.
+However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
+In addition, the number could easily overflow if we use fixed-width integer types.
+The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
+These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
+\begin{equation}
+\eqname{GF$(p)$}
+\begin{split}
+    x ~\oplus~ y &= x+y\pmod p,\\
+    x ~\odot~ y &= xy\pmod p,\\
+    \mymathbb{0} &= 0,\\
+    \mymathbb{1} &= 1.
+\end{split}\label{eq:finitefield}
+\end{equation}
+With a finite-field algebra, we have the following observations:
+\begin{enumerate}
+    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
+The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
+    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
+    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
+\end{enumerate}
+With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
+The algorithm iterates over a sequence of large prime numbers until convergence.
+In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
+Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
+As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
+If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
+All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
+In \App{app:fft}, we provide another method to solve the linear equation using discrete Fourier transformation.
+
+\LinesNumberedHidden
+\begin{algorithm}[!ht]
+    \small
+    \SetAlgoNoLine
+    %\LinesNumbered
+    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
+
+    \While{true}{
+        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
+
+        \For{$i=0\ldots\alpha(G)$}{
+            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
+        }
+
+        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
+
+        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
+
+        \If{$A_P = A_{P \times p}$}{
+            \Return $A_P$ \tcp*[l]{converged}
+        }
+        $P = P \times p$\;
+    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
+\end{algorithm}
 
@@
 \subsection{Sampling extremely large configuration space}
-When the graph size goes large, the configurations might be impossible to fit into any type of storage.
-Then instead of using the set algebra, one can use a binary sum-product tree as a compact representation of the configurations.
+In many times, the number of configurations is too large to fit into any type of storage.
+Then instead of using the set algebra, we can use a binary sum-product tree as a compact representation of the results.
 We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
-$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content in a \texttt{LEAF} node,
+$\{\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM}, \texttt{PROD}\}$, $data$ is a bit string as the content is a \texttt{LEAF} node,
 $left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
@@
 \begin{equation}
-\eqname{SPT}
+\eqname{SUMPROD}
 \begin{split}
@@
 \begin{equation}
-    W^{\rm SPT}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
+    W^{\rm SUMPROD}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{\rm SPT} = \left(\begin{matrix}
+        B^{\rm SUMPROD} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
-To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
+One can generate a random number and descent this expression tree by a probability proportional to the size of left and right branches.
 
@@
 while for general weighted graphs, the independence polynomial is not computable anymore.
-For general weighted graphs, we are more interested to know the $k$ most weighted sets and their sizes.
+For general weighted graphs, we are more interested to know the total weights of maximum $k$ independent set sizes and their configurations.
 Hence we define the extended tropical numbers as the following
@@
 \begin{equation}
-\eqname{T$k$}
+\eqname{Tk}
 \begin{split}
@@
 \begin{equation}
-    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
+    W^{\rm Tk}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{{\rm T}k} = \left(\begin{matrix}
+        B^{\rm Tk} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 
-Similar to the tropical numbers, we can combine it with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
-Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are deterministic and complete.
+Similar to the Tropical numbers, we can attach a bit string sampler algebra \Eq{eq:singleconfig} to it for finding the configurations of each size.
+Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are complete.
 
@@
  a typical type of sparse graphs that has a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
-In this benchmark, we do not include traditional algorithms for finding the MIS size like the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013},
-because to the best of our knowledge, most of the properties mentioned in this paper are not computable within these frameworks.
-The main goal of this section is to show the relative timing for computing different properties.
 
@@
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs,
-        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest sets sizes.
+    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs, and the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$.
     (c) The computing time for calculating the independence polynomials with different approaches.
-    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
-    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum product tree format,
-    with or without bounding the enumeration space.
+    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations, all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$,  with or without bounding the enumeration space.
     }
@@
 We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
-These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
+These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{app:otherproblems}.
 Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 
-\section{Additional contraction overhead using the standard tensor network notations}\label{sec:tensorbad}
+\section{Additional contraction overhead using the standard tensor network notations}\label{app:tensorbad}
 As we have mentioned in the main text,
@@
 
-\section{Generalization to other graph problems}\label{sec:otherproblems}
+\section{Generalization to other graph problems}\label{app:otherproblems}
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
@@
 \begin{equation}
-    B_{\langle v, w\rangle} = \begin{cases}
-    1, & \langle v, w \rangle = 0 \\
-    x, & \langle v, w \rangle = 1,
+    B(w_{\langle u,v \rangle})_{\langle u, v\rangle} = \begin{cases}
+    1, & \langle u, v \rangle = 0 \\
+    x^{w_{\langle u,v \rangle}}_{\langle u, v\rangle}, & \langle u, v \rangle = 1,
 \end{cases}
 \end{equation}
-where label $\langle v, w \rangle$ is equivalent to $\langle w,v\rangle$.
+where label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
 Here, a vertex tensor specifies the restriction that a vertex cannot be matched by more than one edge, while an edge tensor contributes the variable in the polynomial.
@@
 \begin{equation}
-    B(x) = \left(\begin{matrix}
-        0 & x & x\\
-        x & 0 & x\\
-        x & x & 0
-    \end{matrix}\right).
-\end{equation}
-The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
+    B(x, w_{uv}) = \left(\begin{matrix}
+        0 & x^{w_{uv}} & x^{w_{uv}}\\
+        x^{w_{uv}} & 0 & x^{w_{uv}}\\
+        x^{w_{uv}} & x^{w_{uv}} & 0
+    \end{matrix}\right),
+\end{equation}
+where weights are associated with edges. The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
 By designing generic types as tensor elements, one can get other properties.
 Similarly, one can also define the $k$-coloring problem on edges by switching the roles of edges and vertices.
-Let $x_{\langle i,j\rangle} = x$, we have a graph polynomial,
+Let $x^{w_{uv}} = x$, we have a graph polynomial,
 where its $k$th coefficient is the number of coloring with $k$ bonds are satisfied.
@@
 \begin{equation}
-    B(x_{\langle i, j\rangle}) = \left(\begin{matrix}
-        1 & x_{\langle i, j\rangle}\\
-        x_{\langle i, j\rangle} & 1
+    B(x, w_{\langle i, j\rangle}) = \left(\begin{matrix}
+        1 & x_{j}^{w_{\langle i,j\rangle}}\\
+        x_{i}^{w_{\langle i,j\rangle}} & 1
     \end{matrix}\right),
 \end{equation}
-where variable $x_{\langle i, j\rangle}$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
-Let $x_{\langle i,j\rangle} = x$, we have a graph polynomial similar to previous ones,
+where variables $x_i$ and $x_j$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
+Let $x_i^{w_{\langle i,j\rangle}} = x_j^{w_{\langle i,j\rangle}} = x$, we have a graph polynomial similar to previous ones,
 where its $k$th coefficient is two times the number of configurations of cut size $k$.
@@
 \begin{equation}
-T(x_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-    0 & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
-    1 & s_v=0,\\
-    x_v^{w_v} & \text{otherwise},
+T(x, w_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+    0_v & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
+    1_v & s_v=0,\\
+    x^{w_v} & \text{otherwise},
 \end{cases}
@@
 where 0 stands for variable $a$ having value \texttt{false} while 1 stands for having value \texttt{true}.
-Then we map a clause to a tensor. For example, a clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
-\begin{equation}
-C = \left(\begin{matrix}
+Then we map a clause to a tensor. For example, the $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
+\begin{equation}
+C_{k} = \left(\begin{matrix}
 \left(\begin{matrix}
-x & x_{b} \\
-x_a & x_{ab}
+x^{w_k} & x_{b}^{w_k} \\
+x_a^{w_k} & x_{ab}^{w_k}
 \end{matrix}\right) \\
 \left(\begin{matrix}
-x_{c} & x_{bc} \\
-1 & x_{abc}
+x_{c}^{w_k} & x_{bc}^{w_k} \\
+1 & x_{abc}^{w_k}
 \end{matrix}\right)
-\end{matrix}\right).
-\end{equation}
-There is only one entry $(s_x, s_y, s_z) = (1, 0, 1)$ that makes this clause unsatisfied.
+\end{matrix}\right),
+\end{equation}
+where a weight is associated with a clause. There is only one entry $(s_x, s_y, s_z) = (1, 0, 1)$ that makes this clause unsatisfied.
 If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
@@
 
-\section{The fitting approach to computing the independence polynomial}\label{sec:finitefield}
-In this section, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
-One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
-\begin{equation}
-\left(\begin{matrix}
-1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
-1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
-\end{matrix}\right).\label{eq:lineareq}
-\end{equation}
-With this approach, we do not incur the linear overhead in space.
-However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
-In addition, the number could easily overflow if we use fixed-width integer types.
-The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
-These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
-\begin{equation}
-\eqname{GF$(p)$}
-\begin{split}
-    x ~\oplus~ y &= x+y\pmod p,\\
-    x ~\odot~ y &= xy\pmod p,\\
-    \mymathbb{0} &= 0,\\
-    \mymathbb{1} &= 1.
-\end{split}\label{eq:finitefield}
-\end{equation}
-With a finite-field algebra, we have the following observations:
-\begin{enumerate}
-    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
-The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
-    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
-    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
-\end{enumerate}
-With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-The algorithm iterates over a sequence of large prime numbers until convergence.
-In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
-Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
-As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
-All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
-
-\LinesNumberedHidden
-\begin{algorithm}[!ht]
-    \small
-    \SetAlgoNoLine
-    %\LinesNumbered
-    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
-
-    \While{true}{
-        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
-
-        \For{$i=0\ldots\alpha(G)$}{
-            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
-        }
-
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
-
-        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
-
-        \If{$A_P = A_{P \times p}$}{
-            \Return $A_P$ \tcp*[l]{converged}
-        }
-        $P = P \times p$\;
-    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
-\end{algorithm}
-
-\section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
+\section{The discrete Fourier transform approach to computing the independence polynomial}\label{app:fft}
 

### 2022-03-13 paper/paper.tex
update

@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be quantified locally,
+In graph theory and combinatorial optimization, there is an important class of problems that can be quantified over a vertex and its neighborhood,
 including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
@@
 
-The most studied version of the above problems is finding the maximum/minimum set size and one of the sets of that size satisfying the contraints,
+The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size ,
 while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
@@
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the time complexity of contracting a tensor network is $2^{{\rm tw}(G)}$~\cite{Markov2008}, where ${\rm tw}(G)$ is the treewidth of graph $G$.
+Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}.
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
-Although this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013} for solving the maximum size and one of the best set, tensor network has richer algebraic structure, and this structure is crutial for property computation.
+When using tensor network for solving one of the best sets with the maximum size,
+this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013},
+however, tensor network has richer algebraic structure, and this structure is crutial for property computation.
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 \section{Tensor network representation of independent sets} \label{sec:tnmap}
-This section is about reducing the independent set problem to a tensor network contraction problem,
-for people with physics background, it is suggested to use an alternative approach described in \App{sec:energymodel} to understand this construction from the partition function perspective.
+This section is about reducing the independent set problem to a tensor network contraction problem.
+For people with physics background, we suggest using an alternative approach described in \App{sec:energymodel} to understand this reduction from an energy model.
 Let $G=(V,E)$ be a weighted undirected graph with each vertex $i\in V$ being associated with a weight $w_i$.
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
-and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}|I|$. 
-We map a vertex $i\in V$ to a label $s_i \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each label $s_i$, we defined a parametrized rank-one vertex tensor $W(x_i, w_i)$ as
-\begin{equation}
-    W(x_i, w_i) = \left(\begin{matrix}
-        1 \\
-        x_i^{w_i}
+and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$. 
+We map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
+For each label $s_v$, we defined a parametrized rank-one vertex tensor $W(x_v, w_v)$ as
+\begin{equation}
+    W(x_v, w_v) = \left(\begin{matrix}
+        1_v \\
+        x_v^{w_v}
     \end{matrix}\right).\label{eq:vertextensor}
 \end{equation}
-We use subscripts to index tensor elements, e.g.\ $W(x_i, w_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i, w_i)_1=x_i^{w_i}$ is the second element associated with $s_i=1$.
+where we use subscripts to annotate different vertices, these annotation are only used in configuration enumeration and sampling.
+One can index tensor elements by subscripting tensors, e.g.\ $W(x_i, w_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i, w_i)_1=x_i^{w_i}$ is the second element associated with $s_i=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 \section{Independence polynomial}\label{sec:indpoly}
-In the special case of $x_i = x$ and $w_i = 1$, the tensor network contraction result directly corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}.
+Let $x_i = x$ and $w_i = 1$, the evaluation of \Eq{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}.
 which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
-In the previous section, we focused on computing the independence polynomial for a graph $G$ of a given MIS size $\alpha(G)$, but we did not show how to compute this number.
-The method we use to compute this quantity is based on the following observations. Let $x=\infty$, the independence polynomial becomes
+The MIS size $\alpha(G)$, or the independence number is an important graph characteristics.
+The method we use to compute this quantity is based on the following observations.
+Let $x=\infty$, the independence polynomial in the previous section becomes
 \begin{equation}
@@
 \subsection{Truncated polynomial algebra for counting independent sets of large size}
-Instead of counting just the MISs, one may be interested in counting the independent sets of large sizes close to the MIS size.
+Instead of counting just the MISs, one may also be interested in counting the independent sets with largest several sizes.
 For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial} as:
@@
 \subsection{Set algebra for configuration enumeration}
-The enumeration problems of independent sets are also interesting and has been studied extensively in the literature~\cite{Bron1973, Eppstein2010, Johnson1988}, including,
-for example, the enumeration of all independent sets, the enumeration of all maximal independent sets, or the enumeration of all MISs.
+The configuration enumeration of independent sets includes,
+for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
+The most studied enumeration of maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} requires using a different tensor network structure, which is discussed in \App{sec:maximal}.
 To enumerate all independent sets, we designed an algebra defined on sets of bitstrings:
@@
 where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
+The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$.
 The vertex tensor and edge tensor become
 \begin{equation}
-    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes 1) = \left(\begin{matrix}
+    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes 1, w_v) = \left(\begin{matrix}
         \mymathbb{1} \\
-        -\infty^{\otimes k-1} \otimes 1
+        -\infty^{\otimes k-1} \otimes w_v
     \end{matrix}\right),   
@@
         \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-
+    \end{matrix}\right),
+\end{equation}
+where we have used the relation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
 Similar to the tropical numbers, we can combine it with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
-Note here, the $\odot$ of configuration sampler is not used so that the resulting configurations are deterministic and complete.
+Since the $\odot$ operation of configuration sampler is not used, the resulting configurations are deterministic and complete.
 
@@
 \section{Discussion and conclusion}
-In this paper, we introduce a method to use generic programming tensor networks to compute a number of different independent set properties, including the size of the MISs and the number and enumeration of independent sets of a given size.
-For each property, we design an algebra of a commutative semiring with a particular element type and map the computation of the property to the contraction of a tensor network with such an element type.
-The data types introduced in the main text can be represented in the following diagram, where we use overlap to represent two algebras that can be combined to create a new algebra.
+In this paper, we introduce a method to use generic programming tensor networks to compute a number of different properties of a hard problem,
+including the largest several independent sets sizes, the counting of independent sets of a given size and
+the enumeration of independent sets of a given size.
+For each property, we design an algebra being a commutative semiring and let it be the tensor element type.
+The contraction of the same tensor network gives us the corresponding property.
+The data types introduced in the main text is summarized in the diagram in \Fig{fig:venn-diagram}.
 
@@
 
-    \caption{The the tensor network element types used in this work.
+    \caption{The the tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
     The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.}

### 2022-03-13 paper/paper.tex
update

@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be quantified locally.
+We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be quantified over a local set.
 Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 \cyan{a comment} and \xcyan{a resolved comment}
+\blue{I am not sure I an use the word ``quantify'' in a tensor network!
+It is borrowed from the field of logic,
+but I am feeling defining a local tensor in our paper is same as quantifing over a variable in logic.
+\href{https://en.wikipedia.org/wiki/Quantifier\_(logic)}{https://en.wikipedia.org/wiki/Quantifier\_(logic)}}
 
@@
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-Finding maximal independent sets of a graph is equivalent to finding the maximal cliques of its complement graph, so in the following we mainly discuss how to find maximal independent sets.
-Let us denote the neighborhood of a vertex $v$ as $N(v)$ and denote $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent set where there exists no vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$.
-Similar to the independence polynomial, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017},
-which can be helpful for understanding why the program for solving MIS can be trapped in a local minimum.
-Concretely, it is defined as
-\begin{equation}
-I_{\rm max}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
-\end{equation}
-where $b_k$ is the number of maximal independent sets of size $k$ in graph $G=(V, E)$.
-Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$I_{\rm max}(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013}, where, to our knowledge, the fastest algorithm currently has a runtime of $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-If we want to find an MIS, $b_{k}$ counts the number of local optimum at size $k < \alpha(G)$, and can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
-The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
-
-We can modify the tensor network for computing the independence polynomial to include this restriction.
-Instead of defining the restriction on vertices and edges, it is more natural to define it on $N[v]$:
+Since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of its complement graph, in the following,
+we limit our discussion to finding maximal independent sets.
+Let us denote the neighborhood of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
+A maximal independent set $I_m$ is an independent set where there does exist a vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$,
+i.e. an independent set that can not become a larger one by adding a new vertex.
+To characterize the maximal independence restriction, one can quantify over a local set $N[v]$ with a local tensor:
 \begin{equation}\label{eq:maximal}
@@
     \left(\begin{matrix}
-        0 &1 \\
-        1 &1
+        ~~0 &~1 \\
+        ~~1 &~1
     \end{matrix}\right)\\
@@
 
-By contracting this tensor network with generic element types,
-we can compute the maximal independent set properties such as the maximal independence polynomial and the enumeration of maximal independent sets.
 Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
@@
         \def\dx{0};
-        \def\r{0.5cm}
+        \def\r{0.4cm}
         \def\G{1.0}
@@
         \foreach \x/\v/\t in {0/A/$T_a$, 1/B/$T_b$, 2/C/$T_c$, 3/D/$T_d$, 4/E/$T_e$}
-            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\t};
+            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\scriptsize \t};
         \draw [cyan,thick] (a) -- (A);
@@
 
-One can see that the average degree of a tensor is increased.
+One can see that the average rank of a tensor is increased.
 The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
-However, for most sparse graphs, this tensor network contraction approach is still much faster than enumerating all the maximal cliques on its complement graph using the Bron-Kerbosch algorithm~\cite{Bron1973}, which is the standard algorithm that we are aware of to compute the maximal independence polynomial.
+
+By contracting this tensor network with generic element types,
+we can compute the maximal independent set properties such as the maximal independence polynomial and the enumeration of maximal independent sets.
+Similar to the independence polynomial, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017}.
+%which can be helpful for understanding why the program for solving MIS can be trapped in a local minimum.
+Let $G=(V,E)$ be a graph, its maximal independence polynomial is defined as
+\begin{equation}
+D_{m}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
+\end{equation}
+where $b_k$ is the number of maximal independent sets of size $k$.
+Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
+$D_m(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013},
+which to our knowledge, the best algorithm gives a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
+If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
+%The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
+
 We show the benchmark of computing the maximal independent set properties in \Fig{fig:benchmark-maximal},
@@
 \subsection{Matching problem}
-A matching polynomial of a graph $G$ is defined as
-\begin{equation}
-    M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
-\end{equation}
-where $k$ is the size of a matching, and coefficients $c_k$ are the corresponding counting of the number of matchings of the size $k$.
-We map an edge $(u, v) \in E$ to a label $\langle u, v\rangle \in \{0, 1\}$ in a tensor network,
-where $1$ means two vertices of an edge are matched and $0$ otherwise.
-Then we define a tensor of rank $d(v) = |N(v)|$ on vertex $v$ such that,
+A $k$-matching in a graph $G=(V,E)$ is a set of $k$ edges, no two of which have a vertex in common.
+We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network,
+where $1$ means this edge is in the set and $0$ otherwise.
+To characterize the matching, one can define a tensor of rank $d(v) = |N(v)|$ on vertex $v$
 \begin{equation}
@@
 where label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
-Here, a vertex tensor specifies the restriction that a vertex cannot be matched by more than one edge, while an edge tensor contributes the variable in the polynomial.
-
-\subsection{$k$-Coloring}
-Let us use the 3-coloring problem defined on vertices as an example.
-For a vertex $v$, we define the degrees of freedom $c_v\in\{0,1,2\}$ and a vertex tensor labelled by it as
+The vertex tensor specifies the constraint that a vertex cannot be shared by two edges in the matched set,
+while an edge tensor carries the weights as the target to optimize.
+Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction gives us the matching polynomial
+\begin{equation}
+    M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
+\end{equation}
+where $k$ is the size of a matched edges set, and a coefficients $c_k$ is the number of $k$-matchings.
+
+\subsection{Vertex coloring}
+Let $G=(V,E)$ be a graph, a vertex coloring is an assignment of colors to each vertex $v\in V$ such that no edge connects two identically colored vertices. 
+In a $k$-coloring problem, the number of different colors can be used is limited to less or equal to $k$.
+Let us use the 3-coloring problem as an example to show how to characterize with local tensors.
+For each vertex $v \in V$, we associate a degree of freedom $c_v\in\{0,1,2\}$ to it.
+Then we define a vertex tensor labelled by it as
 \begin{equation}
@@
 \end{equation}
-where $r_v$, $g_v$ and $b_v$ are colors used to label the configurations.
-For an edge $(u, v)$, we define an edge tensor as a matrix labelled by $(c_u, c_v)$ to specify the constraint
+where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations.
+For each edge $(u, v)$, we specify the constraint carrying a weight $w_{uv}$ on it by defining an edge tensor labelled by $(c_u, c_v)$ as
 \begin{equation}
@@
         x^{w_{uv}} & x^{w_{uv}} & 0
-    \end{matrix}\right),
-\end{equation}
-where weights are associated with edges. The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
-By designing generic types as tensor elements, one can get other properties.
-Similarly, one can also define the $k$-coloring problem on edges by switching the roles of edges and vertices.
+    \end{matrix}\right).
+\end{equation}
+The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
 Let $x^{w_{uv}} = x$, we have a graph polynomial,
-where its $k$th coefficient is the number of coloring with $k$ bonds are satisfied.
+in which the $k$-th coefficient is the number of coloring with $k$ bonds satisfied.
 If a graph is colorable, the maximum order of this polynomial should be equal to the number of edges in this graph.
+Similarly, one can define the $k$-coloring problem on edges by defining the tensor network on the line graph of $G$.
 
 \subsection{Max-Cut problem}
-The Max-Cut problem is also known as the boolean spin glass problem.
+In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
+which is also known as the boolean spin glass problem in statistic physics.
 For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
@@
 \subsection{Dominating Set}
-Let $G=(V,E)$ be the target graph that we want to solve.
+In graph theory, a dominating set for a graph $G = (V, E)$ is a subset $D \subseteq V$ such that every vertex not in $D$ is adjacent to at least one member of $D$.
 The tensor network representation map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
@@
 
-\subsection{Satisfiability Problem}
-We can contruct a satisfiability problem to solve the above problem.
-To generate a tensor network, we map a boolean variable $a$ and its negation $\neg a$ to a degree of freedom (label) $s_a \in \{0, 1\}$,
+\subsection{Boolean satisfiability Problem}
+The boolean satisfiability problem is the problem of determining if there exists an interpretation that satisfies a given boolean formula.
+One can specify a satisfiable problem in the conjuctive normal form (CNF): a conjuction of disjunctions of boolean literals,
+where a disjunction of boolean literals is also called a clause.
+To reduce a CNF solving to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom (label) $s_a \in \{0, 1\}$,
 where 0 stands for variable $a$ having value \texttt{false} while 1 stands for having value \texttt{true}.

### 2022-03-13 paper/paper.tex
update

--- 2022-03-13 paper/paper.tex
@@
 The most studied enumeration of maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} requires using a different tensor network structure, which is discussed in \App{sec:maximal}.
-To enumerate all independent sets, we designed an algebra defined on sets of bitstrings:
+To enumerate all independent sets, we designed an algebra defined on sets of bit strings:
 \begin{equation}
@@
 For each property, we design an algebra being a commutative semiring and let it be the tensor element type.
-The contraction of the same tensor network gives us the corresponding property.
+With different algebras, the contraction of the same tensor network gives us the different properties.
 The data types introduced in the main text is summarized in the diagram in \Fig{fig:venn-diagram}.
+Other than the case with real numbers, we have polynomials and truncated polynomials.
+We combine them with the bit string algebra, the set algebra, and sum product tree algebra for finding, enumeration, and sampling of independent sets at a given size.
+These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
+Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
+our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
+By adapting to the style of generic programming, we can implement all the algorithms without much effort.
+We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
+A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
+We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
+We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
 
@@
 
-Other than the case with real numbers, we have polynomials and truncated polynomials as algebra types.
-We combine them with the set algebra and the bitstring algebra for set enumeration and sampling. 
-These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
-Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
-our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
-By adapting to the style of generic programming, we can implement all the algorithms without much effort.
-We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
-A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
-We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
-We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
-
 \section*{Acknowledgments}
@@
 We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
-We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt, for solving some implementation issues voluntarily.
+We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt,
+for actively maintaining their packages and resolving related issues voluntarily.
 \blue{funding information}
@@
 Let us characterize the independent set problem on graph $G=(V, E)$ as an energy model
-\begin{equation}
+\begin{equation}\label{eq:eng}
     \mathcal{E}(G, s) = -\sum_{i\in V(G)} w_i s_i + \infty \sum_{\langle i,j\rangle \in E(G)}s_i s_j
 \end{equation}
-where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term.
+where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term associated with it.
 The first term is the energy that corresponds to the inverse of the independent set size and the second term describes the independence contraint.
@@
 Its partition function is defined as
-\begin{equation}
+\begin{equation}\label{eq:partition}
     \begin{split}
     Z(G, \beta) = \sum_{s}e^{-\beta \mathcal{E}(G, s)} = \sum_{s\in \mathcal{I}(G)} e^{\beta \sum w_i s_i}\\
-         = \sum_{k=0}^{\alpha(G)}D(k) e^{\beta k}  \qquad \quad (w_i = 1)
+         = \sum_{k=0}^{\alpha(G)}a(k) e^{\beta k}  \qquad \quad (k = \sum w_i s_i)
     \end{split}
@@
 where $\mathcal{I}(G)$ is the set of independent sets of graph $G$.
-The second line corresponds to the unweighted independent set problem,
-$\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size) and $D(k)$ is the number of states with energy $-k$ (independent sets of size $k$).
-It can be evaluated as a tensor network contraction,
-where the tensor network is constructed by placing a vertex tensor on each vertex $i$
+$\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size).
+$a(k)$ is the number of spin configurations with energy $-k$ (independent sets of size $k$).
+The partition function can be evaluated as a tensor network contraction,
+where the tensor network is constructed by placing a vertex tensor on each spin $i$
 \begin{equation}
@@
 \end{equation}
-and a bond tensor on each edge
+and an edge tensor on each bond
 \begin{equation}
@@
 \end{equation}
-where the $0$ in the bond tensor comes from $e^{-\beta\infty}$ from the second term of the energy model.
-By letting $x = e^{\beta w_i}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
+where the $0$ in the bond tensor coming from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}.
+By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor},
+and by letting $w_i=1$, the second line of \Eq{eq:partition} is the independence polynomial.
 
@@
 
+In the following, we are going to show introducing $\delta$ tensors might increase the contraction complexity of a tensor network.
 Let us consider the following King's graph.
@@
 
-By mapping the independent set problem to a standard tensor network, we have the following graphical representation.
+By mapping the independent set problem to a standard tensor network with $\delta$ tensors,
+we have the following graphical representation.
 
@@
 
-In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor up to rank $8$.
+In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor of rank $8$ or less.
 If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
@@
 A vertex tensor always has rank $1$ and is not shown here since it does not change the contraction complexity.
-If we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be seen by counting the number of colors.
-
-\section{Generalization to other graph problems}\label{sec:otherproblems}
+If we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be seen by counting the number of colors at the cut.
+
+\section{Hard problems and tensor networks}\label{sec:otherproblems}
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}

### 2022-03-13 paper/paper.tex
polish the appendix

@@
 we limit our discussion to finding maximal independent sets.
-Let us denote the neighborhood of a vertex $v$ as $N(v)$ and $N[v] = N(v)\cup \{v\}$.
+Let us denote the neighborhood of a vertex $v$ as $N(v)$ and the closed neighborhood of $v$ as $N[v] = N(v)\cup \{v\}$.
 A maximal independent set $I_m$ is an independent set where there does exist a vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$,
@@
 
-\subsection{Max-Cut problem}
+\subsection{Cutting problem}
 In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
 which is also known as the boolean spin glass problem in statistic physics.
-For a vertex $v\in V$, we define a boolean degree of freedom $s_v\in\{0, 1\}$.
-Then the Max-Cut problem can be encoded to tensor networks by mapping an edge $(i,j)\in E$ to an edge matrix labelled by $s_is_j$
-\begin{equation}
-    B(x, w_{\langle i, j\rangle}) = \left(\begin{matrix}
-        1 & x_{j}^{w_{\langle i,j\rangle}}\\
-        x_{i}^{w_{\langle i,j\rangle}} & 1
+Let $G=(V,E)$ be a graph, to reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
+Then for each edge $(u,v)\in E$, we define an edge matrix labelled by $s_us_v$ as
+\begin{equation}
+    B(x, w_{uv}) = \left(\begin{matrix}
+        1 & x_{v}^{w_{uv}}\\
+        x_{u}^{w_{uv}} & 1
     \end{matrix}\right),
 \end{equation}
-where variables $x_i$ and $x_j$ represents a cut on edge $(i, j)$ or a domain wall of an Ising spin glass.
-Let $x_i^{w_{\langle i,j\rangle}} = x_j^{w_{\langle i,j\rangle}} = x$, we have a graph polynomial similar to previous ones,
-where its $k$th coefficient is two times the number of configurations of cut size $k$.
+where variables $x_u$ and $x_v$ represents a cut on this edge or a domain wall in an spin glass.
+Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$, we have a graph polynomial similar to previous ones,
+where its $k$th coefficient is two times the number of cuts with size $k$ (i.e. cutting $k$ edges).
 
@@
 In graph theory, a dominating set for a graph $G = (V, E)$ is a subset $D \subseteq V$ such that every vertex not in $D$ is adjacent to at least one member of $D$.
-The tensor network representation map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
-We defined the restriction on a vertex and its neighbouring vertices $N(v)$:
+To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
+Then for each vertex $v\in V$ we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
 \begin{equation}
@@
 this configuration is forbidden because $v$ is not adjacent to any member in the set.
-otherwise, if $v$ is in $D$, it has a contribution $x_v^{w_v}$ to the final result.
+Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output.
 The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009},
@@
 \end{equation}
-where $d_k$ is the number of dominating sets of size $k$ in graph $G=(V, E)$.
+where $d_k$ is the number of dominating sets of size $k$.
 
@@
 One can specify a satisfiable problem in the conjuctive normal form (CNF): a conjuction of disjunctions of boolean literals,
-where a disjunction of boolean literals is also called a clause.
-To reduce a CNF solving to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom (label) $s_a \in \{0, 1\}$,
+where a disjunction of boolean literals is also named a clause.
+To reduce the problem of solving CNF to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom (label) $s_a \in \{0, 1\}$,
 where 0 stands for variable $a$ having value \texttt{false} while 1 stands for having value \texttt{true}.
@@
 x_{c}^{w_k} & x_{bc}^{w_k} \\
-1 & x_{abc}^{w_k}
+1_{ac} & x_{abc}^{w_k}
 \end{matrix}\right)
@@
 \end{equation}
-where a weight is associated with a clause. There is only one entry $(s_x, s_y, s_z) = (1, 0, 1)$ that makes this clause unsatisfied.
+where a weight $w_k$ is associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
 If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
-Let $x_{ab\ldots} = x$, then we can get a polynomial that its $k$-th coefficients gives us the number of assignments with $k$ clauses satisfied.
+Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments with $k$ clauses satisfied.
 
@@
 \begin{equation}
-    B_{v,w,\ldots, z} = \begin{cases}
-        1, & v+w+\ldots+z\leq 1,\\
+    B_{s_u,s_v,\ldots, s_w} = \begin{cases}
+        1, & s_u+s_v+\ldots+s_w\leq 1,\\
         0, & \text{otherwise}.

### 2022-03-15 paper/paper.tex
sum combination algorithm

@@
 where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
-The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$.
+The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$,
+one can find an implementation in \App{sec:maxsum}.
 The vertex tensor and edge tensor become
@@
 
+\section{Computing maximum sum combination}\label{sec:maxsum}
+Given two sets $A$ and $B$ of the same size $n$.
+It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $n\log(n)$.
+The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure which can can be much slower to manipulate than arrays.
+In the following, we show an algorithm that has roughly the same complexity (given the data range is not exponentially large)
+but does not need a heap.
+This algorithm first sorts both $A$ and $B$, then use the bisection to find the $n$-th largest value in the sum combination.
+The key point is we can count the number of entries greater than a specific value
+in the sum combination of $A$ and $B$ in linear time.
+We summarize the algorithm as in Algorithm~\ref{alg:sumcombination}.
+
+\LinesNumberedHidden
+\begin{algorithm}[!ht]
+    \SetKwProg{Fn}{function}{}{end}
+    \small
+    \SetAlgoNoLine
+    Let $A$ and $B$ be two sets of size $n$\;
+
+    \tcp{sort $A$ and $B$ in ascending order}
+    $A \gets {\rm sort}(A)$\;
+
+    $B \gets {\rm sort}(B)$\;
+
+    \tcp{use bisection to find the $n$-th largest value in sum combination}
+
+    ${\rm high} \gets A_n+B_n$\;
+
+    ${\rm low} \gets A_1+B_n$\;
+
+    \While{true}{
+        ${\rm mid} \gets ({\rm high} + {\rm low}) / 2$\;
+
+        $c \gets \texttt{count\_geq}(n, A, B, {\rm mid})$\;
+
+        \uIf{$c > n$}{
+            ${\rm low} \gets {\rm mid}$\;
+        }\uElseIf{$c = n$}{
+            \Return \texttt{collect\_geq}$(n, A, B, {\rm mid})$\;
+        }\Else{
+            ${\rm high} \gets {\rm mid}$\;
+        }
+    }
+
+    \Fn{{\rm \texttt{count\_geq}}($n$, $A$, $B$, $v$)}{
+        $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
+
+        $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
+
+        $c \gets 0$\; \tcp*[l]{the counting of sum combinations s.t. $a+b\geq v$}
+
+        \For{$q$ = $n, n-1 \ldots 1$}{
+            $b \gets B_{n-q+1}$\;
+
+            \While{$k < n$ \textbf{and} $a+b \geq v$}{
+                $k \gets k+1$\;
+
+                $a \gets A_{n-k+1}$\;
+            }
+
+            \uIf{$a+b \geq v$}{
+                $c \gets c + k$\;
+            }\Else{
+                $c \gets c + k-1$\;
+            }
+        }
+        \Return c\;
+    }
+
+    % \Fn{\rm collect\_geq($n$, $A$, $B$, $v$)}{
+    %     $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
+
+    %     $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
+
+    %     $S \gets \{\}$ \tcp*[l]{the sum combinations s.t. $a+b\geq v$}
+
+    %     \For{$q$ = $n, n-1 \ldots 1$}{
+    %         $b \gets B_{n-q+1}$\;
+
+    %         \While{$k < n$ \textbf{and} $a+b \geq v$}{
+    %             $k \gets k+1$\;
+
+    %             $a \gets A_{n-k+1}$\;
+    %         }
+
+    %         \uIf{$a+b \geq v$}{
+    %             $m \gets k$\;
+    %         }\Else{
+    %             $m \gets k-1$\;
+    %         }
+    %         \For{$j$ = \KwTo $1,2\ldots,m$}{
+    %             $S \gets S \cup \{b + A_{n-j+1}\}$
+    %         }
+    %     }
+    %     \Return S\;
+    % }
+    \caption{Fast sum combination without using heap}\label{alg:sumcombination} 
+\end{algorithm}
+
+Function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by the item collection.
+Note in function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration,
+the total number of iterations must be smaller or equal to $2n$.
+Here for simplicity, we do not handle the $-\infty$s in $A$ and $B$ and the degeneracy in the sums.
+They need to be taken seriously in practical implementations.
+
 \section{Technical guide}\label{sec:technical}

### 2022-03-15 paper/paper_maddie_edits.tex
added comments on general flow and questions on content

--- 2022-03-15 paper/paper.tex
@@
 \newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
+\newcommand{\purple}[1]{[{\bf  \color{purple}{MC: #1}}]}
+\newcommand{\xpurple}[1]{[{\bf  \color{purple}{\sout{MC: #1}}}]}
 \newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
@@
 including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
-the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
+the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}. \purple{Not clear to me what ``over a vertex and its neighborhood'' means. }
 There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
 wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
-\blue{need more diversed applications not limited to IS}
-
-The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size ,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
-In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a hard problem.
-Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
+\blue{need more diversed applications not limited to IS} \purple{Here I would say that that these problems are intractable (exponential runtime in problem size in the worst-case), but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications.}
+
+The most studied version of the above problems is finding a maximum/minimum set satisfying the constraints and the corresponding set size,
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e.
+it is unlikely to solve them in a polynomial time.
+\purple{Is MIS really the most studied NP-hard optimization problem?
+I would guess it is heavily studied, but not necessarily the most studied.}
+In this paper, we focus on the less studied \textit{property} computation which can be harder but is crucial towards understanding a hard problem.
+\purple{It might be interesting to note that computing the number of sets of a given size is \#P-hard (class of all counting problems), which is believed to be much harder than NP.}
+Here, the \textit{property} \purple{Consider using ``solution space property'' instead of just ``property''.} refers to a class of quantities that not only include the maximum/minimum set size,
 but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.
 For the weighted version of the above problems, it also includes finding largest/smallest $k$ sets and their sizes.
+\purple{I would give examples of why we want to compute solution space properties.
+For instance, in statistical physics, computing thermal states and observables via the partition function.
+In complexity theory, proving limits on local algorithms (OGP).
+}
 %are many interesting and hard computational problems concerning various properties of independent sets.
@@
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is also known as the sum product network or einsum in different fields,
+Tensor network is also known as the sum product network or einsum in different fields, \purple{Say which fields}
 where its tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
+\purple{Briefly say what tensor networks are in a few words, so that ``restricted to standard number types such as real numbers and complex numbers'' can be put into context.
+A reader new to tensor networks might be wondering what a tensor network is, and the only context we get from this sentence is that they involve numbers}
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}.
+Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}. \purple{I'd write out $2^{\text{tw}(G)}$.}
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
+\purple{Is the scaling of these algorithms known?}
 When using tensor network for solving one of the best sets with the maximum size,
-this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013},
-however, tensor network has richer algebraic structure, and this structure is crutial for property computation.
+this time complexity is on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013},
+however, tensor network has richer algebraic structure, and this structure is crucial for property computation. \purple{Not clear how first part and second part of sentence are related}
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 
-To avoid the discussion being unnecessaryly diversed, we mainly focus on the independent set problem,
-and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
+To avoid the discussion being unnecessarily complicated, we  focus concretely on the independent set problem,
+and discuss other combinatorial optimization problems in \App{sec:otherproblems}. \purple{More details on which combinatorial optimization problems this applies to?}
 The paper is organized as follows.
@@
 One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice.
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice \purple{signifying which pairs of indices are summed over}.
 Hence a tensor network can be represented as a simple graph,
@@
 These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
+However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction.
+We illustrate this subtle point in \App{sec:tensorbad}.
+\purple{ I feel that the $\delta$ tensors point is unnecessary to mention in the main text.
+Because not much detail is given, I internalized what it meant only on the third read-through.}
 
@@
 \section{Generic programming tensor contractions}\label{sec:generic}
+\purple{On a second read of this section, I think that the clarity could be improved. My understanding is this is the flow: 
+We would like to use generic programming, where we write code that works regardless of input type, and is optimized on all input types without sacrificing efficiency. 
+In general, we can write code such that a function runs correctly regardless of the input data type.
+This is easy to do for dynamically typed languages like Python, which only verify and enforce the rules for the input data type at runtime (called \textit{type-checking}).
+However, when the input data type is only checked at runtime (as opposed to when the code is compiled), type-specific optimization cannot be used.
+High efficiency  is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).
+}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
 the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
-Owning to the development of modern compiling technology, we no longer need to re our imagination to standard number types.
+Owing to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
 One of the key concepts that push the technology forward is called generic programming:
@@
 \end{definition}
+\purple{I think the following paragraph could be clarified.
+When you read the definition of generic programming, it's not clear what ``in the most general setting'' means.
+My understanding is it just means that the program will work regardless of the input data type - it would be good to say this explicitly.
+I also think the way it is written takes a while to understand what dynamically versus statically typed languages are.
+The definition, ``When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.'' comes rather late in the paragraph.
+Also, while I know what you mean, concepts like ``inlining immutable elements'' and ``cache miss rate'' would be lost on someone only with a physics background.
+}
 
 This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
-To understand the first aspect on generality, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
+To understand the first aspect on generality, \purple{This is a really helpful example!} suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
 One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
@@
 instead it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
-In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
+In such a way, when the program takes a matrix as an input, it computes the matrix power without extra effort.
 The second aspect is about performance. For dynamically typed languages such as Python,
@@
 
-This motivates us to think about what is the most general element type allowed in a tensor network contraction program.
+This motivates us to think about what is the most general element type \purple{I would clarify element type means tensor element type} allowed in a tensor network contraction program.
 We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
@@
 \end{align*}
-We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we wish this contraction order does not change the contraction results.
+We require the algebra be multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we wish this contraction order does not change the contraction results.
+\purple{The previous sentence makes a lot of sense!}
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
@@
    {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their counting} \\
+   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent set sizes and their counting \purple{``and their counting'' is gramatically confusing, can we say independence polynomial or degeneracy or something?}} \\
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
@@
 This section is about reducing the independent set problem to a tensor network contraction problem.
-For people with physics background, we suggest using an alternative approach described in \App{sec:energymodel} to understand this reduction from an energy model.
-Let $G=(V,E)$ be a weighted undirected graph with each vertex $i\in V$ being associated with a weight $w_i$.
+For people with a physics background, we suggest using an alternative approach described in \App{sec:energymodel} to understand this reduction from an energy model.
+Let $G=(V,E)$ be a weighted, undirected graph with each vertex $i\in V$ being associated with a weight $w_i$ \purple{I suggest being consistent in subscripts, and use $u/v$ for nodes as you do later, e.g.
+$v \in V$ instead of $i/j$}
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
@@
 \begin{example}\label{eg:twonode}
-In the following, we show a minimum example of mapping the independent problem of a 2 vertex complete graph K2 (left) to a tensor network (right).
+In the following, we show a minimum example of mapping the independent problem of a complete graphs with two vertices K2 (left) to a tensor network (right).
 
@@
 \end{example}
-
-It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
+\purple{This example is really helpful!}
+
+It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. \purple{Perhaps explicitly say what this scales as?}
 The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
 A fully optimized contraction order can reduce the time to $O(2^{\text{tw}(G)})$~\cite{Markov2008}, while requiring a space at the same order of magnitude to store intermediate contraction results.
+\purple{Perhaps just say time and space complexity?
+Order of magnitude doesn't make sense to me in terms of scaling.
+Also, what is the time complexity of finding a good contraction order?
+Is there a known average-case complexity?
+This seems important.}
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
@@
 One can easily check the maximum tensor during computing is rank 2, and the total number of multiplication operations is reduced significantly.
+\purple{I have not checked this yet but will tomorrow.
+Is it really easy/simple enough to do without writing stuff down?
+Is this the simplest example possible?
+The equations look quite formidable at first glance, and it takes a lot of time to match the hyperedge labels in the equation to the physical graph.}
 \end{example}
@@
 One can feed the standard computer numbers types into this tensor network and evaluate the independence polynomial by contracting it numerically.
+\purple{By feed in standard computer number types into the network, do you mean for $x$?
+Then, you look at multiple $x$, you can fit the independence polynomial to solve for the coefficients?
+It's not very explicit this procedure works at this point.}
 However, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
+\purple{Does the previous technique (contracting the tensor network numerically) give the coefficients of the polynomial?
+The use of the word ``however'' here is confusing to me because it feels like you're saying that the previous technique doesn't give the coefficients, or it's very hard to obtain the coefficients.}
 To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
-$\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+$\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic} \purple{I'd say that you're about to describe this semiring, otherwise it seems like you're going to use the general definition of the semiring rather than a specific type of semiring}.
 Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
@@
 \end{equation}
-Here, the multiplication operation can be evaluated efficiently using the convolution theorem~\cite{Schonhage1971}.
+Here, the multiplication operation can be evaluated efficiently using the convolution theorem~\cite{Schonhage1971}. \purple{What is the time complexity of evaluating the multiplication operation?}
 These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
@@
 By contracting the tensor network with the polynomial type, we have the exact representation of the independence polynomial.
-In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
+In practice, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 In \App{sec:finitefield}, we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
 Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex number at the cost of precision.
+\purple{It's not clear to me what we gain by using the polynomial semiring rather than floating points/integers here.
+Could you comment on how the compiler can optimize on this data type?}
 
@@
 \end{equation}
-where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
+\purple{On the first instance of ``plugging in'' infinity, it might be worth explicitly writing the limit, e.g.
+$I(G, \infty) =\lim_{x\rightarrow \infty}\sum_{k=0}^{\alpha(G)}a_k x^k = a_{\alpha(G)} \infty^{\alpha(G)}$}
+where the lower-order terms vanish.
+We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
+\purple{I was initially confused because I thought $\mymathbb{0} = (0, ?)$ where ``?'' could be anything positive since it's multiplied by zero.
+It confused me that $?$ could equal $-\infty$ since I thought you defined your ring for $k$ positive, since a polynomial has positive exponents.
+If you have negative exponents I thought it is a Laurent polynomial or something.
+After re-reading I see why this doesn't matter, though.}
 From this, we can define a new algebra as
@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
-Similarly, one can also truncate the polynomial and keep only its smallest several orders, which can be used for e.g. counting the minimum maximal independent sets.
+Similarly, one can also truncate the polynomial and keep only its smallest several orders, which can be used for e.g.
+counting the minimum maximal independent sets.\purple{Should define maximal independent sets, and minimum maximal independent sets (I would just say explicitly the smallest cardinality of a maximal independent set, which is...}
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
+\purple{This section makes a lot of sense and I think this paper is really cool!
+The flow between sections so far has been very smooth.}
 
@@
 The contraction of the corresponding tensor network yields an enumeration of all MIS configurations.
-Direct implementing this algebra for configuration MISs might incur significant space overheads for keeping too many intermediate states not contributing to the final maximum independent sets,
+Directly implementing this algebra for configuration MISs might incur significant space overheads for keeping too many intermediate states not contributing to the final maximum independent sets,
 one can avoid this issue by using the bounding technique in \App{sec:bounding}.
@@
 \end{equation}
+\purple{It might be nice to have a picture of an example tree if you have time. However, it is pretty clear from the definition, it would just help to visualize. Do you ever use the zero element?}
 The vertex tensor and edge tensor become
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
+\purple{To clarify - is the sum-product tree now the coefficients on the polynomial?
+I am a little confused on how we would, for instance, use this to compute the MISs.}
 To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
+\purple{How do we compute the size of each branch?}
 

### 2022-03-15 paper/paper_maddie_edits.tex
added remaining comments and questions

@@
 In practice, slicing technique is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth.
+\purple{What is the slicing technique?
+Can you add a refernce if it's from another paper?}
+One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth \purple{with the number of vertices, and therefore the treewidth}.
+\purple{Does this say anything about how optimized the contraction order is?
+If so, it might be worth explicitly saying.
+Some of the quantities in panel d look like they might be superexponential in the number of vertices (tree-width).}
 Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
@@
 are much faster comparing to non-BLAS element types in the same category.
+\purple{It might be worth explicitly saying the data types the first time they're mentioned (for example, I don't know what \texttt{T} is.
+Also, it might be worth adding a couple descriptor words on bounding.}
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN}, \texttt{SN}, \texttt{T100} and \texttt{SPT}.
+Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN}, \texttt{SN}, \texttt{T100} and \texttt{SPT} \purple{What are these things listed?}.
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+but it may suffer from round-off errors \purple{Can the round-off error thing be seen from Figure c?}.
+The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
 In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
@@
 A useful number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs.
-For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
+\purple{Why is it useful and what does it tell us about the physical system?} For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
 This quantity arises in statistical mechanics of hard-square lattice gases~\cite{Baxter1980, Pearce1988} and is used to understand phase transitions for these systems.
@@
 Intuitively, if the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection; it implies that large independent sets are clustered together.
-This clustering property has been used to prove the limitations of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
+This clustering property has been used to prove rigorous bounds on the performance of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
 Here, we use the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property for some given graphs.
@@
 
-    \caption{The the tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
-    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.}
+    \caption{The tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
+    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.
+\purple{It's not clear what some words mean on this diagram, such as ``highest order'' and ``extended tropical''.}}
      \label{fig:venn-diagram}

### 2022-03-15 paper/paper.tex
added experimental configuration graph figure and description

@@
 
-\subsection{The overlap gap property}
+\subsection{The overlap gap property\label{sec:overlap-gap}}
 With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs and the geometry of the solution space.
@@
 \end{figure}
+
+\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{paper/figures/exp_configurations.pdf}
+    \caption{A visualization of experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem.
+Each vertex represents an independent set, with edges between independent sets with pairwise Hamming distance $\leq 2.$}
+    \label{fig:exp_configuratoins}
+\end{figure}
+The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving the Maximum Independent Set problem.
+This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
+As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{ebadi2022quantum}.
+The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets with a small pairwise Hamming distance $\leq 2.$ The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$ The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}, but samples from local minima with a wide range of Hamming distances from the MISs.
+Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this particular King's graph.
 

### 2022-03-16 paper/paper.tex
update

--- 2022-03-15 paper/paper.tex
@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be quantified over a local set.
+We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be decribed by local constraints.
 Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be quantified over a vertex and its neighborhood,
+In graph theory and combinatorial optimization, there is an important class of problems that can be local constraints over a vertex and its neighborhood,
 including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
 the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
-There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
-wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
-\blue{need more diversed applications not limited to IS}
+%There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
+%wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+%\blue{need more diversed applications not limited to IS}
+Many decision and counting properties of these problems are in general intractable at large sizes (exponential runetime in problem size in the worst case),
+but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
 
@@
 while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
-In this paper, we focus on the less studied \textit{property} computation which can be harder but is crutial towards understanding a hard problem.
-Here, the \textit{property} refers to a class of quantities that not only include the maximum/minimum set size,
+In this paper, we focus on the less studied \textit{solution space property} computation which can be harder, e.g.
+counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crutial towards understanding a hard problem.
+Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
 but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.

### 2022-03-16 paper/paper.tex
update 3 regular graphs

@@
 \begin{figure} 
+    \begin{subfigure}[t]{\textwidth}
         \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    \caption{The distribution of pairwise Hamming distances between every two independent sets of size $\geq\alpha(G)-1$ for two random three regular graph instances of size $100$.}
+        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
+        \caption{King's graphs of size $20\times 20$, $0.8$ filling.}
+    \end{subfigure}
+    \begin{subfigure}[t]{\textwidth}
+        \centering
+        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
+        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
+        \caption{Random three regular graphs of size $110$.}
+    \end{subfigure}
+    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.}
     \label{fig:hamming}
@@
     \centering
-    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{paper/figures/exp_configurations.pdf}
+    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
     \caption{A visualization of experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem.

### 2022-03-16 paper/paper.tex
merge maddie comments

@@
 \cyan{a comment} and \xcyan{a resolved comment}
-\blue{I am not sure I an use the word ``quantify'' in a tensor network!
-It is borrowed from the field of logic,
-but I am feeling defining a local tensor in our paper is same as quantifing over a variable in logic.
-\href{https://en.wikipedia.org/wiki/Quantifier\_(logic)}{https://en.wikipedia.org/wiki/Quantifier\_(logic)}}
 
@@
 while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
+\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
 In this paper, we focus on the less studied \textit{solution space property} computation which can be harder, e.g.
-counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crutial towards understanding a hard problem.
+counting independent sets of a general graph is in \#P-complete~\cite{Vadhan2001}, but is crutial towards understanding a hard problem.
 Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 %are many interesting and hard computational problems concerning various properties of independent sets.
+\purple{I would give examples of why we want to compute solution space
+properties.
+For instance, in statistical physics, computing thermal states and
+observables via the partition function. In complexity theory, proving limits on local
+algorithms (OGP).}
 
@@
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is also known as the sum product network or einsum in different fields,
-where its tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
+Tensor network is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy.
+It is composed of a set of tensors and a set of labels for specifying the contraction of tensors,
+where the tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
 Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}.
+\purple{I’d write out $2^{{\rm tw}(G)}$}
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
+\purple{Is the scaling of these algorithms known?}
 When using tensor network for solving one of the best sets with the maximum size,
 this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013},
-however, tensor network has richer algebraic structure, and this structure is crutial for property computation.
+however, tensor network has richer algebraic structure, and this structure is crutial for solution space property computation.
+\purple{Not clear how first part and second part of sentence are related}
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 
-To avoid the discussion being unnecessaryly diversed, we mainly focus on the independent set problem,
-and discuss other combinatorial optimization problems in \App{sec:otherproblems}.
+To avoid the discussion being unnecessarily diversed, we mainly focus on the independent set problem,
+and discuss other combinatorial optimization problems\purple{More details on which combinatorial optimization problems this
+applies to?} in \App{sec:otherproblems}.
 The paper is organized as follows.
@@
 One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice.
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice\purple{signifying which pairs of indices are summed over}.
 Hence a tensor network can be represented as a simple graph,
@@
 However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
+\purple{I feel that the $\delta$ tensors point is unnecessary to mention in the main text. Because not much detail is given, I internalized what it meant only on the third read-through.}
 
@@
 \section{Generic programming tensor contractions}\label{sec:generic}
+\purple{On a second read of this
+section, I think that the clarity could be improved. My understanding is this is the flow:
+We would like to use generic programming, where we write code that works regardless
+of input type, and is optimized on all input types without sacrificing efficiency. In
+general, we can write code such that a function runs correctly regardless of the input
+data type. This is easy to do for dynamically typed languages like Python, which only
+verify and enforce the rules for the input data type at runtime (called type-checking).
+However, when the input data type is only checked at runtime (as opposed to when the
+code is compiled), type-specific optimization cannot be used. High efficiency is only
+achieved in statically typed languages, where modern compiling technology allows the
+function to be individually optimized for each input data type (then give C++/Julia
+examples).}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
@@
 
+\purple{I think the following paragraph could be clarified. When you read the definition
+of generic programming, it’s not clear what “in the most general setting” means. My
+understanding is it just means that the program will work regardless of the input data
+type - it would be good to say this explicitly. I also think the way it is written takes a while
+to understand what dynamically versus statically typed languages are. The definition,
+“When these languages “see” a new input type, the compiler can recompile the generic
+program for the new type.” comes rather late in the paragraph. Also, while I know what
+you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
+lost on someone only with a physics background.}
 This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
@@
 
-This motivates us to think about what is the most general element type allowed in a tensor network contraction program.
+This motivates us to think about what is the most general tensor element type allowed in a tensor network contraction program.
 We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
@@
             \hline
-   \textbf{Element type}     & \textbf{Property to compute} \\
+   \textbf{Element type}     & \textbf{Solution space property} \\
    {$\mathbbm{R}$}     & {Counting of all independent sets} \\
@@
    {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their counting} \\
+   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their numbers\purple{``and their counting'' is gramat-
+ically confusing, can we say independence
+polynomial or degeneracy or something?}} \\
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
@@
 For people with physics background, we suggest using an alternative approach described in \App{sec:energymodel} to understand this reduction from an energy model.
-Let $G=(V,E)$ be a weighted undirected graph with each vertex $i\in V$ being associated with a weight $w_i$.
+Let $G=(V,E)$ be a weighted undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
@@
 It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
+\purple{Perhaps explicitly say what this scales as?}
 The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
 A fully optimized contraction order can reduce the time to $O(2^{\text{tw}(G)})$~\cite{Markov2008}, while requiring a space at the same order of magnitude to store intermediate contraction results.
+\purple{Perhaps just say time and space
+complexity? Order of magnitude doesn’t make sense to me in terms of scaling. Also,
+what is the time complexity of finding a good contraction order? Is there a known
+average-case complexity? This seems important.}
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
@@
 
+\purple{I have not checked this yet but will
+tomorrow. Is it really easy/simple enough to do without writing stuff down? Is this the simplest
+example possible? The equations look quite formidable at first glance, and it takes a lot of time
+to match the hyperedge labels in the equation to the physical graph.}
+
 \section{Independence polynomial}\label{sec:indpoly}
@@
 One can feed the standard computer numbers types into this tensor network and evaluate the independence polynomial by contracting it numerically.
+\purple{By feed in standard computer number types into the network, do you mean for
+x? Then, you look at multiple x, you can fit the independence polynomial to solve for
+the coefficients? It's not very explicit this procedure works at this point.}
 However, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
+\purple{Does the previous technique
+(contracting the tensor network numerically) give the coefficients of the polynomial?
+The use of the word “however” here is confusing to me because it feels like you’re
+saying that the previous technique doesn’t give the coefficients, or it’s very hard to
+obtain the coefficients.}
 To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+\purple{I'd
+say that you're about to describe this semiring, otherwise it seems like you’re going to
+use the general definition of the semiring rather than a specific type of semiring}
 Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
@@
 \end{equation}
-Here, the multiplication operation can be evaluated efficiently using the convolution theorem~\cite{Schonhage1971}.
+Here, the multiplication operation can be evaluated in time $O(k\log(k))$, where $k=\max{k_a, k_b}$, using the convolution theorem~\cite{Schonhage1971}.
 These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
@@
 Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex number at the cost of precision.
+\purple{It's not clear to me what we gain by using the
+polynomial semiring rather than floating points/integers here. Could you comment on
+how the compiler can optimize on this data type?}
 
@@
 \begin{equation}
-I(G, \infty) = a_{\alpha(G)} \infty^{\alpha(G)},
+I(G, \infty) = \lim_{x\rightarrow \infty}\sum_{k=0}^{\alpha(G)}a_k x^k = a_{\alpha(G)} \infty^{\alpha(G)},
 \end{equation}
 where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
+\purple{I was initially confused
+because I thought 0 = (0, ?) where “?” could be anything positive since it's multiplied
+by zero. It confused me that ? could equal $-\infty$ since I thought you defined your ring for
+k positive, since a polynomial has positive exponents. If you have negative exponents I
+thought it is a Laurent polynomial or something. After re-reading I see why this doesn't
+matter, though.}
 From this, we can define a new algebra as
@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
-Similarly, one can also truncate the polynomial and keep only its smallest several orders, which can be used for e.g. counting the minimum maximal independent sets.
+Similarly, one can also truncate the polynomial and keep only its smallest several orders,
+which can be used for e.g. counting the maximal independent sets with smallest cardinality,
+where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence contraint.
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
@@
 \end{equation}
+\purple{It might be nice to have a picture of an example tree if you have time. However,
+it is pretty clear from the definition, it would just help to visualize. Do you ever use the
+zero element?}
 The vertex tensor and edge tensor become
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
+\purple{To clarify - is the sum-product tree now the coefficients
+on the polynomial? I am a little confused on how we would, for instance, use this to
+compute the MISs}
 To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
+\purple{How do we compute the size of each
+branch?}
 
@@
     The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
-    Legends are properties, algebra and devices that we used in the computation; one can find the corresponding computed property in \Tbl{tbl:generictypes}.
+    Legends are properties, algebra and devices that we used in the computation; one can find the corresponding computed solution space property in \Tbl{tbl:generictypes}.
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
@@
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
-In practice, slicing technique is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth.
+In practice, slicing technique~\cite{Kalachev2021} is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
+One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth\purple{with the number
+of vertices, and therefore the treewidth}.
+\purple{Does this say anything about how
+optimized the contraction order is? If so, it might be worth explicitly saying. Some of
+the quantities in panel d look like they might be superexponential in the number of
+vertices (tree-width).}
 Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
@@
 are much faster comparing to non-BLAS element types in the same category.
+\purple{It might be worth explicitly saying
+the data types the first time they're mentioned (for example, I don't know what T is.
+Also, it might be worth adding a couple descriptor words on bounding.}
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ \texttt{PN}, \texttt{SN}, \texttt{T100} and \texttt{SPT}.
+Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ types with algebra defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr}.
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors. The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+but it may suffer from round-off errors\purple{Can the round-off error thing be seen from Figure c?}.
+The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
 In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
@@
 A useful number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs.
+\purple{Why is it useful and
+what does it tell us about the physical system?}
 For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
@@
         \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
-        \caption{King's graphs of size $20\times 20$, $0.8$ filling.}
+        \caption{$9$ King's graphs of size $20\times 20$, $0.8$ filling.}
     \end{subfigure}
@@
         \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-        \caption{Random three regular graphs of size $110$.}
+        \caption{$9$ Random three regular graphs of size $110$.}
     \end{subfigure}
-    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.}
+    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.
+    In each plot, the $x$-axis is the hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
+    }
     \label{fig:hamming}
@@
 the enumeration of independent sets of a given size.
-For each property, we design an algebra being a commutative semiring and let it be the tensor element type.
+For each solution space property, we design an algebra being a commutative semiring and let it be the tensor element type.
 With different algebras, the contraction of the same tensor network gives us the different properties.
@@
     The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.}
+    \purple{It's not clear what
+some words mean on this diagram, such as ``highest order'' and ``extended tropical''}
      \label{fig:venn-diagram}

### 2022-03-17 paper/paper.tex
update

@@
 
-The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size ,
+The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size,
 while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
 \purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
+\blue{Here, we haven't mentioned the independent set, here ``version'' means, e.g.
+counting, enumeration, devision.
+I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
 In this paper, we focus on the less studied \textit{solution space property} computation which can be harder, e.g.
@@
 %are many interesting and hard computational problems concerning various properties of independent sets.
+Solution space property computation allows us to understand the solution space better.
+With the counting of sets at different sizes, one can related the computational hardness with the counting of sets at different sizes~\cite{Xu2018}.
+With the configuration enumeration/sampling at a given size, one can measure the overlap gap property better,
+while the configuration space connectivity also privides us an intuition about designing a better classical or quantum algortihms.
 \purple{I would give examples of why we want to compute solution space
@@
 observables via the partition function. In complexity theory, proving limits on local
-algorithms (OGP).}
+algorithms (OGP).}\blue{now?}
 
@@
 Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}.
-\purple{I’d write out $2^{{\rm tw}(G)}$}
+\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
 Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
-\purple{Is the scaling of these algorithms known?}
+\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
 When using tensor network for solving one of the best sets with the maximum size,
-this time complexity is just on par with the dynamic programming algorithms~\cite{Courcelle1990, Fomin2013},
-however, tensor network has richer algebraic structure, and this structure is crutial for solution space property computation.
-\purple{Not clear how first part and second part of sentence are related}
+this time complexity is the same as the dynamic programming algorithm~\cite{Courcelle1990, Fomin2013}.
+These two algorithms are related but are not equivalent.
+Dynamic programming is more general purposed, while a tensor network has a richer algebraic structure, and this structure is crutial for solution space property computation.
+\purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.

### 2022-03-17 paper/paper.tex
update

@@
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
-Other hard graph problems solvable in our framework includes the cutting problem, the K-coloring problem, the maximal clique problem, the dominating set problem, and satisfiability problem, among others.
+Other hard graph problems solvable in our framework includes the cutting problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and satisfiability problem, among others.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
@@
 In graph theory and combinatorial optimization, there is an important class of problems that can be local constraints over a vertex and its neighborhood,
-including the independent set problem, the cutting problem, the K-coloring problem, the satisfiability problem,
+including the independent set problem, the cutting problem, the vertex coloring problem, the satisfiability problem,
 the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
@@
 To avoid the discussion being unnecessarily diversed, we mainly focus on the independent set problem,
-and discuss other combinatorial optimization problems\purple{More details on which combinatorial optimization problems this
-applies to?} in \App{sec:otherproblems}.
+and discuss other combinatorial optimization problems,
+including the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem and the maximal clique problem, in \App{sec:otherproblems}.
+\xpurple{More details on which combinatorial optimization problems this
+applies to?}
 The paper is organized as follows.
@@
 One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice\purple{signifying which pairs of indices are summed over}.
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor\xpurple{signifying which pairs of indices are summed over}.
 Hence a tensor network can be represented as a simple graph,
@@
 The graphical representation of a generalized tensor network is a hypergraph, in which an edge (a label in subscript) can be shared by an arbitrary number of vertices (tensors).
-These two notations are equivalent in representation power because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
-\purple{I feel that the $\delta$ tensors point is unnecessary to mention in the main text. Because not much detail is given, I internalized what it meant only on the third read-through.}
+These two notations are equivalent in representation power,
+while the generalized tensor network might produce smaller contraction complexity,
+which will be illustrated in \App{sec:tensorbad}.
+% because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
+%However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
+\xpurple{I feel that the $\delta$ tensors point is unnecessary to mention in the main text. Because not much detail is given, I internalized what it meant only on the third read-through.}
 

### 2022-03-17 paper/paper.tex
update

@@
    {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their numbers\purple{``and their counting'' is gramat-
-ically confusing, can we say independence
-polynomial or degeneracy or something?}} \\
+   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their numbers
+   \purple{``and their counting'' is gramatically confusing, can we say independence polynomial or degeneracy or something?}\blue{Since you mentioned degeneracy is bad, what about ``numbers''?}} \\
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
@@
 
-It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
-\purple{Perhaps explicitly say what this scales as?}
+It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products, which scales exponentially as the number of vertices.
+\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
 The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
-A fully optimized contraction order can reduce the time to $O(2^{\text{tw}(G)})$~\cite{Markov2008}, while requiring a space at the same order of magnitude to store intermediate contraction results.
+A fully optimized contraction order can reduce the time complexity significantly, while requiring a minimum space complexity $O(2^{\text{tw}(G)})$~\cite{Markov2008} to store intermediate contraction results.
 \purple{Perhaps just say time and space
-complexity? Order of magnitude doesn’t make sense to me in terms of scaling. Also,
+complexity? Order of magnitude doesn't make sense to me in terms of scaling. Also,
 what is the time complexity of finding a good contraction order? Is there a known
-average-case complexity? This seems important.}
+average-case complexity? This seems important.}\blue{see added texts below.}
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
+In practise, it is difficult to find an optimal contraction order for large tensor networks because finding the tree width itself is NP-hard.
+However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021}.
+For large scale applications,
+it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.
+enumerating certain degrees of freedom in an external loop so that the space complexity of contracting a smaller tensor network inside the loop can be smaller.
 

### 2022-03-17 paper/paper.tex
update

@@
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the space required to contract a tensor network is 2 power the tree width of its line graph~\cite{Markov2008}.
+Given a good contraction order, the space required to contract a tensor network is 2 power the treewidth of its line graph~\cite{Markov2008}.
 \purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
@@
 \purple{I think the following paragraph could be clarified. When you read the definition
-of generic programming, it’s not clear what “in the most general setting” means. My
+of generic programming, it's not clear what ``in the most general setting'' means. My
 understanding is it just means that the program will work regardless of the input data
@@
 you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
-lost on someone only with a physics background.}
+lost on someone only with a physics background.}\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
 This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
@@
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
-In practise, it is difficult to find an optimal contraction order for large tensor networks because finding the tree width itself is NP-hard.
+In practise, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
 However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021}.
@@
 example possible? The equations look quite formidable at first glance, and it takes a lot of time
-to match the hyperedge labels in the equation to the physical graph.}
+to match the hyperedge labels in the equation to the physical graph.}\blue{sometimes I am afraid the example is too trivial to be useful.
+The simplest example to show contraction order matters can be a 3-vertex one.}
 
@@
 and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-One can feed the standard computer numbers types into this tensor network and evaluate the independence polynomial by contracting it numerically.
+By assigning a standard computer number to $x$, one can evaluate this independence polynomial for this specific value by contracting this tensor network directly.
 \purple{By feed in standard computer number types into the network, do you mean for
 x? Then, you look at multiple x, you can fit the independence polynomial to solve for
-the coefficients? It's not very explicit this procedure works at this point.}
-However, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
+the coefficients? It's not very explicit this procedure works at this point.}\blue{how about now?}
+However, instead of evaluating this polynomial for a certain value, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
 \purple{Does the previous technique
 (contracting the tensor network numerically) give the coefficients of the polynomial?
-The use of the word “however” here is confusing to me because it feels like you’re
-saying that the previous technique doesn’t give the coefficients, or it’s very hard to
-obtain the coefficients.}
+The use of the word “however” here is confusing to me because it feels like you're
+saying that the previous technique doesn't give the coefficients, or it's very hard to
+obtain the coefficients.}\blue{Yep, we haven't found the coefficients. I tried to modify words a bit, does it look better now?}
 To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
@@
 \purple{I'd
-say that you're about to describe this semiring, otherwise it seems like you’re going to
-use the general definition of the semiring rather than a specific type of semiring}
+say that you're about to describe this semiring, otherwise it seems like you're going to
+use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}
 Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
@@
 In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-In \App{sec:finitefield}, we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex number at the cost of precision.
+One may argue that one can first evaluate this polynomial at different $x$ being a standard number type,
+and then apply the gaussian elimination to fit the coefficients of this polynomial.
+This seemingly more time and space efficient approach suffers from severe issues in practise.
+The data ranges of standard integer types are too small to cover many practical using cases,
+while the floating point numbers may have round off error that much larger than the value itself, because the number of sets at different sizes may vary tens or even hundreds of orders and this makes the small coefficients can not be retrieved correctly by fitting.
+For the purpose of evaluating these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
+Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex numbers with controllable round off errors.
+For the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
 \purple{It's not clear to me what we gain by using the
 polynomial semiring rather than floating points/integers here. Could you comment on
-how the compiler can optimize on this data type?}
+how the compiler can optimize on this data type?}\blue{I added some discussion here to address why we stick to polynomial number types,
+for short, it is a dynamic type that can be slow, so we do not use it a lot in practise.
+I mention it here because it is the base of the following discussion.}
 
@@
 thought it is a Laurent polynomial or something. After re-reading I see why this doesn't
-matter, though.}
+matter, though.}\blue{I let $\mymathbb{0} = (1, -\infty)$ now, it is still correct, is it easier for understanding or I change it back?}
 From this, we can define a new algebra as
@@
     a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-    \mymathbb{0} &= 0\infty^{-\infty}\\
+    \mymathbb{0} &= 1\infty^{-\infty}\\
     \mymathbb{1} &= 1\infty^{0}.
@@
 it is pretty clear from the definition, it would just help to visualize. Do you ever use the
-zero element?}
+zero element?}\blue{now we have an example, but it does not include a zero element, do you think I should use a more concrete one instead of an abstract one?}
 The vertex tensor and edge tensor become
@@
 This is because once we have this sum-product representation of the configuration space,
+either generate by using this algebra directly or serve as the coefficients of (truncated) polynomials,
 one can compute the number of configurations in each branch rigorously and efficiently.
@@
 on the polynomial? I am a little confused on how we would, for instance, use this to
-compute the MISs}
+compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
 To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
-\purple{How do we compute the size of each
+\xpurple{How do we compute the size of each
 branch?}
+\begin{example}
+Let us consider the following sum product tree 
+\begin{equation*}
+    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
+\end{equation*}
+where siblings $A, B, C$ and $D$ can be any four types of nodes.
+It can be represented diagramatically as the following.
+
+\centerline{\begin{tikzpicture}[]
+    \def\dx{0};
+    \def\a{1.0};
+    \def\b{0.5};
+    \def\ya{-1.0};
+    \def\yb{-0.8};
+    \node[] at (\dx, 0) (P1) {$\oplus$};
+    \node[] at (\dx+\a, \ya) (P2) {$\oplus$};
+    \node[] at (\dx-\a, \ya) (M1) {$\odot$};
+    \node[] at (\dx-\a-\b, \ya+\yb) (A) {$A$};
+    \node[] at (\dx-\a+\b, \ya+\yb) (B) {$B$};
+    \node[] at (\dx+\a+\b, \ya+\yb) (C) {$C$};
+    \node[] at (\dx+\a-\b, \ya+\yb) (D) {$D$};
+    \draw[] (P1) -- (M1);
+    \draw[] (P1) -- (P2);
+    \draw[] (P2) -- (C);
+    \draw[] (P2) -- (D);
+    \draw[] (M1) -- (A);
+    \draw[] (M1) -- (B);
+\end{tikzpicture}}
+
+The left and right sibling of root node has size $|A|\times |B|$ and $|C|+|D|$ respectively,
+and since the root node has type \texttt{SUM}, its size can be computed as $|A|\times |B| + |C|+|D|$.
+One can compute the sizes of $A, B, C$ and $D$ recursively until the program meets either a the \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$ respectively.
+\end{example}
 
@@
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors\purple{Can the round-off error thing be seen from Figure c?}.
+but it may suffer from round-off errors (\App{sec:fft})\purple{Can the round-off error thing be seen from Figure c?}\blue{it is hard, so I added a ref to the appendix, is it more informative?}.
 The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
@@
 
-A useful number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs.
+A theoretically interesting number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs, which can tell us thermal dynamic properties of these lattices at the high temperature limit.
 \purple{Why is it useful and
-what does it tell us about the physical system?}
+what does it tell us about the physical system?}\blue{It is probably useless, so: useful -> theoretically interesting}
 For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
@@
     \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Highest order};
-    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}2nd highest order};
+    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Largest order};
+    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}2nd largest order};
     \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
@@
 some words mean on this diagram, such as ``highest order'' and ``extended tropical''}
+\blue{the extended tropical is defined in \Sec{sec:weighted}, should I emphasis it more? also, ``highest''->``largest''}
      \label{fig:venn-diagram}

### 2022-03-17 paper/paper.tex
update examples and benchmark

@@
 
-Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes, where the space complexity is the same as the treewidth of the problem graph.
+Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes,
+where the space complexity is the same as the treewidth of the problem graph.
+Here, we assume our contraction order finding program has been converged to the optimal treewidth.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
 In practice, slicing technique~\cite{Kalachev2021} is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth\purple{with the number
-of vertices, and therefore the treewidth}.
-\purple{Does this say anything about how
+One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth,
+while in panel (d), the timing of certain computing tasks also strongly correlates with other factors like the configuration space size.
+\purple{with the number of vertices, and therefore the treewidth}\blue{not sure it is safe to say this, because they do not always have a nice linear relation}.
+\xpurple{Does this say anything about how
 optimized the contraction order is? If so, it might be worth explicitly saying. Some of
@@
 vertices (tree-width).}
-Among these benchmarks, computational tasks with data types \texttt{T (CPU)},
-\texttt{$\mathbbm{R}$ (CPU)}, \texttt{$\mathbbm{R}$ (GPU)}, \texttt{$\mathbbm{C}$ (CPU)}, \texttt{$\mathbbm{C}$ (GPU)} and \texttt{T+bounding (CPU)} can utilize fast BLAS functions to evaluate tensor contractions, hence
+Among these benchmarks, computational tasks with data types tropical number of on CPU and real and complex numbers on both CPU and GPU can utilize fast BLAS functions to evaluate tensor contractions, hence
 are much faster comparing to non-BLAS element types in the same category.
-\purple{It might be worth explicitly saying
+\xpurple{It might be worth explicitly saying
 the data types the first time they're mentioned (for example, I don't know what T is.
@@
 \subsection{The overlap gap property\label{sec:overlap-gap}}
-With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs and the geometry of the solution space.
+With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space,
+such as the optimization landscape for finding the MISs and the geometry of the solution space.
 One of the known barriers for finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-Intuitively, if the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection; it implies that large independent sets are clustered together.
+Intuitively, if the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection;
+it implies that large independent sets are clustered together.
 This clustering property has been used to prove the limitations of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
-Here, we use the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property for some given graphs.
-In particular, in \Fig{fig:hamming}, we enumerated all ISs of size $\geq\alpha(G)-1$ for two random three regular graph instances of size 100 and show the pairwise Hamming distance statistics for the enumerated configurations.
-In \Fig{fig:hamming}(a), we observed the multiple peak structure for the pairwise Hamming distance for one of the graphs.
+It was shown that for finding MISs of $d$ regular graphs with $d$ and graph sizes both being large, there exists overlap gap property~\cite{Rahman2017,Gamarnik2021}.
+However, it is not yet clear whether for small $d$, e.g. three regular graphs, this statement is still true.
+Here, we direct sample from the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property for some given graphs.
+We do no explore the full configurations space because the number of configurations is too large to fit into a storage,
+so we have to use the sum product tree representation to store it in a compact format and draw samples from it.
+We compare two categories of graphs, one is the King's graph at $0.8$ filling, a type of unit disk graph having no overlap gap property, \blue{@Maddie, do you have a good reference to justify this statement about unit disk graph OGP?}
+another is the vertex $3$-regular graph that we want to investigate.
+Each category contains $9$ randomly generated instances, due to the limitation of computing resources,
+the size of King's graph is $20\times 20$ ($320$ vertices) and the size of $3$-regular graphs are $110$.
+In particular, in \Fig{fig:hamming}, 
+we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \text{ratio} \times \lfloor\alpha(G)\rfloor$ for each instance
+ and show the pairwise Hamming distance distribution for the enumerated configurations.
+In \Fig{fig:hamming}(a), we observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs.
+While in \Fig{fig:hamming}(b), we observed the multiple peak structure as the ratio becomes small for the $3$-regular graphs.
 This indicates the presence of the overlap gap property and disconnected clusters exist in the configuration space for large independent sets.
@@
 This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
-As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{ebadi2022quantum}.
-The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets with a small pairwise Hamming distance $\leq 2.$ The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$ The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}, but samples from local minima with a wide range of Hamming distances from the MISs.
+As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
+The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets with a small pairwise Hamming distance $\leq 2.$
+The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
+The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010},
+but samples from local minima with a wide range of Hamming distances from the MISs.
 Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this particular King's graph.

### 2022-03-17 paper/paper.tex
update generic programming

@@
 function to be individually optimized for each input data type (then give C++/Julia
-examples).}
+examples).}\blue{how about now?}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
 the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
-Owning to the development of modern compiling technology, we no longer need to re our imagination to standard number types.
-One of the key concepts that push the technology forward is called generic programming:
+%Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
+The truth is, the elements in a tensor does not have to be a regular number type,
+ or even a field (since division is not used in tensor contraction).
+One can use the same tensor contraction program for different purposes with different tensor element types,
+and this idea of using the same program for different purposes is also called the generic programming in computer science:
 
@@
 understanding is it just means that the program will work regardless of the input data
-type - it would be good to say this explicitly. I also think the way it is written takes a while
+type - it would be good to say this explicitly. }
+\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
+\purple{I also think the way it is written takes a while
 to understand what dynamically versus statically typed languages are. The definition,
 “When these languages “see” a new input type, the compiler can recompile the generic
-program for the new type.” comes rather late in the paragraph. Also, while I know what
-you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
-lost on someone only with a physics background.}\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
+program for the new type.” comes rather late in the paragraph.}
+\xpurple{Also, while I know what you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
+lost on someone only with a physics background.}
 This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
@@
 When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.
-A myriad of optimizations can be done during the compilation, such as inlining immutable elements with fixed sizes in an array to decrease the cache miss rate when accessing data.
-In Julia, these inlined arrays can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
+A myriad of optimizations can be done during the compilation, such as optimize the memory layout of immutable elements with fixed sizes in an array to speed up the array indexing.
+In Julia, arrays with immutable elements with fixed sizes can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
 

### 2022-03-17 paper/paper.tex
update

@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor network to compute various properties of a class of hard graph problems that can be decribed by local constraints.
+We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
 Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
-Other hard graph problems solvable in our framework includes the cutting problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and satisfiability problem, among others.
+Other hard graph problems solvable in our framework includes the cutting problem, the vertex coloring problem, the maximal clique problem, the dominating set problem and the satisfiability problem, among others.
 To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps people understand these hard problems better.
+We show how our method helps to understand these hard problems better.
 \end{abstract}
@@
 including the independent set problem, the cutting problem, the vertex coloring problem, the satisfiability problem,
-the maximal clique problem, and the vertex cover problem et al ~\cite{Moore2011}.
+the maximal clique problem, and the vertex cover problem~\cite{Moore2011}.
 %There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
@@
 The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to solve them in a polynomial time.
+while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to be solved in a polynomial time.
 \purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
@@
 In this paper, we focus on the less studied \textit{solution space property} computation which can be harder, e.g.
-counting independent sets of a general graph is in \#P-complete~\cite{Vadhan2001}, but is crutial towards understanding a hard problem.
+counting independent sets of a general graph is in \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
 Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 
-We propose to view the computation of all these properties from an abstract algebra perspective and use a unified framework,
-generic tensor-network, to solve these seeming unrelated properties all.
+We propose to view the computation of all these properties from an abstract algebra perspective and use the unified framework of
+generic tensor-network to solve these seemingly unrelated properties all.
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
@@
 These two algorithms are related but are not equivalent.
-Dynamic programming is more general purposed, while a tensor network has a richer algebraic structure, and this structure is crutial for solution space property computation.
+Dynamic programming is more general purposed, while a tensor network has a richer algebraic structure, and this structure is crucial for solution space property computation.
 \purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
@@
 We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
-Then we show how to reduce an independent set problem to a tensor network contraction problem \Sec{sec:tnmap}
-and show how to engineer the element types in \Sec{sec:counting},\Sec{sec:enumeration} and \Sec{sec:weighted} to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs.
+Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}
+and show how to engineer the element types in \Sec{sec:counting}, \Sec{sec:enumeration} and \Sec{sec:weighted} to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs.
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
@@
 \section{Tensor networks}\label{sec:tn}
-Tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
+A tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
 it can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
@@
 In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
-The second aspect is about performance. For dynamically typed languages such as Python,
+The second aspect is about performance. For dynamically typed languages, such as Python,
 one can easily write very general codes, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two numpy arrays with python objects as elements is much slower than statically typed languages such as C++ and Julia~\cite{Bezanson2012}.
@@
 This motivates us to think about what is the most general tensor element type allowed in a tensor network contraction program.
-We find that as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
+We find that, as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
 A commutative semiring is a ring with its multiplication operation being commutative and without an additive inverse.
@@
 \end{align*}
-We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we wish this contraction order does not change the contraction results.
+We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
@@
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
-   {Sum Product Tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
-   {Polynomial truncated to highest order combined with Bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
-   {Polynomial truncated to $k$-th order combined with Set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
+   {Expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
+   {Polynomial truncated to highest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
+   {Polynomial truncated to $k$-th order combined with set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
             \bottomrule
@@
 
-It is in general not computational efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products, which scales exponentially as the number of vertices.
+It is in general not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products, which scales exponentially as the number of vertices.
 \purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
@@
 \begin{example}\label{eg:tensorcontraction}
-In the following, we mapping a 5 vertex graph (left) to a tensor network (right) and show how the contraction order simplifies the computation.
+In the following, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order simplifies the computation.
 
@@
 \end{equation}
-where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type with two fields: the largest exponent $k$ and its coefficient $a_k$.
+where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
 \purple{I was initially confused
@@
 \begin{split}
-    \sigma \oplus \tau &= {\rm select}(\sigma, \tau), \\
+    \sigma \oplus \tau &= \texttt{select}(\sigma, \tau), \\
     \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
@@
 When the graph size goes large, the configurations might be impossible to fit into any type of storage.
-Then instead of using the set algebra, one can use a binary sum-product tree as a compact representation of the configurations.
+Then instead of using the set algebra, one can use a binary expression tree as a compact representation of the configurations.
 We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
@@
 \begin{equation}
-\eqname{SPT}
+\eqname{EXPR}
 \begin{split}
@@
 \begin{equation}
-    W^{\rm SPT}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
+    W^{\rm EXPR}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{\rm SPT} = \left(\begin{matrix}
+        B^{\rm EXPR} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 
-This algebra is a commutative semiring because we define the equivalence of two sum-product trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
+This algebra is a commutative semiring because we define the equivalence of two expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
 Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
 but he can directly sample configurations from this tree.
-This is because once we have this sum-product representation of the configuration space,
+This is because once we have this expression tree representation of the configuration space,
 either generate by using this algebra directly or serve as the coefficients of (truncated) polynomials,
 one can compute the number of configurations in each branch rigorously and efficiently.
-\purple{To clarify - is the sum-product tree now the coefficients
+\purple{To clarify - is the expression tree now the coefficients
 on the polynomial? I am a little confused on how we would, for instance, use this to
 compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
-To generate samples, one just descends this sum product tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
+To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
 \xpurple{How do we compute the size of each
@@
 \begin{example}
-Let us consider the following sum product tree 
+Let us consider the following expression tree 
 \begin{equation*}
@@
 The graphs that we use in benchmarks are random three regular graphs,
- a typical type of sparse graphs that has a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
-In this benchmark, we do not include traditional algorithms for finding the MIS size like the branching algorithms~\cite{Tarjan1977, Robson1986} and dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013},
+ a typical type of sparse graphs that have a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+In this benchmark, we do not include traditional algorithms for finding the MIS size such as the branching algorithms~\cite{Tarjan1977, Robson1986} or dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013},
 because to the best of our knowledge, most of the properties mentioned in this paper are not computable within these frameworks.
@@
     (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
-    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum product tree format,
+    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the expression tree format,
     with or without bounding the enumeration space.
@@
 We do no explore the full configurations space because the number of configurations is too large to fit into a storage,
-so we have to use the sum product tree representation to store it in a compact format and draw samples from it.
+so we have to use the expression tree representation to store it in a compact format and draw samples from it.
 We compare two categories of graphs, one is the King's graph at $0.8$ filling, a type of unit disk graph having no overlap gap property, \blue{@Maddie, do you have a good reference to justify this statement about unit disk graph OGP?}
@@
     \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
-    \caption{A visualization of experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem.
-Each vertex represents an independent set, with edges between independent sets with pairwise Hamming distance $\leq 2.$}
+    \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
+    Each vertex represents an independent set, with edges between independent sets with pairwise Hamming distance $\leq 2.$ \blue{can be connected by a swap operation?}}
     \label{fig:exp_configuratoins}
@@
 Other than the case with real numbers, we have polynomials and truncated polynomials.
-We combine them with the bit string algebra, the set algebra, and sum product tree algebra for finding, enumeration, and sampling of independent sets at a given size.
+We combine them with the bit string algebra, the set algebra, and expression tree algebra for finding, enumeration, and sampling of independent sets at a given size.
 These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
@@
 We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
-We acknowledge Sepehr Ebadi, Maddie Cain, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
+We acknowledge Sepehr Ebadi, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
+We thank Benjamin Schiffer for providing helpful advices about writing.
 We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!

### 2022-03-18 paper/paper.tex
Updates from Overleaf

@@
 
-The most studied version of the above problems is finding a maximum/minimum set satisfying the contraints and the corresponding set size,
-while many of them belong to the hardness category NP-hard~\cite{Hastad1996}, i.e. it is unlikely to be solved in a polynomial time.
-\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
-\blue{Here, we haven't mentioned the independent set, here ``version'' means, e.g.
+The most studied aspect of the above problems is finding an optimal solution, 
+%The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
+, which is typically 
+%while many of them belong to the hardness category
+NP-hard~\cite{Hastad1996}, i.e. it is unlikely to be solved in a polynomial time.
+%\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
+%\blue{Here, we haven't mentioned the independent set, here ``version'' means, e.g.
 counting, enumeration, devision.
 I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-In this paper, we focus on the less studied \textit{solution space property} computation which can be harder, e.g.
-counting independent sets of a general graph is in \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
+In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.
+counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
 Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the space required to contract a tensor network is 2 power the treewidth of its line graph~\cite{Markov2008}.
-\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
-Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time.
-\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
+Given a good contraction order, the space required to contract a tensor network is
+two to the power of the treewidth of its line graph~\cite{Markov2008}.
+%\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
+Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time using heuristic (inexact) methods.
+%\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
 When using tensor network for solving one of the best sets with the maximum size,
-this time complexity is the same as the dynamic programming algorithm~\cite{Courcelle1990, Fomin2013}.
-These two algorithms are related but are not equivalent.
-Dynamic programming is more general purposed, while a tensor network has a richer algebraic structure, and this structure is crucial for solution space property computation.
-\purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
+the time complexity is the same as the dynamic programming algorithm~\cite{Courcelle1990, Fomin2013}.
+However, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding the solution, which is not possible with dynamic programming.
+%These two algorithms are related but are not equivalent.
+%Dynamic programming is more general purpose, while a tensor network has a richer algebraic structure, and this structure is crucial for solution space property computation.
+%\purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
 %For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
@@
 including the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem and the maximal clique problem, in \App{sec:otherproblems}.
-\xpurple{More details on which combinatorial optimization problems this
-applies to?}
+%\xpurple{More details on which combinatorial optimization problems this applies to?}
 The paper is organized as follows.
@@
 \end{definition}
-
-\purple{I think the following paragraph could be clarified. When you read the definition
-of generic programming, it's not clear what ``in the most general setting'' means. My
-understanding is it just means that the program will work regardless of the input data
-type - it would be good to say this explicitly. }
-\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
-\purple{I also think the way it is written takes a while
-to understand what dynamically versus statically typed languages are. The definition,
-“When these languages “see” a new input type, the compiler can recompile the generic
-program for the new type.” comes rather late in the paragraph.}
-\xpurple{Also, while I know what you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
-lost on someone only with a physics background.}
-This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
-To understand the first aspect on generality, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
+\purple{efficiency}
+By in the most general setting, we mean that a single program should work correctly for different input data types. For example, 
+%\purple{I think the following paragraph could be clarified.
+When you read the definition of generic programming, it's not clear what ``in the most general setting'' means.
+My understanding is it just means that the program will work regardless of the input data type - it would be good to say this explicitly.
+}
+%\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
+%\purple{I also think the way it is written takes a while to understand what dynamically versus statically typed languages are.
+The definition, “When these languages “see” a new input type, the compiler can recompile the generic program for the new type.” comes rather late in the paragraph.}
+%\xpurple{Also, while I know what you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
+%lost on someone only with a physics background.}
+%This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
+%To understand the first aspect on generality,
+suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
 One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
@@
    {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their numbers
-   \purple{``and their counting'' is gramatically confusing, can we say independence polynomial or degeneracy or something?}\blue{Since you mentioned degeneracy is bad, what about ``numbers''?}} \\
+   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their degeneracy} \\
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
@@
 
-It is in general not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products, which scales exponentially as the number of vertices.
-\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
+It is in general not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
+%\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
 The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
 A fully optimized contraction order can reduce the time complexity significantly, while requiring a minimum space complexity $O(2^{\text{tw}(G)})$~\cite{Markov2008} to store intermediate contraction results.
-\purple{Perhaps just say time and space
-complexity? Order of magnitude doesn't make sense to me in terms of scaling. Also,
-what is the time complexity of finding a good contraction order? Is there a known
-average-case complexity? This seems important.}\blue{see added texts below.}
+In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
+However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021}.
 The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
-In practise, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
-However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021}.
 For large scale applications,
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
-\purple{To clarify - is the expression tree now the coefficients
-on the polynomial? I am a little confused on how we would, for instance, use this to
-compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
+%\purple{To clarify - is the expression tree now the coefficients
+%on the polynomial? I am a little confused on how we would, for instance, use this to
+%compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
 To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
@@
 A theoretically interesting number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs, which can tell us thermal dynamic properties of these lattices at the high temperature limit.
-\purple{Why is it useful and
-what does it tell us about the physical system?}\blue{It is probably useless, so: useful -> theoretically interesting}
 For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
@@
     \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
-    Each vertex represents an independent set, with edges between independent sets with pairwise Hamming distance $\leq 2.$ \blue{can be connected by a swap operation?}}
+    Each vertex represents an independent set, with edges between independent sets which differ by a swap operation or a vertex addition.}
     \label{fig:exp_configuratoins}
@@
 As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
-The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets with a small pairwise Hamming distance $\leq 2.$
+The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets which differ by a swap operation or a vertex addition.
 The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$

### 2022-03-18 paper/paper.tex
Updates from Overleaf

@@
 \begin{abstract}
-We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
-Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
-The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph.
-Other hard graph problems solvable in our framework includes the cutting problem, the vertex coloring problem, the maximal clique problem, the dominating set problem and the satisfiability problem, among others.
-To demonstrate the versatility of this tool, we apply it to a few examples including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps to understand these hard problems better.
+%We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
+We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
+to compute various solution space properties of combinatorial optimization problems on graphs with local constraints.
+\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}
+%Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
+We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate the independent sets of a given size.
+%By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
+By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
+the same general, simple-to-implement framework can be used to compute all of these properties.
+Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
+The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph $G$.
+Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
+To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
+% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
+We show how our method helps to understand these hard problems better. \purple{Say on systems with hundreds of vertices or spins?}
 \end{abstract}

### 2022-03-18 paper/paper.tex
Updates from Overleaf

@@
 We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-to compute various solution space properties of combinatorial optimization problems on graphs with local constraints.
-\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}
+to compute various solution space properties of a class of combinatorial optimization problems specified by local constraints.
+\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
-To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
+To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on King's graphs at $0.8$ filling and 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
 % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps to understand these hard problems better. \purple{Say on systems with hundreds of vertices or spins?}
+We show how our method helps to understand these hard problems better on systems with hundreds of vertices or spins. \xpurple{Say on systems with hundreds of vertices or spins?}
 \end{abstract}
@@
 With the counting of sets at different sizes, one can related the computational hardness with the counting of sets at different sizes~\cite{Xu2018}.
-With the configuration enumeration/sampling at a given size, one can measure the overlap gap property better,
+With the configuration enumeration/sampling at a given size, one can measure the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} better,
 while the configuration space connectivity also privides us an intuition about designing a better classical or quantum algortihms.
@@
 
-To avoid the discussion being unnecessarily diversed, we mainly focus on the independent set problem,
+To avoid the discussion being unnecessarily diverged, we mainly focus on the independent set problem,
 and discuss other combinatorial optimization problems,
@@
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide a few examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
-We show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices
-and analyzing the presence of overlap gap property on three regular graphs.
+Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
+In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
+We compute the 2D generalization of Fibonacci integer sequence up to size $39$, while the previous best known result is $37$.
+In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
+We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of overlap gap properties in three regular graphs.
+In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
+This is a research frontier that understand which can help people design better quantum algorithms to beat its classical counterpart.
 %Our method can also be used to find ``maximal'' independent set properties; 
@@
 \end{definition}
-\purple{efficiency}
+This definition of generic programming covers two major aspects: ``work in the most general setting'' and ``with out loss of efficiency''.
 By in the most general setting, we mean that a single program should work correctly for different input data types. For example, 
@@
 In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
-The second aspect is about performance. For dynamically typed languages, such as Python,
+The second aspect is about the efficiency. For dynamically typed languages, such as Python,
 one can easily write very general codes, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two numpy arrays with python objects as elements is much slower than statically typed languages such as C++ and Julia~\cite{Bezanson2012}.
@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-The Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and how are they related, and Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+
+\begin{figure}[th]
+   \centering
+\centerline{\begin{tikzpicture}[]
+    \scriptsize
+    \node[draw,fill=lime!80,fill opacity=1, text opacity=1.0,ellipse,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
+    \def\dx{-3};
+    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Largest order};
+    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}Largest 2 orders};
+    \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
+    \node[draw,fill=brown!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, -0.1) (T2) {};
+    \node at (\dx, -1.2) {$\ldots$};
+    \node[above = 1cm] at (T) (textT) {Tropical};
+    \node[below = 2cm, left=4cm] (textT2) {Extended Tropical};
+    \draw[black,-latex] (textT) -- (T);
+    \draw[black,-latex] (textT2) -- (T2);
+
+    % set and set sampler
+    \node[draw,fill=yellow,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
+    \node[below of=1] at (SN) {Set};
+    \node[draw,fill=red!70,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
+\end{tikzpicture}}
+
+    \caption{The the tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
+    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.
+``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two order.}
+     \label{fig:venn-diagram}
+\end{figure}
 
@@
    {Expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
-   {Polynomial truncated to highest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
+   {Polynomial truncated to largest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
    {Polynomial truncated to $k$-th order combined with set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
@@
 
-    The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements:
-    \small{
-    \begin{align*}
-        &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
-        =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
-        &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
-        =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
-        %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
-    \end{align*}}
-
-One can easily check the maximum tensor during computing is rank 2, and the total number of multiplication operations is reduced significantly.
+The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements.
+The contraction process can be represented as a binary tree structure:
+
+\centerline{\begin{tikzpicture}[]
+    \def\dx{0};
+    \def\dy{0};
+    \def\d{1};
+    \def\a{1.0};
+    \def\b{1};
+    \def\ya{-1.0};
+    \def\yb{-0.8};
+    \node[] at (\dx+5*\a, \dy+5*\b) (R1) {$R[n^2]$};
+    \node[] at (\dx+3*\a, \dy+4*\b) (S1) {$S_{bc}[n^3]$};
+    \node[] at (\dx+2*\a, \dy+3*\b) (Q1) {$Q_{bd}[n^2]$};
+    \node[] at (\dx+8.5*\a, \dy+3*\b) (Q2) {$Q_{bc}[n^2]$};
+    \node[] at (\dx+\a, \dy+2*\b) (P1) {$P_{d}[n]$};
+    \node[] at (\dx+9*\a, \dy+2*\b) (P2) {$P_{bc}[n^3]$};
+    \node[] at (\dx+0.5*\d, \dy+\b) (M1) {$M_{d}[n^2]$};
+    \node[] at (\dx+3.5*\d, \dy+\b) (M2) {$M_{bd}[n^2]$};
+    \node[] at (\dx+5.5*\d, \dy+\b) (M3) {$M_{cd}[n^2]$};
+    \node[] at (\dx+9.5*\d, \dy+\b) (M4) {$M_{ac}[n^2]$};
+    \node[] at (\dx, \dy) (Bde) {$B_{de}$};
+    \node[] at (\dx+\d, \dy) (We) {$W_e$};
+    \node[] at (\dx+2*\d, \dy) (Wd) {$W_d$};
+    \node[] at (\dx+3*\d, \dy) (Bbd) {$B_{bd}$};
+    \node[] at (\dx+4*\d, \dy) (Wb) {$W_b$};
+    \node[] at (\dx+5*\d, \dy) (Bcd) {$B_{cd}$};
+    \node[] at (\dx+6*\d, \dy) (Wc) {$W_c$};
+    \node[] at (\dx+7*\d, \dy) (Bbc) {$B_{bc}$};
+    \node[] at (\dx+8*\d, \dy) (Bab) {$B_{ab}$};
+    \node[] at (\dx+9*\d, \dy) (Bac) {$B_{ac}$};
+    \node[] at (\dx+10*\d, \dy) (Wa) {$W_a$};
+    \draw[] (Bde) -- (M1);
+    \draw[] (We) -- (M1);
+    \draw[] (Bbd) -- (M2);
+    \draw[] (Wb) -- (M2);
+    \draw[] (Bcd) -- (M3);
+    \draw[] (Wc) -- (M3);
+    \draw[] (Bac) -- (M4);
+    \draw[] (Wa) -- (M4);
+    \draw[] (M1) -- (P1);
+    \draw[] (Wd) -- (P1);
+    \draw[] (Bab) -- (P2);
+    \draw[] (M4) -- (P2);
+    \draw[] (P1) -- (Q1);
+    \draw[] (M2) -- (Q1);
+    \draw[] (Bbc) -- (Q2);
+    \draw[] (P2) -- (Q2);
+    \draw[] (Bbc) -- (Q2);
+    \draw[] (P2) -- (Q2);
+    \draw[] (Q1) -- (S1);
+    \draw[] (M3) -- (S1);
+    \draw[] (S1) -- (R1);
+    \draw[] (Q2) -- (R1);
+\end{tikzpicture}}
+% \small{
+% \begin{align*}
+%     &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
+%     =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
+%     &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
+%     =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
+%     %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
+% \end{align*}}
+The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest are all intermediate contraction results.
+Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor, and the contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
+One can easily check the largest tensor during computing has space complexity $n^2$, and the largest contraction time complexity is $n^3$, which is much smaller than direct enumeration ($n^5$).
 \end{example}
@@
 One may argue that one can first evaluate this polynomial at different $x$ being a standard number type,
-and then apply the gaussian elimination to fit the coefficients of this polynomial.
+and then apply the Gaussian elimination to fit the coefficients of this polynomial.
 This seemingly more time and space efficient approach suffers from severe issues in practise.
@@
 where siblings $A, B, C$ and $D$ can be any four types of nodes.
-It can be represented diagramatically as the following.
+It can be represented diagrammatically as the following.
 
@@
 so we have to use the expression tree representation to store it in a compact format and draw samples from it.
-We compare two categories of graphs, one is the King's graph at $0.8$ filling, a type of unit disk graph having no overlap gap property, \blue{@Maddie, do you have a good reference to justify this statement about unit disk graph OGP?}
+We compare two categories of graphs, one is the King's graph at $0.8$ filling,
 another is the vertex $3$-regular graph that we want to investigate.
@@
 In \Fig{fig:hamming}(a), we observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs.
+Which is a clear evidence of that the overlap gap property is absent in $0.8$ filling King's graph.
+Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling~\cite{Ebadi2022}, this result is highly nontrivial.
 While in \Fig{fig:hamming}(b), we observed the multiple peak structure as the ratio becomes small for the $3$-regular graphs.
@@
 The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010},
+The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
 but samples from local minima with a wide range of Hamming distances from the MISs.
@@
 We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
-
-\begin{figure}[th]
-   \centering
-\centerline{\begin{tikzpicture}[]
-    \scriptsize
-    \node[draw,fill=lime!80,fill opacity=1, text opacity=1.0,ellipse,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-    \def\dx{-3};
-    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
-    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Largest order};
-    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}2nd largest order};
-    \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
-    \node[draw,fill=brown!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, -0.1) (T2) {};
-    \node at (\dx, -1.2) {$\ldots$};
-    \node[above = 1cm] at (T) (textT) {Tropical};
-    \node[below = 2cm, left=4cm] (textT2) {Extended Tropical};
-    \draw[black,-latex] (textT) -- (T);
-    \draw[black,-latex] (textT2) -- (T2);
-
-    % set and set sampler
-    \node[draw,fill=yellow,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-    \node[below of=1] at (SN) {Set};
-    \node[draw,fill=red!70,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
-\end{tikzpicture}}
-
-    \caption{The the tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
-    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.}
-    \purple{It's not clear what
-some words mean on this diagram, such as ``highest order'' and ``extended tropical''}
-\blue{the extended tropical is defined in \Sec{sec:weighted}, should I emphasis it more? also, ``highest''->``largest''}
-     \label{fig:venn-diagram}
-\end{figure}
 

### 2022-03-19 paper/paper_before_maddie.tex
Updates from Overleaf

--- 2022-03-18 paper/paper.tex
@@
 By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
-the same general, simple-to-implement framework can be used to compute all of these properties.
+the same simple-to-implement framework can be used to compute all of these properties.
 Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
@@
 To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on King's graphs at $0.8$ filling and 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
-% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps to understand these hard problems better on systems with hundreds of vertices or spins. \xpurple{Say on systems with hundreds of vertices or spins?}
+\purple{I might not directly mention the classes of graphs we look at for overlap gap - it might be too much information.
+I'm not sure though, what do you think?} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
+We show how our method helps to understand these hard problems on systems with hundreds of vertices.
 \end{abstract}
@@
 % \end{align*}}
-The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest are all intermediate contraction results.
-Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor, and the contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
-One can easily check the largest tensor during computing has space complexity $n^2$, and the largest contraction time complexity is $n^3$, which is much smaller than direct enumeration ($n^5$).
+The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest nodes are all intermediate contraction results.
+Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor and the largest number of subscripts is the treewidth of the original $5$-vertex graph.
+The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
+One can easily check the largest tensor during computing has space complexity $n^2$, i.e.
+the treewidth of the original $5$-vertex graph is $2$, and the largest contraction time complexity is $n^3$, which is much smaller than the direct enumeration ($n^5$).
 \end{example}
@@
 one can compute the number of configurations in each branch rigorously and efficiently.
-%\purple{To clarify - is the expression tree now the coefficients
-%on the polynomial? I am a little confused on how we would, for instance, use this to
-%compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
 To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
-\xpurple{How do we compute the size of each
-branch?}
 \begin{example}
@@
 In particular, in \Fig{fig:hamming}, 
-we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \text{ratio} \times \lfloor\alpha(G)\rfloor$ for each instance
+we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lfloor (1-\text{ratio}) \times \alpha(G)\rfloor$ for each instance
  and show the pairwise Hamming distance distribution for the enumerated configurations.
@@
         \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-        \caption{$9$ Random three regular graphs of size $110$.}
+        \caption{$9$ random three regular graphs of size $110$.}
     \end{subfigure}
-    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.
+    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
     In each plot, the $x$-axis is the hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
@@
     \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
-    Each vertex represents an independent set, with edges between independent sets which differ by a swap operation or a vertex addition.}
+    Each vertex represents an independent set, and each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition.}
     \label{fig:exp_configuratoins}
@@
 \section{Discussion and conclusion}
-In this paper, we introduce a method to use generic programming tensor networks to compute a number of different properties of a hard problem,
-including the largest several independent sets sizes, the counting of independent sets of a given size and
+In this paper, we introduce a method to use generic programming and tensor networks to compute a number of different solution space properties of the maximum independent set problem,
+including the largest several independent sets sizes, the number of independent sets of a given size, and
 the enumeration of independent sets of a given size.
-For each solution space property, we design an algebra being a commutative semiring and let it be the tensor element type.
+For each solution space property, we design a commutative semiring algebra for the tensor element type.
 With different algebras, the contraction of the same tensor network gives us the different properties.
@@
 We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
-We acknowledge Sepehr Ebadi, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
-We thank Benjamin Schiffer for providing helpful advices about writing.
-We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
-We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt,
+We acknowledge Sepehr Ebadi and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
+We thank Benjamin Schiffer for providing helpful feedback on the manuscript.
+We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
+We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt
 for actively maintaining their packages and resolving related issues voluntarily.

### 2022-03-20 paper/paper.tex
Updates from Overleaf

@@
 We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-to compute various solution space properties of a class of combinatorial optimization problems specified by local constraints.
+to compute various solution space properties of a class of combinatorial optimization problems that can be specified by local constraints.
 \purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate the independent sets of a given size.
+We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate/sample the independent sets of a given size.
 %By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
 By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
-the same general, simple-to-implement framework can be used to compute all of these properties.
+the same simple-to-implement framework can be used to compute all of these properties.
 Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
-The algorithmic complexity of this approach is $2^{{\rm tw}(G)}$, where ${\rm tw} (G)$ is the treewidth of the problem graph $G$.
+The algorithmic complexity of this approach is $2^{{\rm tw}(\overline G)}$, where ${\rm tw} (\overline G)$ is the treewidth of the line graph of the tensor network graph $G$.
 Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
-To demonstrate the versatility of this tool, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on King's graphs at $0.8$ filling and 3-regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
-% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-We show how our method helps to understand these hard problems better on systems with hundreds of vertices or spins. \xpurple{Say on systems with hundreds of vertices or spins?}
+To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the Overlap Gap Property on unit disk graphs and regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
+\purple{I might not directly mention the classes of graphs we look at for Overlap Gap - it might be too much information.
+I'm not sure though, what do you think?} \blue{I agree ``King's graphs at 0.8 filling and 3-regular graphs'' is a bit too detailed, so I rephrased it as ``unit disk graphs and regular graphs'' that only conveys the most important information.} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the Overlap Gap Property on three regular graphs.
+%We show how our method helps to understand these hard problems on systems with hundreds of vertices.
 \end{abstract}
@@
 \begin{keywords}
-independent set, tensor network, maximum independent set, independence polynomial, generic programming
+solution space property, tensor network, maximum independent set, independence polynomial, generic programming
 \end{keywords}
@@
 In graph theory and combinatorial optimization, there is an important class of problems that can be local constraints over a vertex and its neighborhood,
-including the independent set problem, the cutting problem, the vertex coloring problem, the satisfiability problem,
+including the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the satisfiability problem,
 the maximal clique problem, and the vertex cover problem~\cite{Moore2011}.
@@
 %The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
-, which is typically 
+which is typically 
 %while many of them belong to the hardness category
-NP-hard~\cite{Hastad1996}, i.e. it is unlikely to be solved in a polynomial time.
+NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a polynomial time.
 %\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
@@
 I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.
-counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
+In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.\ counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
 Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 With the counting of sets at different sizes, one can related the computational hardness with the counting of sets at different sizes~\cite{Xu2018}.
-With the configuration enumeration/sampling at a given size, one can measure the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} better,
-while the configuration space connectivity also privides us an intuition about designing a better classical or quantum algortihms.
-\purple{I would give examples of why we want to compute solution space
-properties.
-For instance, in statistical physics, computing thermal states and
-observables via the partition function. In complexity theory, proving limits on local
-algorithms (OGP).}\blue{now?}
+With the configuration enumeration/sampling at a given size, one can measure the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019} better,
+while the configuration space connectivity also provides us an intuition about designing better classical or quantum algorithms.
+%\purple{I would give examples of why we want to compute solution space properties.
+%For instance, in statistical physics, computing thermal states and
+%observables via the partition function. In complexity theory, proving limits on local algorithms (OGP).}\blue{now?}
 
@@
 Tensor network is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy.
-It is composed of a set of tensors and a set of labels for specifying the contraction of tensors,
-where the tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
+It is composed of a set of labelled tensors, where the labels are used for specifying the contraction relation.
+The tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
 We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
@@
 %\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
-When using tensor network for solving one of the best sets with the maximum size,
+When using tensor network for solving one of the best solutions,
 the time complexity is the same as the dynamic programming algorithm~\cite{Courcelle1990, Fomin2013}.
-However, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding the solution, which is not possible with dynamic programming.
+However, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
 %These two algorithms are related but are not equivalent.
@@
 %Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
-%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
+%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
 %However, there is a lack of general and versatile tool to compute these different properties of independent sets.
@@
 Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
-In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
-We compute the 2D generalization of Fibonacci integer sequence up to size $39$, while the previous best known result is $37$.
-In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of overlap gap properties in three regular graphs.
-In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
-This is a research frontier that understand which can help people design better quantum algorithms to beat its classical counterpart.
+%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
+We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
+%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
+We show the strongest numeric evidence so far of the absence of Overlap Gap Property in King's graph and the existence of Overlap Gap properties in three regular graphs.
+%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
+This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
 %Our method can also be used to find ``maximal'' independent set properties; 
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} is also known as einsum, factor graph or sum-product network~\cite{Bishop2006} in different contexts;
-it can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
+A tensor network~\cite{Cirac2020, Orus2014} can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
 Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
@@
 One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor\xpurple{signifying which pairs of indices are summed over}.
-Hence a tensor network can be represented as a simple graph,
-where a tensor is mapped to a vertex and a label shared by two tensors is mapped to an edge.
-In this work, we do not impose such a restriction, so an index can appear an arbitrary number of times. 
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
+Hence a tensor network can be represented as a open simple graph,
+where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
+In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
 The graphical representation of a generalized tensor network is a hypergraph, in which an edge (a label in subscript) can be shared by an arbitrary number of vertices (tensors).
-These two notations are equivalent in representation power,
-while the generalized tensor network might produce smaller contraction complexity,
+Although two notations are equivalent in representation power thought some transformation,
+the generalized tensor network might produce smaller contraction complexity,
 which will be illustrated in \App{sec:tensorbad}.
@@
 %However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
-\xpurple{I feel that the $\delta$ tensors point is unnecessary to mention in the main text. Because not much detail is given, I internalized what it meant only on the third read-through.}
 
@@
 data type. This is easy to do for dynamically typed languages like Python, which only
-verify and enforce the rules for the input data type at runtime (called type-checking).
-However, when the input data type is only checked at runtime (as opposed to when the
+verify and enforce the rules for the input data type at run time (called type-checking).
+However, when the input data type is only checked at run time (as opposed to when the
 code is compiled), type-specific optimization cannot be used. High efficiency is only
@@
 %Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
-The truth is, the elements in a tensor does not have to be a regular number type,
+In fact, the elements in a tensor does not have to be a regular number type,
  or even a field (since division is not used in tensor contraction).
@@
 This motivates us to think about what is the most general tensor element type allowed in a tensor network contraction program.
-We find that, as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction result will be valid and be independent of the contraction order.
-A commutative semiring is a ring with its multiplication operation being commutative and without an additive inverse.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $R$, the following relations must hold for any arbitrary three elements $a, b, c \in R$.
+We find that, as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction will be doable and the result will be independent of the contraction order.
+Here, a commutative semiring is a field without additive inverse and multiplicative inverse.
+Giving up these nice properties of a field means a lot to tensor computation: tensor network compression algorithms might be not applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014}, and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without additive inverse~\cite{Kerr1970}.
+But here, we only use the commutative properties of an algebra for the purpose of tensor network contraction orders optimization.
+To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
 \begin{align*}
@@
 \end{align*}
-We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
+%We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and how are they related, and Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
 
@@
     The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.
-``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two order.}
+``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.}
      \label{fig:venn-diagram}
@@
    {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
-   {Expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
+   {Sum-Product expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
    {Polynomial truncated to largest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
@@
 \end{equation}
-where we use subscripts to annotate different vertices, these annotation are only used in configuration enumeration and sampling.
-One can index tensor elements by subscripting tensors, e.g.\ $W(x_i, w_i)_0=1$ is the first element associated with $s_i=0$ and $W(x_i, w_i)_1=x_i^{w_i}$ is the second element associated with $s_i=1$.
+where subscripts are used to annotate different vertices in configuration enumeration and sampling.
+One can index tensor elements by subscripting tensors, e.g.\ $W(x_v, w_v)_0=1_v$ is the first element associated with $s_v=0$ and $W(x_v, w_v)_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{i=1}^{|V|} W(x_i, w_i)_{s_i} \prod\limits_{(i,j) \in E(G)} B_{s_i s_j},
-\end{equation}
-where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$ (see Example \ref{eg:tensorcontraction} for a concrete example).
+    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W(x_v, w_v)_{s_v} \prod\limits_{(w,v) \in E} B_{s_w s_v},
+\end{equation}
+where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$.
 The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
@@
 
-It is in general not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
+In general, it is not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
 %\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
-The standard approach to evaluate a tensor network is to contract two tensors at a time with a certain order utilizing the associativity and commutativity of tensor contraction.
-A fully optimized contraction order can reduce the time complexity significantly, while requiring a minimum space complexity $O(2^{\text{tw}(G)})$~\cite{Markov2008} to store intermediate contraction results.
+The standard approach to evaluate a random tensor network is: first find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
+An optimal tensor network contraction order corresponds to an optimal tree decomposition of its line graph and the largest intermediate tensor has a rank equal to the tree width of this optimal tree decomposition~\cite{Markov2008}.
 In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
-However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021}.
-The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
-For large scale applications,
-it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.
-enumerating certain degrees of freedom in an external loop so that the space complexity of contracting a smaller tensor network inside the loop can be smaller.
+However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021} utilizing the associativity and commutativity of tensor contraction.
+%The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
+For large scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.
+loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom, which might have a smaller space complexity.
 
 \begin{example}\label{eg:tensorcontraction}
-In the following, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order simplifies the computation.
+In the following, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
 
@@
 
-The contraction of this tensor network can be done in a pairwise order utilizing the associativity, additive commutativity, and multiplicative commutativity of tensor elements.
-The contraction process can be represented as a binary tree structure:
+One can represent a possible pair-wise contraction of tensors as a binary tree structure:
 
@@
 % \end{align*}}
-The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in the our tensor network while the rest are all intermediate contraction results.
-Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor, and the contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is always $2$.
-One can easily check the largest tensor during computing has space complexity $n^2$, and the largest contraction time complexity is $n^3$, which is much smaller than direct enumeration ($n^5$).
+The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in our tensor network while the rest nodes are all intermediate contraction results.
+Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
+The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is $2$.
+One can easily check the largest tensor during computing has space complexity $O(n^2)$ and this is optimal, i.e.
+the treewidth of the original $5$-vertex graph is $2$, and the time complexity is $O(n^3)$, which is much smaller than that of direct enumeration $O(n^5)$.
 \end{example}
-
-\purple{I have not checked this yet but will
-tomorrow. Is it really easy/simple enough to do without writing stuff down? Is this the simplest
-example possible? The equations look quite formidable at first glance, and it takes a lot of time
-to match the hyperedge labels in the equation to the physical graph.}\blue{sometimes I am afraid the example is too trivial to be useful.
-The simplest example to show contraction order matters can be a 3-vertex one.}
 
@@
 and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-By assigning a standard computer number to $x$, one can evaluate this independence polynomial for this specific value by contracting this tensor network directly.
-\purple{By feed in standard computer number types into the network, do you mean for
-x? Then, you look at multiple x, you can fit the independence polynomial to solve for
-the coefficients? It's not very explicit this procedure works at this point.}\blue{how about now?}
-However, instead of evaluating this polynomial for a certain value, we are more interested in finding the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
-\purple{Does the previous technique
-(contracting the tensor network numerically) give the coefficients of the polynomial?
-The use of the word “however” here is confusing to me because it feels like you're
-saying that the previous technique doesn't give the coefficients, or it's very hard to
-obtain the coefficients.}\blue{Yep, we haven't found the coefficients. I tried to modify words a bit, does it look better now?}
+By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly by contracting this tensor network.
+However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
 To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
@@
 In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-One may argue that one can first evaluate this polynomial at different $x$ being a standard number type,
+One may argue that one can first evaluate this polynomial at different $x$ being a real number,
 and then apply the Gaussian elimination to fit the coefficients of this polynomial.
@@
 The data ranges of standard integer types are too small to cover many practical using cases,
-while the floating point numbers may have round off error that much larger than the value itself, because the number of sets at different sizes may vary tens or even hundreds of orders and this makes the small coefficients can not be retrieved correctly by fitting.
+while the floating point numbers may have round off error that much larger than the value itself
+due to the fact that the number of sets at different sizes may vary tens or even hundreds of orders and this makes the small coefficients can not be retrieved correctly by fitting.
 For the purpose of evaluating these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
@@
 For the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
-\purple{It's not clear to me what we gain by using the
-polynomial semiring rather than floating points/integers here. Could you comment on
-how the compiler can optimize on this data type?}\blue{I added some discussion here to address why we stick to polynomial number types,
-for short, it is a dynamic type that can be slow, so we do not use it a lot in practise.
-I mention it here because it is the base of the following discussion.}
 
@@
 \end{equation}
-where the lower-order terms vanish. We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
-\purple{I was initially confused
-because I thought 0 = (0, ?) where “?” could be anything positive since it's multiplied
-by zero. It confused me that ? could equal $-\infty$ since I thought you defined your ring for
-k positive, since a polynomial has positive exponents. If you have negative exponents I
-thought it is a Laurent polynomial or something. After re-reading I see why this doesn't
-matter, though.}\blue{I let $\mymathbb{0} = (1, -\infty)$ now, it is still correct, is it easier for understanding or I change it back?}
+where all terms except the largest order vanish.
+We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
 From this, we can define a new algebra as
@@
     a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-    \mymathbb{0} &= 1\infty^{-\infty}\\
+    \mymathbb{0} &= 0\infty^{-\infty}\\
     \mymathbb{1} &= 1\infty^{0}.
@@
 \end{equation}
+Note here, in order to define the zero element, we have generalized the previous polynomial to the Laurent polynomial.
 To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
@@
 which can be used for e.g. counting the maximal independent sets with smallest cardinality,
-where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence contraint.
+where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence constraint.
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
@@
 \section{Enumerating and sampling independent sets}\label{sec:enumeration}
+
 \subsection{Set algebra for configuration enumeration}
@@
 for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
-The most studied enumeration of maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} requires using a different tensor network structure, which is discussed in \App{sec:maximal}.
+Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables can carry labels, so that in the output polynomials, one can read out all independent sets directly.
+The multiplication between labelled variables are commutative while the summation of labelled variables forms a set.
+Intuitively, one can use a bit string as the representation of a labelled variable and use bit-wise or $\lor^\circ$ as the multiplication operation,
+e.g. in a 5-vertex graph, $x_2$ can be represented as $01000$, $x_5$ can be represented as $00001$ and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
 To enumerate all independent sets, we designed an algebra defined on sets of bit strings:
@@
 \end{equation}
-where $s$ and $t$ are each a set of $|V|$-bit strings and $\lor^\circ$ is the bitwise OR operation over two bit strings.
+where $s$ and $t$ are each a set of $|V|$-bit strings.
 \begin{example}\label{eg:setalgebra}
@@
 one can avoid this issue by using the bounding technique in \App{sec:bounding}.
+One may also be interested in a more studied enumeration of maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988}.
+It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure for the maximal independent set problem.
 
@@
 \end{equation}
-where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g. by picking the one with a smaller integer value.
+where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g.
+by picking the one with a smaller integer value.
+In practise, it is completely fine to pick a random one (not commutative anymore) to generate a random MIS.
 
 \subsection{Sampling extremely large configuration space}
-When the graph size goes large, the configurations might be impossible to fit into any type of storage.
-Then instead of using the set algebra, one can use a binary expression tree as a compact representation of the configurations.
-We use a quadruple $(type, data, left, right)$ to represent a node in the tree, where $type$ is one of
+When the graph size goes large, a set of configurations might be impossible to fit into any type of storage.
+To get something meaningful out of configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.
+instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
+A node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of
 \texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node,
-$left$ and $right$ are left and right operands of \texttt{SUM} and \texttt{PROD} nodes.
+$left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
 
@@
 \end{equation}
-\purple{It might be nice to have a picture of an example tree if you have time. However,
-it is pretty clear from the definition, it would just help to visualize. Do you ever use the
-zero element?}\blue{now we have an example, but it does not include a zero element, do you think I should use a more concrete one instead of an abstract one?}
 The vertex tensor and edge tensor become
@@
 
-This algebra is a commutative semiring because we define the equivalence of two expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
-Although one is probably unable to enumerate the configurations represented by this tree due to the extremely large configuration space size,
-but he can directly sample configurations from this tree.
-This is because once we have this expression tree representation of the configuration space,
-either generate by using this algebra directly or serve as the coefficients of (truncated) polynomials,
-one can compute the number of configurations in each branch rigorously and efficiently.
-%\purple{To clarify - is the expression tree now the coefficients
-%on the polynomial? I am a little confused on how we would, for instance, use this to
-%compute the MISs}\blue{added one more descriptive sentence, does it resolve your concern?}
-To generate samples, one just descends this expression tree to left or right sibling with probability decided by the size of each branch while doing the computation specified by the first field.
-\xpurple{How do we compute the size of each
-branch?}
+This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
+Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial so that one can have such trees for independent sets with largest several sizes.
+Although one probably can not enumerate all configurations represented by a sum-product expression tree due to its extremely large size,
+he can draw unbiased samples from it efficiently.
+One starts from the root node, and descends this tree recursively to its left or right sibling with probability decided by the size of each sub-tree while doing the computation specified by the first field.
+The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
+In an sum-product expression tree, the number of configurations of a sub-trees can be determined easily as we will show in the following example.
 \begin{example}
-Let us consider the following expression tree 
+Let us consider the following sum-product expression tree 
 \begin{equation*}
@@
 
-The left and right sibling of root node has size $|A|\times |B|$ and $|C|+|D|$ respectively,
-and since the root node has type \texttt{SUM}, its size can be computed as $|A|\times |B| + |C|+|D|$.
+The left and right sibling of root node have size $|A|\times |B|$ and $|C|+|D|$ respectively.
+Since the root node has type \texttt{SUM}, its size can be computed as $|A|\times |B| + |C|+|D|$.
 One can compute the sizes of $A, B, C$ and $D$ recursively until the program meets either a the \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$ respectively.
@@
 \section{Weighted graphs}\label{sec:weighted}
-In the previous discussion, we have limited ourselves to unweighted graphs.
-For integer weighted graphs, all results still holds,
-while for general weighted graphs, the independence polynomial is not computable anymore.
+All the previous discussion for unweighted graphs still holds for integer weighted graphs,
+while for general weighted graphs, the independence polynomial is not well defined anymore.
 For general weighted graphs, we are more interested to know the $k$ most weighted sets and their sizes.
-Hence we define the extended tropical numbers as the following
+Hence we define the extended tropical numbers as a natural generalization of tropical numbers:
 
@@
 where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
-The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$,
-one can find an implementation in \App{sec:maxsum}.
+The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$.
+One can find an efficient algorithm in \App{sec:maxsum}.
 The vertex tensor and edge tensor become
@@
 where we have used the relation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
-Similar to the tropical numbers, we can combine it with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
+Similar to the tropical numbers, we can combine the extended tropical algebra with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
 Since the $\odot$ operation of configuration sampler is not used, the resulting configurations are deterministic and complete.
@@
     (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
-    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the expression tree format,
+    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum-product expression tree format,
     with or without bounding the enumeration space.
@@
 while in panel (d), the timing of certain computing tasks also strongly correlates with other factors like the configuration space size.
-\purple{with the number of vertices, and therefore the treewidth}\blue{not sure it is safe to say this, because they do not always have a nice linear relation}.
-\xpurple{Does this say anything about how
-optimized the contraction order is? If so, it might be worth explicitly saying. Some of
-the quantities in panel d look like they might be superexponential in the number of
-vertices (tree-width).}
-Among these benchmarks, computational tasks with data types tropical number of on CPU and real and complex numbers on both CPU and GPU can utilize fast BLAS functions to evaluate tensor contractions, hence
+Among these benchmarks, computational tasks with data types tropical number of on CPU and real and complex numbers on both CPU and GPU can utilize fast basic linear algebra subprograms (BLAS) functions to evaluate tensor contractions, hence
 are much faster comparing to non-BLAS element types in the same category.
-\xpurple{It might be worth explicitly saying
-the data types the first time they're mentioned (for example, I don't know what T is.
-Also, it might be worth adding a couple descriptor words on bounding.}
 GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
@@
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors (\App{sec:fft})\purple{Can the round-off error thing be seen from Figure c?}\blue{it is hard, so I added a ref to the appendix, is it more informative?}.
-The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
 In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
@@
 We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
-The types of graphs include: the square grid graphs (Figure~\ref{fig:lattices}(a)); the square grid graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ square grids are occupied with vertices  (Figure~\ref{fig:lattices}(b));
+The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ square lattices are occupied with vertices  (Figure~\ref{fig:lattices}(b));
 the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)).
-The number of independent sets for square grid graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
+The number of independent sets for square lattice graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
 We computed the integer sequence for $L=38$ and $L=39$, which, to the best of our knowledge, is not known before.
@@
 A theoretically interesting number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs, which can tell us thermal dynamic properties of these lattices at the high temperature limit.
-For the square grid graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
+For the square lattice graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
 This quantity arises in statistical mechanics of hard-square lattice gases~\cite{Baxter1980, Pearce1988} and is used to understand phase transitions for these systems.
@@
 In \Fig{fig:hardsquare}, we look at how $F(L,L)^{1/\lfloor pL^2\rceil}$ scales as a function of the grid size $L$ for all types of graphs shown in Figure~\ref{fig:lattices}.
-Our results match the known results for the non-disordered square grid and King's graphs.
-For disordered square grid and King's graphs with a filling factor $p=0.8$, we randomly sample 1000 graph instances.
+Our results match the known results for the non-disordered square lattice and King's graphs.
+For disordered square lattice and King's graphs with a filling factor $p=0.8$, we randomly sample 1000 graph instances.
 To our knowledge, the entropy constants for these disordered graphs have not been studied before.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{lattices.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/lattices.pdf}
     \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
-    The lattice dimensions are $L\times L$. (a) Square grid graphs. (b) Square grid graphs with a filling factor $p=0.8$.
+    The lattice dimensions are $L\times L$. (a) square lattice graphs. (b) square lattice graphs with a filling factor $p=0.8$.
     (c) King's graphs. (d) King's graphs with a filling factor $p=0.8$.}
@@
     We sampled $1000$ instances for $p=0.8$ lattices and the error bar is too small to be visible.
-    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$ for the corresponding non-disordered square grid and King's graphs.
+    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$ for the corresponding non-disordered square lattice and King's graphs.
     }
@@
 
-\subsection{The overlap gap property\label{sec:overlap-gap}}
-With the tool to enumerate configurations, one can try to understand the structure of the independent set configuration space,
-such as the optimization landscape for finding the MISs and the geometry of the solution space.
-One of the known barriers for finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-Intuitively, if the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection;
+\subsection{The Overlap Gap Property\label{sec:overlap-gap}}
+With the tool to enumerate configurations, one can %try to 
+understand the structure of the independent set configuration space,
+such as the optimization landscape for finding the MISs.
+One of the known barriers for finding the MIS is the so-called Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019}.
+Intuitively, if the Overlap Gap Property is present, it means every two large independent sets either have a significant intersection or very small intersection;
 it implies that large independent sets are clustered together.
-This clustering property has been used to prove the limitations of local algorithms in finding the MISs~\cite{Gamarnik2013, Gamarnik2019}.
-It was shown that for finding MISs of $d$ regular graphs with $d$ and graph sizes both being large, there exists overlap gap property~\cite{Rahman2017,Gamarnik2021}.
-However, it is not yet clear whether for small $d$, e.g. three regular graphs, this statement is still true.
-Here, we direct sample from the computed configurations of large independent sets to investigate the presence or absence of the overlap gap property for some given graphs.
-We do no explore the full configurations space because the number of configurations is too large to fit into a storage,
-so we have to use the expression tree representation to store it in a compact format and draw samples from it.
-We compare two categories of graphs, one is the King's graph at $0.8$ filling,
-another is the vertex $3$-regular graph that we want to investigate.
-Each category contains $9$ randomly generated instances, due to the limitation of computing resources,
-the size of King's graph is $20\times 20$ ($320$ vertices) and the size of $3$-regular graphs are $110$.
+\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{I suppose you want to justify the origin of ``ratio'', then it would great if you can explain it more clearly.
+However, explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
+This clustering property has been used to rigorously prove upper bounds on the performance of local algorithms~\cite{Gamarnik2013, Gamarnik2019}.
+It was shown that for finding MISs of $d$-regular graphs with $d$ and graph sizes both being large, there exists Overlap Gap Property~\cite{Rahman2017,Gamarnik2021}.
+However, it is not known whether for small $d$, e.g. $3$- regular graphs, this statement is still true.
+Here, we direct sample from the computed configurations of large independent sets to investigate the presence or absence of the Overlap Gap Property for some given graphs.
+%We do not explore the full configurations space because the
+Because the number of configurations is too large to fit into storage, we use the compact sum-product expression tree representation to sample from independent sets of a given size. 
+We compare  nine randomly generated instances from two categories of graphs: King's graphs at $\rho = 0.8$ filling and $3$-regular graphs.% that we want to investigate.
+%Each category contains nine randomly generated instances, due to the limitation of computing resources,
+Our method can sample from independent sets of King's graph up to $20\times 20$ ($320$ vertices) and the size of $3$-regular graphs are $110$.
 In particular, in \Fig{fig:hamming}, 
-we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \text{ratio} \times \lfloor\alpha(G)\rfloor$ for each instance
+we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lfloor (1-\text{ratio}) \times \alpha(G)\rfloor$ for each instance
  and show the pairwise Hamming distance distribution for the enumerated configurations.
 In \Fig{fig:hamming}(a), we observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs.
-Which is a clear evidence of that the overlap gap property is absent in $0.8$ filling King's graph.
+Which is a clear evidence of that the Overlap Gap Property is absent in $0.8$ filling King's graph.
 Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling~\cite{Ebadi2022}, this result is highly nontrivial.
 While in \Fig{fig:hamming}(b), we observed the multiple peak structure as the ratio becomes small for the $3$-regular graphs.
-This indicates the presence of the overlap gap property and disconnected clusters exist in the configuration space for large independent sets.
+This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?} and disconnected clusters exist in the configuration space for large independent sets.
 We expect our numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
@@
         \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
-        \caption{$9$ King's graphs of size $20\times 20$, $0.8$ filling.}
+        \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
     \end{subfigure}
@@
         \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-        \caption{$9$ Random three regular graphs of size $110$.}
+        \caption{Nine random three regular graphs of size $110$.}
     \end{subfigure}
-    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor{\rm ratio} \times \alpha(G)\rfloor$.
-    In each plot, the $x$-axis is the hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
+    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
+    In each plot, the $x$-axis is the Hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
     }
@@
     \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
-    Each vertex represents an independent set, with edges between independent sets which differ by a swap operation or a vertex addition.}
+    Each vertex represents an independent set, and each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition.}
     \label{fig:exp_configuratoins}
 \end{figure}
-The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving the Maximum Independent Set problem.
+The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving NP-hard combinatorial optimization problems.
 This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
 As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
-The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, with edges between independent sets which differ by a swap operation or a vertex addition.
-The algorithm either finds the largest independent set with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-The algorithm does not appear to return local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
+The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, and each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition to the set.
+The algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
+The algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
 but samples from local minima with a wide range of Hamming distances from the MISs.
-Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this particular King's graph.
+Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
 
 \section{Discussion and conclusion}
-In this paper, we introduce a method to use generic programming tensor networks to compute a number of different properties of a hard problem,
-including the largest several independent sets sizes, the counting of independent sets of a given size and
-the enumeration of independent sets of a given size.
-For each solution space property, we design an algebra being a commutative semiring and let it be the tensor element type.
-With different algebras, the contraction of the same tensor network gives us the different properties.
-The data types introduced in the main text is summarized in the diagram in \Fig{fig:venn-diagram}.
+In this paper, we introduce a method to use generic programming and tensor networks to compute a number of different solution space properties of certain classes of NP-hard combinatorial optimization problems.
+% the maximum independent set problem.
+%, including the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
+For each solution space property, we design a commutative semiring algebra for the tensor element type.
+By using the same tensor network but replacing the tensor network elements with elements of different algebras, we can compute different solution space properties.
+This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
+% such as the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
+%With different algebras, the contraction of the same tensor network gives us the different properties.
+The different data types introduced in the main text to compute these properties are  summarized in the diagram in \Fig{fig:venn-diagram}. %We go beyond using real numbers and use polyn
 Other than the case with real numbers, we have polynomials and truncated polynomials.
-We combine them with the bit string algebra, the set algebra, and expression tree algebra for finding, enumeration, and sampling of independent sets at a given size.
+We combine them with the bit string algebra, the set algebra, and sum-product expression tree algebra for finding, enumerating, and sampling of independent sets at a given size.
+Three examples are shown to demonstrate how our method can be used to understand the solution space better.
+In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
+We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
+In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
+We show the strongest numeric evidence so far of the absence of Overlap Gap Property in King's graph and the existence of Overlap Gap properties in three regular graphs.
+In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
+This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
 These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
-Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
-our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
+%Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
+%our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
 By adapting to the style of generic programming, we can implement all the algorithms without much effort.
@@
 We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
-We acknowledge Sepehr Ebadi, and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
-We thank Benjamin Schiffer for providing helpful advices about writing.
-We thank Chris Elord for helping us to write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
-We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, and Katharine Hyatt,
+We acknowledge Sepehr Ebadi and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
+We thank Benjamin Schiffer for providing helpful feedback on the manuscript.
+We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
+We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman and Katharine Hyatt
 for actively maintaining their packages and resolving related issues voluntarily.
@@
 \begin{table}[h]
-\caption{The number of independent sets for square grid graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
+\caption{The number of independent sets for square lattice graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
 Here we only include two updated entries for $L=38,39$, which, to our knowledge, has not been computed before~\cite{Butera2014}.
@@
 \begin{tabular}{|c| >{\centering\arraybackslash} p{0.95\linewidth}|}
- \hline $L$  & square grid graphs \\
+ \hline $L$  & square lattice graphs \\
  \hline $38$ & 616 412 251 028 728 207 385 738 562 656 236 093 713 609 747 387 533 907 560 081 990 229 746 115 948 572 583 817 557 035 128 726 922 565 913 748 716 778 414 190 432 479 964 245 067 083 441 583 742 870 993 696 157 129 887 194 203 643 048 435 362 875 885 498 554 979 326 352 127 528 330 481 118 313 702 375 541 902 300 956 879 563 063 343 972 979\\
@@
 \section{Technical guide}\label{sec:technical}
-This project depends on multiple open source packages in the Julia ecosystem.
-We list the Julia packages that play important roles in our code base as follows:
+
+This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package.
+If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
+\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
+One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
+\begin{lstlisting}
+pkg> add GraphTensorNetworks
+\end{lstlisting}
+
+The code we will show below is a gist of how the above package is implemented, which is mainly for the pedagogical purpose.
+It covers most of the topics in the paper without caring much about the performance.
+This project depends on multiple open source packages in the Julia ecosystem:
 
@@
 
-One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
-\begin{lstlisting}
-pkg> add OMEinsum Graphs Mods Primes Polynomials TropicalNumbers OMEinsumContractionOrders
-\end{lstlisting}
-
-The reader may find it surprising that the Julia implementation of the algorithms introduced in this work is so short that except the bounding algorithm,
-all are contained in this appendix. This is due to the power of generic programming. After installing the required packages, one can open a Julia REPL and copy the following codes into it.
+They can be installed in a similar way to \texttt{GraphTensorNetworks}.
+After installing the required packages, one can open a Julia REPL, then copy and paste the following code into it.
 
@@
 
-For better performance, we recommend checking our GitHub repository for the full featured version:
-\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
-It can be installed in a similar style to other packages.
-
 \end{document}

### 2022-03-21 paper/paper.tex
update lattice plot
Updates from Overleaf

@@
 
-\title{Computing properties of independent sets by generic programming tensor networks
+\title{Computing solution space properties by generic programming tensor networks
 \thanks{\funding{...}}
@@
 Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
-The algorithmic complexity of this approach is $2^{{\rm tw}(\overline G)}$, where ${\rm tw} (\overline G)$ is the treewidth of the line graph of the tensor network graph $G$.
+%The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
 Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
@@
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy.
+Tensor network is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy~\cite{Harris2020}.
 It is composed of a set of labelled tensors, where the labels are used for specifying the contraction relation.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/lattices.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 0cm}, clip]{figures/lattices.pdf}
     \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
@@
 In \Fig{fig:hamming}(a), we observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs.
-Which is a clear evidence of that the Overlap Gap Property is absent in $0.8$ filling King's graph.
+Which is a clear evidence of the absence of the Overlap Gap Property in $0.8$ filling King's graph.
 Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling~\cite{Ebadi2022}, this result is highly nontrivial.
-While in \Fig{fig:hamming}(b), we observed the multiple peak structure as the ratio becomes small for the $3$-regular graphs.
+While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the ratio becomes small.
 This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?} and disconnected clusters exist in the configuration space for large independent sets.
@@
     \end{subfigure}
-    \caption{The distribution of pairwise Hamming distances for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
+    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
     In each plot, the $x$-axis is the Hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
+    The ``filled'' region is caused by the fast oscillation of configuration populations of even and odd Hamming distances.
     }

### 2022-03-21 paper/paper.tex

@@
 \begin{figure} 
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
-        \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
-    \end{subfigure}
-    \begin{subfigure}[t]{\textwidth}
-        \centering
-        %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
-        \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-        \caption{Nine random three regular graphs of size $110$.}
-    \end{subfigure}
+    % \begin{subfigure}[t]{\textwidth}
+    %     \centering
+    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
+    %     \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
+    % \end{subfigure}
+    % \begin{subfigure}[t]{\textwidth}
+    %     \centering
+    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
+    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
+    %     \caption{Nine random three regular graphs of size $110$.}
+    % \end{subfigure}
+    \includegraphics[width=\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/fig6.pdf}
     \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.

### 2022-03-21 paper/paper.tex
Updates from Overleaf

@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 0cm}, clip]{figures/lattices.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/lattices.pdf}
     \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
@@
     % \end{subfigure}
-    \includegraphics[width=\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/fig6.pdf}
+    \includegraphics[width=\textwidth, trim={0.0cm 0cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
     \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.

### 2022-03-21 paper/paper.tex
Updates from Overleaf

@@
     % \end{subfigure}
-    \includegraphics[width=\textwidth, trim={0.0cm 0cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
+    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
     \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
@@
 \end{lstlisting}
+To use it, just open Julia REPL and type
+
+\begin{lstlisting}
+julia> using GraphTensorNetworks, Graphs
+
+julia> solve(
+           IndependentSet(
+               Graphs.random_regular_graph(20, 3);
+               optimizer = TreeSA()
+           ),
+           GraphPolynomial()
+       )
+0-dimensional Array{Polynomial{BigInt, :x}, 0}:
+Polynomial(1 + 20*x + 160*x^2 + 659*x^3 + 1500*x^4 + 1883*x^5 + 1223*x^6 + 347*x^7 + 25*x^8)
+\end{lstlisting}
+
+The first time you run the code might trigger the just in time compiling,
+it will be a bit slow, but the following computing will be fast.
 

### 2022-03-21 paper/paper.tex

@@
 \end{lstlisting}
-To use it, just open Julia REPL and type
+
+To use it for solving solution space properties, just open a Julia REPL and type
 
@@
 
+Here the main function \texttt{solve} takes two inputs, the problem instance of type \texttt{IndependentSet} and the property instance of type \texttt{GraphPolynomial}, while the problem instance also takes two arguments to initialize, one is the graph instance one wants to solve and the key word argument \texttt{optimizer} is for tensor network optimization.
+
+\centering{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
+
 The first time you run the code might trigger the just in time compiling,

### 2022-03-22 paper/paper.tex
Updates from Overleaf

--- 2022-03-21 paper/paper.tex
@@
 A myriad of optimizations can be done during the compilation, such as optimize the memory layout of immutable elements with fixed sizes in an array to speed up the array indexing.
-In Julia, arrays with immutable elements with fixed sizes can even be compiled to GPU devices for faster computation~\cite{Besard2018}.
+In Julia, arrays with immutable elements with fixed sizes can even be compiled to graphics processing units (GPU) for faster computation~\cite{Besard2018}.
 
@@
 \section{Performance benchmarks}\label{sec:benchmark}
-We run a single thread benchmark on CPU Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
+We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
 and its CUDA version on a GPU Tesla V100-SXM2 16G.
@@
 
+To use it for solving solution space properties, just open a Julia REPL and type
+
+\begin{lstlisting}
+julia> using GraphTensorNetworks, Graphs
+
+julia> solve(
+           IndependentSet(
+               Graphs.random_regular_graph(20, 3);
+               optimizer = TreeSA(),
+               weights = NoWeight(),
+               openvertices = ()
+           ),
+           GraphPolynomial();
+           usecuda=false
+       )
+0-dimensional Array{Polynomial{BigInt, :x}, 0}:
+Polynomial(1 + 20*x + 160*x^2 + 659*x^3 + 1500*x^4 + 1883*x^5 + 1223*x^6 + 347*x^7 + 25*x^8)
+\end{lstlisting}
+
+Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
+If one wants to use GPU to accelerate the computation, statement ``\texttt{using CUDA}'' must be executed before calling the solve function.
+The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the key word argument \texttt{optimizer} is for tensor network optimization, the key word argument \texttt{weights} specifies the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} allows one to specify the degrees of freedom not summed over, i.e.
+returning a tensor rather than its sum.
+Here, we use \texttt{TreeSA} method in Ref.~\cite{Kalachev2021}.
+The first execution of the code will trigger Julia's just in time compiling,
+which is a bit slow, but the following runs will be fast.
+The following diagram lists possible combinations of input arguments, where graphs are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GraphTensorNetworks}.
+
+\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
+
 The code we will show below is a gist of how the above package is implemented, which is mainly for the pedagogical purpose.

### 2022-03-23 paper/paper.tex
Updates from Overleaf

@@
 We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-to compute various solution space properties of a class of combinatorial optimization problems that can be specified by local constraints.
-\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
+to compute various solution space properties of a class of combinatorial optimization problems on graphs that can be rephrased as satisfiability problems quantified over local sets of vertices, including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-Other hard graph problems solvable in our framework include the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
 To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the Overlap Gap Property on unit disk graphs and regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be local constraints over a vertex and its neighborhood,
-including the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the satisfiability problem,
+In graph theory and combinatorial optimization, there is an important class of problems that can rephrased as satisfiability problems quantified over local sets that typically consists of a vertex and its neighborhood,
+including the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the K-SAT problem,
 the maximal clique problem, and the vertex cover problem~\cite{Moore2011}.
@@
 %\blue{need more diversed applications not limited to IS}
-Many decision and counting properties of these problems are in general intractable at large sizes (exponential runetime in problem size in the worst case),
+Many decision and counting properties of these problems are in general intractable at large sizes (exponential run time in problem size in the worst case),
 but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
@@
 I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.\ counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard problem.
+In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.\ counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard combinatorial optimization problem.
 Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
@@
 %are many interesting and hard computational problems concerning various properties of independent sets.
-Solution space property computation allows us to understand the solution space better.
-With the counting of sets at different sizes, one can related the computational hardness with the counting of sets at different sizes~\cite{Xu2018}.
-With the configuration enumeration/sampling at a given size, one can measure the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019} better,
-while the configuration space connectivity also provides us an intuition about designing better classical or quantum algorithms.
+%Solution space property computation allows us to understand the solution space better.
+In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018}, and use pair-wise Hamming distance distribution of configurations at a given size to tell the presence or absence of the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019}, a no go theorem about when the solution space geometry is formidably hard for any local search algorithm.
+In a recent experiment of using Rydberg atom arrays to optimize the independent set problem~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for classical algorithms and design better quantum algorithms to solve these instances faster, and this experiment gives birth to the paper we are presenting.
 %\purple{I would give examples of why we want to compute solution space properties.
@@
 
-We propose to view the computation of all these properties from an abstract algebra perspective and use the unified framework of
+We give an algebraic interpretation of the computation of all these properties and use the unified framework of
 generic tensor-network to solve these seemingly unrelated properties all.
 %We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy~\cite{Harris2020}.
-It is composed of a set of labelled tensors, where the labels are used for specifying the contraction relation.
+Tensor network is a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}, which is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy~\cite{Harris2020}.
 The tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
@@
 %\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
-When using tensor network for solving one of the best solutions,
-the time complexity is the same as the dynamic programming algorithm~\cite{Courcelle1990, Fomin2013}.
-However, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
+Tensor network is very related to a well known computer programming method, the dynamic programming~\cite{Courcelle1990, Fomin2013}, like the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021} and they have the same time complexity related to the treewidth of a graph.
+However, while being more restrictive regarding the problem set it can solve, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
 %These two algorithms are related but are not equivalent.
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
-Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
-where we use a label in the subscript to represent a degree of freedom.
-One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
-Hence a tensor network can be represented as a open simple graph,
-where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
-In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
-The graphical representation of a generalized tensor network is a hypergraph, in which an edge (a label in subscript) can be shared by an arbitrary number of vertices (tensors).
-Although two notations are equivalent in representation power thought some transformation,
-the generalized tensor network might produce smaller contraction complexity,
+A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions to index tensor elements and an indicator of which tensor is the output, while the contraction of a tensor network is defined as a summation of products of tensor elements over the labels not appearing in the output tensor.
+e.g.
+the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are tensors, $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
+%can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
+%Generalized Einstein's notation is often used to represent a tensor network, where we use a label in the subscript to represent a degree of freedom.
+%One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
+% Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
+% where we use a label in the subscript to represent a degree of freedom.
+% One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
+% In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
+% Hence a tensor network can be represented as a open simple graph,
+% where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
+% In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
+The graphical representation of a generalized tensor network is an open hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
+As a reminder, our notation slightly generalizes the standard tensor network used in physics by not restricting how many times a label can appear in tensors, they are equivalent in representation power thought some transformation,
+but this generalized tensor network might produce smaller contraction complexity,
 which will be illustrated in \App{sec:tensorbad}.
@@
     W(x_v, w_v) = \left(\begin{matrix}
-        1_v \\
+        1 \\
         x_v^{w_v}
@@
 \end{figure}
+\purple{There are some other ideas I have to add to this...}
 The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving NP-hard combinatorial optimization problems.
@@
 
-\section{An example of contraction complexity increase due to introducing $\delta$ tensors}\label{sec:tensorbad}
-As we have mentioned in the main text,
-a standard tensor network notation is equivalent to the generalized tensor network by introducing $\delta$ tensors,
-where a $\delta$ tensor of rank $d$ is defined as
+\section{An example of contraction complexity increase due to using the standard tensor network notation}\label{sec:tensorbad}
+
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
+Hence a tensor network can be represented as a open simple graph, where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
+A standard tensor network notation is equivalent to the generalized tensor network by introducing $\delta$ tensors, where a $\delta$ tensor of rank $d$ is defined as
 \begin{equation}

### 2022-03-23 paper/paper.tex
fix the use of ratio

@@
 In particular, in \Fig{fig:hamming}, 
-we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lfloor (1-\text{ratio}) \times \alpha(G)\rfloor$ for each instance
+we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ for each instance
  and show the pairwise Hamming distance distribution for the enumerated configurations.
@@
 Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling~\cite{Ebadi2022}, this result is highly nontrivial.
-While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the ratio becomes small.
+While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the independent set sizes become large.
 This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?} and disconnected clusters exist in the configuration space for large independent sets.
@@
     \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
-    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lfloor(1-{\rm ratio}) \times \alpha(G)\rfloor$.
+    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
     In each plot, the $x$-axis is the Hamming distance normalized by the total number of vertices and the $y$-axis is the probability.

### 2022-03-23 paper/figures/plot.py

@@ -290,11 +290,11 @@ class PLT(object):
             r3 = np.loadtxt("data/grid-regular-size110d3-k3-alpha0.025-n10000.dat")
 
             gs = plt.GridSpec(8, 10)
-            ratios = [0.1, 0.05, 0.025]
+            ratios = [0.9, 0.95, 0.975]
 
             for i, d in enumerate([d1, d2, d3]):
                 ax = pl.fig.add_subplot(gs[i,0])
-                ax.text(0.75, 0.5, r"ratio = %s"%(ratios[i]), va="center", ha="right", fontsize=20, family="Times New Roman")
+                ax.text(0.0, 0.5, r"$\gamma = %s$"%(ratios[i]), va="center", ha="left", fontsize=20, family="Times New Roman")
                 ax.axis("off")
                 for seed in range(9):
                     ax = pl.fig.add_subplot(gs[i,1+seed])
@@ -307,7 +307,7 @@ class PLT(object):
 
             for i, d in enumerate([r1, r2, r3]):
                 ax = pl.fig.add_subplot(gs[i+4,0])
-                ax.text(0.75, 0.5, r"ratio = %s"%(ratios[i]), va="center", ha="right", fontsize=20, family="Times New Roman")
+                ax.text(0.0, 0.5, r"$\gamma = %s$"%(ratios[i]), va="center", ha="left", fontsize=20, family="Times New Roman")
                 ax.axis("off")
                 for seed in range(9):
                     ax = pl.fig.add_subplot(gs[i+4,1+seed])

### 2022-03-27 paper/paper.tex
Updates from Overleaf

@@
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the Overlap Gap Property on unit disk graphs and regular graphs, and visualizing the output of quantum optimization algorithms for the independent set problem.
+To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the Overlap Gap Property on unit disk graphs and regular graphs, and analyzing the performance of quantum and classical optimization algorithms for the independent set problem.
 \purple{I might not directly mention the classes of graphs we look at for Overlap Gap - it might be too much information.
-I'm not sure though, what do you think?} \blue{I agree ``King's graphs at 0.8 filling and 3-regular graphs'' is a bit too detailed, so I rephrased it as ``unit disk graphs and regular graphs'' that only conveys the most important information.} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the Overlap Gap Property on three regular graphs.
+I'm not sure though, what do you think?} \blue{I agree ``King's graphs at 0.8 filling and 3-regular graphs'' is a bit too detailed, so I rephrased it as ``unit disk graphs and regular graphs'' that only conveys the most important information.}\purple{What about just ``studying the Overlap Gap property'', no mention of what classes of graphs?
+Or studying the Overlap Gap property on different classes of graphs''} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the Overlap Gap Property on three regular graphs.
 %We show how our method helps to understand these hard problems on systems with hundreds of vertices.
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can rephrased as satisfiability problems quantified over local sets that typically consists of a vertex and its neighborhood,
+In graph theory and combinatorial optimization, there is an important class of problems that can rephrased as satisfiability problems of constraints specified over local sets of variables that typically consists of a vertex and its neighborhood, \blue{I still think the information of being local is important, because it best characterizes tensor networks.}
 including the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the K-SAT problem,
@@
 While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the independent set sizes become large.
-This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?} and disconnected clusters exist in the configuration space for large independent sets.
+This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?}\purple{The second thing is correct to say.
+I would just say that.} and disconnected clusters exist in the configuration space for large independent sets.
 We expect our numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
@@
 
-\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
-
+%\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
+\subsection{Analyzing quantum and classical algorithms for solving Maximum Independent Set}
 \begin{figure} 
@@
 \end{figure}
-\purple{There are some other ideas I have to add to this...}
-The ability to enumerate configurations can also be used to understand the distribution of outputs from algorithms for solving NP-hard combinatorial optimization problems.
-This can give detailed insights to performance of the algorithm, such as if the algorithm is likely to return independent sets from certain clusters of local or global minima in the solution space.
-As an example, we show in Figure~\ref{fig:exp_configuratoins} how our algorithm can be used to visualize experimental outputs of a quantum algorithm for solving the Maximum Independent Set problem using a programmable Rydberg atom array quantum computer~\cite{Ebadi2022}.
-The structure of the solution space for a King's graph with $39$ vertices and filling factor $\rho=0.8$ can be visualized on a graph where each vertex represents a large independent set, and each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition to the set.
-The algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-The algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested by~\cite{altshuler2010}\blue{Fix ref.},
-but samples from local minima with a wide range of Hamming distances from the MISs.
-Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
+The ability to enumerate configurations and compute independence polynomials was crucial in understanding the performance of quantum and classical algorithms for Maximum Independent Set in recent experiments~\cite{Ebadi2022}.
+We found that on King's graphs with $\rho=0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
+On the hardest graph instances for simulated annealing that we studied, a high density of local minima were present at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
+Initially, we suspected that simulated annealing was trapped certain clusters of these local minima in the solution space.
+However, by enumerating the configurations, we determined that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimal solution is found.
+Therefore, it is the large ratio of local to global minima that prevents simulated annealing from efficiently finding the MIS.
+%and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
+Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in Sec.~\ref{sec:overlap-gap}.
+Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, we were able to visualize the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for an instances with $39$ nodes~\cite{Ebadi2022}.
+Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
+Each edge represents a pair of  independent sets that differ by a swap operation or a vertex addition to the set, which are the operations naturally present in the effective dynamics at the end of the quantum algorithm.
+%The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
+\blue{We also get some unexpected discovery that the degrees of nodes in the configuration space is concentrated at a certain value, which is a feature not known before.}
+We find that the quantum algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested for adiabatic algorithms by~\cite{altshuler2010},
+but rather samples from local minima with a wide range of Hamming distances from the MISs.
+%Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
+Looking forward, these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
 

### 2022-03-30 paper/paper.tex
Updates from Overleaf

@@
 We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-to compute various solution space properties of a class of combinatorial optimization problems on graphs that can be rephrased as satisfiability problems quantified over local sets of vertices, including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.\purple{I still think there is a more concise way to word the class of combinatorial optimization problems this works on...}\blue{changed a bit, better?}
+to compute various solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
@@
 %By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
-By using generic programming techniques, %which require a program to work correctly for different input data types without sacrificing efficiency,
-the same simple-to-implement framework can be used to compute all of these properties.
+By using generic programming techniques, the same framework can be used to compute all of these properties.
 Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the Overlap Gap Property on unit disk graphs and regular graphs, and analyzing the performance of quantum and classical optimization algorithms for the independent set problem.
-\purple{I might not directly mention the classes of graphs we look at for Overlap Gap - it might be too much information.
-I'm not sure though, what do you think?} \blue{I agree ``King's graphs at 0.8 filling and 3-regular graphs'' is a bit too detailed, so I rephrased it as ``unit disk graphs and regular graphs'' that only conveys the most important information.}\purple{What about just ``studying the Overlap Gap property'', no mention of what classes of graphs?
-Or studying the Overlap Gap property on different classes of graphs''} % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the Overlap Gap Property on three regular graphs.
+To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on different classes of graphs, and analyzing the performance of quantum and classical optimization algorithms for the independent set problem.% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
 %We show how our method helps to understand these hard problems on systems with hundreds of vertices.
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can rephrased as satisfiability problems of constraints specified over local sets of variables that typically consists of a vertex and its neighborhood, \blue{I still think the information of being local is important, because it best characterizes tensor networks.}
-including the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the K-SAT problem,
+In graph theory and combinatorial optimization, there is an important class of problems that can be expressed as satisfiability problems involving constraints specified over %local sets of variables that typically consists of
+a vertex and its neighborhood.
+These include, for example, the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the K-SAT problem,
 the maximal clique problem, and the vertex cover problem~\cite{Moore2011}.
-%There is a widespread interest of these problem because they have wide range of applications in scheduling, logistics,
-%wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
+They have a wide range of applications in scheduling, logistics,
+wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
 %\blue{need more diversed applications not limited to IS}
-Many decision and counting properties of these problems are in general intractable at large sizes (exponential run time in problem size in the worst case),
-but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
-
-The most studied aspect of the above problems is finding an optimal solution, 
+The most studied aspect of these problems is to find an optimal solution, 
 %The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
@@
 %while many of them belong to the hardness category
-NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a polynomial time.
+NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a time polynomial with the size of the problem.
+
+% Many properties of these problems are in general intractable at large sizes (exponential run time in problem size in the worst case),
+ %but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
+
 %\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
@@
 I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-In this paper, we focus on the less studied problem of computing \textit{solution space properties}  which can be much harder, e.g.\ counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001}, but is crucial towards understanding a hard combinatorial optimization problem.
-Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum/minimum set size,
-but also include the number of sets at a give size, enumeration of all sets at a give size or direct sampling of such sets when they are not enumeratable.
-For the weighted version of the above problems, it also includes finding largest/smallest $k$ sets and their sizes.
+In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
+but they can be crucial towards understanding hard combinatorial optimization problems.
+Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum or minimum set size,
+but also include the number of sets at a give size, enumeration of all sets at a give size and direct sampling of such sets when they are too large to be fit into a memory.
+% For the weighted version of the above problems, it also includes finding the largest or smallest $k$ sets and their sizes.
 %are many interesting and hard computational problems concerning various properties of independent sets.
 %Solution space property computation allows us to understand the solution space better.
-In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018}, and use pair-wise Hamming distance distribution of configurations at a given size to tell the presence or absence of the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019}, a no go theorem about when the solution space geometry is formidably hard for any local search algorithm.
-In a recent experiment of using Rydberg atom arrays to optimize the independent set problem~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for classical algorithms and design better quantum algorithms to solve these instances faster, and this experiment gives birth to the paper we are presenting.
+It can be used to understand the hardness of finding one optimal solution for a problem instance and how well a solver performs in solving that instance.
+For example, the number of configurations at different sizes can tell how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
+%In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018},
+The pair-wise Hamming distance distribution of configurations at a given size can indicate %to tell the
+the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local search algorithms.
+%a no-go theorem about when the solution space geometry is formidably
+%hard for any local search algorithm.
+In a recent experiment based on a Rydberg atom array quantum simulator, the authors use the counting and the configuration space connectivity information to find maximum independent set (MIS) problem instances that are hard for simulated annealing \cite{Ebadi2022}.
+% In a recent experiment using a Rydberg atom array quantum simulator to find maximum independent sets (MIS) of a graph~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for simulated annealing.
+%and design better quantum algorithms
+%to solve these instances faster, 
+The need to understand this experiment motivates us to find methodologies to compute these solution space properties.
 %\purple{I would give examples of why we want to compute solution space properties.
@@
 
-We give an algebraic interpretation of the computation of all these properties and use the unified framework of
-generic tensor-network to solve these seemingly unrelated properties all.
-%We map the computation of these properties into generic tensor network contraction with specially designed tensor element algebra.
-Tensor network is a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}, which is also known as the sum product network in probabilistic modeling~\cite{Bishop2006} or einsum in linear algebra libraries such as numpy~\cite{Harris2020}.
-The tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
-We extend this concept to generic tensor network by generalizing the tensor element type to any type being a commutative semiring.
-Given a good contraction order, the space required to contract a tensor network is
-two to the power of the treewidth of its line graph~\cite{Markov2008}.
+We show how to solve all of these seemingly unrelated properties in a unified framework of generic tensor networks.
+Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}.
+They are also known as the sum-product networks in probabilistic modeling~\cite{Bishop2006} or \texttt{einsum} in linear algebra libraries such as NumPy~\cite{Harris2020}.
 %\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
-Recent progress in simulating quantum circuits with random tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to find such a good contraction order for a tensor network with thousands of tensors in a reasonable time using heuristic (inexact) methods.
+Recent progress in simulating quantum circuits with tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to contract a randomly structured sparse tensor network with up to thousands of tensors in a reasonable time.
 %\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
-Tensor network is very related to a well known computer programming method, the dynamic programming~\cite{Courcelle1990, Fomin2013}, like the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021} and they have the same time complexity related to the treewidth of a graph.
-However, while being more restrictive regarding the problem set it can solve, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
+In previous studies, the tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
+We extend this concept to generic tensor networks by generalizing the tensor element type to any type that has the algebraic structure of a commutative semiring.
 %These two algorithms are related but are not equivalent.
@@
 %Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
-%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
+%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
 %However, there is a lack of general and versatile tool to compute these different properties of independent sets.
 
-To avoid the discussion being unnecessarily diverged, we mainly focus on the independent set problem,
-and discuss other combinatorial optimization problems,
-including the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem and the maximal clique problem, in \App{sec:otherproblems}.
+To keep the discussion focused,
+%To avoid the discussion being unnecessarily diverged,
+we mainly study the independent set problem in the main text, and show how to solve other combinatorial optimization problems in  \App{sec:otherproblems},
+which include the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem, and the maximal clique problem.
 %\xpurple{More details on which combinatorial optimization problems this applies to?}
@@
 We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
-Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}
-and show how to engineer the element types in \Sec{sec:counting}, \Sec{sec:enumeration} and \Sec{sec:weighted} to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs.
+Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}.
+Subsequently, we explain how to engineer the element types to compute various solution space properties in \Sec{sec:counting}, \Sec{sec:enumeration} and \Sec{sec:weighted}.
+% to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs, respectively.
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three examples in \Sec{sec:examples} to demonstrate the versatility of our tool.
+Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
 %In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
@@
 %In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of Overlap Gap Property in King's graph and the existence of Overlap Gap properties in three regular graphs.
+We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
 %In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions to index tensor elements and an indicator of which tensor is the output, while the contraction of a tensor network is defined as a summation of products of tensor elements over the labels not appearing in the output tensor.
-e.g.
-the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are tensors, $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
+A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions and an indicator of which tensor is the output.
+The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of products of tensor elements over the labels not appearing in the output tensor.
+For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are tensors, $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
 %can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
@@
 % In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
-The graphical representation of a generalized tensor network is an open hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
-As a reminder, our notation slightly generalizes the standard tensor network used in physics by not restricting how many times a label can appear in tensors, they are equivalent in representation power thought some transformation,
-but this generalized tensor network might produce smaller contraction complexity,
-which will be illustrated in \App{sec:tensorbad}.
+The graphical representation of a tensor network is a open (meaning a hyperedge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
+Our notation slightly generalizes the standard tensor network used in physics by not restricting how many times a label can appear in tensors. 
+While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \App{sec:tensorbad}.
 % because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
@@
 \section{Generic programming tensor contractions}\label{sec:generic}
-\purple{On a second read of this
-section, I think that the clarity could be improved. My understanding is this is the flow:
-We would like to use generic programming, where we write code that works regardless
-of input type, and is optimized on all input types without sacrificing efficiency. In
-general, we can write code such that a function runs correctly regardless of the input
-data type. This is easy to do for dynamically typed languages like Python, which only
-verify and enforce the rules for the input data type at run time (called type-checking).
-However, when the input data type is only checked at run time (as opposed to when the
-code is compiled), type-specific optimization cannot be used. High efficiency is only
-achieved in statically typed languages, where modern compiling technology allows the
-function to be individually optimized for each input data type (then give C++/Julia
-examples).}\blue{how about now?}
+%\purple{On a second read of this section, I think that the clarity could be improved.
+My understanding is this is the flow: We would like to use generic programming, where we write code that works regardless of input type, and is optimized on all input types without sacrificing efficiency.
+In general, we can write code such that a function runs correctly regardless of the input data type.
+This is easy to do for dynamically typed languages like Python, which only verify and enforce the rules for the input data type at run time (called type-checking).
+However, when the input data type is only checked at run time (as opposed to when the code is compiled), type-specific optimization cannot be used.
+High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
 In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
@@
 %Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
-In fact, the elements in a tensor does not have to be a regular number type,
+However, the elements in a tensor do not have to be a regular number type,
  or even a field (since division is not used in tensor contraction).
-One can use the same tensor contraction program for different purposes with different tensor element types,
-and this idea of using the same program for different purposes is also called the generic programming in computer science:
+One can use the same tensor contraction program for different purposes with different tensor element types.
+This idea of using the same program for different purposes is also called the generic programming in computer science:
 
@@
 instead it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
-In such a way, when the program takes a matrix as an input, it computes the matrix power without extra efforts.
-The second aspect is about the efficiency. For dynamically typed languages, such as Python,
-one can easily write very general codes, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two numpy arrays with python objects as elements is much slower than statically typed languages such as C++ and Julia~\cite{Bezanson2012}.
+Then, when the program takes a matrix as an input instead of a standard number type, it computes the matrix power correctly without rewriting the program.
+The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type specific optimization at the compiling stage.
+Therefore, one can easily write code that works for general input types, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two NumPy arrays with Python objects as elements is much slower than statically typed (i.e.
+the type information is used in the compiling stage) languages such as C++ and Julia~\cite{Bezanson2012}.
 C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatch.
 When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.
-A myriad of optimizations can be done during the compilation, such as optimize the memory layout of immutable elements with fixed sizes in an array to speed up the array indexing.
-In Julia, arrays with immutable elements with fixed sizes can even be compiled to graphics processing units (GPU) for faster computation~\cite{Besard2018}.
-
-This motivates us to think about what is the most general tensor element type allowed in a tensor network contraction program.
-We find that, as long as the algebra of tensor elements forms a commutative semiring, the tensor network contraction will be doable and the result will be independent of the contraction order.
+A myriad of optimizations can be done during the compilation.
+For example, the compiler can optimize the memory layout of immutable elements with fixed sizes in an array to speed up the array indexing.
+In Julia, if a type is immutable and contains no references to other values, an array of that type can even be compiled to graphics processing units (GPU) for faster computation~\cite{Besard2018}.
+
+This motivates us to identify the most general tensor element type allowed in a tensor network contraction program.
+We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
 Here, a commutative semiring is a field without additive inverse and multiplicative inverse.
-Giving up these nice properties of a field means a lot to tensor computation: tensor network compression algorithms might be not applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014}, and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without additive inverse~\cite{Kerr1970}.
-But here, we only use the commutative properties of an algebra for the purpose of tensor network contraction orders optimization.
+Giving up these nice properties of  fields has significant implications for tensor computation: tensor network compression algorithms might be not applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014}, and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
+But here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
 To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
@@
 In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
-The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes those properties that can be computed by various tensor element types.
+The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which properties can be computed by which tensor element types.
 
@@
 This section is about reducing the independent set problem to a tensor network contraction problem.
-For people with physics background, we suggest using an alternative approach described in \App{sec:energymodel} to understand this reduction from an energy model.
-Let $G=(V,E)$ be a weighted undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
-An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, $(u, v) \not\in E$,
-and we denote the maximum independent set (MIS) size $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$. 
-We map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$ in a tensor network, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each label $s_v$, we defined a parametrized rank-one vertex tensor $W(x_v, w_v)$ as
-\begin{equation}
-    W(x_v, w_v) = \left(\begin{matrix}
+An alternative approach dedicated to physicists can be found in \App{sec:energymodel}, where we introduce the reduction from the energy model of hard core lattice gases~\cite{Dyre2016, Fernandes2007}.
+Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
+An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
+In its tensor network representation, a vertex $v\in V$ is mapped to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote this vertex is absent (present) in the set.
+For each label $s_v$, we defined a parametrized rank-one vertex tensor $W(x_v^{w_v})$ as
+\begin{equation}
+    W(x_v^{w_v}) = \left(\begin{matrix}
         1 \\
         x_v^{w_v}
-    \end{matrix}\right).\label{eq:vertextensor}
-\end{equation}
-where subscripts are used to annotate different vertices in configuration enumeration and sampling.
-One can index tensor elements by subscripting tensors, e.g.\ $W(x_v, w_v)_0=1_v$ is the first element associated with $s_v=0$ and $W(x_v, w_v)_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
+    \end{matrix}\right),\label{eq:vertextensor}
+\end{equation}
+where $x_v$ is a variable associated with vertex $v$.
+Tensor elements can be indexed by subscripts, e.g.\ $W(x_v^{w_v})_0=1$ is the first element associated with $s_v=0$ and $W(x_v^{w_v})_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
 Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
 \end{equation}
-The corresponding tensor network contraction gives
+The corresponding tensor network contraction is defined as
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W(x_v, w_v)_{s_v} \prod\limits_{(w,v) \in E} B_{s_w s_v},
+    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W(x_v^{w_v})_{s_v} \prod\limits_{(u,v) \in E} B_{s_u s_v},
 \end{equation}
 where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$.
-The edge tensor element $B_{s_{i}=1, s_{j}=1} = 0$ encodes the independent set constraint, meaning vertex $i$ and $j$ cannot be both in the independent set if they are connected by an edge $(i,j)$.
+An edge tensor element $B_{s_us_v}$ encodes the independent set constraint, which zero out the product whenever $u$ and $v$ are both in the independent set.
+While a vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ if the vertex $v$ is in the independent set.
 
@@
         \node[dot=\wr, color=black] at (\x+\dx,\y) (w\v) {};
-        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W(x_\v, w_\v)$}};
+        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W(x_\v^{w_\v})$}};
     }
@@
 and a hyperedge in red color to represent a degree of freedom $s_b$.
-Tensors sharing a same degree of freedom are connected by that hyperedge.
-The contraction of this tensor network can be evaluated manually:
+Tensors sharing a same degree of freedom are connected by a same hyperedge.
+The contraction of this tensor network has the following form:
 \begin{equation}
@@
 %\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
-The standard approach to evaluate a random tensor network is: first find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
-An optimal tensor network contraction order corresponds to an optimal tree decomposition of its line graph and the largest intermediate tensor has a rank equal to the tree width of this optimal tree decomposition~\cite{Markov2008}.
+The standard approach to evaluate a randomly structured tensor network is: first find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
+An optimal tensor network contraction order corresponds to an optimal tree decomposition of its line graph (here it is equivalent to the graph this tensor mapped from) and the largest intermediate tensor has a rank equal to the tree width of this optimal tree decomposition~\cite{Markov2008}.
 In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
-However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic contraction order finding algorithm~\cite{Kourtis2019,Kalachev2021} utilizing the associativity and commutativity of tensor contraction.
+However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic algorithm~\cite{Kourtis2019,Kalachev2021}.
 %The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
 For large scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.
-loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom, which might have a smaller space complexity.
+loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom.
 
 \begin{example}\label{eg:tensorcontraction}
-In the following, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
+In the following, we map a 5-vertex graph (left) to a tensor network (right), and show how the contraction order reduces the time and space complexities.
 
@@
     \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-        \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v, w_\v)$};
+        \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v^{w_\v})$};
     \draw [cyan,thick] (a) -- (aa);
@@
 % \end{align*}}
-The contraction process goes from bottom to top, where the root stores the contraction result that we want, the leaves are tensors in our tensor network while the rest nodes are all intermediate contraction results.
+The contraction process goes from bottom to top, where the root node stores the contraction result, the leaves are input tensors and the rest nodes are all intermediate contraction results.
 Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
@@
 One can easily check the largest tensor during computing has space complexity $O(n^2)$ and this is optimal, i.e.
-the treewidth of the original $5$-vertex graph is $2$, and the time complexity is $O(n^3)$, which is much smaller than that of direct enumeration $O(n^5)$.
+the treewidth of the original $5$-vertex graph is $2$.
+The time complexity is $O(n^3)$, which is much smaller than that of direct enumeration $O(n^5)$.
 \end{example}
@@
 \section{Independence polynomial}\label{sec:indpoly}
-Let $x_i = x$ and $w_i = 1$, the evaluation of \Eq{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}.
-which is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-The independence polynomial is an important graph polynomial that contains the counting information of independent sets. It is defined as
+Let $x_i = x$ and $w_i = 1$, \Eq{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
 \begin{equation}\label{eq:idpdef}
@@
 \end{equation}
-where $a_k$ is the number of independent sets of size $k$ in graph $G=(V,E)$. The total number of independent sets is thus equal to $I(G, 1)$.
-Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly by contracting this tensor network.
+where $a_k$ is the number of independent sets of size $k$, $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$ is the size of an MIS or the independence number.
+An independence polynomial is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
+%Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
+%and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
+By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly by contracting this tensor network, e.g.
+the total number of independent sets is equal to $I(G, 1)$.
 However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
-To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x, 1)$ and $B$ from integers and floating point numbers to the additive identity,
+To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity,
 $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
@@
 use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}
-Let us create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, so, e.g., $x$ is represented as $(0, 1)$.
-We define the algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ as
+Then we create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, e.g.
+$x$ is represented as $(0, 1)$.
+The algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
 \begin{equation}
@@
 \end{equation}
-Here, the multiplication operation can be evaluated in time $O(k\log(k))$, where $k=\max{k_a, k_b}$, using the convolution theorem~\cite{Schonhage1971}.
-These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
+Here, the multiplication of two polynomial numbers can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
+%These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
 \begin{equation}
@@
 One may argue that one can first evaluate this polynomial at different $x$ being a real number,
-and then apply the Gaussian elimination to fit the coefficients of this polynomial.
-This seemingly more time and space efficient approach suffers from severe issues in practise.
+and then apply the Gaussian elimination procedure to fit the coefficients of this polynomial.
+This seemingly more time and space efficient approach suffers from precision issues in practise.
 The data ranges of standard integer types are too small to cover many practical using cases,
-while the floating point numbers may have round off error that much larger than the value itself
-due to the fact that the number of sets at different sizes may vary tens or even hundreds of orders and this makes the small coefficients can not be retrieved correctly by fitting.
-For the purpose of evaluating these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by fitting it in a finite field.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial more time efficiently with complex numbers with controllable round off errors.
+while the floating point numbers may have round off error that much larger than the value itself.
+These are due to the fact that the number of independent sets at different sizes may vary tens or even hundreds of orders.
+For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by contracting and fitting with finite field algebra.
+Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round off errors.
 For the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
-The MIS size $\alpha(G)$, or the independence number is an important graph characteristics.
-The method we use to compute this quantity is based on the following observations.
+%The method we use to count the MISs is based on the following observations:
 Let $x=\infty$, the independence polynomial in the previous section becomes
@@
 \end{equation}
-where all terms except the largest order vanish.
+where all terms except the one with the largest order vanish.
 We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
@@
 \end{equation}
-Algebra \Eq{eq:tropical} and \Eq{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to calculate and count spin glass ground states.
+Algebra \Eq{eq:tropical} and \Eq{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.
 For independent set calculations here, the vertex tensor and edge tensor becomes:
@@
 This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
-Similarly, one can also truncate the polynomial and keep only its smallest several orders,
-which can be used for e.g. counting the maximal independent sets with smallest cardinality,
-where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence constraint.
+Similarly, one can also truncate the polynomial and keep only its smallest several orders.
+It can be used, for example, to count the maximal independent sets with smallest cardinality, where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence constraint.
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
@@
 for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
-Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables can carry labels, so that in the output polynomials, one can read out all independent sets directly.
+Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
 The multiplication between labelled variables are commutative while the summation of labelled variables forms a set.
-Intuitively, one can use a bit string as the representation of a labelled variable and use bit-wise or $\lor^\circ$ as the multiplication operation,
-e.g. in a 5-vertex graph, $x_2$ can be represented as $01000$, $x_5$ can be represented as $00001$ and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
-To enumerate all independent sets, we designed an algebra defined on sets of bit strings:
+Intuitively, one can use a bit string as the representation of a labelled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
+For example, in a 5-vertex graph, $x_2$ and $x_5$ can be represented as $01000$ and $00001$ respectively and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
+To enumerate all independent sets, we designed an algebra on sets of bit strings:
 \begin{equation}
@@
     \mymathbb{0} &= \{\}\\
-    \mymathbb{1} &= \{0^{\otimes |V|}\}.
+    \mymathbb{1} &= \{0^{\otimes |V|}\},
 \end{split}\label{eq:set}
@@
 
-To enumerate all independent sets, 
-we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
+To enumerate all independent sets,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
 The vertex and edge tensors are thus
@@
 
-This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs,
-or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
-As long as the coefficients in a truncated polynomial forms a commutative semiring, the polynomial itself is still a commutative semiring.
-For example, to enumerate only the MISs, with the tropical algebra, we can define $s_{k}\infty^k$,
-where the coefficients follow the algebra in \Eq{eq:set} and the orders (exponents) follow the max-plus tropical algebra.
+This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs, or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
+As long as the coefficients in a truncated polynomial are members of a commutative semiring, the polynomial itself is a commutative semiring.
+For example, to enumerate only the MISs we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Eq{eq:set} and the exponents follow the max-plus tropical algebra.
 The combined operations become: 
@@
 \begin{equation}
-    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\infty^1\}) = \left(\begin{matrix}
+    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\}\infty^1) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
 \end{equation}
-The contraction of the corresponding tensor network yields an enumeration of all MIS configurations.
-Direct implementing this algebra for configuration MISs might incur significant space overheads for keeping too many intermediate states not contributing to the final maximum independent sets,
-one can avoid this issue by using the bounding technique in \App{sec:bounding}.
-One may also be interested in a more studied enumeration of maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988}.
-It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure for the maximal independent set problem.
-
-If one is interested in obtaining only a single MIS configuration, one can just keep a single configuration in the intermediate computations to save the computational effort.
-Here is a new algebra defined on the bit strings, replacing the sets of bit strings in \Eq{eq:set},
+The enumeration of all MIS configurations corresponds to the contraction of this tensor network.
+However, direct contraction might incur significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
+This issue can be avoided by using the bounding technique in \App{sec:bounding}.
+One may also be interested in a more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
+We will discuss this issue in \App{sec:maximal} since it requires using a different tensor network structure for the maximal independent set problem.
+
+If one is interested in obtaining only a single MIS configuration, he can just keep one configuration in each tensor element to save the computational effort.
+By replacing the sets of bit strings in \Eq{eq:set} with a single bit string, we have the following algebra
 
@@
     \mymathbb{0} &= 1^{\otimes |V|}, \\
-    \mymathbb{1} &= 0^{\otimes |V|},
+    \mymathbb{1} &= 0^{\otimes |V|}.
 \end{split}\label{eq:singleconfig}
 \end{equation}
-where the \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria to make the algebra commutative and associative, e.g.
-by picking the one with a smaller integer value.
-In practise, it is completely fine to pick a random one (not commutative anymore) to generate a random MIS.
+The \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria.
+It can be picking the one smaller in the lexicographical order such that the addition operation is commutative and associative.
+In most cases, it is completely fine for the \texttt{select} function to pick a random one (not commutative and associative anymore) to generate a random MIS.
 
 \subsection{Sampling extremely large configuration space}
-When the graph size goes large, a set of configurations might be impossible to fit into any type of storage.
-To get something meaningful out of configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.
+When the problem scale goes large, a set of configurations might be impossible to fit into any type of storage.
+To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.
 instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
-A node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of
-\texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node,
-$left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
+Each node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of \texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node, and $left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
 
@@
 
-This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms, rather than their storages.
-Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial so that one can have such trees for independent sets with largest several sizes.
-Although one probably can not enumerate all configurations represented by a sum-product expression tree due to its extremely large size,
-he can draw unbiased samples from it efficiently.
-One starts from the root node, and descends this tree recursively to its left or right sibling with probability decided by the size of each sub-tree while doing the computation specified by the first field.
+This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms rather than their storage.
+Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with largest several sizes.
+Although one probably can not collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
+he can draw unbiased samples from it by direct sampling.
+The sampling program starts from the root node, and descends this tree recursively to the left and right siblings.
+If a node has type \texttt{SUM}, the program draws samples from the left and right siblings with a probability decided by the size of each sub-tree and returns the union of samples.
+Otherwise, if a node has type \texttt{PROD}, the program draws two sets of samples of equal sizes from its left and right siblings and returns the element-wise multiplication ($\lor^\circ$) of them.
 The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
@@
 \end{equation*}
-where siblings $A, B, C$ and $D$ can be any four types of nodes.
-It can be represented diagrammatically as the following.
+where sub-trees $A, B, C$ and $D$ can be any of the four types of nodes.
+This sum-product expression tree can be represented diagrammatically as the following.
 
@@
 
-The left and right sibling of root node have size $|A|\times |B|$ and $|C|+|D|$ respectively.
-Since the root node has type \texttt{SUM}, its size can be computed as $|A|\times |B| + |C|+|D|$.
-One can compute the sizes of $A, B, C$ and $D$ recursively until the program meets either a the \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$ respectively.
+The left and right siblings of the root node have sizes $|A|\times |B|$ and $|C|+|D|$ respectively, while the root node size can be computed as $|A|\times |B| + |C|+|D|$.
+The sizes of $A, B, C$ and $D$ can be computed recursively until the program meets either a \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$.
 \end{example}
@@
 \section{Weighted graphs}\label{sec:weighted}
-All the previous discussion for unweighted graphs still holds for integer weighted graphs,
-while for general weighted graphs, the independence polynomial is not well defined anymore.
-For general weighted graphs, we are more interested to know the $k$ most weighted sets and their sizes.
-Hence we define the extended tropical numbers as a natural generalization of tropical numbers:
+All the solution space properties and the corresponding algebra on unweighted graphs still holds for integer weighted graphs, while for general weighted graphs, the independence polynomial is not well defined anymore.
+For general weighted graphs, it is more useful to know the $k$ most weighted sets and their sizes.
+They can be computed by the extended tropical algebra, which is a natural generalization of the max-plus tropical algebra:
 
@@
 \end{equation}
-where $\texttt{largest}(s, k)$ means truncating the set by only keeping $k$ largest values in the set $s$.
-The computation of $s \odot t$ is a maximum sum combination problem which can be done in time $\sim k\log(k)$.
-One can find an efficient algorithm in \App{sec:maxsum}.
+where $\texttt{largest}(s, k)$ means truncating the set $s$ by only keeping its $k$ largest values.
+The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$.
+An efficient algorithm for computing the maximum sum combination problem can be found in \App{sec:maxsum}.
 The vertex tensor and edge tensor become
@@
 \end{equation}
-where we have used the relation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
-Similar to the tropical numbers, we can combine the extended tropical algebra with a bit string sampler (\Eq{eq:singleconfig}) for finding the configuration of each size.
-Since the $\odot$ operation of configuration sampler is not used, the resulting configurations are deterministic and complete.
+where we have used the equation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
+To find solutions corresponding largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Eq{eq:singleconfig}).
+Since the $\oplus$ operation of configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
 
 \section{Performance benchmarks}\label{sec:benchmark}
-We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz,
-and its CUDA version on a GPU Tesla V100-SXM2 16G.
+We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
 The results are summarized in Figure~\ref{fig:benchmark}.
-The graphs that we use in benchmarks are random three regular graphs,
- a typical type of sparse graphs that have a small treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
-In this benchmark, we do not include traditional algorithms for finding the MIS size such as the branching algorithms~\cite{Tarjan1977, Robson1986} or dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013},
-because to the best of our knowledge, most of the properties mentioned in this paper are not computable within these frameworks.
-The main goal of this section is to show the relative timing for computing different properties.
+The graphs in all benchmarks are random three regular graphs, which have treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
+The main goal of this section is to show the relative timing of computing different solution space properties.
 
@@
 
-Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes,
-where the space complexity is the same as the treewidth of the problem graph.
-Here, we assume our contraction order finding program has been converged to the optimal treewidth.
+Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
-In practice, slicing technique~\cite{Kalachev2021} is used for graphs with treewidth greater than 27 to fit the computation into a 16GB memory.
-One can see that all the computing times in figure~\ref{fig:benchmark}(b), (c) and (d) have a strong correlation with the treewidth,
-while in panel (d), the timing of certain computing tasks also strongly correlates with other factors like the configuration space size.
-Among these benchmarks, computational tasks with data types tropical number of on CPU and real and complex numbers on both CPU and GPU can utilize fast basic linear algebra subprograms (BLAS) functions to evaluate tensor contractions, hence
-are much faster comparing to non-BLAS element types in the same category.
-GPU computes much faster than CPU in all cases when the problem scale is large enough such that the actual computing time is comparable or larger than the launching overhead of CUDA kernels.
-Most algebras can be computed on a GPU, except those requiring dynamic sized structures, i.e.\ types with algebra defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr}.
+If we assume our contraction order finding program has been converged to the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
+Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
+One can see that all the computing times in figure~\ref{fig:benchmark} (b), (c) and (d) have a strong correlation with the predicted time and space complexity.
+While in panel (d), the computing times of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
+Among these benchmarks, computational tasks with data types real numbers, complex numbers or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
+These tasks usually compute much faster than ones with other element types in the same category.
+Immutable data types with no reference other values can be compiled to GPU devices that runs much faster than CPU in all cases when the problem scale is big enough.
+These data types do not include those defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr} or a data type containing them as a part.
 In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
 but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
-In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space improves the performance for more than one order of magnitude in enumerating the MISs.
-Bounding can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
+In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one orders of magnitude in enumerating the MISs.
+The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
 
 \section{Example case studies} \label{sec:examples}
-In this section, we give a few examples where the different properties of independence sets are used.
+%In this section, we give a few examples where the different properties of independence sets are used.
 
 \subsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
-We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices with lattice dimensions $L \times L$.
-The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ square lattices are occupied with vertices  (Figure~\ref{fig:lattices}(b));
+We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
+The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (Figure~\ref{fig:lattices}(b));
 the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)).
 The number of independent sets for square lattice graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
-We computed the integer sequence for $L=38$ and $L=39$, which, to the best of our knowledge, is not known before.
-In the computation, we used the finite-field algebra for contracting arbitrarily high precision integer tensor networks.
-
-A theoretically interesting number that can be computed using the number of independent sets is the entropy constant for the hardcore lattice gases on these graphs, which can tell us thermal dynamic properties of these lattices at the high temperature limit.
-For the square lattice graphs, it is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
+We computed the integer sequence for $L=38$ and $L=39$, which is, to the best of our knowledge, not known before.
+In the computation, we used the finite-field algebra for contracting integer tensor networks with an arbitrarily high precision.
+
+A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can tell us thermal dynamic properties of hard core lattice gases at the high temperature limit.
+For the square lattice graphs, this number is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
 This quantity arises in statistical mechanics of hard-square lattice gases~\cite{Baxter1980, Pearce1988} and is used to understand phase transitions for these systems.
@@
 Interestingly, the variations due to different random instances are negligible for this entropy quantity.
+\blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
 
@@
 
-\subsection{The Overlap Gap Property\label{sec:overlap-gap}}
-With the tool to enumerate configurations, one can %try to 
-understand the structure of the independent set configuration space,
-such as the optimization landscape for finding the MISs.
-One of the known barriers for finding the MIS is the so-called Overlap Gap Property~\cite{Gamarnik2013, Gamarnik2019}.
-Intuitively, if the Overlap Gap Property is present, it means every two large independent sets either have a significant intersection or very small intersection;
+\subsection{The overlap gap property\label{sec:overlap-gap}}
+With the tool to enumerate or sample configurations, one can understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs.
+One of the known barriers for finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+If the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection;
 it implies that large independent sets are clustered together.
-\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{I suppose you want to justify the origin of ``ratio'', then it would great if you can explain it more clearly.
-However, explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
-This clustering property has been used to rigorously prove upper bounds on the performance of local algorithms~\cite{Gamarnik2013, Gamarnik2019}.
-It was shown that for finding MISs of $d$-regular graphs with $d$ and graph sizes both being large, there exists Overlap Gap Property~\cite{Rahman2017,Gamarnik2021}.
-However, it is not known whether for small $d$, e.g. $3$- regular graphs, this statement is still true.
-Here, we direct sample from the computed configurations of large independent sets to investigate the presence or absence of the Overlap Gap Property for some given graphs.
+\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{Explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
+This clustering property has been used to rigorously prove upper bounds on the performance of local search algorithms~\cite{Gamarnik2013, Gamarnik2019}.
+To investigate the overlap gap property, we compute pair-wise Hamming distance distributions of large independent sets as they are good indicators of the presence or absence of overlap gap properties.
+%Pair-wise Hamming distance distributions are good indicators of the overlap gap properties that a single peak in the distribution indicates the absence of Hamming distances.
 %We do not explore the full configurations space because the
-Because the number of configurations is too large to fit into storage, we use the compact sum-product expression tree representation to sample from independent sets of a given size. 
-We compare  nine randomly generated instances from two categories of graphs: King's graphs at $\rho = 0.8$ filling and $3$-regular graphs.% that we want to investigate.
+%With these samples, we can have a good estimation of the Hamming distance distributions. 
+We inspect two types of graphs that are particularly interesting, the King's graphs with defects and $3$-regular graphs. % that we want to investigate.
 %Each category contains nine randomly generated instances, due to the limitation of computing resources,
-Our method can sample from independent sets of King's graph up to $20\times 20$ ($320$ vertices) and the size of $3$-regular graphs are $110$.
-In particular, in \Fig{fig:hamming}, 
-we sample two sets of $10^4$ configurations from the ISs at sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ for each instance
- and show the pairwise Hamming distance distribution for the enumerated configurations.
-In \Fig{fig:hamming}(a), we observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs.
-Which is a clear evidence of the absence of the Overlap Gap Property in $0.8$ filling King's graph.
-Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling~\cite{Ebadi2022}, this result is highly nontrivial.
-While in \Fig{fig:hamming}(b), we observed the multiple peak structure in $3$-regular graphs as the independent set sizes become large.
-This indicates the presence of the Overlap Gap Property \blue{@Maddie, I am not sure if we can say ``indicates the presence of the Overlap Gap Property'' here because it is so different from the official definition of OGP, I want to change it to ``disconnected clusters exist in the configuration space for large independent sets, however, it requires further study to show whether 3-regular graphs have the overlap gap property or not.'', which one do you think is more correct?}\purple{The second thing is correct to say.
-I would just say that.} and disconnected clusters exist in the configuration space for large independent sets.
+It was known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Ebadi2022}, however, it is not clear whether the MIS problem defined on a randomly generated King's graph with defects can have the overlap gap property.
+It was known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, however, it is not known whether for small $d$, e.g.
+$3$-regular graphs, this statement remains true.
+We randomly generate $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
+At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to direct sample from the target configuration space.
+For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Fig{fig:hamming}.
+We observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs, indicating the absence of the overlap gap property in a random King's graph at $0.8$ filling.
+Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling, this result is highly nontrivial.
+We argue that the King's graphs with defects mapped from hard MIS instances might have a very small measure in the total defected King's graph space.
+Very different pair-wise Hamming distributions are shown in \Fig{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
+It indicates the existence of disconnected clusters in the configuration space of the MIS problem on $3$-regular graphs.
 We expect our numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
@@
 The ability to enumerate configurations and compute independence polynomials was crucial in understanding the performance of quantum and classical algorithms for Maximum Independent Set in recent experiments~\cite{Ebadi2022}.
-We found that on King's graphs with $\rho=0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
+We found that on King's graphs with $0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
 On the hardest graph instances for simulated annealing that we studied, a high density of local minima were present at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
@@
 %The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-\blue{We also get some unexpected discovery that the degrees of nodes in the configuration space is concentrated at a certain value, which is a feature not known before.}
+\blue{Mention the degrees of nodes in the configuration space is concentrated at a certain value, which is a feature not known before.}
 We find that the quantum algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested for adiabatic algorithms by~\cite{altshuler2010},
@@
 \section{Discussion and conclusion}
-In this paper, we introduce a method to use generic programming and tensor networks to compute a number of different solution space properties of certain classes of NP-hard combinatorial optimization problems.
+In this paper, we introduce using generic tensor networks to compute a number of different solution space properties of a certain class of NP-hard combinatorial optimization problems.
 % the maximum independent set problem.
-%, including the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
-For each solution space property, we design a commutative semiring algebra for the tensor element type.
-By using the same tensor network but replacing the tensor network elements with elements of different algebras, we can compute different solution space properties.
-This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
+%,
+These solution space properties include the best several solutions, the number of solution configurations of a given size, and the enumeration and sampling of solution configurations of a given size.
+For each solution space property, we compute it with the same tensor network by replacing the tensor elements with those having an algebra designed for it.
+% This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
 % such as the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
@@
 In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of Overlap Gap Property in King's graph and the existence of Overlap Gap properties in three regular graphs.
+We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
 In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
@@
 These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
+
+It is worth mentioning that a tensor network is very related to a well known computer programming method, the dynamic programming~\cite{Courcelle1990, Fomin2013}, like the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021} and they have the same time complexity related to the treewidth of a graph.
+However, while being more restrictive regarding the problem set it can solve, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
 %our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
-By adapting to the style of generic programming, we can implement all the algorithms without much effort.
-We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
-A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
+%By adapting to the style of generic programming, we can implement all the algorithms without much effort.
+
+The source code in Julia language for this paper can be found in our Github repository~\cite{GraphTensorNetworks}. 
+There is also a short introduction to this repository as well a gist to show how it works in the Appendix~\ref{sec:technical}.
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
@@
 \begin{equation}
-    W(\beta, w_i) = \left(\begin{matrix}
+    W(e^{\beta w_i}) = \left(\begin{matrix}
         1 \\
@@
 \begin{equation}
-    W(v) = \left(\begin{matrix}
+    W = \left(\begin{matrix}
         r_v\\
@@
 \begin{equation}
-    B(x, w_{uv}) = \left(\begin{matrix}
+    B(x^{w_{uv}}) = \left(\begin{matrix}
         0 & x^{w_{uv}} & x^{w_{uv}}\\

### 2022-03-31 paper/paper.tex
Updates from Overleaf

@@
 The enumeration of all MIS configurations corresponds to the contraction of this tensor network.
-However, direct contraction might incur significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
-This issue can be avoided by using the bounding technique in \App{sec:bounding}.
+However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
+We introduce the bounding technique in \App{sec:bounding} to avoid this issue.
 One may also be interested in a more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
-We will discuss this issue in \App{sec:maximal} since it requires using a different tensor network structure for the maximal independent set problem.
-
-If one is interested in obtaining only a single MIS configuration, he can just keep one configuration in each tensor element to save the computational effort.
+It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure.
+
+If one is interested in obtaining only one MIS configuration, he can just keep one configuration in each tensor element to save the computational effort.
 By replacing the sets of bit strings in \Eq{eq:set} with a single bit string, we have the following algebra
@@
 
-Let us characterize the independent set problem on graph $G=(V, E)$ as an energy model
+Let us characterize the independent set problem on graph $G=(V, E)$ as an energy model with two parts
 \begin{equation}\label{eq:eng}
-    \mathcal{E}(G, s) = -\sum_{i\in V(G)} w_i s_i + \infty \sum_{\langle i,j\rangle \in E(G)}s_i s_j
+    \mathcal{E}(G, s) = -\sum_{i\in V} w_i s_i + \infty \sum_{\langle i,j\rangle \in E}s_i s_j
 \end{equation}
 where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term associated with it.
-The first term is the energy that corresponds to the inverse of the independent set size and the second term describes the independence contraint.
-In physical systems, this contraint term usually corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hard core lattice model~\cite{Dyre2016, Fernandes2007}.
-Its partition function is defined as
+The first part corresponds to the negative independent set size and the second part describes the independence contraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hard core lattice model~\cite{Dyre2016, Fernandes2007}.
+The partition function is defined as
 \begin{equation}\label{eq:partition}
@@
 \end{equation}
-where $\mathcal{I}(G)$ is the set of independent sets of graph $G$.
-$\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size).
-$a(k)$ is the number of spin configurations with energy $-k$ (independent sets of size $k$).
-The partition function can be evaluated as a tensor network contraction,
-where the tensor network is constructed by placing a vertex tensor on each spin $i$
+where $\mathcal{I}(G)$ is the set of independent sets of graph $G$, $\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size), $a(k)$ is the number of spin configurations with energy $-k$ (independent sets of size $k$).
+The partition function can be expressed as a tensor network by placing a vertex tensor on each spin $i$
 \begin{equation}
@@
 where the $0$ in the bond tensor coming from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}.
-By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor},
-and by letting $w_i=1$, the second line of \Eq{eq:partition} is the independence polynomial.
+By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
+If we further let $w_i=1$, the second line of \Eq{eq:partition} is equivalent to the independence polynomial.
 
@@
 
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
-Hence a tensor network can be represented as a open simple graph, where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
-A standard tensor network notation is equivalent to the generalized tensor network by introducing $\delta$ tensors, where a $\delta$ tensor of rank $d$ is defined as
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice: either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
+Hence a tensor network can be represented as a open simple graph, where an input tensor is mapped to a vertex, a label shared by two input tensors is mapped to an edge and a label appears in the output tensor is mapped to an open edge.
+A standard tensor network notation is equivalent to the generalized tensor network in representation power.
+A generalized tensor network can be converted to a standard one by adding a $\delta$ tensors at each hyperedge, where a $\delta$ tensor of rank $d$ is defined as
 \begin{equation}
@@
 
-In the following, we are going to show introducing $\delta$ tensors might increase the contraction complexity of a tensor network.
+In the following example, we will show this conversion might increase the contraction complexity of a tensor network.
 Let us consider the following King's graph.
@@
 
-By mapping the independent set problem to a standard tensor network with $\delta$ tensors,
-we have the following graphical representation.
-
-\centerline{\begin{tikzpicture}
-    \def\r{0.08}
-    \def\a{0.1}
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}
-            \filldraw[fill=black] (\x,\y) circle [radius=\r];
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
-            \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
-            \draw [black,thick] (\x,\y) -- (\x,\y+1);
-            \draw [black,thick] (\y,\x) -- (\y+1,\x);
-        }
-    \foreach \x in {1,...,4}
-        \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
-            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
-            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
-            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
-        }
-    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
-                    post length=0mm,pre length=0mm}}
-    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
-\end{tikzpicture}}
-
-In this diagram, the circle on each vertex in the original graph is a $\delta$ tensor of rank $8$ or less.
-If we contract this tensor network in a naive column-wise order, the maximum intermediate tensor has rank $\sim3L$, requiring a storage of size $\approx 2^{3L}$.
-If we relax the restriction that each label must appears exactly twice, we have the following hypergraph representation of a generalized tensor network.
+The generalized tensor network for solving the MIS problem on this graph has the following hypergraph representation, where we use different colors to distinguish different hyperedges.
 
@@
 \end{tikzpicture}}
-Here, we use different colors to distinguish different hyperedges.
-A vertex tensor always has rank $1$ and is not shown here since it does not change the contraction complexity.
-If we contract this tensor network in the column-wise order, the maximum intermediate tensor rank is $\sim L$, which can be seen by counting the number of colors at the cut.
+Here, vertex tensors are not shown here because they can be absorbed into an edge tensor hence do not change the contraction complexity.
+If we contract this tensor network in the column-wise order, the maximum intermediate tensor has rank $\sim L$, which can be seen by counting the number of colors at the cut.
+
+By adding $\delta$ tensors to hyperedges, we have the standard tensor network represented as the following simple graph.
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.08}
+    \def\a{0.1}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
+                    post length=0mm,pre length=0mm}}
+    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
+\end{tikzpicture}}
+
+In this diagram,the additional $\delta$ tensors can have ranks upto $8$.
+If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e. the space complexity is $\approx 2^{3L}$.
 
@@
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-Since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of its complement graph, in the following,
-we limit our discussion to finding maximal independent sets.
-Let us denote the neighborhood of a vertex $v$ as $N(v)$ and the closed neighborhood of $v$ as $N[v] = N(v)\cup \{v\}$.
-A maximal independent set $I_m$ is an independent set where there does exist a vertex $v \in V$ such that $I_m \cap N[v]  = \emptyset$,
-i.e. an independent set that can not become a larger one by adding a new vertex.
-To characterize the maximal independence restriction, one can quantify over a local set $N[v]$ with a local tensor:
+In this section, we focus the discussion on the maximal independent sets problem since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of the complement of the graph.
+Let $G=(V,E)$ be a graph, we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
+A maximal independent set $I_m$ is an independent set that there does exist a vertex $v \in V$ such that $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.
+an independent set that can not become a larger one by adding a new vertex.
+To characterize the maximal independence restriction, we defined a tensor on each $\{v\}\cup N(v)$ as
 \begin{equation}\label{eq:maximal}
@@
 \end{equation}
-Intuitively, it means if all the neighbourhood vertices are not in $I_{m}$, i.e., $ s_1=s_2=\ldots=s_{|N(v)|}=0$, then $v$ should be in $I_{m}$ and contribute a factor $x_{v}$,
-otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
-As an example, for a vertex of degree 2, the resulting rank-3 tensor is
+It means if none of the neighbours of $v$ are in $I_{m}$ ($ s_1=s_2=\ldots=s_{|N(v)|}=0$), then $v$ must be in $I_{m}$ and contribute a factor $x_{v}$, otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
+For a vertex $v$ having degree 2, this tensor has the following form
 \begin{equation}
@@
 
-Let us consider the example in~\Sec{eg:tensorcontraction}: its corresponding tensor network structure for computing the maximal independent polynomial becomes
+Let us consider the graph in Example~\ref{eg:tensorcontraction}, the corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation.
 
@@
 
-One can see that the average rank of a tensor is increased.
-The computational complexity of this new tensor network contraction is often greater than the one for computing the independence polynomial.
-
+%The contraction complexity of this tensor network is often greater than the one for the independence set problem.
 By contracting this tensor network with generic element types,
 we can compute the maximal independent set properties such as the maximal independence polynomial and the enumeration of maximal independent sets.
-Similar to the independence polynomial, the maximal independence polynomial counts the number of maximal independent sets of various sizes~\cite{Hu2017}.
-%which can be helpful for understanding why the program for solving MIS can be trapped in a local minimum.
-Let $G=(V,E)$ be a graph, its maximal independence polynomial is defined as
+The maximal independence polynomial is defined as
 \begin{equation}
@@
 which to our knowledge, the best algorithm gives a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
+%If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
 %The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
 
-We show the benchmark of computing the maximal independent set properties in \Fig{fig:benchmark-maximal},
-including a comparison to the Bron-Kerbosch algorithm from Julia package Graphs~\cite{Graphs}.
-The treewidth of this tensor network is significantly larger, so benchmark with only a smaller graph size is feasible.
-The time for the tensor network approach and the Bron-Kerbosch approach to enumerate all maximal independent sets are comparable,
-while the tensor network does counting much more efficiently.
-Due to the memory limit, this Bron-Kerbosch algorithm is only feasible up to a graph size around $70$.
+We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
+including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
+\Fig{fig:benchmark-maximal} (a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independence set problem.
+In \Fig{fig:benchmark-maximal} (b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
-    \caption{Benchmark results for computing different properties of maximal independent sets on a random three regular graph with different tensor element types.
-    (a) treewidth versus the number of vertices for the benchmarked graphs. 
-    (b) The computing time for calculating the number of independent sets and enumerate all MISs.
+    \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
+    (a) time and space complexity of tensor network contraction. 
+    (b) The wall clock time for counting and enumeration of maximal ISs. The missing data is due to due to the memory limit.
     }
@@
 \subsection{Matching problem}
-A $k$-matching in a graph $G=(V,E)$ is a set of $k$ edges, no two of which have a vertex in common.
-We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network,
-where $1$ means this edge is in the set and $0$ otherwise.
-To characterize the matching, one can define a tensor of rank $d(v) = |N(v)|$ on vertex $v$
+A $k$-matching in a graph $G=(V,E)$ is a set of $k$ edges that no two of which have a vertex in common.
+We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
+To characterize the matching constraint, we define a tensor for each $N(v)=\{n_1, n_2,\ldots, n_{d(v)}\}$ as
 \begin{equation}
@@
 \end{equation}
-and a tensor of rank $1$ on the bond
-\begin{equation}
-    B(w_{\langle u,v \rangle})_{\langle u, v\rangle} = \begin{cases}
+and a tensor for each bond as
+\begin{equation}
+    B(x^{w_{\langle u,v \rangle}}_{\langle u,v\rangle})_{\langle u, v\rangle} = \begin{cases}
     1, & \langle u, v \rangle = 0 \\
@@
 \end{equation}
-where label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
-The vertex tensor specifies the constraint that a vertex cannot be shared by two edges in the matched set,
-while an edge tensor carries the weights as the target to optimize.
-Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction gives us the matching polynomial
+where a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
+$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set,
+and an edge tensor carries the weights.
+Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction corresponds to the matching polynomial
 \begin{equation}
@@
 \end{equation}
-where $k$ is the size of a matched edges set, and a coefficients $c_k$ is the number of $k$-matchings.
+where $k$ is the size of an edge set, and a coefficients $c_k$ is the number of $k$-matchings.
 
@@
 Let $G=(V,E)$ be a graph, a vertex coloring is an assignment of colors to each vertex $v\in V$ such that no edge connects two identically colored vertices. 
-In a $k$-coloring problem, the number of different colors can be used is limited to less or equal to $k$.
-Let us use the 3-coloring problem as an example to show how to characterize with local tensors.
-For each vertex $v \in V$, we associate a degree of freedom $c_v\in\{0,1,2\}$ to it.
-Then we define a vertex tensor labelled by it as
+In a $k$-coloring problem, the number of colors is limited to less or equal to $k$.
+Let us use the 3-coloring problem as an example to show how to reduce it to tensor contractions.
+We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
+Then we define a tensor labelled by $c_v$ for each vertex $v$ as
 \begin{equation}
@@
 \end{equation}
-where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations.
-For each edge $(u, v)$, we specify the constraint carrying a weight $w_{uv}$ on it by defining an edge tensor labelled by $(c_u, c_v)$ as
+and a bond tensor labelled by $(c_u, c_v) $ for each edge $(u, v) \in E$ as
 \begin{equation}
@@
         x^{w_{uv}} & x^{w_{uv}} & 0
-    \end{matrix}\right).
-\end{equation}
-The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
-Let $x^{w_{uv}} = x$, we have a graph polynomial,
-in which the $k$-th coefficient is the number of coloring with $k$ bonds satisfied.
+    \end{matrix}\right),
+\end{equation}
+where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations. $B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
+%The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
+Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$, we have a graph polynomial,
+in which the $k$-th coefficient is the number of coloring that $k$ bonds satisfy constraints.
 If a graph is colorable, the maximum order of this polynomial should be equal to the number of edges in this graph.
-Similarly, one can define the $k$-coloring problem on edges by defining the tensor network on the line graph of $G$.
+Similarly, one can define an edge coloring problem by defining the tensor network on the line graph of $G$.
 
@@
 In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
-which is also known as the boolean spin glass problem in statistic physics.
-Let $G=(V,E)$ be a graph, to reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-Then for each edge $(u,v)\in E$, we define an edge matrix labelled by $s_us_v$ as
-\begin{equation}
-    B(x, w_{uv}) = \left(\begin{matrix}
+which is also known as the spin glass problem in statistic physics.
+Let $G=(V,E)$ be a graph, we associate a weight $w_v$ to each $v\in V$.
+To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
+Then for each edge $(u,v)\in E$, we define an edge matrix labelled by $(s_u, s_v)$ as
+\begin{equation}
+    B(x^{w_{uv}}_u, x^{w_{uv}}_v) = \left(\begin{matrix}
         1 & x_{v}^{w_{uv}}\\
@@
 \end{equation}
-where variables $x_u$ and $x_v$ represents a cut on this edge or a domain wall in an spin glass.
+where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in an spin glass.
 Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$, we have a graph polynomial similar to previous ones,
-where its $k$th coefficient is two times the number of cuts with size $k$ (i.e. cutting $k$ edges).
+in which the $k$th coefficient is two times the number of cut configurations having size $k$ (i.e. cutting $k$ edges).
 
@@
 To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
-Then for each vertex $v\in V$ we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
-\begin{equation}
-T(x, w_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-    0_v & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
-    1_v & s_v=0,\\
-    x^{w_v} & \text{otherwise},
+Then for each vertex $v$ we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
+\begin{equation}
+T(x^{w_v}_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+    0 & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
+    1 & s_v=0,\\
+    x^{w_v}_v & \text{otherwise},
 \end{cases}
 \end{equation}
-where $w_v$ is the weight of vertex $v$.
-This tensor means if both $v$ and its neighbouring vertices are not in $D$, i.e., $s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$,
-this configuration is forbidden because $v$ is not adjacent to any member in the set.
+where $w_v$ is the weight associated with the vertex $v$.
+This tensor means a configurations having a closed neighborhood of $v$ not in $D$ ($s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$) can not be a dominating set.
 Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output.
-The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009},
-which is defined as
+The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009}
 \begin{equation}
@@
 The boolean satisfiability problem is the problem of determining if there exists an interpretation that satisfies a given boolean formula.
-One can specify a satisfiable problem in the conjuctive normal form (CNF): a conjuction of disjunctions of boolean literals,
-where a disjunction of boolean literals is also named a clause.
-To reduce the problem of solving CNF to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom (label) $s_a \in \{0, 1\}$,
-where 0 stands for variable $a$ having value \texttt{false} while 1 stands for having value \texttt{true}.
-Then we map a clause to a tensor. For example, the $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
+One can specify a satisfiable problem in the conjuctive normal form (CNF), i.e. a conjuction of clauses (or disjunctions of boolean literals).
+To reduce the problem of solving a CNF to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom $s_a \in \{0, 1\}$.
+$s_a = 0$ stands for variable $a$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
+Then we map a clause to a tensor. For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
 \begin{equation}
@@
 \end{equation}
-where a weight $w_k$ is associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
-If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
-Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments with $k$ clauses satisfied.
+where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
+%If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
+Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
 
@@
 Set packing is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-To solve the set packing problem, we can just remove the rank-2 restriction of the edge tensor in \Eq{eq:edgetensor}
+To solve the set packing problem, we generalize the edge tensor in \Eq{eq:edgetensor} as
 \begin{equation}
@@
 
-When we use the algebra in \Eq{eq:countingtropicalset} to enumerate all MIS configurations, we find that the program stores significantly more intermediate configurations than necessary and thus incur significant overheads in space.
-To speed up the computation and reduce space overhead, we bound the searching space using the information from the computation of the MIS size $\alpha(G)$.
-As shown in \Fig{fig:bounding}, (a) we first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
-(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean true to represent a tensor element having a contribution to the MIS (i.e.\ with a non-zero gradient) and boolean false otherwise.
-(c) Finally, we perform masked tensor network contraction (i.e.\ discarding the unnecessary intermediate configurations) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
-Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we compute these masks by back propagating the gradients.
+When using the algebra in \Eq{eq:countingtropicalset} to enumerate all MISs, the program often stores significantly more intermediate configurations than necessary.
+To reduce the space overhead, we will show how to bound the searching space using the MIS size $\alpha(G)$.
+The bounded contraction consists of three stages as shown in \Fig{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
+(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean \texttt{true} to represent a tensor element having contribution to the MIS and boolean \texttt{false} otherwise.
+(c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
+The crucial part is computing the masks in step (b).
+Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we can compute these masks by back propagating the gradients.
 To derive the back-propagation rule for tropical tensor contraction,
@@
 \end{equation}
-With this approach, we do not incur the linear overhead in space.
-However, because the independence polynomial coefficients can have a huge order-of-magnitude range, if we use floating point numbers in the computation, the round-off errors can be significant for the counting of large-size independent sets.
-In addition, the number could easily overflow if we use fixed-width integer types.
-The big integer type is also not a good option because big integers with varying width can be very slow and is incompatible with GPU devices.
-These problems can be solved by introducing a finite-field algebra $\text{GF}(p)$:
+Unlike using the polynomial numbers in \Eq{eq:polynomial},  the fitting approach does not have the linear overhead in space.
+However, since the independence polynomial coefficients can have a huge order-of-magnitude range, the round-off errors can be larger than the value itself when using floating point number in computation.
+%In addition, the number could easily overflow if we use fixed-width integer types.
+To avoid using the arbitrary precision number that can be very slow and is incompatible with GPU devices, we introduce the following finite-field algebra $\text{GF}(p)$ approach:
 \begin{equation}
@@
 \end{equation}
-With a finite-field algebra, we have the following observations:
+Regarding the finite-field algebra, we have the following observations:
 \begin{enumerate}
@@
 
-In section~\ref{sec:indpoly}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq}.
-Since the coefficients of the independence polynomial can range many orders of magnitude, the round-off errors in fitting can be significant if we use random floating point numbers for $x_{i}$.
-In the main text, we propose to use a finite field $\text{GF}(p)$ to circumvent integer overflow and round-off errors.
+In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
 One drawback of using finite field algebra is its matrix multiplication is less computational efficient compared with floating point matrix multiplication.
-Here, we give an alternative method based on discrete Fourier transform with controllable round off errors.
+Here, we show an alternative method with standard number types but with controllable round off errors.
 Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
@@
 Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision in low independent set size region by choosing $r<1$ or high independent set size region by choosing $r>1$.
+By choosing different $r$, one can obtain better precision for small $j$ by choosing $r<1$ or large $j$ by choosing $r>1$.
 
@@
 
-We computed the number of independent sets on square lattices and King's graphs
-with our generic tensor network contraction algorithm on GPUs.
+We computed the number of independent sets on square lattices and King's graphs with our generic tensor network contraction algorithm on GPUs.
 The tensor element type is finite-field algebra so that we can reach arbitrary precision.
-We also computed the independence polynomial exactly for these lattices which can be found in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repo}.
+We also computed the independence polynomial for these lattices up to size $30\times 30$ in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repository}.
 
@@
 Given two sets $A$ and $B$ of the same size $n$.
-It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $n\log(n)$.
-The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure which can can be much slower to manipulate than arrays.
-In the following, we show an algorithm that has roughly the same complexity (given the data range is not exponentially large)
-but does not need a heap.
+It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
+The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure that can can be much slower to manipulate than arrays.
+In the following, we show an algorithm with roughly the same complexity, but does not need a heap.
 This algorithm first sorts both $A$ and $B$, then use the bisection to find the $n$-th largest value in the sum combination.
@@
 in the sum combination of $A$ and $B$ in linear time.
+As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
 We summarize the algorithm as in Algorithm~\ref{alg:sumcombination}.
@@
 
-Function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by the item collection.
-Note in function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration,
-the total number of iterations must be smaller or equal to $2n$.
-Here for simplicity, we do not handle the $-\infty$s in $A$ and $B$ and the degeneracy in the sums.
-They need to be taken seriously in practical implementations.
+In this algorithm, function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by collecting the items to a set.
+Inside the function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration,
+the total number of iterations is upper bounded by $2n$.
+Here for simplicity, we do not handle the special element $-\infty$ in $A$ and $B$ and the potential degeneracy in the sums.
+It is nevertheless important to handle them properly in a practical implementation.
 

### 2022-03-31 paper/paper.tex
Updates from Overleaf

@@
 %We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
-We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-to compute various solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others.
+%We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
+We discuss computing solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others, where
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-We look at the independent set problem as an example, and show how to compute the size of the maximum independent set, count the number of independent sets of a given size, and enumerate/sample the independent sets of a given size.
+the solution space properties include finding one of the best solution, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
+We look at the independent set problem as an example, and show how all these solution space properties can be solved in a unified framework of generic programming tensor networks.
 %By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
-By using generic programming techniques, the same framework can be used to compute all of these properties.
-Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
+%By using generic programming techniques, the same framework can be used to compute all of these properties. 
+%Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for several hardcore gases on disordered lattices, studying the overlap gap property on different classes of graphs, and analyzing the performance of quantum and classical optimization algorithms for the independent set problem.% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
+To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
 %We show how our method helps to understand these hard problems on systems with hundreds of vertices.
@@
 A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions and an indicator of which tensor is the output.
-The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of products of tensor elements over the labels not appearing in the output tensor.
+The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
 For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are tensors, $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
@@
 % In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
-The graphical representation of a tensor network is a open (meaning a hyperedge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
+The graphical representation of a tensor network is an open (meaning an edge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
 Our notation slightly generalizes the standard tensor network used in physics by not restricting how many times a label can appear in tensors. 
@@
 High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
-In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017},
-the elements in the tensor networks are limited to standard number types such as floating point numbers and integers.
+In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017}, the elements types in the tensor networks are limited to standard number types such as floating point numbers and integers.
 %Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
-However, the elements in a tensor do not have to be a regular number type,
- or even a field (since division is not used in tensor contraction).
-One can use the same tensor contraction program for different purposes with different tensor element types.
+%However, the elements in a tensor do not have to be a regular number type, or even a field (since division is not used in tensor contraction).
+%One can use the same tensor contraction program for different purposes with different tensor element types.
+We propose to not restricting our imagination to standard number types, but to use a more general element type with certain algebraic property.
+With different element types, we can solve different problems within the same framework.
 This idea of using the same program for different purposes is also called the generic programming in computer science:
@@
 This definition of generic programming covers two major aspects: ``work in the most general setting'' and ``with out loss of efficiency''.
-By in the most general setting, we mean that a single program should work correctly for different input data types. For example, 
+By in the most general setting, we mean that a single program should work correctly for different input data types. 
 %\purple{I think the following paragraph could be clarified.
@@
 %To understand the first aspect on generality,
-suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
+For example, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
 One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
@@
 Then, when the program takes a matrix as an input instead of a standard number type, it computes the matrix power correctly without rewriting the program.
-The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type specific optimization at the compiling stage.
+The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type specific optimizations at the compiling stage.
 Therefore, one can easily write code that works for general input types, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two NumPy arrays with Python objects as elements is much slower than statically typed (i.e.
-the type information is used in the compiling stage) languages such as C++ and Julia~\cite{Bezanson2012}.
+the type information can be accessed at the compiling stage) languages such as C++ and Julia~\cite{Bezanson2012}.
 C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatch.
-When these languages ``see'' a new input type, the compiler can recompile the generic program for the new type.
-A myriad of optimizations can be done during the compilation.
-For example, the compiler can optimize the memory layout of immutable elements with fixed sizes in an array to speed up the array indexing.
+When these languages ``see'' a new input type, the compiler recompiles the generic program for the new type to generate efficient binary.
+A myriad of optimizations can be done during the compilation. For example, the compiler can optimize the memory layout of immutable elements with fixed sizes in an array to speed up array indexing.
 In Julia, if a type is immutable and contains no references to other values, an array of that type can even be compiled to graphics processing units (GPU) for faster computation~\cite{Besard2018}.
@@
 %We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
-In the following sections, we show how to compute a number of properties of independent sets by designing tensor element types as specific commutative semirings without changing the tensor network contraction program~\cite{Stepanov2014}.
+In the following sections, we will show how to compute a number of properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebras.
 The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which properties can be computed by which tensor element types.
@@
 
-    \caption{The the tensor network element types used in this work, while the purpose of these element types can be found in \Tbl{tbl:generictypes}.
-    The overlap between two algebra indicates that a new algebra can be created by combining those two types of algebra.
-``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.}
+    \caption{The the tensor network element types used in this work and their relationships.
+    The overlap between two ellipses indicates that a new algebra can be created by combining those two algebras.
+``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.
+    The purposes of these element types can be found in \Tbl{tbl:generictypes}.}
      \label{fig:venn-diagram}
@@
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-In its tensor network representation, a vertex $v\in V$ is mapped to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote this vertex is absent (present) in the set.
-For each label $s_v$, we defined a parametrized rank-one vertex tensor $W(x_v^{w_v})$ as
+To reduce the independent set problem on $G$ to a tensor network contraction, we first map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex absent (present) in the set.
+For each vertex $v$, we defined a parameterized rank-one tensor indexed by $s_v$ as
 \begin{equation}
@@
 \end{equation}
-where $x_v$ is a variable associated with vertex $v$.
+where $x_v$ is a variable associated with $v$.
 Tensor elements can be indexed by subscripts, e.g.\ $W(x_v^{w_v})_0=1$ is the first element associated with $s_v=0$ and $W(x_v^{w_v})_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
-Similarly, on each edge $(u, v)$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
+Similarly, for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
 \begin{equation}
@@
 \end{equation}
-where the summation runs over all vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$.
-An edge tensor element $B_{s_us_v}$ encodes the independent set constraint, which zero out the product whenever $u$ and $v$ are both in the independent set.
-While a vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ if the vertex $v$ is in the independent set.
+where the summation runs over all $2^{|V|}$ vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$.
+It is easy to see an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
+Meanwhile, a vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
 
@@
 
-In general, it is not computationally efficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
+For a general graph, it is computationally inefficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
 %\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
 The standard approach to evaluate a randomly structured tensor network is: first find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
-An optimal tensor network contraction order corresponds to an optimal tree decomposition of its line graph (here it is equivalent to the graph this tensor mapped from) and the largest intermediate tensor has a rank equal to the tree width of this optimal tree decomposition~\cite{Markov2008}.
+A contraction order of a tensor network corresponds to a tree decomposition of the line graph of its hypergraph representation and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
+An optimal (in terms of space complexity) contraction order corresponds to the tree decomposition with smallest width, i.e. the treewidth.
+Here, this line graph is equivalent to the graph this tensor network mapped from. 
 In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
-However, it is easy to find a close to optimal contraction order in typically a few minutes with a heuristic algorithm~\cite{Kourtis2019,Kalachev2021}.
+However, it is easy to find a close to optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019,Kalachev2021}.
 %The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
@@
 %,
-These solution space properties include the best several solutions, the number of solution configurations of a given size, and the enumeration and sampling of solution configurations of a given size.
+These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
 For each solution space property, we compute it with the same tensor network by replacing the tensor elements with those having an algebra designed for it.
@@
 The different data types introduced in the main text to compute these properties are  summarized in the diagram in \Fig{fig:venn-diagram}. %We go beyond using real numbers and use polyn
-Other than the case with real numbers, we have polynomials and truncated polynomials.
-We combine them with the bit string algebra, the set algebra, and sum-product expression tree algebra for finding, enumerating, and sampling of independent sets at a given size.
+The class of problems solvable by a tensor network include but is not limited to maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
+
+%Other than the case with real numbers, we have polynomials and truncated polynomials.
+%We combine them with the bit string algebra, the set algebra, and sum-product expression tree algebra for finding, enumerating, and sampling of independent sets at a given size.
 Three examples are shown to demonstrate how our method can be used to understand the solution space better.
-In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
+%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
 We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
-In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
+%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
 We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
-In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
+%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
 This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
-These algebras are of generic use: they can be utilized to compute properties of maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
-
-It is worth mentioning that a tensor network is very related to a well known computer programming method, the dynamic programming~\cite{Courcelle1990, Fomin2013}, like the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021} and they have the same time complexity related to the treewidth of a graph.
-However, while being more restrictive regarding the problem set it can solve, the tensor network has a richer algebraic structure, which crucially enables the computation of solution space properties beyond finding a single solution, which is not possible with dynamic programming.
+
+It would be interesting to generalize the idea of generic programming to other algorithms for property computing with certain algebraic structures such as those using the inclusion-exclusion principle or subset Onconvolution~\cite{Fomin2013}.
+To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013} that closely related to a tensor network.
+For example, the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021}.
+However, while being less restrictive regarding the problem it can solve, e.g.
+the traveling sales man can be solved easily with dynamic programming but not with a tensor network to the best of our knowledge, it is still an open question whether dynamic programming can have an algebraic interpretation for computing solution space properties beyond finding a single best solution or not.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
-We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
+We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to other scientific software.
+
+%We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
 
@@
 We acknowledge Sepehr Ebadi and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
-We thank Benjamin Schiffer for providing helpful feedback on the manuscript.
+We thank Benjamin Schiffer for providing helpful feedback on the writing of this manuscript.
 We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
@@
 
-\section{Technical guide}\label{sec:technical}
-
-This appendix covers some technical aspects of this paper, including an open source package and a gist about how to implement this package.
-If you are only interested in using, please checking our GitHub repository for an efficient and full featured implementation aimed for productively:
-\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
-One can install these packages by opening a Julia REPL, type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and type, e.g.
+\section{Technical guides}\label{sec:technical}
+
+This appendix covers some technical guides for productivity, including an introduction to an open source package \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and a gist about how this package is implemented.
+One can install \texttt{GraphTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
 \begin{lstlisting}
@@
 \end{lstlisting}
-
-To use it for solving solution space properties, just open a Julia REPL and type
+followed by an \colorbox{lightgray}{\texttt{<ENTER>}} key.
+To use it for solving solution space properties, just go back to the normal mode (type \colorbox{lightgray}{\texttt{<BACKSPACE>}}) and type
 
@@
 julia> using GraphTensorNetworks, Graphs
+
+julia> # using CUDA
 
@@
 Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
-If one wants to use GPU to accelerate the computation, statement ``\texttt{using CUDA}'' must be executed before calling the solve function.
-The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the key word argument \texttt{optimizer} is for tensor network optimization, the key word argument \texttt{weights} specifies the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} allows one to specify the degrees of freedom not summed over, i.e.
-returning a tensor rather than its sum.
-Here, we use \texttt{TreeSA} method in Ref.~\cite{Kalachev2021}.
-The first execution of the code will trigger Julia's just in time compiling,
-which is a bit slow, but the following runs will be fast.
-The following diagram lists possible combinations of input arguments, where graphs are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GraphTensorNetworks}.
+If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must uncommented.
+The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the key word argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the key word argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
+Here, we use \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} the default values.
+The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
+The first execution of this function will be a bit slow due to Julia's just in time compiling.
+After that, the subsequent runs will be fast.
+The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GraphTensorNetworks}.
 
@@
 It covers most of the topics in the paper without caring much about the performance.
-This project depends on multiple open source packages in the Julia ecosystem:
+It is worth mentioning that this project depends on multiple open source packages in the Julia ecosystem:
 
 \begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
-    \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
-	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication,
-	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a package providing graph utilities, like random regular graph generator,
-	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting,
-	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number generations.
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
+	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
+	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in Julia community.
+	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
+	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number manipulation.
 \end{description}
@@
 They can be installed in a similar way to \texttt{GraphTensorNetworks}.
-After installing the required packages, one can open a Julia REPL, then copy and paste the following code into it.
+After installing the required packages, one can open a Julia REPL, copy and paste the following code snippet into it.
 

### 2022-04-01 paper/paper.tex
Updates from Overleaf

@@
 %\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
-The standard approach to evaluate a randomly structured tensor network is: first find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
-A contraction order of a tensor network corresponds to a tree decomposition of the line graph of its hypergraph representation and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
-An optimal (in terms of space complexity) contraction order corresponds to the tree decomposition with smallest width, i.e. the treewidth.
-Here, this line graph is equivalent to the graph this tensor network mapped from. 
-In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth itself is NP-hard.
+The standard approach to evaluate a randomly structured tensor network is: find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
+Let us denote the line graph of the hypergraph representation of a tensor network as $G'$.
+A contraction order of this tensor network corresponds to a tree decomposition of $G'$ and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
+Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $G'$ with smallest width (or the treewidth ${\rm tw}(G')$).
+In the independent set problem, treewidth of $G'$ is the same to the treewidth of the graph this tensor network mapped from. 
+In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is well known NP-hard problem.
 However, it is easy to find a close to optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019,Kalachev2021}.
@@
 % \end{align*}}
-The contraction process goes from bottom to top, where the root node stores the contraction result, the leaves are input tensors and the rest nodes are all intermediate contraction results.
+The contraction process goes from bottom to top, where the root node stores the contraction result; the leaves are input tensors and the rest nodes are all intermediate contraction results.
 Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
-The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degrees of freedom, which in our case is $2$.
-One can easily check the largest tensor during computing has space complexity $O(n^2)$ and this is optimal, i.e.
+The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degree of freedoms, which is $2$ in a tensor network mapped from an independent set problem.
+One can easily check the largest tensor in contraction has space complexity $O(n^2)$ and this is the smallest over all possible contraction trees, i.e.
 the treewidth of the original $5$-vertex graph is $2$.
@@
 %and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly by contracting this tensor network, e.g.
-the total number of independent sets is equal to $I(G, 1)$.
-However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at each size.
-To achieve this, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity,
-$\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly using tensor network contraction.
+It is already very useful, for example, the total number of independent sets can be evaluated as $I(G, 1)$.
+However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
+To this end, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
 \purple{I'd
@@
 Here, the multiplication of two polynomial numbers can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
-%These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring. The tensors $W$ and $B$ can thus be written as 
+%These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring.
+The tensors $W$ and $B$ can thus be written as 
 \begin{equation}
@@
 These are due to the fact that the number of independent sets at different sizes may vary tens or even hundreds of orders.
-For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by contracting and fitting with finite field algebra.
+For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by contracting and fitting on finite field algebra.
 Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round off errors.
@@
 \subsection{Set algebra for configuration enumeration}
-The configuration enumeration of independent sets includes,
-for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
+The configuration enumeration of independent sets includes, for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
 Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.

### 2022-04-06 paper/paper.tex
Updates from Overleaf

@@
 However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
-To this end, let us first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
-\purple{I'd
-say that you're about to describe this semiring, otherwise it seems like you're going to
-use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}
-Then we create a polynomial type and represent a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, e.g.
+%first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+%\purple{I'd
+%say that you're about to describe this semiring, otherwise it seems like you're going to
+%use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}\purple{Perhaps start the sentence with: Our semiring elements are a polynomial type...}
+To this end, let us create a polynomial number data type by representing a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, e.g.
 $x$ is represented as $(0, 1)$.
-The algebra between the polynomials $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
+Then we can define an algebra among coefficient vectors, including a redefinition of additive identity and multiplicative identity.
+To avoid potential confusion, let us denote the additive identity as $\mymathbb{0}$, and multiplicative identity as $\mymathbb{1}$.
+The algebra between the polynomials number $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
 \begin{equation}
@@
 \subsection{Sampling extremely large configuration space}
-When the problem scale goes large, a set of configurations might be impossible to fit into any type of storage.
+When the problem scale goes large, a set of bitstrings might be impossible to fit into any type of storage.
 To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.
@@
 it implies that large independent sets are clustered together.
-\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{Explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
+%\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{Explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
 This clustering property has been used to rigorously prove upper bounds on the performance of local search algorithms~\cite{Gamarnik2013, Gamarnik2019}.
@@
 Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in Sec.~\ref{sec:overlap-gap}.
-Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, we were able to visualize the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for an instances with $39$ nodes~\cite{Ebadi2022}.
+
+Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, we were able to gain insight by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for an instances with $39$ nodes~\cite{Ebadi2022}.
 Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
@@
 %The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-\blue{Mention the degrees of nodes in the configuration space is concentrated at a certain value, which is a feature not known before.}
-We find that the quantum algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested for adiabatic algorithms by~\cite{altshuler2010},
-but rather samples from local minima with a wide range of Hamming distances from the MISs.
+The solution space graph is well-connected by local changes to the spin configurations, has small diameter, and the degree of each node appears to concentrate. 
+From this visualization, we see that the quantum algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested for adiabatic algorithms by~\cite{altshuler2010}, which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
+Rather, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
 %Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
@@
 
-It would be interesting to generalize the idea of generic programming to other algorithms for property computing with certain algebraic structures such as those using the inclusion-exclusion principle or subset Onconvolution~\cite{Fomin2013}.
-To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013} that closely related to a tensor network.
-For example, the Viterbi algorithm for finding most probable configuration in the hidden Markov model has a nice matrix product state interpretation~\cite{Han2018}, and the tropical tensor network is very likely equivalent to dynamic programming in solving hard combinatorial optimization problems in certain way~\cite{Liu2021}.
-However, while being less restrictive regarding the problem it can solve, e.g.
-the traveling sales man can be solved easily with dynamic programming but not with a tensor network to the best of our knowledge, it is still an open question whether dynamic programming can have an algebraic interpretation for computing solution space properties beyond finding a single best solution or not.
+It would be interesting to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and see what new properties can be computed.
+To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013}.
+Dynamic programming is closely related to a tropical tensor network~\cite{Liu2021}, for example, the Viterbi algorithm for finding the most probable configuration in a hidden Markov model can be interpreted as a matrix product state featured with tropical algebra, and the tropical tensor network in the main text is probably equivalent to dynamic programming in finding a best solution.
+However, while having broader applications,
+%e.g. the traveling sales man can be solved easily with dynamic programming but not with a tensor network to the best of our knowledge, 
+dynamic programming does not have a clear algebraic interpretation required by computing solution space properties beyond finding a best solution.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},

### 2022-04-11 paper/paper.tex
Updates from Overleaf

@@
 
-\title{Computing solution space properties by generic programming tensor networks
+\title{Computing solution space properties of combinatorial optimization problems by generic programming tensor networks
 \thanks{\funding{...}}
@@
 %We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-We discuss computing solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the maximal clique problem, the dominating set problem, and the satisfiability problem, among others, where
+We introduce a unified framework to compute the solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the clique problem, the dominating set problem, the set packing problem, the set covering problem, and the satisfiability problem.
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-the solution space properties include finding one of the best solution, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
-We look at the independent set problem as an example, and show how all these solution space properties can be solved in a unified framework of generic programming tensor networks.
+These solution space properties include, for example, finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
+We use the independent set problem as an example and show how all these solution space properties can be computed in the unified approach of generic programming tensor networks.
 %By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
@@
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate how our versatile tool helps to understand these hard problems, we apply it to a few examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
+To demonstrate the versatility of this computational tool, we apply it to a few examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
+% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
 %We show how our method helps to understand these hard problems on systems with hundreds of vertices.
@@
 \begin{keywords}
-solution space property, tensor network, maximum independent set, independence polynomial, generic programming
+solution space property, tensor network, maximum independent set, independence polynomial, generic programming, combinatorial optimization problems
 \end{keywords}
@@
 
-\cyan{a comment} and \xcyan{a resolved comment}
-
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be expressed as satisfiability problems involving constraints specified over %local sets of variables that typically consists of
-a vertex and its neighborhood.
-These include, for example, the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the vertex coloring problem, the K-SAT problem,
-the maximal clique problem, and the vertex cover problem~\cite{Moore2011}.
+In graph theory and combinatorial optimization, there is an important class of problems that can be expressed as satisfiability problems involving constraints specified over a vertex and its neighborhood.
+These include, for example, the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the set covering problem, the vertex coloring problem, the K-SAT problem, the clique problem, and the vertex cover problem~\cite{Moore2011}.
 They have a wide range of applications in scheduling, logistics,
-wireless networks and telecommunication, and computer vision, etc.~\cite{Butenko2003, Wu2015}.
-%\blue{need more diversed applications not limited to IS}
-The most studied aspect of these problems is to find an optimal solution, 
+wireless networks and telecommunication, computer vision, etc.~\cite{Butenko2003, Wu2015}.
+Finding an optimum solution for these problems is typically NP-hard~\cite{Hastad1996}, which implies it is unlikely to be solved in a time polynomial with the size of the problem.
+
+% The most studied aspect of these problems is to find an optimum solution, 
 %The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
-which is typically 
+% which is typically 
 %while many of them belong to the hardness category
-NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a time polynomial with the size of the problem.
+% NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a time polynomial with the size of the problem.
 
@@
 I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
-but they can be crucial towards understanding hard combinatorial optimization problems.
-Here, the \textit{solution space property} refers to a class of quantities that not only include the maximum or minimum set size,
-but also include the number of sets at a give size, enumeration of all sets at a give size and direct sampling of such sets when they are too large to be fit into a memory.
+
+In this paper, we introduce a unified framework to compute a broader class of quantities associated with these problems, beyond just finding an optimum solution.
+We call them \textit{solution space properties}, which can be much harder to compute (e.g.\ \#P-complete), but they can be crucial for understanding hard combinatorial optimization problems.
+% In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
+% but they can be crucial towards understanding hard combinatorial optimization problems. 
+These \textit{solution space properties} can include not only the maximum or minimum set size but also the number of sets at a given size, enumeration of all sets at a given size, and direct sampling of such sets when they are too large to be fit into memory.
 % For the weighted version of the above problems, it also includes finding the largest or smallest $k$ sets and their sizes.
@@
 %Solution space property computation allows us to understand the solution space better.
-It can be used to understand the hardness of finding one optimal solution for a problem instance and how well a solver performs in solving that instance.
-For example, the number of configurations at different sizes can tell how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
+They can be used to understand the hardness of finding an optimum solution for a problem instance and the performance of a solver in computing the solution for the given instance.
+For example, the number of configurations at different sizes can inform how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
 %In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018},
-The pair-wise Hamming distance distribution of configurations at a given size can indicate %to tell the
-the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local search algorithms.
+The pair-wise Hamming distance distribution of configurations at a given size can indicate the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local search algorithms.
 %a no-go theorem about when the solution space geometry is formidably
 %hard for any local search algorithm.
-In a recent experiment based on a Rydberg atom array quantum simulator, the authors use the counting and the configuration space connectivity information to find maximum independent set (MIS) problem instances that are hard for simulated annealing \cite{Ebadi2022}.
+In a recent experiment based on a Rydberg atom array quantum computer, the authors use the counting and the configuration space connectivity information to find maximum independent set (MIS) problem instances that are hard for simulated annealing \cite{Ebadi2022}.
 % In a recent experiment using a Rydberg atom array quantum simulator to find maximum independent sets (MIS) of a graph~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for simulated annealing.
@@
 
-We show how to solve all of these seemingly unrelated properties in a unified framework of generic tensor networks.
+With \textit{generic tensor networks}, we show how to solve all of these seemingly unrelated properties in a unified approach.
 Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}.
@@
 %\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
-Recent progress in simulating quantum circuits with tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} enables us to contract a randomly structured sparse tensor network with up to thousands of tensors in a reasonable time.
+Recent progress in simulating quantum circuits with tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} makes it possible to contract a randomly structured sparse tensor network with up to thousands of tensors in a reasonable time.
 %\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
-In previous studies, the tensor element types are typically restricted to standard number types such as real numbers and complex numbers.
-We extend this concept to generic tensor networks by generalizing the tensor element type to any type that has the algebraic structure of a commutative semiring.
+In previous studies, the data types of the tensor elements are typically restricted to standard number types such as real numbers and complex numbers.
+Here, we extend to \textit{generic tensor networks} by generalizing the tensor element data types to any type that has the algebraic structure of a commutative semiring.
 %These two algorithms are related but are not equivalent.
@@
 
-To keep the discussion focused,
-%To avoid the discussion being unnecessarily diverged,
-we mainly study the independent set problem in the main text, and show how to solve other combinatorial optimization problems in  \App{sec:otherproblems},
-which include the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem, and the maximal clique problem.
+To keep the discussion focused, we mainly study the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in  \App{sec:otherproblems}, which include the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem, the set covering problem, and the clique problem.
 %\xpurple{More details on which combinatorial optimization problems this applies to?}
@@
 Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}. 
-Subsequently, we explain how to engineer the element types to compute various solution space properties in \Sec{sec:counting}, \Sec{sec:enumeration} and \Sec{sec:weighted}.
+Subsequently, we explain how to engineer the element types to compute various solution space properties in \Sec{sec:counting}, \Sec{sec:enumeration}, and \Sec{sec:weighted}.
 % to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs, respectively.
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
+Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three example applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
 %In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions and an indicator of which tensor is the output.
+A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
 The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
-For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are tensors, $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
+For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are matrices (two-dimensional tensors), $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
 %can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
@@
 The graphical representation of a tensor network is an open (meaning an edge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
-Our notation slightly generalizes the standard tensor network used in physics by not restricting how many times a label can appear in tensors. 
+Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors. 
 While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \App{sec:tensorbad}.
@@
 High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
-In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017}, the elements types in the tensor networks are limited to standard number types such as floating point numbers and integers.
+In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
 %Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
@@
 %One can use the same tensor contraction program for different purposes with different tensor element types.
-We propose to not restricting our imagination to standard number types, but to use a more general element type with certain algebraic property.
-With different element types, we can solve different problems within the same framework.
-This idea of using the same program for different purposes is also called the generic programming in computer science:
+% We propose to not restricting our imagination to standard number types, but to use a more general element type with certain algebraic property.
+We propose to use more general element types with a certain algebraic property.
+With different data types, we can solve different problems within the same unified framework.
+This idea of using the same program for different purposes is also called generic programming in computer science:
 
@@
 \end{definition}
-This definition of generic programming covers two major aspects: ``work in the most general setting'' and ``with out loss of efficiency''.
-By in the most general setting, we mean that a single program should work correctly for different input data types. 
+This definition of generic programming covers two major aspects: ``work in the most general setting'' and ``without loss of efficiency''.
+By the most general setting, we mean that a single program should work correctly for the most general input data types. 
 %\purple{I think the following paragraph could be clarified.
@@
 One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
-Generic programming does not require $x$ to be a standard number type,
-instead it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
+Generic programming does not require $x$ to be a standard number type;
+instead, it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
 Then, when the program takes a matrix as an input instead of a standard number type, it computes the matrix power correctly without rewriting the program.
-The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type specific optimizations at the compiling stage.
+The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type-specific optimizations at the compilation stage.
 Therefore, one can easily write code that works for general input types, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two NumPy arrays with Python objects as elements is much slower than statically typed (i.e.
-the type information can be accessed at the compiling stage) languages such as C++ and Julia~\cite{Bezanson2012}.
-C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatch.
-When these languages ``see'' a new input type, the compiler recompiles the generic program for the new type to generate efficient binary.
+the type information can be accessed at the compilation stage) languages such as C++ and Julia~\cite{Bezanson2012}.
+C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatches.
+When these languages ``see'' a new input type, the compiler recompiles the generic program for the new type to generate an efficient binary.
 A myriad of optimizations can be done during the compilation. For example, the compiler can optimize the memory layout of immutable elements with fixed sizes in an array to speed up array indexing.
@@
 We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
-Here, a commutative semiring is a field without additive inverse and multiplicative inverse.
-Giving up these nice properties of  fields has significant implications for tensor computation: tensor network compression algorithms might be not applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014}, and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
-But here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
+Here, a commutative semiring is a field that needs not to have an additive inverse and a multiplicative inverse.
+Giving up these nice properties of fields has significant implications for tensor computation: tensor network compression algorithms might not be applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014} and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
+Here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
 To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
@@
 %We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
-In the following sections, we will show how to compute a number of properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebras.
-The Venn diagram in \Fig{fig:venn-diagram} shows the algebras we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which properties can be computed by which tensor element types.
+In the following sections, we will show how to compute solution space properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebra.
+The Venn diagram in \Fig{fig:venn-diagram} shows the different types of algebra we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which solution space properties can be computed by which tensor element types.
 
@@
     \def\dx{-3};
-    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0) (PN) {\hspace{-3.5cm}Polynomial};
+    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0.15) (PN) {\hspace{-3.7cm}Polynomial};
     \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Largest order};
@@
 
-    \caption{The the tensor network element types used in this work and their relationships.
-    The overlap between two ellipses indicates that a new algebra can be created by combining those two algebras.
+    \caption{The tensor network element types used in this work and their relations.
+    The overlap between two ellipses indicates that a new algebra can be created by combining those two types of algebra.
 ``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.
@@
 \section{Tensor network representation of independent sets} \label{sec:tnmap}
-This section is about reducing the independent set problem to a tensor network contraction problem.
-An alternative approach dedicated to physicists can be found in \App{sec:energymodel}, where we introduce the reduction from the energy model of hard core lattice gases~\cite{Dyre2016, Fernandes2007}.
+This section describes the reduction of the independent set problem to a tensor network contraction problem.
+An alternative interpretation, perhaps more accessible to physicists, can be found in \App{sec:energymodel}, where we introduce the reduction from the energy model of hardcore lattice gases~\cite{Dyre2016, Fernandes2007}.
 Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-To reduce the independent set problem on $G$ to a tensor network contraction, we first map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex absent (present) in the set.
-For each vertex $v$, we defined a parameterized rank-one tensor indexed by $s_v$ as
+To reduce the independent set problem on $G$ to a tensor network contraction, we first map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
+For each vertex $v$, we define a parameterized rank-one tensor indexed by $s_v$ as
 \begin{equation}
@@
         1 & 0
-    \end{matrix}\right). \label{eq:edgetensor}
-\end{equation}
-The corresponding tensor network contraction is defined as
+    \end{matrix}\right), \label{eq:edgetensor}
+\end{equation}
+which encodes the independent set constraint since $B_{11} = 0$, meaning the two vertices cannot be both in the independent set.
+
+The corresponding tensor network contraction cab be defined as
 \begin{equation}\label{eq:idp}
@@
 where the summation runs over all $2^{|V|}$ vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$. 
-It is easy to see an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
-Meanwhile, a vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
+% It is easy to see that an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
+A vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
 
 \begin{example}\label{eg:twonode}
-In the following, we show a minimum example of mapping the independent problem of a 2 vertex complete graph K2 (left) to a tensor network (right).
+Here, we show a minimum example of mapping the independent problem of a 2-vertex complete graph K2 (left) to a tensor network (right).
 
@@
 
-In the graphical representation of tensor network on the right panel,
+In the graphical representation of the tensor network on the right panel,
 we use a circle to represent a tensor, a hyperedge in cyan color to represent the degree of freedom $s_a$,
-and a hyperedge in red color to represent a degree of freedom $s_b$.
-Tensors sharing a same degree of freedom are connected by a same hyperedge.
+and a hyperedge in red color to represent the degree of freedom $s_b$.
+Tensors sharing the same degree of freedom are connected by the same hyperedge.
 The contraction of this tensor network has the following form:
@@
     \left(\begin{matrix} 1 \\ x_b^{w_b} \end{matrix}\right)\\
-    &= 1 + x_a^{w_a} + x_b^{w_b}
+    &= 1 + x_a^{w_a} + x_b^{w_b}.
     \end{split}
 \end{equation}
-The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$ and $\{b\}$, with weights being $0$, $w_a$ and $w_b$ respectively.
+The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$, and $\{b\}$, with weights being $0$, $w_a$, and $w_b$ respectively.
 \end{example}
 
-For a general graph, it is computationally inefficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products. %, which scales exponentially as the number of vertices.
-%\purple{Perhaps explicitly say what this scales as?}\blue{I am not sure explicitly saying ``scales exponentially as the number of vertices'' is helpful, because treewidth often scales linearly as number of vertices, so tensor network also scales exponentially as the number vertices in most cases.}
-The standard approach to evaluate a randomly structured tensor network is: find a good pair-wise tensor contraction order as a binary tree, and then contract two tensors a time by this order.
+For a general graph, it is computationally inefficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
+A better approach to evaluate a tensor network is: to find a good pair-wise tensor contraction order as a binary tree and then contract two tensors at a time by this order.
 Let us denote the line graph of the hypergraph representation of a tensor network as $G'$.
 A contraction order of this tensor network corresponds to a tree decomposition of $G'$ and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
-Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $G'$ with smallest width (or the treewidth ${\rm tw}(G')$).
-In the independent set problem, treewidth of $G'$ is the same to the treewidth of the graph this tensor network mapped from. 
-In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is well known NP-hard problem.
-However, it is easy to find a close to optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019,Kalachev2021}.
+Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $G'$ with the smallest width (or the treewidth ${\rm tw}(G')$).
+In the independent set problem, the treewidth of $G'$ is the same as the treewidth of the graph this tensor network is mapped from. 
+In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is a well-known NP-hard problem.
+However, it is easy to find a close-to-optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019, Kalachev2021}.
 %The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
-For large scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.
+For large-scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.\
 loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom.
@@
 \begin{example}\label{eg:tensorcontraction}
-In the following, we map a 5-vertex graph (left) to a tensor network (right), and show how the contraction order reduces the time and space complexities.
+In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
 
@@
 % \end{align*}}
-The contraction process goes from bottom to top, where the root node stores the contraction result; the leaves are input tensors and the rest nodes are all intermediate contraction results.
+The contraction process goes from bottom to top, where the root node stores the contraction result; the leaves are input tensors and the rest of the nodes are all intermediate contraction results.
 Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
-The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of degree of freedoms, which is $2$ in a tensor network mapped from an independent set problem.
-One can easily check the largest tensor in contraction has space complexity $O(n^2)$ and this is the smallest over all possible contraction trees, i.e.
-the treewidth of the original $5$-vertex graph is $2$.
-The time complexity is $O(n^3)$, which is much smaller than that of direct enumeration $O(n^5)$.
+The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of the degree of freedoms, which is $2$ in a tensor network mapped from an independent set problem.
+One can easily check the largest tensor in contraction has a space complexity $O(n^2)$ and this is the smallest among all possible contraction trees, i.e.\ the treewidth of the original $5$-vertex graph is $2$.
+The time complexity is $O(n^3)$, which is much smaller than that of direct evaluation $O(n^5)$.
 \end{example}
@@
 \end{equation}
-where $a_k$ is the number of independent sets of size $k$, $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$ is the size of an MIS or the independence number.
+where $a_k$ is the number of independent sets of size $k$, $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$ is the size of a maximum independent set and it is also called the independence number.
 An independence polynomial is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
@@
 By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly using tensor network contraction.
-It is already very useful, for example, the total number of independent sets can be evaluated as $I(G, 1)$.
+For example, the total number of independent sets can be evaluated as $I(G, 1)$.
 However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
@@
 Then we can define an algebra among coefficient vectors, including a redefinition of additive identity and multiplicative identity.
-To avoid potential confusion, let us denote the additive identity as $\mymathbb{0}$, and multiplicative identity as $\mymathbb{1}$.
+To avoid potential confusion, let us denote the additive identity as $\mymathbb{0}$, and the multiplicative identity is $\mymathbb{1}$.
 The algebra between the polynomials number $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
@@
     \mymathbb{0} &= (),  \\
-    \mymathbb{1} &= (1).\label{eq:polynomial}
+    \mymathbb{1} &= (1), \label{eq:polynomial}
     \end{split}
 \end{equation}
-Here, the multiplication of two polynomial numbers can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
-%These operations are standard addition and multiplication operations of polynomials, and the polynomial type forms a commutative ring.
-The tensors $W$ and $B$ can thus be written as 
+where $\oplus$ and $\odot$ are the standard polynomial addition and multiplication operations.
+The multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
+The tensors $W$ and $B$, which are introduced in the previous section (Sec.~\ref{sec:tnmap}), can thus be written as 
 \begin{equation}
@@
 \end{equation}
-By contracting the tensor network with the polynomial type, we have the exact representation of the independence polynomial.
-In practise, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
+By contracting the tensor network with this polynomial type, we have the exact representation of the independence polynomial.
+In practice, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
 One may argue that one can first evaluate this polynomial at different $x$ being a real number,
 and then apply the Gaussian elimination procedure to fit the coefficients of this polynomial.
-This seemingly more time and space efficient approach suffers from precision issues in practise.
-The data ranges of standard integer types are too small to cover many practical using cases,
-while the floating point numbers may have round off error that much larger than the value itself.
-These are due to the fact that the number of independent sets at different sizes may vary tens or even hundreds of orders.
-For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory efficient method to find the polynomial by contracting and fitting on finite field algebra.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round off errors.
-For the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
+This seemingly more time and space-efficient approach suffer from precision issues in practice.
+The data ranges of standard integer types are too small to cover many practical use cases,
+while the floating-point numbers may have round-off errors that are much larger than the value itself.
+These are because the number of independent sets at different sizes may vary by tens or even hundreds of orders of magnitude.
+For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory-efficient method to find the polynomial by contracting and fitting on finite field algebra.
+Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round-off errors.
+For simplicity, we use this less efficient polynomial algebra for the discussion in the main text.
+
+% the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
 
@@
 \end{equation}
-Note here, in order to define the zero element, we have generalized the previous polynomial to the Laurent polynomial.
+Here, we have generalized the previous polynomial to the Laurent polynomial to define the zero-element properly.
 To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
@@
 \subsection{Truncated polynomial algebra for counting independent sets of large size}
-Instead of counting just the MISs, one may also be interested in counting the independent sets with largest several sizes.
+Instead of counting just the MISs, one may also be interested in counting the independent sets with the largest several sizes.
 For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial} as:
@@
 Similarly, one can also truncate the polynomial and keep only its smallest several orders.
-It can be used, for example, to count the maximal independent sets with smallest cardinality, where a maximal independent set is an independent set that can not be made larger by adding a new vertex into the it without violating the independence constraint.
+It can be used, for example, to count the maximal independent sets with the smallest cardinality, where a maximal independent set is an independent set that cannot be made larger by adding a new vertex into it without violating the independence constraint.
 As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
@@
 \subsection{Set algebra for configuration enumeration}
-The configuration enumeration of independent sets includes, for example, the enumeration of all independent sets, the enumeration of all MISs and the enumeration of independent sets with maximum several sizes.
+The configuration enumeration of independent sets include, for example, the enumeration of all independent sets, the enumeration of all MISs, and the enumeration of independent sets with the largest several sizes.
 Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
-The multiplication between labelled variables are commutative while the summation of labelled variables forms a set.
-Intuitively, one can use a bit string as the representation of a labelled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
+The multiplication between labeled variables is commutative while the summation of labeled variables forms a set.
+Intuitively, one can use a bit string as the representation of a labeled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
 For example, in a 5-vertex graph, $x_2$ and $x_5$ can be represented as $01000$ and $00001$ respectively and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
@@
 
-This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs, or \Eq{eq:max2poly} to enumerate all independent sets of size $\alpha(G)$ and $\alpha(G)-1$.
+This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs, or \Eq{eq:max2poly} to enumerate all independent sets of sizes $\alpha(G)$ and $\alpha(G)-1$.
 As long as the coefficients in a truncated polynomial are members of a commutative semiring, the polynomial itself is a commutative semiring.
-For example, to enumerate only the MISs we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Eq{eq:set} and the exponents follow the max-plus tropical algebra.
+For example, to enumerate only the MISs, we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Eq{eq:set} and the exponents follow the max-plus tropical algebra.
 The combined operations become: 
@@
 We introduce the bounding technique in \App{sec:bounding} to avoid this issue.
-One may also be interested in a more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
+One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
 It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure.
 
-If one is interested in obtaining only one MIS configuration, he can just keep one configuration in each tensor element to save the computational effort.
+If one is interested in obtaining only one MIS configuration, they can just keep one configuration in each tensor element to save the computational effort.
 By replacing the sets of bit strings in \Eq{eq:set} with a single bit string, we have the following algebra
@@
 \subsection{Sampling extremely large configuration space}
-When the problem scale goes large, a set of bitstrings might be impossible to fit into any type of storage.
-To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.
-instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
+When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
+To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.\ instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
 Each node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of \texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node, and $left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
@@
 This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms rather than their storage.
-Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with largest several sizes.
-Although one probably can not collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
-he can draw unbiased samples from it by direct sampling.
-The sampling program starts from the root node, and descends this tree recursively to the left and right siblings.
+Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with the largest several sizes.
+Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
+they can draw unbiased samples from it by direct sampling.
+The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
 If a node has type \texttt{SUM}, the program draws samples from the left and right siblings with a probability decided by the size of each sub-tree and returns the union of samples.
@@
 The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
-In an sum-product expression tree, the number of configurations of a sub-trees can be determined easily as we will show in the following example.
+In a sum-product expression tree, the number of configurations of sub-trees can be determined easily as we will show in the following example.
 \begin{example}
@@
 where sub-trees $A, B, C$ and $D$ can be any of the four types of nodes.
-This sum-product expression tree can be represented diagrammatically as the following.
+This sum-product expression tree can be represented diagrammatically as the following:
 
@@
 The left and right siblings of the root node have sizes $|A|\times |B|$ and $|C|+|D|$ respectively, while the root node size can be computed as $|A|\times |B| + |C|+|D|$.
-The sizes of $A, B, C$ and $D$ can be computed recursively until the program meets either a \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$.
+The sizes of $A, B, C$, and $D$ can be computed recursively until the program meets either a \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$.
 \end{example}
@@
 \section{Weighted graphs}\label{sec:weighted}
-All the solution space properties and the corresponding algebra on unweighted graphs still holds for integer weighted graphs, while for general weighted graphs, the independence polynomial is not well defined anymore.
-For general weighted graphs, it is more useful to know the $k$ most weighted sets and their sizes.
+All the solution space properties and the corresponding algebra on unweighted graphs still hold for integer-weighted graphs, while for general weighted graphs, the independence polynomial is not well defined anymore.
+For general weighted graphs, it is more useful to know the $k$ maximum weighted sets and their sizes.
 They can be computed by the extended tropical algebra, which is a natural generalization of the max-plus tropical algebra:
-
 \begin{equation}
@@
     s \oplus t &= \texttt{largest}(s \cup t, k)\\
-    s \odot t &= \texttt{largest}(\{a+b| a \in s, b\in t\}, k)\\
+    s \odot t &= \texttt{largest}(\{a+b | a \in s, b\in t\}, k)\\
     \mymathbb{0} &= -\infty^{\otimes k}\\
@@
 where we have used the equation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
-To find solutions corresponding largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Eq{eq:singleconfig}).
-Since the $\oplus$ operation of configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
+To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Eq{eq:singleconfig}).
+Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
 
@@
 The results are summarized in Figure~\ref{fig:benchmark}.
-The graphs in all benchmarks are random three regular graphs, which have treewidth that asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
-In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming based algorithms~\cite{Courcelle1990, Fomin2013}.
+The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming~\cite{Courcelle1990, Fomin2013}.
 To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
-The main goal of this section is to show the relative timing of computing different solution space properties.
+The main goal of this section is to show the relative computation time for calculating different solution space properties.
 
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
-    \caption{Benchmark results for computing different properties of independent sets of a random three regular graph with different tensor element types.
+    \caption{Benchmark results for computing different solution space properties of independent sets of random three-regular graphs with different tensor element types.
     The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
-    Legends are properties, algebra and devices that we used in the computation; one can find the corresponding computed solution space property in \Tbl{tbl:generictypes}.
+    Legends are properties, algebra, and devices that we used in the computation; one can find the corresponding computed solution space property in \Tbl{tbl:generictypes}.
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computing time for calculating the MIS size and for counting of the number of all independent sets (ISs), the number of MISs,
-        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest sets sizes.
-    (c) The computing time for calculating the independence polynomials with different approaches.
-    (d) The computing time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
+    (b) The computation time for calculating the MIS size and for counting the number of all independent sets (ISs), the number of MISs,
+        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest set sizes.
+    (c) The computation time for calculating the independence polynomials with different approaches.
+    (d) The computation time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
     all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum-product expression tree format,
@@
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
-If we assume our contraction order finding program has been converged to the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
+If we assume our contraction-order finding program has found the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
 Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
-One can see that all the computing times in figure~\ref{fig:benchmark} (b), (c) and (d) have a strong correlation with the predicted time and space complexity.
-While in panel (d), the computing times of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
-Among these benchmarks, computational tasks with data types real numbers, complex numbers or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
+One can see that all the computation times in figure~\ref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
+While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
+Among these benchmarks, computational tasks with data types real numbers, complex numbers, or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
 These tasks usually compute much faster than ones with other element types in the same category.
-Immutable data types with no reference other values can be compiled to GPU devices that runs much faster than CPU in all cases when the problem scale is big enough.
+Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
 These data types do not include those defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr} or a data type containing them as a part.
-In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation based method is the fastest in computing the independence polynomial,
+In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
 but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
-In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one orders of magnitude in enumerating the MISs.
+In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
 The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
@@
 The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (Figure~\ref{fig:lattices}(b));
-the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)).
+the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
+
 The number of independent sets for square lattice graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
 We computed the integer sequence for $L=38$ and $L=39$, which is, to the best of our knowledge, not known before.
-In the computation, we used the finite-field algebra for contracting integer tensor networks with an arbitrarily high precision.
-
-A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can tell us thermal dynamic properties of hard core lattice gases at the high temperature limit.
+In the computation, we used finite-field algebra for contracting integer tensor networks with arbitrarily high precision.
+
+A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can tell us the thermodynamic properties of hard-core lattice gases at the high-temperature limit.
 For the square lattice graphs, this number is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
@@
 To our knowledge, the entropy constants for these disordered graphs have not been studied before.
+They may be used to study phase transitions for disordered lattices, which are typically much harder to understand.
 Interestingly, the variations due to different random instances are negligible for this entropy quantity.
-\blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
+% \blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
 
@@
 \subsection{The overlap gap property\label{sec:overlap-gap}}
-With the tool to enumerate or sample configurations, one can understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs.
-One of the known barriers for finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-If the overlap gap property is present, it means every two large independent sets either have a significant intersection or very small intersection;
+With this tool to enumerate or sample configurations, one can understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs.
+One of the known barriers to finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
+If the overlap gap property is present, it means every two large independent sets either have a significant intersection or a very small intersection;
 it implies that large independent sets are clustered together.
-%\purple{Do you want me to write a more formal definition as well or do you think it's not necessary?}\blue{Explaining the concept overlap gap property well seems to be impossible in a this paper (you need at least some plots).}
 This clustering property has been used to rigorously prove upper bounds on the performance of local search algorithms~\cite{Gamarnik2013, Gamarnik2019}.
 To investigate the overlap gap property, we compute pair-wise Hamming distance distributions of large independent sets as they are good indicators of the presence or absence of overlap gap properties.
-%Pair-wise Hamming distance distributions are good indicators of the overlap gap properties that a single peak in the distribution indicates the absence of Hamming distances.
-%We do not explore the full configurations space because the
-%With these samples, we can have a good estimation of the Hamming distance distributions. 
-We inspect two types of graphs that are particularly interesting, the King's graphs with defects and $3$-regular graphs. % that we want to investigate.
-%Each category contains nine randomly generated instances, due to the limitation of computing resources,
-It was known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Ebadi2022}, however, it is not clear whether the MIS problem defined on a randomly generated King's graph with defects can have the overlap gap property.
-It was known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, however, it is not known whether for small $d$, e.g.
-$3$-regular graphs, this statement remains true.
-We randomly generate $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
-At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to direct sample from the target configuration space.
+We inspect two types of graphs that are particularly interesting, the King's graphs with defects and $3$-regular graphs.
+It was known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Ebadi2022}.
+However, it is not clear whether the MIS problem defined on a randomly generated King's graph with defects can have the overlap gap property.
+It was known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, but, it is not known whether, for small $d$, e.g.\ for $3$-regular graphs, this statement remains true.
+We randomly generated $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
+At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to directly sample from the target configuration space.
 For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Fig{fig:hamming}.
@@
     \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
-    \caption{A visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem.
+    \caption{Visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem~\cite{Ebadi2022}.
     Each vertex represents an independent set, and each edge represents a pair of independent sets that differ by a swap operation or a vertex addition.}
@@
 \end{figure}
-The ability to enumerate configurations and compute independence polynomials was crucial in understanding the performance of quantum and classical algorithms for Maximum Independent Set in recent experiments~\cite{Ebadi2022}.
-We found that on King's graphs with $0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
-On the hardest graph instances for simulated annealing that we studied, a high density of local minima were present at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
-Initially, we suspected that simulated annealing was trapped certain clusters of these local minima in the solution space.
-However, by enumerating the configurations, we determined that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimal solution is found.
-Therefore, it is the large ratio of local to global minima that prevents simulated annealing from efficiently finding the MIS.
+The ability to enumerate configurations and compute independence polynomials was critical in understanding the performance of quantum and classical algorithms for MIS in a recent experiment on a Rydberg atom quantum computer~\cite{Ebadi2022}.
+In this work, the authors found that on King's graphs with $0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
+On the hardest graph instances for simulated annealing studied in the experiment, a high density of local minima were present at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimum solution of size $\alpha(G)$.
+Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space.
+However, by enumerating the configurations, it was then found that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
+Therefore, it was the large ratio of local to global minima that prevents simulated annealing from efficiently finding the MIS.
 %and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
@@
 
-Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, we were able to gain insight by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for an instances with $39$ nodes~\cite{Ebadi2022}.
+Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, the authors were able to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
 Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
@@
 %The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-The solution space graph is well-connected by local changes to the spin configurations, has small diameter, and the degree of each node appears to concentrate. 
-From this visualization, we see that the quantum algorithm does not appear to return solely local minima with large Hamming distance from the MISs as suggested for adiabatic algorithms by~\cite{altshuler2010}, which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
+The solution space graph is well-connected by local changes to the spin configurations, has a small diameter, and the degree of each node appears to concentrate. 
+From this visualization, the authors inferred that the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms by Ref.~\cite{altshuler2010}, which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
 Rather, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
 %Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
-Looking forward, these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
+Looking forward, we expect these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
 
 \section{Discussion and conclusion}
-In this paper, we introduce using generic tensor networks to compute a number of different solution space properties of a certain class of NP-hard combinatorial optimization problems.
-% the maximum independent set problem.
-%,
+In conclusion, in this paper, we introduce a unified framework using generic tensor networks to compute different solution space properties of a certain class of NP-hard combinatorial optimization problems.
 These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
@@
 %With different algebras, the contraction of the same tensor network gives us the different properties.
-The different data types introduced in the main text to compute these properties are  summarized in the diagram in \Fig{fig:venn-diagram}. %We go beyond using real numbers and use polyn
-The class of problems solvable by a tensor network include but is not limited to maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, and the set packing problem, as detailed in \App{sec:otherproblems}.
+The different data types introduced in the main text to compute these properties are summarized in the diagram in \Fig{fig:venn-diagram}.
+The class of problems solvable by a tensor network includes but is not limited to maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \App{sec:otherproblems}.
 
@@
 
-It would be interesting to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and see what new properties can be computed.
-To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013}.
-Dynamic programming is closely related to a tropical tensor network~\cite{Liu2021}, for example, the Viterbi algorithm for finding the most probable configuration in a hidden Markov model can be interpreted as a matrix product state featured with tropical algebra, and the tropical tensor network in the main text is probably equivalent to dynamic programming in finding a best solution.
-However, while having broader applications,
-%e.g. the traveling sales man can be solved easily with dynamic programming but not with a tensor network to the best of our knowledge, 
-dynamic programming does not have a clear algebraic interpretation required by computing solution space properties beyond finding a best solution.
+It would be interesting to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and explore what new properties can be computed.
+To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013} approaches.
+Dynamic programming is closely related to a tropical tensor network~\cite{Liu2021}; for example, the Viterbi algorithm for finding the most probable configuration in a hidden Markov model can be interpreted as a matrix product state featured with tropical algebra, and the tropical tensor network in the main text is potentially equivalent to dynamic programming in finding an optimum solution.
+However, while having broader applications, dynamic programming does not have a clear algebraic interpretation required by computing solution space properties beyond finding an optimum solution.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 
-The source code in Julia language for this paper can be found in our Github repository~\cite{GraphTensorNetworks}. 
-There is also a short introduction to this repository as well a gist to show how it works in the Appendix~\ref{sec:technical}.
+The source code in Julia language for this paper can be found in the Github repository~\cite{GraphTensorNetworks}. 
+There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
-We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to other scientific software.
+We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to the development of other scientific software.
 
@@
 We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
-We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman and Katharine Hyatt
+We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman, and Katharine Hyatt
 for actively maintaining their packages and resolving related issues voluntarily.
-\blue{funding information}
+\blue{funding information, need to mention the AWS}
 
@@
 where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term associated with it.
-The first part corresponds to the negative independent set size and the second part describes the independence contraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hard core lattice model~\cite{Dyre2016, Fernandes2007}.
+The first part corresponds to the negative independent set size and the second part describes the independence constraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hardcore lattice model~\cite{Dyre2016, Fernandes2007}.
 The partition function is defined as
@@
 \end{equation}
-where the $0$ in the bond tensor coming from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}.
+where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}.
 By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
@@
 
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice: either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
-Hence a tensor network can be represented as a open simple graph, where an input tensor is mapped to a vertex, a label shared by two input tensors is mapped to an edge and a label appears in the output tensor is mapped to an open edge.
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice: either both are in input tensors (which will be summed over) or one is in an input tensor and another in the output tensor.
+Hence a tensor network can be represented as an open simple graph, where an input tensor is mapped to a vertex, a label shared by two input tensors is mapped to an edge and a label that appears in the output tensor is mapped to an open edge.
 A standard tensor network notation is equivalent to the generalized tensor network in representation power.
@@
 \end{tikzpicture}}
-Here, vertex tensors are not shown here because they can be absorbed into an edge tensor hence do not change the contraction complexity.
+Vertex tensors are not shown here because they can be absorbed into an edge tensor hence do not change the contraction complexity.
 If we contract this tensor network in the column-wise order, the maximum intermediate tensor has rank $\sim L$, which can be seen by counting the number of colors at the cut.
@@
 
-In this diagram,the additional $\delta$ tensors can have ranks upto $8$.
+In this diagram, the additional $\delta$ tensors can have ranks up to $8$.
 If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e. the space complexity is $\approx 2^{3L}$.
@@
 including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
-\Fig{fig:benchmark-maximal} (a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independence set problem.
+\Fig{fig:benchmark-maximal} (a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
 In \Fig{fig:benchmark-maximal} (b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
@@
 \end{equation}
-where $k$ is the size of an edge set, and a coefficients $c_k$ is the number of $k$-matchings.
+where $k$ is the size of an edge set, and a coefficient $c_k$ is the number of $k$-matchings.
 
@@
 We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
-Then we define a tensor labelled by $c_v$ for each vertex $v$ as
+Then we define a tensor labeled by $c_v$ for each vertex $v$ as
 \begin{equation}
@@
 In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
-which is also known as the spin glass problem in statistic physics.
+which is also known as the spin-glass problem in statistic physics.
 Let $G=(V,E)$ be a graph, we associate a weight $w_v$ to each $v\in V$.
-To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
+To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
 Then for each edge $(u,v)\in E$, we define an edge matrix labelled by $(s_u, s_v)$ as
@@
 \end{equation}
-where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in an spin glass.
+where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin-glass.
 Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$, we have a graph polynomial similar to previous ones,
@@
 In graph theory, a dominating set for a graph $G = (V, E)$ is a subset $D \subseteq V$ such that every vertex not in $D$ is adjacent to at least one member of $D$.
-To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a boolean degree of freedom $s_v\in\{0, 1\}$.
+To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
 Then for each vertex $v$ we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
@@
 \subsection{Boolean satisfiability Problem}
-The boolean satisfiability problem is the problem of determining if there exists an interpretation that satisfies a given boolean formula.
-One can specify a satisfiable problem in the conjuctive normal form (CNF), i.e. a conjuction of clauses (or disjunctions of boolean literals).
-To reduce the problem of solving a CNF to a tensor network contraction, we first map a boolean literal $a$ and its negation $\neg a$ to a same degree of freedom $s_a \in \{0, 1\}$.
+The Boolean satisfiability problem is the problem of determining if there exists an interpretation that satisfies a given Boolean formula.
+One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e. a conjunction of clauses (or disjunctions of Boolean literals).
+To reduce the problem of solving a CNF to a tensor network contraction, we first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
 $s_a = 0$ stands for variable $a$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
@@
 where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
-%If we contract this tensor network, we will get a multiplicative factor $x$ whenever there is a clause satisfied.
 Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
@@
 \subsection{Set packing}
-Set packing is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
+Suppose one has a finite set $S$ and a list of subsets of $S$. Then, the set packing problem asks if some $k$ subsets in the list are pairwise disjoint.
+It is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
 To solve the set packing problem, we generalize the edge tensor in \Eq{eq:edgetensor} as
@@
 \end{equation}
+
+\subsection{Set covering}
+Given a collection of elements, the set covering problem aims to find the minimum number of sets that incorporate (cover) all of these elements.
+In the set covering problem, two sets are given: a set $U$ of elements and a set $S$ of subsets of the set $U$.
+The union of all the subsets covers the set $U$.
+For each set $s \in S$, we associate it with weight $w_s$ to it.
+To get the generic tensor network representation, we first map a set $s\in S$ to a Boolean degree of freedom $l_s\in\{0, 1\}$.
+For each set $s$, we defined a parameterized rank-one tensor indexed by $l_s$ as
+\begin{equation}
+W(x_s^{w_s}) = \left(\begin{matrix}
+    1 \\
+    x_s^{w_s}
+    \end{matrix}\right)
+\end{equation}
+where $x_s$ is a variable associated with $s$.
+For each unique element $a \in U$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(a) = \{s | s \in S \land a\in s\}$, as
+\begin{equation}
+B_{l_1,l_2,\ldots,l_{|N(a)|}} = \begin{cases}
+    0 & l_1=l_2=\ldots=l_{|N(a)|}=0,\\
+    1 & \text{otherwise}.
+\end{cases}
+\end{equation}
+If a subset of $S$ does not include any sets containing element $a$, then this configuration has zero contribution to the contraction result.
 
@@
     \caption{Bounded enumeration of maximum independent sets.
-In these graphs, a circle is a tensor, an arrow specifies execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
-$\overline A$ means the boolean mask of $A$.
+In these graphs, a circle is a tensor, an arrow specifies the execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
+$\overline A$ means the Boolean mask of $A$.
 (a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
-     (b) is the backward pass for computing boolean gradients as masks.
+     (b) is the backward pass for computing Boolean gradients as masks.
      (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
@@
 The bounded contraction consists of three stages as shown in \Fig{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
-(b) Then, we compute a boolean mask for each cached tensor, where we use a boolean \texttt{true} to represent a tensor element having contribution to the MIS and boolean \texttt{false} otherwise.
+(b) Then, we compute a Boolean mask for each cached tensor, where we use a Boolean \texttt{true} to represent a tensor element having a contribution to the MIS and Boolean \texttt{false} otherwise.
 (c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
 The crucial part is computing the masks in step (b).
-Note that these masks in fact correspond to tensor elements with non-zero gradients with respect to the MIS size; we can compute these masks by back propagating the gradients.
+Note that these masks correspond to tensor elements with non-zero gradients to the MIS size; we can compute these masks by back-propagating the gradients.
 To derive the back-propagation rule for tropical tensor contraction,
@@
 \end{equation}
-On the right hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
+On the right-hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
 Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
@@
 \end{equation}
-where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, boolean false is treated as the tropical number $\mymathbb{0}$, and boolean true is treated as the tropical number $\mymathbb{1}$.
+where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, Boolean false is treated as the tropical number $\mymathbb{0}$, and Boolean true is treated as the tropical number $\mymathbb{1}$.
 This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
@@
 Unlike using the polynomial numbers in \Eq{eq:polynomial},  the fitting approach does not have the linear overhead in space.
-However, since the independence polynomial coefficients can have a huge order-of-magnitude range, the round-off errors can be larger than the value itself when using floating point number in computation.
-%In addition, the number could easily overflow if we use fixed-width integer types.
+However, since the independence polynomial coefficients can have a huge order-of-magnitude range, the round-off errors can be larger than the value itself when using floating-point numbers in computation.
 To avoid using the arbitrary precision number that can be very slow and is incompatible with GPU devices, we introduce the following finite-field algebra $\text{GF}(p)$ approach:
@@
 If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
-All computations are done with integers of fixed width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
+All computations are done with integers of fixed-width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
 
@@
 In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
-One drawback of using finite field algebra is its matrix multiplication is less computational efficient compared with floating point matrix multiplication.
-Here, we show an alternative method with standard number types but with controllable round off errors.
+One drawback of using finite field algebra is its matrix multiplication is less computational efficient compared with floating-point matrix multiplication.
+Here, we show an alternative method with standard number types but with controllable round-off errors.
 Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
@@
 It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
-The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure that can can be much slower to manipulate than arrays.
-In the following, we show an algorithm with roughly the same complexity, but does not need a heap.
-This algorithm first sorts both $A$ and $B$, then use the bisection to find the $n$-th largest value in the sum combination.
+The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
+In the following, we show an algorithm with roughly the same complexity but does not need a heap.
+This algorithm first sorts both $A$ and $B$, then uses the bisection to find the $n$-th largest value in the sum combination.
 The key point is we can count the number of entries greater than a specific value
@@
 
-This appendix covers some technical guides for productivity, including an introduction to an open source package \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and a gist about how this package is implemented.
+This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
 One can install \texttt{GraphTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
@@
 Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
-If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must uncommented.
-The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the key word argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the key word argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
+If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
+The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
 Here, we use \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} the default values.
 The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
-The first execution of this function will be a bit slow due to Julia's just in time compiling.
+The first execution of this function will be a bit slow due to Julia's just-in-time compiling.
 After that, the subsequent runs will be fast.
@@
 
-The code we will show below is a gist of how the above package is implemented, which is mainly for the pedagogical purpose.
+The code we will show below is a gist of how the above package is implemented, which is mainly for pedagogical purpose.
 It covers most of the topics in the paper without caring much about the performance.
@@
 \begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/QuEraComputing/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
 	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
-	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in Julia community.
+	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in the Julia community.
 	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
-	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and \href{https://github.com/JuliaMath/Primes.jl}{Primes}] are packages providing finite field algebra and prime number manipulation.
+	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and the \href{https://github.com/JuliaMath/Primes.jl}{Primes}] package providing finite field algebra and prime number manipulation.
 \end{description}
@@
 They can be installed in a similar way to \texttt{GraphTensorNetworks}.
-After installing the required packages, one can open a Julia REPL, copy and paste the following code snippet into it.
+After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.
 

### 2022-04-11 paper/paper.tex
update

--- 2022-04-06 paper/paper.tex
@@
 \end{AMS}
-
-\cyan{a comment} and \xcyan{a resolved comment}
 
@@
 
-The source code in Julia language for this paper can be found in our Github repository~\cite{GraphTensorNetworks}. 
+The source code in Julia language for this paper can be found in our Github repository~\cite{GenericTensorNetworks}. 
 There is also a short introduction to this repository as well a gist to show how it works in the Appendix~\ref{sec:technical}.
@@
 
-This appendix covers some technical guides for productivity, including an introduction to an open source package \href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and a gist about how this package is implemented.
-One can install \texttt{GraphTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
+This appendix covers some technical guides for productivity, including an introduction to an open source package \href{https://github.com/Happy-Diode/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and a gist about how this package is implemented.
+One can install \texttt{GenericTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
 \begin{lstlisting}
-pkg> add GraphTensorNetworks
+pkg> add GenericTensorNetworks
 \end{lstlisting}
@@
 \begin{lstlisting}
-julia> using GraphTensorNetworks, Graphs
+julia> using GenericTensorNetworks, Graphs
 
@@
 After that, the subsequent runs will be fast.
-The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GraphTensorNetworks}.
+The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.
 
@@
 
-They can be installed in a similar way to \texttt{GraphTensorNetworks}.
+They can be installed in a similar way to \texttt{GenericTensorNetworks}.
 After installing the required packages, one can open a Julia REPL, copy and paste the following code snippet into it.

### 2022-04-11 paper/paper_before_maddie.tex
update

@@
 We show some of the Julia language implementations in Appendix~\ref{sec:technical}.
-A complete implementation can be found in our Github repository~\cite{GraphTensorNetworks}. 
+A complete implementation can be found in our Github repository~\cite{GenericTensorNetworks}. 
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
@@
 For better performance, we recommend checking our GitHub repository for the full featured version:
-\href{https://github.com/Happy-Diode/GraphTensorNetworks.jl}{https://github.com/Happy-Diode/GraphTensorNetworks.jl}.
+\href{https://github.com/Happy-Diode/GenericTensorNetworks.jl}{https://github.com/Happy-Diode/GenericTensorNetworks.jl}.
 It can be installed in a similar style to other packages.

### 2022-04-11 paper/figures/plot.py

@@ -317,10 +317,10 @@ class PLT(object):
             plt.text(0.5, 0.7, "(b) Nine random three regular graphs of size 110.", ha="center", va="center", fontsize=20, family="Times New Roman")
             ax.axis("off")
 
-    def fig7(self):
+    def fig7(self, tp="pdf"):
         F1 = 10
         F2 = 12
-        with NoBoxPlt(figsize=(7,6), filename="fig7.pdf") as pl:
+        with NoBoxPlt(figsize=(7,6), filename="fig7.%s"%tp) as pl:
             grid = viznet.Grid((1.0,1.0))
             node = viznet.NodeBrush('box', size=(0.2,0.2), color="none", roundness=0.1)
             edge = viznet.EdgeBrush('->', color='#000000', lw=1.5)

### 2022-04-11 project/independence_polynomial_cpu.jl

@@ -1,8 +1,8 @@
-using GraphTensorNetworks, Random
-using Distributed, DelimitedFiles, GraphTensorNetworks.OMEinsumContractionOrders, GraphTensorNetworks.OMEinsum
+using GenericTensorNetworks, Random
+using Distributed, DelimitedFiles, GenericTensorNetworks.OMEinsumContractionOrders, GenericTensorNetworks.OMEinsum
 
 @everywhere begin
-using GraphTensorNetworks, Random, GraphTensorNetworks.OMEinsumContractionOrders, GraphTensorNetworks.OMEinsum
+using GenericTensorNetworks, Random, GenericTensorNetworks.OMEinsumContractionOrders, GenericTensorNetworks.OMEinsum
 using DelimitedFiles
 
 function do_work(f, jobs, results) # define work function everywhere

### 2022-04-11 paper/paper.tex

--- 2022-04-11 paper/paper.tex
@@
 
-The source code in Julia language for this paper can be found in the Github repository~\cite{GraphTensorNetworks}. 
+The source code in Julia language for this paper can be found in our Github repository~\cite{GenericTensorNetworks}. 
 There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
@@
 
-This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GraphTensorNetworks.jl}{GraphTensorNetworks}~\cite{GraphTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
-One can install \texttt{GraphTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
+This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
+One can install \texttt{GenericTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
 \begin{lstlisting}
-pkg> add GraphTensorNetworks
+pkg> add GenericTensorNetworks
 \end{lstlisting}
@@
 
-They can be installed in a similar way to \texttt{GraphTensorNetworks}.
+They can be installed in a similar way to \texttt{GenericTensorNetworks}.
 After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.

### 2022-04-11 paper/paper_before_maddie.tex

@@
 \begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/Happy-Diode/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/QuEraComputing/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and contraction order optimizations.
     \texttt{OMEinsumContractionOrders} implements state-of-the-art algorithms for finding the optimal contraction order for a tensor network, including the KaHypar+Greedy~\cite{Gray2021, Pan2021} and local transformation based approaches~\cite{Kalachev2021},
@@
 For better performance, we recommend checking our GitHub repository for the full featured version:
-\href{https://github.com/Happy-Diode/GenericTensorNetworks.jl}{https://github.com/Happy-Diode/GenericTensorNetworks.jl}.
+\href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{https://github.com/QuEraComputing/GenericTensorNetworks.jl}.
 It can be installed in a similar style to other packages.

### 2022-04-12 paper/paper.tex
Updates from Overleaf

@@
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-These solution space properties include, for example, finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
+These solution space properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
 We use the independent set problem as an example and show how all these solution space properties can be computed in the unified approach of generic programming tensor networks.
@@
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate the versatility of this computational tool, we apply it to a few examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
+To demonstrate the versatility of this computational tool, we apply it to several  examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
 % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
@@
 
-In this paper, we introduce a unified framework to compute a broader class of quantities associated with these problems, beyond just finding an optimum solution.
-We call them \textit{solution space properties}, which can be much harder to compute (e.g.\ \#P-complete), but they can be crucial for understanding hard combinatorial optimization problems.
+In this paper, we introduce a unified framework to compute a broad class of quantities associated with these problems, beyond just finding an optimum solution.
+We call them \textit{solution space properties}.
+In practice these can be much harder to compute (corresponding e.g.\ to \#P-complete class).
+However, these properties can be crucial for understanding detailed properties of hard combinatorial optimization problems.
 % In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
@@
 where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term associated with it.
-The first part corresponds to the negative independent set size and the second part describes the independence constraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hardcore lattice model~\cite{Dyre2016, Fernandes2007}.
+The first part corresponds to the negative independent set size and the second part describes the independence constraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hardcore lattice models~\cite{Dyre2016, Fernandes2007}.
 The partition function is defined as
@@
 \end{equation}
-where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}.
+where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}, which is the independence constraint.
 By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
@@
 
-\section{An example of contraction complexity increase due to using the standard tensor network notation}\label{sec:tensorbad}
+\section{An example of increased contraction complexity for the standard tensor network notation}\label{sec:tensorbad}
 
@@
 In the following example, we will show this conversion might increase the contraction complexity of a tensor network.
-Let us consider the following King's graph.
+Let us consider the following King's graph. \\
 
@@
 \end{tikzpicture}}
-Vertex tensors are not shown here because they can be absorbed into an edge tensor hence do not change the contraction complexity.
+Vertex tensors are not shown here because they can be absorbed into an edge tensor and hence do not change the contraction complexity.
 If we contract this tensor network in the column-wise order, the maximum intermediate tensor has rank $\sim L$, which can be seen by counting the number of colors at the cut.
@@
 In this diagram, the additional $\delta$ tensors can have ranks up to $8$.
-If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e. the space complexity is $\approx 2^{3L}$.
+If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e.
+the space complexity is $\approx 2^{3L}$, which has a larger complexity than using the generalized tensor network notation.
 
@@
 Let $G=(V,E)$ be a graph, we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
-A maximal independent set $I_m$ is an independent set that there does exist a vertex $v \in V$ such that $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.
-an independent set that can not become a larger one by adding a new vertex.
+A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
 To characterize the maximal independence restriction, we defined a tensor on each $\{v\}\cup N(v)$ as
@@
 It means if none of the neighbours of $v$ are in $I_{m}$ ($ s_1=s_2=\ldots=s_{|N(v)|}=0$), then $v$ must be in $I_{m}$ and contribute a factor $x_{v}$, otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
-For a vertex $v$ having degree 2, this tensor has the following form
+For a vertex $v$ that has a degree 2, this tensor has the following form
 \begin{equation}
@@
 
-Let us consider the graph in Example~\ref{eg:tensorcontraction}, the corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation.
+Let us consider the graph in Example~\ref{eg:tensorcontraction}.
+The corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation.
+\\
 
@@
 Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$D_m(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013},
-which to our knowledge, the best algorithm gives a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
+$D_m(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013};
+to our knowledge, the best algorithm has a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
 %If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
@@
 including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
-\Fig{fig:benchmark-maximal} (a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
-In \Fig{fig:benchmark-maximal} (b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
+\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
+In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
 
@@
     (a) time and space complexity of tensor network contraction. 
-    (b) The wall clock time for counting and enumeration of maximal ISs. The missing data is due to due to the memory limit.
+    (b) The wall clock time for counting and enumeration of maximal ISs. % The missing data is due to the memory limit.
     }
@@
 \subsection{Vertex coloring}
-Let $G=(V,E)$ be a graph, a vertex coloring is an assignment of colors to each vertex $v\in V$ such that no edge connects two identically colored vertices. 
+Let $G=(V,E)$ be a graph. A vertex coloring is an assignment of colors to each vertex $v\in V$ such that no edge connects two identically colored vertices. 
 In a $k$-coloring problem, the number of colors is limited to less or equal to $k$.
@@
 %The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
-Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$, we have a graph polynomial,
+Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$; we then have a graph polynomial,
 in which the $k$-th coefficient is the number of coloring that $k$ bonds satisfy constraints.
@@
 In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
-which is also known as the spin-glass problem in statistic physics.
-Let $G=(V,E)$ be a graph, we associate a weight $w_v$ to each $v\in V$.
+which is also known as the spin-glass problem in statistical physics.
+Let $G=(V,E)$ be a graph.
+We associate a weight $w_v$ to each $v\in V$.
 To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-Then for each edge $(u,v)\in E$, we define an edge matrix labelled by $(s_u, s_v)$ as
+Then for each edge $(u,v)\in E$, we define an edge matrix labeled by $(s_u, s_v)$ as
 \begin{equation}
@@
 \end{equation}
-where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin-glass.
-Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$, we have a graph polynomial similar to previous ones,
-in which the $k$th coefficient is two times the number of cut configurations having size $k$ (i.e. cutting $k$ edges).
+where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem.
+Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$; we have a graph polynomial similar to the previous ones,
+in which the $k$th coefficient is two times the number of cut configurations that have size $k$ (i.e.\ cutting $k$ edges).
 
@@
 To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
-Then for each vertex $v$ we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
+Then for each vertex $v$, we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
 \begin{equation}
@@
 where $w_v$ is the weight associated with the vertex $v$.
-This tensor means a configurations having a closed neighborhood of $v$ not in $D$ ($s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$) can not be a dominating set.
+This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$) cannot be a dominating set.
 Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output.
@@
 \subsection{Boolean satisfiability Problem}
-The Boolean satisfiability problem is the problem of determining if there exists an interpretation that satisfies a given Boolean formula.
-One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e. a conjunction of clauses (or disjunctions of Boolean literals).
+The Boolean satisfiability problem is the problem of determining if there exists an assignment that satisfies a given Boolean formula.
+One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e.\ a conjunction of clauses (or disjunctions of Boolean literals).
 To reduce the problem of solving a CNF to a tensor network contraction, we first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
@@
 To get the generic tensor network representation, we first map a set $s\in S$ to a Boolean degree of freedom $l_s\in\{0, 1\}$.
-For each set $s$, we defined a parameterized rank-one tensor indexed by $l_s$ as
+For each set $s$, we define a parameterized rank-one tensor indexed by $l_s$ as
 \begin{equation}
@@
     \caption{Bounded enumeration of maximum independent sets.
-In these graphs, a circle is a tensor, an arrow specifies the execution direction of a function and $\circ$ is the Hadamard (element-wise) multiplication.
+In these graphs, a circle is a tensor, an arrow specifies the execution direction of a function, and $\circ$ is the Hadamard (element-wise) multiplication.
 $\overline A$ means the Boolean mask of $A$.
@@
 In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
-One drawback of using finite field algebra is its matrix multiplication is less computational efficient compared with floating-point matrix multiplication.
+One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
 Here, we show an alternative method with standard number types but with controllable round-off errors.
@@
 We computed the number of independent sets on square lattices and King's graphs with our generic tensor network contraction algorithm on GPUs.
-The tensor element type is finite-field algebra so that we can reach arbitrary precision.
+The tensor element type is the finite-field algebra so that we can reach an arbitrary precision.
 We also computed the independence polynomial for these lattices up to size $30\times 30$ in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repository}.
@@
 It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
-The standard approach to solve the sum combination problem requires storing the variables in a heap - a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
+The standard approach to solve the sum combination problem requires storing the variables in a heap --- a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
 In the following, we show an algorithm with roughly the same complexity but does not need a heap.
-This algorithm first sorts both $A$ and $B$, then uses the bisection to find the $n$-th largest value in the sum combination.
+This algorithm first sorts both $A$ and $B$ and then uses the bisection to find the $n$-th largest value in the sum combination.
 The key point is we can count the number of entries greater than a specific value
@@
 In this algorithm, function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by collecting the items to a set.
-Inside the function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration,
+Inside the function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration and
 the total number of iterations is upper bounded by $2n$.
@@
 
-This appendix covers some technical guides for productivity, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
-One can install \texttt{GenericTensorNetworks} a Julia REPL, by first type \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then type
+This appendix covers some technical guides for efficiency, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
+One can install \texttt{GenericTensorNetworks} in a Julia REPL, by first typing \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then typing
 \begin{lstlisting}
@@
 
-Here the main function \texttt{solve} takes three inputs, the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide use GPU or not.
+Here the main function \texttt{solve} takes three inputs: the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide to use GPU or not.
 If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
-The problem instance takes four arguments to initialize, the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()} and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
-Here, we use \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} the default values.
+The problem instance takes four arguments to initialize: the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()}, and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
+Here, we use the \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} as  default values.
 The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
-The first execution of this function will be a bit slow due to Julia's just-in-time compiling.
-After that, the subsequent runs will be fast.
-The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.
+The first execution of this function will be a bit slow due to Julia's just-in-time compilation.
+After that, the subsequent runs will be faster.
+The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in the package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.
 
@@
 
-The code we will show below is a gist of how the above package is implemented, which is mainly for pedagogical purpose.
-It covers most of the topics in the paper without caring much about the performance.
+The code we will show below is a gist of how the above package was implemented, which is mainly for pedagogical purpose.
+It covers most of the topics in the paper without caring much about performance.
 It is worth mentioning that this project depends on multiple open source packages in the Julia ecosystem:

### 2022-04-13 paper/paper.tex
Updates from Overleaf

@@
 \title{Computing solution space properties of combinatorial optimization problems by generic programming tensor networks
-\thanks{\funding{...}}
-}
-
-\author{XXX\thanks{XXX 
-  (\email{email}, \url{website}).}
-\and YYY\thanks{yyyyy 
-  (\email{yyyy}, \email{email}).}
+%\thanks{\funding{...}}
+}
+
+\author{
+Jin-Guo Liu\footnote{JIN-GUO LIU and XUN GAO contributed equally to this paper.}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
+    (\email{jinguoliu@g.harvard.edu}).}
+\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}).}
+\and Madelyn Cain\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\and Mikhail D. Lukin\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\and Sheng-Tao Wang\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
 }
@@
 
-The corresponding tensor network contraction cab be defined as
+The corresponding tensor network contraction can be defined as
 \begin{equation}\label{eq:idp}
@@
 \begin{equation}
-    W^{\rm T} = \left(\begin{matrix}
-        \mymathbb{1} \\
+    W^{\rm T}(w_v) = \left(\begin{matrix}
+        w_v \\
         \infty
@@
 \begin{equation}
-    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\}\infty^1) = \left(\begin{matrix}
+    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\}\infty^{w_v}) = \left(\begin{matrix}
         \mymathbb{1} \\
-        \{\boldsymbol{e}_{i}\}\infty^1
+        \{\boldsymbol{e}_{i}\}\infty^{w_v}
     \end{matrix}\right),   
@@
 \begin{equation}
-    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes 1, w_v) = \left(\begin{matrix}
+    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes w_v) = \left(\begin{matrix}
         \mymathbb{1} \\
@@
 We thank Benjamin Schiffer for providing helpful feedback on the writing of this manuscript.
-We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. % he is a man of speed!
+We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. 
 We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman, and Katharine Hyatt
 for actively maintaining their packages and resolving related issues voluntarily.
-\blue{funding information, need to mention the AWS}
+We acknowledge financial support from the DARPA ONISQ program (grant no.\ W911NF2010021), the Center for Ultracold Atoms, the National Science Foundation, the Vannevar Bush Faculty Fellowship, the U.S.
+Department of Energy (DE-SC0021013 and DOE Quantum Systems Accelerator Center (contract no.\ 7568717),
+%the Office of Naval Research, 
+the Army Research Office MURI.
+We acknowledge the computation credits provided by Amazon Web Services for running the benchmarks and case studies.
+Jinguo Liu acknowledges funding support provided by QuEra Computing Inc.\ through a sponsored research program.
 
@@
 \begin{equation}\label{eq:eng}
-    \mathcal{E}(G, s) = -\sum_{i\in V} w_i s_i + \infty \sum_{\langle i,j\rangle \in E}s_i s_j
+    \mathcal{E}(G, s) = -\sum_{i\in V} w_i s_i + \infty \sum_{(i,j) \in E}s_i s_j
 \end{equation}
@@
 \begin{equation}\label{eq:maximal}
-    T(x_v, w_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
+    T(x_v^{w_v})_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
         s_vx_v^{w_v} & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
@@
 It means if none of the neighbours of $v$ are in $I_{m}$ ($ s_1=s_2=\ldots=s_{|N(v)|}=0$), then $v$ must be in $I_{m}$ and contribute a factor $x_{v}$, otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
-For a vertex $v$ that has a degree 2, this tensor has the following form
-\begin{equation}
-    T(x_v, w_v)=\left(\begin{matrix}
+For a vertex $v$ that has a degree 2, the tensor has the following form
+\begin{equation}
+    T(x_v^{w_v})=\left(\begin{matrix}
     \left(\begin{matrix}
@@
 x_{c}^{w_k} & x_{bc}^{w_k} \\
-1_{ac} & x_{abc}^{w_k}
+1 & x_{abc}^{w_k}
 \end{matrix}\right)
@@
 Suppose one has a finite set $S$ and a list of subsets of $S$. Then, the set packing problem asks if some $k$ subsets in the list are pairwise disjoint.
-It is the hypergraph generalization of the maximum independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-To solve the set packing problem, we generalize the edge tensor in \Eq{eq:edgetensor} as
+It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
+The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Eq{eq:vertextensor}, while the edge tensor generalizes \Eq{eq:edgetensor} to higher dimensions
 \begin{equation}

### 2022-04-13 paper/paper.tex

@@
     (c) The computation time for calculating the independence polynomials with different approaches.
-    (d) The computation time for configuration enumeration, including the enumeration of all independent set configurations, a single MIS configuration, all MIS configurations,
+    (d) The computation time for configuration enumeration, includinga single MIS configuration, the enumeration of all independent set configurations, all MIS configurations,
     all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum-product expression tree format,

### 2022-04-13 paper/paper.tex

@@
     (c) The computation time for calculating the independence polynomials with different approaches.
-    (d) The computation time for configuration enumeration, includinga single MIS configuration, the enumeration of all independent set configurations, all MIS configurations,
-    all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$, and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$ in the sum-product expression tree format,
-    with or without bounding the enumeration space.
+    (d) The computation time for configuration enumeration, including single MIS configuration, the enumeration of all independent set configurations, all MIS configurations, all independent sets,
+    and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$.
     }
@@
     \caption{Bounded enumeration of maximum independent sets.
-In these graphs, a circle is a tensor, an arrow specifies the execution direction of a function, and $\circ$ is the Hadamard (element-wise) multiplication.
-$\overline A$ means the Boolean mask of $A$.
-(a) is the forward pass with algebra \Eq{eq:tropical} for computing $\alpha(G)$.
-     (b) is the backward pass for computing Boolean gradients as masks.
-     (c) is the masked forward pass with algebra \Eq{eq:countingtropicalset} for enumerating configurations.}
+Here, a circle is a tensor, an arrow specifies the execution direction of a function, $\overline A$ is the Boolean mask for $A$ and $\circ$ is the Hadamard (element-wise) multiplication.
+(a) is the forward pass with tropical algebra (\Eq{eq:tropical}) for computing $\alpha(G)$.
+     (b) is the backward pass for computing Boolean gradient masks.
+     (c) is the masked tensor network contraction with tropical algebra combined with sets (\Eq{eq:countingtropicalset}) for enumerating configurations.}
      \label{fig:bounding}

### 2022-04-19 paper/paper.tex
Updates from Overleaf

@@
     \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
-    \caption{The plot of pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
+    \caption{Pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
     In each plot, the $x$-axis is the Hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
-    The ``filled'' region is caused by the fast oscillation of configuration populations of even and odd Hamming distances.
     }

### 2022-05-07 paper/paper.tex
Updates from Overleaf

@@
 
-\title{Computing solution space properties of combinatorial optimization problems by generic programming tensor networks
+\title{Computing solution space properties of combinatorial optimization problems via generic %programming 
+tensor networks
 %\thanks{\funding{...}}
@@
 
-\author{
-Jin-Guo Liu\footnote{JIN-GUO LIU and XUN GAO contributed equally to this paper.}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
+\author{\footnote{Jin-Guo Liu and Xun Gao contributed equally to this work.}
+Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA  %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
     (\email{jinguoliu@g.harvard.edu}).}
 \and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}).}
-\and Madelyn Cain\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
-\and Mikhail D. Lukin\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA}
+\and Madelyn Cain\footnotemark[2]
+\and Mikhail D. Lukin\footnotemark[2]
 \and Sheng-Tao Wang\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
@@
 %We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
-We introduce a unified framework to compute the solution space properties of a class of combinatorial optimization problems including the independent set problem, the maximum cut problem, the vertex coloring problem, the clique problem, the dominating set problem, the set packing problem, the set covering problem, and the satisfiability problem.
+We introduce a unified framework to compute the solution space properties of a broad class of combinatorial optimization problems.
+%including the independent set problem, the maximum cut problem, the vertex coloring problem, the clique problem, the dominating set problem, the set packing problem, the set covering problem, and the satisfiability problem.
 %Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-These solution space properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
-We use the independent set problem as an example and show how all these solution space properties can be computed in the unified approach of generic programming tensor networks.
+These 
+%solution space 
+properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size. Using 
+%We use 
+the independent set problem as an example, we show how all these solution space properties can be computed in the unified approach of generic tensor networks.
 %By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
@@
 %The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
-To demonstrate the versatility of this computational tool, we apply it to several  examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
+We demonstrate the versatility of this computational tool by applying it to several  examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
 % including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
@@
 \begin{keywords}
-solution space property, tensor network, maximum independent set, independence polynomial, generic programming, combinatorial optimization problems
+solution space property, tensor networks, maximum independent set, independence polynomial, generic programming, combinatorial optimization 
 \end{keywords}
@@
 \section{Introduction}
-In graph theory and combinatorial optimization, there is an important class of problems that can be expressed as satisfiability problems involving constraints specified over a vertex and its neighborhood.
-These include, for example, the independent set problem, the cutting problem, the dominating set problem, the set packing problem, the set covering problem, the vertex coloring problem, the K-SAT problem, the clique problem, and the vertex cover problem~\cite{Moore2011}.
-They have a wide range of applications in scheduling, logistics,
-wireless networks and telecommunication, computer vision, etc.~\cite{Butenko2003, Wu2015}.
-Finding an optimum solution for these problems is typically NP-hard~\cite{Hastad1996}, which implies it is unlikely to be solved in a time polynomial with the size of the problem.
+
+An important class of problems in graph theory and combinatorial optimization  can be formulated as satisfiability problems involving constraints specified over a vertex and its neighborhood.
+These include, for example, the independent set, the cutting problem, the dominating set, the set packing and  the set covering, the vertex coloring problem, the K-SAT,  the clique problem, and the vertex cover problem~\cite{Moore2011}.
+These problems have a wide range of applications in scheduling, logistics,
+wireless networks and telecommunication, and computer vision, among others~\cite{Butenko2003, Wu2015}.
+Finding an optimum solution for these problems is typically NP-hard~\cite{Hastad1996}.
+%, which implies they can not to be solved in a time that scales polynomialy  with the size of the problem.
 
@@
 
-In this paper, we introduce a unified framework to compute a broad class of quantities associated with these problems, beyond just finding an optimum solution.
+In this Article, we introduce a unified framework to compute a broad class of properties 
+associated with the solutions of these problems, beyond just finding an optimum solution.
 We call them \textit{solution space properties}.
-In practice these can be much harder to compute (corresponding e.g.\ to \#P-complete class).
+In practice, these can be much harder to compute (corresponding e.g.\ to \#P-complete class~\cite{Moore2011}).
 However, these properties can be crucial for understanding detailed properties of hard combinatorial optimization problems.
@@
 %Solution space property computation allows us to understand the solution space better.
-They can be used to understand the hardness of finding an optimum solution for a problem instance and the performance of a solver in computing the solution for the given instance.
+They can be used to understand the hardness of finding an optimum solution for a given problem instance and the performance of a specific solver.  
+%in computing the solution for the given instance.
 For example, the number of configurations at different sizes can inform how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
 %In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018},
-The pair-wise Hamming distance distribution of configurations at a given size can indicate the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local search algorithms.
+The pair-wise Hamming distance distribution of configurations at a given size can indicate the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local optimization algorithms.
 %a no-go theorem about when the solution space geometry is formidably
 %hard for any local search algorithm.
-In a recent experiment based on a Rydberg atom array quantum computer, the authors use the counting and the configuration space connectivity information to find maximum independent set (MIS) problem instances that are hard for simulated annealing \cite{Ebadi2022}.
+In a recent experiment based on a Rydberg atom array quantum computer, 
+%the authors use 
+the counting and the configuration space connectivity information was used to find maximum independent set (MIS) problem instances that are hard for simulated annealing and to evaluate the corresponding quantum algorithm performance \cite{Ebadi2022}.
 % In a recent experiment using a Rydberg atom array quantum simulator to find maximum independent sets (MIS) of a graph~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for simulated annealing.
@@
 %to solve these instances faster, 
-The need to understand this experiment motivates us to find methodologies to compute these solution space properties.
+The need for understanding these important aspects of combinatorial optimization motivates us to find methodologies to compute these solution space properties.
 %\purple{I would give examples of why we want to compute solution space properties.
@@
 
-With \textit{generic tensor networks}, we show how to solve all of these seemingly unrelated properties in a unified approach.
+To this end, we show how to obtain all of these seemingly unrelated properties in a unified approach using
+\textit{generic tensor networks}.
 Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}.
@@
 Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-
 %The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
@@
 %However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-
-To keep the discussion focused, we mainly study the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in  \App{sec:otherproblems}, which include the cutting problem, the matching problem, the vertex coloring problem, the satisfiability problem, the dominating set problem, the set packing problem, the set covering problem, and the clique problem.
+%To keep the discussion focused, 
+In what follows, for clarity of presentation, we focus on the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in  \App{sec:otherproblems}.
+The latter include cutting, matching, vertex coloring, satisfiability,  dominating set,  set packing,  set covering, and the clique problem.
 %\xpurple{More details on which combinatorial optimization problems this applies to?}
+
 The paper is organized as follows.
@@
 
-\section{Example case studies} \label{sec:examples}
+\section{Example applications} \label{sec:examples}
 %In this section, we give a few examples where the different properties of independence sets are used.
 
-\subsection{Number of independent sets and entropy constant for some hardcore lattice gases}\label{sec:entropy}
+\subsection{Number of independent sets and entropy constant for hardcore lattice gases}\label{sec:entropy}
 We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
@@
 
-A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can tell us the thermodynamic properties of hard-core lattice gases at the high-temperature limit.
+A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can describe the thermodynamic properties of hard-core lattice gases at the high-temperature limit.
 For the square lattice graphs, this number is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
@@
 They may be used to study phase transitions for disordered lattices, which are typically much harder to understand.
-Interestingly, the variations due to different random instances are negligible for this entropy quantity.
+Interestingly, the variations due to different random instances are negligible for this quantity.
 % \blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
@@
 We inspect two types of graphs that are particularly interesting, the King's graphs with defects and $3$-regular graphs.
-It was known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Ebadi2022}.
+It is known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Garey1977,Ebadi2022}.
 However, it is not clear whether the MIS problem defined on a randomly generated King's graph with defects can have the overlap gap property.
-It was known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, but, it is not known whether, for small $d$, e.g.\ for $3$-regular graphs, this statement remains true.
+It is known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, but, it is not known whether, for small $d$, e.g.\ for $3$-regular graphs, this statement remains true.
 We randomly generated $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
@@
 For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Fig{fig:hamming}.
-We observed a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs, indicating the absence of the overlap gap property in a random King's graph at $0.8$ filling.
-Given the fact that the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling, this result is highly nontrivial.
-We argue that the King's graphs with defects mapped from hard MIS instances might have a very small measure in the total defected King's graph space.
-Very different pair-wise Hamming distributions are shown in \Fig{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
+We observe a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs, indicating the absence of the overlap gap property in a random King's graph at $0.8$ filling.
+Since the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling, this result is highly nontrivial. It likely implies 
+that the King's graphs with defects mapped from hard MIS instances have a very small measure in the total defected King's graph space. In contrast, 
+very different pair-wise Hamming distributions are obtained in \Fig{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
 It indicates the existence of disconnected clusters in the configuration space of the MIS problem on $3$-regular graphs.
-We expect our numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
+We expect this numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
 \begin{figure} 
@@
 %\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
-\subsection{Analyzing quantum and classical algorithms for solving Maximum Independent Set}
+\subsection{Analyzing quantum and classical algorithms for Maximum Independent Set}
 \begin{figure} 
@@
 \end{figure}
-The ability to enumerate configurations and compute independence polynomials was critical in understanding the performance of quantum and classical algorithms for MIS in a recent experiment on a Rydberg atom quantum computer~\cite{Ebadi2022}.
-In this work, the authors found that on King's graphs with $0.8$ filling, the hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
-On the hardest graph instances for simulated annealing studied in the experiment, a high density of local minima were present at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimum solution of size $\alpha(G)$.
-Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space.
-However, by enumerating the configurations, it was then found that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
-Therefore, it was the large ratio of local to global minima that prevents simulated annealing from efficiently finding the MIS.
+In a recent work, 
+the ability to enumerate configurations and compute independence polynomials was critical in understanding the performance of quantum optimization algorithms for the MIS problem on a Rydberg atom quantum computer~\cite{Ebadi2022}.
+This work focused on
+%, the authors found that
+exploring King's graphs with $0.8$ filling.
+The hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
+On the hardest graph instances for simulated annealing studied in the experiment, a high density of local minima were found at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
+%Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space. However, 
+By enumerating the configurations using techniques described in the present work, we found that %n found that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead
+simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
+Therefore, the large ratio of local to global minima  prevents simulated annealing from efficiently finding an MIS.
 %and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
@@
 
-Although the performance of the quantum algorithm was more challenging to understand due to the inherent difficulty in studying quantum systems, the authors were able to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
+Although the performance of the quantum algorithm is more challenging to understand due to the inherent difficulty in studying quantum systems, the present methods allow one 
+to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
 Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
@@
 The solution space graph is well-connected by local changes to the spin configurations, has a small diameter, and the degree of each node appears to concentrate. 
-From this visualization, the authors inferred that the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms by Ref.~\cite{altshuler2010}, which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
-Rather, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
+This visualization makes it clear that 
+%the authors inferred that 
+the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms e.g.
+by Ref.~\cite{altshuler2010}  which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
+Instead, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
+In the case where a large superposition state of local minima is created during the coherent evolution, the quantum algorithm achieves a quadratic speedup over simulated annealing.
 %Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
@@
 \section{Discussion and conclusion}
-In conclusion, in this paper, we introduce a unified framework using generic tensor networks to compute different solution space properties of a certain class of NP-hard combinatorial optimization problems.
-These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
-For each solution space property, we compute it with the same tensor network by replacing the tensor elements with those having an algebra designed for it.
+In this work, we introduced a framework that uses generic tensor networks to compute different solution space properties of a certain class of NP-hard combinatorial optimization problems.
+%These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
+Each solution space property is computed using the same tensor network with different tensor element algebra.
 % This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
@@
 The different data types introduced in the main text to compute these properties are summarized in the diagram in \Fig{fig:venn-diagram}.
-The class of problems solvable by a tensor network includes but is not limited to maximal independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \App{sec:otherproblems}.
+The class of problems solvable by a tensor network includes but is not limited to maximum independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \App{sec:otherproblems}.
 
@@
 
-It would be interesting to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and explore what new properties can be computed.
-To this end, it is worth mentioning the dynamic programming~\cite{Courcelle1990, Fomin2013} approaches.
+Looking ahead, it could be possible to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and explore what new properties can be computed.
+To this end, dynamic programming~\cite{Courcelle1990, Fomin2013} approaches could be considered.
 Dynamic programming is closely related to a tropical tensor network~\cite{Liu2021}; for example, the Viterbi algorithm for finding the most probable configuration in a hidden Markov model can be interpreted as a matrix product state featured with tropical algebra, and the tropical tensor network in the main text is potentially equivalent to dynamic programming in finding an optimum solution.
-However, while having broader applications, dynamic programming does not have a clear algebraic interpretation required by computing solution space properties beyond finding an optimum solution.
+Since dynamic programming has much broader applications, it would be interesting to extend the ideas from this paper to provide an algebraic interpretation for dynamic programming so that it can be used to compute other solution space properties beyond just finding an optimum solution.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 
-The source code in Julia language for this paper can be found in our Github repository~\cite{GenericTensorNetworks}. 
+The source code in Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
 There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.

### 2022-05-11 paper/paper.tex
update author info

@@
 
-\author{\footnote{Jin-Guo Liu and Xun Gao contributed equally to this work.}
+\author{
 Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA  %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
     (\email{jinguoliu@g.harvard.edu}).}
-\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}).}
+\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}, contributed equally with Jin-Guo Liu to this work.).}
 \and Madelyn Cain\footnotemark[2]

### 2022-05-11 notebooks/hexagon.jl

@@ -1,305 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.15.1
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ ad82840f-f908-49f8-9bc0-091b0ceaafad
-using Pkg; Pkg.activate()
-
-# ╔═╡ 50862912-0ed6-11ec-3db0-01dce2a8a110
-using OMEinsum, SymEngine
-
-# ╔═╡ 67f68723-cb66-44c1-8c04-83eacf6eaaf0
-using Test
-
-# ╔═╡ 809e5737-3dd3-4d1f-817a-76b9d61dbd25
-using Roots
-
-# ╔═╡ 0077b8a4-207a-4dff-b4f1-4ece3055e9f5
-using Zygote
-
-# ╔═╡ 611e081b-f99c-4304-8e15-276523345ad3
-using Optim
-
-# ╔═╡ 5a96edc0-b8a1-4da8-885a-5e1d3e7a74fe
-using StochasticOptimizers
-
-# ╔═╡ ffb21993-9d10-4a66-b0a7-453670c80503
-b, g, ξ, η, z = Basic.((:b, :g, :ξ, :η, :z))
-
-# ╔═╡ b0c4c062-8a59-45a6-aecb-f122a4c5e878
-A = [1, b]
-
-# ╔═╡ a1b3cde7-61a4-4ea1-95ff-d24299afd6ab
-F = [1 g; g 0]
-
-# ╔═╡ f7c88204-8a60-4dca-8914-9ce998fe4236
-w = let
-	x = zeros(Basic, 2,2,2)
-	x[1,1,1] = one(Basic)
-	x[1,1,2] = x[2,1,1] = x[1,2,1] = Basic(z)^(1//6)
-	x
-end
-
-# ╔═╡ 62e6be7b-4705-4255-a3ef-5833f268f24c
-md"4a"
-
-# ╔═╡ 9a277a55-feb4-4ec9-b8b0-06ee7cdfee4f
-ein"(ab,(b,b)),ba->a"(F,A,A,F)
-
-# ╔═╡ 8fca3104-230b-4ad2-bcfa-eb652b7a1e6b
-ein"(a,a),(a,a)->a"(A,A,A,A)*ξ
-
-# ╔═╡ 85af48ad-a493-4e10-b489-42ce6470612a
-md"4b"
-
-# ╔═╡ 8a5f7449-83e8-48ad-96bc-08b9b97df72a
[…]

### 2022-05-11 notebooks/proofs.jl

@@ -1,602 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.2
-
-using Markdown
-using InteractiveUtils
-
-# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
-macro bind(def, element)
-    quote
-        local el = $(esc(element))
-        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
-        el
-    end
-end
-
-# ╔═╡ c8c14900-b7f5-11eb-3dbe-4390dd0fcc0a
-begin
-	using Pkg
-	Pkg.activate(pwd())
-	using Revise, OMEinsum, OMEinsumContractionOrders, TropicalNumbers, NoteOnTropicalMIS, Compose, Viznet, PlutoUI
-	using OMEinsumContractionOrders: uniformsize
-	function savetodisk(obj, filename)
-		obj |> SVG(filename*".svg")
-	end
-end;
-
-# ╔═╡ 2a37780e-53b6-4a40-9738-5daba20c1001
-begin
-	node_black = nodestyle(:circle, r=0.03)
-	node_red = nodestyle(:circle, fill("red"), r=0.03)
-	node_white = nodestyle(:circle, fill("white"), r=0.08)
-	edge_black = bondstyle(:default)
-	text_black = textstyle(:default)
-	text_white = textstyle(:default, fill("white"))
-	
-	function save_pdf(img, fname, save)
-		if save
-			img |> SVG("$fname.svg")
-			run(`rsvg-convert -f pdf -o $fname.pdf $fname.svg`)
-		end
-		return img
-	end
-	
-	mis_solve(code) = mis_contract(Tropical(1.0), OMEinsum.optimize_greedy(code, uniformsize(code, 2)))
[…]

### 2022-05-11 notebooks/regular-generic.jl

@@ -1,157 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.2
-
-using Markdown
-using InteractiveUtils
-
-# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
-macro bind(def, element)
-    quote
-        local el = $(esc(element))
-        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
-        el
-    end
-end
-
-# ╔═╡ 4e4610ca-99e9-43e5-906b-c4f86e17ecd4
-begin
-	using Revise
-	using NoteOnTropicalMIS
-	using NoteOnTropicalMIS.OMEinsum, NoteOnTropicalMIS.TropicalNumbers, NoteOnTropicalMIS.Polynomials, NoteOnTropicalMIS.TropicalGEMM
-	using OMEinsumContractionOrders, PlutoUI
-end
-
-# ╔═╡ c5db88b3-f294-458f-aaf4-f4c50abc8e4e
-using ProfileSVG
-
-# ╔═╡ 525ecde1-d55c-4bde-833e-e5a2bd591165
-using TensorOperations, LinearAlgebra
-
-# ╔═╡ 18124cde-bdf0-11eb-382a-a727d1fbe17a
-md"# Tensor network playground
--- Random Regular graphs"
-
-# ╔═╡ 7be402c5-bc70-49d9-aeb2-2cc4783660cd
-md"## Generate a random-regular graph"
-
-# ╔═╡ d704acbf-12c0-4468-b122-3f25406e2e5a
-n = 200;
-
-# ╔═╡ 5527cdcb-dc41-4237-aeb0-f38b1e218729
-k = 3;
-
-# ╔═╡ aa4fec11-2e61-4dd1-9484-3aca470f07bf
-code = random_regular_eincode(n, k);
-
-# ╔═╡ c7e48886-3cc4-44cf-a9dd-0fa54f05c860
-md"""
-contraction order optimizer $(@bind order_optimizer Select(["Greedy", "KaHyPar"]))
-"""
-
-# ╔═╡ 4480b2b7-4676-4980-a0a9-13831e223e27
-let
-	if order_optimizer == "Greedy"
-		@doc optimize_greedy
-	else
-		md"""
-$(@doc optimize_kahypar)
[…]

### 2022-05-11 notebooks/tropicalwidget.jl

@@ -1,930 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.15.0
-
-using Markdown
-using InteractiveUtils
-
-# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
-macro bind(def, element)
-    quote
-        local el = $(esc(element))
-        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
-        el
-    end
-end
-
-# ╔═╡ 53ce616e-8055-11eb-0caf-e968c041ff4f
-using Revise, Viznet, Compose, TropicalNumbers, OMEinsum
-
-# ╔═╡ a4faf523-31f2-4446-82d2-059e39793e62
-using PlutoUI
-
-# ╔═╡ 448c3e6a-8203-11eb-2c9e-fd7d2a3db9d2
-using Profile
-
-# ╔═╡ 30b768c5-0ce0-4f4a-9981-a23f169b4a96
-function vizconfig(nodes, edges, config=zeros(Int, length(nodes)); xyratio=1.0)
-	X = 12cm
-	Y = xyratio * 12cm
-	Compose.set_default_graphic_size(X, Y)
-	tb = textstyle(:default, fill("white"))
-	nb = nodestyle(:default)
-	nb2 = nodestyle(:default, fill("red"))
-	eb = bondstyle(:default)
-	img = canvas() do
-		for (i, (t, p)) in enumerate(nodes)
-			(config[i]==1 ? nb2 : nb) >> p
-			tb >> (p, t)
-		end
-		for (i,j) in edges
-			eb >> (nodes[i].second, nodes[j].second)
-		end
-	end
-	Compose.compose(context(0, (1-X/Y)/2, 1.0, X/Y), img)
-end
-
-# ╔═╡ 100e3eb1-9d5c-4ae0-9a1b-d279927443fc
-md"## We have a unit disk gadget"
-
-# ╔═╡ 6c9ed9a9-4579-4260-adba-6af2df243ec1
-# find edges in a unit disk graph, returns a vector of tuples
-function find_edges(nodes, distance)
-	edges = Tuple{Int,Int}[]
[…]

### 2022-05-11 notebooks/tropicalwidget_simple.jl

@@ -1,101 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.2
-
-using Markdown
-using InteractiveUtils
-
-# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
-macro bind(def, element)
-    quote
-        local el = $(esc(element))
-        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
-        el
-    end
-end
-
-# ╔═╡ 53ce616e-8055-11eb-0caf-e968c041ff4f
-begin
-	using Revise
-	using Pkg
-	Pkg.activate(pwd())
-	using LightGraphs # graph support
-	using PlutoUI
-	using Viznet, Compose
-	using TropicalNumbers, OMEinsum, NoteOnTropicalMIS#, TropicalGEMM
-end
-
-# ╔═╡ 100e3eb1-9d5c-4ae0-9a1b-d279927443fc
-md"## We have a unit disk gadget"
-
-# ╔═╡ efdc5d3e-58e0-410d-b15a-2363e9c9f156
-locs = let
-	a = 0.12
-	ymid = xmid = 0.5
-	X = 0.33
-	Y = 0.17
-	D = 0.15
-	y = [ymid-Y, ymid-Y+D, ymid-a/2, ymid+a/2, ymid+Y-D, ymid+Y]
-	x = [xmid-X, xmid-X+D, xmid-1.5a, xmid-a/2, xmid+a/2, xmid+1.5a, xmid+X-D, xmid+X]
-	xmin, xmax, ymin, ymax = x[1], x[end], y[1], y[end]
-	[(xmid, y[1]), (xmin, ymid), (xmid, ymax), (xmax, ymid),
-		(x[3], y[3]), (x[4], y[3]),
-		(x[5], y[3]), (x[6], y[3]), (x[3], y[4]),
-		(x[4], y[4]), (x[5], y[4]), (x[6], y[4])]
-end
-
-# ╔═╡ 9d0ba8b7-5a34-418d-97cf-863f376f8453
-graph = NoteOnTropicalMIS.unitdisk_graph(locs, 0.23) # SimpleGraph
-
[…]

### 2022-05-11 notebooks/tutorial-basic.jl

@@ -1,209 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.14.2
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ 4e4610ca-99e9-43e5-906b-c4f86e17ecd4
-using OMEinsum, LightGraphs, TropicalNumbers
-
-# ╔═╡ f67a7abb-d96c-4167-962f-b9afa23300cd
-using Polynomials
-
-# ╔═╡ 0fd7b695-fd29-4570-b33f-a9261565b06b
-using ForwardDiff
-
-# ╔═╡ 496e51c1-6189-4cd2-8f82-8f0f6767f3b6
-using Zygote
-
-# ╔═╡ 18124cde-bdf0-11eb-382a-a727d1fbe17a
-md"# Solving MIS with generic einsum
-
-*A simple introduction that even a gorilla can understand*
-
-Jinguo Liu"
-
-# ╔═╡ 7be402c5-bc70-49d9-aeb2-2cc4783660cd
-md"## Generate a graph"
-
-# ╔═╡ 21165778-a9c7-452d-8330-451550c4176f
-n, k = 16, 3
-
-# ╔═╡ 6329fc8b-2956-4b90-9323-b21704e3c08f
-g = LightGraphs.random_regular_graph(n, k)
-
-# ╔═╡ b326c7f2-2caf-4cbd-9749-76307a984ace
-md"## Generate the einsum code for the graph"
-
-# ╔═╡ 47c852b5-9cc4-4691-8264-4b314359efc6
-md"`einsum` is the so called Einstein's notation, it loops over indices, multiplies elements, and accumulates the results to the output tensor. e.g. the following statement does the matrix multiplication"
-
-# ╔═╡ aa743568-a195-4f0f-aff7-8a8f77c125a6
-ein"ij,jk->ik"(randn(2,2), randn(2,2))
-
-# ╔═╡ 8f1198cd-b342-4bad-8158-576e2f01ca21
-md"The following statement does the trace"
-
-# ╔═╡ f043399f-6ef8-41bf-bdb5-8899109faad1
-ein"ii->"(randn(2,2))
-
-# ╔═╡ 9e3adcec-c012-43c5-8527-04e4e0674462
-md"The following statement does the MPS contraction"
-
[…]

### 2022-05-12 paper/paper.tex
update author list

@@
 
-\title{Computing solution space properties of combinatorial optimization problems via generic %programming 
-tensor networks
+\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks
 %\thanks{\funding{...}}
@@
 \begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/QuEraComputing/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/TensorBFS/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
 	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.

### 2022-05-12 benchmarks/method_analysis.jl

@@ -1,18 +1,0 @@
-using MethodAnalysis
-using OMEinsum, GenericTensorNetworks, LightGraphs
-
-for i=1:10
-    print(i)
-    g = LightGraphs.random_regular_graph(100, 3)
-    id = Independence(g; optmethod=:tree, niters=10, ntrials=1)
-    solve(id, "counting all (finitefield)")
-end
-
-meths = []
-visit(OMEinsum) do item
-    isa(item, Method) && push!(meths, item)
-    true   # walk through everything
-end
-argmax(x->length(methodinstances(x)), meths)
-sorted_meths = sort(meths, by=x->length(methodinstances(x)), rev=true)
-println(length.(methodinstances.(sorted_meths[1:10])))

### 2022-05-12 paper.tex
change codes

--- 2022-05-12 paper/paper.tex
@@
 \begin{abstract}
-%We introduce a method that uses generic programming tensor networks to compute various properties of a class of hard graph problems that can be decribed by local constraints.
-%We introduce a tensor network algorithm %a method that combines generic programming and tensor network techniques 
 We introduce a unified framework to compute the solution space properties of a broad class of combinatorial optimization problems.
-%including the independent set problem, the maximum cut problem, the vertex coloring problem, the clique problem, the dominating set problem, the set packing problem, the set covering problem, and the satisfiability problem.
-%Let the independent set problem be an example, we show how to compute, for example, the maximum several independent set sizes, the counting of independent sets of a give size, the enumeration of independent sets of a given size.
-These 
-%solution space 
-properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size. Using 
-%We use 
-the independent set problem as an example, we show how all these solution space properties can be computed in the unified approach of generic tensor networks.
-%By making use of generic programming, our algorithms are very simple to implement and one can in addition directly utilize recent advances in tensor network contraction techniques such as near-optimal contraction order finding and slicing to achieve high performance.
-%By using generic programming techniques, the same framework can be used to compute all of these properties. 
-%Our algorithm utilizes recent advances in tensor network contraction techniques to achieve high performance, including methods to quickly find a near-optimal contraction order and slicing.
-%The algorithmic complexity of this approach is two to the treewidth of the line graph of the tensor network graph.
+These properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
+Using the independent set problem as an example, we show how all these solution space properties can be computed in the unified approach of generic tensor networks.
 We demonstrate the versatility of this computational tool by applying it to several  examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
-% including the calculations of the entropy constant for some hardcore lattice gases on 2D square lattices and the study of the overlap gap property on three regular graphs.
-%We show how our method helps to understand these hard problems on systems with hundreds of vertices.
 \end{abstract}
@@
 \begin{AMS}
-  05C31, 14N07
+  15A69, 05C31, 14N10
 \end{AMS}
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig1.pdf}
     \caption{Benchmark results for computing different solution space properties of independent sets of random three-regular graphs with different tensor element types.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/lattices.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{lattices.pdf}
     \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig5.pdf}
     \caption{Mean entropy for lattice gases on graphs defined in \Fig{fig:lattices}.
@@
     % \end{subfigure}
-    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
+    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{fig6.pdf}
     \caption{Pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
@@
     \centering
-    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/exp_configurations.pdf}
+    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{exp_configurations.pdf}
     \caption{Visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem~\cite{Ebadi2022}.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig2.pdf}
     \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
@@
     \centering
-    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
+    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{masktree.pdf}
     \caption{Bounded enumeration of maximum independent sets.
@@
 
-\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
+\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{fig7.pdf}}
 
@@
 
-\lstinputlisting[breaklines]{../democode/demo.jl}
+\lstinputlisting[breaklines]{demo.jl}
 

### 2022-05-23 paper/paper.tex
add ref
fix citations

@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
+A tensor network~\cite{Cirac2021, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
 The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
@@
 Since dynamic programming has much broader applications, it would be interesting to extend the ideas from this paper to provide an algebraic interpretation for dynamic programming so that it can be used to compute other solution space properties beyond just finding an optimum solution.
+It is also possible to extend this idea to other algebras.
+For example, generic semiring algebra has been used in computational linguishtics to compute interesting quantities of a given grammar and string.~\cite{Goodman1999}.
 %Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
@@
 We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. 
+We thank Jacob Miller for helpful discussions. 
 We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman, and Katharine Hyatt

### 2022-06-06 paper/paper.tex
update

@@
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three example applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
+Lastly, we provide three example applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
+A benchmark to demonstrate the performance of our algorithms can be found in both the supplementary material and the code repository.
 %In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
@@
 Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors. 
-While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \App{sec:tensorbad}.
+While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in the supplementary material.
 % because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
@@
 For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory-efficient method to find the polynomial by contracting and fitting on finite field algebra.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round-off errors.
 For simplicity, we use this less efficient polynomial algebra for the discussion in the main text.
@@
 The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$.
-An efficient algorithm for computing the maximum sum combination problem can be found in \App{sec:maxsum}.
+An efficient algorithm for computing the maximum sum combination problem can be found in the supplementary material.
 The vertex tensor and edge tensor become
@@
 Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
-
-\section{Performance benchmarks}\label{sec:benchmark}
-We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
-The results are summarized in Figure~\ref{fig:benchmark}.
-The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
-In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming~\cite{Courcelle1990, Fomin2013}.
-To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
-The main goal of this section is to show the relative computation time for calculating different solution space properties.
-
-\begin{figure} 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
-    \caption{Benchmark results for computing different solution space properties of independent sets of random three-regular graphs with different tensor element types.
-    The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
-    Legends are properties, algebra, and devices that we used in the computation; one can find the corresponding computed solution space property in \Tbl{tbl:generictypes}.
-    (a) time and space complexity versus the number of vertices for the benchmarked graphs.
-    (b) The computation time for calculating the MIS size and for counting the number of all independent sets (ISs), the number of MISs,
-        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest set sizes.
-    (c) The computation time for calculating the independence polynomials with different approaches.
-    (d) The computation time for configuration enumeration, including single MIS configuration, the enumeration of all independent set configurations, all MIS configurations, all independent sets,
-    and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$.
-    }
-    \label{fig:benchmark}
-\end{figure}
-
-Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
-The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
-If we assume our contraction-order finding program has found the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
-Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
-One can see that all the computation times in figure~\ref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
-While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
-Among these benchmarks, computational tasks with data types real numbers, complex numbers, or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
-These tasks usually compute much faster than ones with other element types in the same category.
-Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
-These data types do not include those defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr} or a data type containing them as a part.
-In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
-In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
-The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
 
@@
 The source code in Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
-There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
+There is a short introduction to this repository as well a gist to show how it works in the supplementary material as well.
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
@@
 If we further let $w_i=1$, the second line of \Eq{eq:partition} is equivalent to the independence polynomial.
-
-\section{An example of increased contraction complexity for the standard tensor network notation}\label{sec:tensorbad}
-
-In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice: either both are in input tensors (which will be summed over) or one is in an input tensor and another in the output tensor.
-Hence a tensor network can be represented as an open simple graph, where an input tensor is mapped to a vertex, a label shared by two input tensors is mapped to an edge and a label that appears in the output tensor is mapped to an open edge.
-A standard tensor network notation is equivalent to the generalized tensor network in representation power.
-A generalized tensor network can be converted to a standard one by adding a $\delta$ tensors at each hyperedge, where a $\delta$ tensor of rank $d$ is defined as
-\begin{equation}
-    \delta_{i_1, i_2,\ldots,i_d} = \begin{cases}
-        1, & i_1=i_2=\ldots =i_d,\\
-        0, & \text{otherwise}.
-    \end{cases}
-\end{equation}
-
-In the following example, we will show this conversion might increase the contraction complexity of a tensor network.
-Let us consider the following King's graph. \\
-
-\centerline{\begin{tikzpicture}
-    \def\r{0.2}
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}
-            \filldraw[fill=black] (\x,\y) circle [radius=\r];
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,4}{
-            \draw [black,thick] (\x,\y) -- (\x,\y+1);
-            \draw [black,thick] (\y,\x) -- (\y+1,\x);
-        }
-    \foreach \x in {1,...,4}
-        \foreach \y in {1,...,4}{
-            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
-            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
-        }
-\end{tikzpicture}}
-
-The generalized tensor network for solving the MIS problem on this graph has the following hypergraph representation, where we use different colors to distinguish different hyperedges.
-
-\centerline{\begin{tikzpicture}
-    \def\r{0.08}
-    \def\a{0.07}
-    \def\L{0.6}
-    \def\l{0.1}
-    \def\sql{0.24}
-    \pgfmathsetseed{2}
-    \foreach[evaluate={\cr=0.1+0.5*Mod(\x,2)}] \x in {1,...,5}
-        \foreach[evaluate={\cg=0.1+0.3*Mod(\y,2); \cy=0.5-0.5*Mod(\y,2)}] \y in {1,...,5}{
-            \edef\R{\pdfuniformdeviate 255}
-            \edef\G{\pdfuniformdeviate 255}
-            \edef\B{\pdfuniformdeviate 255}
-            \xdefinecolor{MyColor}{RGB}{\R,\G,\B}
-            \ifnum \x < 5
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.5,\y);
-                \ifnum \y < 5
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y+0.3);
-                \fi
-                \ifnum \y > 1
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y-0.3);
-                \fi
-            \fi
-            \ifnum \x > 1
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.5,\y);
-                \ifnum \y < 5
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y+0.7);
-                \fi
-                \ifnum \y > 1
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y-0.7);
-                \fi
-            \fi
-            \ifnum \y < 5
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y+0.5);
-            \fi
-            \ifnum \y > 1
-                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y-0.5);
-            \fi
-        }
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}{
-            %\filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
-        }
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}{
-            \ifnum \y < 5
-                \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
-                \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
-            \fi
-        }
-    \foreach \x in {1,...,4}
-        \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
-            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
-        }
-    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
-                    post length=0mm,pre length=0mm}}
-    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
-\end{tikzpicture}}
-Vertex tensors are not shown here because they can be absorbed into an edge tensor and hence do not change the contraction complexity.
-If we contract this tensor network in the column-wise order, the maximum intermediate tensor has rank $\sim L$, which can be seen by counting the number of colors at the cut.
-
-By adding $\delta$ tensors to hyperedges, we have the standard tensor network represented as the following simple graph.
-
-\centerline{\begin{tikzpicture}
-    \def\r{0.08}
-    \def\a{0.1}
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,5}
-            \filldraw[fill=black] (\x,\y) circle [radius=\r];
-    \foreach \x in {1,...,5}
-        \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
-            \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
-            \draw [black,thick] (\x,\y) -- (\x,\y+1);
-            \draw [black,thick] (\y,\x) -- (\y+1,\x);
-        }
-    \foreach \x in {1,...,4}
-        \foreach \y in {1,...,4}{
-            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
-            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
-            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
-            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
-        }
-    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
-                    post length=0mm,pre length=0mm}}
-    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
-\end{tikzpicture}}
-
-In this diagram, the additional $\delta$ tensors can have ranks up to $8$.
-If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e.
-the space complexity is $\approx 2^{3L}$, which has a larger complexity than using the generalized tensor network notation.
 
@@
 
-We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
-including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
-\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
-In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
-
-\begin{figure} 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
-    \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
-    (a) time and space complexity of tensor network contraction. 
-    (b) The wall clock time for counting and enumeration of maximal ISs. % The missing data is due to the memory limit.
-    }
-    \label{fig:benchmark-maximal}
-\end{figure}
+The benchmark of computing the maximal independent set properties on $3$-regular graphs is shown in the supplementary material.
 
@@
 
-\section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
-
-In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
-One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
-Here, we show an alternative method with standard number types but with controllable round-off errors.
-Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
-The linear equation thus becomes
-\begin{equation}
-\left(\begin{matrix}
-1 & r & r^2 & \ldots & r^{\alpha(G)} \\
-1 & r\omega & r^2\omega^2 & \ldots & r^{\alpha(G)} \omega^{\alpha(G)} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & r\omega^{\alpha(G)} & r^2\omega^{2{\alpha(G)}} & \ldots & r^{\alpha(G)}\omega^{{\alpha(G)}^2}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
-\end{matrix}\right).
-\end{equation}
-
-Let us rearrange the coefficients $r^j$ to $a_j$, the matrix on the left side becomes the discrete Fourier transform matrix.
-Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
-By choosing different $r$, one can obtain better precision for small $j$ by choosing $r<1$ or large $j$ by choosing $r>1$.
+Alternatively, one can use a faster but less accurate Fourier transformation based method to fit this polynomial, which is detailed and benchmarked in the supplementary material.
 
@@
 
-\section{Computing maximum sum combination}\label{sec:maxsum}
-Given two sets $A$ and $B$ of the same size $n$.
-It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
-The standard approach to solve the sum combination problem requires storing the variables in a heap --- a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
-In the following, we show an algorithm with roughly the same complexity but does not need a heap.
-This algorithm first sorts both $A$ and $B$ and then uses the bisection to find the $n$-th largest value in the sum combination.
-The key point is we can count the number of entries greater than a specific value
-in the sum combination of $A$ and $B$ in linear time.
-As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
-We summarize the algorithm as in Algorithm~\ref{alg:sumcombination}.
-
-\LinesNumberedHidden
-\begin{algorithm}[!ht]
-    \SetKwProg{Fn}{function}{}{end}
-    \small
-    \SetAlgoNoLine
-    Let $A$ and $B$ be two sets of size $n$\;
-
-    \tcp{sort $A$ and $B$ in ascending order}
-    $A \gets {\rm sort}(A)$\;
-
-    $B \gets {\rm sort}(B)$\;
-
-    \tcp{use bisection to find the $n$-th largest value in sum combination}
-
-    ${\rm high} \gets A_n+B_n$\;
-
-    ${\rm low} \gets A_1+B_n$\;
-
-    \While{true}{
-        ${\rm mid} \gets ({\rm high} + {\rm low}) / 2$\;
-
-        $c \gets \texttt{count\_geq}(n, A, B, {\rm mid})$\;
-
-        \uIf{$c > n$}{
-            ${\rm low} \gets {\rm mid}$\;
-        }\uElseIf{$c = n$}{
-            \Return \texttt{collect\_geq}$(n, A, B, {\rm mid})$\;
-        }\Else{
-            ${\rm high} \gets {\rm mid}$\;
-        }
-    }
-
-    \Fn{{\rm \texttt{count\_geq}}($n$, $A$, $B$, $v$)}{
-        $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
-
-        $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
-
-        $c \gets 0$\; \tcp*[l]{the counting of sum combinations s.t. $a+b\geq v$}
-
-        \For{$q$ = $n, n-1 \ldots 1$}{
-            $b \gets B_{n-q+1}$\;
-
-            \While{$k < n$ \textbf{and} $a+b \geq v$}{
-                $k \gets k+1$\;
-
-                $a \gets A_{n-k+1}$\;
-            }
-
-            \uIf{$a+b \geq v$}{
-                $c \gets c + k$\;
-            }\Else{
-                $c \gets c + k-1$\;
-            }
-        }
-        \Return c\;
-    }
-
-    % \Fn{\rm collect\_geq($n$, $A$, $B$, $v$)}{
-    %     $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
-
-    %     $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
-
-    %     $S \gets \{\}$ \tcp*[l]{the sum combinations s.t. $a+b\geq v$}
-
-    %     \For{$q$ = $n, n-1 \ldots 1$}{
-    %         $b \gets B_{n-q+1}$\;
-
-    %         \While{$k < n$ \textbf{and} $a+b \geq v$}{
-    %             $k \gets k+1$\;
-
-    %             $a \gets A_{n-k+1}$\;
-    %         }
-
-    %         \uIf{$a+b \geq v$}{
-    %             $m \gets k$\;
-    %         }\Else{
-    %             $m \gets k-1$\;
-    %         }
-    %         \For{$j$ = \KwTo $1,2\ldots,m$}{
-    %             $S \gets S \cup \{b + A_{n-j+1}\}$
-    %         }
-    %     }
-    %     \Return S\;
-    % }
-    \caption{Fast sum combination without using heap}\label{alg:sumcombination} 
-\end{algorithm}
-
-In this algorithm, function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by collecting the items to a set.
-Inside the function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration and
-the total number of iterations is upper bounded by $2n$.
-Here for simplicity, we do not handle the special element $-\infty$ in $A$ and $B$ and the potential degeneracy in the sums.
-It is nevertheless important to handle them properly in a practical implementation.
-
-\section{Technical guides}\label{sec:technical}
-
-This appendix covers some technical guides for efficiency, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
-One can install \texttt{GenericTensorNetworks} in a Julia REPL, by first typing \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then typing
-\begin{lstlisting}
-pkg> add GenericTensorNetworks
-\end{lstlisting}
-followed by an \colorbox{lightgray}{\texttt{<ENTER>}} key.
-To use it for solving solution space properties, just go back to the normal mode (type \colorbox{lightgray}{\texttt{<BACKSPACE>}}) and type
-
-\begin{lstlisting}
-julia> using GenericTensorNetworks, Graphs
-
-julia> # using CUDA
-
-julia> solve(
-           IndependentSet(
-               Graphs.random_regular_graph(20, 3);
-               optimizer = TreeSA(),
-               weights = NoWeight(),
-               openvertices = ()
-           ),
-           GraphPolynomial();
-           usecuda=false
-       )
-0-dimensional Array{Polynomial{BigInt, :x}, 0}:
-Polynomial(1 + 20*x + 160*x^2 + 659*x^3 + 1500*x^4 + 1883*x^5 + 1223*x^6 + 347*x^7 + 25*x^8)
-\end{lstlisting}
-
-Here the main function \texttt{solve} takes three inputs: the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide to use GPU or not.
-If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
-The problem instance takes four arguments to initialize: the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()}, and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
-Here, we use the \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} as  default values.
-The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
-The first execution of this function will be a bit slow due to Julia's just-in-time compilation.
-After that, the subsequent runs will be faster.
-The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in the package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.
-
-\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
-
-The code we will show below is a gist of how the above package was implemented, which is mainly for pedagogical purpose.
-It covers most of the topics in the paper without caring much about performance.
-It is worth mentioning that this project depends on multiple open source packages in the Julia ecosystem:
-
-\begin{description}
-	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/TensorBFS/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
-	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
-	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in the Julia community.
-	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
-	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and the \href{https://github.com/JuliaMath/Primes.jl}{Primes}] package providing finite field algebra and prime number manipulation.
-\end{description}
-
-They can be installed in a similar way to \texttt{GenericTensorNetworks}.
-After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.
-
-\lstinputlisting[breaklines]{../democode/demo.jl}
-
 \end{document}

### 2022-06-06 paper/suppl.tex
update

--- 2022-05-12 paper.tex
@@
-\documentclass[onefignum, onetabnum]{siamart190516}
+%\documentclass[onefignum, onetabnum]{siamart190516}
+\documentclass[a4paper, 12pt]{article}
 %\usepackage{natbib}
@@
 \pdfoutput=1
-%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
 \usepackage[english]{babel}
@@
 %\usepackage{caption}
-%\usepackage[plain]{algorithmic}
-\usepackage[linesnumbered, ruled, vlined, algo2e]{algorithm2e}
+%\usepackage{algorithmic}
+\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
 \usepackage{algpseudocode}
@@
 \usepackage{txfonts}
+\setcounter{secnumdepth}{0}
 %\usepackage[epsilon, tsrm, altpo]{backnaur}
@@
 
-\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks
+\title{The supplementary material of ``Computing solution space properties of combinatorial optimization problems via generic tensor networks''
 %\thanks{\funding{...}}
@@
 \author{
-Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA  %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
-    (\email{jinguoliu@g.harvard.edu}).}
-\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}, contributed equally with Jin-Guo Liu to this work.).}
+Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA.}
+\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (contributed equally with Jin-Guo Liu to this work.).}
 \and Madelyn Cain\footnotemark[2]
@@
 
-\begin{abstract}
-We introduce a unified framework to compute the solution space properties of a broad class of combinatorial optimization problems.
-These properties include finding one of the optimum solutions, counting the number of solutions of a given size, and enumeration and sampling of solutions of a given size.
-Using the independent set problem as an example, we show how all these solution space properties can be computed in the unified approach of generic tensor networks.
-We demonstrate the versatility of this computational tool by applying it to several  examples, including computing the entropy constant for hardcore lattice gases, studying the overlap gap properties, and analyzing the performance of quantum and classical algorithms for finding maximum independent sets.
-\end{abstract}
-
-% REQUIRED
-\begin{keywords}
-solution space property, tensor networks, maximum independent set, independence polynomial, generic programming, combinatorial optimization 
-\end{keywords}
+\tableofcontents
 
@@
 % 14N07  	Secant varieties, tensor rank, varieties of sums of powers
-\begin{AMS}
-  15A69, 05C31, 14N10
-\end{AMS}
-
-\section{Introduction}
-
-An important class of problems in graph theory and combinatorial optimization  can be formulated as satisfiability problems involving constraints specified over a vertex and its neighborhood.
-These include, for example, the independent set, the cutting problem, the dominating set, the set packing and  the set covering, the vertex coloring problem, the K-SAT,  the clique problem, and the vertex cover problem~\cite{Moore2011}.
-These problems have a wide range of applications in scheduling, logistics,
-wireless networks and telecommunication, and computer vision, among others~\cite{Butenko2003, Wu2015}.
-Finding an optimum solution for these problems is typically NP-hard~\cite{Hastad1996}.
-%, which implies they can not to be solved in a time that scales polynomialy  with the size of the problem.
-
-% The most studied aspect of these problems is to find an optimum solution, 
-%The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
-% which is typically 
-%while many of them belong to the hardness category
-% NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a time polynomial with the size of the problem.
-
-% Many properties of these problems are in general intractable at large sizes (exponential run time in problem size in the worst case),
- %but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
-
-%\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
-%\blue{Here, we haven't mentioned the independent set, here ``version'' means, e.g.
-counting, enumeration, devision.
-I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
-
-In this Article, we introduce a unified framework to compute a broad class of properties 
-associated with the solutions of these problems, beyond just finding an optimum solution.
-We call them \textit{solution space properties}.
-In practice, these can be much harder to compute (corresponding e.g.\ to \#P-complete class~\cite{Moore2011}).
-However, these properties can be crucial for understanding detailed properties of hard combinatorial optimization problems.
-% In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
-% but they can be crucial towards understanding hard combinatorial optimization problems. 
-These \textit{solution space properties} can include not only the maximum or minimum set size but also the number of sets at a given size, enumeration of all sets at a given size, and direct sampling of such sets when they are too large to be fit into memory.
-% For the weighted version of the above problems, it also includes finding the largest or smallest $k$ sets and their sizes.
-%are many interesting and hard computational problems concerning various properties of independent sets.
-%Solution space property computation allows us to understand the solution space better.
-They can be used to understand the hardness of finding an optimum solution for a given problem instance and the performance of a specific solver.  
-%in computing the solution for the given instance.
-For example, the number of configurations at different sizes can inform how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
-%In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018},
-The pair-wise Hamming distance distribution of configurations at a given size can indicate the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local optimization algorithms.
-%a no-go theorem about when the solution space geometry is formidably
-%hard for any local search algorithm.
-In a recent experiment based on a Rydberg atom array quantum computer, 
-%the authors use 
-the counting and the configuration space connectivity information was used to find maximum independent set (MIS) problem instances that are hard for simulated annealing and to evaluate the corresponding quantum algorithm performance \cite{Ebadi2022}.
-% In a recent experiment using a Rydberg atom array quantum simulator to find maximum independent sets (MIS) of a graph~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for simulated annealing.
-%and design better quantum algorithms
-%to solve these instances faster, 
-The need for understanding these important aspects of combinatorial optimization motivates us to find methodologies to compute these solution space properties.
-%\purple{I would give examples of why we want to compute solution space properties.
-%For instance, in statistical physics, computing thermal states and
-%observables via the partition function. In complexity theory, proving limits on local algorithms (OGP).}\blue{now?}
-
-To this end, we show how to obtain all of these seemingly unrelated properties in a unified approach using
-\textit{generic tensor networks}.
-Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}.
-They are also known as the sum-product networks in probabilistic modeling~\cite{Bishop2006} or \texttt{einsum} in linear algebra libraries such as NumPy~\cite{Harris2020}.
-%\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
-Recent progress in simulating quantum circuits with tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} makes it possible to contract a randomly structured sparse tensor network with up to thousands of tensors in a reasonable time.
-%\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
-In previous studies, the data types of the tensor elements are typically restricted to standard number types such as real numbers and complex numbers.
-Here, we extend to \textit{generic tensor networks} by generalizing the tensor element data types to any type that has the algebraic structure of a commutative semiring.
-%These two algorithms are related but are not equivalent.
-%Dynamic programming is more general purpose, while a tensor network has a richer algebraic structure, and this structure is crucial for solution space property computation.
-%\purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
-%For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
-Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-%The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
-%Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
-%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
-%However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-%To keep the discussion focused, 
-In what follows, for clarity of presentation, we focus on the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in  \App{sec:otherproblems}.
-The latter include cutting, matching, vertex coloring, satisfiability,  dominating set,  set packing,  set covering, and the clique problem.
-%\xpurple{More details on which combinatorial optimization problems this applies to?}
-
-The paper is organized as follows.
-We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
-Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}. 
-Subsequently, we explain how to engineer the element types to compute various solution space properties in \Sec{sec:counting}, \Sec{sec:enumeration}, and \Sec{sec:weighted}.
-% to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs, respectively.
-% by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we benchmark our algorithms in \Sec{sec:benchmark} and provide three example applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
-%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
-We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
-%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
-%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
-This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
-%Our method can also be used to find ``maximal'' independent set properties; 
-%a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
-
-\section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2020, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
-The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
-For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are matrices (two-dimensional tensors), $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
-%can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
-%Generalized Einstein's notation is often used to represent a tensor network, where we use a label in the subscript to represent a degree of freedom.
-%One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-% Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
-% where we use a label in the subscript to represent a degree of freedom.
-% One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-% In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
-% Hence a tensor network can be represented as a open simple graph,
-% where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
-% In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
-The graphical representation of a tensor network is an open (meaning an edge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
-Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors. 
-While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \App{sec:tensorbad}.
-% because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-%However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
-
-\begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network that can be evaluated as $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
-Its hypergraph representation is shown below, where we use different colors to represent different hyperedges.
-
-\vspace{1em}
-\centerline{\begin{tikzpicture}[
-    dot/.style = {circle, fill, minimum size=#1,
-                inner sep=0pt, outer sep=0pt},
-    dot/.default = 6pt  % size of the circle diameter 
-                    ]  
-    \def\dx{0};
-    \def\r{0.5cm}
-    \def\sr{0.15cm}
-    \def\ax{0}
-    \def\ay{0}
-    \def\bx{1}
-    \def\by{1}
-    \def\cx{1}
-    \def\cy{-1}
-    \node[color=white,fill=black,dot=\r] at (\ax+\dx,\ax) (a) {A};
-    \node[color=white,fill=black,dot=\r] at (\bx+\dx,\by) (b) {B};
-    \node[color=white,fill=black,dot=\r] at (\cx+\dx,\cy) (v) {V};
-    \node[color=transparent,draw=transparent,dot=0] at (\ax-1,\by) (o1) {};
-    \node[color=transparent,draw=transparent,dot=0] at (\ax-1.5,\ay) (o2) {};
-    \node[color=transparent,draw=transparent,dot=0] at (\ax-1,\cy) (o3) {};
-    \node at (\ax-0.8,\ay) (k) {k};
-    \node at (\bx+0.4,\ay) (m) {m};
-    \node at (\ax,\cy) (j) {j};
-    \node at (\bx+1,\by) (l) {l};
-    \node at (\bx-1,\by) (i) {i};
-    \draw[color=blue,thick] (i) -- (b);
-    \draw[color=blue,thick] (i) -- (o1);
-    \draw[color=cyan,thick] (l) -- (b);
-    \draw[color=violet,thick] (k) -- (a);
-    \draw[color=violet,thick] (k) -- (o2);
-    \draw[color=black,thick] (b) -- (m);
-    \draw[color=black,thick] (m) -- (a);
-    \draw[color=black,thick] (m) -- (v);
-    \draw[color=red,thick] (a) -- (j);
-    \draw[color=red,thick] (v) -- (j);
-    \draw[color=red,thick] (o3) -- (j);
-\end{tikzpicture}}
-\end{example}
-
-\section{Generic programming tensor contractions}\label{sec:generic}
-%\purple{On a second read of this section, I think that the clarity could be improved.
-My understanding is this is the flow: We would like to use generic programming, where we write code that works regardless of input type, and is optimized on all input types without sacrificing efficiency.
-In general, we can write code such that a function runs correctly regardless of the input data type.
-This is easy to do for dynamically typed languages like Python, which only verify and enforce the rules for the input data type at run time (called type-checking).
-However, when the input data type is only checked at run time (as opposed to when the code is compiled), type-specific optimization cannot be used.
-High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
-In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
-%Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
-%However, the elements in a tensor do not have to be a regular number type, or even a field (since division is not used in tensor contraction).
-%One can use the same tensor contraction program for different purposes with different tensor element types.
-% We propose to not restricting our imagination to standard number types, but to use a more general element type with certain algebraic property.
-We propose to use more general element types with a certain algebraic property.
-With different data types, we can solve different problems within the same unified framework.
-This idea of using the same program for different purposes is also called generic programming in computer science:
-
-\begin{definition}[Generic programming ~\cite{Stepanov2014}]
-   Generic programming is an approach to programming that focuses on designing algorithms and data structures so that they work in the most general setting without loss of efficiency.
-\end{definition}
-This definition of generic programming covers two major aspects: ``work in the most general setting'' and ``without loss of efficiency''.
-By the most general setting, we mean that a single program should work correctly for the most general input data types. 
-%\purple{I think the following paragraph could be clarified.
-When you read the definition of generic programming, it's not clear what ``in the most general setting'' means.
-My understanding is it just means that the program will work regardless of the input data type - it would be good to say this explicitly.
-}
-%\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
-%\purple{I also think the way it is written takes a while to understand what dynamically versus statically typed languages are.
-The definition, “When these languages “see” a new input type, the compiler can recompile the generic program for the new type.” comes rather late in the paragraph.}
-%\xpurple{Also, while I know what you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
-%lost on someone only with a physics background.}
-%This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
-%To understand the first aspect on generality,
-For example, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
-One can easily write a function for standard number types that computes the power of $x$ in $O \left( \log(n) \right)$ steps using the multiply and square trick.
-Generic programming does not require $x$ to be a standard number type;
-instead, it treats $x$ as an element with an associative multiplication operation $\odot$ and a multiplicative identity $\mymathbb{1}$.
-Then, when the program takes a matrix as an input instead of a standard number type, it computes the matrix power correctly without rewriting the program.
-The second aspect is about efficiency. For dynamically typed languages such as Python, the type information is not available for type-specific optimizations at the compilation stage.
-Therefore, one can easily write code that works for general input types, but the efficiency is not guaranteed; for example, the speed of computing the matrix multiplication between two NumPy arrays with Python objects as elements is much slower than statically typed (i.e.
-the type information can be accessed at the compilation stage) languages such as C++ and Julia~\cite{Bezanson2012}.
-C++ uses templates for generic programming while Julia takes advantage of just-in-time compilation and multiple dispatches.
-When these languages ``see'' a new input type, the compiler recompiles the generic program for the new type to generate an efficient binary.
-A myriad of optimizations can be done during the compilation. For example, the compiler can optimize the memory layout of immutable elements with fixed sizes in an array to speed up array indexing.
-In Julia, if a type is immutable and contains no references to other values, an array of that type can even be compiled to graphics processing units (GPU) for faster computation~\cite{Besard2018}.
-
-This motivates us to identify the most general tensor element type allowed in a tensor network contraction program.
-We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
-Here, a commutative semiring is a field that needs not to have an additive inverse and a multiplicative inverse.
-Giving up these nice properties of fields has significant implications for tensor computation: tensor network compression algorithms might not be applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014} and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
-Here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
-\begin{align*}
-(a \oplus b) \oplus c = a \oplus (b \oplus c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\oplus$ with identity $\mymathbb{0}$}\\
-a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
-a \oplus b = b \oplus a &\\
-&\\
-(a \odot b) \odot c = a \odot (b \odot c)  &   \hspace{5em}\text{$\triangleright$ commutative monoid $\odot$ with identity $\mymathbb{1}$}\\
-a \odot  \mymathbb{1} =  \mymathbb{1} \odot a = a &\\
-a \odot b = b \odot a &\\
-&\\
-a \odot (b\oplus c) = a\odot b \oplus a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
-(a\oplus b) \odot c = a\odot c \oplus b\odot c &\\
-&\\
-a \odot \mymathbb{0} = \mymathbb{0} \odot a = \mymathbb{0}
-\end{align*}
-%We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
-In the following sections, we will show how to compute solution space properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebra.
-The Venn diagram in \Fig{fig:venn-diagram} shows the different types of algebra we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which solution space properties can be computed by which tensor element types.
-
-\begin{figure}[th]
-   \centering
-\centerline{\begin{tikzpicture}[]
-    \scriptsize
-    \node[draw,fill=lime!80,fill opacity=1, text opacity=1.0,ellipse,minimum width=2cm, minimum height=1cm,inner sep=0pt] at (0, 2.5) (R) {$\mathbbm{R}$};
-    \def\dx{-3};
-    \node[draw,fill=teal!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (\dx, 0.15) (PN) {\hspace{-3.7cm}Polynomial};
-    \node[draw,fill=brown!75,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, 0.7) (P1) {\hspace{-1.0cm}Largest order};
-    \node[draw,fill=brown!40,fill opacity=1, text opacity=1.0,ellipse,minimum width=3.5cm, minimum height=1.0cm,inner sep=0pt] at (\dx, -0.4) (P2) {\hspace{-0.8cm}Largest 2 orders};
-    \node[draw,fill=brown,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, 1.0) (T) {};
-    \node[draw,fill=brown!50,fill opacity=1, text opacity=1.0,ellipse,minimum width=0.8cm, minimum height=0.3cm,inner sep=0pt] at (\dx, -0.1) (T2) {};
-    \node at (\dx, -1.2) {$\ldots$};
-    \node[above = 1cm] at (T) (textT) {Tropical};
-    \node[below = 2cm, left=4cm] (textT2) {Extended Tropical};
-    \draw[black,-latex] (textT) -- (T);
-    \draw[black,-latex] (textT2) -- (T2);
-
-    % set and set sampler
-    \node[draw,fill=yellow,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=5cm, minimum height=3cm,inner sep=0pt] at (0, 0) (SN) {};
-    \node[below of=1] at (SN) {Set};
-    \node[draw,fill=red!70,fill opacity=0.5, text opacity=1.0,ellipse,minimum width=4cm, minimum height=1.5cm,inner sep=0pt] at (-0.5, 0) (S1) {\hspace{1.5cm}Bit string};
-\end{tikzpicture}}
-
-    \caption{The tensor network element types used in this work and their relations.
-    The overlap between two ellipses indicates that a new algebra can be created by combining those two types of algebra.
-``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.
-    The purposes of these element types can be found in \Tbl{tbl:generictypes}.}
-     \label{fig:venn-diagram}
-\end{figure}
-
-\begin{table}[t!]\centering
-\begin{minipage}{\columnwidth}
-\ra{1.3}
-        \begin{tabularx}{\textwidth}{sb}\toprule
-            \hline
-   \textbf{Element type}     & \textbf{Solution space property} \\
-   {$\mathbbm{R}$}     & {Counting of all independent sets} \\
-   {Polynomial} (\Eq{eq:polynomial})     & {Independence polynomial} \\
-   {Tropical (\Eq{eq:tropical})}    & {Maximum independent set size} \\
-   {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their degeneracy} \\
-   {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
-   {Sum-Product expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
-   {Polynomial truncated to largest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
-   {Polynomial truncated to $k$-th order combined with set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
-            \bottomrule
-        \end{tabularx}
-    \caption{Tensor element types and the independent set properties that can be computed using them.}\label{tbl:generictypes}
-\end{minipage}
-\end{table}
-
-\section{Tensor network representation of independent sets} \label{sec:tnmap}
-This section describes the reduction of the independent set problem to a tensor network contraction problem.
-An alternative interpretation, perhaps more accessible to physicists, can be found in \App{sec:energymodel}, where we introduce the reduction from the energy model of hardcore lattice gases~\cite{Dyre2016, Fernandes2007}.
-Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
-An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-To reduce the independent set problem on $G$ to a tensor network contraction, we first map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each vertex $v$, we define a parameterized rank-one tensor indexed by $s_v$ as
-\begin{equation}
-    W(x_v^{w_v}) = \left(\begin{matrix}
-        1 \\
-        x_v^{w_v}
-    \end{matrix}\right),\label{eq:vertextensor}
-\end{equation}
-where $x_v$ is a variable associated with $v$.
-Tensor elements can be indexed by subscripts, e.g.\ $W(x_v^{w_v})_0=1$ is the first element associated with $s_v=0$ and $W(x_v^{w_v})_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
-Similarly, for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
-\begin{equation}
-    \qquad \quad 
-       B = \left(\begin{matrix}
-        1  & 1\\
-        1 & 0
-    \end{matrix}\right), \label{eq:edgetensor}
-\end{equation}
-which encodes the independent set constraint since $B_{11} = 0$, meaning the two vertices cannot be both in the independent set.
-
-The corresponding tensor network contraction can be defined as
-\begin{equation}\label{eq:idp}
-    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W(x_v^{w_v})_{s_v} \prod\limits_{(u,v) \in E} B_{s_u s_v},
-\end{equation}
-where the summation runs over all $2^{|V|}$ vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$. 
-% It is easy to see that an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
-A vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
-
-\begin{example}\label{eg:twonode}
-Here, we show a minimum example of mapping the independent problem of a 2-vertex complete graph K2 (left) to a tensor network (right).
-
-\centerline{\begin{tikzpicture}[
-dot/.style = {circle, fill, minimum size=#1,
-            inner sep=0pt, outer sep=0pt},
-dot/.default = 6pt  % size of the circle diameter 
-                ]  
-    \def\dx{0};
-    \def\r{0.5cm}
-    \def\wr{0.25cm}
-    \node[dot=\r, fill=black] at (\dx,0) (a) {\color{white}{a}};
-    \node[dot=\r, fill=black] at (2.5+\dx,0) (b) {\color{white}{b}};
-    \draw [black,thick] (a) -- (b);
-
-    \def\dx{5};
-    \def\r{0.25cm}
-    \foreach \x/\y/\e in {1.25/0/ab}
-        \node[color=black,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize \color{white}{B}};
-    \foreach \x/\y/\v in {0.3/0/a, 2.2/0/b}
-        \node[color=black] at (\x+\dx,\y) (s\v) {$s_\v$};
-    \foreach \x/\y/\v in {-0.5/0/a, 3.0/0.0/b}{
-        \node[dot=\wr, color=black] at (\x+\dx,\y) (w\v) {};
-        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W(x_\v^{w_\v})$}};
-    }
-    \draw [cyan,thick] (wa) -- (sa);
-    \draw [cyan,thick] (sa) -- (ab);
-    \draw [red,thick] (wb) -- (sb);
-    \draw [red,thick] (sb) -- (ab);
-\end{tikzpicture}}
-
-In the graphical representation of the tensor network on the right panel,
-we use a circle to represent a tensor, a hyperedge in cyan color to represent the degree of freedom $s_a$,
-and a hyperedge in red color to represent the degree of freedom $s_b$.
-Tensors sharing the same degree of freedom are connected by the same hyperedge.
-The contraction of this tensor network has the following form:
-\begin{equation}
-    \begin{split}
-    P({\rm K2},\{x_a^{w_a}, x_b^{w_b}\}) &=
-    \left(\begin{matrix} 1 & x_a^{w_a} \end{matrix}\right)
-    \left(\begin{matrix} 1 & 1\\ 1  & 0 \end{matrix}\right)
-    \left(\begin{matrix} 1 \\ x_b^{w_b} \end{matrix}\right)\\
-    &= 1 + x_a^{w_a} + x_b^{w_b}.
-    \end{split}
-\end{equation}
-The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$, and $\{b\}$, with weights being $0$, $w_a$, and $w_b$ respectively.
-\end{example}
-
-For a general graph, it is computationally inefficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
-A better approach to evaluate a tensor network is: to find a good pair-wise tensor contraction order as a binary tree and then contract two tensors at a time by this order.
-Let us denote the line graph of the hypergraph representation of a tensor network as $G'$.
-A contraction order of this tensor network corresponds to a tree decomposition of $G'$ and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
-Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $G'$ with the smallest width (or the treewidth ${\rm tw}(G')$).
-In the independent set problem, the treewidth of $G'$ is the same as the treewidth of the graph this tensor network is mapped from. 
-In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is a well-known NP-hard problem.
-However, it is easy to find a close-to-optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019, Kalachev2021}.
-%The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
-For large-scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.\
-loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom.
-
-\begin{example}\label{eg:tensorcontraction}
-In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
-
-\centerline{\begin{tikzpicture}[
-dot/.style = {circle, fill, minimum size=#1,
-            inner sep=0pt, outer sep=0pt},
-dot/.default = 6pt  % size of the circle diameter 
-                ]  
-    \def\dx{0};
-    \def\r{0.25cm}
-    \filldraw[fill=black] (\dx,0) circle [radius=\r];
-    \filldraw[fill=black] (\dx,1.5) circle [radius=\r];
-    \filldraw[fill=black] (1.5+\dx,0) circle [radius=\r];
-    \filldraw[fill=black] (1.5+\dx,1.5) circle [radius=\r];
-    \filldraw[fill=black] (2.5+\dx,2.5) circle [radius=\r];
-    \draw [black,thick] (\dx,0) -- (\dx,1.5);
-    \draw [black,thick] (\dx,0) -- (1.5+\dx,0);
-    \draw [black,thick] (\dx,1.5) -- (1.5+\dx,1.5);
-    \draw [black,thick] (1.5+\dx,0) -- (1.5+\dx,1.5);
-    \draw [black,thick] (1.5+\dx,0) -- (\dx,1.5);
-    \draw [black,thick] (2.5+\dx,2.5) -- (1.5+\dx,1.5);
-    \node[color=white] at (\dx,0) {a};
-    \node[color=white] at (\dx,1.5) {b};
-    \node[color=white] at (1.5+\dx,0) {c};
-    \node[color=white] at (1.5+\dx,1.5) {d};
-    \node[color=white] at (2.5+\dx,2.5) {e};
-    \def\dx{5};
-    \def\r{0.25cm}
-    \foreach \x/\y/\e in {0.75/0/ac, 0/0.75/ab, 1.5/0.75/cd, 0.75/1.5/bd, 0.75/0.75/bc, 2/2/de}
-        \node[color=white,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize B};
-    \foreach \x/\y/\v in {0/0/a, 0/1.5/b, 1.5/0/c, 1.5/1.5/d, 2.5/2.5/e}
-        \node[color=black] at (\x+\dx,\y) (\v) {$s_\v$};
-    \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-        \node[color=white,fill=black,dot=\r] at (\x+\dx,\y) (\v\v) {};
-    \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-        \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v^{w_\v})$};
-    \draw [cyan,thick] (a) -- (aa);
-    \draw [cyan,thick] (a) -- (ab);
-    \draw [cyan,thick] (a) -- (ac);
-    \draw [blue,thick] (b) -- (bb);
-    \draw [blue,thick] (b) -- (ab);
-    \draw [blue,thick] (b) -- (bc);
-    \draw [blue,thick] (b) -- (bd);
-    \draw [red,thick] (c) -- (cc);
-    \draw [red,thick] (c) -- (ac);
-    \draw [red,thick] (c) -- (bc);
-    \draw [red,thick] (c) -- (cd);
-    \draw [green,thick] (d) -- (dd);
-    \draw [green,thick] (d) -- (bd);
-    \draw [green,thick] (d) -- (de);
-    \draw [green,thick] (d) -- (cd);
-    \draw [orange,thick] (e) -- (ee);
-    \draw [orange,thick] (e) -- (de);
-\end{tikzpicture}}
-
-One can represent a possible pair-wise contraction of tensors as a binary tree structure:
-
-\centerline{\begin{tikzpicture}[]
-    \def\dx{0};
-    \def\dy{0};
-    \def\d{1};
-    \def\a{1.0};
-    \def\b{1};
-    \def\ya{-1.0};
-    \def\yb{-0.8};
-    \node[] at (\dx+5*\a, \dy+5*\b) (R1) {$R[n^2]$};
-    \node[] at (\dx+3*\a, \dy+4*\b) (S1) {$S_{bc}[n^3]$};
-    \node[] at (\dx+2*\a, \dy+3*\b) (Q1) {$Q_{bd}[n^2]$};
-    \node[] at (\dx+8.5*\a, \dy+3*\b) (Q2) {$Q_{bc}[n^2]$};
-    \node[] at (\dx+\a, \dy+2*\b) (P1) {$P_{d}[n]$};
-    \node[] at (\dx+9*\a, \dy+2*\b) (P2) {$P_{bc}[n^3]$};
-    \node[] at (\dx+0.5*\d, \dy+\b) (M1) {$M_{d}[n^2]$};
-    \node[] at (\dx+3.5*\d, \dy+\b) (M2) {$M_{bd}[n^2]$};
-    \node[] at (\dx+5.5*\d, \dy+\b) (M3) {$M_{cd}[n^2]$};
-    \node[] at (\dx+9.5*\d, \dy+\b) (M4) {$M_{ac}[n^2]$};
-    \node[] at (\dx, \dy) (Bde) {$B_{de}$};
-    \node[] at (\dx+\d, \dy) (We) {$W_e$};
-    \node[] at (\dx+2*\d, \dy) (Wd) {$W_d$};
-    \node[] at (\dx+3*\d, \dy) (Bbd) {$B_{bd}$};
-    \node[] at (\dx+4*\d, \dy) (Wb) {$W_b$};
-    \node[] at (\dx+5*\d, \dy) (Bcd) {$B_{cd}$};
-    \node[] at (\dx+6*\d, \dy) (Wc) {$W_c$};
-    \node[] at (\dx+7*\d, \dy) (Bbc) {$B_{bc}$};
-    \node[] at (\dx+8*\d, \dy) (Bab) {$B_{ab}$};
-    \node[] at (\dx+9*\d, \dy) (Bac) {$B_{ac}$};
-    \node[] at (\dx+10*\d, \dy) (Wa) {$W_a$};
-    \draw[] (Bde) -- (M1);
-    \draw[] (We) -- (M1);
-    \draw[] (Bbd) -- (M2);
-    \draw[] (Wb) -- (M2);
-    \draw[] (Bcd) -- (M3);
-    \draw[] (Wc) -- (M3);
-    \draw[] (Bac) -- (M4);
-    \draw[] (Wa) -- (M4);
-    \draw[] (M1) -- (P1);
-    \draw[] (Wd) -- (P1);
-    \draw[] (Bab) -- (P2);
-    \draw[] (M4) -- (P2);
-    \draw[] (P1) -- (Q1);
-    \draw[] (M2) -- (Q1);
-    \draw[] (Bbc) -- (Q2);
-    \draw[] (P2) -- (Q2);
-    \draw[] (Bbc) -- (Q2);
-    \draw[] (P2) -- (Q2);
-    \draw[] (Q1) -- (S1);
-    \draw[] (M3) -- (S1);
-    \draw[] (S1) -- (R1);
-    \draw[] (Q2) -- (R1);
-\end{tikzpicture}}
-% \small{
-% \begin{align*}
-%     &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
-%     =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
-%     &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
-%     =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
-%     %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
-% \end{align*}}
-The contraction process goes from bottom to top, where the root node stores the contraction result; the leaves are input tensors and the rest of the nodes are all intermediate contraction results.
-Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
-The contraction complexity to generate a tensor is annotated in the square brackets, where $n$ is the dimension of the degree of freedoms, which is $2$ in a tensor network mapped from an independent set problem.
-One can easily check the largest tensor in contraction has a space complexity $O(n^2)$ and this is the smallest among all possible contraction trees, i.e.\ the treewidth of the original $5$-vertex graph is $2$.
-The time complexity is $O(n^3)$, which is much smaller than that of direct evaluation $O(n^5)$.
-\end{example}
-
-\section{Independence polynomial}\label{sec:indpoly}
-Let $x_i = x$ and $w_i = 1$, \Eq{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
-\begin{equation}\label{eq:idpdef}
-I(G, x) = \sum_{k=0}^{\alpha(G)} a_k x^k,
-\end{equation}
-where $a_k$ is the number of independent sets of size $k$, $\alpha(G) \equiv \max_{I}\sum_{v\in I}w_v$ is the size of a maximum independent set and it is also called the independence number.
-An independence polynomial is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-%Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-%and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
-By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly using tensor network contraction.
-For example, the total number of independent sets can be evaluated as $I(G, 1)$.
-However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
-%first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
-%\purple{I'd
-%say that you're about to describe this semiring, otherwise it seems like you're going to
-%use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}\purple{Perhaps start the sentence with: Our semiring elements are a polynomial type...}
-To this end, let us create a polynomial number data type by representing a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, e.g.
-$x$ is represented as $(0, 1)$.
-Then we can define an algebra among coefficient vectors, including a redefinition of additive identity and multiplicative identity.
-To avoid potential confusion, let us denote the additive identity as $\mymathbb{0}$, and the multiplicative identity is $\mymathbb{1}$.
-The algebra between the polynomials number $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
-\begin{equation}
-    \eqname{PN}
-    \begin{split}
-    a \oplus b &= (a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
-    a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, a_{2}b_{0} + a_{1}b_{1} + a_{0}b_{2},  \ldots, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (),  \\
-    \mymathbb{1} &= (1), \label{eq:polynomial}
-    \end{split}
-\end{equation}
-where $\oplus$ and $\odot$ are the standard polynomial addition and multiplication operations.
-The multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
-The tensors $W$ and $B$, which are introduced in the previous section (Sec.~\ref{sec:tnmap}), can thus be written as 
-\begin{equation}
-    W^{\rm PN} = \left(\begin{matrix}
-        \mymathbb{1} \\
-        (0,1)
-    \end{matrix}\right),   
-    \qquad \qquad
-        B^{\rm PN} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-By contracting the tensor network with this polynomial type, we have the exact representation of the independence polynomial.
-In practice, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
-One may argue that one can first evaluate this polynomial at different $x$ being a real number,
-and then apply the Gaussian elimination procedure to fit the coefficients of this polynomial.
-This seemingly more time and space-efficient approach suffer from precision issues in practice.
-The data ranges of standard integer types are too small to cover many practical use cases,
-while the floating-point numbers may have round-off errors that are much larger than the value itself.
-These are because the number of independent sets at different sizes may vary by tens or even hundreds of orders of magnitude.
-For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory-efficient method to find the polynomial by contracting and fitting on finite field algebra.
-Alternatively, one can use the method in \App{sec:fft} to fit this polynomial faster with complex numbers with controllable round-off errors.
-For simplicity, we use this less efficient polynomial algebra for the discussion in the main text.
-
-% the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
-
-\section{Maximum independent sets and its counting}\label{sec:counting}
-\subsection{Tropical algebra for finding the MIS size and counting MISs}
-%The method we use to count the MISs is based on the following observations:
-Let $x=\infty$, the independence polynomial in the previous section becomes
-\begin{equation}
-I(G, \infty) = \lim_{x\rightarrow \infty}\sum_{k=0}^{\alpha(G)}a_k x^k = a_{\alpha(G)} \infty^{\alpha(G)},
-\end{equation}
-where all terms except the one with the largest order vanish.
-We can thus replace the polynomial type $a = (a_0, a_1, \ldots, a_k)$ with a new type that has two fields: the largest exponent $k$ and its coefficient $a_k$.
-From this, we can define a new algebra as
-\begin{equation}
-    \eqname{P1}
-\begin{split}
-    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
-        (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
-        a_y\infty^{\max(x,y)}, & x < y\\
-        a_x\infty^{\max(x,y)}, & x > y
-    \end{cases}, \\
-    a_x\infty^x \odot a_y\infty^y &= a_x a_y\infty^{x+y}\\
-    \mymathbb{0} &= 0\infty^{-\infty}\\
-    \mymathbb{1} &= 1\infty^{0}.
-\end{split}%& \text{\rlap{(P1)}}
-\label{eq:countingtropical}
-\end{equation}
-Here, we have generalized the previous polynomial to the Laurent polynomial to define the zero-element properly.
-To implement this algebra programmatically, we create a data type with two fields $(x, a_x)$ to store the MIS size and its counting,
-and define the above operations and constants correspondingly.
-If one is only interested in finding the MIS size, one can drop the counting field.
-The algebra of the exponents becomes the max-plus tropical algebra~\cite{Maclagan2015, Moore2011}:
-\begin{equation}\eqname{T}
-    \begin{split}
-        x \oplus y &= \max(x,y)\\
-        x \odot y &= x + y\\
-        \mymathbb{0} &= -\infty\\
-        \mymathbb{1} &= 0.
-    \end{split}\label{eq:tropical}
-\end{equation}
-Algebra \Eq{eq:tropical} and \Eq{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.
-For independent set calculations here, the vertex tensor and edge tensor becomes:
-\begin{equation}
-    W^{\rm T}(w_v) = \left(\begin{matrix}
-        w_v \\
-        \infty
-    \end{matrix}\right),   
-    \qquad \qquad
-        B^{\rm T} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-
-\subsection{Truncated polynomial algebra for counting independent sets of large size}
-Instead of counting just the MISs, one may also be interested in counting the independent sets with the largest several sizes.
-For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial} as:
-\begin{equation}
-    \eqname{P2}
-    \begin{split}
-    a \oplus b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
-    a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
-    \mymathbb{0} &= (), \\
-    \mymathbb{1} &= (1).\label{eq:max2poly}
-    \end{split}
-\end{equation}
-In the program, we thus need a data structure that contains three fields, the largest order $k$, and the coefficients for the two largest orders $a_k$ and $a_{k-1}$.
-This approach can clearly be extended to calculate more independence polynomial coefficients and is more efficient than calculating the entire independence polynomial.
-Similarly, one can also truncate the polynomial and keep only its smallest several orders.
-It can be used, for example, to count the maximal independent sets with the smallest cardinality, where a maximal independent set is an independent set that cannot be made larger by adding a new vertex into it without violating the independence constraint.
-As will be shown below, this algebra can also be extended to enumerate those large-size independent sets.
-
-\section{Enumerating and sampling independent sets}\label{sec:enumeration}
-
-\subsection{Set algebra for configuration enumeration}
-The configuration enumeration of independent sets include, for example, the enumeration of all independent sets, the enumeration of all MISs, and the enumeration of independent sets with the largest several sizes.
-Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
-The multiplication between labeled variables is commutative while the summation of labeled variables forms a set.
-Intuitively, one can use a bit string as the representation of a labeled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
-For example, in a 5-vertex graph, $x_2$ and $x_5$ can be represented as $01000$ and $00001$ respectively and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
-To enumerate all independent sets, we designed an algebra on sets of bit strings:
-\begin{equation}
-\eqname{SN}
-\begin{split}
-    s \oplus t &= s \cup t\\
-    s \odot t &= \{\sigma \lor^\circ \tau \, | \, \sigma \in s, \tau \in t\}\\
-    \mymathbb{0} &= \{\}\\
-    \mymathbb{1} &= \{0^{\otimes |V|}\},
-\end{split}\label{eq:set}
-\end{equation}
-where $s$ and $t$ are each a set of $|V|$-bit strings.
-\begin{example}\label{eg:setalgebra}
-    For elements being bit strings of length $5$, we have the following set algebra
-\begin{equation*}
-\begin{split}
-    &\{00001\} \oplus \{01110, 01000\} = \{01110, 01000\} \oplus \{00001\} = \{00001,01110, 01000\}\\
-    &\{00001\} \oplus \{\} = \{00001\}\\
-&\\
-    &\{00001\} \odot \{01110, 01000\} = \{01110, 01000\} \odot \{00001\} = \{01111, 01001\}\\
-    &\{00001\} \odot \{\} = \{\}\\
-    &\{00001\} \odot \{00000\} = \{00001\}.
-\end{split}
-\end{equation*}
-\end{example}
-
-To enumerate all independent sets,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
-The vertex and edge tensors are thus
-\begin{equation}
-    W^{\rm SN}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
-        \mymathbb{1} \\
-        \{\boldsymbol{e}_{i}\}
-    \end{matrix}\right),   
-    \qquad \qquad
-        B^{\rm SN} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-
-This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs, or \Eq{eq:max2poly} to enumerate all independent sets of sizes $\alpha(G)$ and $\alpha(G)-1$.
-As long as the coefficients in a truncated polynomial are members of a commutative semiring, the polynomial itself is a commutative semiring.
-For example, to enumerate only the MISs, we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Eq{eq:set} and the exponents follow the max-plus tropical algebra.
-The combined operations become: 
-\begin{equation}
-\eqname{P1+SN}
-\begin{split}
-    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
-        (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
-        s_y\infty^{\max(x,y)}, & x < y\\
-        s_x\infty^{\max(x,y)}, & x > y
-    \end{cases},\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
-    \mymathbb{0} &= \{\}\infty^{-\infty},\\
-    \mymathbb{1} &= \{0^{\otimes |V|}\}\infty^{0}. \label{eq:countingtropicalset}
-\end{split}
-\end{equation}
-Clearly, the vertex tensor and edge tensor become
-\begin{equation}
-    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\}\infty^{w_v}) = \left(\begin{matrix}
-        \mymathbb{1} \\
-        \{\boldsymbol{e}_{i}\}\infty^{w_v}
-    \end{matrix}\right),   
-    \qquad \qquad
-        B^{\rm P1+SN} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-The enumeration of all MIS configurations corresponds to the contraction of this tensor network.
-However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
-We introduce the bounding technique in \App{sec:bounding} to avoid this issue.
-One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
-It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure.
-
-If one is interested in obtaining only one MIS configuration, they can just keep one configuration in each tensor element to save the computational effort.
-By replacing the sets of bit strings in \Eq{eq:set} with a single bit string, we have the following algebra
-
-\begin{equation}
-\eqname{S1}
-\begin{split}
-    \sigma \oplus \tau &= \texttt{select}(\sigma, \tau), \\
-    \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
-    \mymathbb{0} &= 1^{\otimes |V|}, \\
-    \mymathbb{1} &= 0^{\otimes |V|}.
-\end{split}\label{eq:singleconfig}
-\end{equation}
-The \texttt{select} function picks one of $\sigma$ and $\tau$ by some criteria.
-It can be picking the one smaller in the lexicographical order such that the addition operation is commutative and associative.
-In most cases, it is completely fine for the \texttt{select} function to pick a random one (not commutative and associative anymore) to generate a random MIS.
-
-\subsection{Sampling extremely large configuration space}
-When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
-To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.\ instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
-Each node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of \texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node, and $left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
-
-\begin{equation}
-\eqname{EXPR}
-\begin{split}
-    s \oplus t &= (\texttt{SUM}, /, s, t)\\
-    s \odot t &= (\texttt{PROD}, /, s, t)\\
-    \mymathbb{0} &= (\texttt{ZERO}, /, /, /)\\
-    \mymathbb{1} &= (\texttt{LEAF}, 0^{\otimes |V|}, /, /).
-\end{split}\label{eq:expr}
-\end{equation}
-The vertex tensor and edge tensor become
-\begin{equation}
-    W^{\rm EXPR}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
-        \mymathbb{1} \\
-        (\texttt{LEAF},\boldsymbol{e}_i,/,/)
-    \end{matrix}\right),   
-    \qquad
-        B^{\rm EXPR} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right).
-\end{equation}
-
-This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms rather than their storage.
-Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with the largest several sizes.
-Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
-they can draw unbiased samples from it by direct sampling.
-The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
-If a node has type \texttt{SUM}, the program draws samples from the left and right siblings with a probability decided by the size of each sub-tree and returns the union of samples.
-Otherwise, if a node has type \texttt{PROD}, the program draws two sets of samples of equal sizes from its left and right siblings and returns the element-wise multiplication ($\lor^\circ$) of them.
-The recursion stops at a \texttt{LEAF} node having size $1$ or a \texttt{ZERO} node having size $0$.
-In a sum-product expression tree, the number of configurations of sub-trees can be determined easily as we will show in the following example.
-\begin{example}
-Let us consider the following sum-product expression tree 
-\begin{equation*}
-    (\texttt{SUM}, /, (\texttt{PROD}, /, A, B), (\texttt{SUM}, /, C, D)),
-\end{equation*}
-where sub-trees $A, B, C$ and $D$ can be any of the four types of nodes.
-This sum-product expression tree can be represented diagrammatically as the following:
-
-\centerline{\begin{tikzpicture}[]
-    \def\dx{0};
-    \def\a{1.0};
-    \def\b{0.5};
-    \def\ya{-1.0};
-    \def\yb{-0.8};
-    \node[] at (\dx, 0) (P1) {$\oplus$};
-    \node[] at (\dx+\a, \ya) (P2) {$\oplus$};
-    \node[] at (\dx-\a, \ya) (M1) {$\odot$};
-    \node[] at (\dx-\a-\b, \ya+\yb) (A) {$A$};
-    \node[] at (\dx-\a+\b, \ya+\yb) (B) {$B$};
-    \node[] at (\dx+\a+\b, \ya+\yb) (C) {$C$};
-    \node[] at (\dx+\a-\b, \ya+\yb) (D) {$D$};
-    \draw[] (P1) -- (M1);
-    \draw[] (P1) -- (P2);
-    \draw[] (P2) -- (C);
-    \draw[] (P2) -- (D);
-    \draw[] (M1) -- (A);
-    \draw[] (M1) -- (B);
-\end{tikzpicture}}
-
-The left and right siblings of the root node have sizes $|A|\times |B|$ and $|C|+|D|$ respectively, while the root node size can be computed as $|A|\times |B| + |C|+|D|$.
-The sizes of $A, B, C$, and $D$ can be computed recursively until the program meets either a \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$.
-\end{example}
-
-\section{Weighted graphs}\label{sec:weighted}
-All the solution space properties and the corresponding algebra on unweighted graphs still hold for integer-weighted graphs, while for general weighted graphs, the independence polynomial is not well defined anymore.
-For general weighted graphs, it is more useful to know the $k$ maximum weighted sets and their sizes.
-They can be computed by the extended tropical algebra, which is a natural generalization of the max-plus tropical algebra:
-\begin{equation}
-\eqname{T$k$}
-\begin{split}
-    s \oplus t &= \texttt{largest}(s \cup t, k)\\
-    s \odot t &= \texttt{largest}(\{a+b | a \in s, b\in t\}, k)\\
-    \mymathbb{0} &= -\infty^{\otimes k}\\
-    \mymathbb{1} &= -\infty^{\otimes k-1} \otimes 0
-\end{split}\label{eq:ext-tropical}
-\end{equation}
-where $\texttt{largest}(s, k)$ means truncating the set $s$ by only keeping its $k$ largest values.
-The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$.
-An efficient algorithm for computing the maximum sum combination problem can be found in \App{sec:maxsum}.
-The vertex tensor and edge tensor become
-\begin{equation}
-    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes w_v) = \left(\begin{matrix}
-        \mymathbb{1} \\
-        -\infty^{\otimes k-1} \otimes w_v
-    \end{matrix}\right),   
-    \qquad
-        B^{{\rm T}k} = \left(\begin{matrix}
-        \mymathbb{1}  & \mymathbb{1} \\
-        \mymathbb{1} & \mymathbb{0}
-    \end{matrix}\right),
-\end{equation}
-where we have used the equation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
-To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Eq{eq:singleconfig}).
-Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
 
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig1.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
     \caption{Benchmark results for computing different solution space properties of independent sets of random three-regular graphs with different tensor element types.
     The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
-    Legends are properties, algebra, and devices that we used in the computation; one can find the corresponding computed solution space property in \Tbl{tbl:generictypes}.
+    Legends are properties, algebra, and devices that we used in the computation; one can find the corresponding computed solution space property in Table 1 in the main text.
     (a) time and space complexity versus the number of vertices for the benchmarked graphs.
@@
 
-\section{Example applications} \label{sec:examples}
-%In this section, we give a few examples where the different properties of independence sets are used.
-
-\subsection{Number of independent sets and entropy constant for hardcore lattice gases}\label{sec:entropy}
-We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
-The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (Figure~\ref{fig:lattices}(b));
-the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
-
-The number of independent sets for square lattice graphs of size $L \times L$ form a well-known integer sequence (\href{https://oeis.org/A006506}{OEIS A006506}), which is thought as a two-dimensional generalization of the Fibonacci numbers.
-We computed the integer sequence for $L=38$ and $L=39$, which is, to the best of our knowledge, not known before.
-In the computation, we used finite-field algebra for contracting integer tensor networks with arbitrarily high precision.
-
-A theoretically interesting number that can be computed using the number of independent sets is the entropy constant, which can describe the thermodynamic properties of hard-core lattice gases at the high-temperature limit.
-For the square lattice graphs, this number is called the \textit{hard square entropy constant} (\href{https://oeis.org/A085850}{OEIS A085850}), which is defined as $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$, where $F(L,L)$ is the number of independent sets of a given lattice dimensions $L \times L$.
-This quantity arises in statistical mechanics of hard-square lattice gases~\cite{Baxter1980, Pearce1988} and is used to understand phase transitions for these systems.
-This entropy constant is not known to have an exact representation, but it is accurately known in many digits.
-Similarly, we can define entropy constants for other lattice gases.
-In \Fig{fig:hardsquare}, we look at how $F(L,L)^{1/\lfloor pL^2\rceil}$ scales as a function of the grid size $L$ for all types of graphs shown in Figure~\ref{fig:lattices}.
-Our results match the known results for the non-disordered square lattice and King's graphs.
-For disordered square lattice and King's graphs with a filling factor $p=0.8$, we randomly sample 1000 graph instances.
-To our knowledge, the entropy constants for these disordered graphs have not been studied before.
-They may be used to study phase transitions for disordered lattices, which are typically much harder to understand.
-Interestingly, the variations due to different random instances are negligible for this quantity.
-% \blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
-
-\begin{figure}[t] 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{lattices.pdf}
-    \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
-    The lattice dimensions are $L\times L$. (a) square lattice graphs. (b) square lattice graphs with a filling factor $p=0.8$.
-    (c) King's graphs. (d) King's graphs with a filling factor $p=0.8$.}
-    \label{fig:lattices}
-\end{figure}
-
-\begin{figure}[t] 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig5.pdf}
-    \caption{Mean entropy for lattice gases on graphs defined in \Fig{fig:lattices}.
-    We sampled $1000$ instances for $p=0.8$ lattices and the error bar is too small to be visible.
-    The horizontal black dashed lines are for $\lim_{L\rightarrow \infty} F(L,L)^{1/L^2}$ for the corresponding non-disordered square lattice and King's graphs.
-    }
-    \label{fig:hardsquare}
-\end{figure}
-
-\subsection{The overlap gap property\label{sec:overlap-gap}}
-With this tool to enumerate or sample configurations, one can understand the structure of the independent set configuration space, such as the optimization landscape for finding the MISs.
-One of the known barriers to finding the MIS is the so-called overlap gap property~\cite{Gamarnik2013, Gamarnik2019}.
-If the overlap gap property is present, it means every two large independent sets either have a significant intersection or a very small intersection;
-it implies that large independent sets are clustered together.
-This clustering property has been used to rigorously prove upper bounds on the performance of local search algorithms~\cite{Gamarnik2013, Gamarnik2019}.
-To investigate the overlap gap property, we compute pair-wise Hamming distance distributions of large independent sets as they are good indicators of the presence or absence of overlap gap properties.
-We inspect two types of graphs that are particularly interesting, the King's graphs with defects and $3$-regular graphs.
-It is known that the MIS problem on a general graph can be mapped to the King's graph with defects~\cite{Garey1977,Ebadi2022}.
-However, it is not clear whether the MIS problem defined on a randomly generated King's graph with defects can have the overlap gap property.
-It is known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, but, it is not known whether, for small $d$, e.g.\ for $3$-regular graphs, this statement remains true.
-We randomly generated $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
-At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to directly sample from the target configuration space.
-For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Fig{fig:hamming}.
-We observe a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs, indicating the absence of the overlap gap property in a random King's graph at $0.8$ filling.
-Since the MIS problem on an arbitrary graph can be mapped to a King's graph at a certain filling, this result is highly nontrivial. It likely implies 
-that the King's graphs with defects mapped from hard MIS instances have a very small measure in the total defected King's graph space. In contrast, 
-very different pair-wise Hamming distributions are obtained in \Fig{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
-It indicates the existence of disconnected clusters in the configuration space of the MIS problem on $3$-regular graphs.
-We expect this numerical tool can be used to understand this phenomenon better and to further investigate the graph properties and the geometry of the configuration spaces for a variety of graph instances.
-\begin{figure} 
-    % \begin{subfigure}[t]{\textwidth}
-    %     \centering
-    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
-    %     \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
-    % \end{subfigure}
-    % \begin{subfigure}[t]{\textwidth}
-    %     \centering
-    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-    %     \caption{Nine random three regular graphs of size $110$.}
-    % \end{subfigure}
-    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{fig6.pdf}
-    \caption{Pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.
-    In each plot, the $x$-axis is the Hamming distance normalized by the total number of vertices and the $y$-axis is the probability.
-    }
-    \label{fig:hamming}
-\end{figure}
-
-%\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
-\subsection{Analyzing quantum and classical algorithms for Maximum Independent Set}
+We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
+including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
+\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
+In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
+
 \begin{figure} 
     \centering
-    \includegraphics[width=.65\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{exp_configurations.pdf}
-    \caption{Visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem~\cite{Ebadi2022}.
-    Each vertex represents an independent set, and each edge represents a pair of independent sets that differ by a swap operation or a vertex addition.}
-    \label{fig:exp_configuratoins}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
+    \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
+    (a) time and space complexity of tensor network contraction. 
+    (b) The wall clock time for counting and enumeration of maximal ISs. % The missing data is due to the memory limit.
+    }
+    \label{fig:benchmark-maximal}
 \end{figure}
-In a recent work, 
-the ability to enumerate configurations and compute independence polynomials was critical in understanding the performance of quantum optimization algorithms for the MIS problem on a Rydberg atom quantum computer~\cite{Ebadi2022}.
-This work focused on
-%, the authors found that
-exploring King's graphs with $0.8$ filling.
-The hardest instances for classical simulated annealing could be accurately predicted from the independence polynomial, which gave information about the density of local minima at different independent set sizes.
-On the hardest graph instances for simulated annealing studied in the experiment, a high density of local minima were found at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
-%Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space. However, 
-By enumerating the configurations using techniques described in the present work, we found that %n found that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead
-simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
-Therefore, the large ratio of local to global minima  prevents simulated annealing from efficiently finding an MIS.
-%and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
-Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in Sec.~\ref{sec:overlap-gap}.
-
-Although the performance of the quantum algorithm is more challenging to understand due to the inherent difficulty in studying quantum systems, the present methods allow one 
-to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
-Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
-Each edge represents a pair of independent sets that differ by a swap operation or a vertex addition to the set, which are the operations naturally present in the effective dynamics at the end of the quantum algorithm.
-%The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
-The solution space graph is well-connected by local changes to the spin configurations, has a small diameter, and the degree of each node appears to concentrate. 
-This visualization makes it clear that 
-%the authors inferred that 
-the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms e.g.
-by Ref.~\cite{altshuler2010}  which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
-Instead, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
-In the case where a large superposition state of local minima is created during the coherent evolution, the quantum algorithm achieves a quadratic speedup over simulated annealing.
-%Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
-Looking forward, we expect these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
-
-\section{Discussion and conclusion}
-In this work, we introduced a framework that uses generic tensor networks to compute different solution space properties of a certain class of NP-hard combinatorial optimization problems.
-%These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
-Each solution space property is computed using the same tensor network with different tensor element algebra.
-% This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
-% such as the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
-%With different algebras, the contraction of the same tensor network gives us the different properties.
-The different data types introduced in the main text to compute these properties are summarized in the diagram in \Fig{fig:venn-diagram}.
-The class of problems solvable by a tensor network includes but is not limited to maximum independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \App{sec:otherproblems}.
-
-%Other than the case with real numbers, we have polynomials and truncated polynomials.
-%We combine them with the bit string algebra, the set algebra, and sum-product expression tree algebra for finding, enumerating, and sampling of independent sets at a given size.
-Three examples are shown to demonstrate how our method can be used to understand the solution space better.
-%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
-We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
-%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
-%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
-This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
-
-Looking ahead, it could be possible to generalize the idea of generic programming to other algorithms that have certain algebraic structures such as those using the inclusion-exclusion principle or subset convolution~\cite{Fomin2013} and explore what new properties can be computed.
-To this end, dynamic programming~\cite{Courcelle1990, Fomin2013} approaches could be considered.
-Dynamic programming is closely related to a tropical tensor network~\cite{Liu2021}; for example, the Viterbi algorithm for finding the most probable configuration in a hidden Markov model can be interpreted as a matrix product state featured with tropical algebra, and the tropical tensor network in the main text is potentially equivalent to dynamic programming in finding an optimum solution.
-Since dynamic programming has much broader applications, it would be interesting to extend the ideas from this paper to provide an algebraic interpretation for dynamic programming so that it can be used to compute other solution space properties beyond just finding an optimum solution.
-%Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
-%our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
-%By adapting to the style of generic programming, we can implement all the algorithms without much effort.
-
-The source code in Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
-There is a short introduction to this repository as well a gist to show how it works in Appendix~\ref{sec:technical}.
-We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
-We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to the development of other scientific software.
-
-%We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
-
-\section*{Acknowledgments}
-We would like to thank Pan Zhang for sharing his python code for optimizing contraction orders of a tensor network.
-We acknowledge Sepehr Ebadi and Leo Zhou for coming up with many interesting questions about independent sets and their questions strongly motivated the development of this project.
-We thank Benjamin Schiffer for providing helpful feedback on the writing of this manuscript.
-We thank Chris Elord for helping us write the fastest matrix multiplication library for tropical numbers, TropicalGEMM.jl. 
-We would also like to thank a number of open-source software developers, including Roger Luo, Time Besard, Edward Scheinerman, and Katharine Hyatt
-for actively maintaining their packages and resolving related issues voluntarily.
-We acknowledge financial support from the DARPA ONISQ program (grant no.\ W911NF2010021), the Center for Ultracold Atoms, the National Science Foundation, the Vannevar Bush Faculty Fellowship, the U.S.
-Department of Energy (DE-SC0021013 and DOE Quantum Systems Accelerator Center (contract no.\ 7568717),
-%the Office of Naval Research, 
-the Army Research Office MURI.
-We acknowledge the computation credits provided by Amazon Web Services for running the benchmarks and case studies.
-Jinguo Liu acknowledges funding support provided by QuEra Computing Inc.\ through a sponsored research program.
-
-\bibliographystyle{siamplain}
-\bibliography{refs}
-
-\appendix
-
-\section{An alternative way to construct the tensor network}\label{sec:energymodel}
-
-Let us characterize the independent set problem on graph $G=(V, E)$ as an energy model with two parts
-\begin{equation}\label{eq:eng}
-    \mathcal{E}(G, s) = -\sum_{i\in V} w_i s_i + \infty \sum_{(i,j) \in E}s_i s_j
-\end{equation}
-where $s_i$ is a spin on vertex $i \in V$ and $w_i$ is an onsite energy term associated with it.
-The first part corresponds to the negative independent set size and the second part describes the independence constraint, which corresponds to the Rydberg blockade~\cite{Pichler2018, Ebadi2022} in cold atom arrays or the repulsive force in hardcore lattice models~\cite{Dyre2016, Fernandes2007}.
-The partition function is defined as
-\begin{equation}\label{eq:partition}
-    \begin{split}
-    Z(G, \beta) = \sum_{s}e^{-\beta \mathcal{E}(G, s)} = \sum_{s\in \mathcal{I}(G)} e^{\beta \sum w_i s_i}\\
-         = \sum_{k=0}^{\alpha(G)}a(k) e^{\beta k}  \qquad \quad (k = \sum w_i s_i)
-    \end{split}
-\end{equation}
-where $\mathcal{I}(G)$ is the set of independent sets of graph $G$, $\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size), $a(k)$ is the number of spin configurations with energy $-k$ (independent sets of size $k$).
-The partition function can be expressed as a tensor network by placing a vertex tensor on each spin $i$
-\begin{equation}
-    W(e^{\beta w_i}) = \left(\begin{matrix}
-        1 \\
-        e^{\beta w_i}
-    \end{matrix}\right),
-\end{equation}
-and an edge tensor on each bond
-\begin{equation}
-       B = \left(\begin{matrix}
-        1  & 1\\
-        1 & 0
-    \end{matrix}\right),
-\end{equation}
-where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}, which is the independence constraint.
-By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
-If we further let $w_i=1$, the second line of \Eq{eq:partition} is equivalent to the independence polynomial.
 
@@
 
-\section{Hard problems and tensor networks}\label{sec:otherproblems}
-\subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-In this section, we focus the discussion on the maximal independent sets problem since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of the complement of the graph.
-Let $G=(V,E)$ be a graph, we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
-A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
-To characterize the maximal independence restriction, we defined a tensor on each $\{v\}\cup N(v)$ as
-\begin{equation}\label{eq:maximal}
-    T(x_v^{w_v})_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx_v^{w_v} & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
-        1-s_v& \text{otherwise}.\\
-    \end{cases}
-\end{equation}
-It means if none of the neighbours of $v$ are in $I_{m}$ ($ s_1=s_2=\ldots=s_{|N(v)|}=0$), then $v$ must be in $I_{m}$ and contribute a factor $x_{v}$, otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
-For a vertex $v$ that has a degree 2, the tensor has the following form
-\begin{equation}
-    T(x_v^{w_v})=\left(\begin{matrix}
-    \left(\begin{matrix}
-        ~~0 &~1 \\
-        ~~1 &~1
-    \end{matrix}\right)\\
-    \left(\begin{matrix}
-        x_v^{w_v} &0 \\
-        0 &0
-    \end{matrix}\right)
-    \end{matrix}\right).
-\end{equation}
-
-Let us consider the graph in Example~\ref{eg:tensorcontraction}.
-The corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation.
-\\
-
-    \centerline{\begin{tikzpicture}[
-    dot/.style = {circle, fill, minimum size=#1,
-                inner sep=0pt, outer sep=0pt},
-    dot/.default = 6pt  % size of the circle diameter 
-                    ]  
-        \def\dx{0};
-        \def\r{0.4cm}
-        \def\G{1.0}
-        \foreach \x/\y/\v in {0/0/a, 1/0/b, 2/0/c, 3/0/d, 4/0/e}
-            \node[color=black] at (\x*\G+\dx,\y) (\v) {$s_\v$};
-        \foreach \x/\v/\t in {0/A/$T_a$, 1/B/$T_b$, 2/C/$T_c$, 3/D/$T_d$, 4/E/$T_e$}
-            \node[color=white,fill=black,dot=\r] at (\x*\G+\dx,1.5) (\v) {\scriptsize \t};
-        \draw [cyan,thick] (a) -- (A);
-        \draw [cyan,thick] (a) -- (B);
-        \draw [cyan,thick] (a) -- (C);
-        \draw [blue,thick] (b) -- (B);
-        \draw [blue,thick] (b) -- (A);
-        \draw [blue,thick] (b) -- (C);
-        \draw [blue,thick] (b) -- (D);
-        \draw [red,thick] (c) -- (C);
-        \draw [red,thick] (c) -- (A);
-        \draw [red,thick] (c) -- (B);
-        \draw [red,thick] (c) -- (D);
-        \draw [green,thick] (d) -- (D);
-        \draw [green,thick] (d) -- (B);
-        \draw [green,thick] (d) -- (C);
-        \draw [green,thick] (d) -- (E);
-        \draw [orange,thick] (e) -- (E);
-        \draw [orange,thick] (e) -- (D);
-    \end{tikzpicture}}
-
-%The contraction complexity of this tensor network is often greater than the one for the independence set problem.
-By contracting this tensor network with generic element types,
-we can compute the maximal independent set properties such as the maximal independence polynomial and the enumeration of maximal independent sets.
-The maximal independence polynomial is defined as
-\begin{equation}
-D_{m}(G, x) = \sum_{k=0}^{\alpha(G)} b_k x^k,
-\end{equation}
-where $b_k$ is the number of maximal independent sets of size $k$.
-Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
-$D_m(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013};
-to our knowledge, the best algorithm has a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-%If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
-%The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
-
-We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
-including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
-\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
-In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
-
-\begin{figure} 
-    \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig2.pdf}
-    \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
-    (a) time and space complexity of tensor network contraction. 
-    (b) The wall clock time for counting and enumeration of maximal ISs. % The missing data is due to the memory limit.
-    }
-    \label{fig:benchmark-maximal}
-\end{figure}
-
-\subsection{Matching problem}
-A $k$-matching in a graph $G=(V,E)$ is a set of $k$ edges that no two of which have a vertex in common.
-We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
-To characterize the matching constraint, we define a tensor for each $N(v)=\{n_1, n_2,\ldots, n_{d(v)}\}$ as
-\begin{equation}
-    W_{\langle v, n_1\rangle, \langle v, n_2 \rangle, \ldots, \langle v, n_{d(v)}\rangle} = \begin{cases}
-        1, & \sum_{i=1}^{d(v)} \langle v, n_i \rangle \leq 1,\\
-        0, & \text{otherwise},
-    \end{cases}
-\end{equation}
-and a tensor for each bond as
-\begin{equation}
-    B(x^{w_{\langle u,v \rangle}}_{\langle u,v\rangle})_{\langle u, v\rangle} = \begin{cases}
-    1, & \langle u, v \rangle = 0 \\
-    x^{w_{\langle u,v \rangle}}_{\langle u, v\rangle}, & \langle u, v \rangle = 1,
-\end{cases}
-\end{equation}
-where a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
-$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set,
-and an edge tensor carries the weights.
-Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction corresponds to the matching polynomial
-\begin{equation}
-    M(G, x) = \sum\limits_{k=1}^{|V|/2} c_k x^k,
-\end{equation}
-where $k$ is the size of an edge set, and a coefficient $c_k$ is the number of $k$-matchings.
-
-\subsection{Vertex coloring}
-Let $G=(V,E)$ be a graph. A vertex coloring is an assignment of colors to each vertex $v\in V$ such that no edge connects two identically colored vertices. 
-In a $k$-coloring problem, the number of colors is limited to less or equal to $k$.
-Let us use the 3-coloring problem as an example to show how to reduce it to tensor contractions.
-We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
-Then we define a tensor labeled by $c_v$ for each vertex $v$ as
-\begin{equation}
-    W = \left(\begin{matrix}
-        r_v\\
-        g_v\\
-        b_v
-    \end{matrix}\right),
-\end{equation}
-and a bond tensor labelled by $(c_u, c_v) $ for each edge $(u, v) \in E$ as
-\begin{equation}
-    B(x^{w_{uv}}) = \left(\begin{matrix}
-        0 & x^{w_{uv}} & x^{w_{uv}}\\
-        x^{w_{uv}} & 0 & x^{w_{uv}}\\
-        x^{w_{uv}} & x^{w_{uv}} & 0
-    \end{matrix}\right),
-\end{equation}
-where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations. $B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
-%The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
-Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$; we then have a graph polynomial,
-in which the $k$-th coefficient is the number of coloring that $k$ bonds satisfy constraints.
-If a graph is colorable, the maximum order of this polynomial should be equal to the number of edges in this graph.
-Similarly, one can define an edge coloring problem by defining the tensor network on the line graph of $G$.
-
-\subsection{Cutting problem}
-In graph theory, a cut is a partition of the vertices of a graph into two disjoint subsets,
-which is also known as the spin-glass problem in statistical physics.
-Let $G=(V,E)$ be a graph.
-We associate a weight $w_v$ to each $v\in V$.
-To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-Then for each edge $(u,v)\in E$, we define an edge matrix labeled by $(s_u, s_v)$ as
-\begin{equation}
-    B(x^{w_{uv}}_u, x^{w_{uv}}_v) = \left(\begin{matrix}
-        1 & x_{v}^{w_{uv}}\\
-        x_{u}^{w_{uv}} & 1
-    \end{matrix}\right),
-\end{equation}
-where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem.
-Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$; we have a graph polynomial similar to the previous ones,
-in which the $k$th coefficient is two times the number of cut configurations that have size $k$ (i.e.\ cutting $k$ edges).
-
-\subsection{Dominating Set}
-In graph theory, a dominating set for a graph $G = (V, E)$ is a subset $D \subseteq V$ such that every vertex not in $D$ is adjacent to at least one member of $D$.
-To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
-Then for each vertex $v$, we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
-\begin{equation}
-T(x^{w_v}_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-    0 & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
-    1 & s_v=0,\\
-    x^{w_v}_v & \text{otherwise},
-\end{cases}
-\end{equation}
-where $w_v$ is the weight associated with the vertex $v$.
-This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$) cannot be a dominating set.
-Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output.
-The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009}
-\begin{equation}
-D(G, x) = \sum_{k=0}^{\gamma(G)} d_k x^k,
-\end{equation}
-where $d_k$ is the number of dominating sets of size $k$.
-
-\subsection{Boolean satisfiability Problem}
-The Boolean satisfiability problem is the problem of determining if there exists an assignment that satisfies a given Boolean formula.
-One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e.\ a conjunction of clauses (or disjunctions of Boolean literals).
-To reduce the problem of solving a CNF to a tensor network contraction, we first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
-$s_a = 0$ stands for variable $a$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
-Then we map a clause to a tensor. For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
-\begin{equation}
-C_{k} = \left(\begin{matrix}
-\left(\begin{matrix}
-x^{w_k} & x_{b}^{w_k} \\
-x_a^{w_k} & x_{ab}^{w_k}
-\end{matrix}\right) \\
-\left(\begin{matrix}
-x_{c}^{w_k} & x_{bc}^{w_k} \\
-1 & x_{abc}^{w_k}
-\end{matrix}\right)
-\end{matrix}\right),
-\end{equation}
-where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
-Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
-
-\subsection{Set packing}
-Suppose one has a finite set $S$ and a list of subsets of $S$. Then, the set packing problem asks if some $k$ subsets in the list are pairwise disjoint.
-It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Eq{eq:vertextensor}, while the edge tensor generalizes \Eq{eq:edgetensor} to higher dimensions
-\begin{equation}
-    B_{s_u,s_v,\ldots, s_w} = \begin{cases}
-        1, & s_u+s_v+\ldots+s_w\leq 1,\\
-        0, & \text{otherwise}.
-    \end{cases}
-\end{equation}
-
-\subsection{Set covering}
-Given a collection of elements, the set covering problem aims to find the minimum number of sets that incorporate (cover) all of these elements.
-In the set covering problem, two sets are given: a set $U$ of elements and a set $S$ of subsets of the set $U$.
-The union of all the subsets covers the set $U$.
-For each set $s \in S$, we associate it with weight $w_s$ to it.
-To get the generic tensor network representation, we first map a set $s\in S$ to a Boolean degree of freedom $l_s\in\{0, 1\}$.
-For each set $s$, we define a parameterized rank-one tensor indexed by $l_s$ as
-\begin{equation}
-W(x_s^{w_s}) = \left(\begin{matrix}
-    1 \\
-    x_s^{w_s}
-    \end{matrix}\right)
-\end{equation}
-where $x_s$ is a variable associated with $s$.
-For each unique element $a \in U$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(a) = \{s | s \in S \land a\in s\}$, as
-\begin{equation}
-B_{l_1,l_2,\ldots,l_{|N(a)|}} = \begin{cases}
-    0 & l_1=l_2=\ldots=l_{|N(a)|}=0,\\
-    1 & \text{otherwise}.
-\end{cases}
-\end{equation}
-If a subset of $S$ does not include any sets containing element $a$, then this configuration has zero contribution to the contraction result.
-
 \section{Bounding the MIS enumeration space}\label{sec:bounding}
@@
     \centering
-    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{masktree.pdf}
+    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
     \caption{Bounded enumeration of maximum independent sets.
@@
 
-\section{The fitting approach to computing the independence polynomial}\label{sec:finitefield}
-In this section, we propose to find the independence polynomial by fitting $\alpha(G)+1$ random pairs of $x_{i}$ and $y_{i} = I(G,x_{i})$.
-One can then compute the independence polynomial coefficients $a_{i}$ by solving the linear equation:
-\begin{equation}
-\left(\begin{matrix}
-1 & x_0 & x_0^2 & \ldots & x_0^{\alpha(G)} \\
-1 & x_1 & x_1^2 & \ldots & x_1^{\alpha(G)} \\
-\vdots & \vdots & \vdots &\ddots & \vdots \\
-1 & x_{\alpha(G)} & x_{\alpha(G)}^2 & \ldots & x_{\alpha(G)}^{\alpha(G)}
-\end{matrix}\right)
-\left(\begin{matrix}
-a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
-\end{matrix}\right)
-= \left(\begin{matrix}
-y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
-\end{matrix}\right).\label{eq:lineareq}
-\end{equation}
-Unlike using the polynomial numbers in \Eq{eq:polynomial},  the fitting approach does not have the linear overhead in space.
-However, since the independence polynomial coefficients can have a huge order-of-magnitude range, the round-off errors can be larger than the value itself when using floating-point numbers in computation.
-To avoid using the arbitrary precision number that can be very slow and is incompatible with GPU devices, we introduce the following finite-field algebra $\text{GF}(p)$ approach:
-\begin{equation}
-\eqname{GF$(p)$}
-\begin{split}
-    x ~\oplus~ y &= x+y\pmod p,\\
-    x ~\odot~ y &= xy\pmod p,\\
-    \mymathbb{0} &= 0,\\
-    \mymathbb{1} &= 1.
-\end{split}\label{eq:finitefield}
-\end{equation}
-Regarding the finite-field algebra, we have the following observations:
-\begin{enumerate}
-    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
-The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
-    \item Given the remainders of a larger unknown integer $x$ over a set of co-prime integers $\{p_1, p_2, \ldots, p_n\}$,
-    $x \pmod {p_1 \times p_2 \times \ldots \times p_n}$ can be computed using the Chinese remainder theorem. With this, one can infer big integers from small integers.
-\end{enumerate}
-With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
-The algorithm iterates over a sequence of large prime numbers until convergence.
-In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
-Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
-As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
-If this number does not change compared with the previous iteration, it indicates the convergence of the result and the program terminates.
-All computations are done with integers of fixed-width $W$ except the last step of applying the Chinese remainder theorem, where we use arbitrary precision integers to represent the counting.
-
-\LinesNumberedHidden
-\begin{algorithm}[!ht]
-    \small
-    \SetAlgoNoLine
-    %\LinesNumbered
-    Let $P = 1$, $W$ be the integer width, vector $\chi = (0,1,2, \ldots, \alpha(G))$, matrix $X_{ij} = (\chi_i)^j$, where $i,j = 0, 1, \ldots, \alpha(G)$\;
-
-    \While{true}{
-        compute the largest prime $p$ that $\gcd(p, P) = 1$ and $p < 2^W$\;
-
-        \For{$i=0\ldots\alpha(G)$}{
-            $y_i \pmod p$ = ${\rm contract\_tensor\_network}(\chi_i\pmod p)$ \tcp*[l]{on $\text{GF}(p)$}
-        }
-
-        $A_p = (a_0, a_1, \ldots, a_{\alpha(G)}) \pmod p = {\rm gaussian\_elimination}(X, (y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p) $\;
-
-        $A_{P\times p} = {\rm chinese\_remainder}(A_P, A_p)$\;
-
-        \If{$A_P = A_{P \times p}$}{
-            \Return $A_P$ \tcp*[l]{converged}
-        }
-        $P = P \times p$\;
-    }\caption{Computing the independence polynomial exactly without integer overflow}\label{alg:finitefield} 
-\end{algorithm}
-
 \section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
@@
 
-\section{Integer sequence formed by the number of independent sets}
-
-We computed the number of independent sets on square lattices and King's graphs with our generic tensor network contraction algorithm on GPUs.
-The tensor element type is the finite-field algebra so that we can reach an arbitrary precision.
-We also computed the independence polynomial for these lattices up to size $30\times 30$ in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repository}.
-
-\begin{table}[h]
-\caption{The number of independent sets for square lattice graphs of size $L\times L$. This forms the integer sequence \href{https://oeis.org/A006506}{OEIS A006506}.
-Here we only include two updated entries for $L=38,39$, which, to our knowledge, has not been computed before~\cite{Butera2014}.
-}
-\begin{center}
-\scalebox{0.9}{
-\begin{tabular}{|c| >{\centering\arraybackslash} p{0.95\linewidth}|}
- \hline $L$  & square lattice graphs \\
- \hline $38$ & 616 412 251 028 728 207 385 738 562 656 236 093 713 609 747 387 533 907 560 081 990 229 746 115 948 572 583 817 557 035 128 726 922 565 913 748 716 778 414 190 432 479 964 245 067 083 441 583 742 870 993 696 157 129 887 194 203 643 048 435 362 875 885 498 554 979 326 352 127 528 330 481 118 313 702 375 541 902 300 956 879 563 063 343 972 979\\
- \hline $39$ &  29 855 612 447 544 274 159 031 389 813 027 239 335 497 014 990 491 494 036 487 199 167 155 042 005 286 230 480 609 472 592 158 583 920 411 213 748 368 073 011 775 053 878 033 685 239 323 444 700 725 664 632 236 525 923 258 394 737 964 155 747 730 125 966 370 906 864 022 395 459 136 352 378 231 301 643 917 282 836 792 261 715 266 731 741 625 623 207 330 411 607\\
-  \hline
-\end{tabular}
-}
-\end{center}
-\label{tbl:squaregrid}
-\end{table}
-% online digit seperator: https://www.browserling.com/tools/thousands-separator
-
 \section{Computing maximum sum combination}\label{sec:maxsum}
@@
 
-\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{fig7.pdf}}
+\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
 
@@
 
-\lstinputlisting[breaklines]{demo.jl}
+\lstinputlisting[breaklines]{../democode/demo.jl}
+
+\bibliographystyle{siamplain}
+\bibliography{refs}
 

### 2022-06-07 paper/paper.tex
seperate suppl

@@
 \documentclass[onefignum, onetabnum]{siamart190516}
-%\usepackage{natbib}
-%\usepackage[sort]{cite}
-\pdfoutput=1
-%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amssymb}
-\usepackage{tabularx}
-\usepackage{quoting}
-\usepackage{upquote}
-\usepackage{subcaption}
-\usepackage{multicol}
-\usepackage{cancel}
-\usepackage[framemethod=TikZ]{mdframed}
-\usetikzlibrary{shapes}
-\usetikzlibrary{snakes}
-\usetikzlibrary{shapes.geometric}
-\usepackage{wrapfig}
-%\usepackage{caption}
-%\usepackage[plain]{algorithmic}
+
 \usepackage[linesnumbered, ruled, vlined, algo2e]{algorithm2e}
-\usepackage{algpseudocode}
-\usepackage{rotating}
-%\usepackage{cite}
-\usepackage{booktabs}
-%\usepackage{unicode-math}
-%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-%\usepackage{algpseudocode}% http://ctan.org/pkg/algpseudocode
-\usepackage{xcolor}% http://ctan.org/pkg/xcolor
-\makeatletter
-\newsavebox{\@brx}
-\newcommand{\llangle}[1][]{\savebox{\@brx}{\(\m@th{#1\langle}\)}%
-  \mathopen{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
-\newcommand{\rrangle}[1][]{\savebox{\@brx}{\(\m@th{#1\rangle}\)}%
-  \mathclose{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
-\makeatother
-\usepackage{bbm}
-\usepackage{jlcode}
-\usepackage{graphicx}
-\usepackage{amsmath,color}
-\usepackage{mathrsfs}
-\usepackage{float}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{indentfirst}
-\usepackage{txfonts}
-%\usepackage[epsilon, tsrm, altpo]{backnaur}
-
-\makeatletter
-\def\parsept#1#2#3{%
-    \def\nospace##1{\zap@space##1 \@empty}%
-    \def\rawparsept(##1,##2){%
-        \edef#1{\nospace{##1}}%
-        \edef#2{\nospace{##2}}%
-    }%
-    \expandafter\rawparsept#3%
-}
-\makeatother
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-\newcommand{\listingcaption}[1]%
-{%
-\refstepcounter{lstlisting}\hfill%
-Listing \thelstlisting: #1\hfill%\hfill%
-}%
-\newcolumntype{b}{X}
-\newcolumntype{s}{>{\hsize=.7\hsize}X}
-\usepackage{listings}
-\lstset{
-    language=Julia,
-    basicstyle=\ttfamily\scriptsize,
-    numberstyle=\scriptsize,
-    % numbers=left,
-    backgroundcolor=\color{gray!7},
-    %backgroundcolor=\color{white},
-    %frame=single,
-    xleftmargin=2em,
-    tabsize=2,
-    rulecolor=\color{black!15},
-    %title=\lstname,
-    escapeinside={(*}{*)},
-    breaklines=true,
-    %breakatwhitespace=true,
-    %framextopmargin=2pt,
-    %framexbottommargin=2pt,
-    frame=bt,
-    extendedchars=true,
-    inputencoding=utf8,
-    columns=fullflexible,
-    %escapeinside={(*@}{@*)},
-}
-
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=1000
-\hbadness=1000
-
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-
-%Journal reference.  Comma sets off: name, vol, page, year
-\def\journal #1, #2, #3, 1#4#5#6{{\sl #1~}{\bf #2}, #3 (1#4#5#6) }
-\def\pr{\journal Phys. Rev., }
-\def\prb{\journal Phys. Rev. B, }
-\def\prl{\journal Phys. Rev. Lett., }
-\def\pl{\journal Phys. Lett., }
-%\def\np{\journal Nucl. Phys., }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\usepackage[colorlinks, citecolor=blue]{hyperref}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\newcommand{\eqname}[1]{\stepcounter{equation}\tag{\theequation : #1}}
-%%%%%% Shortcut related
-\newcommand{\<}{\langle}
-\renewcommand{\>}{\rangle}
-\newcommand{\out}{{\vx^L}}
-\newcommand{\inp}{{\vx^0}}
-\newcommand{\cquad}{{{ }_{\quad}}}
-\newcommand{\pluseq}{\mathrel{+}=}
-\newcommand{\minuseq}{\mathrel{-}=}
-\newcommand{\vx}{{\mathbf{x}}}
-\newcommand{\vg}{{\mathbf{g}}}
-\newcommand{\vp}{{\mathbf{p}}}
-\newcommand{\vy}{{\mathbf{y}}}
-\newcommand{\Var}{{\mathrm{Var}}}
-\newcommand{\Mean}{{\mathrm{E}}}
-\newcommand{\vvalue}{{\texttt{value}}}
-\newcommand{\grad}{{\texttt{grad}}}
-\newcommand{\parameter}{{\texttt{parameter}}}
-%%%%%% Convention related
-\newcommand{\SWAP}{{\rm SWAP}}
-\newcommand{\CNOT}{{\rm CNOT}}
-\newcommand{\bigO}{{\mathcal{O}}}
-\newcommand{\X}{{\rm X}}
-\renewcommand{\H}{{\rm H}}
-\newcommand{\Rx}{{\rm Rx}}
-\renewcommand{\v}[1]{{\bf #1}}
-\newcommand{\dataset}{{\mathcal{D}}}
-\newcommand{\wfunc}{{\psi}}
-\newcommand{\SU}{{\rm SU}}
-\newcommand{\UU}{{\rm U}}
-\newcommand{\thetav}{{\boldsymbol{\theta}}}
-\newcommand{\gammav}{{\boldsymbol{\gamma}}}
-\newcommand{\thetai}{{\theta^\alpha_l}}
-\newcommand{\Expect}{{\mathbb{E}}}
-\newcommand{\Tr}{{\rm Tr}}
-\newcommand{\etc}{{\it etc~}}
-\newcommand{\etal}{{\it etal~}}
-\newcommand{\xset}{\mathbf{X}}
-\newcommand{\fl}{\texttt{fl}}
-\newcommand{\pdata}{\mathbf{\pi}}
-\newcommand{\q}{\mathbf{q}}
-\newcommand{\epdata}{\mathbf{\hat{\pi}}}
-\newcommand{\gammaset}{\boldsymbol{\Gamma}}
-\newcommand{\ei}{{\mathbf{e}_l^\alpha}}
-\newcommand{\vtheta}{{\boldsymbol{\theta}}}
-\newcommand{\sigmag}{{\nu}}
-\newcommand{\sigmai}[2]{{\sigma^{#2}_{#1}}}
-\newcommand{\qi}[1]{{q^{\alpha_{#1}}_{#1}}}
-\newcommand{\BAS}{Bars-and-Stripes}
-\newcommand{\circled}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
-\newcommand{\qexpect}[1]{{\left\langle #1\right\rangle}}
-\newcommand{\expect}[2]{{\mathop{\mathbb{E}}\limits_{\substack{#2}}\left[#1\right]}}
-\newcommand{\var}[2]{{\mathop{\mathrm{Var}}\limits_{\substack{#2}}\left(#1\right)}}
-\newcommand{\pshift}[1]{{p_{\thetav+#1}}}
-\newcommand{\upcite}[1]{\textsuperscript{\cite{#1}}}
-\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\Fig}[1]{Fig.~\ref{#1}}
-\newcommand{\Lst}[1]{Listing.~\ref{#1}}
-\newcommand{\Tbl}[1]{Table~\ref{#1}}
-\newcommand{\Sec}[1]{Sec.~\ref{#1}}
-\newcommand{\App}[1]{Appendix~\ref{#1}}
-\newcommand{\bra}[1]{\mbox{$\left\langle #1 \right|$}}
-\newcommand{\ket}[1]{\mbox{$\left| #1 \right\rangle$}}
-\newcommand{\braket}[2]{\mbox{$\left\langle #1 | #2 \right\rangle$}}
-\newcommand{\tr}[1]{\mathrm{tr}\mbox{$\left[ #1\right]$}}
-
-\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-
-%%%%%% Comment related
-\newcommand{\red}[1]{[{\bf  \color{red}{ST: #1}}]}
-\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{ST: #1}}}]}
-\newcommand{\green}[1]{[{\bf  \color{green}{XG: #1}}]}
-\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
-\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
-\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
-\newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
-\newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
-\newcommand{\purple}[1]{[{\bf  \color{purple}{MC: #1}}]}
-\newcommand{\xpurple}[1]{[{\bf  \color{purple}{\sout{MC: #1}}}]}
-\newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
-
-\newcounter{example}
-\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
-   \noindent \textbf{Example~\theexample. #1} \rmfamily}{\medskip}
-
-%\newtheorem{theorem}{\textit{Theorem}}
-%\newtheorem{corollary}{\textit Branching Rule}
-%\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
-%\newtheorem{defin}[thm]{Definition}
-
-\makeatother
-
-%\externaldocument{ex_supplement}
-
-\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks
-%\thanks{\funding{...}}
-}
-
-\author{
-Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA  %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
-    (\email{jinguoliu@g.harvard.edu}).}
-\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}, contributed equally with Jin-Guo Liu to this work.).}
-\and Madelyn Cain\footnotemark[2]
-\and Mikhail D. Lukin\footnotemark[2]
-\and Sheng-Tao Wang\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
-}
+\input{shared}
+
+\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks}
+
+\externaldocument{suppl}
 
@@
 %To keep the discussion focused, 
-In what follows, for clarity of presentation, we focus on the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in  \App{sec:otherproblems}.
+In what follows, for clarity of presentation, we focus on the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in \Cref{sec:otherproblems}.
 The latter include cutting, matching, vertex coloring, satisfiability,  dominating set,  set packing,  set covering, and the clique problem.
@@
 The paper is organized as follows.
-We first introduce the basic concepts of tensor networks and generic programming in \Sec{sec:tn} and \Sec{sec:generic}.
-Then we show how to reduce the independent set problem to a tensor network contraction problem in \Sec{sec:tnmap}. 
-Subsequently, we explain how to engineer the element types to compute various solution space properties in \Sec{sec:counting}, \Sec{sec:enumeration}, and \Sec{sec:weighted}.
+We first introduce the basic concepts of tensor networks and generic programming in \Cref{sec:tn} and \Cref{sec:generic}.
+Then we show how to reduce the independent set problem to a tensor network contraction problem in \Cref{sec:tnmap}. 
+Subsequently, we explain how to engineer the element types to compute various solution space properties in \Cref{sec:counting}, \Cref{sec:enumeration}, and \Cref{sec:weighted}.
 % to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs, respectively.
 % by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
-Lastly, we provide three example applications in \Sec{sec:examples} to demonstrate the versatility of our tool.
-A benchmark to demonstrate the performance of our algorithms can be found in both the supplementary material and the code repository.
+Lastly, we provide three example applications in \Cref{sec:examples} to demonstrate the versatility of our tool.
+A benchmark to demonstrate the performance of our algorithms can be found in both the \Cref{sec:benchmark} and the code repository.
 %In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
@@
 Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors. 
-While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in the supplementary material.
+While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \Cref{sec:tensorbad}.
 % because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-%However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \App{sec:tensorbad}.
+%However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \Cref{sec:tensorbad}.
 
@@
 In the following sections, we will show how to compute solution space properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebra.
-The Venn diagram in \Fig{fig:venn-diagram} shows the different types of algebra we will introduce in the main text and their relation, and Table~\ref{tbl:generictypes} summarizes which solution space properties can be computed by which tensor element types.
+The Venn diagram in \Cref{fig:venn-diagram} shows the different types of algebra we will introduce in the main text and their relation, and \Cref{tbl:generictypes} summarizes which solution space properties can be computed by which tensor element types.
 
@@
 ``Largest order'' and ``Largest 2 orders'' mean truncating the polynomial by only keeping its largest or largest two orders.
-    The purposes of these element types can be found in \Tbl{tbl:generictypes}.}
+    The purposes of these element types can be found in \Cref{tbl:generictypes}.}
      \label{fig:venn-diagram}
@@
    {$\mathbbm{R}$}     & {Counting of all independent sets} \\
-   {Polynomial} (\Eq{eq:polynomial})     & {Independence polynomial} \\
-   {Tropical (\Eq{eq:tropical})}    & {Maximum independent set size} \\
-   {Extended tropical of order $k$ (\Eq{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
-   {Polynomial truncated to $k$-th order (\Eq{eq:countingtropical} and \Eq{eq:max2poly})}     & {$k$ largest independent sizes and their degeneracy} \\
-   {Set} (\Eq{eq:set})     & {Enumeration of independent sets} \\
-   {Sum-Product expression tree} (\Eq{eq:expr})     & {Sampling of independent sets} \\
-   {Polynomial truncated to largest order combined with bit string} (\Eq{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
-   {Polynomial truncated to $k$-th order combined with set} (\Eq{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
+   {Polynomial} (\Cref{eq:polynomial})     & {Independence polynomial} \\
+   {Tropical (\Cref{eq:tropical})}    & {Maximum independent set size} \\
+   {Extended tropical of order $k$ (\Cref{eq:ext-tropical})}    & {Largest $k$ independent set sizes} \\
+   {Polynomial truncated to $k$-th order (\Cref{eq:countingtropical} and \Cref{eq:max2poly})}     & {$k$ largest independent sizes and their degeneracy} \\
+   {Set} (\Cref{eq:set})     & {Enumeration of independent sets} \\
+   {Sum-Product expression tree} (\Cref{eq:expr})     & {Sampling of independent sets} \\
+   {Polynomial truncated to largest order combined with bit string} (\Cref{eq:singleconfig})     & {Maximum independent set size and one of such configurations} \\
+   {Polynomial truncated to $k$-th order combined with set} (\Cref{eq:countingtropicalset})    & {$k$ largest independent set sizes and their enumeration} \\
             \bottomrule
@@
 This section describes the reduction of the independent set problem to a tensor network contraction problem.
-An alternative interpretation, perhaps more accessible to physicists, can be found in \App{sec:energymodel}, where we introduce the reduction from the energy model of hardcore lattice gases~\cite{Dyre2016, Fernandes2007}.
+An alternative interpretation, perhaps more accessible to physicists, can be found in \Cref{sec:energymodel}, where we introduce the reduction from the energy model of hardcore lattice gases~\cite{Dyre2016, Fernandes2007}.
 Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
@@
 
-For a general graph, it is computationally inefficient to evaluate \Eq{eq:idp} by directly summing up the $2^{|V|}$ products.
+For a general graph, it is computationally inefficient to evaluate \Cref{eq:idp} by directly summing up the $2^{|V|}$ products.
 A better approach to evaluate a tensor network is: to find a good pair-wise tensor contraction order as a binary tree and then contract two tensors at a time by this order.
@@
 \section{Independence polynomial}\label{sec:indpoly}
-Let $x_i = x$ and $w_i = 1$, \Eq{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
+Let $x_i = x$ and $w_i = 1$, \Cref{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
 \begin{equation}\label{eq:idpdef}
@@
 An independence polynomial is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-%Its connection to \Eq{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
+%Its connection to \Cref{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
 %and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
@@
 However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
-%first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in Sec.~\ref{sec:generic}.
+%first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in \Cref{sec:generic}.
 %\purple{I'd
@@
 The multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
-The tensors $W$ and $B$, which are introduced in the previous section (Sec.~\ref{sec:tnmap}), can thus be written as 
+The tensors $W$ and $B$, which are introduced in the previous section (\Cref{sec:tnmap}), can thus be written as 
 \begin{equation}
@@
 These are because the number of independent sets at different sizes may vary by tens or even hundreds of orders of magnitude.
-For practical methods to evaluate these coefficients, we refer readers to \App{sec:finitefield}, where we provide an accurate and memory-efficient method to find the polynomial by contracting and fitting on finite field algebra.
+For practical methods to evaluate these coefficients, we refer readers to \Cref{sec:finitefield}, where we provide an accurate and memory-efficient method to find the polynomial by contracting and fitting on finite field algebra.
 For simplicity, we use this less efficient polynomial algebra for the discussion in the main text.
@@
 \end{equation}
-Algebra \Eq{eq:tropical} and \Eq{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.
+Algebra \Cref{eq:tropical} and \Cref{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.
 For independent set calculations here, the vertex tensor and edge tensor becomes:
@@
 Instead of counting just the MISs, one may also be interested in counting the independent sets with the largest several sizes.
-For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Eq{eq:polynomial} as:
+For example, if one is interested in counting only $a_{\alpha(G)}$ and $a_{\alpha(G)-1}$, we can define a truncated polynomial algebra by keeping only the largest two coefficients in the polynomial in \Cref{eq:polynomial} as:
 \begin{equation}
@@
 The configuration enumeration of independent sets include, for example, the enumeration of all independent sets, the enumeration of all MISs, and the enumeration of independent sets with the largest several sizes.
-Recall that in the definition of a vertex tensor in \Eq{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
+Recall that in the definition of a vertex tensor in \Cref{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
 The multiplication between labeled variables is commutative while the summation of labeled variables forms a set.
@@
 
-This set algebra can serve as the coefficients in \Eq{eq:polynomial} to enumerate independent sets of all different sizes, \Eq{eq:countingtropical} to enumerate all MISs, or \Eq{eq:max2poly} to enumerate all independent sets of sizes $\alpha(G)$ and $\alpha(G)-1$.
+This set algebra can serve as the coefficients in \Cref{eq:polynomial} to enumerate independent sets of all different sizes, \Cref{eq:countingtropical} to enumerate all MISs, or \Cref{eq:max2poly} to enumerate all independent sets of sizes $\alpha(G)$ and $\alpha(G)-1$.
 As long as the coefficients in a truncated polynomial are members of a commutative semiring, the polynomial itself is a commutative semiring.
-For example, to enumerate only the MISs, we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Eq{eq:set} and the exponents follow the max-plus tropical algebra.
+For example, to enumerate only the MISs, we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Cref{eq:set} and the exponents follow the max-plus tropical algebra.
 The combined operations become: 
@@
 However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
-We introduce the bounding technique in \App{sec:bounding} to avoid this issue.
+We introduce the bounding technique in \Cref{sec:bounding} to avoid this issue.
 One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
-It will be discussed in \App{sec:maximal} since it requires using a different tensor network structure.
+It will be discussed in \Cref{sec:maximal} since it requires using a different tensor network structure.
 
 If one is interested in obtaining only one MIS configuration, they can just keep one configuration in each tensor element to save the computational effort.
-By replacing the sets of bit strings in \Eq{eq:set} with a single bit string, we have the following algebra
+By replacing the sets of bit strings in \Cref{eq:set} with a single bit string, we have the following algebra
 
@@
 When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
-To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.\ instead of directly computing a set using the algebra in \Eq{eq:set}, we store the process of computing it.
+To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.\ instead of directly computing a set using the algebra in \Cref{eq:set}, we store the process of computing it.
 Each node in this tree is a quadruple $(type, data, left, right)$, where $type$ is one of \texttt{LEAF}, \texttt{ZERO}, \texttt{SUM} and \texttt{PROD}, $data$ is a bit string as the content in a \texttt{LEAF} node, and $left$ and $right$ are left and right operands of a \texttt{SUM} or \texttt{PROD} node.
@@
 
-This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Eq{eq:set}) forms rather than their storage.
+This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Cref{eq:set}) forms rather than their storage.
 Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with the largest several sizes.
@@
 The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$.
-An efficient algorithm for computing the maximum sum combination problem can be found in the supplementary material.
+An efficient algorithm for computing the maximum sum combination problem can be found in \Cref{sec:maxsum}.
 The vertex tensor and edge tensor become
@@
 where we have used the equation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
-To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Eq{eq:singleconfig}).
+To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
 Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
@@
 \subsection{Number of independent sets and entropy constant for hardcore lattice gases}\label{sec:entropy}
-We compute the counting of all independent sets for graphs shown in Figure~\ref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
-The types of graphs include: the square lattice graphs (Figure~\ref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (Figure~\ref{fig:lattices}(b));
-the King's graphs  (Figure~\ref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (Figure~\ref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
+We compute the counting of all independent sets for graphs shown in \Cref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
+The types of graphs include: the square lattice graphs (\Cref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (\Cref{fig:lattices}(b));
+the King's graphs  (\Cref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (\Cref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
 
@@
 Similarly, we can define entropy constants for other lattice gases.
-In \Fig{fig:hardsquare}, we look at how $F(L,L)^{1/\lfloor pL^2\rceil}$ scales as a function of the grid size $L$ for all types of graphs shown in Figure~\ref{fig:lattices}.
+In \Cref{fig:hardsquare}, we look at how $F(L,L)^{1/\lfloor pL^2\rceil}$ scales as a function of the grid size $L$ for all types of graphs shown in \Cref{fig:lattices}.
 Our results match the known results for the non-disordered square lattice and King's graphs.
@@
     \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/lattices.pdf}
-    \caption{The types of graphs used in the case study in section \ref{sec:entropy}.
+    \caption{The types of graphs used in the case study in \Cref{sec:entropy}.
     The lattice dimensions are $L\times L$. (a) square lattice graphs. (b) square lattice graphs with a filling factor $p=0.8$.
@@
     \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
-    \caption{Mean entropy for lattice gases on graphs defined in \Fig{fig:lattices}.
+    \caption{Mean entropy for lattice gases on graphs defined in \Cref{fig:lattices}.
     We sampled $1000$ instances for $p=0.8$ lattices and the error bar is too small to be visible.
@@
 At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to directly sample from the target configuration space.
-For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Fig{fig:hamming}.
+For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Cref{fig:hamming}.
 We observe a clear single peak structure at a fixed distance normalized by the MIS size for the King's graphs, indicating the absence of the overlap gap property in a random King's graph at $0.8$ filling.
@@
 that the King's graphs with defects mapped from hard MIS instances have a very small measure in the total defected King's graph space. In contrast, 
-very different pair-wise Hamming distributions are obtained in \Fig{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
+very different pair-wise Hamming distributions are obtained in \Cref{fig:hamming}(b), where we observed the multiple peak structure when the control parameter $\gamma$ is big enough.
 It indicates the existence of disconnected clusters in the configuration space of the MIS problem on $3$-regular graphs.
@@
 %Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space. However, 
-By enumerating the configurations using techniques described in the present work, we found that %n found that there was no clustering in the solution space as in Sec.~\ref{sec:overlap-gap}, and instead
+By enumerating the configurations using techniques described in the present work, we found that %n found that there was no clustering in the solution space as in \Cref{sec:overlap-gap}, and instead 
 simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
@@
 %and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
-Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in Sec.~\ref{sec:overlap-gap}.
+Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in \Cref{sec:overlap-gap}.
 
 Although the performance of the quantum algorithm is more challenging to understand due to the inherent difficulty in studying quantum systems, the present methods allow one 
-to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in Figure~\ref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
+to gain significant insights by visualizing the experimental outputs of a quantum algorithm over the solution space, as shown in \Cref{fig:exp_configuratoins} for instances with $39$ nodes~\cite{Ebadi2022}.
 Here, the structure of the solution space is shown on a graph where each vertex represents a large independent set.
@@
 In the case where a large superposition state of local minima is created during the coherent evolution, the quantum algorithm achieves a quadratic speedup over simulated annealing.
-%Consistent with Sec.~\ref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
+%Consistent with \Cref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
 Looking forward, we expect these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
@@
 %With different algebras, the contraction of the same tensor network gives us the different properties.
-The different data types introduced in the main text to compute these properties are summarized in the diagram in \Fig{fig:venn-diagram}.
-The class of problems solvable by a tensor network includes but is not limited to maximum independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \App{sec:otherproblems}.
+The different data types introduced in the main text to compute these properties are summarized in the diagram in \Cref{fig:venn-diagram}.
+The class of problems solvable by a tensor network includes but is not limited to maximum independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \Cref{sec:otherproblems}.
 
@@
 The source code in Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
-There is a short introduction to this repository as well a gist to show how it works in the supplementary material as well.
+There is a short introduction to this repository as well a gist to show how it works in \Cref{sec:technical} as well.
 We expect our tool can be used to understand and study many interesting applications of independent sets and beyond.
@@
 \end{equation}
-where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Eq{eq:eng}, which is the independence constraint.
-By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Eq{eq:vertextensor} and \Eq{eq:edgetensor}.
-If we further let $w_i=1$, the second line of \Eq{eq:partition} is equivalent to the independence polynomial.
+where the $0$ in the edge tensor comes from $e^{-\beta\infty}$ in the second term of \Cref{eq:eng}, which is the independence constraint.
+By letting $x = e^{\beta}$, we get the tensor network for computing the independence polynomial as described by \Cref{eq:vertextensor} and \Cref{eq:edgetensor}.
+If we further let $w_i=1$, the second line of \Cref{eq:partition} is equivalent to the independence polynomial.
 
@@
 
-Let us consider the graph in Example~\ref{eg:tensorcontraction}.
-The corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation.
-\\
+Let us consider the graph in \Cref{eg:tensorcontraction}. The corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation. \\
 
@@
 where $b_k$ is the number of maximal independent sets of size $k$.
-Comparing with the independence polynomial in \Eq{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
+Comparing with the independence polynomial in \Cref{eq:idpdef}, we have $b_{k} \leq a_{k}$ and $b_{\alpha(G)} = a_{\alpha(G)}$.
 $D_m(G, 1)$ counts the total number of maximal independent sets~\cite{Gaspers2012, Manne2013};
@@
 
-The benchmark of computing the maximal independent set properties on $3$-regular graphs is shown in the supplementary material.
+The benchmark of computing the maximal independent set properties on $3$-regular graphs is shown in \Cref{sec:benchmark}.
 
@@
 It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Eq{eq:vertextensor}, while the edge tensor generalizes \Eq{eq:edgetensor} to higher dimensions
+The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Cref{eq:vertextensor}, while the edge tensor generalizes \Cref{eq:edgetensor} to higher dimensions
 \begin{equation}
@@
 Here, a circle is a tensor, an arrow specifies the execution direction of a function, $\overline A$ is the Boolean mask for $A$ and $\circ$ is the Hadamard (element-wise) multiplication.
-(a) is the forward pass with tropical algebra (\Eq{eq:tropical}) for computing $\alpha(G)$.
+(a) is the forward pass with tropical algebra (\Cref{eq:tropical}) for computing $\alpha(G)$.
      (b) is the backward pass for computing Boolean gradient masks.
-     (c) is the masked tensor network contraction with tropical algebra combined with sets (\Eq{eq:countingtropicalset}) for enumerating configurations.}
+     (c) is the masked tensor network contraction with tropical algebra combined with sets (\Cref{eq:countingtropicalset}) for enumerating configurations.}
      \label{fig:bounding}
@@
 
-When using the algebra in \Eq{eq:countingtropicalset} to enumerate all MISs, the program often stores significantly more intermediate configurations than necessary.
+When using the algebra in \Cref{eq:countingtropicalset} to enumerate all MISs, the program often stores significantly more intermediate configurations than necessary.
 To reduce the space overhead, we will show how to bound the searching space using the MIS size $\alpha(G)$.
-The bounded contraction consists of three stages as shown in \Fig{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
+The bounded contraction consists of three stages as shown in \Cref{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
 (b) Then, we compute a Boolean mask for each cached tensor, where we use a Boolean \texttt{true} to represent a tensor element having a contribution to the MIS and Boolean \texttt{false} otherwise.
-(c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
+(c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Cref{eq:countingtropicalset} to obtain all MIS configurations.
 The crucial part is computing the masks in step (b).
@@
 \end{equation}
-Unlike using the polynomial numbers in \Eq{eq:polynomial},  the fitting approach does not have the linear overhead in space.
+Unlike using the polynomial numbers in \Cref{eq:polynomial},  the fitting approach does not have the linear overhead in space.
 However, since the independence polynomial coefficients can have a huge order-of-magnitude range, the round-off errors can be larger than the value itself when using floating-point numbers in computation.
@@
 \begin{enumerate}
-    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Eq{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
+    \item One can use Gaussian elimination~\cite{Golub2013} to solve the linear equation \Cref{eq:lineareq} since it is a generic algorithm that works for any elements with field algebra.
 The multiplicative inverse of a finite-field algebra can be computed with the extended Euclidean algorithm.
@@
 \end{enumerate}
-With these observations, we develop Algorithm~\ref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
+With these observations, we develop \Cref{alg:finitefield} to compute the independence polynomial exactly without introducing space overheads.
 The algorithm iterates over a sequence of large prime numbers until convergence.
 In each iteration, we choose a large prime number $p$, and contract the tensor networks to evaluate the polynomial for each variable $\chi = (x_{0}, x_{1}, \ldots, x_{\alpha(G)})$ on ${\rm GF}(p)$ and denote the outputs as $(y_0, y_1, \ldots, y_{\alpha(G)}) \pmod p$.
-Then we solve \Eq{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
+Then we solve \Cref{eq:lineareq} using Gaussian elimination on ${\rm GF}(p)$ to find the coefficient modulo $p$, $A_p \equiv (a_0, a_1, \ldots, a_{\alpha(G)})\pmod p$.
 As the last step of each iteration, we apply the Chinese remainder theorem to update $A \pmod P $ to $ A \pmod {P\times p}$, where $P$ is a product of all prime numbers chosen in previous iterations.
@@
 
-Alternatively, one can use a faster but less accurate Fourier transformation based method to fit this polynomial, which is detailed and benchmarked in the supplementary material.
+Alternatively, one can use a faster but less accurate Fourier transformation based method to fit this polynomial, which is detailed and benchmarked in \Cref{sec:benchmark}.
 

### 2022-06-07 paper/suppl.tex
seperate suppl

@@
-%\documentclass[onefignum, onetabnum]{siamart190516}
-\documentclass[a4paper, 12pt]{article}
-%\usepackage{natbib}
-%\usepackage[sort]{cite}
-\pdfoutput=1
-\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{amssymb}
-\usepackage{tabularx}
-\usepackage{quoting}
-\usepackage{upquote}
-\usepackage{subcaption}
-\usepackage{multicol}
-\usepackage{cancel}
-\usepackage[framemethod=TikZ]{mdframed}
-\usetikzlibrary{shapes}
-\usetikzlibrary{snakes}
-\usetikzlibrary{shapes.geometric}
-\usepackage{wrapfig}
-%\usepackage{caption}
-%\usepackage{algorithmic}
-\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
-\usepackage{algpseudocode}
-\usepackage{rotating}
-%\usepackage{cite}
-\usepackage{booktabs}
-%\usepackage{unicode-math}
-%\usepackage{algorithm}% http://ctan.org/pkg/algorithm
-%\usepackage{algpseudocode}% http://ctan.org/pkg/algpseudocode
-\usepackage{xcolor}% http://ctan.org/pkg/xcolor
-\makeatletter
-\newsavebox{\@brx}
-\newcommand{\llangle}[1][]{\savebox{\@brx}{\(\m@th{#1\langle}\)}%
-  \mathopen{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
-\newcommand{\rrangle}[1][]{\savebox{\@brx}{\(\m@th{#1\rangle}\)}%
-  \mathclose{\copy\@brx\kern-0.5\wd\@brx\usebox{\@brx}}}
-\makeatother
-\usepackage{bbm}
-\usepackage{jlcode}
-\usepackage{graphicx}
-\usepackage{amsmath,color}
-\usepackage{mathrsfs}
-\usepackage{float}
-\usepackage[normalem]{ulem}
-\usepackage{makecell}
-\usepackage{indentfirst}
-\usepackage{txfonts}
-\setcounter{secnumdepth}{0}
-%\usepackage[epsilon, tsrm, altpo]{backnaur}
+\documentclass[review,supplement,onefignum,onetabnum]{siamart190516}
+%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
+\usepackage[linesnumbered, ruled, vlined, algo2e]{algorithm2e}
+\input{shared}
 
-\makeatletter
-\def\parsept#1#2#3{%
-    \def\nospace##1{\zap@space##1 \@empty}%
-    \def\rawparsept(##1,##2){%
-        \edef#1{\nospace{##1}}%
-        \edef#2{\nospace{##2}}%
-    }%
-    \expandafter\rawparsept#3%
-}
-\makeatother
-\DeclareMathAlphabet{\mymathbb}{U}{BOONDOX-ds}{m}{n}
-\newcommand{\listingcaption}[1]%
-{%
-\refstepcounter{lstlisting}\hfill%
-Listing \thelstlisting: #1\hfill%\hfill%
-}%
-\newcolumntype{b}{X}
-\newcolumntype{s}{>{\hsize=.7\hsize}X}
-\usepackage{listings}
-\lstset{
-    language=Julia,
-    basicstyle=\ttfamily\scriptsize,
-    numberstyle=\scriptsize,
-    % numbers=left,
-    backgroundcolor=\color{gray!7},
-    %backgroundcolor=\color{white},
-    %frame=single,
-    xleftmargin=2em,
-    tabsize=2,
-    rulecolor=\color{black!15},
-    %title=\lstname,
-    escapeinside={(*}{*)},
-    breaklines=true,
-    %breakatwhitespace=true,
-    %framextopmargin=2pt,
-    %framexbottommargin=2pt,
-    frame=bt,
-    extendedchars=true,
-    inputencoding=utf8,
-    columns=fullflexible,
-    %escapeinside={(*@}{@*)},
-}
+\externaldocument{paper}
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=1000
-\hbadness=1000
-
-\makeatletter
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
-
-%Journal reference.  Comma sets off: name, vol, page, year
-\def\journal #1, #2, #3, 1#4#5#6{{\sl #1~}{\bf #2}, #3 (1#4#5#6) }
-\def\pr{\journal Phys. Rev., }
-\def\prb{\journal Phys. Rev. B, }
-\def\prl{\journal Phys. Rev. Lett., }
-\def\pl{\journal Phys. Lett., }
-%\def\np{\journal Nucl. Phys., }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\usepackage[colorlinks, citecolor=blue]{hyperref}
-\DeclareMathOperator*{\argmax}{arg\,max}
-
-\newcommand{\eqname}[1]{\stepcounter{equation}\tag{\theequation : #1}}
-%%%%%% Shortcut related
-\newcommand{\<}{\langle}
-\renewcommand{\>}{\rangle}
-\newcommand{\out}{{\vx^L}}
-\newcommand{\inp}{{\vx^0}}
-\newcommand{\cquad}{{{ }_{\quad}}}
-\newcommand{\pluseq}{\mathrel{+}=}
-\newcommand{\minuseq}{\mathrel{-}=}
-\newcommand{\vx}{{\mathbf{x}}}
-\newcommand{\vg}{{\mathbf{g}}}
-\newcommand{\vp}{{\mathbf{p}}}
-\newcommand{\vy}{{\mathbf{y}}}
-\newcommand{\Var}{{\mathrm{Var}}}
-\newcommand{\Mean}{{\mathrm{E}}}
-\newcommand{\vvalue}{{\texttt{value}}}
-\newcommand{\grad}{{\texttt{grad}}}
-\newcommand{\parameter}{{\texttt{parameter}}}
-%%%%%% Convention related
-\newcommand{\SWAP}{{\rm SWAP}}
-\newcommand{\CNOT}{{\rm CNOT}}
-\newcommand{\bigO}{{\mathcal{O}}}
-\newcommand{\X}{{\rm X}}
-\renewcommand{\H}{{\rm H}}
-\newcommand{\Rx}{{\rm Rx}}
-\renewcommand{\v}[1]{{\bf #1}}
-\newcommand{\dataset}{{\mathcal{D}}}
-\newcommand{\wfunc}{{\psi}}
-\newcommand{\SU}{{\rm SU}}
-\newcommand{\UU}{{\rm U}}
-\newcommand{\thetav}{{\boldsymbol{\theta}}}
-\newcommand{\gammav}{{\boldsymbol{\gamma}}}
-\newcommand{\thetai}{{\theta^\alpha_l}}
-\newcommand{\Expect}{{\mathbb{E}}}
-\newcommand{\Tr}{{\rm Tr}}
-\newcommand{\etc}{{\it etc~}}
-\newcommand{\etal}{{\it etal~}}
-\newcommand{\xset}{\mathbf{X}}
-\newcommand{\fl}{\texttt{fl}}
-\newcommand{\pdata}{\mathbf{\pi}}
-\newcommand{\q}{\mathbf{q}}
-\newcommand{\epdata}{\mathbf{\hat{\pi}}}
-\newcommand{\gammaset}{\boldsymbol{\Gamma}}
-\newcommand{\ei}{{\mathbf{e}_l^\alpha}}
-\newcommand{\vtheta}{{\boldsymbol{\theta}}}
-\newcommand{\sigmag}{{\nu}}
-\newcommand{\sigmai}[2]{{\sigma^{#2}_{#1}}}
-\newcommand{\qi}[1]{{q^{\alpha_{#1}}_{#1}}}
-\newcommand{\BAS}{Bars-and-Stripes}
-\newcommand{\circled}[1]{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {#1}}}}
-\newcommand{\qexpect}[1]{{\left\langle #1\right\rangle}}
-\newcommand{\expect}[2]{{\mathop{\mathbb{E}}\limits_{\substack{#2}}\left[#1\right]}}
-\newcommand{\var}[2]{{\mathop{\mathrm{Var}}\limits_{\substack{#2}}\left(#1\right)}}
-\newcommand{\pshift}[1]{{p_{\thetav+#1}}}
-\newcommand{\upcite}[1]{\textsuperscript{\cite{#1}}}
-\newcommand{\Eq}[1]{Eq.~(\ref{#1})}
-\newcommand{\Fig}[1]{Fig.~\ref{#1}}
-\newcommand{\Lst}[1]{Listing.~\ref{#1}}
-\newcommand{\Tbl}[1]{Table~\ref{#1}}
-\newcommand{\Sec}[1]{Sec.~\ref{#1}}
-\newcommand{\App}[1]{Appendix~\ref{#1}}
-\newcommand{\bra}[1]{\mbox{$\left\langle #1 \right|$}}
-\newcommand{\ket}[1]{\mbox{$\left| #1 \right\rangle$}}
-\newcommand{\braket}[2]{\mbox{$\left\langle #1 | #2 \right\rangle$}}
-\newcommand{\tr}[1]{\mathrm{tr}\mbox{$\left[ #1\right]$}}
-
-\newcommand{\ra}[1]{\renewcommand{\arraystretch}{#1}}
-
-%%%%%% Comment related
-\newcommand{\red}[1]{[{\bf  \color{red}{ST: #1}}]}
-\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{ST: #1}}}]}
-\newcommand{\green}[1]{[{\bf  \color{green}{XG: #1}}]}
-\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
-\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
-\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
-\newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
-\newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
-\newcommand{\purple}[1]{[{\bf  \color{purple}{MC: #1}}]}
-\newcommand{\xpurple}[1]{[{\bf  \color{purple}{\sout{MC: #1}}}]}
-\newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
-
-\newcounter{example}
-\newenvironment{example}[1][]{\refstepcounter{example}\par\medskip
-   \noindent \textbf{Example~\theexample. #1} \rmfamily}{\medskip}
-
-%\newtheorem{theorem}{\textit{Theorem}}
-%\newtheorem{corollary}{\textit Branching Rule}
-%\theoremstyle{definition}\newtheorem{definition}{\textit{Definition}}
-%\newtheorem{defin}[thm]{Definition}
-
-\makeatother
-
-%\externaldocument{ex_supplement}
-
-\title{The supplementary material of ``Computing solution space properties of combinatorial optimization problems via generic tensor networks''
-%\thanks{\funding{...}}
-}
-
-\author{
-Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA.}
-\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (contributed equally with Jin-Guo Liu to this work.).}
-\and Madelyn Cain\footnotemark[2]
-\and Mikhail D. Lukin\footnotemark[2]
-\and Sheng-Tao Wang\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
-}
-
-\begin{document}
-
-\maketitle
-
-\tableofcontents
+\title{Computing solution space properties of combinatorial optimization problems via generic tensor networks}
 
@@
 % 14N07  	Secant varieties, tensor rank, varieties of sums of powers
+\begin{document}
+\maketitle
 
@@
 We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
-The results are summarized in Figure~\ref{fig:benchmark}.
+The results are summarized in \Cref{fig:benchmark}.
 The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
@@
 
-Figure~\ref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
+\Cref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
 The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
@@
 Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
-One can see that all the computation times in figure~\ref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
+One can see that all the computation times in \Cref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
 While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
@@
 Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
-These data types do not include those defined in \Eq{eq:polynomial}, \Eq{eq:set}, \Eq{eq:ext-tropical} and \Eq{eq:expr} or a data type containing them as a part.
-In figure~\ref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
-but it may suffer from round-off errors (\App{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
-In figure~\ref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \App{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
+These data types do not include those defined in \Cref{eq:polynomial}, \Cref{eq:set}, \Cref{eq:ext-tropical} and \Cref{eq:expr} or a data type containing them as a part.
+In \Cref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
+but it may suffer from round-off errors (\Cref{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+In \Cref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \Cref{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
 The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
 
-We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Fig{fig:benchmark-maximal},
+We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Cref{fig:benchmark-maximal},
 including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
-\Fig{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
-In \Fig{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
+\Cref{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
+In \Cref{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
 
@@
 
-\section{Bounding the MIS enumeration space}\label{sec:bounding}
-\begin{figure}
-    \centering
-    \includegraphics[width=0.9\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/masktree.pdf}
-    \caption{Bounded enumeration of maximum independent sets.
-Here, a circle is a tensor, an arrow specifies the execution direction of a function, $\overline A$ is the Boolean mask for $A$ and $\circ$ is the Hadamard (element-wise) multiplication.
-(a) is the forward pass with tropical algebra (\Eq{eq:tropical}) for computing $\alpha(G)$.
-     (b) is the backward pass for computing Boolean gradient masks.
-     (c) is the masked tensor network contraction with tropical algebra combined with sets (\Eq{eq:countingtropicalset}) for enumerating configurations.}
-     \label{fig:bounding}
-\end{figure}
-
-When using the algebra in \Eq{eq:countingtropicalset} to enumerate all MISs, the program often stores significantly more intermediate configurations than necessary.
-To reduce the space overhead, we will show how to bound the searching space using the MIS size $\alpha(G)$.
-The bounded contraction consists of three stages as shown in \Fig{fig:bounding}. (a) We first compute the value of $\alpha(G)$ with tropical algebra and cache all intermediate tensors.
-(b) Then, we compute a Boolean mask for each cached tensor, where we use a Boolean \texttt{true} to represent a tensor element having a contribution to the MIS and Boolean \texttt{false} otherwise.
-(c) Finally, we perform masked tensor network contraction (i.e.\ discarding elements masked \texttt{false}) using the element type with the algebra in \Eq{eq:countingtropicalset} to obtain all MIS configurations.
-The crucial part is computing the masks in step (b).
-Note that these masks correspond to tensor elements with non-zero gradients to the MIS size; we can compute these masks by back-propagating the gradients.
-To derive the back-propagation rule for tropical tensor contraction,
-we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
-Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
-\begin{equation}
-    A_{ij} \odot B_{jk} \leq C_{ik}.
-\end{equation}
-Here $\leq$ on tropical numbers are the same as the real-number algebra.
-The equality holds for some $j'$, which means $A_{ij'}$ and $B_{j'k}$ have contributions to $C_{ik}$.
-Intuitively, one can use this relation to identify elements with nonzero gradients in $A$ and $B$,
-but if doing this directly, one loses the advantage of using BLAS libraries~\cite{TropicalGEMM} for high performance.
-Since $A_{ij} \odot B_{jk} = A_{ij} + B_{jk}$, one can move $B_{jk}$ to the right hand side of the inequality: 
-\begin{equation}
-    A_{ij} \leq C_{ik} \odot B_{jk}^{\circ -1}
-\end{equation}
-where ${}^{\circ -1}$ is the element-wise multiplicative inverse on tropical algebra (which is the additive inverse on real numbers).
-The inequality still holds if we take the minimum over $k$: 
-\begin{equation}
-    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
-\end{equation}
-On the right-hand side, we transform the operation into a tropical matrix multiplication so that we can utilize the fast tropical BLAS routines~\cite{TropicalGEMM}.
-Again, the equality holds if and only if the element $A_{ij}$ has a contribution to $C$ (i.e.\ having a non-zero gradient).
-Let the gradient mask for $C$ be $\overline C$; the back-propagation rule for gradient masks reads
-\begin{equation}\label{eq:adrule}
-\overline{A}_{ij} = \delta \left(A_{ij}, \left( \left( C^{\circ-1} \circ \overline C \right) B^{\mathsf{T}} \right)_{ij}^{\circ -1} \right),
-\end{equation}
-where $\delta$ is the Dirac delta function that returns one if two arguments have the same value and zero otherwise, $\circ$ is the element-wise product, Boolean false is treated as the tropical number $\mymathbb{0}$, and Boolean true is treated as the tropical number $\mymathbb{1}$.
-This rule defined on matrix multiplication can be easily generalized to tensor contraction by replacing the matrix multiplication between $C^{\circ-1} \circ \overline C$ and $B^{\mathsf{T}}$ by a tensor contraction.
-With the above method, one can significantly reduce the space needed to store the intermediate configurations by setting the tensor elements masked false to zero during contraction.
-
 \section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
 
-In  \App{sec:finitefield}, we show that the independence polynomial can be obtained by solving the linear equation \Eq{eq:lineareq} using the finite field algebra.
+In \Cref{sec:finitefield} in the main text, we show that the independence polynomial can be obtained by solving the linear equation \Cref{eq:lineareq} using the finite field algebra.
 One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
@@
 As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
-We summarize the algorithm as in Algorithm~\ref{alg:sumcombination}.
+We summarize the algorithm as in \Cref{alg:sumcombination}.
 
@@
 \bibliography{refs}
-
 \end{document}

### 2022-08-25 replys/reply.tex
reply

%\documentclass[]{article}
%\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\documentclass[longbibliography]{article}
\usepackage[colorlinks=true,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage[affil-it]{authblk}
\usepackage{graphicx} % Include figure files
%\usepackage{subfig}
\usepackage{subcaption}
\usepackage{bm}% bold math
\usepackage{color}
%\bibliographystyle{pnas2009}
\usepackage{fullpage}
\newcommand{\s}{\mathbf{s}}

\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\else % if luatex or xelatex
\ifxetex
\usepackage{mathspec}
\else
\usepackage{fontspec}
\fi
\defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
%\usepackage[unicode=true]{hyperref}
%\hypersetup{
%            pdfborder={0 0 0},
%            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\definecolor{or}{rgb}{0.9,0.3,0.1}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}

\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{skull}
\usepackage[affil-it]{authblk}
\usepackage{graphicx}% Include figure files
%\usepackage{subfig}
\usepackage{subcaption}
\usepackage{bm}% bold math
\usepackage{color}
%\bibliographystyle{pnas2009}
\usepackage{fullpage}
\usepackage{enumitem}
\usepackage{booktabs}       % professional-quality tables

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
%\usepackage[unicode=true]{hyperref}
%\hypersetup{
%            pdfborder={0 0 0},
%            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
%\definecolor{or}{rgb}{0.0,0.5,0.9}
\definecolor{or}{rgb}{0.9,0.3,0.1}
%\definecolor{gr}{gray}{0.4}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

%%%%%% Comment related
\newcommand{\red}[1]{[{\bf  \color{red}{ST: #1}}]}
\newcommand{\xred}[1]{[{\bf  \color{red}{\sout{ST: #1}}}]}
\newcommand{\green}[1]{[{\bf  \color{green}{XG: #1}}]}
\newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
\newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
\newcommand{\xcyan}[1]{[{\bf  \color{cyan}{\sout{ML: #1}}}]}
\newcommand{\purple}[1]{[{\bf  \color{purple}{MC: #1}}]}
\newcommand{\xpurple}[1]{[{\bf  \color{purple}{\sout{MC: #1}}}]}
\newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}

\date{}

\begin{document}

\subsection{Letter to the Editor}\label{header-n558}

Dear Dr. Oseledets,

Thank you for your handling and careful consideration of our manuscript ``Computing solution space properties of combinatorial optimization problems via generic tensor networks'', MS\#M150178, for sending it for in-depth review, and for giving us the opportunity to address the reviewer's comments and to refine our manuscript. 
%We would also like to thank reviewers for their thorough reading of our manuscript and for their constructive suggestions that have helped us improve our manuscript.
%We thank the referee for their careful readings and constructive questions which
%helped us deepen understandings on the topic and improve the presentation of the manuscript.
We are very excited that you also read through the paper and give a possitive feedback.

We have revised the manuscript according to the reviewers' constructive suggestions.
Below, we provide detailed point-to-point response to all of the reviewers' comments, as well as a summary of the changes we have introduced in the main text, figures, and supplementary materials. Thank you again for your consideration! \\

Best Wishes,\\
Jin-Guo Liu, Xun Gao, Madelyn Cain, Mikhail D. Lukin and Sheng-Tao Wang

%\newpage

\subsection{List of Main Modifications in the Manuscript}\label{header-n30}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item The Section ...
\item A new figure, ...
\item We have added a paragraph at the ...
\item In the revised Supplementary Material, a Section ...
\item In the revised Supplementary Material, the Section ...
\item The section ...
\end{enumerate}

\subsection{Responses to the Referee}

\begin{enumerate}[start=0]

\referee{
This is a review for "Computing solution space properties of combinatorial optimization problems via generic tensor networks" by Jin-Guo Liu, Xun Gao, Madelyn Cain, Mikhail Lukin, and Sheng-Tao Wang. The main contribution of the paper is claimed to be "introduction of a unified framework to compute solution space properties of a broad class of combinatorial optimization problems."
}

{\bf Response:}

\referee{
Comments:
1) line 85, combinatoric problems → combinatorial problems.

2) line 120, "commutative semiring is a field that needs not to have an additive inverse and multiplicative inverse"

I feel the authors meant "need not have" as having the additive inverse and multiplicative inverse does not violate the properties of a commutative semiring. Also, every field has multiplicative and additive inverse by definition so technically a commutative semiring is not a field. Maybe the authors could rephrase the statement to make more sense.

3) line 129, $\oplus$ resembles XOR, it may not be the best notation in my opinion in the context of computer science.

4) line 154, "we map a vertex $v \in V$ to a label $s_v \in {0,1}$ of dimension 2 where we use 0(1) to denote a vertex is absent(present) in the set"

which set? I? there is no label for the set also the type of the map(domain and co-domain) for $s_v$ is not specified, from the context and the word dimension it seems to be a pair for each v i.e. $sv:V\rightarrow{0,1}\times2$ but from the description it seems to be a single number i.e. an element of the set ${0,1}$.

5) Line 156-157, equation (4.1) is said to be indexed by $s_v$ but $s_v$ does not appear in the equation.

6) Line 158-159, " $x_v$ is a variable associated with $v$".

What kind of variable? What does raising it to an exponent mean in line 159?
}

{\bf Response:}

\referee{
A lot of effort seems to have been put in making the paper but due to the informal style of narration from the very beginning, misinterpretation is very likely, especially for a newcomer in the field, and can be quite confusing for specialists as well. The basic definitions for e.g. of tensor networks, contractions etc. could be formulated more rigorously to avoid ambiguity which would aid smoother reading of the paper. I would suggest specifying the types for the maps and variables wherever possible as there are plenty of them.
At present, the work has the flavor of a review paper. In order to address this, the main results obtained could be formulated as theorems or propositions to make them clearly visible in the body of the text as it's hard to locate them at the moment.
 }

{\bf Response:}

\referee{
Also, I recommend the authors better compare with prior work on this topic for e.g. https://arxiv.org/pdf/1405.7375.pdf and relevant references therein.
}

{\bf Response:}
~\cite{Biamonte2017}

\end{enumerate}

\bibliographystyle{unsrt}
\bibliography{refs}

\end{document}

### 2022-08-25 paper/paper.tex
update paper.tex
ave

@@
-\documentclass[onefignum, onetabnum]{siamart190516}
+\documentclass[review, onefignum, onetabnum]{siamart190516}
 
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2021, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
+\begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
+    A tensor network is a triple of $\mathcal{N} = (\Tensors, \Inputs, \Output)$ where $\Tensors = (\Tensors_1, \ldots, \Tensors_m)$ is a vector of tensors, $\Inputs$ is a map from tensor to a vector of labels $\Inputs: \Tensors_j \mapsto \mathbf{l}_j$, $(\mathbf{l}_j)_i \in \Sigma, i=1,\ldots, \rm{rank}(\Tensors_j)$.
+    $\Output$ is a vector of labels for specifying the output.
+\end{definition}
+A tensor network is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
 The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
@@
 High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
-In previous works relating tensor networks and combinatoric problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
+In previous works relating tensor networks and combinatorial problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
 %Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
@@
 We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
-Here, a commutative semiring is a field that needs not to have an additive inverse and a multiplicative inverse.
+Compared to a field, a commutative semiring does not need not to have an additive inverse and a multiplicative inverse.
 Giving up these nice properties of fields has significant implications for tensor computation: tensor network compression algorithms might not be applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014} and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
 Here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
+To define a commutative semiring with the addition operation $\OPLUS$ (not the logical \texttt{XOR} operation in computer science) and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
 \begin{align*}
-(a \oplus b) \oplus c = a \oplus (b \oplus c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\oplus$ with identity $\mymathbb{0}$}\\
-a \oplus \mymathbb{0} = \mymathbb{0} \oplus a = a &\\
-a \oplus b = b \oplus a &\\
+(a \OPLUS b) \OPLUS c = a \OPLUS (b \OPLUS c) & \hspace{5em}\text{$\triangleright$ commutative monoid $\OPLUS$ with identity $\mymathbb{0}$}\\
+a \OPLUS \mymathbb{0} = \mymathbb{0} \OPLUS a = a &\\
+a \OPLUS b = b \OPLUS a &\\
 &\\
@@
 &\\
-a \odot (b\oplus c) = a\odot b \oplus a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
-(a\oplus b) \odot c = a\odot c \oplus b\odot c &\\
+a \odot (b\OPLUS c) = a\odot b \OPLUS a\odot c  &  \hspace{5em}\text{$\triangleright$ left and right distributive}\\
+(a\OPLUS b) \odot c = a\odot c \OPLUS b\odot c &\\
 &\\
@@
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-To reduce the independent set problem on $G$ to a tensor network contraction, we first map a vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in the set.
-For each vertex $v$, we define a parameterized rank-one tensor indexed by $s_v$ as
-\begin{equation}
-    W(x_v^{w_v}) = \left(\begin{matrix}
+To reduce the independent set problem on $G$ to a tensor network contraction, we first map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in $I$.
+For each label $s_v$, we define a parameterized rank-one tensor indexed by it as
+\begin{equation}
+    W(x_v^{w_v})_{s_v} = \left(\begin{matrix}
         1 \\
         x_v^{w_v}
-    \end{matrix}\right),\label{eq:vertextensor}
+    \end{matrix}\right)_{s_v},\label{eq:vertextensor}
 \end{equation}
@@
 \section{Independence polynomial}\label{sec:indpoly}
+
+\begin{theorem}
+    The independence polynomial of a graph $G = (V, E)$ can be computed in time $O(|V|^22^{{\rm tw}(G)})$.
+\end{theorem}
 Let $x_i = x$ and $w_i = 1$, \Cref{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
@@
     \begin{split}
-    a \oplus b &= (a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
+    a \OPLUS b &= (a_0 + b_0, a_1 + b_1, \ldots, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
     a \odot b &= (a_0 + b_0, a_1b_0 + a_0b_1, a_{2}b_{0} + a_{1}b_{1} + a_{0}b_{2},  \ldots, a_{k_a} b_{k_b}),\\
@@
 \end{equation}
-where $\oplus$ and $\odot$ are the standard polynomial addition and multiplication operations.
+where $\OPLUS$ and $\odot$ are the standard polynomial addition and multiplication operations.
 The multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
+\begin{theorem}
+    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $O(|V|2^{{\rm tw}(G)})$.
+\end{theorem}
+\begin{theorem}
+    The number of $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(k|V|2^{{\rm tw}(G)})$.
+\end{theorem}
 %The method we use to count the MISs is based on the following observations:
@@
 \begin{split}
-    a_x\infty^x \oplus a_y\infty^y &= \begin{cases}
+    a_x\infty^x \OPLUS a_y\infty^y &= \begin{cases}
         (a_x + a_y)\infty^{\max(x,y)}, & x = y\\
@@
     \begin{split}
-        x \oplus y &= \max(x,y)\\
+        x \OPLUS y &= \max(x,y)\\
         x \odot y &= x + y\\
@@
     \begin{split}
-    a \oplus b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
+    a \OPLUS b &= (a_{\max(k_a, k_b)-1} + b_{\max(k_a, k_b)-1}, a_{\max(k_a, k_b)} + b_{\max(k_a, k_b)}),\\
     a \odot b &= (a_{k_a-1} b_{k_b}+a_{k_a} b_{k_b-1}, a_{k_a} b_{k_b}),\\
@@
 \section{Enumerating and sampling independent sets}\label{sec:enumeration}
+\begin{theorem}
+    Let $G = (V, E)$ be a graph and $M$ be the number of independent sets with size $>\alpha(G)-k$.
+    The independent sets with size $>\alpha(G)-k$ of $G$ can be computed in time $O(M|V|2^{{\rm tw}(G)})$.
+\end{theorem}
 
 \subsection{Set algebra for configuration enumeration}
+
 The configuration enumeration of independent sets include, for example, the enumeration of all independent sets, the enumeration of all MISs, and the enumeration of independent sets with the largest several sizes.
@@
 \begin{split}
-    s \oplus t &= s \cup t\\
+    s \OPLUS t &= s \cup t\\
     s \odot t &= \{\sigma \lor^\circ \tau \, | \, \sigma \in s, \tau \in t\}\\
@@
 \begin{split}
-    &\{00001\} \oplus \{01110, 01000\} = \{01110, 01000\} \oplus \{00001\} = \{00001,01110, 01000\}\\
-    &\{00001\} \oplus \{\} = \{00001\}\\
+    &\{00001\} \OPLUS \{01110, 01000\} = \{01110, 01000\} \OPLUS \{00001\} = \{00001,01110, 01000\}\\
+    &\{00001\} \OPLUS \{\} = \{00001\}\\
 &\\
@@
 \begin{split}
-    s_x\infty^x \oplus s_y\infty^y &= \begin{cases}
+    s_x\infty^x \OPLUS s_y\infty^y &= \begin{cases}
         (s_x \cup s_y)\infty^{\max(x,y)}, & x = y\\
@@
 \begin{split}
-    \sigma \oplus \tau &= \texttt{select}(\sigma, \tau), \\
+    \sigma \OPLUS \tau &= \texttt{select}(\sigma, \tau), \\
     \sigma \odot \tau &= (\sigma\lor^\circ \tau),\\
@@
 \subsection{Sampling extremely large configuration space}
+\begin{theorem}
+    Let $G = (V, E)$ be a graph, its independent sets with size $>\alpha(G)-k$ of can be unbiasedly sampled in time $O(|V|2^{{\rm tw}(G)}) + O(|V|M)$, where $M$ is the number of samples.
+\end{theorem}
+
 When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
@@
 \begin{split}
-    s \oplus t &= (\texttt{SUM}, /, s, t)\\
+    s \OPLUS t &= (\texttt{SUM}, /, s, t)\\
     s \odot t &= (\texttt{PROD}, /, s, t)\\
@@
     \def\yb{-0.8};
-    \node[] at (\dx, 0) (P1) {$\oplus$};
-    \node[] at (\dx+\a, \ya) (P2) {$\oplus$};
+    \node[] at (\dx, 0) (P1) {$\OPLUS$};
+    \node[] at (\dx+\a, \ya) (P2) {$\OPLUS$};
     \node[] at (\dx-\a, \ya) (M1) {$\odot$};
@@
 \section{Weighted graphs}\label{sec:weighted}
+\begin{theorem}
+    Let $G = (V, E, W)$ be a weighted graph, its $k$ largest independent sets can be computed in time $O(k|V|2^{{\rm tw}(G)})$.
+\end{theorem}
+
 All the solution space properties and the corresponding algebra on unweighted graphs still hold for integer-weighted graphs, while for general weighted graphs, the independence polynomial is not well defined anymore.
@@
 \begin{split}
-    s \oplus t &= \texttt{largest}(s \cup t, k)\\
+    s \OPLUS t &= \texttt{largest}(s \cup t, k)\\
     s \odot t &= \texttt{largest}(\{a+b | a \in s, b\in t\}, k)\\
@@
 To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
-Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
+Since the $\OPLUS$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
 
@@
 The union of all the subsets covers the set $U$.
-For each set $s \in S$, we associate it with weight $w_s$ to it.
+For each set $s \in S$, we associate it with an possitive integer weight $w_s$.
 To get the generic tensor network representation, we first map a set $s\in S$ to a Boolean degree of freedom $l_s\in\{0, 1\}$.
@@
 \end{equation}
-where $x_s$ is a variable associated with $s$.
+where $x_s$ is a generic typed variable associated with $s$ and the positive integer power of which can be define by the repeated multiplication.
 For each unique element $a \in U$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(a) = \{s | s \in S \land a\in s\}$, as
@@
 we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
-Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
+Since $ C_{ik} = \bigOPLUS_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
 \begin{equation}
@@
 \begin{equation}
-    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigoplus_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
+    A_{ij} \leq \min_{k}(C_{ik} \odot B_{jk}^{\circ -1}) = \left(\max_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left(\bigOPLUS_{k} \left(C_{ik}^{\circ -1} \odot B_{jk} \right) \right)^{\circ -1} = \left( C^{\circ-1} B^{\mathsf{T}} \right)^{\circ -1}_{ij}.
 \end{equation}
@@
 \begin{split}
-    x ~\oplus~ y &= x+y\pmod p,\\
+    x ~\OPLUS~ y &= x+y\pmod p,\\
     x ~\odot~ y &= xy\pmod p,\\

### 2022-08-25 replys/reply.tex
ave

@@
 \newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
+\newcommand{\referee}[1]{\item {\color{or}{#1}}}
 
@@
 Thank you for your handling and careful consideration of our manuscript ``Computing solution space properties of combinatorial optimization problems via generic tensor networks'', MS\#M150178, for sending it for in-depth review, and for giving us the opportunity to address the reviewer's comments and to refine our manuscript.
-%We would also like to thank reviewers for their thorough reading of our manuscript and for their constructive suggestions that have helped us improve our manuscript.
-%We thank the referee for their careful readings and constructive questions which
-%helped us deepen understandings on the topic and improve the presentation of the manuscript.
 We are very excited that you also read through the paper and give a possitive feedback.
 
-We have revised the manuscript according to the reviewers' constructive suggestions.
-Below, we provide detailed point-to-point response to all of the reviewers' comments, as well as a summary of the changes we have introduced in the main text, figures, and supplementary materials.
+We have revised the manuscript according to the reviewer's constructive suggestions.
+Below, we provide detailed point-to-point response to all of the reviewer's comments, as well as a summary of the changes we have introduced in the main text, figures, and supplementary materials.
 Thank you again for your consideration!
@@
 The main contribution of the paper is claimed to be "introduction of a unified framework to compute solution space properties of a broad class of combinatorial optimization problems."
-}
 
-{\bf Response:}
-
-\referee{
 Comments:
@@
 {\bf Response:}
+Thank you for the careful reading and constructive comments on notations. We applied the most of the suggested changes accordingly in the main text to make it more readable except the comment 3).
+We can not find a better symbol to replace the existing one, so we emphasised this notation is different from the XOR in computer science when we first introduce it.
 
@@
 {\bf Response:}
+Thanks the Referee for acknologying the effort we put in making the paper.
+The Referee not only points out the problem in writing, but also provide constructive comments to help the paper present better.
+We re-organized the contents in the definition, theorem, proposition style to make the key points more clear to readers in the field of theoretical computational complexity and applied mathematics.
 
@@
 {\bf Response:}
-~\cite{Biamonte2017}
+Thank the Referee for pointing out a work that we did not notice before.
+In the introduction, we cited a review paper from the same author~\cite{Biamonte2017}.
+It is definitely better to cite and compare this earlier work as you suggested as well.
+We also added more discussion about the work you mentioned in the Appendix B.6, where we constructed the tensor network for the satisfiability problem to credit the work you mentioned properly.
 

### 2022-08-27 paper/paper.tex
Updates from Overleaf

--- 2022-06-07 paper/paper.tex
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network~\cite{Cirac2021, Orus2014} is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
+\begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
+    A tensor network is a quadruple of $\mathcal{N} = (\Tensors, \Inputs, \Output, \Sigma)$ where $\Sigma$ is a the alphabet of labels, $\Tensors = (\Tensors_1, \ldots, \Tensors_m)$ is a vector of tensors, $\Inputs$ is a map from tensor to a vector of labels $\Inputs: \Tensors_j \mapsto \mathbf{l}_j$, $(\mathbf{l}_j)_i \in \Sigma, i=1,\ldots, \rm{rank}(\Tensors_j)$.
+    $\Output$ is a vector of labels for specifying the output.
+\end{definition}
+A tensor network is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
 The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
@@
 We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
-Here, a commutative semiring is a field that needs not to have an additive inverse and a multiplicative inverse.
+Compared to a field, a commutative semiring does not need not to have an additive inverse and a multiplicative inverse.
 Giving up these nice properties of fields has significant implications for tensor computation: tensor network compression algorithms might not be applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014} and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
 Here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
-To define a commutative semiring with the addition operation $\oplus$ and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
+To define a commutative semiring with the addition operation $\oplus$\footnote{The $\oplus$ operator in the main text means the generic addition, which different from the logical \texttt{XOR} in computer science} and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
 \begin{align*}
@@
 \section{Independence polynomial}\label{sec:indpoly}
-Let $x_i = x$ and $w_i = 1$, \Cref{eq:idp} corresponds to the independence polynomial~\cite{Harvey2018,Ferrin2014}:
+
+\begin{theorem}
+    The independence polynomial~\cite{Harvey2018,Ferrin2014} of a graph $G = (V, E)$ can be computed in time $O(|V|^22^{{\rm tw}(G)})$.
+\end{theorem}
+\begin{proof}
+    By contracting 
+\end{proof}
+Let $x_i = x$ and $w_i = 1$, \Cref{eq:idp} corresponds to the independence polynomial:
 \begin{equation}\label{eq:idpdef}
@@
 One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e.\ a conjunction of clauses (or disjunctions of Boolean literals).
-To reduce the problem of solving a CNF to a tensor network contraction, we first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
+The standard tensor network can be used to study the counting version of the satisfiability problem~\cite{Biamonte2015}, while in the following, we will show a generic reduction from the problem of solving a CNF to a tensor network contraction for solving more solution space properties.
+We first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
 $s_a = 0$ stands for variable $a$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.

### 2022-08-27 replys/reply.tex
Updates from Overleaf

@@
 Thank you for the careful reading and constructive comments on notations. We applied the most of the suggested changes accordingly in the main text to make it more readable except the comment 3).
-We can not find a better symbol to replace the existing one, so we emphasised this notation is different from the XOR in computer science when we first introduce it.
+We can not find a better symbol than $\oplus$ to represent the generic plus, so we emphasised this notation is different from the XOR in computer science when we first introduce it.
 
@@
 The Referee not only points out the problem in writing, but also provide constructive comments to help the paper present better.
-We re-organized the contents in the definition, theorem, proposition style to make the key points more clear to readers in the field of theoretical computational complexity and applied mathematics.
-
+We re-organized the contents in the definition, theorem, proposition style to make the key points more clear to readers.
 \referee{

### 2022-08-29 paper/paper.tex
Updates from Overleaf

@@
 \section{Tensor networks}\label{sec:tn}
+A tensor network is composed of a collection of tensors $\mathcal{T}$, an indicator of which tensor is the output, and a map $\lambda$ from tensor to labels associated with tensor dimensions.
 \begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
-    A tensor network is a quadruple of $\mathcal{N} = (\Tensors, \Inputs, \Output, \Sigma)$ where $\Sigma$ is a the alphabet of labels, $\Tensors = (\Tensors_1, \ldots, \Tensors_m)$ is a vector of tensors, $\Inputs$ is a map from tensor to a vector of labels $\Inputs: \Tensors_j \mapsto \mathbf{l}_j$, $(\mathbf{l}_j)_i \in \Sigma, i=1,\ldots, \rm{rank}(\Tensors_j)$.
-    $\Output$ is a vector of labels for specifying the output.
+    A tensor network is a quadruple of $\mathcal{N} = (\Tensors, \Sigma, O \in \Tensors, \Inputs : \mathcal{T} \rightarrow \Sigma^k)$.
+$\Tensors$ is a set of tensors and $O$ is the output tensor.
+$\Sigma$ is a the alphabet of labels.
+$\Inputs$ is a map from a tensor to a vector of labels with the vector length the same as the tensor rank.
 \end{definition}
-A tensor network is composed of a collection of tensors, a collection of labels associated with tensor dimensions, and an indicator of which tensor is the output.
 The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
-For example, the matrix multiplication is a special tensor network that can be represented as $C_{ik} = A_{ij}B_{jk}$, where $A, B$ and $C$ are matrices (two-dimensional tensors), $ik,ij$ and $ik$ are labels associated with them, and ``$=$'' is the indicator of $C$ being the output, while its contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$.
+For example, the matrix multiplication is a special tensor network
+\begin{equation}
+\mathcal{N}_{\rm matmul} = (\{A, B, C\}, C, T \mapsto \begin{cases} (i,j), T = A\\(j, k), T=B\\ (i, k), T=C\end{cases}, \{i,j,k\}),
+\end{equation}
+where $A, B$ and $C$ are matrices (two-dimensional tensors), among which $C$ is the output tensor, $(i,k),(i,j)$ and $(i,k)$ are labels associated with them.
+The contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$, where the subscripts are for tensor indexing, and the tensor dimensions with a same label must have the same size.
 %can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
@@
 \begin{example}
-$C_{ijk} = A_{jkm} B_{mil} V_{jm}$ is a tensor network that can be evaluated as $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
+\blue{maybe remove this example?}
+\begin{equation}
+\begin{split}
+    \mathcal{T} &= \{A, B, V, C\},\\
+    \Sigma &= \{i,j,k,l,m\},\\
+    O &= C,\\
+    \lambda &= T \mapsto \begin{cases}
+    (j, k, m), &T = A\\
+    (m, i, l), &T = B \\
+    (j, m), &T = V \\
+    (i, j, k), &T= C
+    \end{cases}
+    \end{split}
+\end{equation}
+is a tensor network that can be evaluated as $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
 Its hypergraph representation is shown below, where we use different colors to represent different hyperedges.
@@
 To reduce the independent set problem on $G$ to a tensor network contraction, we first map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in $I$.
-For each label $s_v$, we define a parameterized rank-one tensor indexed by it as
-\begin{equation}
-    W(x_v^{w_v})_{s_v} = \left(\begin{matrix}
+For each label $s_v$, we define a parameterized rank-one tensor associated with it as
+\begin{equation}
+    W^{(v)} = \left(\begin{matrix}
         1 \\
         x_v^{w_v}
-    \end{matrix}\right)_{s_v},\label{eq:vertextensor}
+    \end{matrix}\right),\label{eq:vertextensor}
 \end{equation}
 where $x_v$ is a variable associated with $v$.
-Tensor elements can be indexed by subscripts, e.g.\ $W(x_v^{w_v})_0=1$ is the first element associated with $s_v=0$ and $W(x_v^{w_v})_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
+Tensor elements can be indexed by $s_v$, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
 Similarly, for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
@@
     \qquad \quad 
-       B = \left(\begin{matrix}
+       B^{(u, v)} = \left(\begin{matrix}
         1  & 1\\
@@
 which encodes the independent set constraint since $B_{11} = 0$, meaning the two vertices cannot be both in the independent set. 
-
-The corresponding tensor network contraction can be defined as
+The corresponding tensor network $\mathcal{N}_{\rm IS}(G)$ is
+\begin{equation}\label{eq:mistensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\}\\
+    \Sigma &= \{s_v | v \in V\}\\
+    O &= P\\
+    \lambda &= T \mapsto \begin{cases}
+                    (s_v), &T = W^{(v)}\\
+                    (s_u, s_v), &T = B^{(u, v)}\\
+                    (), & T = P
+                    \end{cases}
+    \end{split}
+\end{equation}
+where we use the superscripts to denote which vertex or edge a tensor is associated to.
+$P$ is the output tensor of rank $0$, i.e. a scalar.
+The contraction of this tensor network is
 \begin{equation}\label{eq:idp}
-    P(G, \{x_1^{w_1}, x_{2}^{w_2}, \ldots,x_{|V|}^{w_{|V|}}\}) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W(x_v^{w_v})_{s_v} \prod\limits_{(u,v) \in E} B_{s_u s_v},
+    P(G) = \sum\limits_{s_1, s_2, \ldots, s_{|V|} = 0}^{1} \prod\limits_{v\in V} W^{(v)}_{s_v} \prod\limits_{(u,v) \in E} B^{(u,v)}_{s_u s_v},
 \end{equation}
@@
 % It is easy to see that an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
-A vertex tensor element $W(x_v^{w_v})_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
+A vertex tensor element $W^{(v)}_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
 
@@
     \foreach \x/\y/\e in {1.25/0/ab}
-        \node[color=black,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize \color{white}{B}};
+        \node[color=black,fill=black,dot=2.5*\r] at (\x+\dx,\y) (\e) {\scriptsize \color{white}{$B^{(a, b)}$}};
     \foreach \x/\y/\v in {0.3/0/a, 2.2/0/b}
@@
         \node[dot=\wr, color=black] at (\x+\dx,\y) (w\v) {};
-        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W(x_\v^{w_\v})$}};
+        \node at (\x+\dx,\y+0.5) () {\scriptsize \color{black}{$W^{(v)}$}};
     }
@@
     \begin{split}
-    P({\rm K2},\{x_a^{w_a}, x_b^{w_b}\}) &=
+    P({\rm K2}) &=
     \left(\begin{matrix} 1 & x_a^{w_a} \end{matrix}\right)
@@
 A better approach to evaluate a tensor network is: to find a good pair-wise tensor contraction order as a binary tree and then contract two tensors at a time by this order.
-Let us denote the line graph of the hypergraph representation of a tensor network as $G'$.
-A contraction order of this tensor network corresponds to a tree decomposition of $G'$ and the largest intermediate tensor has a rank equal to the width of this tree decomposition~\cite{Markov2008}.
-Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $G'$ with the smallest width (or the treewidth ${\rm tw}(G')$).
-In the independent set problem, the treewidth of $G'$ is the same as the treewidth of the graph this tensor network is mapped from. 
+\begin{theorem}\label{thm:complexreal}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    the optimal time complexity for contracting the tensor network in \Cref{eq:mistensornetwork} for the independent set problem on graph $G = (V,E)$ is $O(|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+Let us denote the line graph, a graph obtained by mapping an edge in the original graph to a vertex and connect two vertices if and only if their associated edges in the original original graph share a common vertex, of the hypergraph representation of a tensor network $\mathcal{N}$ as $L(\mathcal{N})$.
+A contraction order of $\mathcal{N}$ corresponds to a tree decomposition of $L(\mathcal{N})$ and the largest intermediate tensor has a rank equal to the width of its tree decomposition~\cite{Markov2008}.
+Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $L(\mathcal{N})$ with the smallest width (or the treewidth ${\rm tw}(L(\mathcal{N})$).
+The contraction complexity is $O(|\mathcal{N}|)2^{O({\rm tw}(L(\mathcal{N})))}$, where $|\mathcal{N}|$ is the number of tensors in $\mathcal{N}$.
+For the independent set problem on graph $G = (V, E)$, the line graph of the hypergraph representation of the tensor network in \Cref{eq:mistensornetwork} is the same as the graph $G$ up to some isolated vertices, hence the contraction complexity of this tensor network with an optimal contraction order is $O(|E|)2^{O({\rm tw}(G))}$.
+\end{proof}
+
 In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is a well-known NP-hard problem.
@@
 \begin{example}\label{eg:tensorcontraction}
+\blue{maybe remove this example too?}
 In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
@@
     \def\r{0.25cm}
-    \foreach \x/\y/\e in {0.75/0/ac, 0/0.75/ab, 1.5/0.75/cd, 0.75/1.5/bd, 0.75/0.75/bc, 2/2/de}
-        \node[color=white,fill=black,dot=2*\r] at (\x+\dx,\y) (\e) {\scriptsize B};
+    \foreach \x/\y/\u/\v in {0.75/0/a/c, 0/0.75/a/b, 1.5/0.75/c/d, 0.75/1.5/b/d, 0.75/0.75/b/c, 2/2/d/e}
+        \node[color=white,fill=black,dot=2.5*\r] at (\x+\dx,\y) (\u\v) {\scriptsize $B^{(\u,\v)}$};
     \foreach \x/\y/\v in {0/0/a, 0/1.5/b, 1.5/0/c, 1.5/1.5/d, 2.5/2.5/e}
@@
     \foreach \x/\y/\v in {-0.5/-0.5/a, -0.5/2.0/b, 2.0/-0.5/c, 2.0/1.0/d, 3.0/2.0/e}
-        \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W(x_\v^{w_\v})$};
+        \node[color=black] at (\x+\dx+0.6,\y) {\scriptsize $W^{(\v)}$};
     \draw [cyan,thick] (a) -- (aa);
@@
 
-\begin{theorem}
-    The independence polynomial~\cite{Harvey2018,Ferrin2014} of a graph $G = (V, E)$ can be computed in time $O(|V|^22^{{\rm tw}(G)})$.
-\end{theorem}
-\begin{proof}
-    By contracting 
-\end{proof}
 Let $x_i = x$ and $w_i = 1$, \Cref{eq:idp} corresponds to the independence polynomial:
@@
 where $\oplus$ and $\odot$ are the standard polynomial addition and multiplication operations.
-The multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}, where $k=\max(k_a, k_b)$.
+
+\begin{theorem}\label{thm:complexpoly}
+    The independence polynomial~\cite{Harvey2018,Ferrin2014} of a graph $G = (V, E)$ can be computed in time $O(|V|\log(|V|)|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+By doing the following replacement of tensor elements from the standard number type to the polynomial number type
+\begin{equation}
+    \begin{cases}
+    1 \rightarrow \mymathbb{1}\\
+    0 \rightarrow \mymathbb{0}\\
+    x_v^{w_v} \rightarrow (0, 1)
+    \end{cases}
+\end{equation}
 The tensors $W$ and $B$, which are introduced in the previous section (\Cref{sec:tnmap}), can thus be written as 
 \begin{equation}
-    W^{\rm PN} = \left(\begin{matrix}
+    \left(W^{\rm PN}\right)^{(v)} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm PN} = \left(\begin{matrix}
+        \left(B^{\rm PN}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 By contracting the tensor network with this polynomial type, we have the exact representation of the independence polynomial.
+In \Cref{eq:polynomial}, the addition can be computed in time $O(k)$, where $k=\max(k_a, k_b)$, and the multiplication can be evaluated in time $O(k\log(k))$ using the convolution theorem~\cite{Schonhage1971}.
+Since $k$ is upper bounded by the maximum independent set size $\alpha(G) \leq |V|$, the time complexity of element-wise addition and multiplication operation is upper bounded by $|V|\log(|V|)$.
+Combining with \Cref{thm:complexreal}, the a overall time complexity is $O(|V|\log(|V|)|E|)2^{O({\rm tw}(G))}$.
+\end{proof}
+
 In practice, using the polynomial type suffers a space overhead proportional to $\alpha(G)$ because each polynomial requires a vector of such size to store the coefficients. 
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
-\begin{theorem}
-    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $O(|V|2^{{\rm tw}(G)})$.
-\end{theorem}
-\begin{theorem}
-    The number of $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(k|V|2^{{\rm tw}(G)})$.
-\end{theorem}
 %The method we use to count the MISs is based on the following observations:
@@
 Algebra \Cref{eq:tropical} and \Cref{eq:countingtropical} are the same as those used in Liu et al.~\cite{Liu2021} to compute the spin glass ground state energy and its degeneracy.
-For independent set calculations here, the vertex tensor and edge tensor becomes:
-\begin{equation}
-    W^{\rm T}(w_v) = \left(\begin{matrix}
-        w_v \\
-        \infty
+
+\begin{theorem}\label{thm:complextropical}
+    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $O(|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+By replacing the tensor elements from the standard number type to the tropical numbers in \Cref{eq:tropical}, the vertex and edge tensors transforms to
+\begin{equation}\label{eq:tensor-topical}
+    \left(W^{\rm T}\right)^{(v)} = \left(\begin{matrix}
+        1 \\
+        \infty^{w_v}
     \end{matrix}\right),   
     \qquad \qquad
-        B^{\rm T} = \left(\begin{matrix}
+        \left(B^{\rm T}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \end{equation}
-
+The maximum independent set can be obtained by contracting a tensor network with the above vertex tensors and edge tensors.
+Since the element-wise addition and multiplication can be computed in $O(1)$ time, the complexity of contracting this tensor network is $O(|E|)2^{O({\rm tw}(G))}$ by \Cref{thm:complexreal}.
+\end{proof}
 \subsection{Truncated polynomial algebra for counting independent sets of large size}
@@
 
+\begin{lemma}
+    The number of the largest $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+\end{lemma}
+The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.
+
 \section{Enumerating and sampling independent sets}\label{sec:enumeration}
-\begin{theorem}
-    Let $G = (V, E)$ be a graph and $M$ be the number of independent sets with size $>\alpha(G)-k$.
-    The independent sets with size $>\alpha(G)-k$ of $G$ can be computed in time $O(M|V|2^{{\rm tw}(G)})$.
-\end{theorem}
 
@@
 
-To enumerate all independent sets,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
+\begin{theorem}\label{thm:complexset}
+    Let $G = (V, E)$ be a graph and $I$ be its independent sets.
+    $I$ can be computed in time $O(|I||V||E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+To enumerate over $I$,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
 The vertex and edge tensors are thus
 \begin{equation}
-    W^{\rm SN}(\{\boldsymbol{e}_{i}\}) = \left(\begin{matrix}
+    \left(W^{\rm SN}\right)^{(v)} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad \qquad
-        B^{\rm SN} = \left(\begin{matrix}
+        \left(B^{\rm SN}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \end{equation}
+The contraction of this tensor network is a set with its elements being all independent set configurations.
+The time complexity of element-wise addition and multiplication is upper bounded by $|I||V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V||E|)2^{O({\rm tw}(G))}$.
+In practise, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
+This complexity only upper bounds the actually performance of the algorithm.
+\end{proof}
 
@@
 As long as the coefficients in a truncated polynomial are members of a commutative semiring, the polynomial itself is a commutative semiring.
+
 For example, to enumerate only the MISs, we can define a combined element type $s_{k}\infty^k$, where the coefficients follow the algebra in \Cref{eq:set} and the exponents follow the max-plus tropical algebra.
@@
 \end{equation}
-Clearly, the vertex tensor and edge tensor become
-\begin{equation}
-    W^{\rm P1+SN}(\{\boldsymbol{e}_{i}\}\infty^{w_v}) = \left(\begin{matrix}
+
+\begin{theorem}\label{thm:complexmis}
+    Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
+    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V||E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+By replacing the tensor elements in \Cref{sec:tnmap} with the number type defined in \Cref{eq:countingtropicalset}, with variable $x_v^{w_v} = \{\boldsymbol{e}_{v}\}\infty^{w_v}$, the vertex tensor and edge tensor become
+\begin{equation}
+    \left(W^{\rm P1+SN}\right)^{(v)} = \left(\begin{matrix}
         \mymathbb{1} \\
-        \{\boldsymbol{e}_{i}\}\infty^{w_v}
+        \{\boldsymbol{e}_{v}\}\infty^{w_v}
     \end{matrix}\right),   
     \qquad \qquad
-        B^{\rm P1+SN} = \left(\begin{matrix}
+        \left(B^{\rm P1+SN}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 The enumeration of all MIS configurations corresponds to the contraction of this tensor network.
+The time complexity of element-wise addition and multiplication is upper bounded by the number of independent sets $|\mathcal{I}_\alpha|$.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V||E|)2^{O({\rm tw}(G))}$.
+\end{proof}
 However, direct contraction might have significant space overheads for keeping too many intermediate states irrelevant to the final maximum independent sets.
@@
 It will be discussed in \Cref{sec:maximal} since it requires using a different tensor network structure.
+
+\begin{theorem}\label{thm:complexsetk}
+    Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
+    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|E||V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+This can proved by combining the set algebra \Cref{eq:set} with the polynomial number truncated to largest $K$ orders (\Cref{eq:max2poly}).
+The number of bitstring operations in the addition and multiplication of the joint algebra is upper bounded by the elements in the sets $\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|$.
+Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|E||V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)2^{O({\rm tw}(G))}$.
+\end{proof}
 
@@
 
+\begin{theorem}
+    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|E||V|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+The proof is similar to \Cref{thm:complexmis}, except the set algebra is replace by the one in \Cref{eq:singleconfig}, and the time complexity of element-wise addition and multiplication no longer depends on $|\mathcal{I}_\alpha|$.
+The linear dependency of $|V|$ in the time complexity can be remove using the back propagation technique, at the cost of additional space.
+\begin{theorem}
+    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+    Let $\alpha(G) = \max\limits_{s \in I} \sum_{v} s_v$ be the maximum independent set size. The optimal configuration can be obtained by differentiating over vertex tensors as
+    \begin{equation}
+    \begin{cases}
+        1, &\frac{\partial \alpha(G)}{\partial s_v} = 1\\
+        0, &\frac{\partial \alpha(G)}{\partial s_v} = 0
+    \end{cases}.
+    \end{equation}
+    It can be numerically computed by differentiating over the process of the tropical tensor network contraction, where the backward rules can be found in \Cref{sec:bounding}.
+The time overhead of computing single optimal solution is constant comparing to only computing the contraction.
+Thus the computing time complexity should be the same as in \Cref{thm:complextropical}.
+\end{proof}
+
 \subsection{Sampling extremely large configuration space}
-\begin{theorem}
-    Let $G = (V, E)$ be a graph, its independent sets with size $>\alpha(G)-k$ of can be unbiasedly sampled in time $O(|V|2^{{\rm tw}(G)}) + O(|V|M)$, where $M$ is the number of samples.
-\end{theorem}
-
 When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
@@
 \end{equation}
-The vertex tensor and edge tensor become
-\begin{equation}
-    W^{\rm EXPR}((\texttt{LEAF},\boldsymbol{e}_i,/,/)) = \left(\begin{matrix}
+
+This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Cref{eq:set}) forms rather than their storage.
+Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with the largest several sizes.
+
+\begin{theorem}\label{thm:complexexpr}
+        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $O(|E|)2^{O({\rm tw}(G))} + O(|V||I|)$.
+\end{theorem}
+\begin{proof}
+By replacing the tensor elements with the number type in \Cref{eq:expr} with $x_v^{w_v}$ mapped to $(\texttt{LEAF},\boldsymbol{e}_i,/,/)$, the vertex tensor and edge tensor become
+\begin{equation}
+    \left(W^{\rm EXPR}\right)^{(v)} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{\rm EXPR} = \left(\begin{matrix}
+        \left(B^{\rm EXPR}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \end{equation}
-
-This algebra is a commutative semiring because we define the equivalence of two sum-product expression trees by comparing their expanded (using \Cref{eq:set}) forms rather than their storage.
-Except using the sum-product expression tree directly as tensor elements, one can also let it be the coefficients of a (truncated) polynomial to compute such trees for independent sets with the largest several sizes.
+The contraction of such tensor network corresponds to a sum-product expression tree of the set of independent sets, which costs time $O(|E|)2^{O({\rm tw}(G))}$ by \Cref{thm:complexreal} since the computing time of expression tree addition and multiplication are $O(1)$.
+The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
+\end{proof}
+
+Similarly, we have the following lemma by combining the sum-product expression tree algebra with the truncated polynomial.
+
+\begin{lemma}\label{thm:complexexpr}
+        Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$.
+The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))} + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
+\end{lemma}
+
 Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
 they can draw unbiased samples from it by direct sampling.
+\begin{theorem}
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(|E|)2^{O({\rm tw}(G))} + O(|V|^2 M)$, where $M$ is the number of samples.
+\end{theorem}
+\begin{proof}
+Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $O(|E|)2^{O({\rm tw}(G))}$.
+Then we show to generate a sample, the cost is $O(|V|^2)$.
 The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
@@
 
+Since the depth of the expression tree is $|V|$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
+\end{proof}
+
+Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following lemma.
+\begin{lemma}
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K|E|)2^{O({\rm tw}(G))} + O(|V|^2 M)$, where $M$ is the number of samples.
+\end{lemma}
+
 \section{Weighted graphs}\label{sec:weighted}
-\begin{theorem}
-    Let $G = (V, E, W)$ be a weighted graph, its $k$ largest independent sets can be computed in time $O(k|V|2^{{\rm tw}(G)})$.
-\end{theorem}
 
@@
 where $\texttt{largest}(s, k)$ means truncating the set $s$ by only keeping its $k$ largest values.
-The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$.
-An efficient algorithm for computing the maximum sum combination problem can be found in \Cref{sec:maxsum}.
-The vertex tensor and edge tensor become
-\begin{equation}
-    W^{{\rm T}k}(-\infty^{\otimes k-1} \otimes w_v) = \left(\begin{matrix}
+
+\begin{theorem}
+    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+\begin{proof}
+$k$ largest independent sets can be computed by contracting a tensor network with extended tropical numbers. The vertex tensor and edge tensor are
+\begin{equation}
+    \left(W^{{\rm T}k}\right)^{(v)} = \left(\begin{matrix}
         \mymathbb{1} \\
@@
     \qquad
-        B^{{\rm T}k} = \left(\begin{matrix}
+        \left(B^{{\rm T}k}\right)^{(u, v)} = \left(\begin{matrix}
         \mymathbb{1}  & \mymathbb{1} \\
@@
 \end{equation}
-where we have used the equation $(-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
+where we have used $x_v^{w_v} = (-\infty^{\otimes k-1} \otimes 1)^{w_v} = -\infty^{\otimes k-1} \otimes w_v$.
+
+The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$ using the algorithm in \Cref{sec:maxsum}.
+Hence the overall time complexity of contracting the tensor network is $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+\end{proof}
+
+\begin{lemma}
+    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|E||V|)2^{O({\rm tw}(G))}$.
+\end{lemma}
 To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
@@
 where $\mathcal{I}(G)$ is the set of independent sets of graph $G$, $\alpha(G)$ is the absolute value of the minimum energy (maximum independent set size), $a(k)$ is the number of spin configurations with energy $-k$ (independent sets of size $k$).
-The partition function can be expressed as a tensor network by placing a vertex tensor on each spin $i$
-\begin{equation}
-    W(e^{\beta w_i}) = \left(\begin{matrix}
+The partition function can be expressed as a tensor network by placing a vertex tensor on each spin $i \in V$
+\begin{equation}
+    W^{(i)} = \left(\begin{matrix}
         1 \\
@@
 \end{equation}
-and an edge tensor on each bond
-\begin{equation}
-       B = \left(\begin{matrix}
+and an edge tensor on each bond $(u, v) \in E$
+\begin{equation}
+       B^{(u, v)} = \left(\begin{matrix}
         1  & 1\\
@@
 A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
-To characterize the maximal independence restriction, we defined a tensor on each $\{v\}\cup N(v)$ as
+To characterize the maximal independence restriction, we defined a tensor for each $v \in V$ and its neighbor $N(v)$ as
 \begin{equation}\label{eq:maximal}
-    T(x_v^{w_v})_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-        s_vx_v^{w_v} & s_1=s_2=\ldots=s_{|N(v)|}=0,\\
-        1-s_v& \text{otherwise}.\\
+    T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
+        s_vx_v^{w_v} & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
+        1-s_v& \text{otherwise}.
     \end{cases}
 \end{equation}
-It means if none of the neighbours of $v$ are in $I_{m}$ ($ s_1=s_2=\ldots=s_{|N(v)|}=0$), then $v$ must be in $I_{m}$ and contribute a factor $x_{v}$, otherwise, if any of the neighbourhood vertices is in $I_{m}$, then $v$ cannot be in $I_{m}$.
-For a vertex $v$ that has a degree 2, the tensor has the following form
-\begin{equation}
-    T(x_v^{w_v})=\left(\begin{matrix}
+where $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
+If $s_v = 1$, then none of its neighbours can be a member of $I_{m}$ by the independence constraint, contributing a factor $x_v^{w_v}$.
+If $s_v = 0$, then at least on of its neighbors must be in $I_{m}$ by the maximal constraint, contributing a unit factor.
+For a degree 2 vertex $v$, the tensor has the following form
+\begin{equation}
+    T^{(v)}=\left(\begin{matrix}
     \left(\begin{matrix}
@@
     \end{matrix}\right).
+\end{equation}
+The corresponding tensor network $\mathcal{N}_{\rm mIS}(G)$ can be defined as
+\begin{equation}\label{eq:maxistensornetwork}
+\begin{split}
+    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
+                    (), & S = P
+                    \end{cases}.
+\end{split}
 \end{equation}
@@
 We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
-To characterize the matching constraint, we define a tensor for each $N(v)=\{n_1, n_2,\ldots, n_{d(v)}\}$ as
-\begin{equation}
-    W_{\langle v, n_1\rangle, \langle v, n_2 \rangle, \ldots, \langle v, n_{d(v)}\rangle} = \begin{cases}
-        1, & \sum_{i=1}^{d(v)} \langle v, n_i \rangle \leq 1,\\
+To characterize the matching constraint, we define a tensor for each $N(v)$ as
+\begin{equation}
+    W^{(v)}_{\langle v, N(v, 1)\rangle, \langle v, N(v, 2) \rangle, \ldots, \langle v, N(v,d(v))\rangle} = \begin{cases}
+        1, & \sum_{i=1}^{d(v)} \langle v, N(v, i) \rangle \leq 1,\\
         0, & \text{otherwise},
@@
 \begin{equation}
-    B(x^{w_{\langle u,v \rangle}}_{\langle u,v\rangle})_{\langle u, v\rangle} = \begin{cases}
+    B^{(u, v)}_{\langle u, v\rangle} = \begin{cases}
     1, & \langle u, v \rangle = 0 \\
@@
 \end{equation}
-where a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
-$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set,
-and an edge tensor carries the weights.
+where $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$, a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
+$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set, and an edge tensor carries the weights. The tensor network can be defined as
+\begin{equation}\label{eq:matchtensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
+    \Sigma &= \{\langle u,v\rangle | (u, v) \in E\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (\langle v, N(v, 1)\rangle, \langle v, N(v,2) \rangle, \ldots, \langle v, N(v, d(v))\rangle), & S = W^{(v)}\\
+                    (\langle u,v\rangle), & S = B^{(u, v)}\\
+                    (), & S = P
+                    \end{cases}.
+\end{split}
+\end{equation}
+
 Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction corresponds to the matching polynomial
@@
 \begin{equation}
-    W = \left(\begin{matrix}
+    W^{(v)} = \left(\begin{matrix}
         r_v\\
@@
 \begin{equation}
-    B(x^{w_{uv}}) = \left(\begin{matrix}
+    B^{(u, v)} = \left(\begin{matrix}
         0 & x^{w_{uv}} & x^{w_{uv}}\\
@@
 \end{equation}
-where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations. $B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
+where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations.
+$B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
+The tensor network can be defined as
 %The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
+
+\begin{equation}\label{eq:colortensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
+    \Sigma &= \{c_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (c_v), & S = W^{(v)}\\
+                    (c_u, c_v), & S = B^{(u, v)}\\
+                    (), & S = P
+                    \end{cases}
+\end{split}
+\end{equation}
+
 Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$; we then have a graph polynomial,
@@
 \begin{equation}
-    B(x^{w_{uv}}_u, x^{w_{uv}}_v) = \left(\begin{matrix}
+    B^{(u, v)} = \left(\begin{matrix}
         1 & x_{v}^{w_{uv}}\\
@@
 \end{equation}
-where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem.
+where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem. The tensor network can be defined as
+
+\begin{equation}\label{eq:cuttensornetwork}
+\begin{split}
+    \mathcal{T} &= \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (s_u, s_v), & S = B^{(u, v)}\\
+                    (), & S = P
+                    \end{cases}
+\end{split}
+\end{equation}
+
 Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$; we have a graph polynomial similar to the previous ones,
@@
 \begin{equation}
-T(x^{w_v}_v)_{s_1,s_2,\ldots,s_{|N(v)|},s_v} = \begin{cases}
-    0 & s_1=s_2=\ldots=s_{|N(v)|}=s_v=0,\\
+T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
+    0 & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0,\\
     1 & s_v=0,\\
@@
 \end{equation}
-where $w_v$ is the weight associated with the vertex $v$.
-This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_1=s_2=\ldots=s_{|N(v)|}=s_v=0$) cannot be a dominating set.
-Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output.
+where $w_v$ is the weight associated with the vertex $v$, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
+This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0$) cannot be a dominating set.
+Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output. The tensor network can be defined as
+
+\begin{equation}\label{eq:domtensornetwork}
+\begin{split}
+    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
+                    (), & S = P
+                    \end{cases}
+\end{split}
+\end{equation}
 The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009}
@@
 One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e.\ a conjunction of clauses (or disjunctions of Boolean literals).
+Given the alphabet of Boolean variables $V$, a CNF can be formally defined as
+\begin{equation}
+    {\rm CNF} = \bigwedge_{k=1}^{M} \bigvee_{i=1}^{|C^{(k)}|} C^{(k)}_i
+\end{equation}
+where $M$ is the number of clauses, $C^{(k)}$ is the $k$th clause and $C^{(k)}_i \in V \cup \{\neg v | v \in V\}$ is the $i$th literal in it.
 The standard tensor network can be used to study the counting version of the satisfiability problem~\cite{Biamonte2015}, while in the following, we will show a generic reduction from the problem of solving a CNF to a tensor network contraction for solving more solution space properties.
@@
 \begin{equation}
-C_{k} = \left(\begin{matrix}
+T^{(k)} = \left(\begin{matrix}
 \left(\begin{matrix}
-x^{w_k} & x_{b}^{w_k} \\
-x_a^{w_k} & x_{ab}^{w_k}
+x^{w_k} & x^{w_k} \\
+x^{w_k} & x^{w_k}
 \end{matrix}\right) \\
 \left(\begin{matrix}
-x_{c}^{w_k} & x_{bc}^{w_k} \\
-1 & x_{abc}^{w_k}
+x^{w_k} & x^{w_k} \\
+1 & x^{w_k}
 \end{matrix}\right)
@@
 \end{equation}
-where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied.
-Let $x^{w_k}_{\ldots} = x$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
-
+where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied. The tensor network representation is
+
+\begin{equation}\label{eq:domtensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v \in V\} \cup \{T^{(k)} | k=1,\ldots,M\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (s_{l(k,1)}, s_{l(k, 2)}, s_{l(k,3))}), & S = C^{(k)}\\
+                    (), & S = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where a tensor defined on literal $v \in V$ is
+\begin{equation}
+    W^{(v)} = \left(\begin{matrix}
+    1\\
+    1_v
+    \end{matrix}\right)
+\end{equation}
+and a tensor defined on caluse $C^{(k)}$ is
+\begin{equation}
+T^{(k)}_{s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))}} = \begin{cases}
+    x^{}, &C^{k} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
+    1, &{\rm otherwise}
+\end{cases},
+\end{equation}
+where $N(k, i)$ is the $i$th boolean variables in $C^{(k)}$ and $d(k)$ is the number of boolean variables in it.
+Let $x^{w_k} = x$ and $1_v = 1$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
+\blue{polish}
 \subsection{Set packing}
-Suppose one has a finite set $S$ and a list of subsets of $S$. Then, the set packing problem asks if some $k$ subsets in the list are pairwise disjoint.
+Suppose one has a finite set $S$ and a list of subsets of $S$, denoted as $\mathcal{V}$. Then, the set packing problem asks if some $k$ subsets in $\mathcal{V}$ are pairwise disjoint.
 It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Cref{eq:vertextensor}, while the edge tensor generalizes \Cref{eq:edgetensor} to higher dimensions
-\begin{equation}
-    B_{s_u,s_v,\ldots, s_w} = \begin{cases}
-        1, & s_u+s_v+\ldots+s_w\leq 1,\\
+The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Cref{eq:vertextensor}, while the edge tensor generalizes \Cref{eq:edgetensor} to higher dimensions such that for each $\sigma \in S$, we have the constraints on set $N(\sigma) = \{s| s\in \mathcal{V} \wedge \sigma \in s\}$
+\begin{equation}
+    B^{(\sigma)}_{N(\sigma, 1), N(\sigma, 2),\ldots, N(\sigma, d(\sigma))} = \begin{cases}
+        1, & s_{N(\sigma, 1)}+ s_{N(\sigma, 2)} + \ldots + s_{N(\sigma, d(\sigma))}\leq 1,\\
         0, & \text{otherwise}.
@@
 \end{equation}
+where $N(\sigma, k)$ is the $k$th element in $N(\sigma)$ and $d(\sigma) = |N(\sigma)|$ is the number of elements in $N(\sigma)$. The tensor network representation for the set packing problem is
+
+\begin{equation}\label{eq:packtensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(\sigma)} | \sigma \in \mathcal{S}\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= T \mapsto \begin{cases}
+                    (s_v), & T = W^{(v)}\\
+                    (s_{N(\sigma, 1)}, \ldots, s_{N(\sigma, d(\sigma))}), & T = B^{(\sigma)}\\
+                    (), & T = P
+                    \end{cases}
+\end{split}
+\end{equation}
 
@@
 Given a collection of elements, the set covering problem aims to find the minimum number of sets that incorporate (cover) all of these elements.
-In the set covering problem, two sets are given: a set $U$ of elements and a set $S$ of subsets of the set $U$.
-The union of all the subsets covers the set $U$.
-For each set $s \in S$, we associate it with an possitive integer weight $w_s$.
-To get the generic tensor network representation, we first map a set $s\in S$ to a Boolean degree of freedom $l_s\in\{0, 1\}$.
-For each set $s$, we define a parameterized rank-one tensor indexed by $l_s$ as
-\begin{equation}
-W(x_s^{w_s}) = \left(\begin{matrix}
+In the set covering problem, two sets are given: a set $\mathcal{V}$ of elements and a set $S$ of subsets of $\mathcal{V}$.
+The union of all the subsets covers $\mathcal{V}$.
+Each set $s \in S$ is associated with an positive integer weight $w_s$.
+To get the generic tensor network representation, we first map a set $\sigma \in S$ to a Boolean degree of freedom $s_\sigma\in\{0, 1\}$.
+For each $s_\sigma$, we define a parameterized rank-one tensor indexed by it as
+\begin{equation}
+W^{(\sigma)} = \left(\begin{matrix}
     1 \\
-    x_s^{w_s}
+    x_\sigma^{w_\sigma}
     \end{matrix}\right)
 \end{equation}
-where $x_s$ is a generic typed variable associated with $s$ and the positive integer power of which can be define by the repeated multiplication.
-For each unique element $a \in U$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(a) = \{s | s \in S \land a\in s\}$, as
-\begin{equation}
-B_{l_1,l_2,\ldots,l_{|N(a)|}} = \begin{cases}
-    0 & l_1=l_2=\ldots=l_{|N(a)|}=0,\\
-    1 & \text{otherwise}.
+where $x_\sigma$ is a generic typed variable associated with $\sigma$ and the positive integer power of which can be define by the repeated multiplication.
+For each element $v \in \mathcal{V}$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(v) = \{s | s \in S \land v\in s\}$, as
+\begin{equation}
+B^{(v)}_{s_{N(v, 1)}, s_{N(v, 2)}, \ldots, s_{N(v, d(v))}} = \begin{cases}
+    0, & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
+    1, & \text{otherwise}.
 \end{cases}
 \end{equation}
-If a subset of $S$ does not include any sets containing element $a$, then this configuration has zero contribution to the contraction result.
+where $N(v, k)$ is the $k$th element in $N(v)$ and $d(v) = |N(v)|$ is the number of elements in $N(v)$. 
+If a subset of $S$ does not include any sets containing element $v$, then the corresponding entry is zero.
+The tensor network representation for the set packing problem is
+\begin{equation}\label{eq:covertensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(\sigma)} | \sigma \in S\} \cup \{B^{(v)} | v \in \mathcal{V}\} \cup \{P\},\\
+    \Sigma &= \{s_\sigma | \sigma \in \mathcal{S}\},\\
+    O &= P,\\
+    \lambda &= T \mapsto \begin{cases}
+                    (s_\sigma), & T = W^{(\sigma)}\\
+                    (s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(\sigma, d(v))}), & T = B^{(v)}\\
+                    (), & T = P
+                    \end{cases}
+\end{split}
+\end{equation}
 

### 2022-08-29 paper/paper.tex
update

@@
 
+\externaldocument{suppl}
+
 \title{Computing solution space properties of combinatorial optimization problems via generic tensor networks}
-
-\externaldocument{suppl}
 
@@
     A tensor network is a quadruple of $\mathcal{N} = (\Tensors, \Sigma, O \in \Tensors, \Inputs : \mathcal{T} \rightarrow \Sigma^k)$.
-$\Tensors$ is a set of tensors and $O$ is the output tensor.
-$\Sigma$ is a the alphabet of labels.
-$\Inputs$ is a map from a tensor to a vector of labels with the vector length the same as the tensor rank.
+$\Tensors$ is a set of tensors, among which $O$ is the output tensor.
+    $\Sigma$ is an alphabet of labels. $\Inputs$ is a map from a tensor to a vector of labels with the vector length the same as the tensor rank.
 \end{definition}
@@
 \begin{equation}
-\mathcal{N}_{\rm matmul} = (\{A, B, C\}, C, T \mapsto \begin{cases} (i,j), T = A\\(j, k), T=B\\ (i, k), T=C\end{cases}, \{i,j,k\}),
+\mathcal{N}_{\rm matmul} = \left(\{A, B, C\}, \{i,j,k\}, C, T \mapsto \begin{cases} (i,j), T = A\\(j, k), T=B\\ (i, k), T=C\end{cases}\right),
 \end{equation}
@@
     If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    the optimal time complexity for contracting the tensor network in \Cref{eq:mistensornetwork} for the independent set problem on graph $G = (V,E)$ is $O(|E|)2^{O({\rm tw}(G))}$.
+    the tensor network in \Cref{eq:mistensornetwork} for the independent set problem on graph $G = (V,E)$ can be contracted in time $\cc = O(|E|)2^{O({\rm tw}(G))}$.
 \end{theorem}
@@
 \begin{theorem}\label{thm:complexpoly}
-    The independence polynomial~\cite{Harvey2018,Ferrin2014} of a graph $G = (V, E)$ can be computed in time $O(|V|\log(|V|)|E|)2^{O({\rm tw}(G))}$.
+    The independence polynomial~\cite{Harvey2018,Ferrin2014} of a graph $G = (V, E)$ can be computed in time $O(|V|\log(|V|))\cc$.
 \end{theorem}
@@
 Since $k$ is upper bounded by the maximum independent set size $\alpha(G) \leq |V|$, the time complexity of element-wise addition and multiplication operation is upper bounded by $|V|\log(|V|)$.
-Combining with \Cref{thm:complexreal}, the a overall time complexity is $O(|V|\log(|V|)|E|)2^{O({\rm tw}(G))}$.
+Combining with \Cref{thm:complexreal}, the a overall time complexity is $O(|V|\log(|V|))\cc$.
 \end{proof}
@@
 \begin{theorem}\label{thm:complextropical}
-    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $O(|E|)2^{O({\rm tw}(G))}$.
+    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $\cc$.
 \end{theorem}
@@
 The maximum independent set can be obtained by contracting a tensor network with the above vertex tensors and edge tensors.
-Since the element-wise addition and multiplication can be computed in $O(1)$ time, the complexity of contracting this tensor network is $O(|E|)2^{O({\rm tw}(G))}$ by \Cref{thm:complexreal}.
+Since the element-wise addition and multiplication can be computed in $O(1)$ time, the complexity of contracting this tensor network is $\cc$ by \Cref{thm:complexreal}.
 \end{proof}
@@
 \begin{lemma}
-    The number of the largest $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+    The number of the largest $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
 \end{lemma}
@@
     Let $G = (V, E)$ be a graph and $I$ be its independent sets.
-    $I$ can be computed in time $O(|I||V||E|)2^{O({\rm tw}(G))}$.
+    $I$ can be computed in time $O(|I||E|)\cc$.
 \end{theorem}
@@
 The time complexity of element-wise addition and multiplication is upper bounded by $|I||V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration.
-Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V||E|)2^{O({\rm tw}(G))}$.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V|)\cc$.
 In practise, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
@@
     Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
-    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V||E|)2^{O({\rm tw}(G))}$.
+    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V|)\cc$.
 \end{theorem}
@@
 The time complexity of element-wise addition and multiplication is upper bounded by the number of independent sets $|\mathcal{I}_\alpha|$.
-Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V||E|)2^{O({\rm tw}(G))}$.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V|)\cc$.
 \end{proof}
@@
     Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
-    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|E||V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)2^{O({\rm tw}(G))}$.
+    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
 \end{theorem}
@@
 The number of bitstring operations in the addition and multiplication of the joint algebra is upper bounded by the elements in the sets $\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|$.
-Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|E||V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)2^{O({\rm tw}(G))}$.
+Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
 \end{proof}
@@
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|E||V|)2^{O({\rm tw}(G))}$.
+    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
 \end{theorem}
@@
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|E|)2^{O({\rm tw}(G))}$.
+    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $\cc$.
 \end{theorem}
@@
 \begin{theorem}\label{thm:complexexpr}
-        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $O(|E|)2^{O({\rm tw}(G))} + O(|V||I|)$.
+        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $\cc + O(|V||I|)$.
 \end{theorem}
@@
 \end{equation}
-The contraction of such tensor network corresponds to a sum-product expression tree of the set of independent sets, which costs time $O(|E|)2^{O({\rm tw}(G))}$ by \Cref{thm:complexreal} since the computing time of expression tree addition and multiplication are $O(1)$.
+The contraction of such tensor network corresponds to a sum-product expression tree of the set of independent sets, which costs time $\cc$ by \Cref{thm:complexreal} since the computing time of expression tree addition and multiplication are $O(1)$.
 The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
@@
 
-\begin{lemma}\label{thm:complexexpr}
+\begin{lemma}\label{thm:complexexprk}
         Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$.
-The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))} + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
+The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
 \end{lemma}
@@
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(|E|)2^{O({\rm tw}(G))} + O(|V|^2 M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V|^2 M)$, where $M$ is the number of samples.
 \end{theorem}
 \begin{proof}
-Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $O(|E|)2^{O({\rm tw}(G))}$.
+Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $\cc$.
 Then we show to generate a sample, the cost is $O(|V|^2)$.
@@
 \begin{lemma}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K|E|)2^{O({\rm tw}(G))} + O(|V|^2 M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
 \end{lemma}
@@
 \begin{theorem}
-    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K)\cc$.
 \end{theorem}
@@
 The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$ using the algorithm in \Cref{sec:maxsum}.
-Hence the overall time complexity of contracting the tensor network is $O(K\log K|E|)2^{O({\rm tw}(G))}$.
+Hence the overall time complexity of contracting the tensor network is $O(K\log K)\cc$.
 \end{proof}
@@
 \begin{lemma}
-    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|E||V|)2^{O({\rm tw}(G))}$.
+    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
 \end{lemma}
@@
 A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
-To characterize the maximal independence restriction, we defined a tensor for each $v \in V$ and its neighbor $N(v)$ as
+The corresponding tensor network $\mathcal{N}_{\rm mIS}(G)$ can be defined as
+\begin{equation}\label{eq:maxistensornetwork}
+\begin{split}
+    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= S \mapsto \begin{cases}
+                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
+                    (), & S = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where we defined a tensor for each $v \in V$ and its neighborhood $N(v)$ as
 \begin{equation}\label{eq:maximal}
@@
 \end{equation}
-where $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
+Here, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
 If $s_v = 1$, then none of its neighbours can be a member of $I_{m}$ by the independence constraint, contributing a factor $x_v^{w_v}$.
@@
 \end{equation}
-The corresponding tensor network $\mathcal{N}_{\rm mIS}(G)$ can be defined as
-\begin{equation}\label{eq:maxistensornetwork}
-\begin{split}
-    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
-    O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
-                    (), & S = P
-                    \end{cases}.
-\end{split}
-\end{equation}
-
+\begin{theorem}\label{thm:miscomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a maximal independent set problem on graph $G=(V,E)$ defined in \Cref{eq:maxistensornetwork} can be contracted in time $cc(\mathcal{N}_{mIS}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$, where $\Delta$ is the maximum degree of vertices in $G$.
+\end{theorem}
+\begin{proof}
+    The prefactor $|V|$ comes from the number of tensors,
+    while the contraction complexity of pair-wise tensor contraction is closely related to the treewidth of the line graph of its hypergraph representation ${\rm tw}(L(\mathcal{N}_{mIS}(G)))$.
+    In the following, we will show this quantity is upper bounded by $(\Delta+1)$ times the treewidth of $G$.
+    In the line graph $L(\mathcal{N}_{mIS}(G))$, a tensor $T^{(v)}$ corresponds to a clique over $N(v) \cup \{v\}$.
+    In the following, we will show given an optimal tree decomposition of $G$, it is always possible to include all cliques into the bags by increasing the bag size by a factor $(\Delta + 1)$.
+    Let $v \in V$ be a vertex and $N(v)$ be its neighborhood, we first arbitrarily pick an edge $u \in N(v)$,
+    then by the definition of tree decomposition, we can find a bag containing this edge, and lastly we include all $N(v) \cup \{v\}$ into this bag.
+    Hence the maximum tensor rank during contraction is upper bounded by ${\rm tw}(G)\Delta $, proving the theorem.
+\end{proof}
 Let us consider the graph in \Cref{eg:tensorcontraction}. The corresponding tensor network structure for computing the maximal independent polynomial has the following hypergraph representation. \\
@@
 We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
-To characterize the matching constraint, we define a tensor for each $N(v)$ as
-\begin{equation}
-    W^{(v)}_{\langle v, N(v, 1)\rangle, \langle v, N(v, 2) \rangle, \ldots, \langle v, N(v,d(v))\rangle} = \begin{cases}
-        1, & \sum_{i=1}^{d(v)} \langle v, N(v, i) \rangle \leq 1,\\
-        0, & \text{otherwise},
-    \end{cases}
-\end{equation}
-and a tensor for each bond as
-\begin{equation}
-    B^{(u, v)}_{\langle u, v\rangle} = \begin{cases}
-    1, & \langle u, v \rangle = 0 \\
-    x^{w_{\langle u,v \rangle}}_{\langle u, v\rangle}, & \langle u, v \rangle = 1,
-\end{cases}
-\end{equation}
-where $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$, a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
-$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set, and an edge tensor carries the weights. The tensor network can be defined as
+The tensor network representation for the matching problem $\mathcal{N}_{match}$ can be defined as
 \begin{equation}\label{eq:matchtensornetwork}
@@
                     (), & S = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where for each $v\in V$, we define a vertex tensor over its neighborhood $N(v)$ as
+\begin{equation}
+    W^{(v)}_{\langle v, N(v, 1)\rangle, \langle v, N(v, 2) \rangle, \ldots, \langle v, N(v,d(v))\rangle} = \begin{cases}
+        1, & \sum_{i=1}^{d(v)} \langle v, N(v, i) \rangle \leq 1,\\
+        0, & \text{otherwise},
+    \end{cases}
+\end{equation}
+and for each bond $(u, v) \in E$, we define a rank one tensor as
+\begin{equation}
+    B^{(u, v)}_{\langle u, v\rangle} = \begin{cases}
+    1, & \langle u, v \rangle = 0 \\
+    x^{w_{\langle u,v \rangle}}_{\langle u, v\rangle}, & \langle u, v \rangle = 1
 \end{cases}.
-\end{split}
-\end{equation}
-
+\end{equation}
+Here, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$, a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
+$W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set, and an edge tensor carries the weights.
+
+\begin{theorem}\label{thm:matchcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a matching problem on graph $G=(V,E)$ defined in \Cref{eq:matchtensornetwork} can be contracted in time $cc(\mathcal{N}_{match}(G)) = O(|V|)2^{O({\rm tw}(L(G))}$, $L(G)$ is the line graph of $G$.
+\end{theorem}
+\begin{proof}
+    To contract the tensor network, we first absorb edges tensors into the vertex tensors, which does not increase computational complexity.
+    After this, the resulting tensor network is isomorphic to $G$.
+    Hence the contraction complexity is $O(|V|)2^{O({\rm tw}(L(G))}$.
+\end{proof}
 Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction corresponds to the matching polynomial
@@
 We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
-Then we define a tensor labeled by $c_v$ for each vertex $v$ as
-\begin{equation}
-    W^{(v)} = \left(\begin{matrix}
-        r_v\\
-        g_v\\
-        b_v
-    \end{matrix}\right),
-\end{equation}
-and a bond tensor labelled by $(c_u, c_v) $ for each edge $(u, v) \in E$ as
-\begin{equation}
-    B^{(u, v)} = \left(\begin{matrix}
-        0 & x^{w_{uv}} & x^{w_{uv}}\\
-        x^{w_{uv}} & 0 & x^{w_{uv}}\\
-        x^{w_{uv}} & x^{w_{uv}} & 0
-    \end{matrix}\right),
-\end{equation}
-where $r_v$, $g_v$ and $b_v$ are colors for labeling the configurations.
-$B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
-The tensor network can be defined as
-%The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
-
+The tensor network for the vertex coloring problem $\mathcal{N}_{3-color}(G)$ can be formally defined as
 \begin{equation}\label{eq:colortensornetwork}
@@
 \end{equation}
-
+where for each vertex $v \in V$, we define a tensor labeled by $c_v$
+\begin{equation}
+    W^{(v)} = \left(\begin{matrix}
+        1_{c_{v} = r}\\
+        1_{c_{v} = g}\\
+        1_{c_{v} = b}
+    \end{matrix}\right),
+\end{equation}
+and for each edge $(u, v) \in E$, we define a tensor labelled by $(c_u, c_v)$ as
+\begin{equation}
+    B^{(u, v)} = \left(\begin{matrix}
+        0 & x^{w_{uv}} & x^{w_{uv}}\\
+        x^{w_{uv}} & 0 & x^{w_{uv}}\\
+        x^{w_{uv}} & x^{w_{uv}} & 0
+    \end{matrix}\right),
+\end{equation}
+where subscripts $c_v = r$, $c_v = g$ and $c_v = b$ are for labeling the color configurations. $B$ tensors are for specifying the coloring constraints and $W$ tensors are for labeling the solutions.
+
+\begin{theorem}\label{thm:cutcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a K-coloring problem on graph $G=(V,E)$ as defined in \Cref{eq:colortensornetwork} can be contracted in time $cc(\mathcal{N}_{K-color}(G)) = O(|E|)K^{O({\rm tw}(G))}$.
+\end{theorem}
+The proof is similar to that for \Cref{thm:complexreal} except the dimension of each degree of freedom is $K$.
+%The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
 Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$; we then have a graph polynomial,
@@
 To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-Then for each edge $(u,v)\in E$, we define an edge matrix labeled by $(s_u, s_v)$ as
-\begin{equation}
-    B^{(u, v)} = \left(\begin{matrix}
-        1 & x_{v}^{w_{uv}}\\
-        x_{u}^{w_{uv}} & 1
-    \end{matrix}\right),
-\end{equation}
-where variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem. The tensor network can be defined as
-
+The tensor network representation for the cutting problem $\mathcal{N}_{cut}$ can be formally defined as
 \begin{equation}\label{eq:cuttensornetwork}
@@
 \end{equation}
-
+where for each edge $(u,v)\in E$, we define an edge matrix labeled by $(s_u, s_v)$ as
+\begin{equation}
+    B^{(u, v)} = \left(\begin{matrix}
+        1 & x_{v}^{w_{uv}}\\
+        x_{u}^{w_{uv}} & 1
+    \end{matrix}\right).
+\end{equation}
+Here, variables $x_u^{w_{uv}}$ and $x_v^{w_{uv}}$ are for a cut on this edge or a domain wall in a spin glass problem.
+\begin{theorem}\label{thm:colorcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a cuting problem on graph $G=(V,E)$ as defined in \Cref{eq:cuttensornetwork} can be contracted in time $cc(\mathcal{N}_{cut}(G)) = O(|E|)2^{O({\rm tw}(G))}$.
+\end{theorem}
+The proof is similar to that for \Cref{thm:complexreal}.
 Let $x_u^{w_{uv}} = x_v^{w_{uv}} = x$; we have a graph polynomial similar to the previous ones,
@@
 To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
-Then for each vertex $v$, we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
-\begin{equation}
-T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
-    0 & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0,\\
-    1 & s_v=0,\\
-    x^{w_v}_v & \text{otherwise},
-\end{cases}
-\end{equation}
-where $w_v$ is the weight associated with the vertex $v$, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
-This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0$) cannot be a dominating set.
-Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output. The tensor network can be defined as
-
+The tensor network for the dominating set problem $\mathcal{N}_{dom}$ can be formally defined as
 \begin{equation}\label{eq:domtensornetwork}
@@
                     (), & S = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where for each vertex $v$, we define a tensor on its closed neighborhood $\{v\} \cup N(v)$ as
+\begin{equation}
+T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
+    0 & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0,\\
+    1 & s_v=0,\\
+    x^{w_v}_v & \text{otherwise}.
 \end{cases}
-\end{split}
-\end{equation}
+\end{equation}
+Here, $w_v$ is the weight associated with the vertex $v$, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$.
+This tensor implies a configuration having a closed neighborhood of $v$ not in $D$ ($s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0$) cannot be a dominating set.
+Otherwise, if $v$ is in $D$, this tensor contributes a multiplicative factor $x_v^{w_v}$ to the output. 
+\begin{theorem}\label{thm:domcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a dominating set problem on graph $G=(V,E)$ as defined in \Cref{eq:cuttensornetwork} can be contracted in time $cc(\mathcal{N}_{dom}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$.
+\end{theorem}
+The proof is similar to that for \Cref{thm:miscomplex}.
 The graph polynomial for the dominating set problem is known as the domination polynomial~\cite{Alikhani2009}
@@
 The standard tensor network can be used to study the counting version of the satisfiability problem~\cite{Biamonte2015}, while in the following, we will show a generic reduction from the problem of solving a CNF to a tensor network contraction for solving more solution space properties.
-We first map a Boolean literal $a$ and its negation $\neg a$ to the same degree of freedom $s_a \in \{0, 1\}$.
-$s_a = 0$ stands for variable $a$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
-Then we map a clause to a tensor. For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
-\begin{equation}
-T^{(k)} = \left(\begin{matrix}
-\left(\begin{matrix}
-x^{w_k} & x^{w_k} \\
-x^{w_k} & x^{w_k}
-\end{matrix}\right) \\
-\left(\begin{matrix}
-x^{w_k} & x^{w_k} \\
-1 & x^{w_k}
-\end{matrix}\right)
-\end{matrix}\right),
-\end{equation}
-where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied. The tensor network representation is
-
-\begin{equation}\label{eq:domtensornetwork}
+We first map a Boolean literal $v\in V$ and its negation $\neg v$ to the same degree of freedom $s_v \in \{0, 1\}$.
+$s_v = 0$ stands for variable $v$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
+% For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
+% \begin{equation}
+% T^{(k)} = \left(\begin{matrix}
+% \left(\begin{matrix}
+% x^{w_k} & x^{w_k} \\
+% x^{w_k} & x^{w_k}
+% \end{matrix}\right) \\
+% \left(\begin{matrix}
+% x^{w_k} & x^{w_k} \\
+% 1 & x^{w_k}
+% \end{matrix}\right)
+% \end{matrix}\right),
+% \end{equation}
+% where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied. The tensor network representation is
+The tensor network $\mathcal{N}_{CNF}$ can be formally defined as
+\begin{equation}\label{eq:sattensornetwork}
 \begin{split}
@@
 T^{(k)}_{s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))}} = \begin{cases}
-    x^{}, &C^{k} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
+    x^{}, &C^{(k)} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
     1, &{\rm otherwise}
@@
 where $N(k, i)$ is the $i$th boolean variables in $C^{(k)}$ and $d(k)$ is the number of boolean variables in it.
+$w_k$ is the weight associated with clause $C^{(k)}$.
+\begin{theorem}\label{thm:cnfcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a CNF defined in \Cref{eq:sattensornetwork} can be contracted in time $cc(\mathcal{N}_{CNF}) = O(M)2^{O({\rm tw}(H))}$, where $M$ is the number of clauses,
+    $H$ is a hypergraph constructed by mapping a variables $v\in V$ to a vertex and the $k$th clause $C^{(k)}$ to a hyperedge connecting $\{N(k, i)|i=1,\ldots, d(k)\}$.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is exactly the line graph of $\mathcal{N}_{CNF}$.
 Let $x^{w_k} = x$ and $1_v = 1$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
-\blue{polish}
+
 \subsection{Set packing}
-Suppose one has a finite set $S$ and a list of subsets of $S$, denoted as $\mathcal{V}$. Then, the set packing problem asks if some $k$ subsets in $\mathcal{V}$ are pairwise disjoint.
+Suppose one has a finite set $V$ and a list of subsets of $V$, denoted as $S$. Then, the set packing problem asks if some $k$ subsets in $S$ are pairwise disjoint.
 It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem has a similar form as that for the independent set problem, where the vertex tensor is same as \Cref{eq:vertextensor}, while the edge tensor generalizes \Cref{eq:edgetensor} to higher dimensions such that for each $\sigma \in S$, we have the constraints on set $N(\sigma) = \{s| s\in \mathcal{V} \wedge \sigma \in s\}$
-\begin{equation}
-    B^{(\sigma)}_{N(\sigma, 1), N(\sigma, 2),\ldots, N(\sigma, d(\sigma))} = \begin{cases}
-        1, & s_{N(\sigma, 1)}+ s_{N(\sigma, 2)} + \ldots + s_{N(\sigma, d(\sigma))}\leq 1,\\
+The generic tensor network for the set packing problem also has a similar form as that for the independent set problem
+\begin{equation}\label{eq:packtensornetwork}
+\begin{split}
+    \mathcal{T} &= \{B^{(v)} | v\in V\} \cup \{W^{(\sigma)} | \sigma \in S\} \cup \{P\},\\
+    \Sigma &= \{s_\sigma | \sigma \in S\},\\
+    O &= P,\\
+    \lambda &= T \mapsto \begin{cases}
+                    (s_\sigma), & T = W^{(\sigma)}\\
+                    (s_{N(v, 1)}, \ldots, s_{N(v, d(v))}), & T = B^{(v)}\\
+                    (), & T = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where for each $v \in V$, we have the constraints over sets containing it $N(v) = \{\sigma| \sigma\in S \wedge v \in \sigma\}$ as
+\begin{equation}
+    B^{(v)}_{N(v, 1), N(v, 2),\ldots, N(v, d(v))} = \begin{cases}
+        1, & s_{N(v, 1)}+ s_{N(v, 2)} + \ldots + s_{N(v, d(v))}\leq 1,\\
         0, & \text{otherwise}.
@@
 \end{equation}
-where $N(\sigma, k)$ is the $k$th element in $N(\sigma)$ and $d(\sigma) = |N(\sigma)|$ is the number of elements in $N(\sigma)$. The tensor network representation for the set packing problem is
-
-\begin{equation}\label{eq:packtensornetwork}
-\begin{split}
-    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(\sigma)} | \sigma \in \mathcal{S}\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
-    O &= P,\\
-    \lambda &= T \mapsto \begin{cases}
-                    (s_v), & T = W^{(v)}\\
-                    (s_{N(\sigma, 1)}, \ldots, s_{N(\sigma, d(\sigma))}), & T = B^{(\sigma)}\\
-                    (), & T = P
-                    \end{cases}
-\end{split}
-\end{equation}
+and the vertex tensor for each $\sigma \in S$
+\begin{equation}
+    W^{(\sigma)} = \left(\begin{matrix}
+        1\\
+        x^{w_\sigma}_{\sigma}
+    \end{matrix}\right),
+\end{equation}
+where $N(v, k)$ is the $k$th element in $N(v)$ and $d(v) = |N(v)|$ is the number of elements in $N(v)$.
 
 \subsection{Set covering}
-Given a collection of elements, the set covering problem aims to find the minimum number of sets that incorporate (cover) all of these elements.
-In the set covering problem, two sets are given: a set $\mathcal{V}$ of elements and a set $S$ of subsets of $\mathcal{V}$.
-The union of all the subsets covers $\mathcal{V}$.
-Each set $s \in S$ is associated with an positive integer weight $w_s$.
+Suppose one has a finite set $V$ and a list of subsets of $V$, denoted as $S$.
+The set covering problem aims to find the minimum number of sets in $S$ that incorporate (cover) all of elements in $V$.
 To get the generic tensor network representation, we first map a set $\sigma \in S$ to a Boolean degree of freedom $s_\sigma\in\{0, 1\}$.
-For each $s_\sigma$, we define a parameterized rank-one tensor indexed by it as
-\begin{equation}
-W^{(\sigma)} = \left(\begin{matrix}
-    1 \\
-    x_\sigma^{w_\sigma}
-    \end{matrix}\right)
-\end{equation}
-where $x_\sigma$ is a generic typed variable associated with $\sigma$ and the positive integer power of which can be define by the repeated multiplication.
-For each element $v \in \mathcal{V}$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(v) = \{s | s \in S \land v\in s\}$, as
-\begin{equation}
-B^{(v)}_{s_{N(v, 1)}, s_{N(v, 2)}, \ldots, s_{N(v, d(v))}} = \begin{cases}
-    0, & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
-    1, & \text{otherwise}.
-\end{cases}
-\end{equation}
-where $N(v, k)$ is the $k$th element in $N(v)$ and $d(v) = |N(v)|$ is the number of elements in $N(v)$. 
-If a subset of $S$ does not include any sets containing element $v$, then the corresponding entry is zero.
-The tensor network representation for the set packing problem is
+Then the tensor network representation for the set packing problem can be expressed as
 \begin{equation}\label{eq:covertensornetwork}
 \begin{split}
-    \mathcal{T} &= \{W^{(\sigma)} | \sigma \in S\} \cup \{B^{(v)} | v \in \mathcal{V}\} \cup \{P\},\\
+    \mathcal{T} &= \{W^{(\sigma)} | \sigma \in S\} \cup \{B^{(v)} | v \in V\} \cup \{P\},\\
     \Sigma &= \{s_\sigma | \sigma \in \mathcal{S}\},\\
@@
                     (), & T = P
+                    \end{cases},
+\end{split}
+\end{equation}
+where for each $s_\sigma$, we define a parameterized rank-one tensor indexed by it as
+\begin{equation}
+W^{(\sigma)} = \left(\begin{matrix}
+    1 \\
+    x_\sigma^{w_\sigma}
+    \end{matrix}\right)
+\end{equation}
+where $x_\sigma$ is a generic typed variable associated with $\sigma$ and $w_\sigma$ is a positive integer as the weight.
+For each element $v \in V$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(v) = \{s | s \in S \land v\in s\}$, as
+\begin{equation}
+B^{(v)}_{s_{N(v, 1)}, s_{N(v, 2)}, \ldots, s_{N(v, d(v))}} = \begin{cases}
+    0, & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
+    1, & \text{otherwise}.
 \end{cases}
-\end{split}
-\end{equation}
+\end{equation}
+where $N(v, k)$ is the $k$th element in $N(v)$ and $d(v) = |N(v)|$ is the number of elements in $N(v)$. 
+If a subset of $S$ does not include any sets containing element $v$, then the corresponding entry is zero.
 

### 2022-08-29 replys/reply.tex
update

@@
 \def\labelenumi{\arabic{enumi}.}
-\item The Section ...
-\item A new figure, ...
-\item We have added a paragraph at the ...
-\item In the revised Supplementary Material, a Section ...
-\item In the revised Supplementary Material, the Section ...
-\item The section ...
+\item Define what is a tensor network in Definition 2.1,
+\item Define the tensor network representation for all combinatorial optimization problems rigorously in Eq. 4.3 and Appendix B.
+\item Add theorems and proofs to the main claims in the paper, including the computation of solution space properties and tensor network contraction complexities in Appendix B.
 \end{enumerate}
@@
 {\bf Response:}
-Thank you for the careful reading and constructive comments on notations. We applied the most of the suggested changes accordingly in the main text to make it more readable except the comment 3).
+Thank you for the careful reading and constructive comments on notations. We applied all the suggested changes in the main text except the comment 3).
 We can not find a better symbol than $\oplus$ to represent the generic plus, so we emphasised this notation is different from the XOR in computer science when we first introduce it.

### 2022-08-29 paper/paper.tex
update paper

@@
 \end{theorem}
-This can be proved by showing the hypergraph $H$ is exactly the line graph of $\mathcal{N}_{CNF}$.
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{CNF}$.
 Let $x^{w_k} = x$ and $1_v = 1$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
@@
 It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem also has a similar form as that for the independent set problem
+The generic tensor network for the set packing problem $\mathcal{N}_{pack}$ also has a similar form as that for the independent set problem
 \begin{equation}\label{eq:packtensornetwork}
@@
 
+\begin{theorem}\label{thm:packcomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a set packing problem defined in \Cref{eq:packtensornetwork} can be contracted in time $cc(\mathcal{N}_{pack}) = O(|S|)2^{O({\rm tw}(H))}$, where $|S|$ is the number of sets,
+    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{cover}$.
+
 \subsection{Set covering}
@@
 To get the generic tensor network representation, we first map a set $\sigma \in S$ to a Boolean degree of freedom $s_\sigma\in\{0, 1\}$.
-Then the tensor network representation for the set packing problem can be expressed as
+Then the tensor network representation for the set covering problem $\mathcal{N}_{pack}$ can be expressed as
 \begin{equation}\label{eq:covertensornetwork}
@@
 If a subset of $S$ does not include any sets containing element $v$, then the corresponding entry is zero.
+
+\begin{theorem}\label{thm:covercomplex}
+    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
+    The tensor network representation of a set covering problem defined in \Cref{eq:covertensornetwork} can be contracted in time $cc(\mathcal{N}_{cover}) = O(|S|)2^{O({\rm tw}(H))}$, where $|S|$ is the number of sets,
+    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{cover}$.
 

### 2022-08-29 paper/paper.tex
fix a theorem
Updates from Overleaf

@@
 An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-To reduce the independent set problem on $G$ to a tensor network contraction, we first map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in $I$.
-For each label $s_v$, we define a parameterized rank-one tensor associated with it as
+To the independent set problem on $G$ can be encoded as a tensor network $\mathcal{N}_{\rm IS}(G)$
+\begin{equation}\label{eq:mistensornetwork}
+\begin{split}
+    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
+    \Sigma &= \{s_v | v \in V\},\\
+    O &= P,\\
+    \lambda &= T \mapsto \begin{cases}
+                    (s_v), &T = W^{(v)}\\
+                    (s_u, s_v), &T = B^{(u, v)}\\
+                    (), & T = P
+                    \end{cases},
+    \end{split}
+\end{equation}
+where for each vertex $v$, we define a parameterized rank-one tensor associated with it as
 \begin{equation}
@@
 \end{equation}
-where $x_v$ is a variable associated with $v$.
-Tensor elements can be indexed by $s_v$, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$.
-Similarly, for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
+and for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
 \begin{equation}
@@
         1 & 0
-    \end{matrix}\right), \label{eq:edgetensor}
-\end{equation}
-which encodes the independent set constraint since $B_{11} = 0$, meaning the two vertices cannot be both in the independent set. 
-The corresponding tensor network $\mathcal{N}_{\rm IS}(G)$ is
-\begin{equation}\label{eq:mistensornetwork}
-\begin{split}
-    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\}\\
-    \Sigma &= \{s_v | v \in V\}\\
-    O &= P\\
-    \lambda &= T \mapsto \begin{cases}
-                    (s_v), &T = W^{(v)}\\
-                    (s_u, s_v), &T = B^{(u, v)}\\
-                    (), & T = P
-                    \end{cases}
-    \end{split}
-\end{equation}
-where we use the superscripts to denote which vertex or edge a tensor is associated to.
+    \end{matrix}\right). \label{eq:edgetensor}
+\end{equation}
+We map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in $I$.
+%We use the superscripts to denote which vertex or edge a tensor is associated to.
+These labels can be used as subscripts of tensors to index tensor elements, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$, where $x_v$ is a variable associated with vertex $v$.
 $P$ is the output tensor of rank $0$, i.e. a scalar.
+The independence constraint is encoded in the edge tensors, where we use $B_{11} = 0$ to denote two vertices connected by an edge cannot be both in the independent set. 
 The contraction of this tensor network is
@@
     \begin{cases}
-    1 \rightarrow \mymathbb{1}\\
-    0 \rightarrow \mymathbb{0}\\
-    x_v^{w_v} \rightarrow (0, 1)
+    1 &\rightarrow \mymathbb{1},\\
+    0 &\rightarrow \mymathbb{0},\\
+    x_v^{w_v} &\rightarrow (0, 1),
     \end{cases}
 \end{equation}
-The tensors $W$ and $B$, which are introduced in the previous section (\Cref{sec:tnmap}), can thus be written as 
+the tensors $W$ and $B$, which are introduced in the previous section (\Cref{sec:tnmap}), can thus be written as 
 \begin{equation}
@@
 \begin{theorem}\label{thm:complexset}
-    Let $G = (V, E)$ be a graph and $I$ be its independent sets.
-    $I$ can be computed in time $O(|I||E|)\cc$.
+    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I|)\cc$, where $|I|$ is the number of independent sets.
 \end{theorem}

### 2022-09-02 paper/paper.tex
Updates from Overleaf

@@
 
-\begin{lemma}
+\begin{theorem}
     The number of the largest $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
-\end{lemma}
+\end{theorem}
 The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.
@@
 
-Similarly, we have the following lemma by combining the sum-product expression tree algebra with the truncated polynomial.
-
-\begin{lemma}\label{thm:complexexprk}
+Similarly, we have the following theorem by combining the sum-product expression tree algebra with the truncated polynomial.
+
+\begin{theorem}\label{thm:complexexprk}
         Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$.
 The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
-\end{lemma}
+\end{theorem}
 
@@
 
-Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following lemma.
-\begin{lemma}
+Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following theorem.
+\begin{theorem}
     Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
-\end{lemma}
+\end{theorem}
 
@@
 \begin{theorem}
-    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K)\cc$.
+    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K)\cc$.
 \end{theorem}
@@
 
-\begin{lemma}
-    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
-\end{lemma}
+\begin{theorem}
+    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
+\end{theorem}
 To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).

### 2022-09-02 paper/paper.tex
update

--- 2022-08-29 paper/paper.tex
@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network is composed of a collection of tensors $\mathcal{T}$, an indicator of which tensor is the output, and a map $\lambda$ from tensor to labels associated with tensor dimensions.
+A tensor network is a multi-linear map composed of a collection of labelled tensors $\mathcal{T}$ and an indicator for the output tensor. It is formally defined as follows.
 \begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
-    A tensor network is a quadruple of $\mathcal{N} = (\Tensors, \Sigma, O \in \Tensors, \Inputs : \mathcal{T} \rightarrow \Sigma^k)$.
-$\Tensors$ is a set of tensors, among which $O$ is the output tensor.
-    $\Sigma$ is an alphabet of labels. $\Inputs$ is a map from a tensor to a vector of labels with the vector length the same as the tensor rank.
+    A tensor network is a triple of $\mathcal{N} = (\Sigma, \Tensors, O)$.
+    $\Sigma$ is an alphabet of labels.
+    $\Tensors$ is a set of labelled tensors as the inputs, each $T_{\boldsymbol{\sigma}} \in \mathcal{T}$ is labeled by a vector of labels $\boldsymbol{\sigma} \in \Sigma^{r(T)}$, where $r(T)$ the rank of $T$.
+    $O$ is a labbeled tensor as the output.
 \end{definition}
@@
 \begin{equation}
-\mathcal{N}_{\rm matmul} = \left(\{A, B, C\}, \{i,j,k\}, C, T \mapsto \begin{cases} (i,j), T = A\\(j, k), T=B\\ (i, k), T=C\end{cases}\right),
+\mathcal{N}_{\rm matmul} = \left(\{i,j,k\}, \{A_{ij}, B_{jk}\}, C_{ik}\right),
 \end{equation}
@@
 \begin{split}
-    \mathcal{T} &= \{A, B, V, C\},\\
     \Sigma &= \{i,j,k,l,m\},\\
-    O &= C,\\
-    \lambda &= T \mapsto \begin{cases}
-    (j, k, m), &T = A\\
-    (m, i, l), &T = B \\
-    (j, m), &T = V \\
-    (i, j, k), &T= C
-    \end{cases}
+    \mathcal{T} &= \{A_{jkm}, B_{mil}, V_{jm}\},\\
+    O &= C_{ijk},\\
     \end{split}
@@
 \begin{split}
-    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
-    O &= P,\\
-    \lambda &= T \mapsto \begin{cases}
-                    (s_v), &T = W^{(v)}\\
-                    (s_u, s_v), &T = B^{(u, v)}\\
-                    (), & T = P
-                    \end{cases},
+    \Sigma &= \{s_v \mid v \in V\},\\
+    \mathcal{T} &= \{W^{(v)}_{v} \mid v\in V\} \cup \{B^{(u, v)}_{uv} \mid (u, v) \in E\},\\
+    O &= P,
     \end{split}
@@
 \begin{theorem}\label{thm:complexreal}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    the tensor network in \Cref{eq:mistensornetwork} for the independent set problem on graph $G = (V,E)$ can be contracted in time $\cc = O(|E|)2^{O({\rm tw}(G))}$.
+    The tensor network in \Cref{eq:mistensornetwork} for the independent set problem on graph $G = (V,E)$ can be contracted in $\cc = O(|E|)2^{O({\rm tw}(G))}$ number of additions and multiplications.
 \end{theorem}
@@
 \begin{lemma}
-    The number of the largest $k$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
+    The number of the largest $K$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
 \end{lemma}
@@
     s \oplus t &= s \cup t\\
-    s \odot t &= \{\sigma \lor^\circ \tau \, | \, \sigma \in s, \tau \in t\}\\
+    s \odot t &= \{\sigma \lor^\circ \tau \, \mid \, \sigma \in s, \tau \in t\}\\
     \mymathbb{0} &= \{\}\\
@@
 \begin{theorem}\label{thm:complexset}
-    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I|)\cc$, where $|I|$ is the number of independent sets.
+    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I||V|)\cc$, where $|I|$ is the number of independent sets.
 \end{theorem}
@@
     \end{cases},\\
-    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau | \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
+    s_x\infty^x \odot s_y\infty^y &= \{\sigma \lor^\circ \tau \mid \sigma \in s_x, \tau \in s_y\}\infty^{x+y},\\
     \mymathbb{0} &= \{\}\infty^{-\infty},\\
@@
 
-\begin{theorem}
+\begin{corollary}
     Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
-\end{theorem}
+\end{corollary}
 The proof is similar to \Cref{thm:complexmis}, except the set algebra is replace by the one in \Cref{eq:singleconfig}, and the time complexity of element-wise addition and multiplication no longer depends on $|\mathcal{I}_\alpha|$.
@@
     s \oplus t &= \texttt{largest}(s \cup t, k)\\
-    s \odot t &= \texttt{largest}(\{a+b | a \in s, b\in t\}, k)\\
+    s \odot t &= \texttt{largest}(\{a+b \mid a \in s, b\in t\}, k)\\
     \mymathbb{0} &= -\infty^{\otimes k}\\
@@
 \subsection{Maximal independent sets and maximal cliques}\label{sec:maximal}
-In this section, we focus the discussion on the maximal independent sets problem since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of the complement of the graph.
+In this section, we focus the discussion on the maximal independent sets problem since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of its complement.
 Let $G=(V,E)$ be a graph, we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
@@
 \begin{split}
-    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
+    \Sigma &= \{s_v \mid v \in V\},\\
+    \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)} s_{N(v, 2)}\ldots s_{N(v,d(v))}s_v} \mid v\in V\},\\
     O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
-                    (), & S = P
-                    \end{cases},
 \end{split}
@@
 \begin{equation}\label{eq:maximal}
-    T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
+    T^{(v)}_{s_{N(v, 1)}s_{N(v, 2)}\ldots s_{N(v, d(v))}s_v} = \begin{cases}
         s_vx_v^{w_v} & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
@@
 \begin{theorem}\label{thm:miscomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a maximal independent set problem on graph $G=(V,E)$ defined in \Cref{eq:maxistensornetwork} can be contracted in time $cc(\mathcal{N}_{mIS}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$, where $\Delta$ is the maximum degree of vertices in $G$.
+    The tensor network representation of a maximal independent set problem on graph $G=(V,E)$ (\Cref{eq:maxistensornetwork}) can be contracted in $cc(\mathcal{N}_{mIS}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications, where $\Delta$ is the maximum degree of vertices in $G$.
 \end{theorem}
@@
 \begin{split}
-    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
-    \Sigma &= \{\langle u,v\rangle | (u, v) \in E\},\\
-    O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (\langle v, N(v, 1)\rangle, \langle v, N(v,2) \rangle, \ldots, \langle v, N(v, d(v))\rangle), & S = W^{(v)}\\
-                    (\langle u,v\rangle), & S = B^{(u, v)}\\
-                    (), & S = P
-                    \end{cases},
+    \Sigma &= \{\langle u,v\rangle \mid (u, v) \in E\},\\
+    \mathcal{T} &= \{W^{(v)}_{\langle v, N(v, 1)\rangle \langle v, N(v,2) \rangle \ldots \langle v, N(v, d(v))\rangle} \mid v\in V\} \cup \{B^{(u, v)}_{\langle u,v\rangle} \mid (u, v) \in E\},\\
+    O &= P,
 \end{split}
@@
 \begin{equation}
-    W^{(v)}_{\langle v, N(v, 1)\rangle, \langle v, N(v, 2) \rangle, \ldots, \langle v, N(v,d(v))\rangle} = \begin{cases}
+    W^{(v)}_{\langle v, N(v, 1)\rangle \langle v, N(v, 2) \rangle \ldots \langle v, N(v,d(v))\rangle} = \begin{cases}
         1, & \sum_{i=1}^{d(v)} \langle v, N(v, i) \rangle \leq 1,\\
@@
 \begin{theorem}\label{thm:matchcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a matching problem on graph $G=(V,E)$ defined in \Cref{eq:matchtensornetwork} can be contracted in time $cc(\mathcal{N}_{match}(G)) = O(|V|)2^{O({\rm tw}(L(G))}$, $L(G)$ is the line graph of $G$.
+    The tensor network representation of a matching problem on graph $G=(V,E)$ (\Cref{eq:matchtensornetwork}) can be contracted in $cc(\mathcal{N}_{match}(G)) = O(|V|)2^{O({\rm tw}(L(G))}$ number of additions and multiplications, $L(G)$ is the line graph of $G$.
 \end{theorem}
@@
 \begin{split}
-    \mathcal{T} &= \{W^{(v)} | v\in V\} \cup \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
-    \Sigma &= \{c_v | v \in V\},\\
+    \Sigma &= \{c_v \mid v \in V\},\\
+    \mathcal{T} &= \{W^{(v)}_{c_v} \mid v\in V\} \cup \{B^{(u, v)}_{c_uc_v} \mid (u, v) \in E\},\\
     O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (c_v), & S = W^{(v)}\\
-                    (c_u, c_v), & S = B^{(u, v)}\\
-                    (), & S = P
-                    \end{cases}
 \end{split}
@@
 \begin{theorem}\label{thm:cutcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a K-coloring problem on graph $G=(V,E)$ as defined in \Cref{eq:colortensornetwork} can be contracted in time $cc(\mathcal{N}_{K-color}(G)) = O(|E|)K^{O({\rm tw}(G))}$.
+    The tensor network representation of a K-coloring problem on graph $G=(V,E)$ (\Cref{eq:colortensornetwork}) can be contracted in $cc(\mathcal{N}_{K-color}(G)) = O(|E|)K^{O({\rm tw}(G))}$ number of additions and multiplications.
 \end{theorem}
@@
 \begin{split}
-    \mathcal{T} &= \{B^{(u, v)} | (u, v) \in E\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
+    \mathcal{T} &= \{B^{(u, v)}_{s_us_v} \mid (u, v) \in E\},\\
+    \Sigma &= \{s_v \mid v \in V\},\\
     O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (s_u, s_v), & S = B^{(u, v)}\\
-                    (), & S = P
-                    \end{cases}
 \end{split}
@@
 \begin{theorem}\label{thm:colorcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a cuting problem on graph $G=(V,E)$ as defined in \Cref{eq:cuttensornetwork} can be contracted in time $cc(\mathcal{N}_{cut}(G)) = O(|E|)2^{O({\rm tw}(G))}$.
+    The tensor network representation of a cuting problem on graph $G=(V,E)$ (\Cref{eq:cuttensornetwork}) can be contracted in $cc(\mathcal{N}_{cut}(G)) = O(|E|)2^{O({\rm tw}(G))}$ number of additions and multiplications.
 \end{theorem}
@@
 \begin{split}
-    \mathcal{T} &= \{T^{(v)} | v\in V\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
+    \Sigma &= \{s_v \mid v \in V\},\\
+    \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)}s_{N(v, 2)} \ldots s_{N(v,d(v))}, s_v} \mid v\in V\},\\
     O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (s_{N(v,1)}, \ldots, s_{N(v,d(v))}, s_v), & S = T^{(v)}\\
-                    (), & S = P
-                    \end{cases},
 \end{split}
@@
 \begin{equation}
-T^{(v)}_{s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(v, d(v))},s_v} = \begin{cases}
+T^{(v)}_{s_{N(v, 1)}s_{N(v, 2)}\ldots s_{N(v, d(v))}s_v} = \begin{cases}
     0 & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=s_v=0,\\
@@
 \begin{theorem}\label{thm:domcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a dominating set problem on graph $G=(V,E)$ as defined in \Cref{eq:cuttensornetwork} can be contracted in time $cc(\mathcal{N}_{dom}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$.
+    The tensor network representation of a dominating set problem on graph $G=(V,E)$ (\Cref{eq:domtensornetwork}) can be contracted in $cc(\mathcal{N}_{dom}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications.
 \end{theorem}
@@
 One can specify a satisfiable problem in the conjunctive normal form (CNF), i.e.\ a conjunction of clauses (or disjunctions of Boolean literals).
-Given the alphabet of Boolean variables $V$, a CNF can be formally defined as
+Given the alphabet of Boolean variables $V$ and its negation $\neg V = \{\neg v \mid v \in V\}$, a CNF can be formally defined as
 \begin{equation}
@@
 \end{equation}
-where $M$ is the number of clauses, $C^{(k)}$ is the $k$th clause and $C^{(k)}_i \in V \cup \{\neg v | v \in V\}$ is the $i$th literal in it.
+where $M$ is the number of clauses, $C^{(k)}$ is the $k$th clause and $C^{(k)}_i \in V \cup \neg V$ is the $i$th literal in it.
 The standard tensor network can be used to study the counting version of the satisfiability problem~\cite{Biamonte2015}, while in the following, we will show a generic reduction from the problem of solving a CNF to a tensor network contraction for solving more solution space properties.
-We first map a Boolean literal $v\in V$ and its negation $\neg v$ to the same degree of freedom $s_v \in \{0, 1\}$.
+We first map each Boolean literal $v\in V$ to a Boolean degree of freedom $s_v \in \{0, 1\}$.
 $s_v = 0$ stands for variable $v$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
@@
 \begin{split}
-    \mathcal{T} &= \{W^{(v)} | v \in V\} \cup \{T^{(k)} | k=1,\ldots,M\} \cup \{P\},\\
-    \Sigma &= \{s_v | v \in V\},\\
+    \Sigma &= \{s_v \mid v \in V\},\\
+    \mathcal{T} &= \{W^{(v)}_v \mid v \in V\} \cup \{T^{(k)}_{s_{N(k,1)} s_{N(k, 2)} s_{N(k,3))}} \mid k=1,\ldots,M\},\\
     O &= P,\\
-    \lambda &= S \mapsto \begin{cases}
-                    (s_{l(k,1)}, s_{l(k, 2)}, s_{l(k,3))}), & S = C^{(k)}\\
-                    (), & S = P
-                    \end{cases},
 \end{split}
@@
 \begin{equation}
-T^{(k)}_{s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))}} = \begin{cases}
+T^{(k)}_{s_{N(k, 1)} s_{N(k, 2)} \ldots s_{N(k, d(k))}} = \begin{cases}
     x^{}, &C^{(k)} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
@@
 \end{equation}
-where $N(k, i)$ is the $i$th boolean variables in $C^{(k)}$ and $d(k)$ is the number of boolean variables in it.
+where $N(k, i) = \begin{cases}\neg C^{(k)}_i, &C^{(k)}_i \in \neg V\\ C^{(k)}_i, & C^{(k)}_i \in V\end{cases}$ is the $i$th literal in $C^{(k)}$ with its negation sign removed and $d(k)$ is the number of boolean variables in it.
 $w_k$ is the weight associated with clause $C^{(k)}$.
 \begin{theorem}\label{thm:cnfcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a CNF defined in \Cref{eq:sattensornetwork} can be contracted in time $cc(\mathcal{N}_{CNF}) = O(M)2^{O({\rm tw}(H))}$, where $M$ is the number of clauses,
-    $H$ is a hypergraph constructed by mapping a variables $v\in V$ to a vertex and the $k$th clause $C^{(k)}$ to a hyperedge connecting $\{N(k, i)|i=1,\ldots, d(k)\}$.
+    The tensor network representation of a CNF (\Cref{eq:sattensornetwork}) can be contracted in $cc(\mathcal{N}_{CNF}) = O(M)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $M$ is the number of clauses,
+    $H$ is a hypergraph constructed by mapping a variables $v\in V$ to a vertex and the $k$th clause $C^{(k)}$ to a hyperedge connecting $\{N(k, i)\mid i=1,\ldots, d(k)\}$.
 \end{theorem}
@@
 \begin{split}
-    \mathcal{T} &= \{B^{(v)} | v\in V\} \cup \{W^{(\sigma)} | \sigma \in S\} \cup \{P\},\\
-    \Sigma &= \{s_\sigma | \sigma \in S\},\\
-    O &= P,\\
-    \lambda &= T \mapsto \begin{cases}
-                    (s_\sigma), & T = W^{(\sigma)}\\
-                    (s_{N(v, 1)}, \ldots, s_{N(v, d(v))}), & T = B^{(v)}\\
-                    (), & T = P
-                    \end{cases},
+    \Sigma &= \{s_\sigma \mid \sigma \in S\},\\
+    \mathcal{T} &= \{B^{(v)}_{s_{N(v, 1)} \ldots s_{N(v, d(v))}} \mid v\in V\} \cup \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\},\\
+    O &= P,
 \end{split}
 \end{equation}
-where for each $v \in V$, we have the constraints over sets containing it $N(v) = \{\sigma| \sigma\in S \wedge v \in \sigma\}$ as
-\begin{equation}
-    B^{(v)}_{N(v, 1), N(v, 2),\ldots, N(v, d(v))} = \begin{cases}
+where for each $v \in V$, we have the constraints over sets containing it $N(v) = \{\sigma\mid \sigma\in S \wedge v \in \sigma\}$ as
+\begin{equation}
+    B^{(v)}_{N(v, 1) N(v, 2)\ldots N(v, d(v))} = \begin{cases}
         1, & s_{N(v, 1)}+ s_{N(v, 2)} + \ldots + s_{N(v, d(v))}\leq 1,\\
@@
 \begin{theorem}\label{thm:packcomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a set packing problem defined in \Cref{eq:packtensornetwork} can be contracted in time $cc(\mathcal{N}_{pack}) = O(|S|)2^{O({\rm tw}(H))}$, where $|S|$ is the number of sets,
+    The tensor network representation of a set packing problem (\Cref{eq:packtensornetwork}) can be contracted in $cc(\mathcal{N}_{pack}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
     $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.
@@
 \begin{split}
-    \mathcal{T} &= \{W^{(\sigma)} | \sigma \in S\} \cup \{B^{(v)} | v \in V\} \cup \{P\},\\
-    \Sigma &= \{s_\sigma | \sigma \in \mathcal{S}\},\\
-    O &= P,\\
-    \lambda &= T \mapsto \begin{cases}
-                    (s_\sigma), & T = W^{(\sigma)}\\
-                    (s_{N(v, 1)},s_{N(v, 2)},\ldots,s_{N(\sigma, d(v))}), & T = B^{(v)}\\
-                    (), & T = P
-                    \end{cases},
+    \Sigma &= \{s_\sigma \mid \sigma \in \mathcal{S}\},\\
+    \mathcal{T} &= \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\} \cup \{B^{(v)}_{s_{N(v, 1)}s_{N(v, 2)}\ldots s_{N(\sigma, d(v))}} \mid v \in V\},\\
+    O &= P,
 \end{split}
@@
 where $x_\sigma$ is a generic typed variable associated with $\sigma$ and $w_\sigma$ is a positive integer as the weight.
-For each element $v \in V$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(v) = \{s | s \in S \land v\in s\}$, as
-\begin{equation}
-B^{(v)}_{s_{N(v, 1)}, s_{N(v, 2)}, \ldots, s_{N(v, d(v))}} = \begin{cases}
+For each element $v \in V$, we can define a constraint over all $s \in S$ containing this element, i.e. $N(v) = \{s \mid s \in S \land v\in s\}$, as
+\begin{equation}
+B^{(v)}_{s_{N(v, 1)} s_{N(v, 2)} \ldots s_{N(v, d(v))}} = \begin{cases}
     0, & s_{N(v, 1)}=s_{N(v, 2)}=\ldots=s_{N(v, d(v))}=0,\\
@@
 \begin{theorem}\label{thm:covercomplex}
-    If the addition and multiplication of tensor elements can be computed in time $O(1)$,
-    The tensor network representation of a set covering problem defined in \Cref{eq:covertensornetwork} can be contracted in time $cc(\mathcal{N}_{cover}) = O(|S|)2^{O({\rm tw}(H))}$, where $|S|$ is the number of sets,
+    The tensor network representation of a set covering problem (\Cref{eq:covertensornetwork}) can be contracted in $cc(\mathcal{N}_{cover}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
     $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.

### 2022-09-02 paper/paper.tex

@@
 \section{Maximum independent sets and its counting}\label{sec:counting}
+\subsection{The number of independent sets}
+\begin{theorem}\label{thm:complexrealnum}
+    Let $G = (V, E)$ be a graph, the total number independent sets of $G$ can be computed in time $\cc$.
+\end{theorem}
+\begin{proof}
+Let $x = 1$ be a real constant number, the independence polynomial in the previous section becomes
+\begin{equation}
+I(G, 1) = \sum_{k=0}^{\alpha(G)}a_k,
+\end{equation}
+which corresponds to the total number of independent sets.
+Since the real number addtion and multiplication can be computed in $O(1)$ time,
+proving the theorem by \Cref{thm:complexreal}.
+\end{proof}
+
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
@@
 
-\begin{lemma}
+\begin{theorem}
     The number of the largest $K$ independent sets of a graph $G = (V, E)$ can be computed in time $O(K\log K)\cc$.
-\end{lemma}
+\end{theorem}
 The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.
@@
 
-\begin{theorem}\label{thm:complexset}
+\begin{lemma}\label{thm:complexset}
     The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I||V|)\cc$, where $|I|$ is the number of independent sets.
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{theorem}\label{thm:complexmis}
+\begin{lemma}\label{thm:complexmis}
     Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
     $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V|)\cc$.
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{theorem}\label{thm:complexsetk}
+\begin{lemma}\label{thm:complexsetk}
     Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
     The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 
-\begin{corollary}
+\begin{proposition}
     Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
-\end{corollary}
+\end{proposition}
 The proof is similar to \Cref{thm:complexmis}, except the set algebra is replace by the one in \Cref{eq:singleconfig}, and the time complexity of element-wise addition and multiplication no longer depends on $|\mathcal{I}_\alpha|$.
@@
 \end{equation}
-The contraction of such tensor network corresponds to a sum-product expression tree of the set of independent sets, which costs time $\cc$ by \Cref{thm:complexreal} since the computing time of expression tree addition and multiplication are $O(1)$.
+The contraction result of this tensor network corresponds to a sum-product expression tree for the set of independent sets.
+Unlike in \Cref{thm:complexset}, the contraction complexity is independent of the set size, i.e. the time complexity is $\cc$ by \Cref{thm:complexreal}.
 The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
+Proving the theorem by adding two computing times.
 \end{proof}
 
-Similarly, we have the following lemma by combining the sum-product expression tree algebra with the truncated polynomial.
-
-\begin{lemma}\label{thm:complexexprk}
+Similarly, we have the following corollary by combining the sum-product expression tree algebra with the truncated polynomial.
+
+\begin{corollary}\label{thm:complexexprk}
         Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$.
 The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
-\end{lemma}
-
-Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large size,
-they can draw unbiased samples from it by direct sampling.
+\end{corollary}
+Again, the theorem can be proved by relating it with its set algebra version in \Cref{thm:complexsetk}.
+Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large configuration space,
+one can draw samples unbiasedly from it by direct sampling.
 \begin{theorem}
@@
 
-Since the depth of the expression tree is $|V|$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
+Since the depth of the expression tree is $O(|V|)$ and the cost of each arithmetic operation is also $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
+Proving the theorem.
 \end{proof}
 
-Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following lemma.
-\begin{lemma}
+Similarly, if one is only interested in obtaining independent sets with largest $K$ sizes, we have the following corollary.
+\begin{corollary}
     Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
-\end{lemma}
+\end{corollary}
 
@@
 
-\begin{lemma}
-    Let $G = (V, E, W)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
-\end{lemma}
+\begin{corollary}
+    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
+\end{corollary}
 To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).

### 2022-09-02 paper/paper.tex
fix sampling complexity

@@
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V|^2 M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V||E| M)$, where $M$ is the number of samples.
 \end{theorem}
@@
 Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $\cc$.
-Then we show to generate a sample, the cost is $O(|V|^2)$.
+Then we show to generate a sample, the cost is $O(|V||E|)$.
 The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
@@
 
-Since the depth of the expression tree is $O(|V|)$ and the cost of each arithmetic operation is also $O(|V|)$, the overall time complexity to generate a sample is $O(|V|^2)$.
+Since the depth of the expression tree is $O(|E|)$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V||E|)$.
 Proving the theorem.
@@
 \begin{corollary}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|^2 M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V||E| M)$, where $M$ is the number of samples.
 \end{corollary}

### 2022-09-03 paper/paper.tex
update notation

@@
 \section{Tensor networks}\label{sec:tn}
-A tensor network is a multi-linear map composed of a collection of labelled tensors $\mathcal{T}$ and an indicator for the output tensor. It is formally defined as follows.
+A tensor network is a multi-linear map from a collection of labelled tensors $\mathcal{T}$ to an output tensor.
+It is formally defined as follows.
 \begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
-    A tensor network is a triple of $\mathcal{N} = (\Sigma, \Tensors, O)$.
-    $\Sigma$ is an alphabet of labels.
-    $\Tensors$ is a set of labelled tensors as the inputs, each $T_{\boldsymbol{\sigma}} \in \mathcal{T}$ is labeled by a vector of labels $\boldsymbol{\sigma} \in \Sigma^{r(T)}$, where $r(T)$ the rank of $T$.
-    $O$ is a labbeled tensor as the output.
+    A tensor network a multi-linear map specified by a triple of $\mathcal{N} = (\Sigma, \Tensors, \boldsymbol{\sigma}_o)$,
+    where $\Sigma$ is an alphabet of labels,
+    $\Tensors = \{T^{(1)}_{\boldsymbol{\sigma}_1}, T^{(2)}_{\boldsymbol{\sigma}_2}, \ldots, T^{(M)}_{\boldsymbol{\sigma}_M}\}$ is a set of tensors as the inputs,
+    and $\boldsymbol{\sigma}_o$ is a string of labels for the output tensor.
+    Each $T^{(k)}_{\boldsymbol{\sigma_k}} \in \mathcal{T}$ is labelled by a string of labels $\boldsymbol{\sigma}_k \in \Sigma^{r(T^{(k)})}$, where $r(T^{(k)})$ the rank of $T^{(k)}$.
+    The multi-linear map or the \emph{contraction} on this triple is
+    \begin{equation}
+        O_{\boldsymbol{\sigma}_o} = \sum_{\Sigma \setminus \sigma_o} \prod_{k=1}^{M} T^{(k)}_{\boldsymbol{\sigma_k}},
+    \end{equation}
+    where the summation runs over all possible configurations over the set of labels absent in the output tensor.
 \end{definition}
-The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
-For example, the matrix multiplication is a special tensor network
-\begin{equation}
-\mathcal{N}_{\rm matmul} = \left(\{i,j,k\}, \{A_{ij}, B_{jk}\}, C_{ik}\right),
-\end{equation}
-where $A, B$ and $C$ are matrices (two-dimensional tensors), among which $C$ is the output tensor, $(i,k),(i,j)$ and $(i,k)$ are labels associated with them.
-The contraction is defined as $C_{ik} = \sum_j A_{ij}B_{jk}$, where the subscripts are for tensor indexing, and the tensor dimensions with a same label must have the same size.
+%The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
+For example, the matrix multiplication can be specified as a tensor network
+\begin{equation}
+\mathcal{N}_{\rm matmul} = \left(\{i,j,k\}, \{A_{ij}, B_{jk}\}, ik\right),
+\end{equation}
+where $A_{ij}$ and $B_{jk}$ are input matrices (two-dimensional tensors), and $(i,k)$ are labels associated to the output.
+The contraction is defined as $O_{ik} = \sum_j A_{ij}B_{jk}$, where the subscripts are for tensor indexing, and the tensor dimensions with a same label must have the same size.
 %can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
@@
 \begin{example}
-\blue{maybe remove this example?}
 \begin{equation}
@@
     \mathcal{T} &= \{A_{jkm}, B_{mil}, V_{jm}\},\\
-    O &= C_{ijk},\\
+    \boldsymbol{\sigma}_o &= ijk,\\
     \end{split}
 \end{equation}
-is a tensor network that can be evaluated as $C_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
+is a tensor network that can be evaluated as $O_{ijk} = \sum_{ml}A_{jkm} B_{mil} V_{jm}$.
 Its hypergraph representation is shown below, where we use different colors to represent different hyperedges.
@@
     \Sigma &= \{s_v \mid v \in V\},\\
-    \mathcal{T} &= \{W^{(v)}_{v} \mid v\in V\} \cup \{B^{(u, v)}_{uv} \mid (u, v) \in E\},\\
-    O &= P,
+    \mathcal{T} &= \{W^{(v)}_{s_v} \mid v\in V\} \cup \{B^{(u, v)}_{s_us_v} \mid (u, v) \in E\},\\
+    \boldsymbol{\sigma}_o &= \varepsilon,
     \end{split}
@@
 These labels can be used as subscripts of tensors to index tensor elements, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$, where $x_v$ is a variable associated with vertex $v$.
-$P$ is the output tensor of rank $0$, i.e. a scalar.
+The labels associated to the output tensor is an empty string $\varepsilon$, meaning this tensor has rank $0$, i.e. a scalar.
 The independence constraint is encoded in the edge tensors, where we use $B_{11} = 0$ to denote two vertices connected by an edge cannot be both in the independent set. 
@@
 \begin{example}\label{eg:tensorcontraction}
-\blue{maybe remove this example too?}
 In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
@@
 To avoid potential confusion, let us denote the additive identity as $\mymathbb{0}$, and the multiplicative identity is $\mymathbb{1}$.
-The algebra between the polynomials number $a$ of order $k_a$ and $b$ of order $k_b$ is defined as
+The algebra between the polynomials number $a$ of order $k_a$ and $b$ of order $k_b$ is specified as
 \begin{equation}
@@
 Recall that in the definition of a vertex tensor in \Cref{eq:vertextensor}, variables carry labels, so that one can read out all independent sets directly from the output polynomials.
-The multiplication between labeled variables is commutative while the summation of labeled variables forms a set.
-Intuitively, one can use a bit string as the representation of a labeled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
+The multiplication between labelled variables is commutative while the summation of labelled variables forms a set.
+Intuitively, one can use a bit string as the representation of a labelled variable and use the bit-wise or $\lor^\circ$ as the multiplication operation.
 For example, in a 5-vertex graph, $x_2$ and $x_5$ can be represented as $01000$ and $00001$ respectively and their multiplication $x_2x_5$ can be represented as $01000 \lor^\circ 00001 = 01001$.
@@
 A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
-The corresponding tensor network $\mathcal{N}_{\rm mIS}(G)$ can be defined as
+The corresponding tensor network $\mathcal{N}_{\rm mIS}(G)$ can be specified as
 \begin{equation}\label{eq:maxistensornetwork}
@@
     \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)} s_{N(v, 2)}\ldots s_{N(v,d(v))}s_v} \mid v\in V\},\\
-    O &= P,\\
+    \boldsymbol{\sigma}_o &= \varepsilon,\\
 \end{split}
@@
 We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
-The tensor network representation for the matching problem $\mathcal{N}_{match}$ can be defined as
+The tensor network representation for the matching problem $\mathcal{N}_{match}$ can be specified as
 \begin{equation}\label{eq:matchtensornetwork}
@@
     \mathcal{T} &= \{W^{(v)}_{\langle v, N(v, 1)\rangle \langle v, N(v,2) \rangle \ldots \langle v, N(v, d(v))\rangle} \mid v\in V\} \cup \{B^{(u, v)}_{\langle u,v\rangle} \mid (u, v) \in E\},\\
-    O &= P,
+    \boldsymbol{\sigma}_o &= \varepsilon,
 \end{split}
@@
 We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
-The tensor network for the vertex coloring problem $\mathcal{N}_{3-color}(G)$ can be formally defined as
+The tensor network for the vertex coloring problem $\mathcal{N}_{3-color}(G)$ can be specified as
 \begin{equation}\label{eq:colortensornetwork}
@@
     \mathcal{T} &= \{W^{(v)}_{c_v} \mid v\in V\} \cup \{B^{(u, v)}_{c_uc_v} \mid (u, v) \in E\},\\
-    O &= P,\\
+    \boldsymbol{\sigma}_o &= \varepsilon,\\
 \end{split}
 \end{equation}
-where for each vertex $v \in V$, we define a tensor labeled by $c_v$
+where for each vertex $v \in V$, we define a tensor labelled by $c_v$
 \begin{equation}
@@
 To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-The tensor network representation for the cutting problem $\mathcal{N}_{cut}$ can be formally defined as
+The tensor network representation for the cutting problem $\mathcal{N}_{cut}$ can be specified as
 \begin{equation}\label{eq:cuttensornetwork}
@@
     \Sigma &= \{s_v \mid v \in V\},\\
-    O &= P,\\
+    \boldsymbol{\sigma}_o &= \varepsilon,\\
 \end{split}
 \end{equation}
-where for each edge $(u,v)\in E$, we define an edge matrix labeled by $(s_u, s_v)$ as
+where for each edge $(u,v)\in E$, we define an edge matrix labelled by $(s_u, s_v)$ as
 \begin{equation}
@@
 To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
-The tensor network for the dominating set problem $\mathcal{N}_{dom}$ can be formally defined as
+The tensor network for the dominating set problem $\mathcal{N}_{dom}$ can be specified as
 \begin{equation}\label{eq:domtensornetwork}
@@
     \Sigma &= \{s_v \mid v \in V\},\\
-    \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)}s_{N(v, 2)} \ldots s_{N(v,d(v))}, s_v} \mid v\in V\},\\
-    O &= P,\\
+    \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)}s_{N(v, 2)} \ldots s_{N(v,d(v))} s_v} \mid v\in V\},\\
+    \boldsymbol{\sigma}_o &= \varepsilon,\\
 \end{split}
@@
 $s_v = 0$ stands for variable $v$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
-% For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labeled by $(s_a, s_b, s_c)$.
+% For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labelled by $(s_a, s_b, s_c)$.
 % \begin{equation}
@@
 % where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied. The tensor network representation is
-The tensor network $\mathcal{N}_{CNF}$ can be formally defined as
+The tensor network $\mathcal{N}_{CNF}$ can be specified as
 \begin{equation}\label{eq:sattensornetwork}
@@
     \Sigma &= \{s_v \mid v \in V\},\\
-    \mathcal{T} &= \{W^{(v)}_v \mid v \in V\} \cup \{T^{(k)}_{s_{N(k,1)} s_{N(k, 2)} s_{N(k,3))}} \mid k=1,\ldots,M\},\\
-    O &= P,\\
+    \mathcal{T} &= \{W^{(v)}_v \mid v \in V\} \cup \{T^{(k)}_{s_{N(k,1)} s_{N(k, 2)}\ldots s_{N(k,d(k)))}} \mid k=1,\ldots,M\},\\
+    \boldsymbol{\sigma}_o &= \varepsilon,\\
 \end{split}
@@
 T^{(k)}_{s_{N(k, 1)} s_{N(k, 2)} \ldots s_{N(k, d(k))}} = \begin{cases}
-    x^{}, &C^{(k)} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
+    x^{w_k}, &C^{(k)} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
     1, &{\rm otherwise}
@@
     \mathcal{T} &= \{B^{(v)}_{s_{N(v, 1)} \ldots s_{N(v, d(v))}} \mid v\in V\} \cup \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\},\\
-    O &= P,
+    \boldsymbol{\sigma}_o &= \varepsilon,
 \end{split}
@@
 To get the generic tensor network representation, we first map a set $\sigma \in S$ to a Boolean degree of freedom $s_\sigma\in\{0, 1\}$.
-Then the tensor network representation for the set covering problem $\mathcal{N}_{pack}$ can be expressed as
+Then the tensor network representation for the set covering problem $\mathcal{N}_{pack}$ can be specified as
 \begin{equation}\label{eq:covertensornetwork}
@@
     \mathcal{T} &= \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\} \cup \{B^{(v)}_{s_{N(v, 1)}s_{N(v, 2)}\ldots s_{N(\sigma, d(v))}} \mid v \in V\},\\
-    O &= P,
+    \boldsymbol{\sigma}_o &= \varepsilon,
 \end{split}
@@
 we first reduce the problem to finding the back-propagation rule of a tropical matrix multiplication $C = A B$.
-Since $ C_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
+Since $ O_{ik} = \bigoplus_{j} \ A_{ij} \odot B_{jk} = \max_{j} \ A_{ij} \odot B_{jk}$ with tropical algebra, we have the following inequality
 \begin{equation}

### 2022-09-23 paper/paper.tex
Updates from Overleaf

@@
 
-% REQUIRED
-% 14N07  	Secant varieties, tensor rank, varieties of sums of powers
 \begin{AMS}
@@
 An important class of problems in graph theory and combinatorial optimization  can be formulated as satisfiability problems involving constraints specified over a vertex and its neighborhood.
-These include, for example, the independent set, the cutting problem, the dominating set, the set packing and  the set covering, the vertex coloring problem, the K-SAT,  the clique problem, and the vertex cover problem~\cite{Moore2011}.
+These problems include, for example, the independent set problem, the cutting problem, dominating set, set packing, set covering, vertex coloring, K-SAT,  the clique problem, and the vertex cover problem~\cite{Moore2011}.
 These problems have a wide range of applications in scheduling, logistics,
 wireless networks and telecommunication, and computer vision, among others~\cite{Butenko2003, Wu2015}.
-Finding an optimum solution for these problems is typically NP-hard~\cite{Hastad1996}.
-%, which implies they can not to be solved in a time that scales polynomialy  with the size of the problem.
-
-% The most studied aspect of these problems is to find an optimum solution, 
-%The most studied version of the above problems is finding an optimal solution maximum/minimum set satisfying the contraints and the corresponding set size,
-% which is typically 
-%while many of them belong to the hardness category
-% NP-hard~\cite{Hastad1996}, i.e.\ it is unlikely to be solved in a time polynomial with the size of the problem.
-
-% Many properties of these problems are in general intractable at large sizes (exponential run time in problem size in the worst case),
- %but it is nevertheless desirable to have high-performance algorithms because of their ubiquitous applications~\cite{Butenko2003, Wu2015}.
-
-%\purple{Is MIS really the most studied NP-hard optimization problem? I would guess it is heavily studied, but not necessarily the most studied.}
-%\blue{Here, we haven't mentioned the independent set, here ``version'' means, e.g.
-counting, enumeration, devision.
-I think finding one of the largest/smallest set and its cardinality in the above mentioned problems is the most studied?}
+Finding an optimum solution for these problems is typically NP-hard in the worst case~\cite{Hastad1996}.
 
@@
 However, these properties can be crucial for understanding detailed properties of hard combinatorial optimization problems.
-% In this paper, we focus on the less studied aspects of computing \textit{solution space properties}, which can be much harder to compute, %; for example, counting independent sets of a general graph is \#P-complete~\cite{Vadhan2001},
-% but they can be crucial towards understanding hard combinatorial optimization problems. 
-These \textit{solution space properties} can include not only the maximum or minimum set size but also the number of sets at a given size, enumeration of all sets at a given size, and direct sampling of such sets when they are too large to be fit into memory.
-% For the weighted version of the above problems, it also includes finding the largest or smallest $k$ sets and their sizes.
-%are many interesting and hard computational problems concerning various properties of independent sets.
-%Solution space property computation allows us to understand the solution space better.
+For example, for the independent set problem, these \textit{solution space properties} can include not only the maximum or minimum independent set size but also the number of sets at a given size, enumeration of all sets at a given size, and direct sampling of such sets when they are too large to be fit into memory.
 They can be used to understand the hardness of finding an optimum solution for a given problem instance and the performance of a specific solver.  
-%in computing the solution for the given instance.
 For example, the number of configurations at different sizes can inform how likely a simulated annealing algorithm will be trapped in local minima at certain sizes~\cite{Xu2018}.
-%In the past, people use the counting of configurations at different sizes to tell how likely the simulated annealing will be trapped in certain size in the strong defensive alliance problem~\cite{Xu2018},
 The pair-wise Hamming distance distribution of configurations at a given size can indicate the presence or absence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, which can be used to bound the performance of local optimization algorithms.
-%a no-go theorem about when the solution space geometry is formidably
-%hard for any local search algorithm.
 In a recent experiment based on a Rydberg atom array quantum computer, 
-%the authors use 
-the counting and the configuration space connectivity information was used to find maximum independent set (MIS) problem instances that are hard for simulated annealing and to evaluate the corresponding quantum algorithm performance \cite{Ebadi2022}.
-% In a recent experiment using a Rydberg atom array quantum simulator to find maximum independent sets (MIS) of a graph~\cite{Ebadi2022}, the authors use the counting information and the configuration space connectivity to find instances hard for simulated annealing.
-%and design better quantum algorithms
-%to solve these instances faster, 
-The need for understanding these important aspects of combinatorial optimization motivates us to find methodologies to compute these solution space properties.
-%\purple{I would give examples of why we want to compute solution space properties.
-%For instance, in statistical physics, computing thermal states and
-%observables via the partition function. In complexity theory, proving limits on local algorithms (OGP).}\blue{now?}
+the counting and the configuration space connectivity information was used to find maximum independent set (MIS) problem instances that are hard for simulated annealing and to evaluate the corresponding quantum algorithm performance~\cite{Ebadi2022}.
+The need to understand these important aspects of combinatorial optimization motivates us to find methodologies to compute these solution space properties.
 
@@
 \textit{generic tensor networks}.
-Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014} and mathematics~\cite{Oseledets2011}.
+Tensor networks are a computational model widely used in condensed matter physics~\cite{Orus2014}, quantum computing~\cite{Markov2008}, big data~\cite{Cichocki2014}, mathematics~\cite{Oseledets2011} and combinatorial optimization~\cite{Biamonte2015, Biamonte2017,Kourtis2019}.
 They are also known as the sum-product networks in probabilistic modeling~\cite{Bishop2006} or \texttt{einsum} in linear algebra libraries such as NumPy~\cite{Harris2020}.
-%\purple{I’d write out $2^{{\rm tw}(G)}$}\blue{I feel it is hard to explain line graph without texts.}
 Recent progress in simulating quantum circuits with tensor networks~\cite{Gray2021, Pan2021, Kalachev2021} makes it possible to contract a randomly structured sparse tensor network with up to thousands of tensors in a reasonable time.
-%\purple{Is the scaling of these algorithms known?}\blue{They are not exact algorithms, the time can be any, typically a few minutes, will it be helpful to mention this?}
 In previous studies, the data types of the tensor elements are typically restricted to standard number types such as real numbers and complex numbers.
 Here, we extend to \textit{generic tensor networks} by generalizing the tensor element data types to any type that has the algebraic structure of a commutative semiring.
-%These two algorithms are related but are not equivalent.
-%Dynamic programming is more general purpose, while a tensor network has a richer algebraic structure, and this structure is crucial for solution space property computation.
-%\purple{Not clear how first part and second part of sentence are related}\blue{now? or maybe just removing the comparison with dynamic programming?}
-%For sparse graphs, the treewidth is usually much smaller than the number of vertices~\cite{Fomin2006}.
-Our algorithms, on the other hand, are much more versatile than traditional methods and can be used to compute many other properties than just the MIS size.
-%The independent set problem is related to physics applications such as in the hard-core lattice gas model~\cite{Dyre2016, Fernandes2007}
-%in statistical mechanics and the Rydberg hamiltonian with neutral atoms~\cite{Pichler2018, Ebadi2022};
-%Property computation can, for example, be used to understand phase transitions~\cite{Dyre2016, Fernandes2007},
-%to identify harder graphs in an ensemble of graphs~\cite{Ebadi2022} and to analyze the presence of the overlap gap property~\cite{Gamarnik2013, Gamarnik2019} related to the clustering phenomenon of large independent sets.
-%However, there is a lack of general and versatile tool to compute these different properties of independent sets.
-%To keep the discussion focused, 
 In what follows, for clarity of presentation, we focus on the independent set problem in the main text, and show how to compute the solution space properties for other combinatorial optimization problems in \Cref{sec:otherproblems}.
-The latter include cutting, matching, vertex coloring, satisfiability,  dominating set,  set packing,  set covering, and the clique problem.
-%\xpurple{More details on which combinatorial optimization problems this applies to?}
+The latter includes cutting, matching, vertex coloring, satisfiability,  dominating set,  set packing,  set covering, and the clique problem.
 
@@
 Subsequently, we explain how to engineer the element types to compute various solution space properties in \Cref{sec:counting}, \Cref{sec:enumeration}, and \Cref{sec:weighted}.
-% to count independent sets at a given size, enumerate/sample independent sets at a given size and find largest set sizes in weighted graphs, respectively.
-% by computing a number of independent set properties of certain sparse graphs on central processing units (CPUs) and graphics processing units (GPUs) and show its good performance.
 Lastly, we provide three example applications in \Cref{sec:examples} to demonstrate the versatility of our tool.
-A benchmark to demonstrate the performance of our algorithms can be found in both the \Cref{sec:benchmark} and the code repository.
-%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
-We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
-%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
-%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
-This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
-%Our method can also be used to find ``maximal'' independent set properties; 
-%a maximal independent set is an independent set that is not a subset of any other independent set, but its size may not be the maximum.
+A benchmark to demonstrate the performance of our algorithms can be found in both the \Cref{sec:benchmark} and the code repository~\cite{GenericTensorNetworks}.
 
@@
 \begin{definition}[Tensor Network~\cite{Cirac2021, Orus2014}]
-    A tensor network a multi-linear map specified by a triple of $\mathcal{N} = (\Sigma, \Tensors, \boldsymbol{\sigma}_o)$,
-    where $\Sigma$ is an alphabet of labels,
+    A tensor network is a multi-linear map specified by a triple of $\mathcal{N} = (\Lambda, \Tensors, \boldsymbol{\sigma}_o)$,
+    where $\Lambda$ is a set of symbols (or labels),
     $\Tensors = \{T^{(1)}_{\boldsymbol{\sigma}_1}, T^{(2)}_{\boldsymbol{\sigma}_2}, \ldots, T^{(M)}_{\boldsymbol{\sigma}_M}\}$ is a set of tensors as the inputs,
-    and $\boldsymbol{\sigma}_o$ is a string of labels for the output tensor.
-    Each $T^{(k)}_{\boldsymbol{\sigma_k}} \in \mathcal{T}$ is labelled by a string of labels $\boldsymbol{\sigma}_k \in \Sigma^{r(T^{(k)})}$, where $r(T^{(k)})$ the rank of $T^{(k)}$.
-    The multi-linear map or the \emph{contraction} on this triple is
-    \begin{equation}
-        O_{\boldsymbol{\sigma}_o} = \sum_{\Sigma \setminus \sigma_o} \prod_{k=1}^{M} T^{(k)}_{\boldsymbol{\sigma_k}},
-    \end{equation}
-    where the summation runs over all possible configurations over the set of labels absent in the output tensor.
+    and $\boldsymbol{\sigma}_o$ is a string of symbols labelling the output tensor.
+    Each $T^{(k)}_{\boldsymbol{\sigma_k}} \in \mathcal{T}$ is labelled by a string $\boldsymbol{\sigma}_k \in \Lambda^{r \left(T^{(k)} \right)}$, where $r \left(T^{(k)} \right)$ is the rank of $T^{(k)}$.
+    The multi-linear map or the \textbf{contraction} on this triple is
+    \begin{equation}
+        O_{\boldsymbol{\sigma}_o} = \sum_{\Lambda \setminus \sigma_o} \prod_{k=1}^{M} T^{(k)}_{\boldsymbol{\sigma_k}},
+    \end{equation}
+    where the summation runs over all possible configurations over the set of symbols absent in the output tensor.
 \end{definition}
-%The operation to evaluate a tensor network is called \textit{contraction}, which is defined as a summation of tensor element products over the labels not appearing in the output tensor.
 For example, the matrix multiplication can be specified as a tensor network
@@
 where $A_{ij}$ and $B_{jk}$ are input matrices (two-dimensional tensors), and $(i,k)$ are labels associated to the output.
-The contraction is defined as $O_{ik} = \sum_j A_{ij}B_{jk}$, where the subscripts are for tensor indexing, and the tensor dimensions with a same label must have the same size.
-%can be viewed as a generalization of binary matrix multiplication to nary tensor contraction.
-%Generalized Einstein's notation is often used to represent a tensor network, where we use a label in the subscript to represent a degree of freedom.
-%One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-% Einstein's notation is often used to represent a tensor network, e.g.\ it represents the matrix multiplication between two matrices $A$ and $B$ as $C_{ik} = A_{ij}B_{jk}$,
-% where we use a label in the subscript to represent a degree of freedom.
-% One can enumerate these degrees of freedom and accumulate the product of tensor elements to the output tensor.
-% In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice, either both in input tensors (which will be summed over) or one in a input tensor and another in the output tensor.
-% Hence a tensor network can be represented as a open simple graph,
-% where a tensor is mapped to a vertex, a label shared by two input tensors is mapped to a normal edge and a label appears in the output tensor is mapped to an open edge.
-% In this work, we adopt a more general form of tensor networks that do not restrict how many times a label can appear in tensors. 
-The graphical representation of a tensor network is an open (meaning an edge can connect to external vertices) hypergraph, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are open.
-Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors. 
+The contraction is defined as $O_{ik} = \sum_j A_{ij}B_{jk}$, where the subscripts are for tensor indexing, and the tensor dimensions with the same label must have the same size.
+The graphical representation of a tensor network is an open hypergraph that having open hyperedges, where an input tensor is mapped to a vertex and a label is mapped to a hyperedge that can connect an arbitrary number of vertices, while the labels appearing in the output tensor are mapped to open hyperedges.
+Our notation is a minor generalization of the standard tensor network notation used in physics as we do not restrict the number of times a label can appear in the tensors to two. 
 While this generalized form is equivalent in representation power, it can have smaller contraction complexity as will be illustrated in \Cref{sec:tensorbad}.
-% because one can easily translate a generalized tensor network to the standard notation by adding $\delta$ tensors, a high dimensional equivalence of the identity matrix.
-%However, introducing $\delta$ tensors may significantly increase the complexity of the tensor contraction. We illustrate this subtle point in \Cref{sec:tensorbad}.
 
@@
 \begin{split}
-    \Sigma &= \{i,j,k,l,m\},\\
+    \Lambda &= \{i,j,k,l,m\},\\
     \mathcal{T} &= \{A_{jkm}, B_{mil}, V_{jm}\},\\
@@
 \section{Generic programming tensor contractions}\label{sec:generic}
-%\purple{On a second read of this section, I think that the clarity could be improved.
-My understanding is this is the flow: We would like to use generic programming, where we write code that works regardless of input type, and is optimized on all input types without sacrificing efficiency.
-In general, we can write code such that a function runs correctly regardless of the input data type.
-This is easy to do for dynamically typed languages like Python, which only verify and enforce the rules for the input data type at run time (called type-checking).
-However, when the input data type is only checked at run time (as opposed to when the code is compiled), type-specific optimization cannot be used.
-High efficiency is only achieved in statically typed languages, where modern compiling technology allows the function to be individually optimized for each input data type (then give C++/Julia examples).}\blue{how about now?}
-In previous works relating tensor networks and combinatorial problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
-%Owning to the development of modern compiling technology, we no longer need to restrict our imagination to standard number types.
-%However, the elements in a tensor do not have to be a regular number type, or even a field (since division is not used in tensor contraction).
-%One can use the same tensor contraction program for different purposes with different tensor element types.
-% We propose to not restricting our imagination to standard number types, but to use a more general element type with certain algebraic property.
+In previous works relating tensor networks and combinatorial optimization problems~\cite{Kourtis2019, Biamonte2017}, the element types in the tensor networks are limited to standard number types such as floating-point numbers and integers.
 We propose to use more general element types with a certain algebraic property.
@@
 By the most general setting, we mean that a single program should work correctly for the most general input data types. 
-%\purple{I think the following paragraph could be clarified.
-When you read the definition of generic programming, it's not clear what ``in the most general setting'' means.
-My understanding is it just means that the program will work regardless of the input data type - it would be good to say this explicitly.
-}
-%\blue{This definition is from the book I cited, I also do not like ``in the most general setting'', maybe we just use our version?}
-%\purple{I also think the way it is written takes a while to understand what dynamically versus statically typed languages are.
-The definition, “When these languages “see” a new input type, the compiler can recompile the generic program for the new type.” comes rather late in the paragraph.}
-%\xpurple{Also, while I know what you mean, concepts like “inlining immutable elements” and “cache miss rate” would be
-%lost on someone only with a physics background.}
-%This definition of generic programming contains two major aspects: a single program works in the most general setting and efficiency.
-%To understand the first aspect on generality,
 For example, suppose we want to write a function that raises an element to a power, $f(x, n) := x^n$.
@@
 We find that as long as the tensor elements are members of a commutative semiring, the tensor network contraction will be well defined and the result will be independent of the contraction order.
-Compared to a field, a commutative semiring does not need not to have an additive inverse and a multiplicative inverse.
+In contrast with a field, a commutative semiring does not need not to have an additive inverse and a multiplicative inverse.
 Giving up these nice properties of fields has significant implications for tensor computation: tensor network compression algorithms might not be applicable because matrix factorization is NP-hard for commutative semirings~\cite{Shitov2014} and matrix multiplication faster than $O(n^3)$ does not exist for an algebra without an additive inverse~\cite{Kerr1970}.
 Here, we only use the commutative properties of an algebra for optimizing the tensor network contraction order.
-To define a commutative semiring with the addition operation $\oplus$\footnote{The $\oplus$ operator in the main text means the generic addition, which different from the logical \texttt{XOR} in computer science} and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
+To define a commutative semiring with the addition operation $\oplus$\footnote{We use the $\oplus$ operator throughout this paper to denote the generic addition, which is not the logical \texttt{XOR} operation, in which the symbol typically represents in computer science.} and the multiplication operation $\odot$ on a set $S$, the following relations must hold for any arbitrary three elements $a, b, c \in S$.
 \begin{align*}
@@
 \end{align*}
-%We require the algebra being multiplicative commutative because the contraction order optimizer will change the multiplication order of elements, while we require that the contraction order does not change the contraction results.
 In the following sections, we will show how to compute solution space properties of independent sets using the same tensor network contraction algorithm by engineering tensor element algebra.
@@
 An alternative interpretation, perhaps more accessible to physicists, can be found in \Cref{sec:energymodel}, where we introduce the reduction from the energy model of hardcore lattice gases~\cite{Dyre2016, Fernandes2007}.
-Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a weight $w_v$.
-An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$.
-To the independent set problem on $G$ can be encoded as a tensor network $\mathcal{N}_{\rm IS}(G)$
+Let $G=(V,E)$ be an undirected graph with each vertex $v\in V$ being associated with a integer weight $w_v$.
+An independent set $I \subseteq V$ is a set of vertices that for any vertex pair $u,v \in I$, we have $(u, v) \not\in E$; we refer to this constraint as the independence constraint. 
+The independent set problem on $G$ can be encoded as a tensor network $\mathcal{N}_{\rm IS}(G)$
 \begin{equation}\label{eq:mistensornetwork}
 \begin{split}
-    \Sigma &= \{s_v \mid v \in V\},\\
+    \Lambda &= \{s_v \mid v \in V\},\\
     \mathcal{T} &= \{W^{(v)}_{s_v} \mid v\in V\} \cup \{B^{(u, v)}_{s_us_v} \mid (u, v) \in E\},\\
@@
 \end{equation}
-and for each edge $(u, v) \in E$, we define a matrix $B$ indexed by $s_u$ and $s_v$ as
+and for each edge $(u, v) \in E$, we define a matrix $B$ as
 \begin{equation}
     \qquad \quad 
-       B^{(u, v)} = \left(\begin{matrix}
+       B^{(u,v)} = \left(\begin{matrix}
         1  & 1\\
@@
 \end{equation}
-We map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$ of dimension $2$, where we use $0$ ($1$) to denote a vertex is absent (present) in $I$.
-%We use the superscripts to denote which vertex or edge a tensor is associated to.
-These labels can be used as subscripts of tensors to index tensor elements, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$, where $x_v$ is a variable associated with vertex $v$.
-The labels associated to the output tensor is an empty string $\varepsilon$, meaning this tensor has rank $0$, i.e. a scalar.
-The independence constraint is encoded in the edge tensors, where we use $B_{11} = 0$ to denote two vertices connected by an edge cannot be both in the independent set. 
+We map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$, where we use $0$ or $1$ to denote a vertex is absent or present in $I$, respectively.
+These labels can be used as subscripts of tensors to index tensor elements, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$, where $x_v$ is an  element of some commutative semiring (e.g., listed in \Cref{tbl:generictypes}) associated with vertex $v$ and its power with an integer is defined by repeated multiplication.
+The labels associated to the output tensor is an empty string $\varepsilon$, meaning this tensor has rank $0$, i.e.~a scalar.
+The independence constraint is encoded in the edge tensors, where we use $B^{(u, v)}_{11} = 0$ to denote two vertices connected by an edge $(u, v)$ cannot be both in the independent set. 
 The contraction of this tensor network is
@@
 where the summation runs over all $2^{|V|}$ vertex configurations $\{s_1, s_{2}, \ldots,s_{|V|}\}$ and accumulates the product of tensor elements to the output $P$. 
-% It is easy to see that an edge tensor element $B_{s_us_v}$ encodes the independent set constraint. It zeros out the product whenever both $u$ and $v$ are in the independent set.
 A vertex tensor element $W^{(v)}_{s_v}$ contributes a multiplicative factor $x_v^{w_v}$ whenever $v$ is in the set.
@@
 In the graphical representation of the tensor network on the right panel,
-we use a circle to represent a tensor, a hyperedge in cyan color to represent the degree of freedom $s_a$,
-and a hyperedge in red color to represent the degree of freedom $s_b$.
+we use a circle to represent a tensor, a cyan-colored hyperedge to represent the degree of freedom $s_a$,
+and a hyperedge in red to represent the degree of freedom $s_b$.
 Tensors sharing the same degree of freedom are connected by the same hyperedge.
@@
 \end{equation}
-The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$, and $\{b\}$, with weights being $0$, $w_a$, and $w_b$ respectively.
+The resulting polynomial represents 3 different independent sets $\{\}$, $\{a\}$, and $\{b\}$ with weights $0$, $w_a$, and $w_b$, respectively.
 \end{example}
@@
 \begin{proof}
-Let us denote the line graph, a graph obtained by mapping an edge in the original graph to a vertex and connect two vertices if and only if their associated edges in the original original graph share a common vertex, of the hypergraph representation of a tensor network $\mathcal{N}$ as $L(\mathcal{N})$.
+Let us denote the line graph, a graph obtained by mapping an edge in the original graph to a vertex and connect two vertices if and only if their associated edges in the original graph share a common vertex, of the hypergraph representation of a tensor network $\mathcal{N}$ as $L(\mathcal{N})$.
 A contraction order of $\mathcal{N}$ corresponds to a tree decomposition of $L(\mathcal{N})$ and the largest intermediate tensor has a rank equal to the width of its tree decomposition~\cite{Markov2008}.
 Therefore, an optimal (in terms of space complexity) contraction order corresponds to the tree decomposition of $L(\mathcal{N})$ with the smallest width (or the treewidth ${\rm tw}(L(\mathcal{N})$).
-The contraction complexity is $O(|\mathcal{N}|)2^{O({\rm tw}(L(\mathcal{N})))}$, where $|\mathcal{N}|$ is the number of tensors in $\mathcal{N}$.
+The contraction complexity is $O(|\mathcal{N}|)2^{O({\rm tw}(L(\mathcal{N})))}$, where $|\mathcal{N}|$ is the number of tensors in $\mathcal{N}$~\cite{Markov2008}.
 For the independent set problem on graph $G = (V, E)$, the line graph of the hypergraph representation of the tensor network in \Cref{eq:mistensornetwork} is the same as the graph $G$ up to some isolated vertices, hence the contraction complexity of this tensor network with an optimal contraction order is $O(|E|)2^{O({\rm tw}(G))}$.
@@
 In practice, it is difficult to find an optimal contraction order for large tensor networks because finding the treewidth is a well-known NP-hard problem.
-However, it is easy to find a close-to-optimal contraction order within typically a few minutes with a heuristic algorithm~\cite{Kourtis2019, Kalachev2021}.
-%The pairwise tensor contraction also makes it possible to utilize basic linear algebra subprograms (BLAS) functions to speed up the computation for certain tensor element types.
+However, it is easy to find a close-to-optimal contraction order within typically a few minutes using a heuristic algorithm~\cite{Kourtis2019, Kalachev2021}.
 For large-scale applications, it is also possible to slice over certain degrees of freedom to reduce the space complexity, i.e.\
-loop and accumulate over certain degrees of freedom so that one can have a smaller tensor network inside the loop due to the removal of these degrees of freedom.
+loop over possible combinations of certain degrees of freedom so that one can have a smaller tensor network inside the loop since these degrees of freedoms are fixed.
 
 \begin{example}\label{eg:tensorcontraction}
-In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how the contraction order reduces the time and space complexities.
+In this example, we map a 5-vertex graph (left) to a tensor network (right) and show how optimizing the contraction order reduces the time and space complexities.
 
@@
 \end{tikzpicture}}
-% \small{
-% \begin{align*}
-%     &\sum_{s_a,s_b,s_c,s_d,s_e} W(x_a, w_a)_{s_a} W(x_b, w_b)_{s_b} W(x_c, w_c)_{s_c} W(x_d, w_d)_{s_d} W(x_e, w_e)_{s_e} B_{s_a s_b} B_{s_b s_d} B_{s_c s_d} B_{s_a s_c} B_{s_b s_c} B_{s_d s_e}\\
-%     =&\sum_{s_b,s_c}\left(\sum_{s_d}\left(\left(\left(\left(\sum_{s_e}B_{s_d s_e}W(x_e,w_e)_{s_e}\right) W(x_d,w_d)_{s_d}\right) \left(B_{s_bs_d} W(x_b, w_b)_{s_b}\right)\right) \left(B_{s_cs_d} W(x_c, w_c)_{s_c}\right)\right)\right.\\
-%     &\phantom{XXX}\left.\left(B_{s_bs_c}\left(\sum_{s_a}B_{s_as_b}\left(B_{s_as_c}W(x_a,w_a)_{s_a}\right)\right)\right)\right)\\
-%     =&1 + x_a^{w_a} + x_b^{w_b} + x_c^{w_c} + x_d^{w_d} + x_e^{w_e} + x_a^{w_a}x_d^{w_d} + x_a^{w_a}x_e^{w_e} + x_c^{w_c}x_e^{w_e} + x_b^{w_b}x_e^{w_e}
-%     %=&1+5x+4x^2 \qquad \quad (x_{i} = x, w_{i}=1).
-% \end{align*}}
-The contraction process goes from bottom to top, where the root node stores the contraction result; the leaves are input tensors and the rest of the nodes are all intermediate contraction results.
+The contraction process goes from bottom to top, where the root node stores the contraction result, the leaves are input tensors, and the rest of the nodes are all intermediate contraction results.
 Tensor subscripts are indices so that the number of subscripts indicates the space complexity to store this tensor.
@@
 An independence polynomial is a useful graph characteristic related to, for example, the partition functions~\cite{Lee1952,Yang1952} and Euler characteristics of the independence complex~\cite{Bousquet2008, Levit2009}.
-%Its connection to \Cref{eq:idp} can be understood as follows: the product over vertex tensor elements produces a factor $x^k$, where $k=\sum_i s_i$ counts the set size,
-%and the product over edge tensor elements gives a factor $1$ for a configuration being in an independent set and $0$ otherwise. The summation counts the number of independent sets of size $k$. 
 By assigning a real number to $x$, one can evaluate this independence polynomial for this specific value directly using tensor network contraction.
@@
 However, instead of evaluating this polynomial for a certain value, we are more interested in knowing the coefficients of this polynomial, because this quantity tells us the counting of independent sets at different sizes.
-%first elevate the tensor elements $0$s and $1$s in tensors $W(x)$ and $B$ from the standard number types to the additive identity, $\mymathbb{0}$, and multiplicative identity, $\mymathbb{1}$, of a commutative semiring as discussed in \Cref{sec:generic}.
-%\purple{I'd
-%say that you're about to describe this semiring, otherwise it seems like you're going to
-%use the general definition of the semiring rather than a specific type of semiring}\blue{from $1$ to $\mymathbb{1}$ and $0$ to $\mymathbb{0}$ applies for a general semiring, I haven't change this part, let's discuss to make sure I understand your point.}\purple{Perhaps start the sentence with: Our semiring elements are a polynomial type...}
 To this end, let us create a polynomial number data type by representing a polynomial $a_0 + a_1 x + \ldots + a_k x^k$ as a coefficient vector $a = (a_0, a_1, \ldots, a_k) \in \mathbb{R}^k$, e.g.
@@
 Since $k$ is upper bounded by the maximum independent set size $\alpha(G) \leq |V|$, the time complexity of element-wise addition and multiplication operation is upper bounded by $|V|\log(|V|)$.
-Combining with \Cref{thm:complexreal}, the a overall time complexity is $O(|V|\log(|V|))\cc$.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|V|\log(|V|))\cc$.
 \end{proof}
@@
 and then apply the Gaussian elimination procedure to fit the coefficients of this polynomial.
-This seemingly more time and space-efficient approach suffer from precision issues in practice.
+However, in practice this seemingly more time and space-efficient approach suffers from precision issues.
 The data ranges of standard integer types are too small to cover many practical use cases,
@@
 
-% the purpose of discussion in the main text, let us stick to this less efficient polynomial algebra.
-
 \section{Maximum independent sets and its counting}\label{sec:counting}
@@
 \begin{theorem}\label{thm:complexrealnum}
-    Let $G = (V, E)$ be a graph, the total number independent sets of $G$ can be computed in time $\cc$.
+    Let $G = (V, E)$ be a graph. The total number independent sets of $G$ can be computed in time $\cc$.
 \end{theorem}
 \begin{proof}
-Let $x = 1$ be a real constant number, the independence polynomial in the previous section becomes
+Let $x = 1$ be a real constant number; the independence polynomial in the previous section becomes
 \begin{equation}
@@
 which corresponds to the total number of independent sets.
-Since the real number addtion and multiplication can be computed in $O(1)$ time,
+Since the real number addition and multiplication can be computed in $O(1)$ time, thus
 proving the theorem by \Cref{thm:complexreal}.
@@
 \subsection{Tropical algebra for finding the MIS size and counting MISs}
-%The method we use to count the MISs is based on the following observations:
 Let $x=\infty$, the independence polynomial in the previous section becomes
@@
 \begin{theorem}\label{thm:complextropical}
-    Let $G = (V, E)$ be a graph, its maximum independent set size $\alpha(G)$ can be computed in time $\cc$.
+    Let $G = (V, E)$ be a graph. Its maximum independent set size $\alpha(G)$ can be computed in time $\cc$.
 \end{theorem}
@@
 \end{theorem}
-The proof is similar to proving \Cref{thm:complexpoly}, except only $k$ largest coefficients are involved in the addition and multiplication.
+The proof is similar to the proof of \Cref{thm:complexpoly}, except only $K$ largest coefficients are involved in the addition and multiplication.
 
@@
 \begin{example}\label{eg:setalgebra}
-    For elements being bit strings of length $5$, we have the following set algebra
+    For elements that are bit strings of length $5$, we have the following set algebra
 \begin{equation*}
@@
 \begin{lemma}\label{thm:complexset}
-    The independent sets of graph $G = (V, E)$ be a graph can be enumerated in time $O(|I||V|)\cc$, where $|I|$ is the number of independent sets.
+    The independent sets of a graph $G = (V, E)$ can be enumerated in time $O\left(|I|*|V| \right)\cc$, where $|I|$ is the number of independent sets.
 \end{lemma}
 \begin{proof}
-To enumerate over $I$,  we initialize variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
+To enumerate over $I$,  we initialize the variable $x_{i}$ in the vertex tensor to $x_i = \{\boldsymbol{e}_{i}\}$, where $\boldsymbol{e}_i$ is a basis bit string of size $|V|$ that has only one non-zero value at location $i$.
 The vertex and edge tensors are thus
@@
 The contraction of this tensor network is a set with its elements being all independent set configurations.
-The time complexity of element-wise addition and multiplication is upper bounded by $|I||V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration.
-Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I||V|)\cc$.
-In practise, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
-This complexity only upper bounds the actually performance of the algorithm.
+The time complexity of element-wise addition and multiplication is upper bounded by $|I|*|V|$, where $|V|$ comes from the linear cost of representing a $|V|$-vertex configuration.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|I|*|V|)\cc$.
+In practice, the huge multiplicative factor $|I|$ only appear in the last step of tensor contraction.
+This complexity only serves as an upper bound for the actual performance of the algorithm.
 \end{proof}
@@
 \begin{lemma}\label{thm:complexmis}
-    Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be its maximum independent sets.
-    $I_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha||V|)\cc$.
+    Let $G = (V, E)$ be a graph and $\mathcal{I}_\alpha$ be the set of all maximum independent sets of $G$.
+    $\mathcal{I}_\alpha$ can be computed in time $O(|\mathcal{I}_\alpha|*|V|)\cc$.
 \end{lemma}
 \begin{proof}
-By replacing the tensor elements in \Cref{sec:tnmap} with the number type defined in \Cref{eq:countingtropicalset}, with variable $x_v^{w_v} = \{\boldsymbol{e}_{v}\}\infty^{w_v}$, the vertex tensor and edge tensor become
+By replacing the tensor elements in \Cref{sec:tnmap} with the number type defined in \Cref{eq:countingtropicalset} and with variable $x_v^{w_v} = \{\boldsymbol{e}_{v}\}\infty^{w_v}$, the vertex tensor and edge tensor become
 \begin{equation}
@@
 The enumeration of all MIS configurations corresponds to the contraction of this tensor network.
-The time complexity of element-wise addition and multiplication is upper bounded by the number of independent sets $|\mathcal{I}_\alpha|$.
-Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha||V|)\cc$.
+The time complexity of element-wise addition and multiplication is upper bounded by the number of maximum independent sets $|\mathcal{I}_\alpha|$.
+Combining with \Cref{thm:complexreal}, the overall time complexity is $O(|\mathcal{I}_\alpha|*|V|)\cc$.
 \end{proof}
@@
 One may also be interested in the more studied maximal independent sets~\cite{Bron1973, Eppstein2010, Johnson1988} enumeration.
-It will be discussed in \Cref{sec:maximal} since it requires using a different tensor network structure.
+We discuss this in \Cref{sec:maximal} since it requires using a different tensor network structure.
 
@@
     Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the set of independent sets with size $k$.
-    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
+    The independent sets with size $k > \alpha(G)-K$ of $G$ can be computed in time $O\left(|V|* \sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k| \right)\cc$.
 \end{lemma}
 \begin{proof}
-This can proved by combining the set algebra \Cref{eq:set} with the polynomial number truncated to largest $K$ orders (\Cref{eq:max2poly}).
+This can be proved by combining the set algebra \Cref{eq:set} with the polynomial number truncated to largest $K$ orders (\Cref{eq:max2poly}).
 The number of bitstring operations in the addition and multiplication of the joint algebra is upper bounded by the elements in the sets $\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|$.
-Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)\cc$.
+Combining with \Cref{thm:complexreal}, the overall time complexity of contracting this tensor network is $O\left(|V|* \sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|\right)\cc$.
 \end{proof}
@@
 By replacing the sets of bit strings in \Cref{eq:set} with a single bit string, we have the following algebra
-
 \begin{equation}
@@
 \begin{proposition}
-    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $O(|V|)\cc$.
+    Let $G = (V, E)$ be a graph. One of its maximum independent set can be computed in time $O(|V|)\cc$.
 \end{proposition}
@@
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, one of its maximum independent set can be computed in time $\cc$.
+    Let $G = (V, E)$ be a graph. One of its maximum independent set can be computed in time $\cc$.
 \end{theorem}
@@
     It can be numerically computed by differentiating over the process of the tropical tensor network contraction, where the backward rules can be found in \Cref{sec:bounding}.
-The time overhead of computing single optimal solution is constant comparing to only computing the contraction.
-Thus the computing time complexity should be the same as in \Cref{thm:complextropical}.
+The time overhead of computing a single optimal solution is constant compared to only computing the contraction.
+Thus, the computing time complexity should be the same as in \Cref{thm:complextropical}.
 \end{proof}
 
-\subsection{Sampling extremely large configuration space}
-When the problem scale becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
+\subsection{Sampling from the extremely large configuration space}
+When the problem size becomes larger, a set of all bitstrings might be impossible to fit into any type of storage.
 To get something meaningful out of the configuration space, we use a binary sum-product expression tree as a compact representation of a set of configurations, i.e.\ instead of directly computing a set using the algebra in \Cref{eq:set}, we store the process of computing it.
@@
 \begin{theorem}\label{thm:complexexpr}
-        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $\cc + O(|V||I|)$.
+        The independent sets $I$ of a graph $G=(V,E)$ can be enumerated in time $\cc + O(|V|*|I|)$.
 \end{theorem}
@@
 The contraction result of this tensor network corresponds to a sum-product expression tree for the set of independent sets.
-Unlike in \Cref{thm:complexset}, the contraction complexity is independent of the set size, i.e. the time complexity is $\cc$ by \Cref{thm:complexreal}.
-The time complexity to evaluating this expression tree is $O(|V||I|)$, where $|V|$ comes from the number of bits to represent a configuration.
+Unlike in \Cref{thm:complexset}, the contraction complexity is independent of the set size, i.e.~the time complexity is $\cc$ by \Cref{thm:complexreal}.
+The time complexity to evaluating this expression tree is $O(|V|*|I|)$, where $|V|$ comes from the number of bits to represent a configuration.
 Proving the theorem by adding two computing times.
@@
         Let $G = (V, E)$ be a graph and $\mathcal{I}_k$ be the number of independent sets with size $k$.
-The independent sets with size $k > \alpha(G)-K$ of can be computed in time $O(K\log K)\cc + O(|V|\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k|)$.
+The independent sets with size $k > \alpha(G)-K$ can be computed in time $O(K\log K)\cc + O\left(|V|*\sum_{k=\alpha(G)-K+1}^{\alpha(G)}|\mathcal{I}_k| \right)$.
 \end{corollary}
-Again, the theorem can be proved by relating it with its set algebra version in \Cref{thm:complexsetk}.
-Although likely, one cannot collect all configurations represented by a sum-product expression tree into a vector due to its extremely large configuration space,
-one can draw samples unbiasedly from it by direct sampling.
+Again, the theorem can be proven by relating it with its set algebra version in \Cref{thm:complexsetk}.
+Because it is unlikely that one can collect all configurations represented by a sum-product expression tree into a set due to its space complexity, one can also use this construction to produce unbiased samples of the sum-product tree.
+
 \begin{theorem}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $\cc + O(|V||E| M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph. Its independent sets with size $k > \alpha(G)-K$ can be unbiasedly sampled in time $\cc + O(|V|*|E| *M)$, where $M$ is the number of samples.
 \end{theorem}
@@
 Similar to the proof of \Cref{thm:complexexpr}, we first obtain a sum-product tree representation of the configurations in time $\cc$.
-Then we show to generate a sample, the cost is $O(|V||E|)$.
+Then we generate a sample using the following procedure with cost $O(|V|*|E|)$.
 The sampling program starts from the root node and descends this tree recursively to the left and right siblings.
@@
 
-The left and right siblings of the root node have sizes $|A|\times |B|$ and $|C|+|D|$ respectively, while the root node size can be computed as $|A|\times |B| + |C|+|D|$.
+The left and right siblings of the root node have sizes $|A| * |B|$ and $|C|+|D|$ respectively, while the root node size can be computed as $|A|* |B| + |C|+|D|$.
 The sizes of $A, B, C$, and $D$ can be computed recursively until the program meets either a \texttt{LEAF} node or a \texttt{ZERO} node, which has a known size of $1$ or $0$.
@@
 
-Since the depth of the expression tree is $O(|E|)$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V||E|)$.
-Proving the theorem.
+Since the depth of the expression tree is $O(|E|)$ and the cost of each arithmetic operation is $O(|V|)$, the overall time complexity to generate a sample is $O(|V|*|E|)$, hence proving the theorem.
 \end{proof}
@@
 \begin{corollary}
-    Let $G = (V, E)$ be a graph, its independent sets with size $k > \alpha(G)-K$ of can be unbiasedly sampled in time $O(K\log K)\cc + O(|V||E| M)$, where $M$ is the number of samples.
+    Let $G = (V, E)$ be a graph. Its independent sets with size $k > \alpha(G)-K$ can be unbiasedly sampled in time $O(K\log K)\cc + O(|V|*|E|*M)$, where $M$ is the number of samples.
 \end{corollary}
@@
 \begin{theorem}
-    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets sizes can be computed in time $O(K\log K)\cc$.
+    Let $G = (V, E)$ be a weighted graph. Its $K$ largest independent set sizes can be computed in time $O(K\log K)\cc$.
 \end{theorem}
 \begin{proof}
-$k$ largest independent sets can be computed by contracting a tensor network with extended tropical numbers. The vertex tensor and edge tensor are
+The $K$ largest independent sets can be computed by contracting a tensor network with extended tropical numbers. The vertex tensor and edge tensor are
 \begin{equation}
@@
 The computation of $s \odot t$ is a maximum sum combination problem that can be done in time $O(k\log(k))$ using the algorithm in \Cref{sec:maxsum}.
-Hence the overall time complexity of contracting the tensor network is $O(K\log K)\cc$.
+Hence, the overall time complexity of contracting the tensor network is $O(K\log K)\cc$.
 \end{proof}
@@
 \begin{corollary}
-    Let $G = (V, E)$ be a weighted graph, its $K$ largest independent sets can be computed in time $O(K\log K|V|)\cc$.
+    Let $G = (V, E)$ be a weighted graph. Its $K$ largest independent sets can be computed in time $O(|V|* K\log K)\cc$.
 \end{corollary}
-To find solutions corresponding to the largest $k$ sizes, one can combine the extended tropical algebra with the bit string algebra (\Cref{eq:singleconfig}).
+To find solutions corresponding to the largest $K$ sizes, one can combine the extended tropical algebra with the bit-string algebra (\Cref{eq:singleconfig}).
 Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
@@
 \section{Example applications} \label{sec:examples}
-%In this section, we give a few examples where the different properties of independence sets are used.
 
@@
 We compute the counting of all independent sets for graphs shown in \Cref{fig:lattices}, where vertices are all placed on square lattices of dimensions $L \times L$.
-The types of graphs include: the square lattice graphs (\Cref{fig:lattices}(a)); the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (\Cref{fig:lattices}(b));
-the King's graphs  (\Cref{fig:lattices}(c)); the King's graphs with a filling factor $p = 0.8$  (\Cref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
+The types of graphs include: the square lattice graphs (\Cref{fig:lattices}(a)), the square lattice graphs with a filling factor $p=0.8$, which means $\lfloor pL^{2} \rceil$ sites are occupied with vertices  (\Cref{fig:lattices}(b)),
+the King's graphs  (\Cref{fig:lattices}(c)), the King's graphs with a filling factor $p = 0.8$  (\Cref{fig:lattices}(d)), which is the ensemble of graphs used in Ref.~\cite{Ebadi2022} to benchmark quantum algorithms on a Rydberg atom array quantum computer.
 
@@
 Interestingly, the variations due to different random instances are negligible for this quantity.
-% \blue{@Shengtao We either keep this example simple by keeping only square and king's graphs, or explain better why we care about entropy constants at filling 0.8.}
 
@@
 It is known that finding MISs of a $d$-regular graphs has the overlap gap property~\cite{Rahman2017,Gamarnik2021} when both $d$ and the graph sizes are large, but, it is not known whether, for small $d$, e.g.\ for $3$-regular graphs, this statement remains true.
-We randomly generated $9$ instances for each category of King's graph at $0.8$ filling with size $20\times 20$ ($320$ vertices) and $3$-regular graphs with size $110$.
-At this problem size, independent sets are too many to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to directly sample from the target configuration space.
+We randomly generated $9$ instances for each category of King's graph at $0.8$ filling with dimensions $20\times 20$ ($320$ vertices) and $3$-regular graphs with $110$ vertices.
+At this problem size, there are too many independent sets to fit into any storage, hence we combine the truncated polynomial and sum-product expression tree to directly sample from the target configuration space.
 For each instance $G$, we sample $10^4$ pairs of configurations from the independent sets of sizes $\geq \lceil \gamma \times \alpha(G)\rceil$ and show the pair-wise Hamming distance distribution in \Cref{fig:hamming}.
@@
 \begin{figure} 
-    % \begin{subfigure}[t]{\textwidth}
-    %     \centering
-    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.1-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.05-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-diag-size20d3-k3-alpha0.025-n10000.pdf}
-    %     \caption{Nine King's graphs of size $20\times 20$, $0.8$ filling.}
-    % \end{subfigure}
-    % \begin{subfigure}[t]{\textwidth}
-    %     \centering
-    %     %\includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig3.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.1-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.05-n10000.pdf}
-    %     \includegraphics[width=0.3\textwidth, trim={0.5cm 0cm 0.5cm 1cm}, clip]{figures/grid-regular-size110d3-k3-alpha0.025-n10000.pdf}
-    %     \caption{Nine random three regular graphs of size $110$.}
-    % \end{subfigure}
     \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
@@
 
-%\subsection{Visualizing experimental quantum algorithm outputs for solving Maximum Independent Set}
 \subsection{Analyzing quantum and classical algorithms for Maximum Independent Set}
@@
     \caption{Visualization of experimental outputs of a quantum algorithm for solving the maximum independent set problem~\cite{Ebadi2022}.
-    Each vertex represents an independent set, and each edge represents a pair of independent sets that differ by a swap operation or a vertex addition.}
+    Each vertex represents an independent set, and each edge represents a pair of independent sets that differ by a swap operation or a vertex addition/removal.}
     \label{fig:exp_configuratoins}
@@
 This work focused on
-%, the authors found that
 exploring King's graphs with $0.8$ filling.
@@
 On the hardest graph instances for simulated annealing studied in the experiment, a high density of local minima were found at independent set sizes of $\alpha(G)-1,$ which the algorithm became trapped in instead of finding the optimal solution of size $\alpha(G)$.
-%Initially, it was suspected that simulated annealing trapped certain clusters of these local minima in the solution space. However, 
-By enumerating the configurations using techniques described in the present work, we found that %n found that there was no clustering in the solution space as in \Cref{sec:overlap-gap}, and instead 
+By enumerating the configurations using techniques described in the present work, we found that 
 simulated annealing randomly explores the independent sets of size $\alpha(G)-1$ until an optimum solution is found.
 Therefore, the large ratio of local to global minima  prevents simulated annealing from efficiently finding an MIS.
-%and studying the solution space properties for independent sets of size $\alpha(G)$ and $\alpha(G)-1$, we gained detailed insights to performance of both the quantum algorithm and simulated annealing, and could determine if these algorithm were likely to return independent sets from certain clusters of local or global minima in the solution space.
-Instead, we found that simulated annealing becomes trapped in independent sets of size $\alpha(G)-1$ uniformly at random, which is related to observation that there are no disconnected clusters in the solution space for King's graphs in \Cref{sec:overlap-gap}.
 
@@
 Each edge represents a pair of independent sets that differ by a swap operation or a vertex addition to the set, which are the operations naturally present in the effective dynamics at the end of the quantum algorithm.
-%The quantum algorithm either finds the MIS with size $\alpha(G)$ with high probability, or returns a suboptimal independent set, usually with size $\alpha(G)-1.$
 The solution space graph is well-connected by local changes to the spin configurations, has a small diameter, and the degree of each node appears to concentrate. 
 This visualization makes it clear that 
-%the authors inferred that 
-the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms e.g.
-by Ref.~\cite{altshuler2010}  which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
+the quantum algorithm does not appear to return solely local minima with a large Hamming distance from the MISs as suggested for adiabatic algorithms e.g.~by Ref.~\cite{altshuler2010}  which would appear as a long path on the solution space graph from the sampled local minima to the MIS.
 Instead, the quantum algorithm samples from local minima across the solution space graph with a wide range of Hamming distances from the MISs.
-In the case where a large superposition state of local minima is created during the coherent evolution, the quantum algorithm achieves a quadratic speedup over simulated annealing.
-%Consistent with \Cref{sec:overlap-gap}, there are no disconnected clusters in the solution space for this King's graph.
+In the case where a large superposition state of local minima is created during the coherent evolution, the quantum algorithm achieves a quadratic speedup over simulated annealing~\cite{Ebadi2022}.
 Looking forward, we expect these tools can be applied to understanding the performance of quantum and classical algorithms on a wide class of NP-hard combinatorial optimization problems.
@@
 In this work, we introduced a framework that uses generic tensor networks to compute different solution space properties of a certain class of NP-hard combinatorial optimization problems.
-%These solution space properties include the best several solutions, the number of solutions of a given size, and the enumeration and sampling of solutions of a given size.
 Each solution space property is computed using the same tensor network with different tensor element algebra.
-% This technique can further be generalized to computing solution space properties beyond the examples given in this paper.
-% such as the largest several independent sets sizes, the number of independent sets of a given size, and the enumeration of independent sets of a given size.
-%With different algebras, the contraction of the same tensor network gives us the different properties.
 The different data types introduced in the main text to compute these properties are summarized in the diagram in \Cref{fig:venn-diagram}.
 The class of problems solvable by a tensor network includes but is not limited to maximum independent sets and a variety of other combinatorial problems such as the matching problem, the k-coloring problem, the max-cut problem, the set packing problem, and the set covering problem, as detailed in \Cref{sec:otherproblems}.
-
-%Other than the case with real numbers, we have polynomials and truncated polynomials.
-%We combine them with the bit string algebra, the set algebra, and sum-product expression tree algebra for finding, enumerating, and sampling of independent sets at a given size.
-Three examples are shown to demonstrate how our method can be used to understand the solution space better.
-%In the first example, we show how our method can help computing the entropy constant for some hardcore lattice gases on 2D square lattices.
-We compute the 2D generalization of Fibonacci integer sequence up to size $39$, which is larger than the previous record $37$.
-%In the second example, we analyze the pairwise Hamming distances from configurations directly sampled from large independent sets of King's graphs at $0.8$ filling and three regular graphs.
-We show the strongest numeric evidence so far of the absence of overlap gap property in King's graph and the existence of Overlap Gap properties in three regular graphs.
-%In the last example, we show how our algorithm helps people to understand the performance of a quantum variational algorithms on Rydberg atom arrays to find maximum independent sets.
-This is a research frontier that understanding which can help people design better quantum algorithms to beat its classical counterpart.
 
@@
 It is also possible to extend this idea to other algebras.
-For example, generic semiring algebra has been used in computational linguishtics to compute interesting quantities of a given grammar and string.~\cite{Goodman1999}.
-%Moreover, since the independence polynomial is closely related to the matching polynomial~\cite{Levit2005}, the clique polynomial~\cite{Hoede1994}, and the vertex cover polynomial~\cite{Akbari2013},
-%our algorithm to compute the independence polynomial can also be used to compute these graph polynomials.
-%By adapting to the style of generic programming, we can implement all the algorithms without much effort.
-
-The source code in Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
+For example, generic semiring algebra has been used in computational linguistics to compute interesting quantities of a given grammar and string~\cite{Goodman1999}.
+
+The source code in the Julia language for this paper can be found in the Github repository~\cite{GenericTensorNetworks}. 
 There is a short introduction to this repository as well a gist to show how it works in \Cref{sec:technical} as well.
@@
 We also hope the toolkit we built, including tensor network contraction order optimization and efficient tropical matrix multiplication, can be helpful to the development of other scientific software.
-
-%We also hope this approach of generic tensor networks can inspire future works on tensor network computations.
 
@@
 Department of Energy (DE-SC0021013 and DOE Quantum Systems Accelerator Center (contract no.\ 7568717),
-%the Office of Naval Research, 
 the Army Research Office MURI.
@@
 In this section, we focus the discussion on the maximal independent sets problem since finding maximal cliques of a graph is equivalent to finding the maximal independent sets of its complement.
-Let $G=(V,E)$ be a graph, we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
+Let $G=(V,E)$ be a graph; we denote the neighborhood of a vertex $v\in V$ as $N(v)$.
 A maximal independent set $I_m$ is an independent set such that no $v \in V$ satisfies $I_m \cap (\{v\} \cup N[v])  = \emptyset$, i.e.\ an independent set that cannot become a larger one by adding a new vertex.
@@
 \begin{split}
-    \Sigma &= \{s_v \mid v \in V\},\\
+    \Lambda &= \{s_v \mid v \in V\},\\
     \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)} s_{N(v, 2)}\ldots s_{N(v,d(v))}s_v} \mid v\in V\},\\
@@
 \begin{theorem}\label{thm:miscomplex}
-    The tensor network representation of a maximal independent set problem on graph $G=(V,E)$ (\Cref{eq:maxistensornetwork}) can be contracted in $cc(\mathcal{N}_{mIS}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications, where $\Delta$ is the maximum degree of vertices in $G$.
+    The tensor network representation of a maximal independent set problem on a graph $G=(V,E)$ (\Cref{eq:maxistensornetwork}) can be contracted in $cc(\mathcal{N}_{mIS}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications, where $\Delta$ is the maximum degree of vertices in $G$.
 \end{theorem}
@@
     In the following, we will show given an optimal tree decomposition of $G$, it is always possible to include all cliques into the bags by increasing the bag size by a factor $(\Delta + 1)$.
-    Let $v \in V$ be a vertex and $N(v)$ be its neighborhood, we first arbitrarily pick an edge $u \in N(v)$,
+    Let $v \in V$ be a vertex and $N(v)$ be its neighborhood; we first arbitrarily pick an edge $u \in N(v)$,
     then by the definition of tree decomposition, we can find a bag containing this edge, and lastly we include all $N(v) \cup \{v\}$ into this bag.
@@
 
-%The contraction complexity of this tensor network is often greater than the one for the independence set problem.
 By contracting this tensor network with generic element types,
@@
 to our knowledge, the best algorithm has a time complexity $O(1.3642^{|V|})$~\cite{Gaspers2012}.
-%If we want to find an MIS, $b_{k}$ can, in some cases, provide hints on the difficulty of finding the MIS using local algorithms~\cite{Ebadi2022}.
-%The uni-modality, log-concavity, and real-rootness properties of the maximal independence polynomial for special classes of graphs have also been studied~\cite{Hu2017}.
 
@@
 We map an edge $(u, v) \in E$ to a degree of freedom $\langle u, v\rangle \in \{0, 1\}$ in a tensor network, where $1$ means an edge is in the set and $0$ otherwise.
-The tensor network representation for the matching problem $\mathcal{N}_{match}$ can be specified as
+The tensor network representation for the matching problem $\mathcal{N}_{\text{match}}$ can be specified as
 \begin{equation}\label{eq:matchtensornetwork}
 \begin{split}
-    \Sigma &= \{\langle u,v\rangle \mid (u, v) \in E\},\\
+    \Lambda &= \{\langle u,v\rangle \mid (u, v) \in E\},\\
     \mathcal{T} &= \{W^{(v)}_{\langle v, N(v, 1)\rangle \langle v, N(v,2) \rangle \ldots \langle v, N(v, d(v))\rangle} \mid v\in V\} \cup \{B^{(u, v)}_{\langle u,v\rangle} \mid (u, v) \in E\},\\
@@
 \end{equation}
-Here, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$, a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
+Here, $N(v, k)$ is the $k$th vertex in $N(v)$ and $d(v) = |N(v)|$ is the degree of vertex $v$; a label $\langle v, u \rangle$ is equivalent to $\langle u,v\rangle$.
 $W$ tensor specifies the constraint that a vertex cannot be shared by two edges in the edge set, and an edge tensor carries the weights.
@@
 \begin{theorem}\label{thm:matchcomplex}
-    The tensor network representation of a matching problem on graph $G=(V,E)$ (\Cref{eq:matchtensornetwork}) can be contracted in $cc(\mathcal{N}_{match}(G)) = O(|V|)2^{O({\rm tw}(L(G))}$ number of additions and multiplications, $L(G)$ is the line graph of $G$.
+    The tensor network representation of a matching problem on graph $G=(V,E)$ (\Cref{eq:matchtensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{match}}(G)) = O(|V|)2^{O({\rm tw}(L(G))}$ number of additions and multiplications, where $L(G)$ is the line graph of $G$.
 \end{theorem}
@@
 \end{proof}
-Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$, the tensor network contraction corresponds to the matching polynomial
+Let $x_{\langle u,v\rangle}^{w_{\langle u,v\rangle}}=x$; the tensor network contraction corresponds to the matching polynomial
 \begin{equation}
@@
 We first map a vertex $v \in V$ to a degree of freedom $c_v\in\{0,1,2\}$.
-The tensor network for the vertex coloring problem $\mathcal{N}_{3-color}(G)$ can be specified as
+The tensor network for the vertex coloring problem $\mathcal{N}_{\text{3-color}}(G)$ can be specified as
 \begin{equation}\label{eq:colortensornetwork}
 \begin{split}
-    \Sigma &= \{c_v \mid v \in V\},\\
+    \Lambda &= \{c_v \mid v \in V\},\\
     \mathcal{T} &= \{W^{(v)}_{c_v} \mid v\in V\} \cup \{B^{(u, v)}_{c_uc_v} \mid (u, v) \in E\},\\
@@
 \begin{theorem}\label{thm:cutcomplex}
-    The tensor network representation of a K-coloring problem on graph $G=(V,E)$ (\Cref{eq:colortensornetwork}) can be contracted in $cc(\mathcal{N}_{K-color}(G)) = O(|E|)K^{O({\rm tw}(G))}$ number of additions and multiplications.
+    The tensor network representation of a K-coloring problem on a graph $G=(V,E)$ (\Cref{eq:colortensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{K-color}}(G)) = O(|E|)K^{O({\rm tw}(G))}$ number of additions and multiplications.
 \end{theorem}
 The proof is similar to that for \Cref{thm:complexreal} except the dimension of each degree of freedom is $K$.
-%The number of possible colorings can be obtained by contracting this tensor network by setting $r_v, g_v$ and $b_v$ to $1$.
 Let $x^{w_{uv}} = x$ and $r_v = g_v = b_v = 1$; we then have a graph polynomial,
@@
 To reduce the cutting problem on $G$ to the contraction of a tensor network, we first define a Boolean degree of freedom $s_v\in\{0, 1\}$ for each vertex $v\in V$.
-The tensor network representation for the cutting problem $\mathcal{N}_{cut}$ can be specified as
+The tensor network representation for the cutting problem $\mathcal{N}_{\text{cut}}$ can be specified as
 \begin{equation}\label{eq:cuttensornetwork}
@@
     \mathcal{T} &= \{B^{(u, v)}_{s_us_v} \mid (u, v) \in E\},\\
-    \Sigma &= \{s_v \mid v \in V\},\\
+    \Lambda &= \{s_v \mid v \in V\},\\
     \boldsymbol{\sigma}_o &= \varepsilon,\\
@@
 \begin{theorem}\label{thm:colorcomplex}
-    The tensor network representation of a cuting problem on graph $G=(V,E)$ (\Cref{eq:cuttensornetwork}) can be contracted in $cc(\mathcal{N}_{cut}(G)) = O(|E|)2^{O({\rm tw}(G))}$ number of additions and multiplications.
+    The tensor network representation of a cuting problem on a graph $G=(V,E)$ (\Cref{eq:cuttensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{cut}}(G)) = O(|E|)2^{O({\rm tw}(G))}$ number of additions and multiplications.
 \end{theorem}
@@
 To reduce this problem to the contraction of a tensor network, we first map a vertex $v\in V$ to a Boolean degree of freedom $s_v\in\{0, 1\}$.
-The tensor network for the dominating set problem $\mathcal{N}_{dom}$ can be specified as
+The tensor network for the dominating set problem $\mathcal{N}_{\text{dom}}$ can be specified as
 \begin{equation}\label{eq:domtensornetwork}
 \begin{split}
-    \Sigma &= \{s_v \mid v \in V\},\\
+    \Lambda &= \{s_v \mid v \in V\},\\
     \mathcal{T} &= \{T^{(v)}_{s_{N(v,1)}s_{N(v, 2)} \ldots s_{N(v,d(v))} s_v} \mid v\in V\},\\
@@
 \begin{theorem}\label{thm:domcomplex}
-    The tensor network representation of a dominating set problem on graph $G=(V,E)$ (\Cref{eq:domtensornetwork}) can be contracted in $cc(\mathcal{N}_{dom}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications.
+    The tensor network representation of a dominating set problem on a graph $G=(V,E)$ (\Cref{eq:domtensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{dom}}(G)) = O(|V|)2^{O({\rm tw}(G)\Delta)}$ number of additions and multiplications.
 \end{theorem}
@@
 $s_v = 0$ stands for variable $v$ having value \texttt{false} while $s_a=1$ stands for having value \texttt{true}.
-% For example, a $k$-th clause $\neg a \vee b \vee \neg c$ can be mapped to a tensor labelled by $(s_a, s_b, s_c)$.
-% \begin{equation}
-% T^{(k)} = \left(\begin{matrix}
-% \left(\begin{matrix}
-% x^{w_k} & x^{w_k} \\
-% x^{w_k} & x^{w_k}
-% \end{matrix}\right) \\
-% \left(\begin{matrix}
-% x^{w_k} & x^{w_k} \\
-% 1 & x^{w_k}
-% \end{matrix}\right)
-% \end{matrix}\right),
-% \end{equation}
-% where $w_k$ is a weight associated with a clause. There is only one entry $(s_a, s_b, s_c) = (1, 0, 1)$ that makes this clause unsatisfied. The tensor network representation is
-The tensor network $\mathcal{N}_{CNF}$ can be specified as
+The tensor network $\mathcal{N}_{\text{CNF}}$ can be specified as
 \begin{equation}\label{eq:sattensornetwork}
 \begin{split}
-    \Sigma &= \{s_v \mid v \in V\},\\
+    \Lambda &= \{s_v \mid v \in V\},\\
     \mathcal{T} &= \{W^{(v)}_v \mid v \in V\} \cup \{T^{(k)}_{s_{N(k,1)} s_{N(k, 2)}\ldots s_{N(k,d(k)))}} \mid k=1,\ldots,M\},\\
@@
 \end{equation}
-and a tensor defined on caluse $C^{(k)}$ is
+and a tensor defined on the clause $C^{(k)}$ is
 \begin{equation}
 T^{(k)}_{s_{N(k, 1)} s_{N(k, 2)} \ldots s_{N(k, d(k))}} = \begin{cases}
-    x^{w_k}, &C^{(k)} ~is~ satisfied ~by~ (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
+    x^{w_k}, &C^{(k)} \text{~is~ satisfied ~by~ } (s_{N(k, 1)}, s_{N(k, 2)}, \ldots, s_{N(k, d(k))})\\
     1, &{\rm otherwise}
@@
 \end{equation}
-where $N(k, i) = \begin{cases}\neg C^{(k)}_i, &C^{(k)}_i \in \neg V\\ C^{(k)}_i, & C^{(k)}_i \in V\end{cases}$ is the $i$th literal in $C^{(k)}$ with its negation sign removed and $d(k)$ is the number of boolean variables in it.
+where $N(k, i) = \begin{cases}\neg C^{(k)}_i, &C^{(k)}_i \in \neg V\\ C^{(k)}_i, & C^{(k)}_i \in V\end{cases}$ is the $i$th literal in $C^{(k)}$ with its negation sign removed and $d(k)$ is the number of boolean variables in it;
 $w_k$ is the weight associated with clause $C^{(k)}$.
 \begin{theorem}\label{thm:cnfcomplex}
-    The tensor network representation of a CNF (\Cref{eq:sattensornetwork}) can be contracted in $cc(\mathcal{N}_{CNF}) = O(M)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $M$ is the number of clauses,
-    $H$ is a hypergraph constructed by mapping a variables $v\in V$ to a vertex and the $k$th clause $C^{(k)}$ to a hyperedge connecting $\{N(k, i)\mid i=1,\ldots, d(k)\}$.
-\end{theorem}
-This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{CNF}$.
-Let $x^{w_k} = x$ and $1_v = 1$, one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
+    The tensor network representation of a CNF (\Cref{eq:sattensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{CNF}}) = O(M)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $M$ is the number of clauses,
+    $H$ is a hypergraph constructed by mapping a variable $v\in V$ to a vertex and the $k$th clause $C^{(k)}$ to a hyperedge connecting $\{N(k, i)\mid i=1,\ldots, d(k)\}$.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{\text{CNF}}$.
+Let $x^{w_k} = x$ and $1_v = 1$; one can get a polynomial, in which the $k$-th coefficient gives the number of assignments that $k$ clauses are satisfied.
 
@@
 It is the hypergraph generalization of the independent set problem, where a set corresponds to a vertex and an element corresponds to a hyperedge.
-The generic tensor network for the set packing problem $\mathcal{N}_{pack}$ also has a similar form as that for the independent set problem
+The generic tensor network for the set packing problem $\mathcal{N}_{\text{pack}}$ also has a similar form as that for the independent set problem
 \begin{equation}\label{eq:packtensornetwork}
 \begin{split}
-    \Sigma &= \{s_\sigma \mid \sigma \in S\},\\
+    \Lambda &= \{s_\sigma \mid \sigma \in S\},\\
     \mathcal{T} &= \{B^{(v)}_{s_{N(v, 1)} \ldots s_{N(v, d(v))}} \mid v\in V\} \cup \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\},\\
@@
 \end{equation}
-where for each $v \in V$, we have the constraints over sets containing it $N(v) = \{\sigma\mid \sigma\in S \wedge v \in \sigma\}$ as
+where for each $v \in V$, we have the constraints over sets, $N(v) = \{\sigma\mid \sigma\in S \wedge v \in \sigma\}$, that containing it as
 \begin{equation}
@@
 \begin{theorem}\label{thm:packcomplex}
-    The tensor network representation of a set packing problem (\Cref{eq:packtensornetwork}) can be contracted in $cc(\mathcal{N}_{pack}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
-    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.
-\end{theorem}
-This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{cover}$.
+    The tensor network representation of a set packing problem (\Cref{eq:packtensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{pack}}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
+    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets, $N(v)$, that containing it.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{\text{pack}}$.
 
@@
 To get the generic tensor network representation, we first map a set $\sigma \in S$ to a Boolean degree of freedom $s_\sigma\in\{0, 1\}$.
-Then the tensor network representation for the set covering problem $\mathcal{N}_{pack}$ can be specified as
+Then the tensor network representation for the set covering problem $\mathcal{N}_{\text{cover}}$ can be specified as
 \begin{equation}\label{eq:covertensornetwork}
 \begin{split}
-    \Sigma &= \{s_\sigma \mid \sigma \in \mathcal{S}\},\\
+    \Lambda &= \{s_\sigma \mid \sigma \in \mathcal{S}\},\\
     \mathcal{T} &= \{W^{(\sigma)}_{s_\sigma} \mid \sigma \in S\} \cup \{B^{(v)}_{s_{N(v, 1)}s_{N(v, 2)}\ldots s_{N(\sigma, d(v))}} \mid v \in V\},\\
@@
 \begin{theorem}\label{thm:covercomplex}
-    The tensor network representation of a set covering problem (\Cref{eq:covertensornetwork}) can be contracted in $cc(\mathcal{N}_{cover}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
-    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets containing it $N(v)$.
-\end{theorem}
-This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{cover}$.
+    The tensor network representation of a set covering problem (\Cref{eq:covertensornetwork}) can be contracted in $cc(\mathcal{N}_{\text{cover}}) = O(|S|)2^{O({\rm tw}(H))}$ number of additions and multiplications, where $|S|$ is the number of sets,
+    $H$ is a hypergraph constructed by mapping a set $\sigma\in S$ to a vertex and element $v \in V$ to a hyperedge connecting sets $N(v)$, that containing it.
+\end{theorem}
+This can be proved by showing the hypergraph $H$ is the line graph of $\mathcal{N}_{\text{cover}}$.
 
@@
 The tensor element type is the finite-field algebra so that we can reach an arbitrary precision.
-We also computed the independence polynomial for these lattices up to size $30\times 30$ in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{Github repository}.
+We also computed the independence polynomial for these lattices up to size $30\times 30$ in our \href{https://github.com/GiggleLiu/NoteOnTropicalMIS/tree/master/data}{GitHub repository}.
 
@@
 \end{table}
-% online digit seperator: https://www.browserling.com/tools/thousands-separator
 

### 2022-09-23 reply/reply.tex
Updates from Overleaf

--- 2022-08-27 replys/reply.tex
@@
 \newcommand{\xgreen}[1]{[{\bf  \color{green}{\sout{XG: #1}}}]}
-\newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
-\newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
+% \newcommand{\blue}[1]{[{\bf  \color{blue}{JG: #1}}]}
+% \newcommand{\xblue}[1]{[{\bf  \color{blue}{\sout{JG: #1}}}]}
 \newcommand{\cyan}[1]{[{\bf  \color{cyan}{ML: #1}}]}
@@
 \newcommand{\material}[1]{\iffalse[{\bf  \color{cyan}{Material: #1}}]\fi}
-\newcommand{\referee}[1]{\item {\color{or}{#1}}}
+\newcommand{\referee}[1]{\item {\color{blue}{#1}}}
 
@@
 
-Thank you for your handling and careful consideration of our manuscript ``Computing solution space properties of combinatorial optimization problems via generic tensor networks'', MS\#M150178, for sending it for in-depth review, and for giving us the opportunity to address the reviewer's comments and to refine our manuscript.
-We are very excited that you also read through the paper and give a possitive feedback.
+Thank you for your handling and careful consideration of our manuscript (MS\#M150178) titled ``Computing solution space properties of combinatorial optimization problems via generic tensor networks'' and offering us the opportunity to address the referee's comments and improve our manuscript.
+We appreciate that you also spent time to read the manuscript and are delighted to hear that you deem it may merit publication after minor revision.
 
-We have revised the manuscript according to the reviewer's constructive suggestions.
-Below, we provide detailed point-to-point response to all of the reviewer's comments, as well as a summary of the changes we have introduced in the main text, figures, and supplementary materials.
-Thank you again for your consideration!
-\\
+We have revised the manuscript according to the referee's constructive suggestions.
+Below, we provide a detailed point-to-point response to all of the referee's comments, as well as a summary of the changes we have introduced in the main text, figures, and appendices.
+We thank the referee's feedback and we think these revisions improved our manuscript.
+We believe we have satisfactorily addressed all referee's questions and the manuscript will be a valuable contribution to the SISC journal.
 
-Best Wishes,\\
+Thank you again for your consideration! \\
+
+Sincerely,\\
 Jin-Guo Liu, Xun Gao, Madelyn Cain, Mikhail D. Lukin and Sheng-Tao Wang
@@
 
-\subsection{List of Main Modifications in the Manuscript}\label{header-n30}
+\subsection{List of Main Changes in the Manuscript}\label{header-n30}
 \begin{enumerate}
 \def\labelenumi{\arabic{enumi}.}
-\item The Section ...
-\item A new figure, ...
-\item We have added a paragraph at the ...
-\item In the revised Supplementary Material, a Section ...
-\item In the revised Supplementary Material, the Section ...
-\item The section ...
+\item We added a definition on tensor network in \textit{Definition 2.1}.
+\item We defined the tensor network representation for all combinatorial optimization problems rigorously in Eq.~4.3 and Appendix B.
+\item We restructured the manuscript and added several theorems and proofs to the main claims in the paper, including the computational complexity of solution space properties in the main text and tensor networks in Appendix B.
+\item We fixed a number of typos and sharpened some sentences according to the Referee's suggestions.
 \end{enumerate}
@@
 \referee{
-This is a review for "Computing solution space properties of combinatorial optimization problems via generic tensor networks" by Jin-Guo Liu, Xun Gao, Madelyn Cain, Mikhail Lukin, and Sheng-Tao Wang.
-The main contribution of the paper is claimed to be "introduction of a unified framework to compute solution space properties of a broad class of combinatorial optimization problems."
+\textbf{Referee's comments}: This is a review for "Computing solution space properties of combinatorial optimization problems via generic tensor networks" by Jin-Guo Liu, Xun Gao, Madelyn Cain, Mikhail Lukin, and Sheng-Tao Wang.
+The main contribution of the paper is claimed to be "introduction of a unified framework to compute solution space properties of a broad class of combinatorial optimization problems."}
 
-Comments:
-1) line 85, combinatoric problems → combinatorial problems.
+{\bf Response:}
+We thank the referee for a succinct summary of our main contributions.
 
+\referee{
+\textbf{Referee's comments}: Comments:
+1) line 85, combinatoric problems → combinatorial problems.}
+
+{\bf Response:}
+We've fixed the typo. Thanks the referee for pointing this point.
+
+\referee{\textbf{Referee's comments}:
 2) line 120, "commutative semiring is a field that needs not to have an additive inverse and multiplicative inverse"
@@
 Also, every field has multiplicative and additive inverse by definition so technically a commutative semiring is not a field.
-Maybe the authors could rephrase the statement to make more sense.
+Maybe the authors could rephrase the statement to make more sense.}
 
-3) line 129, $\oplus$ resembles XOR, it may not be the best notation in my opinion in the context of computer science.
+{\bf Response:}
+We thank the referee for pointing this out.
+We agree with the referee that the original sentence is not technically correct.
+We've changed the sentence to ``In contrast with a field, a commutative semiring does not need not to have an additive inverse and a multiplicative inverse”.
 
-4) line 154, "we map a vertex $v \in V$ to a label $s_v \in {0,1}$ of dimension 2 where we use 0(1) to denote a vertex is absent(present) in the set"
+\referee{\textbf{Referee's comments}:
+3) line 129, $\oplus$ resembles XOR, it may not be the best notation in my opinion in the context of computer science.}
+
+{\bf Response:}
+After some considerations, we did not find a better symbol than $\oplus$ to represent the generic plus, but we've added in the manuscript a footnote to emphasize this notation is different from the XOR in computer science when we first introduce the notation: ``We use the $\oplus$ operator throughout this paper to denote the generic addition, which is not the logical \texttt{XOR} operation, in which the symbol typically represents in computer science”.
+This should be able to reduce confusion from readers.
+
+\referee{\textbf{Referee's comments}:
+4) line 154, ``we map a vertex $v \in V$ to a label $s_v \in {0,1}$ of dimension 2 where we use 0(1) to denote a vertex is absent(present) in the set”
 
@@
 $sv:V\rightarrow{0,1}\times2$ but from the description it seems to be a single number i.e.
-an element of the set ${0,1}$.
+an element of the set ${0,1}$.}
 
-5) Line 156-157, equation (4.1) is said to be indexed by $s_v$ but $s_v$ does not appear in the equation.
+{\bf Response:} We thank the referee for pointing out the confusion.
+We've revised the sentence to be the following: ``We map each vertex $v\in V$ to a label $s_v \in \{0, 1\}$, where we use $0$ or $1$ to denote a vertex is absent or present in $I$, respectively”.
+$s_v$ is a single number and an element of the set $\{0, 1\}$.
+We removed ``of dimension 2” as well to avoid confusion.
 
+\referee{\textbf{Referee's comments}:
+5) Line 156-157, equation (4.1) is said to be indexed by $s_v$ but $s_v$ does not appear in the equation.}
+
+{\bf Response:} We removed the reference to $s_v$ in the sentence.
+
+\referee{\textbf{Referee's comments}:
 6) Line 158-159, " $x_v$ is a variable associated with $v$".
@@
 {\bf Response:} 
-Thank you for the careful reading and constructive comments on notations. We applied the most of the suggested changes accordingly in the main text to make it more readable except the comment 3).
-We can not find a better symbol than $\oplus$ to represent the generic plus, so we emphasised this notation is different from the XOR in computer science when we first introduce it.
+We clarified this and changed the text to ``$x_v$ is an  element of some commutative semiring (e.g., listed in Table 1) associated with vertex $v$ and its power with an integer is defined by repeated multiplication.'' in the main text.
 
 \referee{
-A lot of effort seems to have been put in making the paper but due to the informal style of narration from the very beginning, misinterpretation is very likely, especially for a newcomer in the field, and can be quite confusing for specialists as well.
+\textbf{Referee's comments}: A lot of effort seems to have been put in making the paper but due to the informal style of narration from the very beginning, misinterpretation is very likely, especially for a newcomer in the field, and can be quite confusing for specialists as well.
 The basic definitions for e.g.
@@
 {\bf Response:}
-Thanks the Referee for acknologying the effort we put in making the paper.
-The Referee not only points out the problem in writing, but also provide constructive comments to help the paper present better.
-We re-organized the contents in the definition, theorem, proposition style to make the key points more clear to readers.
+We thank the referee for acknowledging our efforts in this work and appreciate 
+their constructive comments on how to reduce confusion from readers by improving the presentations of the paper.
+We followed the suggestions from the referee and added the definition of tensor networks in Definition 2.1.
+More extensively, we reorganized the main results in the theorem-proof style to make them more clear to readers and specialists.
+
 \referee{
-Also, I recommend the authors better compare with prior work on this topic for e.g. https://arxiv.org/pdf/1405.7375.pdf and relevant references therein.
+\textbf{Referee's comments}: Also, I recommend the authors better compare with prior work on this topic for e.g. https://arxiv.org/pdf/1405.7375.pdf and relevant references therein.
 }
@@
 {\bf Response:}
-Thank the Referee for pointing out a work that we did not notice before.
-In the introduction, we cited a review paper from the same author~\cite{Biamonte2017}.
-It is definitely better to cite and compare this earlier work as you suggested as well.
-We also added more discussion about the work you mentioned in the Appendix B.6, where we constructed the tensor network for the satisfiability problem to credit the work you mentioned properly.
+We thank the referee for pointing out this relevant work.
+Besides citing and comparing with the paper the referee suggested, we have added another review paper in the introduction of section 3 from one of the authors of the suggested paper~\cite{Biamonte2017}.
+We have also added more discussion in Appendix B.6 about the work the referee mentioned, where we constructed the tensor network for the satisfiability problem.
 

### 2022-09-23 paper/paper.tex
new unified paper

@@
-\documentclass[review, onefignum, onetabnum]{siamart190516}
+\documentclass[onefignum, onetabnum]{siamart190516}
 
@@
 \input{shared}
-
-\externaldocument{suppl}
 
@@
 These labels can be used as subscripts of tensors to index tensor elements, e.g.\ $W^{(v)}_0=1$ is the first element associated with $s_v=0$ and $W^{(v)}_1=x_v^{w_v}$ is the second element associated with $s_v=1$, where $x_v$ is an  element of some commutative semiring (e.g., listed in \Cref{tbl:generictypes}) associated with vertex $v$ and its power with an integer is defined by repeated multiplication.
-The labels associated to the output tensor is an empty string $\varepsilon$, meaning this tensor has rank $0$, i.e.~a scalar.
+The labels associated to the output tensor is an empty string $\varepsilon$, meaning this tensor has rank $0$, i.e.~the output is a scalar.
 The independence constraint is encoded in the edge tensors, where we use $B^{(u, v)}_{11} = 0$ to denote two vertices connected by an edge $(u, v)$ cannot be both in the independent set. 
@@
 The contraction complexity is $O(|\mathcal{N}|)2^{O({\rm tw}(L(\mathcal{N})))}$, where $|\mathcal{N}|$ is the number of tensors in $\mathcal{N}$~\cite{Markov2008}.
-For the independent set problem on graph $G = (V, E)$, the line graph of the hypergraph representation of the tensor network in \Cref{eq:mistensornetwork} is the same as the graph $G$ up to some isolated vertices, hence the contraction complexity of this tensor network with an optimal contraction order is $O(|E|)2^{O({\rm tw}(G))}$.
+For the independent set problem on graph $G = (V, E)$, the line graph of the hypergraph representation of the tensor network in \Cref{eq:mistensornetwork} is isomorphic to the graph $G$ up to some isolated vertices, hence the contraction complexity of this tensor network with an optimal contraction order is $O(|E|)2^{O({\rm tw}(G))}$.
 \end{proof}
@@
     \left(W^{\rm T}\right)^{(v)} = \left(\begin{matrix}
-        1 \\
+        \mymathbb{1} \\
         \infty^{w_v}
@@
 To find solutions corresponding to the largest $K$ sizes, one can combine the extended tropical algebra with the bit-string algebra (\Cref{eq:singleconfig}).
-Since the $\oplus$ operation of the configuration sampler will not be used in the combined algebra, the resulting configurations are deterministic and complete.
+Since the $\oplus$ operation of the configuration sampler is not used in the combined algebra, the resulting configurations are deterministic and complete.
 
@@
 
+\section{Performance benchmarks}\label{sec:benchmark}
+We run a single thread benchmark on central processing units (CPU) Intel(R) Xeon(R) CPU E5-2686 v4 @ 2.30GHz, and its CUDA version on a GPU Tesla V100-SXM2 16G.
+The results are summarized in \Cref{fig:benchmark}.
+The graphs in all benchmarks are random three-regular graphs, which have treewidth that is asymptotically smaller than $|V|/6$~\cite{Fomin2006}.
+In this benchmark, we do not include traditional algorithms for finding the MIS sizes such as branching~\cite{Tarjan1977, Robson1986} or dynamic programming~\cite{Courcelle1990, Fomin2013}.
+To the best of our knowledge, these algorithms are not suitable for computing most of the solution space properties mentioned in this paper.
+The main goal of this section is to show the relative computation time for calculating different solution space properties.
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig1.pdf}
+    \caption{Benchmark results for computing different solution space properties of independent sets of random three-regular graphs with different tensor element types.
+    The time in these plots only includes tensor network contraction, without taking into account the contraction order finding and just-in-time compilation time.
+    Legends are properties, algebra, and devices that we used in the computation; one can find the corresponding computed solution space property in Table 1 in the main text.
+    (a) time and space complexity versus the number of vertices for the benchmarked graphs.
+    (b) The computation time for calculating the MIS size and for counting the number of all independent sets (ISs), the number of MISs,
+        the number of independent sets having size $\alpha(G)$ and $\alpha(G)-1$, and finding $100$ largest set sizes.
+    (c) The computation time for calculating the independence polynomials with different approaches.
+    (d) The computation time for configuration enumeration, including single MIS configuration, the enumeration of all independent set configurations, all MIS configurations, all independent sets,
+    and all independent set configurations having size $\alpha(G)$ and $\alpha(G)-1$.
+    }
+    \label{fig:benchmark}
+\end{figure}
+
+\Cref{fig:benchmark}(a) shows the time and space complexity of tensor network contraction for different graph sizes.
+The contraction order is obtained using the local search algorithm in Ref.~\cite{Kalachev2021}.
+If we assume our contraction-order finding program has found the optimal treewidth, which is very likely to be true, the space complexity is the same as the treewidth of the problem graph.
+Slicing technique~\cite{Kalachev2021} has been used for graphs with space complexity greater than $2^{27}$ (above the yellow dashed line) to fit the computation into a 16GB memory.
+One can see that all the computation times in \Cref{fig:benchmark} (b), (c), and (d) have a strong correlation with the predicted time and space complexity.
+While in panel (d), the computation time of configuration enumeration and sum-product expression tree generation also strongly correlates with other factors such as the configuration space size.
+Among these benchmarks, computational tasks with data types real numbers, complex numbers, or tropical numbers (CPU only) can utilize fast basic linear algebra subprograms (BLAS) functions.
+These tasks usually compute much faster than ones with other element types in the same category.
+Immutable data types with no reference to other values can be compiled to GPU devices that run much faster than CPUs in all cases when the problem scale is big enough.
+These data types do not include those defined in \Cref{eq:polynomial}, \Cref{eq:set}, \Cref{eq:ext-tropical} and \Cref{eq:expr} or a data type containing them as a part.
+In \Cref{fig:benchmark}(c), one can see the Fourier transformation-based method is the fastest in computing the independence polynomial,
+but it may suffer from round-off errors (\Cref{sec:fft}). The finite field (GF$(p)$) approach is the only method that does not have round-off errors and can be run on a GPU.
+In \Cref{fig:benchmark}(d), one can see the technique to bound the enumeration space in \Cref{sec:bounding} improves the performance for more than one order of magnitude in enumerating the MISs.
+The bounding technique can also reduce the memory usage significantly, without which the largest computable graph size is only $\sim150$ on a device with 32GB main memory.
+
+We show the benchmark of computing the maximal independent set properties on $3$-regular graphs in \Cref{fig:benchmark-maximal},
+including a comparison to the Bron-Kerbosch algorithm from Julia package \href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}~\cite{Graphs}.
+\Cref{fig:benchmark-maximal}(a) shows the space and time complexities of tensor contraction, which are typically larger than those for the independent set problem.
+In \Cref{fig:benchmark-maximal}(b), one can see counting maximal independent sets are much more efficient than enumerating them, while our generic tensor network approach runs slightly faster than the Bron-Kerbosch approach in enumerating all maximal independent sets.
+
+\begin{figure} 
+    \centering
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig2.pdf}
+    \caption{Benchmarks of computing different solution space properties of the maximal independent sets (ISs) problem on random three regular graphs at different sizes.
+    (a) time and space complexity of tensor network contraction. 
+    (b) The wall clock time for counting and enumeration of maximal ISs. % The missing data is due to the memory limit.
+    }
+    \label{fig:benchmark-maximal}
+\end{figure}
+
+\section{An example of increased contraction complexity for the standard tensor network notation}\label{sec:tensorbad}
+
+In the standard Einstein's notation for tensor networks in physics, each index appears precisely twice: either both are in input tensors (which will be summed over) or one is in an input tensor and another in the output tensor.
+Hence a tensor network can be represented as an open simple graph, where an input tensor is mapped to a vertex, a label shared by two input tensors is mapped to an edge and a label that appears in the output tensor is mapped to an open edge.
+A standard tensor network notation is equivalent to the generalized tensor network in representation power.
+A generalized tensor network can be converted to a standard one by adding a $\delta$ tensors at each hyperedge, where a $\delta$ tensor of rank $d$ is defined as
+\begin{equation}
+    \delta_{i_1, i_2,\ldots,i_d} = \begin{cases}
+        1, & i_1=i_2=\ldots =i_d,\\
+        0, & \text{otherwise}.
+    \end{cases}
+\end{equation}
+
+In the following example, we will show this conversion might increase the contraction complexity of a tensor network.
+Let us consider the following King's graph. \\
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.2}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+\end{tikzpicture}}
+
+The generalized tensor network for solving the MIS problem on this graph has the following hypergraph representation, where we use different colors to distinguish different hyperedges.
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.08}
+    \def\a{0.07}
+    \def\L{0.6}
+    \def\l{0.1}
+    \def\sql{0.24}
+    \pgfmathsetseed{2}
+    \foreach[evaluate={\cr=0.1+0.5*Mod(\x,2)}] \x in {1,...,5}
+        \foreach[evaluate={\cg=0.1+0.3*Mod(\y,2); \cy=0.5-0.5*Mod(\y,2)}] \y in {1,...,5}{
+            \edef\R{\pdfuniformdeviate 255}
+            \edef\G{\pdfuniformdeviate 255}
+            \edef\B{\pdfuniformdeviate 255}
+            \xdefinecolor{MyColor}{RGB}{\R,\G,\B}
+            \ifnum \x < 5
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.5,\y);
+                \ifnum \y < 5
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y+0.3);
+                \fi
+                \ifnum \y > 1
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x+0.3,\y-0.3);
+                \fi
+            \fi
+            \ifnum \x > 1
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.5,\y);
+                \ifnum \y < 5
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y+0.7);
+                \fi
+                \ifnum \y > 1
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x-0.7,\y-0.7);
+                \fi
+            \fi
+            \ifnum \y < 5
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y+0.5);
+            \fi
+            \ifnum \y > 1
+                \draw [thick, MyColor, opacity=1.0, line cap=round] (\x,\y) -- (\x,\y-0.5);
+            \fi
+        }
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}{
+            %\filldraw[fill=black] (\x,\y) circle [radius=0.7*\r];
+        }
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}{
+            \ifnum \y < 5
+                \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
+                \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
+            \fi
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
+        }
+    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
+                    post length=0mm,pre length=0mm}}
+    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
+\end{tikzpicture}}
+Vertex tensors are not shown here because they can be absorbed into an edge tensor and hence do not change the contraction complexity.
+If we contract this tensor network in the column-wise order, the maximum intermediate tensor has rank $\sim L$, which can be seen by counting the number of colors at the cut.
+
+By adding $\delta$ tensors to hyperedges, we have the standard tensor network represented as the following simple graph.
+
+\centerline{\begin{tikzpicture}
+    \def\r{0.08}
+    \def\a{0.1}
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,5}
+            \filldraw[fill=black] (\x,\y) circle [radius=\r];
+    \foreach \x in {1,...,5}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x,\y+0.5) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.5,\x) circle [radius=\r];
+            \draw [black,thick] (\x,\y) -- (\x,\y+1);
+            \draw [black,thick] (\y,\x) -- (\y+1,\x);
+        }
+    \foreach \x in {1,...,4}
+        \foreach \y in {1,...,4}{
+            \filldraw[fill=black] (\x+0.3,\y+0.3) circle [radius=\r];
+            \filldraw[fill=black] (\y+0.3,\x+0.7) circle [radius=\r];
+            \draw [black,thick] (\x,\y) -- (\x+1,\y+1);
+            \draw [black,thick] (\y+1,\x) -- (\y,\x+1);
+        }
+    \tikzset{decoration={snake,amplitude=.4mm,segment length=2mm,
+                    post length=0mm,pre length=0mm}}
+    \draw [decorate] (2.7, 0.5) -- (2.7, 5.5);
+\end{tikzpicture}}
+
+In this diagram, the additional $\delta$ tensors can have ranks up to $8$.
+If we still contract this tensor network in a column-wise order, the maximum intermediate tensor has rank $\sim3L$, i.e.
+the space complexity is $\approx 2^{3L}$, which has a larger complexity than using the generalized tensor network notation.
+
+\section{The discrete Fourier transform approach to computing the independence polynomial}\label{sec:fft}
+
+In \Cref{sec:finitefield} in the main text, we show that the independence polynomial can be obtained by solving the linear equation \Cref{eq:lineareq} using the finite field algebra.
+One drawback of using finite field algebra is that its matrix multiplication is less computationally efficient compared with floating-point matrix multiplication.
+Here, we show an alternative method with standard number types but with controllable round-off errors.
+Instead of choosing $x_{i}$ as random numbers, we can choose them such that they form a geometric sequence in the complex domain $x_j = r\omega^j$, where $r \in \mathbb{R}$ and $\omega = e^{-2\pi i/( \alpha(G)+1)}$.
+The linear equation thus becomes
+\begin{equation}
+\left(\begin{matrix}
+1 & r & r^2 & \ldots & r^{\alpha(G)} \\
+1 & r\omega & r^2\omega^2 & \ldots & r^{\alpha(G)} \omega^{\alpha(G)} \\
+\vdots & \vdots & \vdots &\ddots & \vdots \\
+1 & r\omega^{\alpha(G)} & r^2\omega^{2{\alpha(G)}} & \ldots & r^{\alpha(G)}\omega^{{\alpha(G)}^2}
+\end{matrix}\right)
+\left(\begin{matrix}
+a_0 \\ a_1 \\ \vdots \\ a_{\alpha(G)}
+\end{matrix}\right)
+= \left(\begin{matrix}
+y_0 \\ y_1 \\ \vdots \\ y_{\alpha(G)}
+\end{matrix}\right).
+\end{equation}
+
+Let us rearrange the coefficients $r^j$ to $a_j$, the matrix on the left side becomes the discrete Fourier transform matrix.
+Thus, we can obtain the coefficients by inverse Fourier transform $\vec a_r = {\rm FFT^{-1}}(\omega) \cdot \vec y$, where $(\vec a_r)_j = a_j r ^j$.
+By choosing different $r$, one can obtain better precision for small $j$ by choosing $r<1$ or large $j$ by choosing $r>1$.
+
+\section{Computing maximum sum combination}\label{sec:maxsum}
+Given two sets $A$ and $B$ of the same size $n$.
+It is known that the maximum $n$ sum combination of $A$ and $B$ can be computed in time $O(n\log(n))$.
+The standard approach to solve the sum combination problem requires storing the variables in a heap --- a highly dynamic binary tree structure that can be much slower to manipulate than arrays.
+In the following, we show an algorithm with roughly the same complexity but does not need a heap.
+This algorithm first sorts both $A$ and $B$ and then uses the bisection to find the $n$-th largest value in the sum combination.
+The key point is we can count the number of entries greater than a specific value
+in the sum combination of $A$ and $B$ in linear time.
+As long as the data range is not exponentially large, the bisection can be done in $O(\log(n))$ steps, giving the time complexity $O(n\log(n))$.
+We summarize the algorithm as in \Cref{alg:sumcombination}.
+
+\LinesNumberedHidden
+\begin{algorithm}[!ht]
+    \SetKwProg{Fn}{function}{}{end}
+    \small
+    \SetAlgoNoLine
+    Let $A$ and $B$ be two sets of size $n$\;
+
+    \tcp{sort $A$ and $B$ in ascending order}
+    $A \gets {\rm sort}(A)$\;
+
+    $B \gets {\rm sort}(B)$\;
+
+    \tcp{use bisection to find the $n$-th largest value in sum combination}
+
+    ${\rm high} \gets A_n+B_n$\;
+
+    ${\rm low} \gets A_1+B_n$\;
+
+    \While{true}{
+        ${\rm mid} \gets ({\rm high} + {\rm low}) / 2$\;
+
+        $c \gets \texttt{count\_geq}(n, A, B, {\rm mid})$\;
+
+        \uIf{$c > n$}{
+            ${\rm low} \gets {\rm mid}$\;
+        }\uElseIf{$c = n$}{
+            \Return \texttt{collect\_geq}$(n, A, B, {\rm mid})$\;
+        }\Else{
+            ${\rm high} \gets {\rm mid}$\;
+        }
+    }
+
+    \Fn{{\rm \texttt{count\_geq}}($n$, $A$, $B$, $v$)}{
+        $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
+
+        $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
+
+        $c \gets 0$\; \tcp*[l]{the counting of sum combinations s.t. $a+b\geq v$}
+
+        \For{$q$ = $n, n-1 \ldots 1$}{
+            $b \gets B_{n-q+1}$\;
+
+            \While{$k < n$ \textbf{and} $a+b \geq v$}{
+                $k \gets k+1$\;
+
+                $a \gets A_{n-k+1}$\;
+            }
+
+            \uIf{$a+b \geq v$}{
+                $c \gets c + k$\;
+            }\Else{
+                $c \gets c + k-1$\;
+            }
+        }
+        \Return c\;
+    }
+
+    % \Fn{\rm collect\_geq($n$, $A$, $B$, $v$)}{
+    %     $k \gets 1$\; \tcp*[l]{number of entries in $A$ s.t. $a+b\geq v$}
+
+    %     $a \gets A_{n}$\; \tcp*[l]{the smallest entry in $A$ s.t. $a+b\geq v$}
+
+    %     $S \gets \{\}$ \tcp*[l]{the sum combinations s.t. $a+b\geq v$}
+
+    %     \For{$q$ = $n, n-1 \ldots 1$}{
+    %         $b \gets B_{n-q+1}$\;
+
+    %         \While{$k < n$ \textbf{and} $a+b \geq v$}{
+    %             $k \gets k+1$\;
+
+    %             $a \gets A_{n-k+1}$\;
+    %         }
+
+    %         \uIf{$a+b \geq v$}{
+    %             $m \gets k$\;
+    %         }\Else{
+    %             $m \gets k-1$\;
+    %         }
+    %         \For{$j$ = \KwTo $1,2\ldots,m$}{
+    %             $S \gets S \cup \{b + A_{n-j+1}\}$
+    %         }
+    %     }
+    %     \Return S\;
+    % }
+    \caption{Fast sum combination without using heap}\label{alg:sumcombination} 
+\end{algorithm}
+
+In this algorithm, function \texttt{collect\_geq} is similar the \texttt{count\_geq} except the counting is replace by collecting the items to a set.
+Inside the function \texttt{count\_geq}, variable $k$ monotoneously increase while $q$ monotoneously decrease in each iteration and
+the total number of iterations is upper bounded by $2n$.
+Here for simplicity, we do not handle the special element $-\infty$ in $A$ and $B$ and the potential degeneracy in the sums.
+It is nevertheless important to handle them properly in a practical implementation.
+
+\section{Technical guides}\label{sec:technical}
+
+This appendix covers some technical guides for efficiency, including an introduction to an open-source package \href{https://github.com/QuEraComputing/GenericTensorNetworks.jl}{GenericTensorNetworks}~\cite{GenericTensorNetworks} implementing the algorithms in this paper and the gist about how this package is implemented.
+One can install \texttt{GenericTensorNetworks} in a Julia REPL, by first typing \colorbox{lightgray}{\texttt{]}} to enter the \texttt{pkg>} mode and then typing
+\begin{lstlisting}
+pkg> add GenericTensorNetworks
+\end{lstlisting}
+followed by an \colorbox{lightgray}{\texttt{<ENTER>}} key.
+To use it for solving solution space properties, just go back to the normal mode (type \colorbox{lightgray}{\texttt{<BACKSPACE>}}) and type
+
+\begin{lstlisting}
+julia> using GenericTensorNetworks, Graphs
+
+julia> # using CUDA
+
+julia> solve(
+           IndependentSet(
+               Graphs.random_regular_graph(20, 3);
+               optimizer = TreeSA(),
+               weights = NoWeight(),
+               openvertices = ()
+           ),
+           GraphPolynomial();
+           usecuda=false
+       )
+0-dimensional Array{Polynomial{BigInt, :x}, 0}:
+Polynomial(1 + 20*x + 160*x^2 + 659*x^3 + 1500*x^4 + 1883*x^5 + 1223*x^6 + 347*x^7 + 25*x^8)
+\end{lstlisting}
+
+Here the main function \texttt{solve} takes three inputs: the problem instance of type \texttt{IndependentSet}, the property instance of type \texttt{GraphPolynomial} and an optional key word argument \texttt{usecuda} to decide to use GPU or not.
+If one wants to use GPU to accelerate the computation, ``\texttt{using CUDA}'' must be uncommented.
+The problem instance takes four arguments to initialize: the only positional argument is the graph instance one wants to solve, the keyword argument \texttt{optimizer} is for specifying the tensor network optimization algorithm, the keyword argument \texttt{weights} is for specifying the weights of vertices as either a vector or \texttt{NoWeight()}, and the keyword argument \texttt{openvertices} is for specifying the degrees of freedom not summed over.
+Here, we use the \texttt{TreeSA} method as the tensor network optimizer, and leave \texttt{weights} and \texttt{openvertices} as  default values.
+The \texttt{TreeSA} algorithm, which was invented in Ref.~\cite{Kalachev2021}, performs the best in most of our applications.
+The first execution of this function will be a bit slow due to Julia's just-in-time compilation.
+After that, the subsequent runs will be faster.
+The following diagram lists possible combinations of input arguments, where functions in the \texttt{Graph} are mainly defined in the package \texttt{Graphs}, and the rest can be found in \texttt{GenericTensorNetworks}.
+
+\centerline{\includegraphics[width=0.8\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/fig7.pdf}}
+
+The code we will show below is a gist of how the above package was implemented, which is mainly for pedagogical purpose.
+It covers most of the topics in the paper without caring much about performance.
+It is worth mentioning that this project depends on multiple open source packages in the Julia ecosystem:
+
+\begin{description}
+	\item[\href{https://github.com/under-Peter/OMEinsum.jl}{OMEinsum} and \href{https://github.com/TensorBFS/OMEinsumContractionOrders.jl}{OMEinsumContractionOrders}] are packages providing the support for Einstein's (or tensor network) notation and state-of-the-art algorithms for contraction order optimization, which includes the one based on KaHypar+Greedy~\cite{Gray2021, Pan2021} and the one based on local search~\cite{Kalachev2021}.
+	\item[\href{https://github.com/TensorBFS/TropicalNumbers.jl}{TropicalNumbers} and \href{https://github.com/TensorBFS/TropicalGEMM.jl}{TropicalGEMM}] are packages providing tropical number and efficient tropical matrix multiplication.
+	\item[\href{https://github.com/JuliaGraphs/Graphs.jl}{Graphs}] is a foundational package for graph manipulation in the Julia community.
+	\item[\href{https://github.com/JuliaMath/Polynomials.jl}{Polynomials}] is a package providing polynomial algebra and polynomial fitting.
+	\item[\href{https://github.com/scheinerman/Mods.jl}{Mods} and the \href{https://github.com/JuliaMath/Primes.jl}{Primes}] package providing finite field algebra and prime number manipulation.
+\end{description}
+
+They can be installed in a similar way to \texttt{GenericTensorNetworks}.
+After installing the required packages, one can open a Julia REPL, and copy-paste the following code snippet into it.
+
+\lstinputlisting[breaklines]{../democode/demo.jl}
+
 \end{document}

### 2022-11-21 paper/paper.tex
update

@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{figures/lattices.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 1cm 0cm 1cm}, clip]{lattices.pdf}
     \caption{The types of graphs used in the case study in \Cref{sec:entropy}.
@@
     \centering
-    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{figures/fig5.pdf}
+    \includegraphics[width=\textwidth, trim={0cm 0cm 0cm 0cm}, clip]{fig5.pdf}
     \caption{Mean entropy for lattice gases on graphs defined in \Cref{fig:lattices}.
@@
 \begin{figure} 
-    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{figures/fig6.pdf}
+    \includegraphics[width=\textwidth, trim={0.0cm 1cm 0.0cm 0cm}, clip]{fig6.pdf}
     \caption{Pairwise Hamming distances distribution for configurations sampled from independent sets with sizes $\geq \lceil\gamma \times \alpha(G)\rceil$.

### 2022-11-21 project/configurations.jl

@@ -9,14 +9,14 @@ function mis_configurations(n, seed; order, writefile, sc_target=12)
     mask = Matrix{Bool}(reshape(readdlm(fname)[seed+1,4:end], n, n))
     g = diagonal_coupled_graph(mask)
     gp = Independence(g; optimizer=GreedyMethod(), simplifier=MergeGreedy())
-    res_c = solve(gp, "counting max$order")[]
+    res_c = solve(gp, CountingMax(order))[]
     println("Graph $seed, n = $n, max2 count = $res_c")
     if sum(res_c.coeffs) > 10000000
         @warn "degeneracy too high!"
         return res_c, nothing
     end
     gp = Independence(g; optimizer=TreeSA(sc_target=sc_target), simplifier=MergeGreedy())
-    s2, configs = (res = solve(gp, "configs max$order (bounded)")[]; (res.maxorder, res.coeffs))
+    s2, configs = (res = solve(gp, ConfigsMax(order; bounded=true))[]; (res.maxorder, res.coeffs))
     @assert all(res_c.coeffs .== length.(configs))
     for i=1:order
         ofname = joinpath(folder, "$seed-$(i-1).dat")
@@ -62,7 +62,8 @@ for (n, seeds) in [
     #(10, 81:99)
     #(11, 0:99)
     #(12, 51:99)
-    (10, [156, 773, 105, 222, 417, 269, 309, 350, 786, 590, 109, 83, 243, 699, 425, 174, 925])
+    #(10, [156, 773, 105, 222, 417, 269, 309, 350, 786, 590, 109, 83, 243, 699, 425, 174, 925])
+    (9, [263])
     ]
     for seed in seeds
         @time mis_configurations(n, seed; order=2, writefile=true, sc_target=14)

### 2022-12-20 submit/paper.tex
update

--- 2022-05-11 paper/paper.tex
@@
 
-\author{
+\author{\footnote{Jin-Guo Liu and Xun Gao contributed equally to this work.}
 Jin-Guo Liu\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA; QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA  %\thanks{QuEra Computing Inc., 1284 Soldiers Field Road, Boston, MA, 02135, USA}
     (\email{jinguoliu@g.harvard.edu}).}
-\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}, contributed equally with Jin-Guo Liu to this work.).}
+\and {Xun Gao}\thanks{Department of Physics, Harvard University, Cambridge, Massachusetts 02138, USA (\email{xungao@g.harvard.edu}).}
 \and Madelyn Cain\footnotemark[2]

### 2022-12-20 project/fib2d.jl

@@ -1,0 +1,56 @@
+# To run this script, you need to install required packages in a Julia REPL:
+# ```julia
+# using Pkg; Pkg.add(["GenericTensorNetworks", "CUDA", "Comonicon", "DelimitedFiles"])
+# ```
+#
+# Then open a terminal, go to the file folder and type
+# ```bash
+# $ julia fib2d.jl 20
+# ```
+#
+# Report an issue here: https://github.com/QuEraComputing/GenericTensorNetworks.jl/issues
+# If you want the multi-GPU version of this code, please let me know: cacate0129@gmail.com
+
+using GenericTensorNetworks, Random, Comonicon, DelimitedFiles
+using CUDA; CUDA.allowscalar(false)
+
+"""
+Computing the two dimensional generalizatioon of Fibonacci numbers.
+
+# Arguments
+* `L`: the lattice size L x L.
+
+# Options
+* `--usecuda`: the CUDA device, -1 for not using GPU. Default is -1.
+* `--nslices`: the number of slices, which is used to reduce the space complexity. Default is `L-28`.
+* `--filename`: the filename to store the output. Default is `""` (not writting to a file).
+* `--seed`: the seed for finding contraction order. Default is `2`.
+"""
+@main function fib2d(L::Int; nslices::Int=max(0, L-28), usecuda::Int=-1, filename::String="", seed::Int=2)
+    usecuda >= 0 && CUDA.device!(usecuda)
+    Random.seed!(seed)
+    # the 2D Fibonacci number is defined by the total number of independent sets of a square lattice
+    g = square_lattice_graph(trues(L, L))
+    # both `optimizer` and `simplifier` are for tensor network contraction order optimization.
+    gp = Independence(g; optimizer=TreeSA(sc_target=28, sc_weight=1.0, nslices=nslices;
+        ntrials=7, βs=0.01:0.05:22.0, niters=20, rw_weight=2.0), simplifier=MergeGreedy())
+    @info "The graph size $L x $L, usecuda = $usecuda"
+    tc, sc, rw = timespacereadwrite_complexity(gp)
+    # complexities are defiened by the log2 number of arithmetic operations/elements/read write operations.
+    @info "Time complexity = $tc, space complexity = $sc, read-write complexity = $rw"
+   
+    # `big_integer_solve` uses the Chinese remainder theorem to combine many small remainders into a big integer.
+    # Note the number of independent sets is a very big number that can not be stored with fixed width integers.
+    res = GenericTensorNetworks.big_integer_solve(Int32, 100) do T
[…]
